### 2019-10-04 thesis_template/1_Intro/intro.tex
added content in latex

\chapter{Introduction}
\label{chapter:Introduction}
\thispagestyle{myheadings}

\section{Problem Description}
\label{sec:history}

Many of popular open source cluster computing frameworks for large scale data analysis, 
such as Hadoop and Spark, allow programmers to define objects in a host languages, such as Java.
The objects are then managed in RAM by the language and its runtime, Java Virtual Machine 
in the case of Java and Scala. Storing objects in memory enables machine to process iterative computation. 
One of the fundamental tasks for recent big data analysis is analysis using Machine Learning Algorithms, 
which require iterative process. As the amount of data increases, memory is required to keep many objects. 
Therefore, memory management plays a critical role in this task.

Memory management in Java and Scala is performed by garbage collection. 
The garbage collection brings a significant advantage for programmers by removing responsibility
for planning memory management by themselves. Instead, JVM monitors the state of memory and performs garbage
collection at certain points. However, these monitoring and auto-execution of garbage collection cost additional 
computation and might consume computation resources which should be used for data processing. This can significantly decrease performance of the computation.

In contrast, memory management in system language, such as C++, relies on programmers’ decision for when to allocate and deallocate memory. 
The functions, malloc/free consume most of the memory management. Proper implementation of system language for big data processing can be overperform the implementation in host language.
Nevertheless, implementing C++ performing proper memory management and guaranteeing security can be unproductive and complicated.

Considering the issue of memory management, we introduce solution based on unique memory management methods implemented in Rust, ownership and borrowing.
This unique concepts in Rust secure codes and perform memory management without monitoring memory or calling functions. We introduce implementations of
machine learning algorithms in both Java and Rust to assess performances of each memory management system for iterative big data processing tasks.

\section{Memory Management}
\label{sec:history}

Each value in Rust has a variable called its owner. This owner has information about the value, such as location in memory, 
length and capacity of the value. This owner can live on the scope associated with its life time. When the owner goes out of it’s scope, 
the value will be dropped. When a value already assigned to a variable is assigned to another variable, if the value is allocated 
on heap its information is copied to the new owner and drop the old owner disabling old variable. Similar thing happens when we pass variable to parameter of function. 
After passing a variable to a parameter, all the information is copied to new owner through the parameter and old owner is no longer available. 
The new owner can only live in the function and the object will be dropped. In this case, we have no longer access to the object after the function. 
To avoid this, Rust has a concept called borrowing. We can set reference for the parameter of function and use the reference for operation within function and drop the reference, 
but not the ownership.

### 2019-10-04 project/create_csv/run.sh

@@ -1,1 +1,4 @@
 
+cargo run ../data/input1.csv 1000 100
+cargo run ../data/input2.csv 2000 100
+cargo run ../data/input3.csv 3000 100

### 2019-10-06 thesis_template/0_Prelim/abs.tex
added RDD caching

--- 2019-10-04 thesis_template/1_Intro/intro.tex
@@
-\chapter{Introduction}
-\label{chapter:Introduction}
-\thispagestyle{myheadings}
+% ABSTRACT
 
-\section{Problem Description}
-\label{sec:history}
-
-Many of popular open source cluster computing frameworks for large scale data analysis, 
-such as Hadoop and Spark, allow programmers to define objects in a host languages, such as Java.
-The objects are then managed in RAM by the language and its runtime, Java Virtual Machine 
-in the case of Java and Scala. Storing objects in memory enables machine to process iterative computation. 
-One of the fundamental tasks for recent big data analysis is analysis using Machine Learning Algorithms, 
-which require iterative process. As the amount of data increases, memory is required to keep many objects. 
+Abstract 
+Many of popular open source cluster computing frameworks for large scale data analysis, such as Hadoop and Spark, 
+allow programmers to define objects in a host languages, such as Java. The objects are then managed in RAM 
+by the language and its runtime, Java Virtual Machine in the case of Java and Scala. Storing objects 
+in memory enables machine to process iterative computation. One of the fundamental tasks for recent big data analysis 
+is analysis using Machine Learning Algorithms, which require iterative process. As the amount of data increases, memory is required to keep many objects. 
 Therefore, memory management plays a critical role in this task.
 
-Memory management in Java and Scala is performed by garbage collection. 
-The garbage collection brings a significant advantage for programmers by removing responsibility
-for planning memory management by themselves. Instead, JVM monitors the state of memory and performs garbage
-collection at certain points. However, these monitoring and auto-execution of garbage collection cost additional 
-computation and might consume computation resources which should be used for data processing. This can significantly decrease performance of the computation.
+Memory management in Java and Scala is performed by garbage collection. The garbage collection brings a significant advantage 
+for programmers by removing responsibility for planning memory management by themselves. Instead, JVM monitors the state of memory 
+and performs garbage collection at certain points. However, these monitoring and auto-execution of garbage collection cost additional computation 
+and might consume computation resources which should be used for data processing. This can significantly decrease performance of the computation.
 
@@
 Considering the issue of memory management, we introduce solution based on unique memory management methods implemented in Rust, ownership and borrowing. 
-This unique concepts in Rust secure codes and perform memory management without monitoring memory or calling functions. We introduce implementations of
-machine learning algorithms in both Java and Rust to assess performances of each memory management system for iterative big data processing tasks.
-
-\section{Memory Management}
-\label{sec:history}
-
-Each value in Rust has a variable called its owner. This owner has information about the value, such as location in memory, 
-length and capacity of the value. This owner can live on the scope associated with its life time. When the owner goes out of it’s scope, 
-the value will be dropped. When a value already assigned to a variable is assigned to another variable, if the value is allocated 
-on heap its information is copied to the new owner and drop the old owner disabling old variable. Similar thing happens when we pass variable to parameter of function. 
-After passing a variable to a parameter, all the information is copied to new owner through the parameter and old owner is no longer available. 
-The new owner can only live in the function and the object will be dropped. In this case, we have no longer access to the object after the function. 
-To avoid this, Rust has a concept called borrowing. We can set reference for the parameter of function and use the reference for operation within function and drop the reference, 
-but not the ownership.
+This unique concepts in Rust secure codes and perform memory management without monitoring memory or calling functions. 
+We introduce implementations of machine learning algorithms in both Java and Rust to assess performances of each memory management system for iterative big data processing tasks.

### 2019-10-06 thesis_template/1_Intro/intro.tex
added RDD caching

@@
 
-\section{Memory Management}
+\section{Memory Management in Rust}
 \label{sec:history}
@@
 but not the ownership.
+
+\section{Spark and RDD Catching}
+\label{sec:history}
+
+Spark is one of the most used big data computing framework. Spark uses Resilient Distributed Datasets (RDDs) which implement in-memory data structures 
+used to cache intermediate data across a set of nodes. This enables multiple rounds of computation on the same data, which is required for machine learning 
+and graph analytics iteratively process the data.
+
+In RDD caching, there are different stages of caching, such as MEMOR\_YONLY and DISK\_ONLY. 
+Currently, for very large data sets, we need to pay attention to garbage collection (GC) and OS page swapping overhead, 
+because these could degrades execution time significantly. Therefore, DISK\_ONLY RDD caching can be better configuration in this case. 
+However, writing and reading intermediate data among desk and memory could have bad effects for execution time, due to need of serialization and deserialization.

### 2019-10-06 thesis_template/1_Intro/intro.tex
added BLAS LAPACK

@@
 However, writing and reading intermediate data among desk and memory could have bad effects for execution time, due to need of serialization and deserialization.
+
+\section{BLAS LAPACK}
+\label{sec:history}
+
+Basic Linear Algebra System (BLAS) is a linear algebra library written in Fortran. This library includes basic linear algebra functionality such as matrix addition 
+and dot product. LAPACK is developed on BLAS and has advanced functionality such as LU decomposition and Singular Value Decomposition (SVD). These library optimize 
+hardware use for linear algebra operation so they are hardware dependant.
+
+Linear algebra library used for Spark is netlib-java, which is a Java wrapper library for Netlib, C API of BLAS and LAPACK. The reason why the developers addressed 
+to use this package is that the BLAS and LAPACK are already bug free and implementing linear algebra library from scratch can usually buggy.
+
+However, the main advantage of use of BLAS and LAPACK is system optimized implementation. So if we implement original Fortran linear algebra library, 
+it cannot perform as well as BLAS and LAPACK.
+And the performance would not be such different from one of implementation in Java or Rust.
+If we want to test only memory management between Rust and Java,
+ it can be enough implementation of linear algebra operation from  pure Java and Rust sacrificing the best performance taking advantage of system optimization.
+My concern is implementing linear algebra operation
+  from scratch can be buggy and cause a lot of problems when we test on machine learning algorithms.

### 2019-10-07 thesis_template/0_Prelim/abs.tex
added matrix operation in Spark

@@
 
-Abstract 
 Many of popular open source cluster computing frameworks for large scale data analysis, such as Hadoop and Spark, 

### 2019-10-07 thesis_template/1_Intro/intro.tex
added matrix operation in Spark

@@
   from scratch can be buggy and cause a lot of problems when we test on machine learning algorithms.
+
+\section{Matrix Computation and Optimization in Apache Spark}
+\label{sec:history}
+
+Matrix operation is a fundamental part of machine learning. Apache Spark provides implementation for distributed and local matrix operation. 
+To translate single-node algorithms to run on a distributed cluster, Spark addresses separating matrix operations from vector operations and run matrix operations on the cluster, 
+while keeping vector operations local to the driver.
+
+Spark changes its behavior for matrix operations depending on the type of operations and shape of matrices.
+For example, Singular Value Decomposition (SVD) for a square matrix is performed in distributed cluster,
+but SVD for a tall and skinny matrix is on a driver node. This is because the matrix derived among the computation of SVD for tall and skinny matrix is usually small so that it can fit to single node.
+
+Spark uses ARPACK to solve square SVD.
+ARPACK is a collection of Fortran77 designed to solve eigenvalue problems.
+ARPACK is based upon an algorithmic variant of the Arnoldi process called the Implicitly Restarted Arnoldi Method (IRAM).
+When the matrix A is symmetric it reduces to a variant of the Lanczos process called the Implicitly Restarted Lanczos Method (IRLM). 
+ARPACK calculate matrix multiplication by performing matrix-vector multiplication.
+So we can distribute matrix-vector multiplies, and exploit the computational resources available in the entire cluster.
+The other method to distribute matrix operations is Spark TFOCS. Spark TFOCS supports several optimization methods.
+
+To allow full use of hardware-specific linear algebraic operations on single node, Spark uses the BLAS (Basic Linear Algebra Systems) interface with relevant libraries for CPU and GPU acceleration. 
+Native libraries can be used in Scala are ones with C BLAS interface or wrapper and called through the Java native interface implemented in Netlib-java library and wrapped by the Scala library called Breeze.
+Following is some of the implementation of BLAS.
+
+\begin{itemize}
+    \item f2jblas -  Java implementation of Fortran BLAS
+    \item OpenBLAS - open source CPU-optimized C implementation of BLAS
+    \item MKL - CPU-optimized C and Fortran implementation of BLAS by Intel
+\end{itemize}
+
+These have different implementation and they perform differently for the type of operation and matrices shape. 
+In Sark, OpenBlas is the default method of choice. BLAS interface is made specifically for dense linear algebra. 
+Then, there are few libraries that efficiently handle sparse matrix operations.

### 2019-10-17 thesis_template/1_Intro/intro.tex
changed latex stracture related work is added

--- 2019-10-06 thesis_template/1_Intro/intro.tex
@@
 machine learning algorithms in both Java and Rust to assess performances of each memory management system for iterative big data processing tasks.
-
-\section{Memory Management in Rust}
-\label{sec:history}
-
-Each value in Rust has a variable called its owner. This owner has information about the value, such as location in memory, 
-length and capacity of the value. This owner can live on the scope associated with its life time. When the owner goes out of it’s scope, 
-the value will be dropped. When a value already assigned to a variable is assigned to another variable, if the value is allocated 
-on heap its information is copied to the new owner and drop the old owner disabling old variable. Similar thing happens when we pass variable to parameter of function. 
-After passing a variable to a parameter, all the information is copied to new owner through the parameter and old owner is no longer available. 
-The new owner can only live in the function and the object will be dropped. In this case, we have no longer access to the object after the function. 
-To avoid this, Rust has a concept called borrowing. We can set reference for the parameter of function and use the reference for operation within function and drop the reference, 
-but not the ownership.
-
-\section{Spark and RDD Catching}
-\label{sec:history}
-
-Spark is one of the most used big data computing framework. Spark uses Resilient Distributed Datasets (RDDs) which implement in-memory data structures 
-used to cache intermediate data across a set of nodes. This enables multiple rounds of computation on the same data, which is required for machine learning 
-and graph analytics iteratively process the data.
-
-In RDD caching, there are different stages of caching, such as MEMOR\_YONLY and DISK\_ONLY. 
-Currently, for very large data sets, we need to pay attention to garbage collection (GC) and OS page swapping overhead, 
-because these could degrades execution time significantly. Therefore, DISK\_ONLY RDD caching can be better configuration in this case. 
-However, writing and reading intermediate data among desk and memory could have bad effects for execution time, due to need of serialization and deserialization.

### 2019-10-17 thesis_template/2_RelatedWork/relatedWork.tex
changed latex stracture related work is added

\chapter{Related Work}
\label{chapter:relatedwork}
\thispagestyle{myheadings}

\section{Memory Management in Rust}
\label{sec:history}

Each value in Rust has a variable called its owner. This owner has information about the value, such as location in memory, 
length and capacity of the value. This owner can live on the scope associated with its life time. When the owner goes out of it’s scope, 
the value will be dropped. When a value already assigned to a variable is assigned to another variable, if the value is allocated 
on heap its information is copied to the new owner and drop the old owner disabling old variable. Similar thing happens when we pass variable to parameter of function. 
After passing a variable to a parameter, all the information is copied to new owner through the parameter and old owner is no longer available. 
The new owner can only live in the function and the object will be dropped. In this case, we have no longer access to the object after the function. 
To avoid this, Rust has a concept called borrowing. We can set reference for the parameter of function and use the reference for operation within function and drop the reference, 
but not the ownership.

\section{Spark and RDD Catching}
\label{sec:history}

Spark is one of the most used big data computing framework. Spark uses Resilient Distributed Datasets (RDDs) which implement in-memory data structures 
used to cache intermediate data across a set of nodes. This enables multiple rounds of computation on the same data, which is required for machine learning 
and graph analytics iteratively process the data.

In RDD caching, there are different stages of caching, such as MEMOR\_YONLY and DISK\_ONLY. 
Currently, for very large data sets, we need to pay attention to garbage collection (GC) and OS page swapping overhead, 
because these could degrades execution time significantly. Therefore, DISK\_ONLY RDD caching can be better configuration in this case. 
However, writing and reading intermediate data among desk and memory could have bad effects for execution time, due to need of serialization and deserialization.

\section{BLAS LAPACK}
\label{sec:history}

Basic Linear Algebra Subprograms (BLAS) are standard building blocks for basic vector and matrix operations. There are 3 levels of operation. The level 1 BLAS performs scalar, 
vector and vector-vector operations, the level 2 BLAS performs matrix-vector operation, and the level 3 BLAS performs matrix-matrix operation.

LAPACK is developed on BLAS and has advanced functionalities such as LU decomposition and Singular Value Decomposition (SVD). Dense and banded matrices are handled, but not general 
sparse matrices. The initial motivation of development of LAPACK was to make the widely used EISPACK and LINPACK libraries run efficiently on shared-memory vector and parallel processors. 
LINPACK and EISPACK are inefficient because their memory access patterns disregard the multi-layered memory hierarchies of the machines, thereby spending too much time moving data. 
LAPACK addresses this problem by recognizing the algorithms to use block matrix operations, such as matrix multiplication, in the innermost loops. These block operations can be optimized for each architecture to account for the memory hierarchy, 
and so provide a portable way to achieve high efficiency on diverse modern machines. However, LAPACK requires that highly optimized block matrix operations be already implemented on each machine.

The original BLAS and LAPACK are written in Fortran90. Linear algebra library used for Spark is netlib-java, which is a Java wrapper library for Netlib, C API of BLAS and LAPACK. 
The reason why the developers addressed to use this package is that the BLAS and LAPACK are already bug free and implementing linear algebra library from scratch can usually buggy.

However, the main advantage of use of BLAS and LAPACK is system optimized implementation. So if we implement original Fortran linear algebra library, it cannot perform as well as BLAS and LAPACK. 
And the performance would not be such different from one of implementation in Java or Rust.  If we want to test only memory management between Rust and Java, 
it can be enough implementation of linear algebra operation from  pure Java and Rust sacrificing the best performance taking advantage of system optimization. 
My concern is implementing linear algebra operation from scratch can be buggy and cause a lot of problems when we test on machine learning algorithms.

\section{Matrix Computation and Optimization in Apache Spark}
\label{sec:history}

Matrix operation is a fundamental part of machine learning. Apache Spark provides implementation for distributed and local matrix operation. 
To translate single-node algorithms to run on a distributed cluster, Spark addresses separating matrix operations from vector operations and run matrix operations on the cluster, 
while keeping vector operations local to the driver.

Spark changes its behavior for matrix operations depending on the type of operations and shape of matrices. For example, Singular Value Decomposition (SVD) for a square matrix is performed in distributed cluster, 
but SVD for a tall and skinny matrix is on a driver node. This is because the matrix derived among the computation of SVD for tall and skinny matrix is usually small so that it can fit to single node.

Spark uses ARPACK to solve square SVD. ARPACK is a collection of Fortran77 designed to solve eigenvalue problems. ARPACK is based upon an algorithmic variant of the Arnoldi process called the Implicitly Restarted Arnoldi Method (IRAM). 
When the matrix A is symmetric it reduces to a variant of the Lanczos process called the Implicitly Restarted Lanczos Method (IRLM). 
ARPACK calculate matrix multiplication by performing matrix-vector multiplication. So we can distribute matrix-vector multiplies, and exploit the computational resources available in the entire cluster. 
The other method to distribute matrix operations is Spark TFOCS. Spark TFOCS supports several optimization methods.

To allow full use of hardware-specific linear algebraic operations on single node, Spark uses the BLAS (Basic Linear Algebra Systems) interface with relevant libraries for CPU and GPU acceleration. 
Native libraries can be used in Scala are ones with C BLAS interface or wrapper and called through the Java native interface implemented in Netlib-java library and wrapped by the Scala library called Breeze. 
Following is some of the implementation of BLAS.

\begin{itemize}
    \item f2jblas -  Java implementation of Fortran BLAS
    \item OpenBLAS - open source CPU-optimized C implementation of BLAS
    \item MKL - CPU-optimized C and Fortran implementation of BLAS by Intel
\end{itemize}

These have different implementation and they perform differently for the type of operation and matrices shape. 
In Sark, OpenBlas is the default method of choice. BLAS interface is made specifically for dense linear algebra. 
Then, there are few libraries that efficiently handle sparse matrix operations.

### 2019-10-17 thesis_template/3_Body/body.tex
changed latex stracture related work is added

\chapter{Body of my thesis}
\label{chapter:body}
\thispagestyle{myheadings}

% set this to the location of the figures for this chapter. it may
% also want to be ../Figures/3_Body/ or something. make sure that
% it has a trailing directory separator (i.e., '/')!
\graphicspath{{3_Body/Figures/}}

\section{Some results}
\label{sec:results}

Here goes all the important stuff, likely with a lot of graphics like this:

\begin{figure}[htb]
  \begin{minipage}[t]{0.49\linewidth}\centering
    \includegraphics[width=7cm]{figure_sampling_view1.eps}
    \medskip
    \centerline{(a)}
  \end{minipage}\hfill
  \begin{minipage}[t]{0.49\linewidth}\centering
    \includegraphics[width=7cm]{figure_sampling_view2.eps}
    \medskip
    \centerline{(b)}
  \end{minipage}
  \caption{Assignment of single-view intensities to RGB components: (a) view
    \#1; and (b) view \#2. }
  \label{fig:Sampling}
\end{figure}

You will also be using a lot of citations. Here is the format required in the dissertation: \cite{lamport1985:latex},\cite{Debr01}.

In all likelihood, you will need to insert tables. See one example on the next page.
\clearpage

\begin{table}[h]
	\caption{Absolute disparity error per pixel for the test data from
		Fig.~\ref{fig:Sampling} and different parameter values. In each experiment one
		parameter is adjusted while other parameters are unchanged.} 
	\centering
	\begin{minipage}[b]{0.30\linewidth}
		\centerline{$\eta=6000$, $\mu=2000$}\smallskip
		\centering
		\begin{tabular}{ccc}
			\hline
			$K$ & $u_1$ & $u_2$\\
			\hline
			3   & 0.52 &0.46\\
			7   & 0.47 &0.43\\
			10  & 0.35 &0.36\\
			12  & 0.37 &0.36\\
			\hline
		\end{tabular}
	\end{minipage}
	%
	\begin{minipage}[b]{0.34\linewidth}
		\centerline{$K=10$, $\mu=2000$}\smallskip
		\centering
		\begin{tabular}{ccc}
			\hline
			$\eta$ & $u_1$ & $u_2$\\
			\hline
			1000&0.54& 0.45\\
			3000&0.43& 0.40\\
			6000&0.35& 0.36\\
			9000&0.37& 0.37\\
			\hline
		\end{tabular}
	\end{minipage}
	%
	\begin{minipage}[b]{0.32\linewidth}
		\centerline{$K=10$, $\eta=6000$}\smallskip
		\centering
		\begin{tabular}{ccc}
			\hline
			$\mu$ & $u_1$ & $u_2$\\
			\hline
			100 &1.00&1.16\\
			1000&0.53&0.47\\
			2000&0.35&0.36\\
			3000&0.44&0.43\\
			\hline
		\end{tabular}
	\end{minipage}
	%
	\label{tab:Parameters}
\end{table}

Of course, there must be a Table of Contents at the beginning of the thesis.

### 2019-10-17 thesis_template/4_Conclusion/conclusion.tex
changed latex stracture related work is added

\chapter{Conclusions}
\label{chapter:Conclusions}
\thispagestyle{myheadings}

% set this to the location of the figures for this chapter. it may
% also want to be ../Figures/3_Body/ or something. make sure that
% it has a trailing directory separator (i.e., '/')!
\graphicspath{{3_Conclusion/Figures/}}

\section{Summary of the thesis}

Time to get philosophical and wordy.

IMPORTANT: In the references at the end of thesis, all journal names must be
spelled out in full, except for standard abbreviations like IEEE, ACM, SPIE,
INFOCOM, ...

### 2019-10-18 thesis_template/2_RelatedWork/relatedWork.tex
added how to build CBLAS

@@
 \thispagestyle{myheadings}
+
+\graphicspath{{2_RelatedWork/Figures/}}
 
@@
 
+ARPACK is also a collection of linear algebra subroutines which is designed to compute a few eigenvalues and corresponding eigenvectors from large scale matrix. 
+ARPACK is based upon an algorithmic variant of the Arnoldi process called the Implicitly Restarted Arnoldi Method (IRAM). 
+When the matrix is symmetric it reduces to a variant of the Lanczos process called the Implicitly Restarted Lanczos Method(IRLM).
+The Arnoldi process only interacts with the matrix via matrix-vector multiplies.
+Therefore, this method can be applied to distributed matrix operations required in big data analysis.
+
 The original BLAS and LAPACK are written in Fortran90. Linear algebra library used for Spark is netlib-java, which is a Java wrapper library for Netlib, C API of BLAS and LAPACK. 
@@
 it can be enough implementation of linear algebra operation from  pure Java and Rust sacrificing the best performance taking advantage of system optimization.
-My concern is implementing linear algebra operation from scratch can be buggy and cause a lot of problems when we test on machine learning algorithms.
+
+\section{Netlib-Java}
+\label{sec:history}
+
+Netlib-java is a Java wrapper of BLAS, LAPACK, and ARPACK. Netlib-java choose  implementation of linear algebra depending on installation of the libraries. 
+First, if we have installed machine optimised system libraries, such as Intel MKL and OpenBLAS, netlib-java will use these as the implementation to use. 
+Next, it try to load netlib references which netlib-java use CBLAS and LAPCKE interface to perform BLAS and LAPACK native call. 
+The last option is to use f2j which is intended to translate the BLAS and LAPACK libraries from their Fortran77 reference source code to Java class files, 
+instead of calling native libraries by using Java Native Interface (JNI).
+
+We can use JNI to call native libraries from Java. The JNI is a native programming interface which allows Java code that runs inside a Java Virtual Machine (VM) 
+to interoperate with applications and libraries written in other programming languages.
+
+\section{Create Java interface of CBLAS with JNI}
+\label{sec:history}
+\begin{enumerate}
+    \item Download BLAS and build using make file. In the figure2.1, the built file is libblas.a and the header file is blas.h.
+    \item Download CBLAS and build using make file (I am not sure whether we should build archive file or shared library).
+In figure, the build file would be libcblas.a or libcblas.dylib and header file is cblas.h.
+    \item Create java file which will be the Java interface of CBLAS.
+    \item Compile java file with -h header flag to create class file (CBLASJ.class) and header file (CBLASJ.h).
+    \begin{lstlisting}[language=bash]
+        $ javac -h . CBLASJ.java
+    \end{lstlisting}
+    \item Create C file (CBLASJ.c) which will bind Java interface and CBLAS library. And compile it with JNI to create object file (CBLASJ.o).
+    \begin{lstlisting}[language=bash]
+        $ gcc -c -fPIC -I${JAVA_HOME}/include -I${JAVA_HOME}/include/darwin CBLASJ.c
+    \end{lstlisting}
+    \item Compile shared library linking library (libcblas.a or libcblas.dylib) object file (CBLASJ.o).
+    \begin{lstlisting}[language=bash]
+        $ gcc -o libcblas.dylib (or libcblas.a) CBLASJ.o 
+    \end{lstlisting}
+\end{enumerate}
+
+\begin{figure}[htb]
+    \includegraphics[width=15cm]{cblas_with_jni.eps}
+    \caption{Integration of Native Methods }
+    \label{fig:Sampling}
+\end{figure}
 

### 2019-11-15 thesis_template/2_RelatedWork/relatedWork.tex
changed readme
changed character size
added memory management part

@@
 Then, there are few libraries that efficiently handle sparse matrix operations.
+
+\section{Memory Management of Java}
+\label{sec:history}
+
+Garbage Collection (GC) is a Java memory management method performed by JVM. 
+GC tracks the state of objects on Java heap and triggers removal of unreferenced objects from memory.
+
+The Java heap structure is shown in Figure. It can be separated into three main parts where store objects for each corresponding generation: 
+permanent generation, young generation, and old generation. The region for permanent generation stores metadata required by JVM to describe 
+class and method used in application which will be permanently lived on the region of memory.
+
+The young generation of Java heap contains new objects allocated and aged. When the young generation fills up, this triggers minor GC. 
+All of unreferenced objects will be removed from Java heap and remained objects will be aged and eventually promoted to the old generation.
+
+The old generation is used to store long survived objects. Typically, a threshold is set for young generation object and when the age is met, 
+the object will be moved to the old generation. Eventually, the old generation object also needs to be removed when the object is unreferenced. 
+This is called major GC. The process of generational GC is shown in Figure.
+
+\begin{figure}[htb]
+    \includegraphics[width=15cm]{java_heap.eps}
+    \caption{Java Heap Structure}
+    \label{fig:Sampling}
+\end{figure}
+
+\begin{figure}[htb]
+    \includegraphics[width=15cm]{java_gc.eps}
+    \caption{Java Garbage Collection}
+    \label{fig:Sampling}
+\end{figure}
+
+\section{Memory Management of each Linear Algebra Library}
+\label{sec:history}
+
+The pure Java linear algebra library, such as La4j, EJML, and Apache Common Math, 
+use normal GC performed by JVM to manage memory. This is because the implementation of these libraries are in purely Java.
+
+Netlib-java, Jblas or other simple Java wrapper of BLAS, LAPACK, and ARPACK with Java Native Interface (JNI) use normal GC as well. 
+This is because the native code deals with Java array by obtaining a reference to it. After the operation, 
+the native method releases the reference to the Java array with or without returning new Java array or Java primitive type object.
+
+ND4J has two types of  its own memory management methods, GC to pointer of off-heap NDArray, and MemoryWorkspaces. 
+ND4J used off-heap memory to store NDArrats, to provide better performance while working with NDArrays from vative code such as BLAS and CUDA libraries. 
+Off-heap means that the memory is allocated outside of the Java heap so that it is not managed by the JVM’s GC. NDArray itself is not tracked by JVM, 
+but its pointer is. The Java heap stores pointer to NDArray on off-heap. When a pointer is dereferenced, this pointer can be a target of JVM’s GC and when it is collected, 
+the corresponding NDArray will be deallocated. When using MemoryWorkspaces, NDArray lives only within specific workspace scope. 
+When NDArray leaves the workspace scope, the memory is deallocated unless explicitly calling method to copy the NDArray out of the scope.

### 2019-11-25 thesis_template/2_RelatedWork/relatedWork.tex
documented experiment

@@
 When NDArray leaves the workspace scope, the memory is deallocated unless explicitly calling method to copy the NDArray out of the scope.
+
+\section{Experiment of Memory Allocation}
+\label{sec:history}
+This experiment is to test how static and dynamic memory allocation of Java and Rust behave. For the assessment, Element addition to ArrayList in the case of Java and Vector in the case of Rust 
+is emploied here. These data stractures are resizable and we have control to set initial size. There are two parameters; initial size and final size of ArrayList of Vector after additions of element. 
+We are interested in the impact to memory allocation by initial allocation and expantion to runtime.
+
+First, an ArrayList and an Vector are created with specified initial size.
+Then, in a loop, a element is added for each iteration until the size of the ArrayList or Vector get the specified final size.
+When each data structure has a different resizing strategy. When an ArrayList hits current limit of its size and expands the limit, it doubles the current size.  
+While Vector does not have specific strategy for its resizing, the expantions of size of both ArrayList and Vector might affect the digradation of runtime performance.
+
+To perform benchmarks, we use Java Microbenchamrk Hardness (JMH) for Java and Criterion for Rust. The benchmark time is calculated mean from several iterarions. 
+We warm up before the execution. The results are shown in Figures
+
+\begin{figure}[htb]
+    \includegraphics[width=15cm]{java_arraylist.eps}
+    \caption{Memory allocation of ArrayList}
+    \label{fig:Sampling}
+\end{figure}
+
+\begin{figure}[htb]
+    \includegraphics[width=15cm]{rust_vector.eps}
+    \caption{Memory allocation of ArrayList}
+    \label{fig:Sampling}
+\end{figure}

### 2019-11-25 thesis_template/2_RelatedWork/relatedWork.tex
documented

@@
 This experiment is to test how static and dynamic memory allocation of Java and Rust behave. For the assessment, Element addition to ArrayList in the case of Java and Vector in the case of Rust 
-is emploied here. These data stractures are resizable and we have control to set initial size. There are two parameters; initial size and final size of ArrayList of Vector after additions of element. 
+is emploied here.
+These data stractures are resizable and we have control to set initial size.
+There are two parameters; initial size of ArrayList or Vector and thier final size after additions of elements.
 We are interested in the impact to memory allocation by initial allocation and expantion to runtime.
@@
 Then, in a loop, a element is added for each iteration until the size of the ArrayList or Vector get the specified final size.
-When each data structure has a different resizing strategy. When an ArrayList hits current limit of its size and expands the limit, it doubles the current size.  
+Each data structure has a different resizing strategy. When an ArrayList hits current limit of its size and expands the limit, it doubles the current size.  
 While Vector does not have specific strategy for its resizing, the expantions of size of both ArrayList and Vector might affect the digradation of runtime performance.
@@
 To perform benchmarks, we use Java Microbenchamrk Hardness (JMH) for Java and Criterion for Rust. The benchmark time is calculated mean from several iterarions. 
-We warm up before the execution. The results are shown in Figures
+We warm up before the execution. The parameters are set in combination of initial size, 10, 100, 1000, and 10000 and final size, 9, 99, 999, 9999. 
+The results are shown in Figure 2-4 and 2-5.
+
+Discussions here are separated to two cases: when initial size is set bigger than final size and when final size is set bigger than initial size. 
+For ArrayList in Java, it shows performance significant degradation when the initial size is bigger than final size. When we create ArrayList with intial size of 1000 and add 99 elements 
+to the ArrayList, the the average execution time is 1125 ns. However, the average excution time when we create ArrayList with intial size of 100 and add 99 elements is 623 ns. 
+This degration is caused by the cost of initializing the large array.
+On the other hand, Rust Vector does not have significant cost for the initialization of size compared to the cost of addition of elements.
+In the case of Vector with initial size of 1000 and add 99 elements to the Vector, the average excution is 320 ns. In the case of the initial size of 100 and 99 elements additions, 
+the average excution is 279 ns. This is such small degradation compared to element addition in Vector.
+
+In ArrayList when the initial size is smaller than the final size, there can be degradation in performance. When its initial size and final size are set 100 and 999 respectively, 
+the average execution time is 10884 ns. However when its initial size and final size are set 1000 and 999 respectively, the average execution time is 4250 ns. 
+This result shows the degradation of in performance caused by the copy of existing elements into newly allocated array whose size is double of the last array.
+
+This characteristic can be seen in the case of Vector in Rust. Vector with initial size 100 and final size 999 performs the average excution time 3514 ns, 
+but one with initial size 1000 and final size 999 performs 2723 ns. When the Vector reachs its capacity, it allocates a larger buffer and copies the present elements to it.
+This cost results in the degradation of the average excution time.
 
@@
     \includegraphics[width=15cm]{java_arraylist.eps}
-    \caption{Memory allocation of ArrayList}
+    \caption{Memory allocation of ArrayList in Java}
     \label{fig:Sampling}
@@
     \includegraphics[width=15cm]{rust_vector.eps}
-    \caption{Memory allocation of ArrayList}
+    \caption{Memory allocation of Vector in Rust}
     \label{fig:Sampling}

### 2020-01-03 thesis_template/2_RelatedWork/relatedWork.tex
experimented
documented

@@
 \end{figure}
+
+\section{Experiment of Memory Allocation for Different Element Type.}
+\label{sec:history}
+This experiment is to test how static and dynamic memory allocation of Java and Rust behave. For the assessment, Element addition to ArrayList in the case of Java and Vector in the case of Rust 
+is emploied here.
+These data stractures are resizable and we have control to set initial size.
+There are two parameters; initial size of ArrayList or Vector and thier final size after additions of elements.
+We are interested in the impact to runtime performance by initializing memory allocation and dynamicaly allocating memory space.
+
+First, an ArrayList and an Vector are created with specified initial size.
+Then, in a loop, a element is added for each iteration until the size of the ArrayList or Vector get the specified final size.
+Each data structure has a different resizing strategy. When an ArrayList hits current limit of its size and expands the limit, it doubles the current size.  
+While Vector does not have specific strategy for its resizing, the expantions of size of both ArrayList and Vector might affect the digradation of runtime performance.
+
+Second, four types of element are used for elements addition to each data structure: integer, array of charactors, string, and Customer object. 
+Assamption is that there would be different behavior between element additions of dynamically resizable and static size objects. 
+Customer object has three fields. These fields are total order, weight of order, and zip code whose types are integer (i32 in rust), double (f32 in rust), and string respectively.
+Figure 2-6 and 2-7 are representations of customer objects in Java and Rust.
+
+Figure 2-8 and 2-9 represent the result of the experiments. For both data structures, integer elements addition shows the fastest runtime among all object types. 
+This is because the compilers know each integer need 4 bytes to be stored in memory so that the space for memory that should be allocated is easily inspected. 
+The elements addition of strings and array of character behave similally among each languages.
+These two types of elements addition perform the similar speed and significantly slower than integer addition.
+Customer object addition is the slowest in Java and seems to have little impact of initialization of size of ArrayList.
+However, in Rust the addition of Customer object is the second fastest among all element typs.
+
+\begin{figure}[htb]
+    \begin{lstlisting}
+        class Customer {
+            int totalOrder;
+            double weightOrder;
+            String zipCode;
+        }
+    \end{lstlisting}
+    \caption{Representation of Customer object in Java.}
+    \label{fig:Sampling}    
+\end{figure}
+
+\begin{figure}[htb]
+    \begin{lstlisting}
+        struct Customer {
+            total_order: i32,
+            weight_order: f32,
+            zip_code: String,
+        }
+    \end{lstlisting}
+    \caption{Representation of Customer object in Rust.}
+    \label{fig:Sampling}
+\end{figure}
+
+\begin{figure}[htb]
+    \includegraphics[width=15cm]{java_arraylist_log.eps}
+    \caption{Memory allocation of Java ArrayList}
+    \label{fig:Sampling}
+\end{figure}
+
+\begin{figure}[htb]
+    \includegraphics[width=15cm]{rust_vector_log.eps}
+    \caption{Memory allocation of Rust Vector}
+    \label{fig:Sampling}
+\end{figure}

### 2020-01-17 thesis_template/2_RelatedWork/relatedWork.tex
added

@@
 
-Figure 2-8 and 2-9 represent the result of the experiments. For both data structures, integer elements addition shows the fastest runtime among all object types. 
+Figure 2-10, 2-11, 2-12, and 2-13 represent the result of the experiments. For both data structures, integer elements addition shows the fastest runtime among all object types. 
 This is because the compilers know each integer need 4 bytes to be stored in memory so that the space for memory that should be allocated is easily inspected. 
+For the same reason, the initialization of data structures whose elements are integers alaways improves runtim performance.
+
 The elements addition of strings and array of character behave similally among each languages.
 These two types of elements addition perform the similar speed and significantly slower than integer addition.
-Customer object addition is the slowest in Java and seems to have little impact of initialization of size of ArrayList.
-However, in Rust the addition of Customer object is the second fastest among all element typs.
+Customer object addition is the slowest in Java. However, in Rust the addition of Customer object is the second fastest among all element typs.
+The impacts of initialization of Java ArrayList vary among elemet types. On the other hand, the initailization Rust Vector always improves runtime performance for any of 4 types of elements addition.
 
@@
 \end{figure}
+
+\begin{figure}[htb]
+    \includegraphics[width=15cm]{java_arraylist_difference.eps}
+    \caption{Difference of Memory allocation of Java ArrayList between Non-initialization and Initialization}
+    \label{fig:Sampling}
+\end{figure}
+
+\begin{figure}[htb]
+    \includegraphics[width=15cm]{rust_arraylist_difference.eps}
+    \caption{Difference of Memory allocation of Rust Vector between Non-initialization and Initialization}
+    \label{fig:Sampling}
+\end{figure}

### 2020-01-17 project/k_means_java/src/main/java/Filter.java

@@ -1,4 +1,4 @@
-package PACKAGE_NAME;
-
 public interface Filter {
+    boolean get();
+    void set();
 }

### 2020-01-17 project/k_means_java/src/main/java/FilterMatrix.java

@@ -1,13 +1,13 @@
-public class Filter {
+public class FilterMatrix {
     int numRows;
     int numColumns;
     boolean[] data;
-    public Filter(int numRows, int numColumns) {
+    public FilterMatrix(int numRows, int numColumns) {
         this.numRows = numRows;
         this.numColumns = numColumns;
         this.data = new boolean[numRows * numColumns];
     }
-    public Filter(boolean[][] arr) {
+    public FilterMatrix(boolean[][] arr) {
         this.numRows = arr[0].length;
         this.numColumns = arr.length;
         boolean[] data = new boolean[numRows * numColumns];

### 2020-01-17 project/k_means_java/src/main/java/FuncInterface.java

@@ -1,4 +1,3 @@
-package PACKAGE_NAME;
-
 public interface FuncInterface {
+    boolean condition(int a, int b);
 }

### 2020-01-17 project/k_means_java/src/main/java/Kmeans.java

@@ -1,4 +1,126 @@
-package PACKAGE_NAME;
+import no.uib.cipr.matrix.*;
+import no.uib.cipr.matrix.Vector;
+
+import java.util.*;
+import java.util.function.Supplier;
 
 public class Kmeans {
+    int nCluster;
+    int maxIter;
+    int randomState;
+
+    public Kmeans(int nCluster, int maxIter, int randomState) {
+        this.nCluster = nCluster;
+        this.maxIter = maxIter;
+        this.randomState = randomState;
+    }
+
+    private static int[] getRandomIntegersRange(int min, int max, int size) {
+
+        if (min >= max) {
+            throw new IllegalArgumentException("max must be greater than min");
+        }
+
+        Random r = new Random();
+        Set<Integer> generated = new HashSet<Integer>();
+        while (size < generated.size()) {
+            int element = r.nextInt((max - min) + 1) + min;
+            generated.add(element);
+        }
+        int[] res = new int[size];
+        int i = 0;
+        for (int e : generated) {
+            res[i] = e;
+            i++;
+        }
+        return res;
+    }
+
+    private Matrix initializeCentroid(DenseMatrix X) {
+        int[] randomIdx = getRandomIntegersRange(0, X.numColumns(), nCluster);
+        Matrix centroids = Matrices.getSubMatrix(X, randomIdx, Matrices.index(0, X.numColumns()));
+        return centroids;
+    }
+
+    private DenseMatrix computeCentroids(DenseMatrix X, DenseVector labels) {
+        int numColumns = X.numColumns();
+
+        double[] contents = new double[nCluster * numColumns]
+
+        for (int k = 0; k < nCluster; k++) {
+            FilterVector filter = getFilterByCondition(labels, k);
+            DenseMatrix filtered = sliceByFilter(X, filter);
+            DenseVector mean = mean(X, 1);
+            for (int c = 0; c < numColumns; c++) {
+                contents[k + c* nCluster] = mean.getData()[c];
+            }
+        }
+
+        DenseMatrix res = new DenseMatrix(nCluster, numColumns, contents, true);
+        return res;
+    }
+
+    public DenseVector sliceRow(DenseMatrix X, int row) {
+        double[] content =  X.getData();
+        int numRows = X.numRows();
+        int numColumns = X.numColumns();
+        double[] arr = new double[numColumns];
+        for (int c = 0; c < numColumns; c++) {
+            arr[c] = content[row + c * numRows];
+        }
+        DenseVector res = new DenseVector(arr, true);
[…]

### 2020-01-17 project/playground/src/main.rs

@@ -4,119 +4,52 @@ use std::env;
 use std::time::Instant;
 use std::fs::OpenOptions;
 use std::io::prelude::*;
+use std::ptr;
 
 use rand::{thread_rng, Rng};
 use rand::distributions::Alphanumeric;
 
 fn main() {
+
+    let args: Vec<String> = env::args().collect();
     
-    let v = vector_addition(2, true, 2);
-    println!("{:?}", v);
+    let size: usize = args[1].parse().unwrap();
+    add_to_imutable(size);
+
 }
 
-fn vector_addition(size: usize, initialization: bool, elementtype: i32) {
-    match size {
-        1 => add_to_vector(10, initialization, elementtype), 
-        2 => add_to_vector(100, initialization, elementtype), 
-        3 => add_to_vector(1000, initialization, elementtype), 
-        4 => add_to_vector(10000, initialization, elementtype), 
-        _ => println!("Invalid input!"),
-    }
-}
+fn add_to_imutable(size: usize) {
+    
+    println!("size: {}", size);
+    let start_init = Instant::now();
+    let vector;
+    vector = Vec::with_capacity(size);
+    
 
-fn vector_initialization(size: usize, initialization: bool, ) -> std::vec::Vec<i32> {
-    let mut vector;
-    if initialization {
-        vector = Vec::with_capacity(size);
-    } else {
-        vector = Vec::new();
-    }
-    return vector;
-}
+    let elapsed_init = start_init.elapsed().as_nanos();
 
-
-fn get_elementsVec(size: usize, elementtype: i32) {
-    let mut elements = Vec::new();
-    match elementtype {
-        1 => element_integer(size),
-        2 => element_string(size),
-        3 => elements_charArr(size),
-        4 => elements_object(size),
-        _ => println!("Invalid input!"),
-    }
-}
-
-
-fn element_integer(size: usize) -> std::vec::Vec<i32> {
-    let mut elements = Vec::new();
-    for e in 0..size {
-        elements.push(e as i32);
-    }
-    return elements;
-}
-
-fn element_string(size: usize) -> std::vec::Vec<String> {
-    let mut elements = Vec::new();
+    let mut strings_arr = Vec::with_capacity(size);
     for _i in 0..size {
-        let rand_string: String = thread_rng()
+        let mut rand_string: String = thread_rng()
                             .sample_iter(&Alphanumeric)
                             .take(10)
                             .collect();
[…]

### 2020-01-17 project/rust_memory_alloc_immutable_charArr/run.sh

@@ -1,0 +1,32 @@
+#!/bin/bash
+
+cargo clean
+cargo build --release
+
+for size in 1 2 3 4
+do
+
+
+  rm -rf loging.log
+  echo "datastructure#size#inittime#addtime#totaltime" > loging.log
+
+	for counter in 1 2 3 4 5
+	do
+
+
+
+    # write the first line
+
+
+        echo "Adding $size elements in Run number  $counter "
+
+        # Server experiment
+        time taskset -c 0 cargo run $size $initialization
+        # Loacal experiment
+        #time cargo run $size $initialization
+    
+
+
+	done
+  cat loging.log  >  result/resultRustImmutableCharArr_"$size".txt
+done

### 2020-01-17 project/rust_memory_alloc_immutable_charArr/src/main.rs

@@ -1,0 +1,57 @@
+extern crate rand;
+
+use std::env;
+use std::time::Instant;
+use std::fs::OpenOptions;
+use std::io::prelude::*;
+use std::ptr;
+
+
+fn main() {
+
+    let args: Vec<String> = env::args().collect();
+    
+    let size: usize = args[1].parse().unwrap();
+    add_to_imutable(size);
+
+}
+
+fn add_to_imutable(size: usize) {
+    
+    println!("size: {}", size);
+    let start_init = Instant::now();
+    let vector;
+    vector = Vec::with_capacity(size);
+    
+
+    let elapsed_init = start_init.elapsed().as_nanos();
+
+    let mut src_arr = Vec::with_capacity(size);
+    for _i in 0..size {
+        let char_arr = ['a', 'b', 'c', 'd', 'e', 
+                        'f', 'g', 'h', 'i', 'j'];
+        src_arr.push(char_arr);
+    }
+    
+    let mut dst = vector;
+    let src = &src_arr;
+    let dst_ptr = dst.as_mut_ptr();
+    let src_ptr = src.as_ptr();
+    let start_add = Instant::now();
+    unsafe {
+        ptr::copy_nonoverlapping(src_ptr, dst_ptr, size);
+    }
+
+    let elapsed_add = start_add.elapsed().as_nanos();
+    let elapsed_total = start_init.elapsed().as_nanos();
+
+    let output = format!("[RustVector]#{:?}#{:?}#{:?}#{:?}\n", size, elapsed_init, elapsed_add, elapsed_total);
+
+    let mut file = OpenOptions::new()
+        .append(true)
+        .create(true)
+        .open("loging.log")
+        .unwrap();
+
+    file.write_all(output.as_bytes()).expect("Fail to write file.");    
+}

### 2020-01-17 project/rust_memory_alloc_immutable_integer/run.sh

@@ -1,0 +1,32 @@
+#!/bin/bash
+
+cargo clean
+cargo build --release
+
+for size in 1 2 3 4
+do
+
+
+  rm -rf loging.log
+  echo "datastructure#size#inittime#addtime#totaltime" > loging.log
+
+	for counter in 1 2 3 4 5
+	do
+
+
+
+    # write the first line
+
+
+        echo "Adding $size elements in Run number  $counter "
+
+        # Server experiment
+        time taskset -c 0 cargo run $size $initialization
+        # Loacal experiment
+        # time cargo run $size $initialization
+    
+
+
+	done
+  cat loging.log  >  result/resultRustImmutableInteger_"$size".txt
+done

### 2020-01-17 project/rust_memory_alloc_immutable_integer/src/main.rs

@@ -1,0 +1,57 @@
+extern crate rand;
+
+use std::env;
+use std::time::Instant;
+use std::fs::OpenOptions;
+use std::io::prelude::*;
+use std::ptr;
+
+use rand::{thread_rng, Rng};
+use rand::distributions::Alphanumeric;
+
+fn main() {
+
+    let args: Vec<String> = env::args().collect();
+    
+    let size: usize = args[1].parse().unwrap();
+    add_to_imutable(size);
+
+}
+
+fn add_to_imutable(size: usize) {
+    
+    println!("size: {}", size);
+    let start_init = Instant::now();
+    let vector;
+    vector = Vec::with_capacity(size);
+    
+
+    let elapsed_init = start_init.elapsed().as_nanos();
+
+    let mut src_arr = Vec::with_capacity(size);
+    for i in 0..size {
+        src_arr.push(i);
+    }
+    
+    let mut dst = vector;
+    let src = &src_arr;
+    let dst_ptr = dst.as_mut_ptr();
+    let src_ptr = src.as_ptr();
+    let start_add = Instant::now();
+    unsafe {
+        ptr::copy_nonoverlapping(src_ptr, dst_ptr, size);
+    }
+
+    let elapsed_add = start_add.elapsed().as_nanos();
+    let elapsed_total = start_init.elapsed().as_nanos();
+
+    let output = format!("[RustVector]#{:?}#{:?}#{:?}#{:?}\n", size, elapsed_init, elapsed_add, elapsed_total);
+
+    let mut file = OpenOptions::new()
+        .append(true)
+        .create(true)
+        .open("loging.log")
+        .unwrap();
+
+    file.write_all(output.as_bytes()).expect("Fail to write file.");    
+}

### 2020-01-17 project/rust_memory_alloc_immutable_string/run.sh

@@ -1,0 +1,32 @@
+#!/bin/bash
+
+cargo clean
+cargo build --release
+
+for size in 1 2 3 4
+do
+
+
+  rm -rf loging.log
+  echo "datastructure#size#inittime#addtime#totaltime" > loging.log
+
+	for counter in 1 2 3 4 5
+	do
+
+
+
+    # write the first line
+
+
+        echo "Adding $size elements in Run number  $counter "
+
+        # Server experiment
+        time taskset -c 0 cargo run $size $initialization
+        # Loacal experiment
+        # time cargo run $size $initialization
+    
+
+
+	done
+  cat loging.log  >  result/resultRustImmutableString_"$size".txt
+done

### 2020-01-17 project/rust_memory_alloc_immutable_string/src/main.rs

@@ -1,0 +1,61 @@
+extern crate rand;
+
+use std::env;
+use std::time::Instant;
+use std::fs::OpenOptions;
+use std::io::prelude::*;
+use std::ptr;
+
+use rand::{thread_rng, Rng};
+use rand::distributions::Alphanumeric;
+
+fn main() {
+
+    let args: Vec<String> = env::args().collect();
+    
+    let size: usize = args[1].parse().unwrap();
+    add_to_imutable(size);
+
+}
+
+fn add_to_imutable(size: usize) {
+    
+    println!("size: {}", size);
+    let start_init = Instant::now();
+    let vector;
+    vector = Vec::with_capacity(size);
+    
+
+    let elapsed_init = start_init.elapsed().as_nanos();
+
+    let mut src_arr = Vec::with_capacity(size);
+    for _i in 0..size {
+        let rand_string: String = thread_rng()
+                            .sample_iter(&Alphanumeric)
+                            .take(10)
+                            .collect();
+        src_arr.push(rand_string);    
+    }
+    
+    let mut dst = vector;
+    let src = &src_arr;
+    let dst_ptr = dst.as_mut_ptr();
+    let src_ptr = src.as_ptr();
+    let start_add = Instant::now();
+    unsafe {
+        ptr::copy_nonoverlapping(src_ptr, dst_ptr, size);
+    }
+
+    let elapsed_add = start_add.elapsed().as_nanos();
+    let elapsed_total = start_init.elapsed().as_nanos();
+
+    let output = format!("[RustVector]#{:?}#{:?}#{:?}#{:?}\n", size, elapsed_init, elapsed_add, elapsed_total);
+
+    let mut file = OpenOptions::new()
+        .append(true)
+        .create(true)
+        .open("loging.log")
+        .unwrap();
+
+    file.write_all(output.as_bytes()).expect("Fail to write file.");    
+}

### 2020-01-24 thesis_template/2_RelatedWork/relatedWork.tex

@@
 \end{figure}
+
+\section{Elements Copy and Insertion into Size-initialized Vector in Rust}
+\label{sec:history}
+In this experiment, three methods to insert elements into vector in Rust. One is clone method which is performs bitwise deep copy.
+Another is copy_nonoverlapping function which copies values from source to distination memory region. 
+The other is pushing elements of source to distination vector one by one. Insertions of elements with 4 size are conducted, 1000, 10000, 100000, 1000000 and, 
+their runtime for each

### 2020-01-29 thesis_template/2_RelatedWork/relatedWork.tex
struct experiment

--- 2020-01-17 thesis_template/2_RelatedWork/relatedWork.tex
@@
 \end{figure}
+
+\section{Elements Copy and Insertion into Size-initialized Vector in Rust.}
+\label{sec:history}
+In this experiment, four methods are used to insert elements into vector in Rust. One is clone method which performs bitwise deep copy. 
+Another is clone_from which also performs bitwise deep copy, but copies elements of the vector to distination vector rather than 
+creating new one. We initialize the distination vector with the same size to the number of elements we insert into it. 
+Another is copy_nonoverlapping function which copies values from source to distination memory region. 
+The other is pushing elements of source to distination vector one by one. Insertions of elements with 4 size are conducted 1000000, 1500000, 10000000, 15000000, and, 
+their runtimes for each elements type, integer and String are measured.
+
+The figure shows the result of the experiment. Among the runtime performances of integer insertion for every methods, 
+clone, clone_from, and copy_nonoverlapping method shows the similar performance. However, the pushing the copy of elements one by one has much slower runtime performance 
+compared to the rest. This is because integer elements are allocated contiguously in the memory, so that accessing address of memory by pointer reads some next address. 
+This boosts the copy and insertion of elements.
+
+On the other hand, all of methods show the similar runtime performance in experiment for String object insertion. 
+This is because String object is not stored in contiguous memory region. The vector stores pointer to the object and 
+process need to access around different memory region again and again to deeply copy the object.
+
+\begin{figure}[htb]
+    \includegraphics[width=15cm]{rust_various_insertion.eps}
+    \caption{Runtime of elements copy from one vector and insertion to the other vector.}
+    \label{fig:Sampling}
+\end{figure}
+
+\section{Access time to elements in vector}
+\label{sec:history}
+In this experiment, whether mutability has impacts to operation on the object in terms of runtime performance. 
+According to the experiment, there is no difference on accessing to elements of mutable and immutable vector.
+
+\begin{figure}[htb]
+    \includegraphics[width=15cm]{rust_various_access.eps}
+    \caption{Runtime of elements copy from one vector and insertion to the other vector.}
+    \label{fig:Sampling}
+\end{figure}
+
+\section{Note for next}
+\label{sec:history}
+Complex object of elements copy and insertion among vector is worth to experiment. This can be compared with Java, ¥
+because memory layouts of struct in Rust and class in Java are different. Rust stores fieds in the contiguous memory region. 
+However, Java stores field elements to different region.
+
+Complex object whose fields has reference elemenets insertion to vector can be evaluated. Operation to the fields can be little 
+more expensive because the pointer to the value of the field is not stored in contiguous memory region.
+
+Generic type and static type function can be compared.
+
+To optimise access to String elements of vector, smallstring can be improve the runtime performance. 
+This is because the smallstring optimization enables short length of string on stack as byte array. 
+This string type sets condition where it makes decition where the string is stored on heap or stack as array at certain length.
+
+Comparing operation on reference and owned variable is also interested to examine.
+
+Comparing operation on various smart pointer type. 
+Rc<T> enables value to have multiple owners, but the value should be immutable. Rx<T> is used in case of single thread. 
+When the situation is multi-thread, Arc<T> is used. Arc<T> performs atomic operation, so it is more expensive than Arc<T>. 
+When we need to mutate value of Rc<T>, RefCell<T> can be useful. RefCell<T> allow us to have mutiple mutable reference and immutable
+of reference mutable or immutable variable at the same time. When the mutability consistency is voilented, it terminates program during runtime. 
+That is why RefCell<T> is expensive so that the state of mutable consistency should tracked. 
+As Cell<T>, the value is copied in and out of the Cell<T> instead of getting refrence to it. 
+In addition, Mutex<T> provides intetior mutability across multi-thread.
+
+ Comparison between mutable and immutable tree or graph structure can be checked. 
+ This is because tree structure requires Rc<T> or Week<T> and in addition RefCell<T> to make it mutable.

### 2020-01-29 project/rust_memAlloc_various/src/main.rs

@@ -152,7 +152,7 @@ fn get_vector_string(size: usize) -> Vec<String>{
     for _i in 0..size {
         let rand_string: String = thread_rng()
                             .sample_iter(&Alphanumeric)
-                            .take(dist.sample(&mut thread_rng()))
+                            .take(dist.sample(&mut thread_rng())
                             .collect();
         source.push(rand_string);    
     }
@@ -196,7 +196,9 @@ fn access_integer_test_mutable(distination :&mut Vec<i32>, source: &Vec<i32>) ->
     for i in 0..len {
         true_sum += source[i] as i64;
     }
+
     let correct = (sum == true_sum);
+
     return (elapsed_access, correct);
 }
 
@@ -231,6 +233,7 @@ fn access_string_test_mutable(distination :&mut Vec<String>, source: &Vec<String
     }
 
     let correct = (sum == true_sum);
+
     return (elapsed_access, correct);
 }
 

### 2020-01-29 project/rust_object_ref_own/run.sh

@@ -1,0 +1,28 @@
+#!/bin/bash
+
+cargo clean
+cargo build --release
+for size in 1000000 1500000 10000000 15000000
+do
+    rm -rf loging.log
+    echo "datastructure#size#field#createtime#accesstime#totaltime#count" > loging.log
+
+    for field in 1 2 
+    do
+        
+        for counter in 1 2 3 4 5
+        do
+
+        # write the first line
+
+
+            echo "Adding $size elements in Run number  $counter "
+
+            # Server experiment
+            # time taskset -c 0 cargo run $size $field
+            # Loacal experiment
+            time cargo run $size $method $field
+        done
+    done
+    cat loging.log  >  result/resultRustVarious_"$size".txt
+done

### 2020-01-29 project/rust_object_ref_own/src/main.rs

@@ -1,9 +1,11 @@
 extern crate rand;
+use std::iter;
 use std::env;
 use std::time::Instant;
 use std::io::prelude::*;
 use std::fs::OpenOptions;
-use rand::{thread_rng, Rng};
+use rand::{Rng, thread_rng, SeedableRng};
+use rand::rngs::StdRng;
 use rand::distributions::Alphanumeric;
 use rand::distributions::{Distribution, Uniform};
 
@@ -18,14 +20,17 @@ fn run(field: i32, size: usize) {
     match field {
         1 => run_ex_zip_code(size),
         2 => run_ex_address(size),
+        3 => run_ex_country(size),
         _ => println!("Wrong input!")
     }
 }
 
 fn run_ex_zip_code(size: usize) {
     let start = Instant::now();
-    let addresses = get_address_vector(size);
-    let (elapsed_create, customers) = create_customer_vecor(size, &addresses);
+    let addresses = get_string_vector(size);
+    let zip_codes = get_string_vector(size);
+    let countries = get_string_vector(size);
+    let (elapsed_create, customers) = create_customer_vecor(size, &addresses, zip_codes, &countries);
     let (elapsed_access, count) = access_zip_code(& customers);
     let elapsed_total = start.elapsed().as_nanos();
     write_to_file(size, "own", elapsed_create, elapsed_access, elapsed_total, count);
@@ -33,9 +38,22 @@ fn run_ex_zip_code(size: usize) {
 
 fn run_ex_address(size: usize) {
     let start = Instant::now();
-    let addresses = get_address_vector(size);
-    let (elapsed_create, customers) = create_customer_vecor(size, &addresses);
+    let addresses = get_string_vector(size);
+    let zip_codes = get_string_vector(size);
+    let countries = get_string_vector(size);
+    let (elapsed_create, customers) = create_customer_vecor(size, &addresses, zip_codes, &countries);
     let (elapsed_access, count) = access_address(& customers);
+    let elapsed_total = start.elapsed().as_nanos();
+    write_to_file(size, "reference", elapsed_create, elapsed_access, elapsed_total, count);
+}
+
+fn run_ex_country(size: usize) {
+    let start = Instant::now();
+    let addresses = get_string_vector(size);
+    let zip_codes = get_string_vector(size);
+    let countries = get_string_vector(size);
+    let (elapsed_create, customers) = create_customer_vecor(size, &addresses, zip_codes, &countries);
+    let (elapsed_access, count) = access_country(& customers);
[…]

### 2020-01-31 thesis_template/2_RelatedWork/relatedWork.tex
resolved experiment

@@
 
+\section{Access time to onwned, borrowed, and sliced field of object}
+\label{sec:history}
+In this experiment, differences of access time among to owned, borrowed, and sliced are observed. 
+The figure is representation of a Customer object. Among the experiment, we focus on zip_code, address, country fields. 
+These three fields take differet type of String value. The zip_code field takes owned String variable. 
+The address field takes borrowed String variable. The country field takes slice String variable. 
+The assumption here is that there may be difference of operation time among variable types: ownner, reference, slice.
+
+The result shows that access times to onwer and reference are almost the same, but the one to slice is relatively faster 
+compared to the other two.
+
+\begin{figure}[htb]
+    \begin{lstlisting}
+        struct Customer<'a> {
+            total_order: i32,
+            weight_order: f32,
+            zip_code: String,
+            address: &'a String,
+            country: &'a str
+        }
+    \end{lstlisting}
+    \caption{Representation of Customer object in Rust.}
+    \label{fig:Sampling}
+\end{figure}
+
 \section{Note for next}
@@
 This is because tree structure requires Rc<T> or Week<T> and in addition RefCell<T> to make it mutable.
+
+Design experiment for Trait object and Generic function. 
+We can have Trait object which is pointer to object which imprements its Trait and use the method of Trait object.
+This object has additional information other than just reference to tye original object. 
+This is because Rust needs the type information to dynamically calll the right method of Trait object depending on the type of 
+original object.
+On the other hand, we can have Generic function whose parameter types are Generic types corresponding to Trait. 
+When Rust compiles the code, it emits independent function corresponding to every types that implements the Trains specified in parameter.
+
+Vector of Trait(need to put element into Box) vs Vector of concrete type.

### 2020-02-02 project/boolean_evaluation/src/main/java/Main.java
added description

@@ -1,48 +1,0 @@
-import java.util.HashMap;
-
-public class Main {
-    public static void main(String[] args) {
-
-    }
-
-    public static int countEval(String s, boolean result, HashMap<String, Integer> map) {
-        if (s.length() == 0) return 0;
-        if (s.length() == 1) return stringToBoolean(s) == result ? 1 : 0;
-        if (map.containsKey(result + s)) return map.get(result + s);
-        int ways = 0
-        for (int i = 1; i < s.length(); i+=2) {
-            char operator = s.charAt(i);
-            String left = s.substring(0, i);
-            String right = s.substring(i+1, s.length());
-
-            int leftTrue = countEval(left, true, map);
-            int leftFalse = countEval(left, false, map);
-            int rightTrue = countEval(right, true, map);
-            int rightFalse = countEval(left, false, map);
-            int total = (leftTrue + leftFalse) * (rightTrue * rightFalse);
-            int totalTrue = 0;
-            if (operator == '|') {
-                totalTrue = leftTrue * rightFalse +
-                                leftFalse * rightTrue +
-                                leftTrue * leftTrue;
-            } else if (operator == '&') {
-                totalTrue = leftTrue * rightTrue;
-            } else if (operator == '^') {
-                totalTrue = leftTrue * rightFalse +
-                                leftFalse * rightTrue;
-            }
-
-            int subways = result ? totalTrue : total - totalTrue;
-            ways += subways;
-        }
-        map.put(result + s, ways);
-        return ways;
-    }
-    public static boolean stringToBoolean(String s) {
-        if (s.equals("0")) {
-            return false;
-        } else {
-            return true;
-        }
-    }
-}

### 2020-02-02 project/create_csv/create_run.py

@@ -1,23 +1,0 @@
-from __future__ import print_function
-import sys
-
-if __name__ == "__main__":
-    print(len(sys.argv))
-    if len(sys.argv) != 3:
-        print("Usage: create_run.py min_row max_row", file=sys.stderr)
-        exit(-1)
-
-    min_row = int(sys.argv[1])
-    max_row = int(sys.argv[2])
-    start_num = int(min_row / 1000)
-    end_num = int(max_row / 1000)
-
-    f = open("run.sh", "a")
-    for i in range(start_num, end_num + 1):
-        s = "cargo run ../data/input" + str(i) + ".csv " + str(i * 1000) + " "\
-        + str(i * 1000) + "\n"
-        print(s)
-        f.write(s)
-    
-    f.close()
-

### 2020-02-02 project/create_csv/run.sh

@@ -1,6 +1,0 @@
-cargo run ../data/input5.csv 5000 5000
-cargo run ../data/input6.csv 6000 6000
-cargo run ../data/input7.csv 7000 7000
-cargo run ../data/input8.csv 8000 8000
-cargo run ../data/input9.csv 9000 9000
-cargo run ../data/input10.csv 10000 10000

### 2020-02-02 project/create_csv/src/main.rs

@@ -1,77 +1,0 @@
-extern crate csv;
-#[macro_use]
- extern crate serde_derive;
-
-extern crate ndarray;
-extern crate rand;
-
-
-use std::error::Error;
-
-use csv::Writer;
-
-use ndarray::prelude::*;
-//use ndarray_linalg::Solve;
-use rand::{thread_rng, Rng};
-use rand::distributions::{Standard};
-use std::env;
-
-
-#[derive(Serialize)]
-pub struct Row {
-    values: Vec<f32>,
-}
-
-// path row number and column number on command line arguments ex: cargo run filename 1000 10
-fn main() -> Result<(), Box<Error>>  {
-    let args: Vec<String> = env::args().collect();
-    let row_num = args[2].parse::<i32>()?;
-    let col_num = args[3].parse::<usize>()?;
-    let rng = thread_rng();
-    let mut wtr = Writer::from_path(&args[1])?;
-    for _i in 0..row_num {
-        let x: Vec<f32> = rng.sample_iter(&Standard).take(col_num).collect();
-        wtr.serialize(&x)?;
-    }
-    wtr.flush()?;
-    Ok(())
-}
-// fn to_array(v :&Vec<f32>) {
-//     const v_len: f32 = v.len();
-//     let mut a: [f32; v_len];
-//     for i in 0..v_len {
-//         a[i] = v[i];
-//     }
-//     a
-// }
-
-// fn generate_array() -> [f32] {
-    
-    
-//     let a = to_array(&x);
-//     a
-//}
-
-
-
-// fn main() -> Result<(), Box<Error>>  {
-//     let mut wtr = Writer::from_path("random_raw_num.csv")?;
-//     for _i in 0..1000 {
-//         let t = generate_tuple();
-//         wtr.serialize(&t)?;  
-//     }
-//     wtr.flush()?;
-//     Ok(())
-// }
-// fn to_tuple(v :&Vec<f32>) -> (f32, f32, f32, f32, f32, f32, f32, f32, f32, f32 ) {
-//     let t = (v[0], v[1], v[2], v[3], v[4], v[5], v[6], v[7], v[8], v[9]);
-//     return t;
-// }
-
-// fn generate_tuple() -> (f32, f32, f32, f32, f32, f32, f32, f32, f32, f32) {
-//     let rng = thread_rng();
-//     let x: Vec<f32> = rng.sample_iter(&Standard).take(10).collect();
-//     let t = to_tuple(&x);
-//     return t;
-// }
-

### 2020-02-02 project/java_memory_alloc/src/main/java/allocation/ElementAddition.java

@@ -1,34 +1,0 @@
-package allocation;
-
-import org.apache.log4j.PropertyConfigurator;
-
-public class ElementAddition {
-    public static void main(String[] args) {
-
-        int size = Integer.parseInt(args[0]);
-        boolean initialization = Boolean.parseBoolean(args[1]);
-
-        PropertyConfigurator.configure("log4j.properties");
-        System.gc();
-
-        runExperiments(size, initialization);
-    }
-
-    public static void runExperiments(int size, boolean initialization) {
-        switch (size) {
-            case 1:
-                AddToArrayList.addition(10, initialization);
-                break;
-            case 2:
-                AddToArrayList.addition(100, initialization);
-                break;
-            case 3:
-                AddToArrayList.addition(1000, initialization);
-                break;
-            case 4:
-                AddToArrayList.addition(10000, initialization);
-                break;
-        }
-
-    }
-}

### 2020-02-02 project/jmh-arraylist-allocation-performance-test/src/main/java/com/test/MyBenchmark.java

@@ -1,359 +1,0 @@
-/*
- * Copyright (c) 2014, Oracle America, Inc.
- * All rights reserved.
- *
- * Redistribution and use in source and binary forms, with or without
- * modification, are permitted provided that the following conditions are met:
- *
- *  * Redistributions of source code must retain the above copyright notice,
- *    this list of conditions and the following disclaimer.
- *
- *  * Redistributions in binary form must reproduce the above copyright
- *    notice, this list of conditions and the following disclaimer in the
- *    documentation and/or other materials provided with the distribution.
- *
- *  * Neither the name of Oracle nor the names of its contributors may be used
- *    to endorse or promote products derived from this software without
- *    specific prior written permission.
- *
- * THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS IS"
- * AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
- * IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE
- * ARE DISCLAIMED. IN NO EVENT SHALL THE COPYRIGHT HOLDER OR CONTRIBUTORS BE
- * LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR
- * CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF
- * SUBSTITUTE GOODS OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS
- * INTERRUPTION) HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN
- * CONTRACT, STRICT LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE)
- * ARISING IN ANY WAY OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF
- * THE POSSIBILITY OF SUCH DAMAGE.
- */
-
-package com.test;
-
-import org.openjdk.jmh.annotations.*;
-
-import java.util.*;
-import java.util.concurrent.TimeUnit;
-
-public class MyBenchmark {
-
-    @Benchmark
-    @BenchmarkMode(Mode.AverageTime)
[…]

### 2020-02-02 project/la4jproject/run.sh

@@ -1,1 +1,0 @@
- mvn compile exec:java -Dexec.mainClass="Main" -Dexec.args="input5.csv"

### 2020-02-02 project/la4jproject/src/main/java/Main.java

@@ -1,69 +1,0 @@
-import java.io.BufferedReader;
-import java.io.FileReader;
-import java.io.IOException;
-import java.util.ArrayList;
-import java.util.List;
-import org.la4j.Matrix;
-import org.la4j.matrix.dense.Basic2DMatrix;
-
-public class Main {
-  public static void main(String[] args) {
-
-    String file = "../data/";
-
-    //
-    long loadStart = System.currentTimeMillis();
-
-    double[][] data = CSVload(file + args[0]);
-    long loadEnd = System.currentTimeMillis();
-    long loadDuration = loadEnd - loadStart;
-    System.out.println("Load csv file: " + loadDuration + " milliseconds");
-   // System.out.println("m: "+ data.length + " n: " + data[0].length);
-
-    Matrix matrix = new Basic2DMatrix().from2DArray(data);
-
-    long productStart = System.currentTimeMillis();
-    Matrix dotProdcut = matrix.multiplyByItsTranspose();
-    long productEnd = System.currentTimeMillis();
-    long productDuration = productEnd - productStart;
-    System.out.println("Dot Product: " + productDuration + " milliseconds");
-
-    //Matrix X = matrix.slice(0, 0, data[0].length - 1, data.length - 1);
-    //Matrix Y = matrix.slice(data[0].length - 1, data.length - 1, data[0].length, data.length);
-
-
-  }
-
-  public static double[][] CSVload(String csvFile) {
-    BufferedReader csvReader = null;
-    List<double[]> dataDouble = new ArrayList<double[]>();
-    try
-    {
-      String row;
-      csvReader = new BufferedReader(new FileReader(csvFile));
-      while ((row = csvReader.readLine()) != null) {
-        String[] elmStr = row.split(",");
-        double[] elmDouble = new double[elmStr.length];
-        for (int i = 0; i < elmStr.length; i++) {
-          elmDouble[i] = Float.parseFloat(elmStr[i]);
-        }
-        dataDouble.add(elmDouble);
-      }
-    }
-    catch (Exception e) {
-      e.printStackTrace();
-    }
-    finally {
-      try {
-        csvReader.close();
-      } catch (IOException e) {
-        e.printStackTrace();
-      }
-    }
-    double[][] data = new double[dataDouble.size()][];
-    for (int i = 0; i < dataDouble.size(); i++) {
-      data[i] = dataDouble.get(i);
-    }
-    return data;
-  }
-}

### 2020-02-02 project/rust_memory_alloc/run.sh

@@ -1,37 +1,0 @@
-#!/bin/bash
-
-cargo clean
-cargo build
-
-for size in 1 2 3 4
-do
-
-
-  rm -rf loging.log
-  echo "datastructure#elementtype#initialization#size#inittime#addtime#totaltime" > loging.log
-
-	for counter in 1 2 3 4 5
-	do
-
-
-
-    # write the first line
-
-
-    for initialization in true false
-    do
-        for elementtype in 1 2 3 4
-        do
-            echo "Adding $size elements with initialization $initialization in Run number  $counter "
-
-            # Server experiment
-            # time taskset -c 0 cargo run $size $initialization $elementtype
-            # Loacal experiment
-            time cargo run $size $initialization $elementtype
-        done
-    done
-
-
-	done
-  cat loging.log  >  result/resultRustAlloc_"$size".txt
-done

### 2020-02-02 project/rust_memory_alloc/src/main.rs

@@ -1,148 +1,0 @@
-extern crate rand;
-
-use std::env;
-use std::time::Instant;
-use std::fs::OpenOptions;
-use std::io::prelude::*;
-
-use rand::{thread_rng, Rng};
-use rand::distributions::Alphanumeric;
-
-fn main() {
-
-    let args: Vec<String> = env::args().collect();
-    
-    let size: usize = args[1].parse().unwrap();
-    let initialization: bool = args[2].parse().unwrap();
-    let elementtype: i32 = args[3].parse().unwrap();
-    vector_addition(size, initialization, elementtype)
-
-}
-fn vector_addition(size: usize, initialization: bool, elementtype: i32) {
-    match size {
-        1 => add_to_vector(10, initialization, elementtype), 
-        2 => add_to_vector(100, initialization, elementtype), 
-        3 => add_to_vector(1000, initialization, elementtype), 
-        4 => add_to_vector(10000, initialization, elementtype), 
-        _ => println!("Invalid input!"),
-    }
-}
-
-fn vector_initialization(size: usize, initialization: bool) {
-    let mut vector;
-    if initialization {
-        vector = Vec::with_capacity(size);
-    } else {
-        vector = Vec::new();
-    }
-    return vector;
-}
-
-
-fn get_elementsVec(size: usize, elementtype: i32) -> std::vec::Vec<T> {
-    let mut elements = Vec::new();
-    match elementtype {
-        1 => element_integer(size),
-        2 => element_string(size),
-        3 => elements_charArr(size),
-        4 => elements_object(size),
-        _ => println!("Invalid input!"),
-    }
-}
-
-
-fn element_integer(size: usize) -> std::vec::Vec<T> {
-    let mut elements = Vec::new();
-    for e in 0..size {
-        elements.push(e as i32);
-    }
-    return elements;
-}
-
-fn element_string(size: usize) -> std::vec::Vec<T> {
-    let mut elements = Vec::new();
-    for _i in 0..size {
-        let rand_string: String = thread_rng()
-                            .sample_iter(&Alphanumeric)
-                            .take(10)
-                            .collect();
-        elements.push(rand_string);
-    }
-    return elements;
-}
-
-fn elements_charArr(size: usize) -> std::vec::Vec<T> {
-    let mut elements = Vec::new();
-    for _i in 0..size {
-        let char_arr = ['a', 'b', 'c', 'd', 'e',
-                        'f', 'g', 'h', 'i', 'j'];
-        elements.push(char_arr);
-    }
[…]

### 2020-02-02 project/rust_object_ref_own_slice/src/main.rs

@@ -29,10 +29,13 @@ fn run(field: i32, size: usize) {
 
 fn run_ex_owned(size: usize) {
     let start = Instant::now();
+    // Create String vectors.
     let addresses = get_string_vector(size);
     let zip_codes = get_string_vector(size);
     let countries = get_string_vector(size);
+    // Create vector of CustomerOwned objects and take creation time.
     let (elapsed_create, customers) = create_customer_onwed_vector(size, addresses, zip_codes, countries);
+    // Access to every feild of each object in the vector and take access time.
     let (elapsed_access, count) = access_owned(& customers).unwrap();
     let elapsed_total = start.elapsed().as_micros();
     write_to_file(size, "own", elapsed_create, elapsed_access, elapsed_total, count);
@@ -40,57 +43,71 @@ fn run_ex_owned(size: usize) {
 
 fn run_ex_borrowed(size: usize) {
     let start = Instant::now();
+    // Create String vectors.
     let addresses = get_string_vector(size);
     let zip_codes = get_string_vector(size);
     let countries = get_string_vector(size);
+    // Create vector of CustomerBorrowed objects and take creation time.
     let (elapsed_create, customers) = create_customer_borrowed_vector(size, &addresses, &zip_codes, &countries);
+    // Access to every feild of each object in the vector and take access time.
     let (elapsed_access, count) = access_borrowed(& customers).unwrap();
     let elapsed_total = start.elapsed().as_micros();
     write_to_file(size, "reference", elapsed_create, elapsed_access, elapsed_total, count);
 }
 
-
+// Function to run experiment for object whose fields are slice.
 fn run_ex_slice(size: usize) {
     let start = Instant::now();
+    // Create String vectors.
     let addresses = get_string_vector(size);
     let zip_codes = get_string_vector(size);
     let countries = get_string_vector(size);
+    // Create vector of CustomerSlice objects and take creation time.
     let (elapsed_create, customers) = create_customer_slice_vector(size, &addresses, &zip_codes, &countries);
+    // Access to every feild of each object in the vector and take access time.   
     let (elapsed_access, count) = access_slice(& customers).unwrap();
[…]

### 2020-02-02 project/test_disk_memory/create_run.py

@@ -1,22 +1,0 @@
-from __future__ import print_function
-import sys
-
-if __name__ == "__main__":
-    print(len(sys.argv))
-    if len(sys.argv) != 3:
-        print("Usage: create_run.py min_row max_row", file=sys.stderr)
-        exit(-1)
-
-    min_row = int(sys.argv[1])
-    max_row = int(sys.argv[2])
-    start_num = int(min_row / 1000)
-    end_num = int(max_row / 1000)
-    
-
-    f = open("run.sh", "a")
-    for i in range(start_num, end_num + 1):
-        s = "(time cargo run ../data/input" + str(i) + ".csv output/output" + str(i) + ".csv) 2>&1 | tee -a log.txt\n"
-        print(s)
-        f.write(s)
-    
-    f.close()

### 2020-02-02 project/test_disk_memory/run.sh

@@ -1,4 +1,0 @@
-
-(time cargo run ../data/input1.csv output/output1.csv) 2>&1 | tee -a log.txt
-(time cargo run ../data/input2.csv output/output2.csv) 2>&1 | tee -a log.txt
-(time cargo run ../data/input3.csv output/output3.csv) 2>&1 | tee -a log.txt

### 2020-02-02 project/test_disk_memory/src/main.rs

@@ -1,133 +1,0 @@
-extern crate csv;
-#[macro_use(s)]
-extern crate ndarray;
-extern crate ndarray_linalg;
-
-
-//use ndarray::{Array, Axis, ArrayBase, stack};
-use ndarray::prelude::*;
-use ndarray::stack;
-use ndarray_linalg::Solve;
-use csv::ReaderBuilder;
-use serde::Deserialize;
-use std::env;
-use std::error::Error;
-use std::convert::From;
-use csv::Writer;
-
-
-// run like (time cargo run input1.csv output1.csv) 2>&1 | tee log1.txt
-fn main() -> Result<(), Box<dyn Error>>  {
-    let args: Vec<String> = env::args().collect();
-    let file_path = String::from(&args[1]);
-    let ret = get_vector_csv(&file_path).unwrap();
-    let (v, d)= ret;
-    let matrix = Array::from_shape_vec((d[0], d[1]), v).unwrap();
-    let x = matrix.slice(s![.., 0..d[1]-2]);
-    let y = matrix.slice(s![.., d[1]-1]);
-    let x_train = x.slice(s![0..d[0]/10*9, ..]).to_owned();
-    let y_train = y.slice(s![0..d[0]/10*9]).to_owned();
-    let _x_test = x.slice(s![d[0]/10*9..d[0], ..]).to_owned();
-    let _y_test = y.slice(s![d[0]/10*9..d[0]]).to_owned();
-    let mut model = LinearRegression::new();
-    model.fit(&x_train, &y_train);
-    //let prediction = model.predict(&x_test);
-    let w = model.w();
-    let mut wtr = Writer::from_path(&args[2])?;
-    wtr.serialize(&w.to_vec())?;
-    wtr.flush()?;
-    println!("{:?}",d);
-    println!("{:?}",w);
-    Ok(())
-}
-
-
-
-// function to get a vector from csv file. Every row is combined into one long vector
-// and later it will be reshaped.
-fn get_vector_csv(file :&String) -> Result<(Vec<f32>, [usize;2]), Box<dyn Error>> {
-    
-    // Configulate file reader and load from csv file in binary
-    let mut rdr = ReaderBuilder::new()
-        .has_headers(false)
-        .from_path(file)?;    
-    
-    // deserialize and make iterator whose element is each row
-    let mut iter = rdr.deserialize();
-
-    // append rows to x until iterator returns None
-    let mut x = Vec::new();
[…]

### 2020-02-02 project/vector_alloc_test/benches/my_benchmark.rs

@@ -1,24 +1,0 @@
-use criterion::{black_box, criterion_group, criterion_main, Criterion};
-use vector_alloc_test::vector_addition;
-
-fn criterion_benchmark(c: &mut Criterion) {
-    c.bench_function("intial_10_fanal_9", |b| b.iter(|| vector_addition(black_box(10), black_box(9))));
-    c.bench_function("intial_100_fanal_9", |b| b.iter(|| vector_addition(black_box(100), black_box(9))));
-    c.bench_function("intial_1000_fanal_9", |b| b.iter(|| vector_addition(black_box(1000), black_box(9))));
-    c.bench_function("intial_10000_fanal_9", |b| b.iter(|| vector_addition(black_box(10000), black_box(9))));
-    c.bench_function("intial_10_fanal_99", |b| b.iter(|| vector_addition(black_box(10), black_box(99))));
-    c.bench_function("intial_100_fanal_99", |b| b.iter(|| vector_addition(black_box(100), black_box(99))));
-    c.bench_function("intial_1000_fanal_99", |b| b.iter(|| vector_addition(black_box(1000), black_box(99))));
-    c.bench_function("intial_10000_fanal_99", |b| b.iter(|| vector_addition(black_box(10000), black_box(99))));
-    c.bench_function("intial_10_fanal_999", |b| b.iter(|| vector_addition(black_box(10), black_box(999))));
-    c.bench_function("intial_100_fanal_999", |b| b.iter(|| vector_addition(black_box(100), black_box(999))));
-    c.bench_function("intial_1000_fanal_999", |b| b.iter(|| vector_addition(black_box(1000), black_box(999))));
-    c.bench_function("intial_10000_fanal_999", |b| b.iter(|| vector_addition(black_box(10000), black_box(999))));
-    c.bench_function("intial_10_fanal_9999", |b| b.iter(|| vector_addition(black_box(10), black_box(9999))));
-    c.bench_function("intial_100_fanal_9999", |b| b.iter(|| vector_addition(black_box(100), black_box(9999))));
-    c.bench_function("intial_1000_fanal_9999", |b| b.iter(|| vector_addition(black_box(1000), black_box(9999))));
-    c.bench_function("intial_10000_fanal_9999", |b| b.iter(|| vector_addition(black_box(10000), black_box(9999))));
-}
-
-criterion_group!(benches, criterion_benchmark);
-criterion_main!(benches);

### 2020-02-02 project/vector_alloc_test/src/lib.rs

@@ -1,7 +1,0 @@
-#[inline]
-pub fn vector_addition(initial_capacity: usize, final_capacity: usize) {
-    let mut vector = Vec::with_capacity(initial_capacity);
-    for i in 0..final_capacity {
-        vector.push(i);
-    }
-}

### 2020-02-05 project/rust_vec_memalloc_for_different_type/src/main.rs
resolved

@@ -654,12 +654,12 @@ impl Serialize for CustomerBorrowed<'_> {
     where S: Serializer,
     {
         let mut state = serializer.serialize_struct("CustomerBorrowed", 6).unwrap();
-        state.serialize_field("key", &*self.key)?;
-        state.serialize_field("age", &*self.age)?;
-        state.serialize_field("num_purchase", &*self.num_purchase)?;
-        state.serialize_field("total_purchase", &*self.total_purchase)?;
-        state.serialize_field("duration_spent", &*self.duration_spent)?;
-        state.serialize_field("duration_since", &*self.duration_since)?;
+        state.serialize_field("key", &self.key)?;
+        state.serialize_field("age", &self.age)?;
+        state.serialize_field("num_purchase", &self.num_purchase)?;
+        state.serialize_field("total_purchase", &self.total_purchase)?;
+        state.serialize_field("duration_spent", &self.duration_spent)?;
+        state.serialize_field("duration_since", &self.duration_since)?;
         state.serialize_field("zip_code", &self.zip_code)?;
         state.serialize_field("address", &self.address)?;
         state.serialize_field("country", &self.country)?;
@@ -679,21 +679,21 @@ impl Serialize for CustomerSlice<'_> {
     where S: Serializer,
     {
         let mut state = serializer.serialize_struct("CustomerBorrowed", 6).unwrap();
-        state.serialize_field("key", &*self.key)?;
-        state.serialize_field("age", &*self.age)?;
-        state.serialize_field("num_purchase", &*self.num_purchase)?;
-        state.serialize_field("total_purchase", &*self.total_purchase)?;
-        state.serialize_field("duration_spent", &*self.duration_spent)?;
-        state.serialize_field("duration_since", &*self.duration_since)?;
-        state.serialize_field("zip_code", &*self.zip_code)?;
-        state.serialize_field("address", &*self.address)?;
-        state.serialize_field("country", &*self.country)?;
-        state.serialize_field("state", &*self.state)?;
-        state.serialize_field("first_name", &*self.first_name)?;
-        state.serialize_field("last_name", &*self.last_name)?;
-        state.serialize_field("province", &*self.province)?;
-        state.serialize_field("comment", &*self.comment)?;
-        state.serialize_field("order", &*self.order)?;
+        state.serialize_field("key", &self.key)?;
+        state.serialize_field("age", &self.age)?;
+        state.serialize_field("num_purchase", &self.num_purchase)?;
[…]

### 2020-02-06 thesis_template/2_RelatedWork/relatedWork.tex
added description
resolved
added

@@
 
+\section{Possible Graph Structure in Rust}
+\label{sec:history}
+In Rust, there are two essential problems to construct graph structure, lifetime and mutability.
+
+The first problem is about what kind of pointer to use to point to other nodes. 
+Since graph can be cyclic, so the ownership consept in Rust is violated if we use Box<Node>.
+
+All of graph structure are immutable at least at creation time. Because graph may have cyclic, 
+we can not create graph at one statement. Although edge of graph has to be mutable to create entire graph structure, 
+we might need multiple references to edges, which violates basic rule of Rust programming.
+
+One solution is to use raw pointers. This is the most flexible approach, but also the most dangerous. 
+By taking this way, we are ignoring all the benefits of Rust.
+
+For
+
 \section{Note for next}
@@
 Comparing operation on various smart pointer type. 
-Rc<T> enables value to have multiple owners, but the value should be immutable. Rx<T> is used in case of single thread. 
-When the situation is multi-thread, Arc<T> is used. Arc<T> performs atomic operation, so it is more expensive than Arc<T>. 
+Rc<T> enables value to have multiple owners, but the value should be immutable. Rc<T> is used in case of single thread. 
+When the situation is multi-thread, Arc<T> is used. Arc<T> performs atomic operation, so it is more expensive than Rc<T>. 
 When we need to mutate value of Rc<T>, RefCell<T> can be useful. RefCell<T> allow us to have mutiple mutable reference and immutable

### 2020-02-06 project/playground/src/main.rs

@@ -1,8 +1,760 @@
 
+extern crate rand;
+extern crate bytes;
+use std::iter;
+use std::env;
+use std::time::Instant;
+use std::io::prelude::*;
+use std::fs::OpenOptions;
+use rand::{Rng,SeedableRng};
+use rand::rngs::StdRng;
+use rand::distributions::Alphanumeric;
+use rand::distributions::{Uniform, Distribution};
+use serde::ser::{Serialize, Serializer, SerializeStruct};
+
+
 fn main() {
     let args: Vec<String> = env::args().collect();
     let size: usize = args[1].parse().unwrap();
-    let method: i32 = args[2].parse().unwrap();
-    run_experiment(size, method);
+    let field: i32 = args[2].parse().unwrap();
+    run(field, size);
+}
+
+fn run(field: i32, size: usize) {
+    match field {
+        1 => run_ex_owned(size),
+        2 => run_ex_borrowed(size),
+        3 => run_ex_slice(size),
+        _ => println!("Wrong input!")
+    }
+}
+
+fn run_ex_owned(size: usize) {
+    let start = Instant::now();
+    let order_ids = get_integer_vector(size);
+    let num_itemss = get_integer_vector(size);
+    let payments = get_float_vector(size);
+    let order_times = get_float_vector(size);
+    let titles = get_string_vector(size);
+    let comments_order = get_string_vector(size);
+    let orders = get_order_owned_vector(size, order_ids, num_itemss, payments, order_times, titles, comments_order);
+    
+    let keys = get_integer_vector(size);
+    let ages = get_integer_vector(size);
+    let num_purchases = get_integer_vector(size);
+    let total_purchases = get_float_vector(size);
+    let duration_spents = get_float_vector(size);
+    let duration_sinces = get_float_vector(size);
+    let zip_codes = get_string_vector(size);
+    let addresss = get_string_vector(size);
+    let countrys = get_string_vector(size);
+    let states = get_string_vector(size);
+    let first_names = get_string_vector(size);
+    let last_names = get_string_vector(size);
+    let provinces = get_string_vector(size);
+    let comments = get_string_vector(size);
+
+    // Create vector of CustomerOwned objects and take creation time.
+    let (elapsed_create, customers) = create_customer_onwed_vector(size, keys, ages, num_purchases, total_purchases, duration_spents, duration_sinces, 
[…]

### 2020-02-06 project/rust_vec_memalloc_for_different_type/run.sh

@@ -24,5 +24,6 @@ do
             # time cargo run --release $size $method $field
         done
     done
+    cat string.log  >  result/vectorSize_"$size".txt
     cat loging.log  >  result/resultRustOwnerType_"$size".txt
 done

### 2020-02-06 project/rust_vec_memalloc_for_different_type/src/main.rs

@@ -279,7 +279,8 @@ fn create_customer_onwed_vector(size: usize, mut keys: Vec<i32>, mut ages: Vec<i
                                 mut states: Vec<String>, mut first_names: Vec<String>, mut last_names: Vec<String>,
                                 mut provinces: Vec<String>, mut comments: Vec<String>, mut orders: Vec<OrderOwned>) -> (u128, Vec<CustomerOwned>) {
     let start = Instant::now();
-    let mut customers: Vec<CustomerOwned> = Vec::with_capacity(size);
+    // let mut customers: Vec<CustomerOwned> = Vec::with_capacity(size);
+    let mut customers: Vec<CustomerOwned> = Vec::new();
     for _ in 0..size {
         // Get owner by poping String from vector and create CustomerOwned.
         let key = keys.pop().unwrap();
@@ -311,7 +312,8 @@ fn create_customer_borrowed_vector<'a>(size: usize, keys: &'a Vec<i32>, ages: &'
                                         states: &'a Vec<String>, first_names: &'a Vec<String>, last_names: &'a Vec<String>,
                                         provinces: &'a Vec<String>, comments: &'a Vec<String>, orders: &'a Vec<OrderBorrowed>) -> (u128, Vec<CustomerBorrowed<'a>>) {
     let start = Instant::now();
-    let mut customers: Vec<CustomerBorrowed> = Vec::with_capacity(size);
+    // let mut customers: Vec<CustomerBorrowed> = Vec::with_capacity(size);
+    let mut customers: Vec<CustomerBorrowed> = Vec::new();
     for i in 0..size {
         // Get reference by acceesing String in vector and create CustomerBorrowed.
         let key = &keys[i];
@@ -344,7 +346,8 @@ fn create_customer_slice_vector<'a>(size: usize, keys: &'a Vec<i32>, ages: &'a V
                                     states: &'a Vec<String>, first_names: &'a Vec<String>, last_names: &'a Vec<String>,
                                     provinces: &'a Vec<String>, comments: &'a Vec<String>, orders: &'a Vec<OrderSlice>) -> (u128, Vec<CustomerSlice<'a>>) {
     let start = Instant::now();
-    let mut customers: Vec<CustomerSlice> = Vec::with_capacity(size);
+    // let mut customers: Vec<CustomerSlice> = Vec::with_capacity(size);
+    let mut customers: Vec<CustomerSlice> = Vec::new();
     for i in 0..size {
         // Get slice by acceesing String in vector and create CustomerSlice.
         let key = &keys[i];

### 2020-02-09 thesis_template/2_RelatedWork/relatedWork.tex
d
experiment plan

@@
 Vector of Trait(need to put element into Box) vs Vector of concrete type.
+
+Design experiment for comparing among the performance of smart pointers.
+
+If we keep first created owner until the last phase, we can use borrowing to operate.
+If we delete first created owner during the operation, we should use Rc<T>.
+The question would be, we can use Rc<T> every where?
+
+Smart pointer
+    Box<T> - Box pointer lets value allocated on heap rather than on the stack.
+    Rc<T> - Reference counted pointer lets variable take multiple immutable ownership.
+Interier mutability
+    Cell<T> - For only Copy type, it allows us to mutate variable, even if it is immutable
+            Howeever, it does not support sharing the variable so that it returns always copy of the value.
+    RefCell<T> - This support sharing and interier immutability for all types. This is done by allowing to get 
+                mutable reference from immutable variable and push the error detacting time from compile time to runtime.
+
+Experiment to do
+
+Difference of operation time for 
+    - T vs Box<T> vs Rc<T>
+Vec<Box<T>>
+&Box<T>  vs 
+Vec<Rc<T>>
+Vec<Rc<RefCell>>
+
+\section{Todos}
+\label{sec:history}
+\begin{itemize}
+    \item Document experiment of reference and dereferenced
+    \item Redo the experiment with appropriate size
+    \item Design experiment for reference counting(measure dropt time using criterion)
+    \item Design experiment for Graph
+    \item Design experiment for Multithread
+    \item Study about LLVM
+    \item Study about OS memory management(optional)
+\end{itemize}

### 2020-02-09 project/playground/src/main.rs

@@ -29,6 +29,17 @@ fn run(field: i32, size: usize) {
     }
 }
 
+fn run_ex_rc(size: usize) {
+    let start = Instant::now();
+    let order_ids = get_integer_vector(size);
+    let num_itemss = get_integer_vector(size);
+    let payments = get_float_vector(size);
+    let order_times = get_float_vector(size);
+    let titles = get_string_vector(size);
+    let comments_order = get_string_vector(size);
+    
+}
+
 fn run_ex_owned(size: usize) {
     let start = Instant::now();
     let order_ids = get_integer_vector(size);

### 2020-02-14 thesis_template/2_RelatedWork/relatedWork.tex
documented

--- 2020-02-06 thesis_template/2_RelatedWork/relatedWork.tex
@@
 \label{sec:history}
-In this experiment, differences of access time among to owned, borrowed, and sliced are observed. 
-The figure is representation of a Customer object. Among the experiment, we focus on zip_code, address, country fields. 
-These three fields take differet type of String value. The zip_code field takes owned String variable. 
-The address field takes borrowed String variable. The country field takes slice String variable. 
-The assumption here is that there may be difference of operation time among variable types: ownner, reference, slice.
-
-The result shows that access times to onwer and reference are almost the same, but the one to slice is relatively faster 
-compared to the other two.
+In this experiment, differences of access time to among owned, borrowed, and sliced are observed. 
+Each variable has slightly different use of memomry.
 
@@
     \begin{lstlisting}
-        struct Customer<'a> {
-            total_order: i32,
-            weight_order: f32,
+        struct CustomerOwned {
+            key: i32,
+            age: i32,
+            num_purchase: i32,
+            total_purchase: f64,
+            duration_spent: f64, 
+            duration_since: f64,
             zip_code: String,
+            address: String,
+            country: String,
+            state: String,
+            first_name: String,
+            last_name: String,
+            province: String,
+            comment: String, 
+            order: OrderOwned
+        }
+
+        struct CustomerBorrowed<'a> {
+            key: &'a i32,
+            age: &'a i32,
+            num_purchase: &'a i32,
+            total_purchase: &'a f64,
+            duration_spent: &'a f64, 
+            duration_since: &'a f64,
+            zip_code: &'a String,
             address: &'a String,
-            country: &'a str
+            country: &'a String,
+            state: &'a String,
+            first_name: &'a String,
+            last_name: &'a String,
+            province: &'a String,
+            comment: &'a String, 
+            order: &'a OrderBorrowed<'a>
+        }
+
+        struct CustomerSlice<'a> {
+            key: &'a i32,
+            age: &'a i32,
+            num_purchase: &'a i32,
+            total_purchase: &'a f64,
+            duration_spent: &'a f64, 
+            duration_since: &'a f64,
+            zip_code: &'a str,
+            address: &'a str,
+            country: &'a str, 
+            state: &'a str,
+            first_name: &'a str,
+            last_name: &'a str,
+            province: &'a str,
+            comment: &'a str,
+            order: &'a OrderSlice<'a>
+        }
+
+        struct CustomerRc {
+            key: Rc<i32>,
+            age: Rc<i32>,
+            num_purchase: Rc<i32>,
+            total_purchase: Rc<f64>,
+            duration_spent: Rc<f64>, 
+            duration_since: Rc<f64>,
+            zip_code: Rc<String>,
+            address: Rc<String>,
+            country: Rc<String>,
+            state: Rc<String>,
+            first_name: Rc<String>,
+            last_name: Rc<String>,
+            province: Rc<String>,
+            comment: Rc<String>, 
+            order: Rc<OrderRc>
         }
@@
 \end{figure}
+
+\section{Accessment of different reference methods in Rust}
+\label{sec:history}
+The goal of this experiment is to assess efficiency of different reference strategies in Rust, borrowing and reference counting.
+
+By levaraging reference counting, a value can be shared like what borrowing plays the role in Rust programming. 
+The difference is that reference counting checks number of reference pointing to the actual data and makes sure the data is not deleted 
+until all the references are dereferenced. Using reference counting is sometimes preferable approach for developers, 
+we do not have care about lifetime which is usually troublesome when we use borrowing approach many times in our code. 
+However, the possible problem regarding to reference counting is the cost for tracking the number of references. 
+Having this assumption, this experiment will show difference of behavior among reference countinig and borrowing.
+
+In this experiment, CustomerBorrowed and CustomerRc in figure are used to see difference of dropping time among borrowing and reference counting. 
+In the CustomerRc and OrderRc struct, all fields take reference counting (Rc<T>). Similaly to the experiment in the last section, 
+vectors of CustomerRc and CustomerBorrowed are created and droped the elements one by one.
+
+The result shows significant difference of dropping time among the two objects; deletion of CustomerRc is much slower than CustomerBorrowed. 
+This is because reference counters which are feilds of CustomerRc have to check the number of reference pointing to the actual content and decide 
+deallocate the memory or not. However, memory management and lifetime strategy of borrowing is already determined at compile time.
 
@@
 By taking this way, we are ignoring all the benefits of Rust.
-
-For
 
@@
 
-Vector of Trait(need to put element into Box) vs Vector of concrete type.
+Vector of Trait object (need to put element into Box) vs Vector of concrete type.
+
+If we keep first created owner until the last phase, we can use borrowing to operate.
+If we delete first created owner during the operation, we should use Rc<T>.
+The question would be, we can use Rc<T> every where?
+
+Smart pointer
+\begin{itemize}
+    \item Box<T>: Box pointer lets value allocated on heap rather than on the stack.
+    \item Rc<T>: Reference counted pointer lets variable take multiple immutable ownership.
+\end{itemize}
+
+Interier mutability
+    \item Cell<T>: For only Copy type, it allows us to mutate variable, even if it is immutable. Howeever, it does not support sharing the variable so that it returns always copy of the value.
+    \item RefCell<T>: This support sharing and interier immutability for all types.
+This is done by allowing to get mutable reference from immutable variable and push the error detacting time from compile time to runtime.
+
+\section{Todos}
+\label{sec:history}
+\begin{itemize}
+    \item Redo the experiment with appropriate size
+    \item Document for reference counting(measure dropt time using criterion)
+    \item Design experiment for Graph
+    \item Design experiment for Multithread
+    \item Study about LLVM
+    \item Study about OS memory management
+\end{itemize}
+
+\section{LLVM}
+\label{sec:history}
+LLVM (Low Level Virtual Machine) is an umbrella project which contains components of compilation of programming language.
+Exsiting compilers have tightly coupled functionalities so that it is not possible to embed them into other applications.
+However, the abstract framework of LLVM decouples the functionalities into peaces and the peaces of functionalities can be reused.
+
+In structure of a compiler, there are three main components; flontend, optimizer, and backend. 
+In flontend, a develper designs the interface of source programming language in way where it can be optimized by optimizer. 
+Then, backend takes optimized code and produce the native machine code. LLVM has a component called LLVM Intermediate Representation (IR), 
+which places itself across frontend to optimizer. IR is designed to host mid-level analyses and transformations that you find in optimizer section of a compiler.
+High-level language has many common structures and functionalities, so most of all high-level program languages can be represented with IR. 
+Once source code is represented with IR, optimizer can easily find pattern and optimize it in faster time. 
+IR is useful in terms of flontend. This is because developer of language flontend need to know only how the IR works and use the framework to develop a language.
+
+LLVM is a library for programmatically creating machine-native code. A develpers can use the API to generate instruction in a format 
+called an intermeidiate representation (IR). LLVM can then compile tht IR into a standalone binary, 
+perform a JIT (just-in-time) compilation on the code to run in the context of another porgram, such as an interpreter for the language.
+LLVM provides a framework API of intermediate representation for common structures of progamming language, such as function, type, struct.
+LLVM comes with the portability. It independents of machine architecture.
+
+The most common use of LLVM is for ahead-of-time (AOT) compiler for a language, such as C, C++, Rust. 
+However, LLVM can be leveraged with just-in-time (JIT) compiling. 
+For example, python is offten used in iterative workflow and rapid development by being a interpreted language.
+Using JIT compilation to produce such code complements Python's interactive workflow better thatn ahead-of-time compilation.
+
+LLVM

### 2020-02-14 thesis_template/Appendix/Appendix.tex
documented

\chapter{Proof of xyz}
\label{appendix}
\thispagestyle{myheadings}

\section{Memory and Process in Operation Systems}
\label{sec:history}
A process is a section of commutation job. A process can work on a CPU core. We can devide process as well.
Basically, each process does not share thier memory. However, for multiprocessing, we could avoid this restriction.
Processes can be represented as tree structure, because a process may create onther child processes.
Process has 4 states, new, running, waiting, and ready. 
Process is represented in process control block (PCB) with state type, process ID, registers, and so on.
The scheduling for process assigning to CPU core is implemented in queues containing PCB. There are two main queues in this scheduler: 
ready queue and wait queue. The head of process in ready queue is selected for execution and once the process requested I/O request or 
production of child process, the running process will be stored n wait queue. Once the request that the process waiting for end, 
the waiting process will be pushed tail of ready queue.

Processes executing concurrently in the operating system may be either independent processes or cooperating processes excuting in the system.
A process is indepenedent if it does not share data with any other processes. A process cooperating if ti can affect or be affected by the 
other processed executing in the system. In cooperating process, there are two kinds, shared memory and message passing. 
In shared memory, it removes restriction of not interfering memory region. Message passing can be useful for destribution systems as well.

For a pair of processes to communicate throught message, a socket is needed to be established. 
A socket is identified by an IP address concatenated with a port number. When two process communicate, each process will have socket. 
If another process of the same machine wants to communicate, we need new socket to be established. The protocol used in the socket connection
can be TPC and UDP.

\section{Miltithreading and Parallelism}
\label{sec:history}
A thread is a basic unit of CPU usilization, so that a process can have multiple thread. Threads shares mainly code and data. 
Multithreaing is increasingly popular as the multicore programming becomes in common, becasue we can run multiple thread on different core.
Creating thread is much cheaper than creating process and it shares resources so that we do not need addtional methods to allow threads to 
communicate each other, such as sharing memory and message passing.

\section{Memory management in Operation System}
\label{sec:history}
In computer storage hierarchy, the closest strage to CPU is register. It is built into each CPU core and accessible within one cycle of the CPU clock.
However, the same cannot be said of main memory, which is accessed via a transaction on the memory bus. This takes many cycles of the CPU clock.
The remedy is to add fast memeory between the CPU and main memory, typically on the CPU chip for faster access. Such a cache plays a role for this.

For the layout of main memory, it must be ensured that each process has a separate memory space, including operation system. 
The base register and limit register, whose roles are lower boound of memory region and specific size of range respectively, can achieve that goal.

Usually a program resides on a disk as binary excutable file. To run, the program must be brought into memory and placed within the context of a crocess.
The process is binded to corresponding parts of the physical memory. Binding program to memeory address is staging process. 
There three stages: compile time, load time excution time. The source program is compiled by compiler producing object file. 
After the compilation, the object file is linked with other object file by linker creating executable file . 
Finally, the executable file will be loaded to run execute. At this run time dynamic linbrary link can be done.

If where the process will reside in memory at compile time, absolute code is generated. If this is unknown at the time, 
the binding will be done at load time. At this time, the compiler must generate relocatable code. Otherwise, the binding will be done at 
execution time.

A process does not interact with addresses of physical memory, instead virtual memory. The memory-management unit (MMU) takes roles to map 
logical address to physical address. OS needs to ensure that any of physical memory spaces of processes do not overlap. 
Since one process can be created and deleted and the corresponding memory space should be de/allocated, 
optimization for use of physical memory space is important; we need to allocate memory contiguously avoiding fragmentation.

There are several approaches to deal with this problems. However, we will focus on paging here, which is the most used method OS use to manage memory.
A frame and page are a unit of Separated physical and virtaual memory space in fixed size (4KB or 8KB) respectively.
A process can use as many as pages and correspinding frames obtained by page table matching.

### 2020-02-16 thesis_template/2_RelatedWork/relatedWork.tex
documented

@@
 In this experiment, CustomerBorrowed and CustomerRc in figure are used to see difference of dropping time among borrowing and reference counting. 
-In the CustomerRc and OrderRc struct, all fields take reference counting (Rc<T>). Similaly to the experiment in the last section, 
+In the CustomerRc and OrderRc struct, all fields take reference counting (Rc$<$T$>$). Similaly to the experiment in the last section, 
 vectors of CustomerRc and CustomerBorrowed are created and droped the elements one by one.
@@
 Comparing operation on various smart pointer type. 
-Rc<T> enables value to have multiple owners, but the value should be immutable. Rc<T> is used in case of single thread. 
-When the situation is multi-thread, Arc<T> is used. Arc<T> performs atomic operation, so it is more expensive than Rc<T>. 
-When we need to mutate value of Rc<T>, RefCell<T> can be useful. RefCell<T> allow us to have mutiple mutable reference and immutable
+Rc<T> enables value to have multiple owners, but the value should be immutable. Rc$<$T$>$ is used in case of single thread. 
+When the situation is multi-thread, Arc$<$T$>$ is used. Arc$<$T$>$ performs atomic operation, so it is more expensive than Rc$<$T$>$. 
+When we need to mutate value of Rc$<$T$>$, RefCell$<$T$>$ can be useful. RefCell$<$T$>$ allow us to have mutiple mutable reference and immutable
 of reference mutable or immutable variable at the same time. When the mutability consistency is voilented, it terminates program during runtime. 
-That is why RefCell<T> is expensive so that the state of mutable consistency should tracked. 
-As Cell<T>, the value is copied in and out of the Cell<T> instead of getting refrence to it. 
-In addition, Mutex<T> provides intetior mutability across multi-thread.
+That is why RefCell$<$T$>$ is expensive so that the state of mutable consistency should tracked. 
+As Cell$<$T$>$, the value is copied in and out of the Cell$<$T$>$ instead of getting refrence to it. 
+In addition, Mutex$<$T$>$ provides intetior mutability across multi-thread.
 
 Comparison between mutable and immutable tree or graph structure can be checked. 
-This is because tree structure requires Rc<T> or Week<T> and in addition RefCell<T> to make it mutable.
+This is because tree structure requires Rc$<$T$>$ or Week$<$T$>$ and in addition RefCell<T> to make it mutable.
 
@@
 If we keep first created owner until the last phase, we can use borrowing to operate.
-If we delete first created owner during the operation, we should use Rc<T>.
-The question would be, we can use Rc<T> every where?
+If we delete first created owner during the operation, we should use Rc$<$T$>$.
+The question would be, we can use Rc$<$T$>$ every where?
 
@@
 \begin{itemize}
-    \item Box<T>: Box pointer lets value allocated on heap rather than on the stack.
-    \item Rc<T>: Reference counted pointer lets variable take multiple immutable ownership.
+    \item Box$<$T$>$: Box pointer lets value allocated on heap rather than on the stack.
+    \item Rc$<$T$>$: Reference counted pointer lets variable take multiple immutable ownership.
 \end{itemize}
@@
 Interier mutability
-    \item Cell<T>: For only Copy type, it allows us to mutate variable, even if it is immutable. Howeever, it does not support sharing the variable so that it returns always copy of the value.
-    \item RefCell<T>: This support sharing and interier immutability for all types.
+    \item Cell$<$T$>$: For only Copy type, it allows us to mutate variable, even if it is immutable. Howeever, it does not support sharing the variable so that it returns always copy of the value.
+    \item RefCell$<$T$>$: This support sharing and interier immutability for all types.
 This is done by allowing to get mutable reference from immutable variable and push the error detacting time from compile time to runtime.
-
-\section{Todos}
-\label{sec:history}
-\begin{itemize}
-    \item Redo the experiment with appropriate size
-    \item Document for reference counting(measure dropt time using criterion)
-    \item Design experiment for Graph
-    \item Design experiment for Multithread
-    \item Study about LLVM
-    \item Study about OS memory management
-\end{itemize}
 
@@
 
-LLVM is a library for programmatically creating machine-native code. A develpers can use the API to generate instruction in a format 
-called an intermeidiate representation (IR). LLVM can then compile tht IR into a standalone binary, 
-perform a JIT (just-in-time) compilation on the code to run in the context of another porgram, such as an interpreter for the language.
-LLVM provides a framework API of intermediate representation for common structures of progamming language, such as function, type, struct.
-LLVM comes with the portability. It independents of machine architecture.
+\section{Todos}
+\label{sec:history}
+\begin{itemize}
+    \item Redo the experiment with appropriate size
+    \item Document for reference counting(measure dropt time using criterion)
+    \item Design experiment for Graph
+    \item Design experiment for Multithread
+    \item Study about LLVM
+    \item Study about OS memory management
+\end{itemize}
 
-The most common use of LLVM is for ahead-of-time (AOT) compiler for a language, such as C, C++, Rust. 
-However, LLVM can be leveraged with just-in-time (JIT) compiling. 
-For example, python is offten used in iterative workflow and rapid development by being a interpreted language.
-Using JIT compilation to produce such code complements Python's interactive workflow better thatn ahead-of-time compilation.
-
-LLVM
+\section{Time Line}
+\label{sec:history}
+\begin{itemize}
+    \item End Feb: Finish Experiment for Multithread and Graph
+    \item Mid May: ML experiment
+    \item End May: Redo experiment with bench mark dataset.
+    \item Start April: Finish Writing for first revise.
+\end{itemize}

### 2020-02-16 thesis_template/Appendix/Appendix.tex
documented

@@
 \label{sec:history}
-A process is a section of commutation job. A process can work on a CPU core. We can devide process as well.
+A process is a section of computation job. A process can work on a CPU core. We can devide process as well.
 Basically, each process does not share thier memory. However, for multiprocessing, we could avoid this restriction.
@@
 A frame and page are a unit of Separated physical and virtaual memory space in fixed size (4KB or 8KB) respectively.
-A process can use as many as pages and correspinding frames obtained by page table matching.
+A process can use as many as pages and correspinding frames obtained by page table matching. This strategy does improve external fragmentation, but not for internal fragmentation.
+The smaller size of page has smaller fragmentation, but mapping from page to grame has overhead and also disk I/O is more efficient when the amount of data transfered is larger.
+
+\section{Demand Paging}
+\label{sec:history}
+A process can have mutiple pages. However, loading entire executable code from sendory storage to memory is not necessarily needed to 
+get jobs done. A storategy used in several operating systems is loading only the portion of programs that are needed, demand page.
+
+In the storatege, some pages currently used are in memory and the others are in secondary storage. 
+The page table specifies whether pages are valid or invalid, which means are in memory or not. 
+Access to a page marked invalid causes page fault and some steps to resolve the error will be required.
+
+The first part of process of demand pageing would be that we check an internal table to check whether the reference is valide or invalid.
+If the reference is valid, the process reads the content from the memory. Otherwise, we terminates the process and find the free frame in 
+physical memory. Then, we schedule a secondary storage operation to read the desired page into newly allocated frame. 
+When the storage complete reading the page, we modify the internal table to indicate the page is now in memory. 
+Finally, we restart the instruction that was interrupted.
+
+However, there would be a case where the memory does not have any free frame. In this case, a victim frame that will be replaced with new comming frame should be selected. 
+To perform this selection efficiently, a modify bit is tracked for each frame or page. The modify bit represents whether the page is modified since it is loaded from secondary storage. 
+If the page or frame is modified, when we swap page we need to update the content in the secondary storage. However, it is not modified, we can simplly delete the frame and replace with new frame.
+
+\section{Copy on Page}
+\label{sec:history}
+When a parent process creates child process and if these process shares contents on particular page and modify it, 
+only the page whitch has the contenst will be copied.

### 2020-02-18 thesis_template/2_RelatedWork/relatedWork.tex
documented

@@
 
+\section{Time to Drop Reference vs Reference Counting}
+\label{sec:history}
+In this experiment, an assessment is conducted to valify whether there is difference between behavior of borrowing and reference counting. 
+These two methods can be used in similar situation. Especially, when we want reference to an original variable and keep the original variable until all of references are dereferenced, 
+we can have reference with both storategies, borrowing and reference counting. One advantage of using reference counting is that we do not have to pay attention to lifetime.
+However, the assumption here is that use of reference counting might be computationally expenesive than borrowing, because reference counting has to track the number of reference pointing to the value.
+Considered this assumption, we assess difference of time for dropping reference using borrowing and reference counting strategies.
+
+Similally to the last section, we implement struct whose fields are borrowing reference and reference counting and measure the time to drop the struct.
+
+The result shows the time to drop borrowing reference is significatly faster than reference counting.
+This says that we should use borrwoing storategies whenever high performance computation is critical.
+
+\begin{figure}[htb]
+    \includegraphics[width=15cm]{rust_droptime_borring_rc.eps}
+    \caption{Runtime for Droping to fields of Customer Object}
+    \label{fig:Sampling}
+\end{figure}
+
 \section{Possible Graph Structure in Rust}

### 2020-02-18 thesis_template/Appendix/Appendix.tex
documented

@@
 When a parent process creates child process and if these process shares contents on particular page and modify it, 
-only the page whitch has the contenst will be copied.
+only the page which has the contenst will be copied.
+
+\section{Threads and Concurrency}
+\label{sec:history}

### 2020-02-22 project/playground/src/main.rs
mergesort

@@ -4,170 +4,32 @@ extern crate serde;
 extern crate bytes;
 use std::env;
 use std::time::Instant;
-use std::io::prelude::*;
-use std::fs::OpenOptions;
-use std::rc::Rc;
+
+use std::sync::Arc;
 mod objects;
-use objects::customer::*;
-use objects::order::*;
+//use objects::customer::*;
+//use objects::order::*;
 use objects::field::*;
-use objects::dropping::*;
-use objects::access::*;
+//use objects::dropping::*;
+//use objects::access::*;
+use objects::sort::*;
+
 
 fn main() {
     let args: Vec<String> = env::args().collect();
     let size: usize = args[1].parse().unwrap();
-    let field: i32 = args[2].parse().unwrap();
-    run(field, size);
+    let mut nums1 = get_integer_vector(size);
+    let n1 = nums1.len();
+    println!("Initial: {:?}", nums1);
+    mergesort_st(&mut nums1[..], 0, n1);
+    println!("Sort with ST: {:?}", nums1);
+    let nums2 = get_integer_vector(size);
+    let n2 = nums2.len();
+    let merged = mergesort_mt(nums2, 0, n2);
+    println!("Sort with MT{:?}", merged);
+    let nums3 = get_integer_vector(size);
+    let n3 = nums3.len();
+    let num3_atomic = Arc::new(Mutex::new(nums3));
+    mergesort_mt_mutex(Arc::clone(&num3_atomic), 0, n3);
+    println!("Sort with Mutex{:?}", num3_atomic);
 }
-
-fn run(field: i32, size: usize) {
-    match field {
-        1 => run_ex_owned(size),
-        2 => run_ex_borrowed(size),
-        3 => run_ex_rc(size),
-        _ => println!("Wrong input!")
-    }
-}
-
-
-fn run_ex_owned(size: usize) {
-    let start = Instant::now();
-    let order_ids = get_integer_vector(size);
-    let num_itemss = get_integer_vector(size);
-    let payments = get_float_vector(size);
-    let order_times = get_float_vector(size);
-    let titles = get_string_vector(size);
-    let comments_order = get_string_vector(size);
-    let orders = get_order_owned_vector(size, order_ids, num_itemss, payments, order_times, titles, comments_order);
-    
-    let keys = get_integer_vector(size);
-    let ages = get_integer_vector(size);
-    let num_purchases = get_integer_vector(size);
-    let total_purchases = get_float_vector(size);
[…]

### 2020-02-22 project/playground/src/objects/mod.rs

@@ -3,3 +3,4 @@ pub mod order;
 pub mod field;
 pub mod dropping;
 pub mod access;
+pub mod sort;

### 2020-02-22 project/playground/src/objects/sort.rs

@@ -1,0 +1,279 @@
+use std::thread;
+pub use std::sync::{mpsc, Mutex, Arc};
+use std::cell::RefCell;
+pub use crossbeam::atomic::AtomicCell;
+
+const MAX_THREADS: usize = 4;
+
+pub fn mergesort_st(arr: &mut [i32], left: usize, right: usize) {
+    let size = right - left;
+    let mut helper: Vec<i32> = vec![0; size];
+    merge_st_helper(arr, left, right, &mut helper[..]);
+}
+
+
+fn merge_st(arr: &mut [i32], left: usize, mid: usize,right: usize, helper: &mut [i32])  {
+    for i in left..mid {
+        helper[i] = arr[i];
+    }
+    for i in mid..right {
+        helper[i] = arr[i];
+    }
+    let mut left_ptr = left;
+    let mut right_ptr = mid;
+    let mut current_ptr = left;
+
+    while left_ptr < mid && right_ptr < right {
+        if helper[left_ptr] < helper[right_ptr] {
+            arr[current_ptr] = helper[left_ptr];
+            left_ptr += 1; 
+        } else {
+            arr[current_ptr] = helper[right_ptr];
+            right_ptr += 1;
+        }
+        current_ptr += 1;
+    }
+
+    while left_ptr < mid {
+        arr[current_ptr] = helper[left_ptr];
+        left_ptr += 1;
+        current_ptr += 1; 
+    }
+
+    while right_ptr < right {
+        arr[current_ptr] = helper[right_ptr];
+        right_ptr += 1;
+        current_ptr += 1; 
+    }
+}
+
+fn merge_st_helper(arr: &mut [i32], left: usize, right: usize, helper: &mut [i32]){
+    if right - left > 1 {
+        let mid = (left + right) / 2;
+
+        merge_st_helper(arr, left, mid, helper);
+        merge_st_helper(arr, mid, right, helper);
+
+        merge_st(arr, left, mid, right, helper);
+    }
+}
+
+///////////////////////////////////////////////////////////////
+///////////////////////////////////////////////////////////////
+///////////////////////////////////////////////////////////////
+pub fn mergesort_mt(arr:Vec<i32>, left: usize, right: usize) -> Vec<i32> {
+    return merge_mt_helper(arr, left, right, 0);
+}
+
+fn merge_mt_helper(arr: Vec<i32>, left: usize, right: usize, depth: usize) -> Vec<i32> {
+    if right - left > 1 {
[…]

### 2020-02-24 thesis_template/2_RelatedWork/relatedWork.tex
mergesort
good implementation

@@
 
+\section{Experiment for Multithread}
+\label{sec:history}
+Experiment for multithreading in Rust is interesting, because there are many memory allocation and deallocation in each threads.
+This is because each thread offten need to form independent memory state to each other to perform computation concurrently safely.
+In addition, the multithreading strategy can be planned in different ways in Rust using different concurrent computation tools, 
+Mutex, Arc, spawn, channel, scope, and so on.
+
+Currently available plan
+\begin{itemize}
+    \item spawn, channel and sending data (currently deviding data, but we probably do not need to).
+    \item spawn, forkjoin and shared data.(shared data among child and parent).
+    \item scope, forkjoin and slice shared data.
+    \item Use linkedList instead of Vector (Each node can be sharable data structure). When we have complex object of elements in vector, we want to copy the pointer to the object.
+    \item Compare performace on LinkedList which is not contiguous allocation, but do not need additional memory allocation and Vec.
+\end{itemize}
+
 \section{Note for next}
@@
 The question would be, we can use Rc$<$T$>$ every where?
+
+Multithread in Rust vs Java
 

### 2020-02-24 project/playground/src/main.rs

@@ -3,13 +3,11 @@ extern crate rand;
 extern crate serde;
 extern crate bytes;
 use std::env;
-use std::time::Instant;
-
 use std::sync::Arc;
 mod objects;
-//use objects::customer::*;
-//use objects::order::*;
-use objects::field::*;
+use objects::customer::{create_customer_onwed_vector};
+use objects::order::{get_order_owned_vector};
+use objects::field::{get_float_vector, get_integer_vector, get_string_vector};
 //use objects::dropping::*;
 //use objects::access::*;
 use objects::sort::*;
@@ -18,18 +16,65 @@ use objects::sort::*;
 fn main() {
     let args: Vec<String> = env::args().collect();
     let size: usize = args[1].parse().unwrap();
-    let mut nums1 = get_integer_vector(size);
-    let n1 = nums1.len();
+    let nums1 = get_integer_vector(size);
     println!("Initial: {:?}", nums1);
-    mergesort_st(&mut nums1[..], 0, n1);
-    println!("Sort with ST: {:?}", nums1);
+
     let nums2 = get_integer_vector(size);
     let n2 = nums2.len();
-    let merged = mergesort_mt(nums2, 0, n2);
+    let merged = mergesort_mt_mp(nums2, 0, n2);
     println!("Sort with MT{:?}", merged);
+
     let nums3 = get_integer_vector(size);
     let n3 = nums3.len();
     let num3_atomic = Arc::new(Mutex::new(nums3));
     mergesort_mt_mutex(Arc::clone(&num3_atomic), 0, n3);
     println!("Sort with Mutex{:?}", num3_atomic);
+
+    let nums4 = get_integer_vector(size);
+    let n4 = nums4.len();
+    let num4_atomic = Arc::new(nums4);
+    let merged2 = mergesort_mt_im(Arc::clone(&num4_atomic), 0, n4);
+    println!("Sort with Immutable{:?}", merged2);
+    
+    let nums5 = get_integer_vector(size);
+    let n5= nums5.len();
+    //let num5_atomic = Arc::new(nums5);
+    let merged5 = mergesort_mt_mp_improve(nums5, 0, n5);
+    println!("Sort with Improve{:?}", merged5);
+
+    let keys = get_integer_vector(size);
+    let ages = get_integer_vector(size);
+    let num_purchases = get_integer_vector(size);
+    let total_purchases = get_float_vector(size);
+    let duration_spents = get_float_vector(size);
[…]

### 2020-02-24 project/playground/src/objects/customer.rs

@@ -1,7 +1,9 @@
-use crate::objects::order::*;
+use crate::objects::order::{OrderOwned, OrderBorrowed, OrderRc};
 use std::rc::Rc;
 use std::time::Instant;
+use std::cmp::Ordering;
 use serde::ser::{Serialize, Serializer, SerializeStruct};
+use std::fmt;
 // Custorm trait (interface for all objects.)
 pub trait Customer {
     fn zip_code_bytes(&self) -> &[u8];
@@ -12,6 +14,7 @@ pub trait Customer {
 
 
 // Objects whose fields are all owned.
+#[derive(Clone, Debug)]
 pub struct CustomerOwned {
     key: i32,
     age: i32,
@@ -31,6 +34,7 @@ pub struct CustomerOwned {
 }
 
 // Objects whose fields are all borrowed.
+#[derive(Clone, Debug)]
 pub struct CustomerBorrowed<'a> {
     key: &'a i32,
     age: &'a i32,
@@ -48,8 +52,7 @@ pub struct CustomerBorrowed<'a> {
     comment: &'a String, 
     order: &'a OrderBorrowed<'a>
 }
-
-
+#[derive(Clone, Debug)]
 pub struct CustomerRc {
     key: Rc<i32>,
     age: Rc<i32>,
@@ -181,6 +184,73 @@ impl Customer for CustomerRc {
     }
     fn country_bytes(&self) -> &[u8] {
         self.country.as_bytes()
+    }
+}
+
+impl Eq for CustomerOwned {}
+
+impl Ord for CustomerOwned {
+    fn cmp(&self, other: &Self) -> Ordering {
+        self.key.cmp(&other.key)
+    }
+}
+
+impl PartialOrd for CustomerOwned {
+    fn partial_cmp(&self, other: &Self) -> Option<Ordering> {
+        Some(self.cmp(other))
+    }
+}
+
+impl PartialEq for CustomerOwned {
+    fn eq(&self, other: &Self) -> bool {
+        self.key == other.key
+    }
+}
+
+impl Eq for CustomerBorrowed<'_> {}
+
+impl Ord for CustomerBorrowed<'_> {
+    fn cmp(&self, other: &Self) -> Ordering {
+        self.key.cmp(&other.key)
+    }
+}
+
+impl PartialOrd for CustomerBorrowed<'_> {
+    fn partial_cmp(&self, other: &Self) -> Option<Ordering> {
+        Some(self.cmp(other))
+    }
+}
+
[…]

### 2020-02-24 project/playground/src/objects/mod.rs

@@ -1,6 +1,6 @@
 pub mod customer;
 pub mod order;
 pub mod field;
-pub mod dropping;
-pub mod access;
+//pub mod dropping;
+//pub mod access;
 pub mod sort;

### 2020-02-24 project/playground/src/objects/order.rs

@@ -1,6 +1,8 @@
 use std::rc::Rc;
 use serde::ser::{Serialize, Serializer, SerializeStruct};
+use std::cmp::Ordering;
 
+#[derive(Clone, Debug)]
 pub struct OrderOwned {
     order_id: i32,
     num_items: i32, 
@@ -9,8 +11,7 @@ pub struct OrderOwned {
     title: String,
     comment: String
 }
-
-
+#[derive(Clone, Debug)]
 pub struct OrderBorrowed<'a> {
     order_id: &'a i32,
     num_items: &'a i32, 
@@ -20,6 +21,7 @@ pub struct OrderBorrowed<'a> {
     comment: &'a String
 }
 
+#[derive(Clone, Debug)]
 pub struct OrderRc {
     order_id: Rc<i32>,
     num_items: Rc<i32>, 
@@ -65,6 +67,66 @@ impl OrderRc {
             title: title,
             comment: comment
         }
+    }
+}
+
+impl Eq for OrderOwned {}
+
+impl Ord for OrderOwned {
+    fn cmp(&self, other: &Self) -> Ordering {
+        self.order_id.cmp(&other.order_id)
+    }
+}
+
+impl PartialOrd for OrderOwned {
+    fn partial_cmp(&self, other: &Self) -> Option<Ordering> {
+        Some(self.cmp(other))
+    }
+}
+
+impl PartialEq for OrderOwned {
+    fn eq(&self, other: &Self) -> bool {
+        self.order_id == other.order_id
+    }
+}
+
+impl Eq for OrderBorrowed<'_> {}
+
+impl Ord for OrderBorrowed<'_> {
+    fn cmp(&self, other: &Self) -> Ordering {
+        self.order_id.cmp(&other.order_id)
+    }
+}
+
+impl PartialOrd for OrderBorrowed<'_> {
+    fn partial_cmp(&self, other: &Self) -> Option<Ordering> {
+        Some(self.cmp(other))
+    }
+}
+
+impl PartialEq for OrderBorrowed<'_> {
+    fn eq(&self, other: &Self) -> bool {
+        self.order_id == other.order_id
+    }
+}
+
+impl Eq for OrderRc {}
+
+impl Ord for OrderRc {
+    fn cmp(&self, other: &Self) -> Ordering {
+        self.order_id.cmp(&other.order_id)
+    }
+}
+
+impl PartialOrd for OrderRc {
[…]

### 2020-02-24 project/playground/src/objects/sort.rs

@@ -2,70 +2,21 @@ use std::thread;
 pub use std::sync::{mpsc, Mutex, Arc};
 use std::cell::RefCell;
 pub use crossbeam::atomic::AtomicCell;
+use crate::objects::customer::*;
 
 const MAX_THREADS: usize = 4;
 
-pub fn mergesort_st(arr: &mut [i32], left: usize, right: usize) {
-    let size = right - left;
-    let mut helper: Vec<i32> = vec![0; size];
-    merge_st_helper(arr, left, right, &mut helper[..]);
+
+
+//////////////////////////////////////
+//////////////////////////////////////
+/////////////////////////////////////////
+///////////////////////////////////////// 
+pub fn mergesort_mt_mp_customer(arr:Vec<CustomerOwned>, left: usize, right: usize) -> Vec<CustomerOwned> {
+    return merge_mt_helper_mp_customer(arr, left, right, 0);
 }
 
-
-fn merge_st(arr: &mut [i32], left: usize, mid: usize,right: usize, helper: &mut [i32])  {
-    for i in left..mid {
-        helper[i] = arr[i];
-    }
-    for i in mid..right {
-        helper[i] = arr[i];
-    }
-    let mut left_ptr = left;
-    let mut right_ptr = mid;
-    let mut current_ptr = left;
-
-    while left_ptr < mid && right_ptr < right {
-        if helper[left_ptr] < helper[right_ptr] {
-            arr[current_ptr] = helper[left_ptr];
-            left_ptr += 1; 
-        } else {
-            arr[current_ptr] = helper[right_ptr];
-            right_ptr += 1;
-        }
-        current_ptr += 1;
-    }
-
-    while left_ptr < mid {
-        arr[current_ptr] = helper[left_ptr];
-        left_ptr += 1;
-        current_ptr += 1; 
-    }
-
-    while right_ptr < right {
-        arr[current_ptr] = helper[right_ptr];
-        right_ptr += 1;
-        current_ptr += 1; 
-    }
-}
-
-fn merge_st_helper(arr: &mut [i32], left: usize, right: usize, helper: &mut [i32]){
-    if right - left > 1 {
-        let mid = (left + right) / 2;
-
-        merge_st_helper(arr, left, mid, helper);
-        merge_st_helper(arr, mid, right, helper);
-
-        merge_st(arr, left, mid, right, helper);
-    }
-}
-
[…]

### 2020-02-28 thesis_template/0_Prelim/abs.tex
need to improve expeliment

@@
 
-Many of popular open source cluster computing frameworks for large scale data analysis, such as Hadoop and Spark, 
-allow programmers to define objects in a host languages, such as Java. The objects are then managed in RAM 
-by the language and its runtime, Java Virtual Machine in the case of Java and Scala. Storing objects 
-in memory enables machine to process iterative computation. One of the fundamental tasks for recent big data analysis 
-is analysis using Machine Learning Algorithms, which require iterative process. As the amount of data increases, memory is required to keep many objects. 
-Therefore, memory management plays a critical role in this task.
-
-Memory management in Java and Scala is performed by garbage collection. The garbage collection brings a significant advantage 
-for programmers by removing responsibility for planning memory management by themselves. Instead, JVM monitors the state of memory 
-and performs garbage collection at certain points. However, these monitoring and auto-execution of garbage collection cost additional computation 
-and might consume computation resources which should be used for data processing. This can significantly decrease performance of the computation.
-
-In contrast, memory management in system language, such as C++, relies on programmers’ decision for when to allocate and deallocate memory. 
-The functions, malloc/free consume most of the memory management. Proper implementation of system language for big data processing can be overperform the implementation in host language. 
-Nevertheless, implementing C++ performing proper memory management and guaranteeing security can be unproductive and complicated.
-
-Considering the issue of memory management, we introduce solution based on unique memory management methods implemented in Rust, ownership and borrowing. 
-This unique concepts in Rust secure codes and perform memory management without monitoring memory or calling functions. 
-We introduce implementations of machine learning algorithms in both Java and Rust to assess performances of each memory management system for iterative big data processing tasks.
+Existing big data processing tools are developed on A

### 2020-02-28 thesis_template/1_Intro/intro.tex
need to improve expeliment

@@
 \thispagestyle{myheadings}
+
+\section{Motivataion}
+\label{sec:history}
+Importance of cluster computing tool for Big Data Analysis has been increasing as amount, value, use of data has increased. 
+Recently, almost all businesses stand on data, from web marketing analysis to factory automations and leverage of data is ubiquitous, because 
+there are many open source tools to analyze data and cloud computer infractrustures which can support computation for massive amount of data. 
+The improvement of accessability to these technologies to deal with big data democratized data driven businesses by 
+eliminating significant amount of initial investment.
+
+However these technologies do not come with free; we need to pay for it. Ususally, user needs to pay depending on use of computational resources. 
+If your process of data analysis is too long or need to use a number of cluster with high speck specification, the cost will end up significantly hight.
+To address these problems, the quality of analysis tool is critical. If the tool can optimize the runtime performance and usage of computational resources, 
+the cost for runing the businesses can be efficient.
+
+Multiple cluster computing analysis tools have been developed, such as Hadoop MapReduce, Spark, and Flink. These tools have brought reliable and scalable ways to deal massive data. 
+These has become widely popular, in which data-parallel computations are executed on clusters of unreliable machines by systems that automatically provide locality-aware scheduling, 
+fault tolerance, and load balancing.
+
+These tools are constructed on top of Java Virtual Machine (JVM). JVM abstracts hardware and memory management from the developper so that the development is fairly easy. 
+In addition, Java or Scala compiled code is platform-independent, which can run on any machine with JVM. However, these advantages may be really critical weakness when it comes to 
+processing big data. JVM abstract away most detail regarding memeory management from the system designer, including memory deallocation, reuse, and movement, as well as pointers, 
+object serialization and deserialization. Since managing and utilizing memory is one of the most important factors determining Big Data systems performance, 
+reliance on a managed environment can mean an ordeer-of-magnitude increase in CPU cost for some computations. This cost may be unacceptable for high-perfomance tool development by an expert.
+
+To overcome these problems, one can use programming languages with more contoral on hardware, system languages, for development of Big Data tools.
+For example, C++ is a general-purpose, statically typed,
+compiled programming language which supports multiple programming paradcigm.
+It is also a system language which gives full control over hardware.
+There are several researches or projects where developers and
+researchers implement Big Data tools with this language. These tools shows significantly better performances than those developed with application languages. 
+Although the evidence of the advantage of building high speed computational tools with C++ has been discovered, the steep learning curve and difficulty of writing memory safe codes are bariiers to technology diffusion.
+
+Rust is a system language which give the similar performance and control of hardware to C++ or C and safety of runtime.
+Unique memory management strategy of Rust, ownership and borrowing, and fearless concurrenry
+make the language one of the ideal candidate for development of Big Data tools.
+
+Write about some development and research for Big Data tools with system language.
+
+Platform depenedance is no longer disadvantage, because of docker and kubernets.
+
+Rust safe language advantage
 

### 2020-02-28 project/playground/src/main.rs

@@ -4,13 +4,15 @@ extern crate serde;
 extern crate bytes;
 use std::env;
 use std::sync::Arc;
+use std::rc::Rc;
 mod objects;
-use objects::customer::{create_customer_onwed_vector};
-use objects::order::{get_order_owned_vector};
-use objects::field::{get_float_vector, get_integer_vector, get_string_vector};
+use objects::customer::*;
+use objects::order::*;
+use objects::field::*;
 //use objects::dropping::*;
 //use objects::access::*;
 use objects::sort::*;
+use std::mem;
 
 
 fn main() {
@@ -18,29 +20,6 @@ fn main() {
     let size: usize = args[1].parse().unwrap();
     let nums1 = get_integer_vector(size);
     println!("Initial: {:?}", nums1);
-
-    let nums2 = get_integer_vector(size);
-    let n2 = nums2.len();
-    let merged = mergesort_mt_mp(nums2, 0, n2);
-    println!("Sort with MT{:?}", merged);
-
-    let nums3 = get_integer_vector(size);
-    let n3 = nums3.len();
-    let num3_atomic = Arc::new(Mutex::new(nums3));
-    mergesort_mt_mutex(Arc::clone(&num3_atomic), 0, n3);
-    println!("Sort with Mutex{:?}", num3_atomic);
-
-    let nums4 = get_integer_vector(size);
-    let n4 = nums4.len();
-    let num4_atomic = Arc::new(nums4);
-    let merged2 = mergesort_mt_im(Arc::clone(&num4_atomic), 0, n4);
-    println!("Sort with Immutable{:?}", merged2);
-    
-    let nums5 = get_integer_vector(size);
-    let n5= nums5.len();
-    //let num5_atomic = Arc::new(nums5);
-    let merged5 = mergesort_mt_mp_improve(nums5, 0, n5);
-    println!("Sort with Improve{:?}", merged5);
 
     let keys = get_integer_vector(size);
     let ages = get_integer_vector(size);
@@ -66,14 +45,56 @@ fn main() {
 
     let mut orders = get_order_owned_vector(size, order_ids, num_itemss, payments,  order_times, titles, comments_order);
 
-    let (_t, customers) = create_customer_onwed_vector(size, keys, ages, num_purchases, total_purchases, duration_spents, duration_sinces, 
+    let (_t, mut customers) = create_customer_onwed_vector(size, keys, ages, num_purchases, total_purchases, duration_spents, duration_sinces, 
[…]

### 2020-02-28 project/playground/src/objects/sort.rs

@@ -1,10 +1,306 @@
 use std::thread;
 pub use std::sync::{mpsc, Mutex, Arc};
 use std::cell::RefCell;
+use std::rc::Rc;
 pub use crossbeam::atomic::AtomicCell;
 use crate::objects::customer::*;
+use std::cmp::Ordering;
+use std::marker::{Send, Sync};
+use std::mem;
+use std::collections::{LinkedList, VecDeque};
 
 const MAX_THREADS: usize = 4;
+
+
+
+pub fn mergesort_vecdeque<T: 'static>(mut arr:Vec<Arc<T>>, left: usize, right: usize) -> Vec<Arc<T>> 
+    where T: Clone + Customer + PartialOrd + Send + Sync
+{
+    let l = arr.len();
+    return merge_helper_vecdeque(Arc::new(arr), 0, l, 0);
+}
+
+
+fn merge_helper_vecdeque<T: 'static>(arr: Arc<Vec<Arc<T>>>, left: usize, right: usize, depth: usize) -> Vec<Arc<T>>  
+    where T: Clone + Customer + PartialOrd + Send + Sync
+{
+    if right - left > 1 {
+        let mid = (left + right) / 2;
+        let new_depth = depth + 1;
+        let arr_cloned1 = Arc::clone(&arr);
+        let arr_cloned2 = Arc::clone(&arr);
+        let mut arr_right;
+        let mut arr_left;
+
+        if new_depth < MAX_THREADS {
+            let (sender, receiver) = mpsc::channel();
+            let _ = thread::spawn(move || {
+                let sorted = merge_helper_vecdeque(arr_cloned1, left, mid, new_depth);
+                sender.send(sorted).unwrap();
+            });
+            arr_right = merge_helper_vecdeque(arr_cloned2, mid, right, new_depth);
+            arr_left = receiver.recv().unwrap();
+        } else {
+            arr_left = merge_helper_vecdeque(arr_cloned1, left, mid, new_depth);
+            arr_right = merge_helper_vecdeque(arr_cloned2, mid, right, new_depth);
+        }
+        return merge_vecdeque(arr_left, arr_right);
+    }
+    return merge_vecdeque_base(arr, left);
+}
+
+fn merge_vecdeque<T: 'static>(arr_left: Vec<Arc<T>>, arr_right: Vec<Arc<T>>) -> Vec<Arc<T>> 
+    where T: Clone + Customer + PartialOrd + Send + Sync
+{
[…]

### 2020-02-28 project/practice/src/main.rs

@@ -1,0 +1,157 @@
+use std::thread;
+use std::mem;
+use std::sync::{mpsc, Arc};
+use std::collections::{LinkedList, VecDeque};
+use std::cell::RefCell;
+use rand::{Rng,SeedableRng};
+use rand::rngs::StdRng;
+use std::env;
+use rand::distributions::{Uniform, Distribution};
+use crossbeam;
+const MAX_THREADS: usize = 4;
+fn main() {
+    let args: Vec<String> = env::args().collect();
+    let size: usize = args[1].parse().unwrap();
+    let mut nums = get_integer_vector(size);
+    println!("Initial: {:?}", nums);
+    let res = mergesort_vecdeque(nums, 0, size);
+    println!("Sorted: {:?}", res);
+}
+
+pub fn mergesort_vecdeque(arr: Vec<i32>, left: usize, right: usize) -> Vec<i32>{
+    let mut res = Vec::with_capacity(right);
+    merge_helper_vecdeque(&mut arr[..], left, right, 0, &mut res[..]);
+    return res
+}
+
+
+fn merge_helper_vecdeque(arr: &mut [i32], left: usize, right: usize, depth: usize, res: &mut [i32]) {
+    if right - left > 1 {
+        let mid = (left + right) / 2;
+        let new_depth = depth + 1;
+        let n = arr.len();
+        let res_left = Vec::with_capacity(n);
+        let res_right = Vec::with_capacity(n);
+        let (arr_right, arr_left) = arr.split_at_mut(mid);
+        if new_depth < MAX_THREADS {
+            crossbeam::scope(|scope| {
+                let arr_left_ptr = &mut arr_left[..];
+                let arr_right_ptr = &mut arr_right[..];
+                let ref_left = &mut res_left[..];
+                let ref_right = &mut res_right[..];
+                scope.spawn(move |_| {
+                    merge_helper_vecdeque(arr_left_ptr, left, mid, new_depth, ref_left);
+                });
+                scope.spawn(move |_| {
+                    merge_helper_vecdeque(arr_right_ptr, mid, right, new_depth, ref_right);
+                })
+            });
+        } else {
+            merge_helper_vecdeque(&mut arr_left[..], left, mid, new_depth, &mut res_left[..]);
+            merge_helper_vecdeque(&mut arr_right[..], mid, right, new_depth, &mut res_right[..]);
+        }
+        merge_vecdeque(&mut res_left[..], &mut res_right[..], &mut res[..]);
+    } else if right - left == 1 {
[…]

### 2020-02-28 project/rust_merge_sort/src/main.rs

@@ -1,0 +1,80 @@
+
+extern crate rand;
+extern crate serde;
+extern crate bytes;
+use std::env;
+use std::sync::Arc;
+mod objects;
+use objects::customer::{create_customer_onwed_vector, create_customer_borrowed_vector};
+use objects::order::{get_order_owned_vector, get_order_borrowed_vector};
+use objects::field::{get_float_vector, get_integer_vector, get_string_vector};
+//use objects::dropping::*;
+//use objects::access::*;
+use objects::sort::*;
+
+
+fn main() {
+    let args: Vec<String> = env::args().collect();
+    let size: usize = args[1].parse().unwrap();
+    let nums1 = get_integer_vector(size);
+    println!("Initial: {:?}", nums1);
+
+    let nums2 = get_integer_vector(size);
+    let n2 = nums2.len();
+    let merged = mergesort_mt_mp(nums2, 0, n2);
+    println!("Sort with MT{:?}", merged);
+
+    let nums3 = get_integer_vector(size);
+    let n3 = nums3.len();
+    let num3_atomic = Arc::new(Mutex::new(nums3));
+    mergesort_mt_mutex(Arc::clone(&num3_atomic), 0, n3);
+    println!("Sort with Mutex{:?}", num3_atomic);
+
+    let nums4 = get_integer_vector(size);
+    let n4 = nums4.len();
+    let num4_atomic = Arc::new(nums4);
+    let merged2 = mergesort_mt_im(Arc::clone(&num4_atomic), 0, n4);
+    println!("Sort with Immutable{:?}", merged2);
+    
+    let nums5 = get_integer_vector(size);
+    let n5= nums5.len();
+    //let num5_atomic = Arc::new(nums5);
+    let merged5 = mergesort_mt_mp_improve(nums5, 0, n5);
+    println!("Sort with Improve{:?}", merged5);
+
+    let keys = get_integer_vector(size);
+    let ages = get_integer_vector(size);
+    let num_purchases = get_integer_vector(size);
+    let total_purchases = get_float_vector(size);
+    let duration_spents = get_float_vector(size);
+    let duration_sinces = get_float_vector(size);
+    let zip_codes = get_string_vector(size);
+    let addresses = get_string_vector(size);
+    let countries = get_string_vector(size);
+    let states = get_string_vector(size);
+    let first_names = get_string_vector(size);
+    let last_names = get_string_vector(size);
+    let provinces = get_string_vector(size);
[…]

### 2020-02-28 project/rust_merge_sort/src/objects/customer.rs

@@ -1,12 +1,10 @@
-use crate::objects::order::{OrderOwned, OrderBorrowed, OrderRc, OrderArc};
+use crate::objects::order::{OrderOwned, OrderBorrowed, OrderRc};
 use std::rc::Rc;
 use std::time::Instant;
 use std::cmp::Ordering;
 use serde::ser::{Serialize, Serializer, SerializeStruct};
 use std::fmt;
 use std::marker::{Send, Sync};
-use std::sync::Arc;
-
 // Custorm trait (interface for all objects.)
 pub trait Customer {
     fn zip_code_bytes(&self) -> &[u8];
@@ -72,26 +70,6 @@ pub struct CustomerRc {
     province: Rc<String>,
     comment: Rc<String>, 
     order: Rc<OrderRc>
-}
-
-
-#[derive(Clone, Debug)]
-pub struct CustomerArc {
-    key: Arc<i32>,
-    age: Arc<i32>,
-    num_purchase: Arc<i32>,
-    total_purchase: Arc<f64>,
-    duration_spent: Arc<f64>, 
-    duration_since: Arc<f64>,
-    zip_code: Arc<String>,
-    address: Arc<String>,
-    country: Arc<String>,
-    state: Arc<String>,
-    first_name: Arc<String>,
-    last_name: Arc<String>,
-    province: Arc<String>,
-    comment: Arc<String>, 
-    order: Arc<OrderArc>
 }
 
 
@@ -170,32 +148,6 @@ impl CustomerRc {
     }
 }
 
-impl CustomerArc {
-    pub fn new(key: Arc<i32>, age: Arc<i32>, num_purchase: Arc<i32>, total_purchase: Arc<f64>, duration_spent: Arc<f64>, duration_since: Arc<f64>, 
-        zip_code: Arc<String>, address: Arc<String>, country: Arc<String>, state: Arc<String>, 
-        first_name: Arc<String>, last_name: Arc<String>, province: Arc<String>, comment: Arc<String>, order: Arc<OrderArc>) -> CustomerArc{
-        CustomerArc {
-            key: key, 
-            age: age,
-            num_purchase: num_purchase, 
-            total_purchase: total_purchase,
-            duration_spent: duration_spent,
-            duration_since: duration_since,
-            zip_code: zip_code,
-            address: address,
-            country: country,
-            state: state,
-            first_name: first_name, 
-            last_name: last_name, 
-            province: province,
-            comment: comment,
-            order: order
[…]

### 2020-02-28 project/rust_merge_sort/src/objects/mod.rs

@@ -4,4 +4,3 @@ pub mod field;
 //pub mod dropping;
 //pub mod access;
 pub mod sort;
-//pub mod linkedlist;

### 2020-02-28 project/rust_merge_sort/src/objects/order.rs

@@ -2,7 +2,7 @@ use std::rc::Rc;
 use serde::ser::{Serialize, Serializer, SerializeStruct};
 use std::cmp::Ordering;
 use std::marker::Send;
-use std::sync::Arc;
+
 
 #[derive(Clone, Debug)]
 pub struct OrderOwned {
@@ -32,15 +32,7 @@ pub struct OrderRc {
     title: Rc<String>,
     comment: Rc<String>
 }
-#[derive(Clone, Debug)]
-pub struct OrderArc {
-    order_id: Arc<i32>,
-    num_items: Arc<i32>, 
-    payment: Arc<f64>,
-    order_time: Arc<f64>,
-    title: Arc<String>,
-    comment: Arc<String>
-}
+
 impl OrderOwned {
     pub fn new(order_id: i32, num_items: i32, payment: f64, order_time: f64, title: String, comment: String) -> OrderOwned {
         OrderOwned {
@@ -70,20 +62,6 @@ impl OrderBorrowed<'_> {
 impl OrderRc {
     pub fn new(order_id: Rc<i32>, num_items: Rc<i32>, payment: Rc<f64>, order_time: Rc<f64>, title: Rc<String>, comment: Rc<String>) -> OrderRc {
         OrderRc {
-            order_id: order_id, 
-            num_items: num_items, 
-            payment: payment,
-            order_time: order_time,
-            title: title,
-            comment: comment
-        }
-    }
-}
-
-
-impl OrderArc {
-    pub fn new(order_id: Arc<i32>, num_items: Arc<i32>, payment: Arc<f64>, order_time: Arc<f64>, title: Arc<String>, comment: Arc<String>) -> OrderArc {
-        OrderArc {
             order_id: order_id, 
             num_items: num_items, 
             payment: payment,
@@ -154,28 +132,6 @@ impl PartialEq for OrderRc {
     }
 }
 
-
-impl Eq for OrderArc {}
-
-impl Ord for OrderArc {
-    fn cmp(&self, other: &Self) -> Ordering {
-        self.order_id.cmp(&other.order_id)
-    }
-}
-
-impl PartialOrd for OrderArc {
-    fn partial_cmp(&self, other: &Self) -> Option<Ordering> {
-        Some(self.cmp(other))
-    }
-}
-
-impl PartialEq for OrderArc {
-    fn eq(&self, other: &Self) -> bool {
-        self.order_id == other.order_id
-    }
-}
-
-
[…]

### 2020-02-28 project/rust_merge_sort/src/objects/sort.rs

@@ -1,0 +1,380 @@
+use std::thread;
+pub use std::sync::{mpsc, Mutex, Arc};
+use std::cell::RefCell;
+pub use crossbeam::atomic::AtomicCell;
+use crate::objects::customer::*;
+use std::cmp::Ordering;
+use std::marker::{Send, Sync};
+
+const MAX_THREADS: usize = 4;
+
+
+//////////////////////////////////////
+//////////////////////////////////////
+/////////////////////////////////////////
+///////////////////////////////////////// 
+pub fn mergesort_mt_mp_customer(arr:Vec<CustomerOwned>, left: usize, right: usize) -> Vec<CustomerOwned> {
+    return merge_mt_helper_mp_customer(arr, left, right, 0);
+}
+
+fn merge_mt_helper_mp_customer(arr: Vec<CustomerOwned>, left: usize, right: usize, depth: usize) -> Vec<CustomerOwned> {
+    if right - left > 1 {
+        let mid = (left + right) / 2;
+        let new_depth = depth + 1;
+        
+        let (mut arr_left, mut arr_right) = match arr.split_at(mid) {
+            (l, r) => (l.to_vec(), r.to_vec())
+        };
+        let arr_left_len = arr_left.len();
+        let arr_right_len = arr_right.len();
+
+        if new_depth < MAX_THREADS {
+            let (sender, receiver) = mpsc::channel();
+            let left_ptr = RefCell::new(arr_left);
+            let _ = thread::spawn(move || {
+                let left_sorted = merge_mt_helper_mp_customer(left_ptr.into_inner(), 0, arr_left_len, new_depth);
+                sender.send(left_sorted).unwrap();
+            });
+            arr_right = merge_mt_helper_mp_customer(arr_right, 0, arr_right_len, new_depth);
+            arr_left = receiver.recv().unwrap();
+        } else {
+            arr_left = merge_mt_helper_mp_customer(arr_left, 0, arr_left_len, new_depth);
+            arr_right = merge_mt_helper_mp_customer(arr_right, 0, arr_right_len, new_depth);
+        }
+        return merge_mt_mp_customer(arr_left, arr_right);
+    }
+    return arr;
+}
+
+
+fn merge_mt_mp_customer(mut arr_left: Vec<CustomerOwned>, mut arr_right: Vec<CustomerOwned>) -> Vec<CustomerOwned> {
+    let arr_left_len = arr_left.len();
[…]

### 2020-02-28 thesis_template/2_RelatedWork/relatedWork.tex
document resolved

@@
 In this experiment, four methods are used to insert elements into vector in Rust. One is clone method which performs bitwise deep copy. 
-Another is clone_from which also performs bitwise deep copy, but copies elements of the vector to distination vector rather than 
+Another is clone\_from which also performs bitwise deep copy, but copies elements of the vector to distination vector rather than 
 creating new one. We initialize the distination vector with the same size to the number of elements we insert into it. 
-Another is copy_nonoverlapping function which copies values from source to distination memory region. 
+Another is copy\_nonoverlapping function which copies values from source to distination memory region. 
 The other is pushing elements of source to distination vector one by one. Insertions of elements with 4 size are conducted 1000000, 1500000, 10000000, 15000000, and, 
@@
 The figure shows the result of the experiment. Among the runtime performances of integer insertion for every methods, 
-clone, clone_from, and copy_nonoverlapping method shows the similar performance. However, the pushing the copy of elements one by one has much slower runtime performance 
+clone, clone\_from, and copy\_nonoverlapping method shows the similar performance. However, the pushing the copy of elements one by one has much slower runtime performance 
 compared to the rest. This is because integer elements are allocated contiguously in the memory, so that accessing address of memory by pointer reads some next address. 
@@
 The first problem is about what kind of pointer to use to point to other nodes. 
-Since graph can be cyclic, so the ownership consept in Rust is violated if we use Box<Node>.
+Since graph can be cyclic, so the ownership consept in Rust is violated if we use Box$<$Node$>$.
 
@@
 \label{sec:history}
-Complex object of elements copy and insertion among vector is worth to experiment. This can be compared with Java, ¥
+Complex object of elements copy and insertion among vector is worth to experiment. This can be compared with Java,
 because memory layouts of struct in Rust and class in Java are different. Rust stores fieds in the contiguous memory region. 
@@
 Comparing operation on various smart pointer type. 
-Rc<T> enables value to have multiple owners, but the value should be immutable. Rc$<$T$>$ is used in case of single thread. 
+Rc$<$T$>$ enables value to have multiple owners, but the value should be immutable. Rc$<$T$>$ is used in case of single thread. 
 When the situation is multi-thread, Arc$<$T$>$ is used. Arc$<$T$>$ performs atomic operation, so it is more expensive than Rc$<$T$>$. 
@@
 Comparison between mutable and immutable tree or graph structure can be checked. 
-This is because tree structure requires Rc$<$T$>$ or Week$<$T$>$ and in addition RefCell<T> to make it mutable.
+This is because tree structure requires Rc$<$T$>$ or Week$<$T$>$ and in addition RefCell$<$T$>$ to make it mutable.
 
@@
 Interier mutability
+\begin{itemize}
     \item Cell$<$T$>$: For only Copy type, it allows us to mutate variable, even if it is immutable. Howeever, it does not support sharing the variable so that it returns always copy of the value.
@@
 This is done by allowing to get mutable reference from immutable variable and push the error detacting time from compile time to runtime.
+\end{itemize}
 

### 2020-02-29 thesis_template/1_Intro/intro.tex
document resolved
completed experiment

@@
 
-Rust is a system language which give the similar performance and control of hardware to C++ or C and safety of runtime.
+Rust is a system language which gives the similar performance and control of hardware to C++ or C and safety of runtime.
 Unique memory management strategy of Rust, ownership and borrowing, and fearless concurrenry
-make the language one of the ideal candidate for development of Big Data tools.
+make the language one of the ideal candidate for development of Big Data tools. There are several existing Big Data tools developed with Rust. Inspired by these activity
 

### 2020-02-29 thesis_template/2_RelatedWork/relatedWork.tex
completed experiment

@@
 \label{sec:history}
-
-Each value in Rust has a variable called its owner. This owner has information about the value, such as location in memory, 
-length and capacity of the value. This owner can live on the scope associated with its life time. When the owner goes out of it’s scope, 
-the value will be dropped. When a value already assigned to a variable is assigned to another variable, if the value is allocated 
-on heap its information is copied to the new owner and drop the old owner disabling old variable. Similar thing happens when we pass variable to parameter of function. 
-After passing a variable to a parameter, all the information is copied to new owner through the parameter and old owner is no longer available. 
-The new owner can only live in the function and the object will be dropped. In this case, we have no longer access to the object after the function. 
-To avoid this, Rust has a concept called borrowing. We can set reference for the parameter of function and use the reference for operation within function and drop the reference, 
-but not the ownership.
+\input{2_RelatedWork/rust_memory_management}
 
@@
 
+\section{The existing Big Data tools}
+\label{sec:history}
+The existing Big Data tools are JVM based. JVM abstract hardware so that JVM can rarely achieve near-native speed. A garbage collector is a
+
 \section{Todos}

### 2020-02-29 project/playground/src/objects/sort.rs

@@ -54,27 +54,25 @@ fn merge_vecdeque<T: 'static>(arr_left: VecDeque<Arc<T>>, arr_right: VecDeque<Ar
 {
     let arr_left_len = arr_left.len();
     let arr_right_len = arr_right.len();
-    let mut left_q = VecDeque::from(arr_left);
-    let mut right_q = VecDeque::from(arr_right);
     let mut arr_merged = VecDeque::with_capacity(arr_left_len + arr_right_len);
 
-    while !left_q.is_empty() && !right_q.is_empty() {
-        if left_q.front().unwrap() < right_q.front().unwrap() {
-            arr_merged.push_back(left_q.pop_front().unwrap());
+    while !arr_left.is_empty() && !arr_right.is_empty() {
+        if arr_left.front().unwrap() < arr_right.front().unwrap() {
+            arr_merged.push_back(arr_left.pop_front().unwrap());
         } else {
-            arr_merged.push_back(right_q.pop_front().unwrap());
+            arr_merged.push_back(arr_right.pop_front().unwrap());
         }
     }
 
-    if !left_q.is_empty() {
-        arr_merged.append(&mut left_q);
+    if !arr_left.is_empty() {
+        arr_merged.append(&mut arr_left);
     }
 
-    if !right_q.is_empty() {
-        arr_merged.append(&mut right_q);
+    if !arr_right.is_empty() {
+        arr_merged.append(&mut arr_right);
     }
 
-    return Vec::from(arr_merged);
+    return arr_merged;
 }
 
 fn merge_vecdeque_base<T: 'static>(arr: Arc<Vec<Arc<T>>>, left: usize) -> Vec<Arc<T>> 

### 2020-02-29 project/practice/src/main.rs

@@ -14,31 +14,33 @@ fn main() {
     let size: usize = args[1].parse().unwrap();
     let mut nums = get_integer_vector(size);
     println!("Initial: {:?}", nums);
-    let res = mergesort_vecdeque(nums, 0, size);
+    let res = mergesort_vecdeque(nums, size);
     println!("Sorted: {:?}", res);
 }
 
-pub fn mergesort_vecdeque(mut arr: Vec<i32>, left: usize, right: usize) -> VecDeque<i32> {
-    let res = merge_helper_vecdeque(&mut arr[..], left, right, 0);
+pub fn mergesort_vecdeque(mut arr: Vec<i32>, len: usize) -> VecDeque<i32> {
+    let res = merge_helper_vecdeque(&mut arr[..], len, 0);
     return res;
 }
 
 
-fn merge_helper_vecdeque(arr: &mut [i32], left: usize, right: usize, depth: usize) -> VecDeque<i32> {
-    if right - left > 1 {
-        let mid = (left + right) / 2;
+fn merge_helper_vecdeque(arr: &mut [i32], len: usize ,depth: usize) -> VecDeque<i32> {
+    if len > 1 {
+        let mid = len / 2;
         let new_depth = depth + 1;
-        let (arr_right, arr_left) = arr.split_at_mut(mid);
+        let (arr_left, arr_right) = arr.split_at_mut(mid);
+        let len_left = arr_left.len();
+        let len_right = arr_right.len();
         let res_left: VecDeque<i32>;
         let res_right: VecDeque<i32>;
         if new_depth < MAX_THREADS {
             let (left_thread, right_thread) = crossbeam::scope(|scope| {
                 
                 let left_handler = scope.spawn(move |_| {
-                    merge_helper_vecdeque(arr_left, left, mid, new_depth)
+                    merge_helper_vecdeque(arr_left, len_left, new_depth)
                 });
                 let right_handler = scope.spawn(move |_| {
-                    merge_helper_vecdeque(arr_right, mid, right, new_depth)
+                    merge_helper_vecdeque(arr_right, len_right, new_depth)
                 });
                 
                 let l = left_handler.join().unwrap();
@@ -48,12 +50,12 @@ fn merge_helper_vecdeque(arr: &mut [i32], left: usize, right: usize, depth: usiz
             res_left = left_thread;
             res_right = right_thread;
         } else {
[…]

### 2020-03-02 thesis_template/2_RelatedWork/model/manual_memory_management.tex
documented

Programming languages, such as C and C++, perform memory management manuallu and explicitly. The functions, malloc() and free(), take roll for
memory allocation and deallocation in respectively. However, these method to manage memory may cause several problems and require developers 
attention to the problems with siginificant effort for debugging and testing. Here, we explain two of the most common problems regarding to memory management.

Dangling pointer or reference is apointer or reference pointing to object that no longer exists. The situation of dangling pointer happens 
because of deallocation of memory without modification of value of the pointer. 
If the memory region is reallocated for other object and the dangling pointer tries to aceess the original object, the unpredictable behavior may result.

Memory leak occurs when memory is acllocated and no longer referenced so that the object in the memory location cannot be reached and released.
This is result of dereferencing object with deallocation. Memory leak consumes more memory than necessary by making unreachable location.

Many solutions are established to address these problems. Garbage Collection (GC) is a sofisticated memory management storategy with sacrifice of computation resources 
to track the state of memory. Resource Acquisition is Initialisation (RAII) is a solution without significant overhead and with limitation of situation where is applicable.
Region-Based Memory Management is

Garbage Collection is automated - Reference Counting, Tracing, the cost of GC is propotional to number of objects (Vector and array is fastor than LinkedList in Java)
(Refer https://www.oracle.com/technetwork/java/javase/tech/memorymanagement-whitepaper-1-150020.pdf)
Resource Acquisition is Initialisation (RAII) (Refer https://www.stephanboyer.com/post/60/region-based-memory-management)
Region-Based Memory Management (Refer Region-Based Memory Management in Cyclone)
Rust, ownership and borrwing

### 2020-03-02 thesis_template/2_RelatedWork/model/memory_management_java.tex
documented

--- 2020-02-29 thesis_template/2_RelatedWork/relatedWork.tex
@@
-\chapter{Related Work}
-\label{chapter:relatedwork}
-\thispagestyle{myheadings}
+Memory Allocation
+Java memory management has concepts
 
-\graphicspath{{2_RelatedWork/Figures/}}
-
-\section{Memory Management in Rust}
-\label{sec:history}
-\input{2_RelatedWork/rust_memory_management}
-
-\section{Spark and RDD Catching}
-\label{sec:history}
-
-Spark is one of the most used big data computing framework. Spark uses Resilient Distributed Datasets (RDDs) which implement in-memory data structures 
-used to cache intermediate data across a set of nodes. This enables multiple rounds of computation on the same data, which is required for machine learning 
-and graph analytics iteratively process the data.
-
-In RDD caching, there are different stages of caching, such as MEMOR\_YONLY and DISK\_ONLY. 
-Currently, for very large data sets, we need to pay attention to garbage collection (GC) and OS page swapping overhead, 
-because these could degrades execution time significantly. Therefore, DISK\_ONLY RDD caching can be better configuration in this case. 
-However, writing and reading intermediate data among desk and memory could have bad effects for execution time, due to need of serialization and deserialization.
-
-\section{BLAS LAPACK}
-\label{sec:history}
-
-Basic Linear Algebra Subprograms (BLAS) are standard building blocks for basic vector and matrix operations. There are 3 levels of operation. The level 1 BLAS performs scalar, 
-vector and vector-vector operations, the level 2 BLAS performs matrix-vector operation, and the level 3 BLAS performs matrix-matrix operation.
-
-LAPACK is developed on BLAS and has advanced functionalities such as LU decomposition and Singular Value Decomposition (SVD). Dense and banded matrices are handled, but not general 
-sparse matrices. The initial motivation of development of LAPACK was to make the widely used EISPACK and LINPACK libraries run efficiently on shared-memory vector and parallel processors. 
-LINPACK and EISPACK are inefficient because their memory access patterns disregard the multi-layered memory hierarchies of the machines, thereby spending too much time moving data. 
-LAPACK addresses this problem by recognizing the algorithms to use block matrix operations, such as matrix multiplication, in the innermost loops.
-These block operations can be optimized for each architecture to account for the memory hierarchy,
-and so provide a portable way to achieve high efficiency on diverse modern machines. However, LAPACK requires that highly optimized block matrix operations be already implemented on each machine.
-
-ARPACK is also a collection of linear algebra subroutines which is designed to compute a few eigenvalues and corresponding eigenvectors from large scale matrix. 
-ARPACK is based upon an algorithmic variant of the Arnoldi process called the Implicitly Restarted Arnoldi Method (IRAM). 
-When the matrix is symmetric it reduces to a variant of the Lanczos process called the Implicitly Restarted Lanczos Method(IRLM).
-The Arnoldi process only interacts with the matrix via matrix-vector multiplies.
-Therefore, this method can be applied to distributed matrix operations required in big data analysis.
-
-The original BLAS and LAPACK are written in Fortran90. Linear algebra library used for Spark is netlib-java, which is a Java wrapper library for Netlib, C API of BLAS and LAPACK. 
-The reason why the developers addressed to use this package is that the BLAS and LAPACK are already bug free and implementing linear algebra library from scratch can usually buggy.
-
-However, the main advantage of use of BLAS and LAPACK is system optimized implementation. So if we implement original Fortran linear algebra library, it cannot perform as well as BLAS and LAPACK. 
-And the performance would not be such different from one of implementation in Java or Rust.  If we want to test only memory management between Rust and Java, 
-it can be enough implementation of linear algebra operation from  pure Java and Rust sacrificing the best performance taking advantage of system optimization.
-
-\section{Netlib-Java}
-\label{sec:history}
-
-Netlib-java is a Java wrapper of BLAS, LAPACK, and ARPACK. Netlib-java choose  implementation of linear algebra depending on installation of the libraries. 
-First, if we have installed machine optimised system libraries, such as Intel MKL and OpenBLAS, netlib-java will use these as the implementation to use. 
-Next, it try to load netlib references which netlib-java use CBLAS and LAPCKE interface to perform BLAS and LAPACK native call. 
-The last option is to use f2j which is intended to translate the BLAS and LAPACK libraries from their Fortran77 reference source code to Java class files, 
-instead of calling native libraries by using Java Native Interface (JNI).
-
-We can use JNI to call native libraries from Java. The JNI is a native programming interface which allows Java code that runs inside a Java Virtual Machine (VM) 
-to interoperate with applications and libraries written in other programming languages.
-
-\section{Create Java interface of CBLAS with JNI}
-\label{sec:history}
-\begin{enumerate}
-    \item Download BLAS and build using make file. In the figure2.1, the built file is libblas.a and the header file is blas.h.
-    \item Download CBLAS and build using make file (I am not sure whether we should build archive file or shared library).
-In figure, the build file would be libcblas.a or libcblas.dylib and header file is cblas.h.
-    \item Create java file which will be the Java interface of CBLAS.
-    \item Compile java file with -h header flag to create class file (CBLASJ.class) and header file (CBLASJ.h).
-\begin{lstlisting}[language=bash]
-    $ javac -h . CBLASJ.java
-\end{lstlisting}
-    \item Create C file (CBLASJ.c) which will bind Java interface and CBLAS library. And compile it with JNI to create object file (CBLASJ.o).
-\begin{lstlisting}[language=bash]
-    $ gcc -c -fPIC -I${JAVA_HOME}/include -I${JAVA_HOME}/include/darwin CBLASJ.c
-\end{lstlisting}
-    \item Compile shared library linking library (libcblas.a or libcblas.dylib) object file (CBLASJ.o).
-\begin{lstlisting}[language=bash]
-    $ gcc -o libcblas.dylib (or libcblas.a) CBLASJ.o 
-\end{lstlisting}
-\end{enumerate}
-
-\begin{figure}[htb]
-    \includegraphics[width=15cm]{cblas_with_jni.eps}
-    \caption{Integration of Native Methods }
-    \label{fig:Sampling}
-\end{figure}
-
-\section{Matrix Computation and Optimization in Apache Spark}
-\label{sec:history}
-
-Matrix operation is a fundamental part of machine learning. Apache Spark provides implementation for distributed and local matrix operation. 
-To translate single-node algorithms to run on a distributed cluster, Spark addresses separating matrix operations from vector operations and run matrix operations on the cluster, 
-while keeping vector operations local to the driver.
-
-Spark changes its behavior for matrix operations depending on the type of operations and shape of matrices.
-For example, Singular Value Decomposition (SVD) for a square matrix is performed in distributed cluster,
-but SVD for a tall and skinny matrix is on a driver node. This is because the matrix derived among the computation of SVD for tall and skinny matrix is usually small so that it can fit to single node.
-
-Spark uses ARPACK to solve square SVD.
-ARPACK is a collection of Fortran77 designed to solve eigenvalue problems.
-ARPACK is based upon an algorithmic variant of the Arnoldi process called the Implicitly Restarted Arnoldi Method (IRAM).
-When the matrix A is symmetric it reduces to a variant of the Lanczos process called the Implicitly Restarted Lanczos Method (IRLM). 
-ARPACK calculate matrix multiplication by performing matrix-vector multiplication.
-So we can distribute matrix-vector multiplies, and exploit the computational resources available in the entire cluster.
-The other method to distribute matrix operations is Spark TFOCS. Spark TFOCS supports several optimization methods.
-
-To allow full use of hardware-specific linear algebraic operations on single node, Spark uses the BLAS (Basic Linear Algebra Systems) interface with relevant libraries for CPU and GPU acceleration. 
-Native libraries can be used in Scala are ones with C BLAS interface or wrapper and called through the Java native interface implemented in Netlib-java library and wrapped by the Scala library called Breeze.
-Following is some of the implementation of BLAS.
-
-\begin{itemize}
-    \item f2jblas -  Java implementation of Fortran BLAS
-    \item OpenBLAS - open source CPU-optimized C implementation of BLAS
-    \item MKL - CPU-optimized C and Fortran implementation of BLAS by Intel
-\end{itemize}
-
-These have different implementation and they perform differently for the type of operation and matrices shape. 
-In Sark, OpenBlas is the default method of choice. BLAS interface is made specifically for dense linear algebra. 
-Then, there are few libraries that efficiently handle sparse matrix operations.
-
-\section{Memory Management of Java}
-\label{sec:history}
-
+Memory Deallocation
 Garbage Collection (GC) is a Java memory management method performed by JVM. 
@@
 \end{figure}
-
-\section{Memory Management of each Linear Algebra Library}
-\label{sec:history}
-
-The pure Java linear algebra library, such as La4j, EJML, and Apache Common Math, 
-use normal GC performed by JVM to manage memory. This is because the implementation of these libraries are in purely Java.
-
-Netlib-java, Jblas or other simple Java wrapper of BLAS, LAPACK, and ARPACK with Java Native Interface (JNI) use normal GC as well. 
-This is because the native code deals with Java array by obtaining a reference to it. After the operation, 
-the native method releases the reference to the Java array with or without returning new Java array or Java primitive type object.
-
-ND4J has two types of  its own memory management methods, GC to pointer of off-heap NDArray, and MemoryWorkspaces. 
-ND4J used off-heap memory to store NDArrats, to provide better performance while working with NDArrays from vative code such as BLAS and CUDA libraries. 
-Off-heap means that the memory is allocated outside of the Java heap so that it is not managed by the JVM’s GC. NDArray itself is not tracked by JVM, 
-but its pointer is. The Java heap stores pointer to NDArray on off-heap. When a pointer is dereferenced, this pointer can be a target of JVM’s GC and when it is collected, 
-the corresponding NDArray will be deallocated. When using MemoryWorkspaces, NDArray lives only within specific workspace scope. 
-When NDArray leaves the workspace scope, the memory is deallocated unless explicitly calling method to copy the NDArray out of the scope.
-
-\section{Experiment of Memory Allocation}
-\label{sec:history}
-This experiment is to test how static and dynamic memory allocation of Java and Rust behave. For the assessment, Element addition to ArrayList in the case of Java and Vector in the case of Rust 
-is emploied here.
-These data stractures are resizable and we have control to set initial size.
-There are two parameters; initial size of ArrayList or Vector and thier final size after additions of elements.
-We are interested in the impact to memory allocation by initial allocation and expantion to runtime.
-
-First, an ArrayList and an Vector are created with specified initial size.
-Then, in a loop, a element is added for each iteration until the size of the ArrayList or Vector get the specified final size.
-Each data structure has a different resizing strategy. When an ArrayList hits current limit of its size and expands the limit, it doubles the current size.  
-While Vector does not have specific strategy for its resizing, the expantions of size of both ArrayList and Vector might affect the digradation of runtime performance.
-
-To perform benchmarks, we use Java Microbenchamrk Hardness (JMH) for Java and Criterion for Rust. The benchmark time is calculated mean from several iterarions. 
-We warm up before the execution. The parameters are set in combination of initial size, 10, 100, 1000, and 10000 and final size, 9, 99, 999, 9999. 
-The results are shown in Figure 2-4 and 2-5.
-
-Discussions here are separated to two cases: when initial size is set bigger than final size and when final size is set bigger than initial size. 
-For ArrayList in Java, it shows performance significant degradation when the initial size is bigger than final size. When we create ArrayList with intial size of 1000 and add 99 elements 
-to the ArrayList, the the average execution time is 1125 ns. However, the average excution time when we create ArrayList with intial size of 100 and add 99 elements is 623 ns. 
-This degration is caused by the cost of initializing the large array.
-On the other hand, Rust Vector does not have significant cost for the initialization of size compared to the cost of addition of elements.
-In the case of Vector with initial size of 1000 and add 99 elements to the Vector, the average excution is 320 ns. In the case of the initial size of 100 and 99 elements additions, 
-the average excution is 279 ns. This is such small degradation compared to element addition in Vector.
-
-In ArrayList when the initial size is smaller than the final size, there can be degradation in performance. When its initial size and final size are set 100 and 999 respectively, 
-the average execution time is 10884 ns. However when its initial size and final size are set 1000 and 999 respectively, the average execution time is 4250 ns. 
-This result shows the degradation of in performance caused by the copy of existing elements into newly allocated array whose size is double of the last array.
-
-This characteristic can be seen in the case of Vector in Rust. Vector with initial size 100 and final size 999 performs the average excution time 3514 ns, 
-but one with initial size 1000 and final size 999 performs 2723 ns. When the Vector reachs its capacity, it allocates a larger buffer and copies the present elements to it.
-This cost results in the degradation of the average excution time.
-
-\begin{figure}[htb]
-    \includegraphics[width=15cm]{java_arraylist.eps}
-    \caption{Memory allocation of ArrayList in Java}
-    \label{fig:Sampling}
-\end{figure}
-
-\begin{figure}[htb]
-    \includegraphics[width=15cm]{rust_vector.eps}
-    \caption{Memory allocation of Vector in Rust}
-    \label{fig:Sampling}
-\end{figure}
-
-\section{Experiment of Memory Allocation for Different Element Type.}
-\label{sec:history}
-This experiment is to test how static and dynamic memory allocation of Java and Rust behave. For the assessment, Element addition to ArrayList in the case of Java and Vector in the case of Rust 
-is emploied here.
-These data stractures are resizable and we have control to set initial size.
-There are two parameters; initial size of ArrayList or Vector and thier final size after additions of elements.
-We are interested in the impact to runtime performance by initializing memory allocation and dynamicaly allocating memory space.
-
-First, an ArrayList and an Vector are created with specified initial size.
-Then, in a loop, a element is added for each iteration until the size of the ArrayList or Vector get the specified final size.
-Each data structure has a different resizing strategy. When an ArrayList hits current limit of its size and expands the limit, it doubles the current size.  
-While Vector does not have specific strategy for its resizing, the expantions of size of both ArrayList and Vector might affect the digradation of runtime performance.
-
-Second, four types of element are used for elements addition to each data structure: integer, array of charactors, string, and Customer object. 
-Assamption is that there would be different behavior between element additions of dynamically resizable and static size objects. 
-Customer object has three fields. These fields are total order, weight of order, and zip code whose types are integer (i32 in rust), double (f32 in rust), and string respectively.
-Figure 2-6 and 2-7 are representations of customer objects in Java and Rust.
-
-Figure 2-10, 2-11, 2-12, and 2-13 represent the result of the experiments. For both data structures, integer elements addition shows the fastest runtime among all object types. 
-This is because the compilers know each integer need 4 bytes to be stored in memory so that the space for memory that should be allocated is easily inspected. 
-For the same reason, the initialization of data structures whose elements are integers alaways improves runtim performance.
-
-The elements addition of strings and array of character behave similally among each languages.
-These two types of elements addition perform the similar speed and significantly slower than integer addition.
-Customer object addition is the slowest in Java. However, in Rust the addition of Customer object is the second fastest among all element typs.
-The impacts of initialization of Java ArrayList vary among elemet types. On the other hand, the initailization Rust Vector always improves runtime performance for any of 4 types of elements addition.
-
-\begin{figure}[htb]
-    \begin{lstlisting}
-        class Customer {
-            int totalOrder;
-            double weightOrder;
-            String zipCode;
-        }
-    \end{lstlisting}
-    \caption{Representation of Customer object in Java.}
-    \label{fig:Sampling}    
-\end{figure}
-
-\begin{figure}[htb]
-    \begin{lstlisting}
-        struct Customer {
-            total_order: i32,
-            weight_order: f32,
-            zip_code: String,
-        }
-    \end{lstlisting}
-    \caption{Representation of Customer object in Rust.}
-    \label{fig:Sampling}
-\end{figure}
-
-\begin{figure}[htb]
-    \includegraphics[width=15cm]{java_arraylist_log.eps}
-    \caption{Memory allocation of Java ArrayList}
-    \label{fig:Sampling}
-\end{figure}
-
-\begin{figure}[htb]
-    \includegraphics[width=15cm]{rust_vector_log.eps}
-    \caption{Memory allocation of Rust Vector}
-    \label{fig:Sampling}
-\end{figure}
-
-\begin{figure}[htb]
-    \includegraphics[width=15cm]{java_arraylist_difference.eps}
-    \caption{Difference of Memory allocation of Java ArrayList between Non-initialization and Initialization}
-    \label{fig:Sampling}
-\end{figure}
-
-\begin{figure}[htb]
-    \includegraphics[width=15cm]{rust_arraylist_difference.eps}
-    \caption{Difference of Memory allocation of Rust Vector between Non-initialization and Initialization}
-    \label{fig:Sampling}
-\end{figure}
-
-\section{Elements Copy and Insertion into Size-initialized Vector in Rust.}
-\label{sec:history}
-In this experiment, four methods are used to insert elements into vector in Rust. One is clone method which performs bitwise deep copy. 
-Another is clone\_from which also performs bitwise deep copy, but copies elements of the vector to distination vector rather than 
-creating new one. We initialize the distination vector with the same size to the number of elements we insert into it. 
-Another is copy\_nonoverlapping function which copies values from source to distination memory region. 
-The other is pushing elements of source to distination vector one by one. Insertions of elements with 4 size are conducted 1000000, 1500000, 10000000, 15000000, and, 
-their runtimes for each elements type, integer and String are measured.
-
-The figure shows the result of the experiment. Among the runtime performances of integer insertion for every methods, 
-clone, clone\_from, and copy\_nonoverlapping method shows the similar performance. However, the pushing the copy of elements one by one has much slower runtime performance 
-compared to the rest. This is because integer elements are allocated contiguously in the memory, so that accessing address of memory by pointer reads some next address. 
-This boosts the copy and insertion of elements.
-
-On the other hand, all of methods show the similar runtime performance in experiment for String object insertion. 
-This is because String object is not stored in contiguous memory region. The vector stores pointer to the object and 
-process need to access around different memory region again and again to deeply copy the object.
-
-\begin{figure}[htb]
-    \includegraphics[width=15cm]{rust_various_insertion.eps}
-    \caption{Runtime of elements copy from one vector and insertion to the other vector.}
-    \label{fig:Sampling}
-\end{figure}
-
-\section{Access time to elements in vector}
-\label{sec:history}
-In this experiment, whether mutability has impacts to operation on the object in terms of runtime performance. 
-According to the experiment, there is no difference on accessing to elements of mutable and immutable vector.
-
-\begin{figure}[htb]
-    \includegraphics[width=15cm]{rust_various_access.eps}
-    \caption{Runtime of elements copy from one vector and insertion to the other vector.}
-    \label{fig:Sampling}
-\end{figure}
-
-\section{Access time to onwned, borrowed, and sliced field of object}
-\label{sec:history}
-In this experiment, differences of access time to among owned, borrowed, and sliced are observed. 
-Each variable has slightly different use of memomry.
-
-\begin{figure}[htb]
-    \begin{lstlisting}
-        struct CustomerOwned {
-            key: i32,
-            age: i32,
-            num_purchase: i32,
-            total_purchase: f64,
-            duration_spent: f64, 
-            duration_since: f64,
-            zip_code: String,
-            address: String,
-            country: String,
-            state: String,
-            first_name: String,
-            last_name: String,
-            province: String,
-            comment: String, 
-            order: OrderOwned
-        }
-
-        struct CustomerBorrowed<'a> {
-            key: &'a i32,
-            age: &'a i32,
-            num_purchase: &'a i32,
-            total_purchase: &'a f64,
-            duration_spent: &'a f64, 
-            duration_since: &'a f64,
-            zip_code: &'a String,
-            address: &'a String,
-            country: &'a String,
-            state: &'a String,
-            first_name: &'a String,
-            last_name: &'a String,
-            province: &'a String,
-            comment: &'a String, 
-            order: &'a OrderBorrowed<'a>
-        }
-
-        struct CustomerSlice<'a> {
-            key: &'a i32,
-            age: &'a i32,
-            num_purchase: &'a i32,
-            total_purchase: &'a f64,
-            duration_spent: &'a f64, 
-            duration_since: &'a f64,
-            zip_code: &'a str,
-            address: &'a str,
-            country: &'a str, 
-            state: &'a str,
-            first_name: &'a str,
-            last_name: &'a str,
-            province: &'a str,
-            comment: &'a str,
-            order: &'a OrderSlice<'a>
-        }
-
-        struct CustomerRc {
-            key: Rc<i32>,
-            age: Rc<i32>,
-            num_purchase: Rc<i32>,
-            total_purchase: Rc<f64>,
-            duration_spent: Rc<f64>, 
-            duration_since: Rc<f64>,
-            zip_code: Rc<String>,
-            address: Rc<String>,
-            country: Rc<String>,
-            state: Rc<String>,
-            first_name: Rc<String>,
-            last_name: Rc<String>,
-            province: Rc<String>,
-            comment: Rc<String>, 
-            order: Rc<OrderRc>
-        }
-    \end{lstlisting}
-    \caption{Representation of Customer object in Rust.}
-    \label{fig:Sampling}
-\end{figure}
-
-\section{Accessment of different reference methods in Rust}
-\label{sec:history}
-The goal of this experiment is to assess efficiency of different reference strategies in Rust, borrowing and reference counting.
-
-By levaraging reference counting, a value can be shared like what borrowing plays the role in Rust programming. 
-The difference is that reference counting checks number of reference pointing to the actual data and makes sure the data is not deleted 
-until all the references are dereferenced. Using reference counting is sometimes preferable approach for developers, 
-we do not have care about lifetime which is usually troublesome when we use borrowing approach many times in our code. 
-However, the possible problem regarding to reference counting is the cost for tracking the number of references. 
-Having this assumption, this experiment will show difference of behavior among reference countinig and borrowing.
-
-In this experiment, CustomerBorrowed and CustomerRc in figure are used to see difference of dropping time among borrowing and reference counting. 
-In the CustomerRc and OrderRc struct, all fields take reference counting (Rc$<$T$>$). Similaly to the experiment in the last section, 
-vectors of CustomerRc and CustomerBorrowed are created and droped the elements one by one.
-
-The result shows significant difference of dropping time among the two objects; deletion of CustomerRc is much slower than CustomerBorrowed. 
-This is because reference counters which are feilds of CustomerRc have to check the number of reference pointing to the actual content and decide 
-deallocate the memory or not. However, memory management and lifetime strategy of borrowing is already determined at compile time.
-
-\section{Time to Drop Reference vs Reference Counting}
-\label{sec:history}
-In this experiment, an assessment is conducted to valify whether there is difference between behavior of borrowing and reference counting. 
-These two methods can be used in similar situation. Especially, when we want reference to an original variable and keep the original variable until all of references are dereferenced, 
-we can have reference with both storategies, borrowing and reference counting. One advantage of using reference counting is that we do not have to pay attention to lifetime.
-However, the assumption here is that use of reference counting might be computationally expenesive than borrowing, because reference counting has to track the number of reference pointing to the value.
-Considered this assumption, we assess difference of time for dropping reference using borrowing and reference counting strategies.
-
-Similally to the last section, we implement struct whose fields are borrowing reference and reference counting and measure the time to drop the struct.
-
-The result shows the time to drop borrowing reference is significatly faster than reference counting.
-This says that we should use borrwoing storategies whenever high performance computation is critical.
-
-\begin{figure}[htb]
-    \includegraphics[width=15cm]{rust_droptime_borring_rc.eps}
-    \caption{Runtime for Droping to fields of Customer Object}
-    \label{fig:Sampling}
-\end{figure}
-
-\section{Possible Graph Structure in Rust}
-\label{sec:history}
-In Rust, there are two essential problems to construct graph structure, lifetime and mutability.
-
-The first problem is about what kind of pointer to use to point to other nodes. 
-Since graph can be cyclic, so the ownership consept in Rust is violated if we use Box$<$Node$>$.
-
-All of graph structure are immutable at least at creation time. Because graph may have cyclic, 
-we can not create graph at one statement. Although edge of graph has to be mutable to create entire graph structure, 
-we might need multiple references to edges, which violates basic rule of Rust programming.
-
-One solution is to use raw pointers. This is the most flexible approach, but also the most dangerous. 
-By taking this way, we are ignoring all the benefits of Rust.
-
-\section{Experiment for Multithread}
-\label{sec:history}
-Experiment for multithreading in Rust is interesting, because there are many memory allocation and deallocation in each threads.
-This is because each thread offten need to form independent memory state to each other to perform computation concurrently safely.
-In addition, the multithreading strategy can be planned in different ways in Rust using different concurrent computation tools, 
-Mutex, Arc, spawn, channel, scope, and so on.
-
-Currently available plan
-\begin{itemize}
-    \item spawn, channel and sending data (currently deviding data, but we probably do not need to).
-    \item spawn, forkjoin and shared data.(shared data among child and parent).
-    \item scope, forkjoin and slice shared data.
-    \item Use linkedList instead of Vector (Each node can be sharable data structure). When we have complex object of elements in vector, we want to copy the pointer to the object.
-    \item Compare performace on LinkedList which is not contiguous allocation, but do not need additional memory allocation and Vec.
-\end{itemize}
-
-\section{Note for next}
-\label{sec:history}
-Complex object of elements copy and insertion among vector is worth to experiment. This can be compared with Java,
-because memory layouts of struct in Rust and class in Java are different. Rust stores fieds in the contiguous memory region. 
-However, Java stores field elements to different region.
-
-Complex object whose fields has reference elemenets insertion to vector can be evaluated. Operation to the fields can be little 
-more expensive because the pointer to the value of the field is not stored in contiguous memory region.
-
-Generic type and static type function can be compared.
-
-To optimise access to String elements of vector, smallstring can be improve the runtime performance. 
-This is because the smallstring optimization enables short length of string on stack as byte array. 
-This string type sets condition where it makes decition where the string is stored on heap or stack as array at certain length.
-
-Comparing operation on reference and owned variable is also interested to examine.
-
-Comparing operation on various smart pointer type. 
-Rc$<$T$>$ enables value to have multiple owners, but the value should be immutable. Rc$<$T$>$ is used in case of single thread. 
-When the situation is multi-thread, Arc$<$T$>$ is used. Arc$<$T$>$ performs atomic operation, so it is more expensive than Rc$<$T$>$. 
-When we need to mutate value of Rc$<$T$>$, RefCell$<$T$>$ can be useful. RefCell$<$T$>$ allow us to have mutiple mutable reference and immutable
-of reference mutable or immutable variable at the same time. When the mutability consistency is voilented, it terminates program during runtime. 
-That is why RefCell$<$T$>$ is expensive so that the state of mutable consistency should tracked. 
-As Cell$<$T$>$, the value is copied in and out of the Cell$<$T$>$ instead of getting refrence to it. 
-In addition, Mutex$<$T$>$ provides intetior mutability across multi-thread.
-
-Comparison between mutable and immutable tree or graph structure can be checked. 
-This is because tree structure requires Rc$<$T$>$ or Week$<$T$>$ and in addition RefCell$<$T$>$ to make it mutable.
-
-Design experiment for Trait object and Generic function. 
-We can have Trait object which is pointer to object which imprements its Trait and use the method of Trait object.
-This object has additional information other than just reference to tye original object. 
-This is because Rust needs the type information to dynamically calll the right method of Trait object depending on the type of 
-original object.
-On the other hand, we can have Generic function whose parameter types are Generic types corresponding to Trait. 
-When Rust compiles the code, it emits independent function corresponding to every types that implements the Trains specified in parameter.
-
-Vector of Trait object (need to put element into Box) vs Vector of concrete type.
-
-If we keep first created owner until the last phase, we can use borrowing to operate.
-If we delete first created owner during the operation, we should use Rc$<$T$>$.
-The question would be, we can use Rc$<$T$>$ every where?
-
-Multithread in Rust vs Java
-
-Smart pointer
-\begin{itemize}
-    \item Box$<$T$>$: Box pointer lets value allocated on heap rather than on the stack.
-    \item Rc$<$T$>$: Reference counted pointer lets variable take multiple immutable ownership.
-\end{itemize}
-
-Interier mutability
-\begin{itemize}
-    \item Cell$<$T$>$: For only Copy type, it allows us to mutate variable, even if it is immutable. Howeever, it does not support sharing the variable so that it returns always copy of the value.
-    \item RefCell$<$T$>$: This support sharing and interier immutability for all types.
-This is done by allowing to get mutable reference from immutable variable and push the error detacting time from compile time to runtime.
-\end{itemize}
-
-\section{LLVM}
-\label{sec:history}
-LLVM (Low Level Virtual Machine) is an umbrella project which contains components of compilation of programming language.
-Exsiting compilers have tightly coupled functionalities so that it is not possible to embed them into other applications.
-However, the abstract framework of LLVM decouples the functionalities into peaces and the peaces of functionalities can be reused.
-
-In structure of a compiler, there are three main components; flontend, optimizer, and backend. 
-In flontend, a develper designs the interface of source programming language in way where it can be optimized by optimizer. 
-Then, backend takes optimized code and produce the native machine code. LLVM has a component called LLVM Intermediate Representation (IR), 
-which places itself across frontend to optimizer. IR is designed to host mid-level analyses and transformations that you find in optimizer section of a compiler.
-High-level language has many common structures and functionalities, so most of all high-level program languages can be represented with IR. 
-Once source code is represented with IR, optimizer can easily find pattern and optimize it in faster time. 
-IR is useful in terms of flontend. This is because developer of language flontend need to know only how the IR works and use the framework to develop a language.
-
-\section{The existing Big Data tools}
-\label{sec:history}
-The existing Big Data tools are JVM based. JVM abstract hardware so that JVM can rarely achieve near-native speed. A garbage collector is a
-
-\section{Todos}
-\label{sec:history}
-\begin{itemize}
-    \item Redo the experiment with appropriate size
-    \item Document for reference counting(measure dropt time using criterion)
-    \item Design experiment for Graph
-    \item Design experiment for Multithread
-    \item Study about LLVM
-    \item Study about OS memory management
-\end{itemize}
-
-\section{Time Line}
-\label{sec:history}
-\begin{itemize}
-    \item End Feb: Finish Experiment for Multithread and Graph
-    \item Mid May: ML experiment
-    \item End May: Redo experiment with bench mark dataset.
-    \item Start April: Finish Writing for first revise.
-\end{itemize}

### 2020-03-02 thesis_template/2_RelatedWork/model/rust_memory_management.tex
documented

Each value in Rust has a variable called its owner. This owner has information about the value, such as location in memory, 
length and capacity of the value. This owner can live on the scope associated with its life time. When the owner goes out of it’s scope, 
the value will be dropped. When a value already assigned to a variable is assigned to another variable, if the value is allocated 
on heap its information is copied to the new owner and drop the old owner disabling old variable. Similar thing happens when we pass variable to parameter of function. 
After passing a variable to a parameter, all the information is copied to new owner through the parameter and old owner is no longer available. 
The new owner can only live in the function and the object will be dropped. In this case, we have no longer access to the object after the function. 
To avoid this, Rust has a concept called borrowing. We can set reference for the parameter of function and use the reference for operation within function and drop the reference, 
but not the ownership.

### 2020-03-02 thesis_template/2_RelatedWork/model/spark_memory_management.tex
documented

--- 2020-02-29 thesis_template/2_RelatedWork/relatedWork.tex
@@
-\chapter{Related Work}
-\label{chapter:relatedwork}
-\thispagestyle{myheadings}
-
-\graphicspath{{2_RelatedWork/Figures/}}
-
-\section{Memory Management in Rust}
-\label{sec:history}
-\input{2_RelatedWork/rust_memory_management}
-
-\section{Spark and RDD Catching}
-\label{sec:history}
-
 Spark is one of the most used big data computing framework. Spark uses Resilient Distributed Datasets (RDDs) which implement in-memory data structures 
@@
 However, writing and reading intermediate data among desk and memory could have bad effects for execution time, due to need of serialization and deserialization.
-
-\section{BLAS LAPACK}
-\label{sec:history}
-
-Basic Linear Algebra Subprograms (BLAS) are standard building blocks for basic vector and matrix operations. There are 3 levels of operation. The level 1 BLAS performs scalar, 
-vector and vector-vector operations, the level 2 BLAS performs matrix-vector operation, and the level 3 BLAS performs matrix-matrix operation.
-
-LAPACK is developed on BLAS and has advanced functionalities such as LU decomposition and Singular Value Decomposition (SVD). Dense and banded matrices are handled, but not general 
-sparse matrices. The initial motivation of development of LAPACK was to make the widely used EISPACK and LINPACK libraries run efficiently on shared-memory vector and parallel processors. 
-LINPACK and EISPACK are inefficient because their memory access patterns disregard the multi-layered memory hierarchies of the machines, thereby spending too much time moving data. 
-LAPACK addresses this problem by recognizing the algorithms to use block matrix operations, such as matrix multiplication, in the innermost loops.
-These block operations can be optimized for each architecture to account for the memory hierarchy,
-and so provide a portable way to achieve high efficiency on diverse modern machines. However, LAPACK requires that highly optimized block matrix operations be already implemented on each machine.
-
-ARPACK is also a collection of linear algebra subroutines which is designed to compute a few eigenvalues and corresponding eigenvectors from large scale matrix. 
-ARPACK is based upon an algorithmic variant of the Arnoldi process called the Implicitly Restarted Arnoldi Method (IRAM). 
-When the matrix is symmetric it reduces to a variant of the Lanczos process called the Implicitly Restarted Lanczos Method(IRLM).
-The Arnoldi process only interacts with the matrix via matrix-vector multiplies.
-Therefore, this method can be applied to distributed matrix operations required in big data analysis.
-
-The original BLAS and LAPACK are written in Fortran90. Linear algebra library used for Spark is netlib-java, which is a Java wrapper library for Netlib, C API of BLAS and LAPACK. 
-The reason why the developers addressed to use this package is that the BLAS and LAPACK are already bug free and implementing linear algebra library from scratch can usually buggy.
-
-However, the main advantage of use of BLAS and LAPACK is system optimized implementation. So if we implement original Fortran linear algebra library, it cannot perform as well as BLAS and LAPACK. 
-And the performance would not be such different from one of implementation in Java or Rust.  If we want to test only memory management between Rust and Java, 
-it can be enough implementation of linear algebra operation from  pure Java and Rust sacrificing the best performance taking advantage of system optimization.
-
-\section{Netlib-Java}
-\label{sec:history}
-
-Netlib-java is a Java wrapper of BLAS, LAPACK, and ARPACK. Netlib-java choose  implementation of linear algebra depending on installation of the libraries. 
-First, if we have installed machine optimised system libraries, such as Intel MKL and OpenBLAS, netlib-java will use these as the implementation to use. 
-Next, it try to load netlib references which netlib-java use CBLAS and LAPCKE interface to perform BLAS and LAPACK native call. 
-The last option is to use f2j which is intended to translate the BLAS and LAPACK libraries from their Fortran77 reference source code to Java class files, 
-instead of calling native libraries by using Java Native Interface (JNI).
-
-We can use JNI to call native libraries from Java. The JNI is a native programming interface which allows Java code that runs inside a Java Virtual Machine (VM) 
-to interoperate with applications and libraries written in other programming languages.
-
-\section{Create Java interface of CBLAS with JNI}
-\label{sec:history}
-\begin{enumerate}
-    \item Download BLAS and build using make file. In the figure2.1, the built file is libblas.a and the header file is blas.h.
-    \item Download CBLAS and build using make file (I am not sure whether we should build archive file or shared library).
-In figure, the build file would be libcblas.a or libcblas.dylib and header file is cblas.h.
-    \item Create java file which will be the Java interface of CBLAS.
-    \item Compile java file with -h header flag to create class file (CBLASJ.class) and header file (CBLASJ.h).
-\begin{lstlisting}[language=bash]
-    $ javac -h . CBLASJ.java
-\end{lstlisting}
-    \item Create C file (CBLASJ.c) which will bind Java interface and CBLAS library. And compile it with JNI to create object file (CBLASJ.o).
-\begin{lstlisting}[language=bash]
-    $ gcc -c -fPIC -I${JAVA_HOME}/include -I${JAVA_HOME}/include/darwin CBLASJ.c
-\end{lstlisting}
-    \item Compile shared library linking library (libcblas.a or libcblas.dylib) object file (CBLASJ.o).
-\begin{lstlisting}[language=bash]
-    $ gcc -o libcblas.dylib (or libcblas.a) CBLASJ.o 
-\end{lstlisting}
-\end{enumerate}
-
-\begin{figure}[htb]
-    \includegraphics[width=15cm]{cblas_with_jni.eps}
-    \caption{Integration of Native Methods }
-    \label{fig:Sampling}
-\end{figure}
-
-\section{Matrix Computation and Optimization in Apache Spark}
-\label{sec:history}
-
-Matrix operation is a fundamental part of machine learning. Apache Spark provides implementation for distributed and local matrix operation. 
-To translate single-node algorithms to run on a distributed cluster, Spark addresses separating matrix operations from vector operations and run matrix operations on the cluster, 
-while keeping vector operations local to the driver.
-
-Spark changes its behavior for matrix operations depending on the type of operations and shape of matrices.
-For example, Singular Value Decomposition (SVD) for a square matrix is performed in distributed cluster,
-but SVD for a tall and skinny matrix is on a driver node. This is because the matrix derived among the computation of SVD for tall and skinny matrix is usually small so that it can fit to single node.
-
-Spark uses ARPACK to solve square SVD.
-ARPACK is a collection of Fortran77 designed to solve eigenvalue problems.
-ARPACK is based upon an algorithmic variant of the Arnoldi process called the Implicitly Restarted Arnoldi Method (IRAM).
-When the matrix A is symmetric it reduces to a variant of the Lanczos process called the Implicitly Restarted Lanczos Method (IRLM). 
-ARPACK calculate matrix multiplication by performing matrix-vector multiplication.
-So we can distribute matrix-vector multiplies, and exploit the computational resources available in the entire cluster.
-The other method to distribute matrix operations is Spark TFOCS. Spark TFOCS supports several optimization methods.
-
-To allow full use of hardware-specific linear algebraic operations on single node, Spark uses the BLAS (Basic Linear Algebra Systems) interface with relevant libraries for CPU and GPU acceleration. 
-Native libraries can be used in Scala are ones with C BLAS interface or wrapper and called through the Java native interface implemented in Netlib-java library and wrapped by the Scala library called Breeze.
-Following is some of the implementation of BLAS.
-
-\begin{itemize}
-    \item f2jblas -  Java implementation of Fortran BLAS
-    \item OpenBLAS - open source CPU-optimized C implementation of BLAS
-    \item MKL - CPU-optimized C and Fortran implementation of BLAS by Intel
-\end{itemize}
-
-These have different implementation and they perform differently for the type of operation and matrices shape. 
-In Sark, OpenBlas is the default method of choice. BLAS interface is made specifically for dense linear algebra. 
-Then, there are few libraries that efficiently handle sparse matrix operations.
-
-\section{Memory Management of Java}
-\label{sec:history}
-
-Garbage Collection (GC) is a Java memory management method performed by JVM. 
-GC tracks the state of objects on Java heap and triggers removal of unreferenced objects from memory.
-
-The Java heap structure is shown in Figure. It can be separated into three main parts where store objects for each corresponding generation: 
-permanent generation, young generation, and old generation. The region for permanent generation stores metadata required by JVM to describe 
-class and method used in application which will be permanently lived on the region of memory.
-
-The young generation of Java heap contains new objects allocated and aged. When the young generation fills up, this triggers minor GC. 
-All of unreferenced objects will be removed from Java heap and remained objects will be aged and eventually promoted to the old generation.
-
-The old generation is used to store long survived objects. Typically, a threshold is set for young generation object and when the age is met, 
-the object will be moved to the old generation. Eventually, the old generation object also needs to be removed when the object is unreferenced. 
-This is called major GC. The process of generational GC is shown in Figure.
-
-\begin{figure}[htb]
-    \includegraphics[width=15cm]{java_heap.eps}
-    \caption{Java Heap Structure}
-    \label{fig:Sampling}
-\end{figure}
-
-\begin{figure}[htb]
-    \includegraphics[width=15cm]{java_gc.eps}
-    \caption{Java Garbage Collection}
-    \label{fig:Sampling}
-\end{figure}
-
-\section{Memory Management of each Linear Algebra Library}
-\label{sec:history}
-
-The pure Java linear algebra library, such as La4j, EJML, and Apache Common Math, 
-use normal GC performed by JVM to manage memory. This is because the implementation of these libraries are in purely Java.
-
-Netlib-java, Jblas or other simple Java wrapper of BLAS, LAPACK, and ARPACK with Java Native Interface (JNI) use normal GC as well. 
-This is because the native code deals with Java array by obtaining a reference to it. After the operation, 
-the native method releases the reference to the Java array with or without returning new Java array or Java primitive type object.
-
-ND4J has two types of  its own memory management methods, GC to pointer of off-heap NDArray, and MemoryWorkspaces. 
-ND4J used off-heap memory to store NDArrats, to provide better performance while working with NDArrays from vative code such as BLAS and CUDA libraries. 
-Off-heap means that the memory is allocated outside of the Java heap so that it is not managed by the JVM’s GC. NDArray itself is not tracked by JVM, 
-but its pointer is. The Java heap stores pointer to NDArray on off-heap. When a pointer is dereferenced, this pointer can be a target of JVM’s GC and when it is collected, 
-the corresponding NDArray will be deallocated. When using MemoryWorkspaces, NDArray lives only within specific workspace scope. 
-When NDArray leaves the workspace scope, the memory is deallocated unless explicitly calling method to copy the NDArray out of the scope.
-
-\section{Experiment of Memory Allocation}
-\label{sec:history}
-This experiment is to test how static and dynamic memory allocation of Java and Rust behave. For the assessment, Element addition to ArrayList in the case of Java and Vector in the case of Rust 
-is emploied here.
-These data stractures are resizable and we have control to set initial size.
-There are two parameters; initial size of ArrayList or Vector and thier final size after additions of elements.
-We are interested in the impact to memory allocation by initial allocation and expantion to runtime.
-
-First, an ArrayList and an Vector are created with specified initial size.
-Then, in a loop, a element is added for each iteration until the size of the ArrayList or Vector get the specified final size.
-Each data structure has a different resizing strategy. When an ArrayList hits current limit of its size and expands the limit, it doubles the current size.  
-While Vector does not have specific strategy for its resizing, the expantions of size of both ArrayList and Vector might affect the digradation of runtime performance.
-
-To perform benchmarks, we use Java Microbenchamrk Hardness (JMH) for Java and Criterion for Rust. The benchmark time is calculated mean from several iterarions. 
-We warm up before the execution. The parameters are set in combination of initial size, 10, 100, 1000, and 10000 and final size, 9, 99, 999, 9999. 
-The results are shown in Figure 2-4 and 2-5.
-
-Discussions here are separated to two cases: when initial size is set bigger than final size and when final size is set bigger than initial size. 
-For ArrayList in Java, it shows performance significant degradation when the initial size is bigger than final size. When we create ArrayList with intial size of 1000 and add 99 elements 
-to the ArrayList, the the average execution time is 1125 ns. However, the average excution time when we create ArrayList with intial size of 100 and add 99 elements is 623 ns. 
-This degration is caused by the cost of initializing the large array.
-On the other hand, Rust Vector does not have significant cost for the initialization of size compared to the cost of addition of elements.
-In the case of Vector with initial size of 1000 and add 99 elements to the Vector, the average excution is 320 ns. In the case of the initial size of 100 and 99 elements additions, 
-the average excution is 279 ns. This is such small degradation compared to element addition in Vector.
-
-In ArrayList when the initial size is smaller than the final size, there can be degradation in performance. When its initial size and final size are set 100 and 999 respectively, 
-the average execution time is 10884 ns. However when its initial size and final size are set 1000 and 999 respectively, the average execution time is 4250 ns. 
-This result shows the degradation of in performance caused by the copy of existing elements into newly allocated array whose size is double of the last array.
-
-This characteristic can be seen in the case of Vector in Rust. Vector with initial size 100 and final size 999 performs the average excution time 3514 ns, 
-but one with initial size 1000 and final size 999 performs 2723 ns. When the Vector reachs its capacity, it allocates a larger buffer and copies the present elements to it.
-This cost results in the degradation of the average excution time.
-
-\begin{figure}[htb]
-    \includegraphics[width=15cm]{java_arraylist.eps}
-    \caption{Memory allocation of ArrayList in Java}
-    \label{fig:Sampling}
-\end{figure}
-
-\begin{figure}[htb]
-    \includegraphics[width=15cm]{rust_vector.eps}
-    \caption{Memory allocation of Vector in Rust}
-    \label{fig:Sampling}
-\end{figure}
-
-\section{Experiment of Memory Allocation for Different Element Type.}
-\label{sec:history}
-This experiment is to test how static and dynamic memory allocation of Java and Rust behave. For the assessment, Element addition to ArrayList in the case of Java and Vector in the case of Rust 
-is emploied here.
-These data stractures are resizable and we have control to set initial size.
-There are two parameters; initial size of ArrayList or Vector and thier final size after additions of elements.
-We are interested in the impact to runtime performance by initializing memory allocation and dynamicaly allocating memory space.
-
-First, an ArrayList and an Vector are created with specified initial size.
-Then, in a loop, a element is added for each iteration until the size of the ArrayList or Vector get the specified final size.
-Each data structure has a different resizing strategy. When an ArrayList hits current limit of its size and expands the limit, it doubles the current size.  
-While Vector does not have specific strategy for its resizing, the expantions of size of both ArrayList and Vector might affect the digradation of runtime performance.
-
-Second, four types of element are used for elements addition to each data structure: integer, array of charactors, string, and Customer object. 
-Assamption is that there would be different behavior between element additions of dynamically resizable and static size objects. 
-Customer object has three fields. These fields are total order, weight of order, and zip code whose types are integer (i32 in rust), double (f32 in rust), and string respectively.
-Figure 2-6 and 2-7 are representations of customer objects in Java and Rust.
-
-Figure 2-10, 2-11, 2-12, and 2-13 represent the result of the experiments. For both data structures, integer elements addition shows the fastest runtime among all object types. 
-This is because the compilers know each integer need 4 bytes to be stored in memory so that the space for memory that should be allocated is easily inspected. 
-For the same reason, the initialization of data structures whose elements are integers alaways improves runtim performance.
-
-The elements addition of strings and array of character behave similally among each languages.
-These two types of elements addition perform the similar speed and significantly slower than integer addition.
-Customer object addition is the slowest in Java. However, in Rust the addition of Customer object is the second fastest among all element typs.
-The impacts of initialization of Java ArrayList vary among elemet types. On the other hand, the initailization Rust Vector always improves runtime performance for any of 4 types of elements addition.
-
-\begin{figure}[htb]
-    \begin{lstlisting}
-        class Customer {
-            int totalOrder;
-            double weightOrder;
-            String zipCode;
-        }
-    \end{lstlisting}
-    \caption{Representation of Customer object in Java.}
-    \label{fig:Sampling}    
-\end{figure}
-
-\begin{figure}[htb]
-    \begin{lstlisting}
-        struct Customer {
-            total_order: i32,
-            weight_order: f32,
-            zip_code: String,
-        }
-    \end{lstlisting}
-    \caption{Representation of Customer object in Rust.}
-    \label{fig:Sampling}
-\end{figure}
-
-\begin{figure}[htb]
-    \includegraphics[width=15cm]{java_arraylist_log.eps}
-    \caption{Memory allocation of Java ArrayList}
-    \label{fig:Sampling}
-\end{figure}
-
-\begin{figure}[htb]
-    \includegraphics[width=15cm]{rust_vector_log.eps}
-    \caption{Memory allocation of Rust Vector}
-    \label{fig:Sampling}
-\end{figure}
-
-\begin{figure}[htb]
-    \includegraphics[width=15cm]{java_arraylist_difference.eps}
-    \caption{Difference of Memory allocation of Java ArrayList between Non-initialization and Initialization}
-    \label{fig:Sampling}
-\end{figure}
-
-\begin{figure}[htb]
-    \includegraphics[width=15cm]{rust_arraylist_difference.eps}
-    \caption{Difference of Memory allocation of Rust Vector between Non-initialization and Initialization}
-    \label{fig:Sampling}
-\end{figure}
-
-\section{Elements Copy and Insertion into Size-initialized Vector in Rust.}
-\label{sec:history}
-In this experiment, four methods are used to insert elements into vector in Rust. One is clone method which performs bitwise deep copy. 
-Another is clone\_from which also performs bitwise deep copy, but copies elements of the vector to distination vector rather than 
-creating new one. We initialize the distination vector with the same size to the number of elements we insert into it. 
-Another is copy\_nonoverlapping function which copies values from source to distination memory region. 
-The other is pushing elements of source to distination vector one by one. Insertions of elements with 4 size are conducted 1000000, 1500000, 10000000, 15000000, and, 
-their runtimes for each elements type, integer and String are measured.
-
-The figure shows the result of the experiment. Among the runtime performances of integer insertion for every methods, 
-clone, clone\_from, and copy\_nonoverlapping method shows the similar performance. However, the pushing the copy of elements one by one has much slower runtime performance 
-compared to the rest. This is because integer elements are allocated contiguously in the memory, so that accessing address of memory by pointer reads some next address. 
-This boosts the copy and insertion of elements.
-
-On the other hand, all of methods show the similar runtime performance in experiment for String object insertion. 
-This is because String object is not stored in contiguous memory region. The vector stores pointer to the object and 
-process need to access around different memory region again and again to deeply copy the object.
-
-\begin{figure}[htb]
-    \includegraphics[width=15cm]{rust_various_insertion.eps}
-    \caption{Runtime of elements copy from one vector and insertion to the other vector.}
-    \label{fig:Sampling}
-\end{figure}
-
-\section{Access time to elements in vector}
-\label{sec:history}
-In this experiment, whether mutability has impacts to operation on the object in terms of runtime performance. 
-According to the experiment, there is no difference on accessing to elements of mutable and immutable vector.
-
-\begin{figure}[htb]
-    \includegraphics[width=15cm]{rust_various_access.eps}
-    \caption{Runtime of elements copy from one vector and insertion to the other vector.}
-    \label{fig:Sampling}
-\end{figure}
-
-\section{Access time to onwned, borrowed, and sliced field of object}
-\label{sec:history}
-In this experiment, differences of access time to among owned, borrowed, and sliced are observed. 
-Each variable has slightly different use of memomry.
-
-\begin{figure}[htb]
-    \begin{lstlisting}
-        struct CustomerOwned {
-            key: i32,
-            age: i32,
-            num_purchase: i32,
-            total_purchase: f64,
-            duration_spent: f64, 
-            duration_since: f64,
-            zip_code: String,
-            address: String,
-            country: String,
-            state: String,
-            first_name: String,
-            last_name: String,
-            province: String,
-            comment: String, 
-            order: OrderOwned
-        }
-
-        struct CustomerBorrowed<'a> {
-            key: &'a i32,
-            age: &'a i32,
-            num_purchase: &'a i32,
-            total_purchase: &'a f64,
-            duration_spent: &'a f64, 
-            duration_since: &'a f64,
-            zip_code: &'a String,
-            address: &'a String,
-            country: &'a String,
-            state: &'a String,
-            first_name: &'a String,
-            last_name: &'a String,
-            province: &'a String,
-            comment: &'a String, 
-            order: &'a OrderBorrowed<'a>
-        }
-
-        struct CustomerSlice<'a> {
-            key: &'a i32,
-            age: &'a i32,
-            num_purchase: &'a i32,
-            total_purchase: &'a f64,
-            duration_spent: &'a f64, 
-            duration_since: &'a f64,
-            zip_code: &'a str,
-            address: &'a str,
-            country: &'a str, 
-            state: &'a str,
-            first_name: &'a str,
-            last_name: &'a str,
-            province: &'a str,
-            comment: &'a str,
-            order: &'a OrderSlice<'a>
-        }
-
-        struct CustomerRc {
-            key: Rc<i32>,
-            age: Rc<i32>,
-            num_purchase: Rc<i32>,
-            total_purchase: Rc<f64>,
-            duration_spent: Rc<f64>, 
-            duration_since: Rc<f64>,
-            zip_code: Rc<String>,
-            address: Rc<String>,
-            country: Rc<String>,
-            state: Rc<String>,
-            first_name: Rc<String>,
-            last_name: Rc<String>,
-            province: Rc<String>,
-            comment: Rc<String>, 
-            order: Rc<OrderRc>
-        }
-    \end{lstlisting}
-    \caption{Representation of Customer object in Rust.}
-    \label{fig:Sampling}
-\end{figure}
-
-\section{Accessment of different reference methods in Rust}
-\label{sec:history}
-The goal of this experiment is to assess efficiency of different reference strategies in Rust, borrowing and reference counting.
-
-By levaraging reference counting, a value can be shared like what borrowing plays the role in Rust programming. 
-The difference is that reference counting checks number of reference pointing to the actual data and makes sure the data is not deleted 
-until all the references are dereferenced. Using reference counting is sometimes preferable approach for developers, 
-we do not have care about lifetime which is usually troublesome when we use borrowing approach many times in our code. 
-However, the possible problem regarding to reference counting is the cost for tracking the number of references. 
-Having this assumption, this experiment will show difference of behavior among reference countinig and borrowing.
-
-In this experiment, CustomerBorrowed and CustomerRc in figure are used to see difference of dropping time among borrowing and reference counting. 
-In the CustomerRc and OrderRc struct, all fields take reference counting (Rc$<$T$>$). Similaly to the experiment in the last section, 
-vectors of CustomerRc and CustomerBorrowed are created and droped the elements one by one.
-
-The result shows significant difference of dropping time among the two objects; deletion of CustomerRc is much slower than CustomerBorrowed. 
-This is because reference counters which are feilds of CustomerRc have to check the number of reference pointing to the actual content and decide 
-deallocate the memory or not. However, memory management and lifetime strategy of borrowing is already determined at compile time.
-
-\section{Time to Drop Reference vs Reference Counting}
-\label{sec:history}
-In this experiment, an assessment is conducted to valify whether there is difference between behavior of borrowing and reference counting. 
-These two methods can be used in similar situation. Especially, when we want reference to an original variable and keep the original variable until all of references are dereferenced, 
-we can have reference with both storategies, borrowing and reference counting. One advantage of using reference counting is that we do not have to pay attention to lifetime.
-However, the assumption here is that use of reference counting might be computationally expenesive than borrowing, because reference counting has to track the number of reference pointing to the value.
-Considered this assumption, we assess difference of time for dropping reference using borrowing and reference counting strategies.
-
-Similally to the last section, we implement struct whose fields are borrowing reference and reference counting and measure the time to drop the struct.
-
-The result shows the time to drop borrowing reference is significatly faster than reference counting.
-This says that we should use borrwoing storategies whenever high performance computation is critical.
-
-\begin{figure}[htb]
-    \includegraphics[width=15cm]{rust_droptime_borring_rc.eps}
-    \caption{Runtime for Droping to fields of Customer Object}
-    \label{fig:Sampling}
-\end{figure}
-
-\section{Possible Graph Structure in Rust}
-\label{sec:history}
-In Rust, there are two essential problems to construct graph structure, lifetime and mutability.
-
-The first problem is about what kind of pointer to use to point to other nodes. 
-Since graph can be cyclic, so the ownership consept in Rust is violated if we use Box$<$Node$>$.
-
-All of graph structure are immutable at least at creation time. Because graph may have cyclic, 
-we can not create graph at one statement. Although edge of graph has to be mutable to create entire graph structure, 
-we might need multiple references to edges, which violates basic rule of Rust programming.
-
-One solution is to use raw pointers. This is the most flexible approach, but also the most dangerous. 
-By taking this way, we are ignoring all the benefits of Rust.
-
-\section{Experiment for Multithread}
-\label{sec:history}
-Experiment for multithreading in Rust is interesting, because there are many memory allocation and deallocation in each threads.
-This is because each thread offten need to form independent memory state to each other to perform computation concurrently safely.
-In addition, the multithreading strategy can be planned in different ways in Rust using different concurrent computation tools, 
-Mutex, Arc, spawn, channel, scope, and so on.
-
-Currently available plan
-\begin{itemize}
-    \item spawn, channel and sending data (currently deviding data, but we probably do not need to).
-    \item spawn, forkjoin and shared data.(shared data among child and parent).
-    \item scope, forkjoin and slice shared data.
-    \item Use linkedList instead of Vector (Each node can be sharable data structure). When we have complex object of elements in vector, we want to copy the pointer to the object.
-    \item Compare performace on LinkedList which is not contiguous allocation, but do not need additional memory allocation and Vec.
-\end{itemize}
-
-\section{Note for next}
-\label{sec:history}
-Complex object of elements copy and insertion among vector is worth to experiment. This can be compared with Java,
-because memory layouts of struct in Rust and class in Java are different. Rust stores fieds in the contiguous memory region. 
-However, Java stores field elements to different region.
-
-Complex object whose fields has reference elemenets insertion to vector can be evaluated. Operation to the fields can be little 
-more expensive because the pointer to the value of the field is not stored in contiguous memory region.
-
-Generic type and static type function can be compared.
-
-To optimise access to String elements of vector, smallstring can be improve the runtime performance. 
-This is because the smallstring optimization enables short length of string on stack as byte array. 
-This string type sets condition where it makes decition where the string is stored on heap or stack as array at certain length.
-
-Comparing operation on reference and owned variable is also interested to examine.
-
-Comparing operation on various smart pointer type. 
-Rc$<$T$>$ enables value to have multiple owners, but the value should be immutable. Rc$<$T$>$ is used in case of single thread. 
-When the situation is multi-thread, Arc$<$T$>$ is used. Arc$<$T$>$ performs atomic operation, so it is more expensive than Rc$<$T$>$. 
-When we need to mutate value of Rc$<$T$>$, RefCell$<$T$>$ can be useful. RefCell$<$T$>$ allow us to have mutiple mutable reference and immutable
-of reference mutable or immutable variable at the same time. When the mutability consistency is voilented, it terminates program during runtime. 
-That is why RefCell$<$T$>$ is expensive so that the state of mutable consistency should tracked. 
-As Cell$<$T$>$, the value is copied in and out of the Cell$<$T$>$ instead of getting refrence to it. 
-In addition, Mutex$<$T$>$ provides intetior mutability across multi-thread.
-
-Comparison between mutable and immutable tree or graph structure can be checked. 
-This is because tree structure requires Rc$<$T$>$ or Week$<$T$>$ and in addition RefCell$<$T$>$ to make it mutable.
-
-Design experiment for Trait object and Generic function. 
-We can have Trait object which is pointer to object which imprements its Trait and use the method of Trait object.
-This object has additional information other than just reference to tye original object. 
-This is because Rust needs the type information to dynamically calll the right method of Trait object depending on the type of 
-original object.
-On the other hand, we can have Generic function whose parameter types are Generic types corresponding to Trait. 
-When Rust compiles the code, it emits independent function corresponding to every types that implements the Trains specified in parameter.
-
-Vector of Trait object (need to put element into Box) vs Vector of concrete type.
-
-If we keep first created owner until the last phase, we can use borrowing to operate.
-If we delete first created owner during the operation, we should use Rc$<$T$>$.
-The question would be, we can use Rc$<$T$>$ every where?
-
-Multithread in Rust vs Java
-
-Smart pointer
-\begin{itemize}
-    \item Box$<$T$>$: Box pointer lets value allocated on heap rather than on the stack.
-    \item Rc$<$T$>$: Reference counted pointer lets variable take multiple immutable ownership.
-\end{itemize}
-
-Interier mutability
-\begin{itemize}
-    \item Cell$<$T$>$: For only Copy type, it allows us to mutate variable, even if it is immutable. Howeever, it does not support sharing the variable so that it returns always copy of the value.
-    \item RefCell$<$T$>$: This support sharing and interier immutability for all types.
-This is done by allowing to get mutable reference from immutable variable and push the error detacting time from compile time to runtime.
-\end{itemize}
-
-\section{LLVM}
-\label{sec:history}
-LLVM (Low Level Virtual Machine) is an umbrella project which contains components of compilation of programming language.
-Exsiting compilers have tightly coupled functionalities so that it is not possible to embed them into other applications.
-However, the abstract framework of LLVM decouples the functionalities into peaces and the peaces of functionalities can be reused.
-
-In structure of a compiler, there are three main components; flontend, optimizer, and backend. 
-In flontend, a develper designs the interface of source programming language in way where it can be optimized by optimizer. 
-Then, backend takes optimized code and produce the native machine code. LLVM has a component called LLVM Intermediate Representation (IR), 
-which places itself across frontend to optimizer. IR is designed to host mid-level analyses and transformations that you find in optimizer section of a compiler.
-High-level language has many common structures and functionalities, so most of all high-level program languages can be represented with IR. 
-Once source code is represented with IR, optimizer can easily find pattern and optimize it in faster time. 
-IR is useful in terms of flontend. This is because developer of language flontend need to know only how the IR works and use the framework to develop a language.
-
-\section{The existing Big Data tools}
-\label{sec:history}
-The existing Big Data tools are JVM based. JVM abstract hardware so that JVM can rarely achieve near-native speed. A garbage collector is a
-
-\section{Todos}
-\label{sec:history}
-\begin{itemize}
-    \item Redo the experiment with appropriate size
-    \item Document for reference counting(measure dropt time using criterion)
-    \item Design experiment for Graph
-    \item Design experiment for Multithread
-    \item Study about LLVM
-    \item Study about OS memory management
-\end{itemize}
-
-\section{Time Line}
-\label{sec:history}
-\begin{itemize}
-    \item End Feb: Finish Experiment for Multithread and Graph
-    \item Mid May: ML experiment
-    \item End May: Redo experiment with bench mark dataset.
-    \item Start April: Finish Writing for first revise.
-\end{itemize}

### 2020-03-02 thesis_template/2_RelatedWork/relatedWork.tex
documented

@@
 \label{sec:history}
-\input{2_RelatedWork/rust_memory_management}
+\input{2_RelatedWork/model/rust_memory_management}
 
@@
 \label{sec:history}
-
-Spark is one of the most used big data computing framework. Spark uses Resilient Distributed Datasets (RDDs) which implement in-memory data structures 
-used to cache intermediate data across a set of nodes. This enables multiple rounds of computation on the same data, which is required for machine learning 
-and graph analytics iteratively process the data.
-
-In RDD caching, there are different stages of caching, such as MEMOR\_YONLY and DISK\_ONLY. 
-Currently, for very large data sets, we need to pay attention to garbage collection (GC) and OS page swapping overhead, 
-because these could degrades execution time significantly. Therefore, DISK\_ONLY RDD caching can be better configuration in this case. 
-However, writing and reading intermediate data among desk and memory could have bad effects for execution time, due to need of serialization and deserialization.
-
-\section{BLAS LAPACK}
-\label{sec:history}
-
-Basic Linear Algebra Subprograms (BLAS) are standard building blocks for basic vector and matrix operations. There are 3 levels of operation. The level 1 BLAS performs scalar, 
-vector and vector-vector operations, the level 2 BLAS performs matrix-vector operation, and the level 3 BLAS performs matrix-matrix operation.
-
-LAPACK is developed on BLAS and has advanced functionalities such as LU decomposition and Singular Value Decomposition (SVD). Dense and banded matrices are handled, but not general 
-sparse matrices. The initial motivation of development of LAPACK was to make the widely used EISPACK and LINPACK libraries run efficiently on shared-memory vector and parallel processors. 
-LINPACK and EISPACK are inefficient because their memory access patterns disregard the multi-layered memory hierarchies of the machines, thereby spending too much time moving data. 
-LAPACK addresses this problem by recognizing the algorithms to use block matrix operations, such as matrix multiplication, in the innermost loops.
-These block operations can be optimized for each architecture to account for the memory hierarchy,
-and so provide a portable way to achieve high efficiency on diverse modern machines. However, LAPACK requires that highly optimized block matrix operations be already implemented on each machine.
-
-ARPACK is also a collection of linear algebra subroutines which is designed to compute a few eigenvalues and corresponding eigenvectors from large scale matrix. 
-ARPACK is based upon an algorithmic variant of the Arnoldi process called the Implicitly Restarted Arnoldi Method (IRAM). 
-When the matrix is symmetric it reduces to a variant of the Lanczos process called the Implicitly Restarted Lanczos Method(IRLM).
-The Arnoldi process only interacts with the matrix via matrix-vector multiplies.
-Therefore, this method can be applied to distributed matrix operations required in big data analysis.
-
-The original BLAS and LAPACK are written in Fortran90. Linear algebra library used for Spark is netlib-java, which is a Java wrapper library for Netlib, C API of BLAS and LAPACK. 
-The reason why the developers addressed to use this package is that the BLAS and LAPACK are already bug free and implementing linear algebra library from scratch can usually buggy.
-
-However, the main advantage of use of BLAS and LAPACK is system optimized implementation. So if we implement original Fortran linear algebra library, it cannot perform as well as BLAS and LAPACK. 
-And the performance would not be such different from one of implementation in Java or Rust.  If we want to test only memory management between Rust and Java, 
-it can be enough implementation of linear algebra operation from  pure Java and Rust sacrificing the best performance taking advantage of system optimization.
-
-\section{Netlib-Java}
-\label{sec:history}
-
-Netlib-java is a Java wrapper of BLAS, LAPACK, and ARPACK. Netlib-java choose  implementation of linear algebra depending on installation of the libraries. 
-First, if we have installed machine optimised system libraries, such as Intel MKL and OpenBLAS, netlib-java will use these as the implementation to use. 
-Next, it try to load netlib references which netlib-java use CBLAS and LAPCKE interface to perform BLAS and LAPACK native call. 
-The last option is to use f2j which is intended to translate the BLAS and LAPACK libraries from their Fortran77 reference source code to Java class files, 
-instead of calling native libraries by using Java Native Interface (JNI).
-
-We can use JNI to call native libraries from Java. The JNI is a native programming interface which allows Java code that runs inside a Java Virtual Machine (VM) 
-to interoperate with applications and libraries written in other programming languages.
-
-\section{Create Java interface of CBLAS with JNI}
-\label{sec:history}
-\begin{enumerate}
-    \item Download BLAS and build using make file. In the figure2.1, the built file is libblas.a and the header file is blas.h.
-    \item Download CBLAS and build using make file (I am not sure whether we should build archive file or shared library).
-In figure, the build file would be libcblas.a or libcblas.dylib and header file is cblas.h.
-    \item Create java file which will be the Java interface of CBLAS.
-    \item Compile java file with -h header flag to create class file (CBLASJ.class) and header file (CBLASJ.h).
-\begin{lstlisting}[language=bash]
-    $ javac -h . CBLASJ.java
-\end{lstlisting}
-    \item Create C file (CBLASJ.c) which will bind Java interface and CBLAS library. And compile it with JNI to create object file (CBLASJ.o).
-\begin{lstlisting}[language=bash]
-    $ gcc -c -fPIC -I${JAVA_HOME}/include -I${JAVA_HOME}/include/darwin CBLASJ.c
-\end{lstlisting}
-    \item Compile shared library linking library (libcblas.a or libcblas.dylib) object file (CBLASJ.o).
-\begin{lstlisting}[language=bash]
-    $ gcc -o libcblas.dylib (or libcblas.a) CBLASJ.o 
-\end{lstlisting}
-\end{enumerate}
-
-\begin{figure}[htb]
-    \includegraphics[width=15cm]{cblas_with_jni.eps}
-    \caption{Integration of Native Methods }
-    \label{fig:Sampling}
-\end{figure}
-
-\section{Matrix Computation and Optimization in Apache Spark}
-\label{sec:history}
-
-Matrix operation is a fundamental part of machine learning. Apache Spark provides implementation for distributed and local matrix operation. 
-To translate single-node algorithms to run on a distributed cluster, Spark addresses separating matrix operations from vector operations and run matrix operations on the cluster, 
-while keeping vector operations local to the driver.
-
-Spark changes its behavior for matrix operations depending on the type of operations and shape of matrices.
-For example, Singular Value Decomposition (SVD) for a square matrix is performed in distributed cluster,
-but SVD for a tall and skinny matrix is on a driver node. This is because the matrix derived among the computation of SVD for tall and skinny matrix is usually small so that it can fit to single node.
-
-Spark uses ARPACK to solve square SVD.
-ARPACK is a collection of Fortran77 designed to solve eigenvalue problems.
-ARPACK is based upon an algorithmic variant of the Arnoldi process called the Implicitly Restarted Arnoldi Method (IRAM).
-When the matrix A is symmetric it reduces to a variant of the Lanczos process called the Implicitly Restarted Lanczos Method (IRLM). 
-ARPACK calculate matrix multiplication by performing matrix-vector multiplication.
-So we can distribute matrix-vector multiplies, and exploit the computational resources available in the entire cluster.
-The other method to distribute matrix operations is Spark TFOCS. Spark TFOCS supports several optimization methods.
-
-To allow full use of hardware-specific linear algebraic operations on single node, Spark uses the BLAS (Basic Linear Algebra Systems) interface with relevant libraries for CPU and GPU acceleration. 
-Native libraries can be used in Scala are ones with C BLAS interface or wrapper and called through the Java native interface implemented in Netlib-java library and wrapped by the Scala library called Breeze.
-Following is some of the implementation of BLAS.
-
-\begin{itemize}
-    \item f2jblas -  Java implementation of Fortran BLAS
-    \item OpenBLAS - open source CPU-optimized C implementation of BLAS
-    \item MKL - CPU-optimized C and Fortran implementation of BLAS by Intel
-\end{itemize}
-
-These have different implementation and they perform differently for the type of operation and matrices shape. 
-In Sark, OpenBlas is the default method of choice. BLAS interface is made specifically for dense linear algebra. 
-Then, there are few libraries that efficiently handle sparse matrix operations.
+\input{2_RelatedWork/model/spark_memory_management}
 
@@
 \label{sec:history}
+\input{2_RelatedWork/model/memory_management_java}
 
-Garbage Collection (GC) is a Java memory management method performed by JVM. 
-GC tracks the state of objects on Java heap and triggers removal of unreferenced objects from memory.
+\section{Memory Management Problems of Java}
+\label{sec:history}
+\input{2_RelatedWork/model/manual_memory_management}
 
-The Java heap structure is shown in Figure. It can be separated into three main parts where store objects for each corresponding generation: 
-permanent generation, young generation, and old generation. The region for permanent generation stores metadata required by JVM to describe 
-class and method used in application which will be permanently lived on the region of memory.
-
-The young generation of Java heap contains new objects allocated and aged. When the young generation fills up, this triggers minor GC. 
-All of unreferenced objects will be removed from Java heap and remained objects will be aged and eventually promoted to the old generation.
-
-The old generation is used to store long survived objects. Typically, a threshold is set for young generation object and when the age is met, 
-the object will be moved to the old generation. Eventually, the old generation object also needs to be removed when the object is unreferenced. 
-This is called major GC. The process of generational GC is shown in Figure.
-
-\begin{figure}[htb]
-    \includegraphics[width=15cm]{java_heap.eps}
-    \caption{Java Heap Structure}
-    \label{fig:Sampling}
-\end{figure}
-
-\begin{figure}[htb]
-    \includegraphics[width=15cm]{java_gc.eps}
-    \caption{Java Garbage Collection}
-    \label{fig:Sampling}
-\end{figure}
-
-\section{Memory Management of each Linear Algebra Library}
+\section{Serialization}
 \label{sec:history}
-
-The pure Java linear algebra library, such as La4j, EJML, and Apache Common Math, 
-use normal GC performed by JVM to manage memory. This is because the implementation of these libraries are in purely Java.
-
-Netlib-java, Jblas or other simple Java wrapper of BLAS, LAPACK, and ARPACK with Java Native Interface (JNI) use normal GC as well. 
-This is because the native code deals with Java array by obtaining a reference to it. After the operation, 
-the native method releases the reference to the Java array with or without returning new Java array or Java primitive type object.
-
-ND4J has two types of  its own memory management methods, GC to pointer of off-heap NDArray, and MemoryWorkspaces. 
-ND4J used off-heap memory to store NDArrats, to provide better performance while working with NDArrays from vative code such as BLAS and CUDA libraries. 
-Off-heap means that the memory is allocated outside of the Java heap so that it is not managed by the JVM’s GC. NDArray itself is not tracked by JVM, 
-but its pointer is. The Java heap stores pointer to NDArray on off-heap. When a pointer is dereferenced, this pointer can be a target of JVM’s GC and when it is collected, 
-the corresponding NDArray will be deallocated. When using MemoryWorkspaces, NDArray lives only within specific workspace scope. 
-When NDArray leaves the workspace scope, the memory is deallocated unless explicitly calling method to copy the NDArray out of the scope.
+\input{2_RelatedWork/model/serialization}
 
@@
 \begin{itemize}
+    \item 
     \item Redo the experiment with appropriate size
+    \item Document for Memory Management of Java with Garbage Collection and the impact for Big Data tools
+    \item The safety of Region Based Maemory Management and advantage of using Rust.
+    \item Serialize problem 
     \item Document for reference counting(measure dropt time using criterion)
@@
     \item Study about LLVM
+\end{itemize}
+
+\section{Done}
+\label{sec:history}
+\begin{itemize}
     \item Study about OS memory management

### 2020-03-02 thesis_template/Appendix/Appendix.tex
mergesort
documented

@@
 \thispagestyle{myheadings}
+
+\graphicspath{{Appendix/Figures/}}
 
@@
 \label{sec:history}
+
+\section{BLAS LAPACK}
+\label{sec:history}
+
+Basic Linear Algebra Subprograms (BLAS) are standard building blocks for basic vector and matrix operations. There are 3 levels of operation. The level 1 BLAS performs scalar, 
+vector and vector-vector operations, the level 2 BLAS performs matrix-vector operation, and the level 3 BLAS performs matrix-matrix operation.
+
+LAPACK is developed on BLAS and has advanced functionalities such as LU decomposition and Singular Value Decomposition (SVD). Dense and banded matrices are handled, but not general 
+sparse matrices. The initial motivation of development of LAPACK was to make the widely used EISPACK and LINPACK libraries run efficiently on shared-memory vector and parallel processors. 
+LINPACK and EISPACK are inefficient because their memory access patterns disregard the multi-layered memory hierarchies of the machines, thereby spending too much time moving data. 
+LAPACK addresses this problem by recognizing the algorithms to use block matrix operations, such as matrix multiplication, in the innermost loops.
+These block operations can be optimized for each architecture to account for the memory hierarchy,
+and so provide a portable way to achieve high efficiency on diverse modern machines. However, LAPACK requires that highly optimized block matrix operations be already implemented on each machine.
+
+ARPACK is also a collection of linear algebra subroutines which is designed to compute a few eigenvalues and corresponding eigenvectors from large scale matrix. 
+ARPACK is based upon an algorithmic variant of the Arnoldi process called the Implicitly Restarted Arnoldi Method (IRAM). 
+When the matrix is symmetric it reduces to a variant of the Lanczos process called the Implicitly Restarted Lanczos Method(IRLM).
+The Arnoldi process only interacts with the matrix via matrix-vector multiplies.
+Therefore, this method can be applied to distributed matrix operations required in big data analysis.
+
+The original BLAS and LAPACK are written in Fortran90. Linear algebra library used for Spark is netlib-java, which is a Java wrapper library for Netlib, C API of BLAS and LAPACK. 
+The reason why the developers addressed to use this package is that the BLAS and LAPACK are already bug free and implementing linear algebra library from scratch can usually buggy.
+
+However, the main advantage of use of BLAS and LAPACK is system optimized implementation. So if we implement original Fortran linear algebra library, it cannot perform as well as BLAS and LAPACK. 
+And the performance would not be such different from one of implementation in Java or Rust.  If we want to test only memory management between Rust and Java, 
+it can be enough implementation of linear algebra operation from  pure Java and Rust sacrificing the best performance taking advantage of system optimization.
+
+\section{Netlib-Java}
+\label{sec:history}
+
+Netlib-java is a Java wrapper of BLAS, LAPACK, and ARPACK. Netlib-java choose  implementation of linear algebra depending on installation of the libraries. 
+First, if we have installed machine optimised system libraries, such as Intel MKL and OpenBLAS, netlib-java will use these as the implementation to use. 
+Next, it try to load netlib references which netlib-java use CBLAS and LAPCKE interface to perform BLAS and LAPACK native call. 
+The last option is to use f2j which is intended to translate the BLAS and LAPACK libraries from their Fortran77 reference source code to Java class files, 
+instead of calling native libraries by using Java Native Interface (JNI).
+
+We can use JNI to call native libraries from Java. The JNI is a native programming interface which allows Java code that runs inside a Java Virtual Machine (VM) 
+to interoperate with applications and libraries written in other programming languages.
+
+\section{Create Java interface of CBLAS with JNI}
+\label{sec:history}
+\begin{enumerate}
+    \item Download BLAS and build using make file. In the figure2.1, the built file is libblas.a and the header file is blas.h.
+    \item Download CBLAS and build using make file (I am not sure whether we should build archive file or shared library).
+In figure, the build file would be libcblas.a or libcblas.dylib and header file is cblas.h.
+    \item Create java file which will be the Java interface of CBLAS.
+    \item Compile java file with -h header flag to create class file (CBLASJ.class) and header file (CBLASJ.h).
+\begin{lstlisting}[language=bash]
+    $ javac -h . CBLASJ.java
+\end{lstlisting}
+    \item Create C file (CBLASJ.c) which will bind Java interface and CBLAS library. And compile it with JNI to create object file (CBLASJ.o).
+\begin{lstlisting}[language=bash]
+    $ gcc -c-fPIC -I${JAVA_HOME}/include -I${JAVA_HOME}/include/darwin CBLASJ.c
+\end{lstlisting}
+    \item Compile shared library linking library (libcblas.a or libcblas.dylib) object file (CBLASJ.o).
+\begin{lstlisting}[language=bash]
+    $ gcc -o libcblas.dylib (or libcblas.a) CBLASJ.o 
+\end{lstlisting}
+\end{enumerate}
+
+\begin{figure}[htb]
+    \includegraphics[width=15cm]{cblas_with_jni.eps}
+    \caption{Integration of Native Methods }
+    \label{fig:Sampling}
+\end{figure}
+
+\section{Matrix Computation and Optimization in Apache Spark}
+\label{sec:history}
+
+Matrix operation is a fundamental part of machine learning. Apache Spark provides implementation for distributed and local matrix operation. 
+To translate single-node algorithms to run on a distributed cluster, Spark addresses separating matrix operations from vector operations and run matrix operations on the cluster, 
+while keeping vector operations local to the driver.
+
+Spark changes its behavior for matrix operations depending on the type of operations and shape of matrices.
+For example, Singular Value Decomposition (SVD) for a square matrix is performed in distributed cluster,
+but SVD for a tall and skinny matrix is on a driver node. This is because the matrix derived among the computation of SVD for tall and skinny matrix is usually small so that it can fit to single node.
+
+Spark uses ARPACK to solve square SVD.
+ARPACK is a collection of Fortran77 designed to solve eigenvalue problems.
+ARPACK is based upon an algorithmic variant of the Arnoldi process called the Implicitly Restarted Arnoldi Method (IRAM).
+When the matrix A is symmetric it reduces to a variant of the Lanczos process called the Implicitly Restarted Lanczos Method (IRLM). 
+ARPACK calculate matrix multiplication by performing matrix-vector multiplication.
+So we can distribute matrix-vector multiplies, and exploit the computational resources available in the entire cluster.
+The other method to distribute matrix operations is Spark TFOCS. Spark TFOCS supports several optimization methods.
+
+To allow full use of hardware-specific linear algebraic operations on single node, Spark uses the BLAS (Basic Linear Algebra Systems) interface with relevant libraries for CPU and GPU acceleration. 
+Native libraries can be used in Scala are ones with C BLAS interface or wrapper and called through the Java native interface implemented in Netlib-java library and wrapped by the Scala library called Breeze.
+Following is some of the implementation of BLAS.
+
+\begin{itemize}
+    \item f2jblas -  Java implementation of Fortran BLAS
+    \item OpenBLAS - open source CPU-optimized C implementation of BLAS
+    \item MKL - CPU-optimized C and Fortran implementation of BLAS by Intel
+\end{itemize}
+
+These have different implementation and they perform differently for the type of operation and matrices shape. 
+In Sark, OpenBlas is the default method of choice. BLAS interface is made specifically for dense linear algebra. 
+Then, there are few libraries that efficiently handle sparse matrix operations.
+
+\section{Memory Management of each Linear Algebra Library}
+\label{sec:history}
+
+The pure Java linear algebra library, such as La4j, EJML, and Apache Common Math, 
+use normal GC performed by JVM to manage memory. This is because the implementation of these libraries are in purely Java.
+
+Netlib-java, Jblas or other simple Java wrapper of BLAS, LAPACK, and ARPACK with Java Native Interface (JNI) use normal GC as well. 
+This is because the native code deals with Java array by obtaining a reference to it. After the operation, 
+the native method releases the reference to the Java array with or without returning new Java array or Java primitive type object.
+
+ND4J has two types of  its own memory management methods, GC to pointer of off-heap NDArray, and MemoryWorkspaces. 
+ND4J used off-heap memory to store NDArrats, to provide better performance while working with NDArrays from vative code such as BLAS and CUDA libraries. 
+Off-heap means that the memory is allocated outside of the Java heap so that it is not managed by the JVM’s GC. NDArray itself is not tracked by JVM, 
+but its pointer is. The Java heap stores pointer to NDArray on off-heap. When a pointer is dereferenced, this pointer can be a target of JVM’s GC and when it is collected, 
+the corresponding NDArray will be deallocated. When using MemoryWorkspaces, NDArray lives only within specific workspace scope. 
+When NDArray leaves the workspace scope, the memory is deallocated unless explicitly calling method to copy the NDArray out of the scope.

### 2020-03-04 thesis_template/2_RelatedWork/model/merge_sort_experiment.tex
implemented experiment

This experiment is to assess importance of careful memory management in multithreading of Rust. 
We implement merge-sort algorithm in three different ways. One is sharing source vector with Arc. 
Another is passing slice of source vector to child thread. The other is LinkedList implementation other than vector.

Our merge-sort algorithm with vector is implemented with recursion. In these alogorithm, the splitting phase is merely aquiring index of split position, 
not actually splitting the source vector. At merge phase, merge function receives two independent vector and merge these into single new vector.

For sharing data implementaion, channel with sending data is used for multithreading method, because we want to ensure children threads return values before parent thread proceed execution. 
For passing slice implementation, we use scope method to enable children threads to receive reference from their parent ensuring the same purpose of sending data. 
The linkedlist implementation is different from another two. This algorithm is inplace sorting so that it does not de/allocate memory during execution.

The comparison among sharing data and passing slice implementations is to see the impact of Arc, Atomic reference conuting, to runtime performance.
These two implementations are doing the same operations other than using or not using Arc to share data. 
This comparison can effectively show how important careful memory management is in multithreading computation in Rust.

One concern of these vector implementation is that type of elements of vector. To create merged vector in every merging phase, we need to get element value of vector at base case.
To acquire the value of element, we need reference counting as element or copying the value of object. Both does not seem perform the best in other languages.

The comparison among vector and linkedlist implementations can show trade-off between contiguous memory access and inplace non memory de/allocation. 
Experiment with Java linkedlist implementation can be interesting, because Java GC is severe problem when number of object is large.

### 2020-03-04 project/playground/src/main.rs

@@ -13,6 +13,7 @@ use objects::field::*;
 //use objects::access::*;
 use objects::sort::*;
 use std::mem;
+use std::collections::{VecDeque, LinkedList};
 
 
 fn main() {
@@ -48,17 +49,21 @@ fn main() {
     let (_t, mut customers) = create_customer_onwed_vector(size, keys, ages, num_purchases, total_purchases, duration_spents, duration_sinces, 
                                                 zip_codes, addresses, countries, states, first_names, last_names, provinces, comments, orders);
     
-
-    let mut smart_customers = Vec::with_capacity(size);
+    let mut atomic_custorms = VecDeque::with_capacity(size);
     for i in 0..size {
-        smart_customers.push(Arc::new(customers.remove(0)));
+        let customer = customers.remove(0);
+        atomic_custorms.push_back(Arc::new(customer));
     }
-    let sorted_customers = mergesort_mt_mp_gr_nocp(smart_customers, 0, size);
+    let sorted_customers = mergesort_vecdeque(atomic_custorms, 0, size);
     print!("cusotomer vector: [");
     for i in 0..size {
         print!("{}, ", sorted_customers[i]);
     }
     print!("]");
+
+
+    
+    
 
     let keys = get_integer_arc_vector(size);
     let ages = get_integer_arc_vector(size); 
@@ -97,5 +102,7 @@ fn main() {
         print!("{}, ", sorted_customers2[i]);
     }
     print!("]");
+
+    
     
 }

### 2020-03-04 project/playground/src/objects/sort.rs

@@ -8,49 +8,56 @@ use std::cmp::Ordering;
 use std::marker::{Send, Sync};
 use std::mem;
 use std::collections::{LinkedList, VecDeque};
+use std::default::Default;
 
 const MAX_THREADS: usize = 4;
 
-
-
-pub fn mergesort_vecdeque<T: 'static>(mut arr:VecDeque<Arc<T>>, left: usize, right: usize) -> VecDeque<Arc<T>> 
-    where T: Clone + Customer + PartialOrd + Send + Sync
+pub fn mergesort_vecdeque_slice<T: 'static>(mut arr: Vec<T>, len: usize) -> VecDeque<T> 
+    where T: Clone + Customer + PartialOrd + Send + Sync + Default
 {
-    let l = arr.len();
-    return merge_helper_vecdeque(Arc::new(arr), 0, l, 0);
+    let res = merge_helper_vecdeque_slice(&mut arr[..], len, 0);
+    return res;
 }
 
 
-fn merge_helper_vecdeque<T: 'static>(arr: Arc<VecDeque<Arc<T>>>, left: usize, right: usize, depth: usize) -> VecDeque<Arc<T>>  
-    where T: Clone + Customer + PartialOrd + Send + Sync
+fn merge_helper_vecdeque_slice<T: 'static>(arr: &mut [T], len: usize ,depth: usize) -> VecDeque<T> 
+    where T: Clone + Customer + PartialOrd + Send + Sync + Default
 {
-    if right - left > 1 {
-        let mid = (left + right) / 2;
+    if len > 1 {
+        let mid = len / 2;
         let new_depth = depth + 1;
-        let arr_cloned1 = Arc::clone(&arr);
-        let arr_cloned2 = Arc::clone(&arr);
-        let mut arr_right;
-        let mut arr_left;
-
+        let (arr_left, arr_right) = arr.split_at_mut(mid);
+        let len_left = arr_left.len();
+        let len_right = arr_right.len();
+        let res_left;
+        let res_right;
         if new_depth < MAX_THREADS {
-            let (sender, receiver) = mpsc::channel();
-            let _ = thread::spawn(move || {
-                let sorted = merge_helper_vecdeque(arr_cloned1, left, mid, new_depth);
-                sender.send(sorted).unwrap();
-            });
-            arr_right = merge_helper_vecdeque(arr_cloned2, mid, right, new_depth);
-            arr_left = receiver.recv().unwrap();
[…]

### 2020-03-04 project/rust_merge_sort/run.sh

@@ -1,0 +1,30 @@
+#!/bin/bash
+
+cargo clean
+cargo build --release
+
+
+for size in 100000 150000 200000
+do
+    rm -rf loging.log
+    echo "datastructure#size#method#sorttime" > loging.log
+
+    for method in 1 2 3
+    do
+        
+        for counter in 1 2 3 4 5
+        do
+           # rm -rf string.log
+        # write the first line
+
+
+            echo "Size: $size, Method: $method, Counter: $counter"
+
+            # Server experiment
+            # time cargo run --release $size $method
+            # Loacal experiment
+            time cargo run --release $size $method
+        done
+    done
+cat loging.log  >  result/resultMergesort_"$size".txt
+done

### 2020-03-04 project/rust_merge_sort/src/main.rs

@@ -3,45 +3,44 @@ extern crate rand;
 extern crate serde;
 extern crate bytes;
 use std::env;
-use std::sync::Arc;
 mod objects;
-use objects::customer::{create_customer_onwed_vector, create_customer_borrowed_vector};
-use objects::order::{get_order_owned_vector, get_order_borrowed_vector};
-use objects::field::{get_float_vector, get_integer_vector, get_string_vector};
+use objects::customer::create_customer_onwed_vector;
+use objects::order::get_order_owned_vector;
+use objects::field::*;
 //use objects::dropping::*;
 //use objects::access::*;
 use objects::sort::*;
-
+//use std::mem;
+use std::collections::{VecDeque, LinkedList};
+use std::fs::OpenOptions;
+use std::io::prelude::*;
+use objects::access::*;
 
 fn main() {
     let args: Vec<String> = env::args().collect();
     let size: usize = args[1].parse().unwrap();
-    let nums1 = get_integer_vector(size);
-    println!("Initial: {:?}", nums1);
+    let method: i32 = args[2].parse().unwrap(); 
+    run(method, size);
+}
 
-    let nums2 = get_integer_vector(size);
-    let n2 = nums2.len();
-    let merged = mergesort_mt_mp(nums2, 0, n2);
-    println!("Sort with MT{:?}", merged);
+fn run(method: i32, size: usize) {
+    match method {
+        1 => run_ex_shared(size),
+        2 => run_ex_scope(size),
+        3 => run_ex_linkedlist(size),
+        _ => println!("Wrong input!")
+    }
+}
 
-    let nums3 = get_integer_vector(size);
-    let n3 = nums3.len();
-    let num3_atomic = Arc::new(Mutex::new(nums3));
-    mergesort_mt_mutex(Arc::clone(&num3_atomic), 0, n3);
-    println!("Sort with Mutex{:?}", num3_atomic);
-
-    let nums4 = get_integer_vector(size);
-    let n4 = nums4.len();
-    let num4_atomic = Arc::new(nums4);
-    let merged2 = mergesort_mt_im(Arc::clone(&num4_atomic), 0, n4);
-    println!("Sort with Immutable{:?}", merged2);
+fn run_ex_shared(size: usize) {
+    let order_ids = get_integer_vector(size);
+    let num_itemss = get_integer_vector(size);
+    let payments = get_float_vector(size);
+    let order_times = get_float_vector(size);
+    let titles = get_string_vector(size);
[…]

### 2020-03-04 project/rust_merge_sort/src/objects/access.rs

@@ -3,6 +3,7 @@ use serde::ser::Serialize;
 use std::fs::OpenOptions;
 use std::io::prelude::*;
 use std::time::Instant;
+use std::collections::LinkedList;
 
 fn de_serialize<T>(customer: &T) 
     where T: Customer + Serialize, 
@@ -16,9 +17,20 @@ fn de_serialize<T>(customer: &T)
     file.write_all(serialized.as_bytes()).expect("Fail to write file.");
 }
 
+pub fn access_linkedlist(customers: &LinkedList<CustomerOwned>) -> u128 {
+    let mut iterater = customers.iter();
+    let start = Instant::now();
+    while let Some(customer) = iterater.next() {
+        de_serialize(customer);
+    }
+    let elapsed = start.elapsed().as_millis(); 
+    elapsed 
+}
+
+
 // Function access object whose field is owned.
 
-pub fn access_owned(customers: &Vec<CustomerOwned>) -> u128 {
+pub fn access_owned(customers: &[CustomerOwned]) -> u128 {
     let len = customers.len();
     let start = Instant::now();
     for i in 0..len {
@@ -29,24 +41,24 @@ pub fn access_owned(customers: &Vec<CustomerOwned>) -> u128 {
 }
 
 // Function access object whose field is borrowed.
-pub fn access_borrowed(customers: &Vec<CustomerBorrowed>) -> u128 {
-    let len = customers.len();
-    let start = Instant::now();
-    for i in 0..len {
-        de_serialize(&customers[i])
-    }
-    let elapsed = start.elapsed().as_millis(); 
-    elapsed
-}
+// pub fn access_borrowed(customers: &Vec<CustomerBorrowed>) -> u128 {
+//     let len = customers.len();
+//     let start = Instant::now();
+//     for i in 0..len {
+//         de_serialize(&customers[i])
+//     }
+//     let elapsed = start.elapsed().as_millis(); 
+//     elapsed
+// }
 
 
 
-pub fn access_rc(customers: &Vec<CustomerRc>) -> u128 {
-    let len = customers.len();
-    let start = Instant::now();
-    for i in 0..len {
-        de_serialize(&customers[i])
-    }
-    let elapsed = start.elapsed().as_millis(); 
-    elapsed
-}
+// pub fn access_rc(customers: &Vec<CustomerRc>) -> u128 {
+//     let len = customers.len();
+//     let start = Instant::now();
+//     for i in 0..len {
[…]

### 2020-03-04 project/rust_merge_sort/src/objects/customer.rs

@@ -1,10 +1,13 @@
-use crate::objects::order::{OrderOwned, OrderBorrowed, OrderRc};
-use std::rc::Rc;
+use crate::objects::order::OrderOwned;
+//use std::rc::Rc;
 use std::time::Instant;
 use std::cmp::Ordering;
 use serde::ser::{Serialize, Serializer, SerializeStruct};
 use std::fmt;
 use std::marker::{Send, Sync};
+//use std::sync::Arc;
+use std::default::Default;
+
 // Custorm trait (interface for all objects.)
 pub trait Customer {
     fn zip_code_bytes(&self) -> &[u8];
@@ -15,7 +18,7 @@ pub trait Customer {
 
 
 // Objects whose fields are all owned.
-#[derive(Clone, Debug)]
+#[derive(Clone, Debug, Default)]
 pub struct CustomerOwned {
     key: i32,
     age: i32,
@@ -35,42 +38,62 @@ pub struct CustomerOwned {
 }
 
 // Objects whose fields are all borrowed.
-#[derive(Clone, Debug)]
-pub struct CustomerBorrowed<'a> {
-    key: &'a i32,
-    age: &'a i32,
-    num_purchase: &'a i32,
-    total_purchase: &'a f64,
-    duration_spent: &'a f64, 
-    duration_since: &'a f64,
-    zip_code: &'a String,
-    address: &'a String,
-    country: &'a String,
-    state: &'a String,
-    first_name: &'a String,
-    last_name: &'a String,
-    province: &'a String,
-    comment: &'a String, 
-    order: &'a OrderBorrowed<'a>
-}
-#[derive(Clone, Debug)]
-pub struct CustomerRc {
-    key: Rc<i32>,
-    age: Rc<i32>,
-    num_purchase: Rc<i32>,
-    total_purchase: Rc<f64>,
-    duration_spent: Rc<f64>, 
-    duration_since: Rc<f64>,
-    zip_code: Rc<String>,
-    address: Rc<String>,
-    country: Rc<String>,
-    state: Rc<String>,
-    first_name: Rc<String>,
-    last_name: Rc<String>,
-    province: Rc<String>,
-    comment: Rc<String>, 
-    order: Rc<OrderRc>
-}
+// #[derive(Clone, Debug)]
+// pub struct CustomerBorrowed<'a> {
+//     key: &'a i32,
+//     age: &'a i32,
+//     num_purchase: &'a i32,
+//     total_purchase: &'a f64,
[…]

### 2020-03-04 project/rust_merge_sort/src/objects/field.rs

@@ -2,8 +2,9 @@ use rand::{Rng,SeedableRng};
 use rand::rngs::StdRng;
 use rand::distributions::Alphanumeric;
 use rand::distributions::{Uniform, Distribution};
-use std::rc::Rc;
+//use std::rc::Rc;
 use std::iter;
+//use std::sync::Arc;
 // Function to get string vector.
 // All vector will have the same elements with length of 5.
 pub fn get_string_vector(size: usize) -> Vec<String> {
@@ -21,24 +22,39 @@ pub fn get_string_vector(size: usize) -> Vec<String> {
     strings
 }
 
-pub fn get_stirng_rc_vector(size: usize) -> Vec<Rc<String>> {
-    let mut strings = Vec::with_capacity(size);
-    let mut rng: StdRng = SeedableRng::seed_from_u64(0);
-    for _ in 0..size {
-        // Get random Stirng whose length is 5.
-        let string: String = iter::repeat(())
-                            .map(|()| rng.sample(Alphanumeric))
-                            .take(5)
-                            .collect();
-        strings.push(Rc::new(string));
-    }
-    strings
-}
+// pub fn get_string_rc_vector(size: usize) -> Vec<Rc<String>> {
+//     let mut strings = Vec::with_capacity(size);
+//     let mut rng: StdRng = SeedableRng::seed_from_u64(0);
+//     for _ in 0..size {
+//         // Get random Stirng whose length is 5.
+//         let string: String = iter::repeat(())
+//                             .map(|()| rng.sample(Alphanumeric))
+//                             .take(5)
+//                             .collect();
+//         strings.push(Rc::new(string));
+//     }
+//     strings
+// }
+
+
+// pub fn get_string_arc_vector(size: usize) -> Vec<Arc<String>> {
+//     let mut strings = Vec::with_capacity(size);
+//     let mut rng: StdRng = SeedableRng::seed_from_u64(0);
+//     for _ in 0..size {
+//         // Get random Stirng whose length is 5.
+//         let string: String = iter::repeat(())
+//                             .map(|()| rng.sample(Alphanumeric))
+//                             .take(5)
+//                             .collect();
+//         strings.push(Arc::new(string));
+//     }
+//     strings
+// }
 
[…]

### 2020-03-04 project/rust_merge_sort/src/objects/mod.rs

@@ -2,5 +2,5 @@ pub mod customer;
 pub mod order;
 pub mod field;
 //pub mod dropping;
-//pub mod access;
+pub mod access;
 pub mod sort;

### 2020-03-04 project/rust_merge_sort/src/objects/order.rs

@@ -1,10 +1,11 @@
-use std::rc::Rc;
+//use std::rc::Rc;
 use serde::ser::{Serialize, Serializer, SerializeStruct};
 use std::cmp::Ordering;
-use std::marker::Send;
+//use std::marker::Send;
+//use std::sync::Arc;
+use std::default::Default;
 
-
-#[derive(Clone, Debug)]
+#[derive(Clone, Debug, Default)]
 pub struct OrderOwned {
     order_id: i32,
     num_items: i32, 
@@ -13,26 +14,34 @@ pub struct OrderOwned {
     title: String,
     comment: String
 }
-#[derive(Clone, Debug)]
-pub struct OrderBorrowed<'a> {
-    order_id: &'a i32,
-    num_items: &'a i32, 
-    payment: &'a f64,
-    order_time: &'a f64,
-    title: &'a String,
-    comment: &'a String
-}
+// #[derive(Clone, Debug)]
+// pub struct OrderBorrowed<'a> {
+//     order_id: &'a i32,
+//     num_items: &'a i32, 
+//     payment: &'a f64,
+//     order_time: &'a f64,
+//     title: &'a String,
+//     comment: &'a String
+// }
 
-#[derive(Clone, Debug)]
-pub struct OrderRc {
-    order_id: Rc<i32>,
-    num_items: Rc<i32>, 
-    payment: Rc<f64>,
-    order_time: Rc<f64>,
-    title: Rc<String>,
-    comment: Rc<String>
-}
-
+// #[derive(Clone, Debug, Default)]
+// pub struct OrderRc {
+//     order_id: Rc<i32>,
+//     num_items: Rc<i32>, 
+//     payment: Rc<f64>,
+//     order_time: Rc<f64>,
+//     title: Rc<String>,
+//     comment: Rc<String>
+// }
+// #[derive(Clone, Debug, Default)]
+// pub struct OrderArc {
+//     order_id: Arc<i32>,
+//     num_items: Arc<i32>, 
+//     payment: Arc<f64>,
+//     order_time: Arc<f64>,
+//     title: Arc<String>,
+//     comment: Arc<String>
+// }
 impl OrderOwned {
     pub fn new(order_id: i32, num_items: i32, payment: f64, order_time: f64, title: String, comment: String) -> OrderOwned {
         OrderOwned {
@@ -46,31 +55,45 @@ impl OrderOwned {
     }
 }
 
-impl OrderBorrowed<'_> {
[…]

### 2020-03-05 thesis_template/2_RelatedWork/model/spark.tex
improved state of the art

\section{Hahoop MapReduce to Spark}
\label{sec:history}
In several Big Data mining tools that have been developed, the most notable ones are MapReduce and Spark. MapReduce is a cluster computing framework 
which supports locality-aware scheduling, fault tolerance, and load balancing. Spark improves operations that MapReduce does not cover well.

MapReduce provides a programming model where the user creates acyclic data flow graphs to pass input data through a set of opperation. This 
data flow programming model is useful for many of query applications. However, MapReduce framework struggles from two of main resent data mining jobs: iterative jobs and interactive analysis.

Iterative job is especially common in Machine Learning Algorithm, such as Gradient Descent. In traditional MapReduce framework, each iteration can be expressed as single MapReduce job 
so taht each job must reload the data from disk. This leads I/O overhead and deteriorates performance of iterative algorithms.

Interactive analysis is also an inevitable task in modern data science. A data scientist want perform exploratory analysis in interactive way. 
Nevertheless, MapReduce is designed in the way more sutable for ad-hoc query, so each analysis can be single MapReduce job. 
To perform multiple analysis to explore dataset, the data needs to be written to and reload from disk many times.

To overcome these limitations, Spark has been developed as a new cluster computing framework maintaining the innovative characteristics of MapReduce and improving 
its iterative and interactive jobs with in-memory data structure.

\section{Resilient Distributed Datasets}
\label{sec:history}
The major methods in Spark are Resilient Distributed Datasets (RDDs), a data structue that abstracts distributed memoy across different clusters. 
The immutable coarse-grained transformantion, spark-scheduler with lazy-evaluation, and memory management with cacheing achieve computation with fault-tolerance, 
fast execution, and moderate control on memory efficiency.

A RDD is essentially a multi-layer Java data structure. A top RDD object references Java array, which intern, references a set of tuple objects. 
The coarse-grained transformantion and immutability requires a RDD to be deep-copied to produce a new RDD, but efficiently offers fault tolerance. 
The lost partitions of a RDD can be recomputed in parallel on different nodes rather than rolling back the whole program.

Spark-pipeline consists of sequence of transformations and actions over RDDs. A transformation produces a new RDD from a set of existing RDD. 
An action is method that computes statistics from an RDD. Due to lazy-evaluation nature, transformantions do not materialize the newly created RDD. 
Instead, RDD Lineages are created. Lineage is a graph among parent and child RDDs which represents logical execution plan. 
This enhance fault-tolerance and improve ability to optimize execution plan.

Spark is one of the most used big data computing framework. Spark uses Resilient Distributed Datasets (RDDs) which implement in-memory data structures 
used to cache intermediate data across a set of nodes. This enables multiple rounds of computation on the same data, which is required for machine learning 
and graph analytics iteratively process the data.

In RDD caching, there are different stages of caching, such as MEMOR\_YONLY and DISK\_ONLY. 
Currently, for very large data sets, we need to pay attention to garbage collection (GC) and OS page swapping overhead, 
because these could degrades execution time significantly. Therefore, DISK\_ONLY RDD caching can be better configuration in this case. 
However, writing and reading intermediate data among desk and memory could have bad effects for execution time, due to need of serialization and deserialization.

### 2020-03-06 thesis_template/2_RelatedWork/model/spark.tex
completed RDD

@@
 
-Spark is one of the most used big data computing framework. Spark uses Resilient Distributed Datasets (RDDs) which implement in-memory data structures 
-used to cache intermediate data across a set of nodes. This enables multiple rounds of computation on the same data, which is required for machine learning 
-and graph analytics iteratively process the data.
+RDDs can be cached in memory for faster access by persist method. Developers can specify a storage level for a persisted RDD, in memory with serialized or deserialized, or on disk. 
+Other than persisted RDD, Spark generates a lot of intermediate RDDs during excution. Since RDD is a Java object, they are managed by Garbage Collection (GC) in the JVM. 
+However, persisted RDDs are never collected by GC. This GC might cause significant deterioration of performance of Spark, because GC shows heavy overhead when there are a number of objects.
 
-In RDD caching, there are different stages of caching, such as MEMOR\_YONLY and DISK\_ONLY. 
-Currently, for very large data sets, we need to pay attention to garbage collection (GC) and OS page swapping overhead, 
-because these could degrades execution time significantly. Therefore, DISK\_ONLY RDD caching can be better configuration in this case. 
-However, writing and reading intermediate data among desk and memory could have bad effects for execution time, due to need of serialization and deserialization.
+\section{Memory Management in Spark}
+\label{sec:history}
+
+\begin{itemize}
+    \item Java Garbage Collection
+    \item Spark Generation Heep structure
+    \item Spark RDD life-time, shuffled data
+    \item Annotation, off-heap solution 
+    \item GC tuning solutions
+\end{itemize}
+
+\section{Application to System Language}
+\label{sec:history}

### 2020-03-06 thesis_template/2_RelatedWork/model/spark.tex
added experiment document

@@
 The immutable coarse-grained transformantion, spark-scheduler with lazy-evaluation, and memory management with cacheing achieve computation with fault-tolerance, 
-fast execution, and moderate control on memory efficiency.
+fast execution, and moderate control on memory efficiency \cite{DBLP:conf/nsdi/ZahariaCDDMMFSS12}.
 

### 2020-03-07 thesis_template/2_RelatedWork/model/spark.tex
finished java memory management documentation

--- 2020-03-06 thesis_template/2_RelatedWork/model/spark.tex
@@
-\section{Hahoop MapReduce to Spark}
+\section{Hadoop MapReduce to Spark}
 \label{sec:history}
@@
 
-MapReduce provides a programming model where the user creates acyclic data flow graphs to pass input data through a set of opperation. This 
+MapReduce provides a programming model where the user creates acyclic data flow graphs to pass input data through a set of operations. This 
 data flow programming model is useful for many of query applications. However, MapReduce framework struggles from two of main resent data mining jobs: iterative jobs and interactive analysis.
@@
 Iterative job is especially common in Machine Learning Algorithm, such as Gradient Descent. In traditional MapReduce framework, each iteration can be expressed as single MapReduce job 
-so taht each job must reload the data from disk. This leads I/O overhead and deteriorates performance of iterative algorithms.
+so that each job must reload the data from disk. This leads I/O overhead and deteriorates performance of iterative algorithms.
 
 Interactive analysis is also an inevitable task in modern data science. A data scientist want perform exploratory analysis in interactive way. 
-Nevertheless, MapReduce is designed in the way more sutable for ad-hoc query, so each analysis can be single MapReduce job. 
+Nevertheless, MapReduce is designed in the way more stable for ad-hoc query, so each analysis can be single MapReduce job. 
 To perform multiple analysis to explore dataset, the data needs to be written to and reload from disk many times.
@@
 \label{sec:history}
-The major methods in Spark are Resilient Distributed Datasets (RDDs), a data structue that abstracts distributed memoy across different clusters. 
-The immutable coarse-grained transformantion, spark-scheduler with lazy-evaluation, and memory management with cacheing achieve computation with fault-tolerance, 
-fast execution, and moderate control on memory efficiency.
+The major methods in Spark are Resilient Distributed Datasets (RDDs), a data structure that abstracts distributed memory across different clusters. 
+The immutable coarse-grained transformation, spark-scheduler with lazy-evaluation, and memory management with cacheing achieve computation with fault-tolerance, 
+fast execution, and moderate control on memory efficiency \cite{DBLP:conf/nsdi/ZahariaCDDMMFSS12}.
 
 A RDD is essentially a multi-layer Java data structure. A top RDD object references Java array, which intern, references a set of tuple objects. 
-The coarse-grained transformantion and immutability requires a RDD to be deep-copied to produce a new RDD, but efficiently offers fault tolerance. 
+The coarse-grained transformations and immutability requires a RDD to be deep-copied to produce a new RDD, but efficiently offers fault tolerance. 
 The lost partitions of a RDD can be recomputed in parallel on different nodes rather than rolling back the whole program.
@@
 Spark-pipeline consists of sequence of transformations and actions over RDDs. A transformation produces a new RDD from a set of existing RDD. 
-An action is method that computes statistics from an RDD. Due to lazy-evaluation nature, transformantions do not materialize the newly created RDD. 
+An action is method that computes statistics from an RDD. Due to lazy-evaluation nature, transformations do not materialize the newly created RDD. 
 Instead, RDD Lineages are created. Lineage is a graph among parent and child RDDs which represents logical execution plan. 
@@
 RDDs can be cached in memory for faster access by persist method. Developers can specify a storage level for a persisted RDD, in memory with serialized or deserialized, or on disk. 
-Other than persisted RDD, Spark generates a lot of intermediate RDDs during excution. Since RDD is a Java object, they are managed by Garbage Collection (GC) in the JVM. 
+Other than persisted RDD, Spark generates a lot of intermediate RDDs during execution. Since RDD is a Java object, they are managed by Garbage Collection (GC) in the JVM. 
 However, persisted RDDs are never collected by GC. This GC might cause significant deterioration of performance of Spark, because GC shows heavy overhead when there are a number of objects.
@@
 \label{sec:history}
+Spark framework allocates multiple executors, JVMs, that run sequence of transformations and actions. As we describe the previous section, data in Spark is mainly stored as Java objects in memory, 
+so that they are allocated on JVM heap and managed by JVM Garbage Collection.
+The data may form three types \cite{DBLP:journals/pvldb/XuGDWW19}: Cached data, Shuffled data, and Operator-generated data.
+
+Spark can cache data in memory to reduce disk I/O. This Cached data usually long-lived Java objects and span multiple stages in Spark-pipeline. 
+Spark allocates a logical storage space to store the cached data as shown in Figure. After aggregation, Spark generates Shuffled data. Shuffled data is usually long-lived, 
+because it need to be kept in memory until the task ends. Spark allocates execution space to store Shuffled data.
+The storage space and execution space spans 60 \% of JVM heap space in default.
+Operator-generated data is data generated by user-defined operations.
+Since Operator-generated data may or may not be used,
+after the operation finish, the data object can be both short-lived or long-lived objects. These are stored in user space allocated on default 40 \% of JVM heap.
+
+All data of these types on JVM heap is managed by JVM GC. GC check references graph of objects, mark whether the objects are used and deallocate memory space occupied by unused objects. 
+There are three popular GCs: Parallel, CMS and G1. All of these method track generation of object based on the region of memory. 
+The Java logical heap structure is shown in Figure. It can be separated into three main parts where store objects for each corresponding generation: 
+permanent generation, young generation, and old generation. The region for permanent generation stores metadata required by JVM to describe 
+class and method used in application which will be permanently lived on the region of memory.
+
+The region for young generation mainly consists of two parts: Eden and Survivor space. 
+First, Java objects are created in Eden space and promoted to Survivor space when survive from GC. 
+After objects survive several GCs in Survivor space, they are finally promoted to old generation.
+
+In old generation, JVM lunches multi-thread to perform GC. GC with multi-threading suffers from Stop-The-World (STW) pauses; 
+GC may suspend application threads while performing object marking and deallocation. 
+Different GC algorithms try to solve this problem with trade-off between GC frequency and memory utilization. 
+Because of the problem of STW, JVM GC is inefficient when number of objects is large. 
+Therefore, GC become severe issue under Big Data situation where might produce significant number of object.
+
+\begin{figure}[htb]
+    \includegraphics[width=15cm]{java_heap.eps}
+    \caption{Java Heap Structure}
+    \label{fig:Sampling}
+\end{figure}
+
+\begin{figure}[htb]
+    \includegraphics[width=15cm]{java_gc.eps}
+    \caption{Java Garbage Collection}
+    \label{fig:Sampling}
+\end{figure}
 
 \begin{itemize}
-    \item Java Garbage Collection
-    \item Spark Generation Heep structure
-    \item Spark RDD life-time, shuffled data
+    \item GC tuning solutions
     \item Annotation, off-heap solution 
-    \item GC tuning solutions
 \end{itemize}

### 2020-03-09 project/playground/src/objects/access.rs
started to implement tree aggregation

@@ -3,9 +3,13 @@ use serde::ser::Serialize;
 use std::fs::OpenOptions;
 use std::io::prelude::*;
 use std::time::Instant;
+use std::net::SocketAddr;
+use std::error::Error;
+use std::io::BufReader;
+use std::path::Path;
 
-fn de_serialize<T>(customer: &T) 
-    where T: Customer + Serialize, 
+fn serialize<T>(customer: &T) 
+where T: Customer + Serialize, 
 {
     let serialized = serde_json::to_string(&customer).unwrap();
     let mut file = OpenOptions::new()
@@ -16,13 +20,35 @@ fn de_serialize<T>(customer: &T)
     file.write_all(serialized.as_bytes()).expect("Fail to write file.");
 }
 
+fn serialize_vector<T, P>(customers: &[T], path: P) 
+    where T: Customer + Serialize,
+          P: AsRef<Path> 
+{
+    let serialized = serde_json::to_string(customers).unwrap();
+    let mut file = OpenOptions::new()
+                    .append(false)
+                    .create(true)
+                    .open(file_name)
+                    .unwrap();
+    file.write_all(serialized.as_bytes()).expect("Fail to write file.");
+}
+
+fn deserialize_vector<T, P>(path: P) -> Result<Vec<T>, Box<Error>>
+    where T: Customer + Serialize + Deserialize,
+          P: AsRef<Path>
+{
+    let file = File::open(path)?;
+    let reader = BufReader::new(file);
+    let customers = serde_json::from_reader(reader)?;
+    Ok(customers)
+}
 // Function access object whose field is owned.
 
 pub fn access_owned(customers: &Vec<CustomerOwned>) -> u128 {
     let len = customers.len();
     let start = Instant::now();
     for i in 0..len {
-        de_serialize(&customers[i])
+        serialize(&customers[i])
     }
     let elapsed = start.elapsed().as_millis(); 
     elapsed
@@ -33,7 +59,7 @@ pub fn access_borrowed(customers: &Vec<CustomerBorrowed>) -> u128 {
     let len = customers.len();
     let start = Instant::now();
     for i in 0..len {
-        de_serialize(&customers[i])
+        serialize(&customers[i])
     }
     let elapsed = start.elapsed().as_millis(); 
     elapsed
@@ -45,7 +71,7 @@ pub fn access_rc(customers: &Vec<CustomerRc>) -> u128 {
     let len = customers.len();
     let start = Instant::now();
[…]

### 2020-03-09 project/playground/src/objects/aggregate.rs

@@ -1,0 +1,70 @@
+use std::thread;
+use std::path::Path;
+pub use std::sync::Arc;
+use crate::objects::customer::*;
+use crate::objects::access::*;
+const MAX_THREADS: usize = 4;
+
+fn tree_aggregate_sum<P: AsRef<Path>>(arr: Arc<Vec<P>>, left: usize, right: usize, depth: usize)
+{   
+    let sum_current;
+    let path;
+    if right - left > 1 {
+        let mid = (left + right) / 2;
+        let new_depth = depth + 1;
+        let arr_cloned1 = Arc::clone(&arr);
+        let arr_cloned2 = Arc::clone(&arr);
+        let sum_left;
+        let sum_right;
+        path = arr[mid];
+        if new_depth < MAX_THREADS {
+            let (sender1, receiver1) = crossbeam::channel::unbounded();
+            let (sender2, receiver2) = crossbeam::channel::unbounded(); 
+        
+            let _ = thread::spawn(move |_| {
+               let sum = tree_aggregate_sum(arr_cloned1, left, mid, new_depth);
+               sender1.send(sum).unwrap();
+            });
+            
+            let _ = thread::spawn(move |_| {
+                let sum = tree_aggregate_sum(arr_cloned2, mid, right, new_depth);
+                sender2.send(sum).unwrap();
+             });
+             sum_current = add_local(path);
+             sum_left = receiver1.recv().unwrap();
+             sum_right = receiver2.recv().unwrap();
+        } else {
+            sum_current = add_local(path);
+            sum_left = tree_aggregate_sum(arr_cloned1, left, mid, new_depth);
+            sum_right = tree_aggregate_sum(arr_cloned2, mid, right, new_depth);
+        }
+        return tree_reduce_sum(sum_current, sum_left, sum_right);
+    } else if (right - left == 1) {
+        let mid = (right - left) / 2;
+        path = arr[mid];
+        sum_current = add_local(path);
+        return tree_aggregate_sum(sum_current, 0, 0);
+    }    
+}
+
+fn tree_reduce_sum<T>(sum_current: i32,  sum_left: i32, sum_right: i32) 
+{
+    let sum =  sum_left + sum_current + sum_right;
+    sum
+}
+
+fn add_local<P: AsRef<Path>>(path: P) {
+    let customers = deserialize_vector(file).unwrap();
+    let sum_current = add_customer_key(&customers[..]);
+    sum_current
[…]

### 2020-03-09 project/playground/src/objects/customer.rs

@@ -1,11 +1,11 @@
-use crate::objects::order::{OrderOwned, OrderBorrowed, OrderRc, OrderArc};
-use std::rc::Rc;
+use crate::objects::order::OrderOwned;
+//use std::rc::Rc;
 use std::time::Instant;
 use std::cmp::Ordering;
 use serde::ser::{Serialize, Serializer, SerializeStruct};
 use std::fmt;
 use std::marker::{Send, Sync};
-use std::sync::Arc;
+//use std::sync::Arc;
 use std::default::Default;
 
 // Custorm trait (interface for all objects.)
@@ -38,62 +38,62 @@ pub struct CustomerOwned {
 }
 
 // Objects whose fields are all borrowed.
-#[derive(Clone, Debug)]
-pub struct CustomerBorrowed<'a> {
-    key: &'a i32,
-    age: &'a i32,
-    num_purchase: &'a i32,
-    total_purchase: &'a f64,
-    duration_spent: &'a f64, 
-    duration_since: &'a f64,
-    zip_code: &'a String,
-    address: &'a String,
-    country: &'a String,
-    state: &'a String,
-    first_name: &'a String,
-    last_name: &'a String,
-    province: &'a String,
-    comment: &'a String, 
-    order: &'a OrderBorrowed<'a>
-}
-#[derive(Clone, Debug, Default)]
-pub struct CustomerRc {
-    key: Rc<i32>,
-    age: Rc<i32>,
-    num_purchase: Rc<i32>,
-    total_purchase: Rc<f64>,
-    duration_spent: Rc<f64>, 
-    duration_since: Rc<f64>,
-    zip_code: Rc<String>,
-    address: Rc<String>,
-    country: Rc<String>,
-    state: Rc<String>,
-    first_name: Rc<String>,
-    last_name: Rc<String>,
-    province: Rc<String>,
-    comment: Rc<String>, 
-    order: Rc<OrderRc>
-}
+// #[derive(Clone, Debug)]
+// pub struct CustomerBorrowed<'a> {
+//     key: &'a i32,
+//     age: &'a i32,
+//     num_purchase: &'a i32,
+//     total_purchase: &'a f64,
+//     duration_spent: &'a f64, 
+//     duration_since: &'a f64,
+//     zip_code: &'a String,
+//     address: &'a String,
+//     country: &'a String,
+//     state: &'a String,
+//     first_name: &'a String,
+//     last_name: &'a String,
[…]

### 2020-03-09 project/playground/src/objects/mod.rs

@@ -2,6 +2,7 @@ pub mod customer;
 pub mod order;
 pub mod field;
 //pub mod dropping;
-//pub mod access;
+pub mod access;
 pub mod sort;
 //pub mod linkedlist;
+pub mod aggregate;

### 2020-03-09 thesis_template/2_RelatedWork/model/spark.tex
added deserialization

@@
 Different GC algorithms try to solve this problem with trade-off between GC frequency and memory utilization.
-Because of the problem of STW, JVM GC is inefficient when number of objects is large. 
-Therefore, GC become severe issue under Big Data situation where might produce significant number of object.
+
+Because of the problem of STW and copying objects to different physical memory pages , JVM GC cause huge overhead when number of objects is large. 
+Therefore, GC become severe issue in Big Data processing where might produce significant number of object.
 

### 2020-03-09 thesis_template/2_RelatedWork/relatedWork.tex
improved state of the art
finished java memory management documentation
started to implement tree aggregation
added deserialization

@@
 
-\section{Spark and RDD Catching}
+\section{State of the Art}
 \label{sec:history}
-\input{2_RelatedWork/model/spark_memory_management}
-
-\section{Memory Management of Java}
-\label{sec:history}
-\input{2_RelatedWork/model/memory_management_java}
+\input{2_RelatedWork/model/spark}
 
@@
 
+\section{Experiment: Tree aggregate}
+\label{sec:history}
+Three aggregate can be more memory de/allocation intensive experiment, when we load data from disk line by line to aggregate.
+This is because, we will allocate many small objects and deallocate them many times.
+We can imitate ShuffledRDDs by writing result to disk and reading it to other thread.  
+We can compare to Java implementation for ration of runtime increase.
+
 \section{Todos}
@@
     \item Document for Memory Management of Java with Garbage Collection and the impact for Big Data tools
-    \item The safety of Region Based Maemory Management and advantage of using Rust.
+    \item The safety of Region Based Memory Management and advantage of using Rust.
     \item Serialize problem 
@@
 \end{itemize}
+
+\begin{figure}[htb]
+    \includegraphics[width=15cm]{rust_merge_sort.eps}
+    \caption{mergesort}
+    \label{fig:Sampling}
+\end{figure}

### 2020-03-09 thesis_template/Appendix/Appendix.tex
added deserialization

@@
 \label{sec:history}
-A process is a section of computation job. A process can work on a CPU core. We can devide process as well.
-Basically, each process does not share thier memory. However, for multiprocessing, we could avoid this restriction.
-Processes can be represented as tree structure, because a process may create onther child processes.
+A process is a section of computation job. A process can work on a CPU core. We can divide process as well.
+Basically, each process does not share their memory. However, for multiprocessing, we could avoid this restriction.
+Processes can be represented as tree structure, because a process may create other child processes.
 Process has 4 states, new, running, waiting, and ready. 
@@
 
-Processes executing concurrently in the operating system may be either independent processes or cooperating processes excuting in the system.
-A process is indepenedent if it does not share data with any other processes. A process cooperating if ti can affect or be affected by the 
+Processes executing concurrently in the operating system may be either independent processes or cooperating processes executing in the system.
+A process is independent if it does not share data with any other processes. A process cooperating if it can affect or be affected by the 
 other processed executing in the system. In cooperating process, there are two kinds, shared memory and message passing. 
-In shared memory, it removes restriction of not interfering memory region. Message passing can be useful for destribution systems as well.
+In shared memory, it removes restriction of not interfering memory region. Message passing can be useful for distribution systems as well.
 
-For a pair of processes to communicate throught message, a socket is needed to be established. 
+For a pair of processes to communicate through message, a socket is needed to be established. 
 A socket is identified by an IP address concatenated with a port number. When two process communicate, each process will have socket. 
@@
 
-\section{Miltithreading and Parallelism}
+\section{Multi-threading and Parallelism}
 \label{sec:history}
-A thread is a basic unit of CPU usilization, so that a process can have multiple thread. Threads shares mainly code and data. 
-Multithreaing is increasingly popular as the multicore programming becomes in common, becasue we can run multiple thread on different core.
-Creating thread is much cheaper than creating process and it shares resources so that we do not need addtional methods to allow threads to 
+A thread is a basic unit of CPU utilization, so that a process can have multiple thread. Threads share mainly code and data. 
+Multi-threading is increasingly popular as the multicore programming becomes in common, because we can run multiple thread on different core.
+Creating thread is much cheaper than creating process and it shares resources so that we do not need additional methods to allow threads to 
 communicate each other, such as sharing memory and message passing.
@@
 \label{sec:history}
-In computer storage hierarchy, the closest strage to CPU is register. It is built into each CPU core and accessible within one cycle of the CPU clock.
+In computer storage hierarchy, the closest storage to CPU is register. It is built into each CPU core and accessible within one cycle of the CPU clock.
 However, the same cannot be said of main memory, which is accessed via a transaction on the memory bus. This takes many cycles of the CPU clock.
-The remedy is to add fast memeory between the CPU and main memory, typically on the CPU chip for faster access. Such a cache plays a role for this.
+The remedy is to add fast memory between the CPU and main memory, typically on the CPU chip for faster access. Such a cache plays a role for this.
 
 For the layout of main memory, it must be ensured that each process has a separate memory space, including operation system. 
-The base register and limit register, whose roles are lower boound of memory region and specific size of range respectively, can achieve that goal.
+The base register and limit register, whose roles are lower bound of memory region and specific size of range respectively, can achieve that goal.
 
-Usually a program resides on a disk as binary excutable file. To run, the program must be brought into memory and placed within the context of a crocess.
-The process is binded to corresponding parts of the physical memory. Binding program to memeory address is staging process. 
-There three stages: compile time, load time excution time. The source program is compiled by compiler producing object file. 
+Usually a program resides on a disk as binary executable file. To run, the program must be brought into memory and placed within the context of a process.
+The process is bound to corresponding parts of the physical memory. Binding program to memory address is staging process. 
+There three stages: compile time, load time execution time. The source program is compiled by compiler producing object file. 
 After the compilation, the object file is linked with other object file by linker creating executable file . 
-Finally, the executable file will be loaded to run execute. At this run time dynamic linbrary link can be done.
+Finally, the executable file will be loaded to run execute. At this run time dynamic library link can be done.
 
@@
 There are several approaches to deal with this problems. However, we will focus on paging here, which is the most used method OS use to manage memory.
-A frame and page are a unit of Separated physical and virtaual memory space in fixed size (4KB or 8KB) respectively.
-A process can use as many as pages and correspinding frames obtained by page table matching. This strategy does improve external fragmentation, but not for internal fragmentation.
-The smaller size of page has smaller fragmentation, but mapping from page to grame has overhead and also disk I/O is more efficient when the amount of data transfered is larger.
+A frame and page are a unit of Separated physical and virtual memory space in fixed size (4KB or 8KB) respectively.
+A process can use as many as pages and corresponding frames obtained by page table matching. This strategy does improve external fragmentation, but not for internal fragmentation.
+The smaller size of page has smaller fragmentation, but mapping from page to frame has overhead and also disk I/O is more efficient when the amount of data transfered is larger.
 
@@
 \label{sec:history}
-A process can have mutiple pages. However, loading entire executable code from sendory storage to memory is not necessarily needed to 
-get jobs done. A storategy used in several operating systems is loading only the portion of programs that are needed, demand page.
+A process can have multiple pages. However, loading entire executable code from secondary storage to memory is not necessarily needed to 
+get jobs done. A strategy used in several operating systems is loading only the portion of programs that are needed, demand page.
 
-In the storatege, some pages currently used are in memory and the others are in secondary storage. 
+In the storage, some pages currently used are in memory and the others are in secondary storage. 
 The page table specifies whether pages are valid or invalid, which means are in memory or not. 
@@
 
-The first part of process of demand pageing would be that we check an internal table to check whether the reference is valide or invalid.
+The first part of process of demand paging would be that we check an internal table to check whether the reference is valid or invalid.
 If the reference is valid, the process reads the content from the memory. Otherwise, we terminates the process and find the free frame in 
@@
 
-However, there would be a case where the memory does not have any free frame. In this case, a victim frame that will be replaced with new comming frame should be selected. 
+However, there would be a case where the memory does not have any free frame. In this case, a victim frame that will be replaced with new coming frame should be selected. 
 To perform this selection efficiently, a modify bit is tracked for each frame or page. The modify bit represents whether the page is modified since it is loaded from secondary storage. 
-If the page or frame is modified, when we swap page we need to update the content in the secondary storage. However, it is not modified, we can simplly delete the frame and replace with new frame.
+If the page or frame is modified, when we swap page we need to update the content in the secondary storage. However, it is not modified, we can simply delete the frame and replace with new frame.
 

### 2020-03-09 project/playground/src/objects/access.rs

@@ -1,5 +1,6 @@
 use crate::objects::customer::*;
 use serde::ser::Serialize;
+use serde::de::DeserializeOwned;
 use std::fs::OpenOptions;
 use std::io::prelude::*;
 use std::time::Instant;
@@ -7,7 +8,7 @@ use std::net::SocketAddr;
 use std::error::Error;
 use std::io::BufReader;
 use std::path::Path;
-
+use std::fs::File;
 fn serialize<T>(customer: &T) 
 where T: Customer + Serialize, 
 {
@@ -28,13 +29,13 @@ fn serialize_vector<T, P>(customers: &[T], path: P)
     let mut file = OpenOptions::new()
                     .append(false)
                     .create(true)
-                    .open(file_name)
+                    .open(path)
                     .unwrap();
     file.write_all(serialized.as_bytes()).expect("Fail to write file.");
 }
 
 fn deserialize_vector<T, P>(path: P) -> Result<Vec<T>, Box<Error>>
-    where T: Customer + Serialize + Deserialize,
+    where T: Customer + Serialize + DeserializeOwned,
           P: AsRef<Path>
 {
     let file = File::open(path)?;
@@ -54,25 +55,25 @@ pub fn access_owned(customers: &Vec<CustomerOwned>) -> u128 {
     elapsed
 }
 
-// Function access object whose field is borrowed.
-pub fn access_borrowed(customers: &Vec<CustomerBorrowed>) -> u128 {
-    let len = customers.len();
-    let start = Instant::now();
-    for i in 0..len {
-        serialize(&customers[i])
-    }
-    let elapsed = start.elapsed().as_millis(); 
-    elapsed
-}
+// // Function access object whose field is borrowed.
+// pub fn access_borrowed(customers: &Vec<CustomerBorrowed>) -> u128 {
+//     let len = customers.len();
+//     let start = Instant::now();
+//     for i in 0..len {
+//         serialize(&customers[i])
+//     }
+//     let elapsed = start.elapsed().as_millis(); 
+//     elapsed
+// }
 
 
 
-pub fn access_rc(customers: &Vec<CustomerRc>) -> u128 {
-    let len = customers.len();
-    let start = Instant::now();
-    for i in 0..len {
-        serialize(&customers[i])
-    }
-    let elapsed = start.elapsed().as_millis(); 
-    elapsed
-}
+// pub fn access_rc(customers: &Vec<CustomerRc>) -> u128 {
[…]

### 2020-03-09 project/playground/src/objects/customer.rs

@@ -3,6 +3,7 @@ use crate::objects::order::OrderOwned;
 use std::time::Instant;
 use std::cmp::Ordering;
 use serde::ser::{Serialize, Serializer, SerializeStruct};
+use serde::de::{self, Deserialize, Deserializer, Visitor, SeqAccess, MapAccess};
 use std::fmt;
 use std::marker::{Send, Sync};
 //use std::sync::Arc;
@@ -524,6 +525,258 @@ impl Serialize for CustomerOwned {
         state.serialize_field("comment", &self.comment)?;
         state.serialize_field("order", &self.order)?;
         state.end()
+    }
+}
+
+
+impl<'de> Deserialize<'de> for CustomerOwned {
+    fn deserialize<D>(deserializer: D) -> Result<Self, D::Error>
+    where D: Deserializer<'de>,
+    {
+        enum Field {Key, Age, NumPurchase, TotalPurchase, DurationSpent, DurationSince, 
+                    ZipCode, Address, Country, State, FirstName, 
+                    LastName, Province, Comment, Order};
+
+        impl<'de> Deserialize<'de> for Field {
+            fn deserialize<D>(deserializer: D) -> Result<Field, D::Error>
+            where D: Deserializer<'de>, 
+            {
+                struct FieldVisitor;
+
+                impl<'de> Visitor<'de> for FieldVisitor {
+                    type Value = Field;
+
+                    fn expecting(&self, formatter: &mut fmt::Formatter) -> fmt::Result {
+                        formatter.write_str("9 fields")
+                    }
+
+                    fn visit_str<E>(self, value: &str) -> Result<Field, E>
+                    where E: de::Error, 
+                    {
+                        match value {
+                            "key" => Ok(Field::Key), 
+                            "age" => Ok(Field::Age), 
+                            "num_purchase" => Ok(Field::NumPurchase),  
+                            "total_purchase" => Ok(Field::TotalPurchase),
+                            "duration_spent" => Ok(Field::DurationSpent),
+                            "duration_since" => Ok(Field::DurationSince),
+                            "zip_code" => Ok(Field::ZipCode),
+                            "address" => Ok(Field::Address),
+                            "country" => Ok(Field::Country),
+                            "state" => Ok(Field::State),
+                            "first_name" => Ok(Field::FirstName),
+                            "last_name" => Ok(Field::LastName),
+                            "province" => Ok(Field::Province),
+                            "comment" => Ok(Field::Comment),
[…]

### 2020-03-09 project/playground/src/objects/order.rs

@@ -1,9 +1,11 @@
-use std::rc::Rc;
+//use std::rc::Rc;
 use serde::ser::{Serialize, Serializer, SerializeStruct};
+use serde::de::{self, Deserialize, Deserializer, Visitor, SeqAccess, MapAccess};
 use std::cmp::Ordering;
-use std::marker::Send;
-use std::sync::Arc;
+//use std::marker::Send;
+//use std::sync::Arc;
 use std::default::Default;
+use std::fmt;
 
 #[derive(Clone, Debug, Default)]
 pub struct OrderOwned {
@@ -14,34 +16,34 @@ pub struct OrderOwned {
     title: String,
     comment: String
 }
-#[derive(Clone, Debug)]
-pub struct OrderBorrowed<'a> {
-    order_id: &'a i32,
-    num_items: &'a i32, 
-    payment: &'a f64,
-    order_time: &'a f64,
-    title: &'a String,
-    comment: &'a String
-}
+// #[derive(Clone, Debug)]
+// pub struct OrderBorrowed<'a> {
+//     order_id: &'a i32,
+//     num_items: &'a i32, 
+//     payment: &'a f64,
+//     order_time: &'a f64,
+//     title: &'a String,
+//     comment: &'a String
+// }
 
-#[derive(Clone, Debug, Default)]
-pub struct OrderRc {
-    order_id: Rc<i32>,
-    num_items: Rc<i32>, 
-    payment: Rc<f64>,
-    order_time: Rc<f64>,
-    title: Rc<String>,
-    comment: Rc<String>
-}
-#[derive(Clone, Debug, Default)]
-pub struct OrderArc {
-    order_id: Arc<i32>,
-    num_items: Arc<i32>, 
-    payment: Arc<f64>,
-    order_time: Arc<f64>,
-    title: Arc<String>,
-    comment: Arc<String>
-}
+// #[derive(Clone, Debug, Default)]
+// pub struct OrderRc {
+//     order_id: Rc<i32>,
+//     num_items: Rc<i32>, 
+//     payment: Rc<f64>,
+//     order_time: Rc<f64>,
+//     title: Rc<String>,
+//     comment: Rc<String>
+// }
+// #[derive(Clone, Debug, Default)]
+// pub struct OrderArc {
+//     order_id: Arc<i32>,
+//     num_items: Arc<i32>, 
+//     payment: Arc<f64>,
+//     order_time: Arc<f64>,
+//     title: Arc<String>,
+//     comment: Arc<String>
+// }
 impl OrderOwned {
[…]

### 2020-03-10 thesis_template/2_RelatedWork/model/spark.tex
added GC tuning section

@@
 
-\begin{itemize}
-    \item GC tuning solutions
-    \item Annotation, off-heap solution 
-\end{itemize}
+\section{Garbage Collection Tuning}
+\label{sec:history}
+Several solutions are suggested. Main idea is to reduce number of object and execution of GC. 
+One is avoiding pointer-based data structures, such as HashMap and LinkedList. These objects have a "wrapper" object for each entry 
+so that number of object tends to be larger than when when an array is used. Caching serialized object in memory also reduce number of object and memory usage 
+since the set of objects become a byte array. In addition, developers can allocate byte array off-heap of JVM to avoid tracking by GC. 
+Although these memory management solution for GC help developer improve performance of Spark applications, the effort to discover the best GC tuning afflicts developers.
 

### 2020-03-10 thesis_template/2_RelatedWork/model/tree_aggregate_experiment.tex
added GC tuning section

Tree-aggregate is a communication patten heavily used for Machine Learning algorithm in Spark (MLlib). 
In the traditional aggregation function in Spark, results of aggregation in all executor clusters are sent to the driver. 
That is why this operation suffers from the CUP cost in merging partial results and the network bandwidth limit.
Tree-aggregate is a communication pattern which overcomes these problems by breaking aggregate operation in multi-level represented like tree structure.

In multi-thread situation, tree-aggregate is just fork-join thread algorithm. We already implemented Merge-Sort algorithm with fork-join. 
If we implement tree-aggregate with multi-thread, the difference is only aggregation and sorting.

### 2020-03-10 project/playground/src/main.rs

@@ -21,91 +21,19 @@ fn main() {
     let args: Vec<String> = env::args().collect();
     let size: usize = args[1].parse().unwrap();
     let method: i32 = args[2].parse().unwrap(); 
-    run(method, size);
+    // run(method, size);
 }
 
-fn run(method: i32, size: usize) {
-    match method {
-        1 => run_ex_shared(size),
-        2 => run_ex_scope(size),
-       //3 => run_ex_linkedlist(size),
-        _ => println!("Wrong input!")
-    }
-}
+// fn run(method: i32, size: usize) {
+//     match method {
+//         1 => run_ex_shared(size),
+//         2 => run_ex_scope(size),
+//        //3 => run_ex_linkedlist(size),
+//         _ => println!("Wrong input!")
+//     }
+// }
 
-fn run_ex_shared(size: usize) {
-    let order_ids = get_integer_vector(size);
-    let num_itemss = get_integer_vector(size);
-    let payments = get_float_vector(size);
-    let order_times = get_float_vector(size);
-    let titles = get_string_vector(size);
-    let comments_order = get_string_vector(size);
-    let orders = get_order_owned_vector(size, order_ids, num_itemss, payments, order_times, titles, comments_order);
-    
-    let keys = get_integer_vector(size);
-    let ages = get_integer_vector(size);
-    let num_purchases = get_integer_vector(size);
-    let total_purchases = get_float_vector(size);
-    let duration_spents = get_float_vector(size);
-    let duration_sinces = get_float_vector(size);
-    let zip_codes = get_string_vector(size);
-    let addresss = get_string_vector(size);
-    let countrys = get_string_vector(size);
-    let states = get_string_vector(size);
-    let first_names = get_string_vector(size);
-    let last_names = get_string_vector(size);
-    let provinces = get_string_vector(size);
-    let comments = get_string_vector(size);
-
-    let (_, customers) = create_customer_onwed_vector(size, keys, ages, num_purchases, total_purchases, duration_spents, duration_sinces, 
-                                                                    zip_codes, addresss, countrys, states, first_names, last_names, provinces, comments, orders);
-
-    let q_custorms = VecDeque::from(customers);
-    
-    let (elapsed_sort, sorted) = mergesort_vecdeque(q_custorms, 0, size);
-    let (slice, _) = sorted.as_slices();
-    access_owned(slice);
-    write_to_file(size, "shared", elapsed_sort);
-    
-}
-
-
-fn run_ex_scope(size: usize) {
[…]

### 2020-03-10 project/playground/src/objects/access.rs

@@ -34,7 +34,7 @@ fn serialize_vector<T, P>(customers: &[T], path: P)
     file.write_all(serialized.as_bytes()).expect("Fail to write file.");
 }
 
-fn deserialize_vector<T, P>(path: P) -> Result<Vec<T>, Box<Error>>
+pub fn deserialize_vector<T, P>(path: P) -> Result<Vec<T>, Box<Error>>
     where T: Customer + Serialize + DeserializeOwned,
           P: AsRef<Path>
 {

### 2020-03-10 project/playground/src/objects/aggregate.rs

@@ -5,7 +5,7 @@ use crate::objects::customer::*;
 use crate::objects::access::*;
 const MAX_THREADS: usize = 4;
 
-fn tree_aggregate_sum<P: AsRef<Path>>(arr: Arc<Vec<P>>, left: usize, right: usize, depth: usize)
+fn tree_aggregate_sum(arr: Arc<Vec<String>>, left: usize, right: usize, depth: usize) -> i32
 {   
     let sum_current;
     let path;
@@ -21,12 +21,12 @@ fn tree_aggregate_sum<P: AsRef<Path>>(arr: Arc<Vec<P>>, left: usize, right: usiz
             let (sender1, receiver1) = crossbeam::channel::unbounded();
             let (sender2, receiver2) = crossbeam::channel::unbounded(); 
         
-            let _ = thread::spawn(move |_| {
+            let _ = thread::spawn(move || {
                let sum = tree_aggregate_sum(arr_cloned1, left, mid, new_depth);
                sender1.send(sum).unwrap();
             });
             
-            let _ = thread::spawn(move |_| {
+            let _ = thread::spawn(move || {
                 let sum = tree_aggregate_sum(arr_cloned2, mid, right, new_depth);
                 sender2.send(sum).unwrap();
              });
@@ -39,27 +39,28 @@ fn tree_aggregate_sum<P: AsRef<Path>>(arr: Arc<Vec<P>>, left: usize, right: usiz
             sum_right = tree_aggregate_sum(arr_cloned2, mid, right, new_depth);
         }
         return tree_reduce_sum(sum_current, sum_left, sum_right);
-    } else if (right - left == 1) {
+    } else {
         let mid = (right - left) / 2;
         path = arr[mid];
         sum_current = add_local(path);
-        return tree_aggregate_sum(sum_current, 0, 0);
+        return sum_current;
     }    
 }
 
-fn tree_reduce_sum<T>(sum_current: i32,  sum_left: i32, sum_right: i32) 
+fn tree_reduce_sum(sum_current: i32,  sum_left: i32, sum_right: i32) -> i32
 {
     let sum =  sum_left + sum_current + sum_right;
     sum
 }
 
-fn add_local<P: AsRef<Path>>(path: P) {
-    let customers = deserialize_vector(file).unwrap();
+fn add_local<P: AsRef<Path>>(path: P) -> i32 
+{
+    let customers = deserialize_vector(path).unwrap();
[…]

### 2020-03-10 thesis_template/2_RelatedWork/model/spark.tex
application to system

@@
 \label{sec:history}
+Considered overhead produced by Memory Management in JVM, we suggest application of system language to Big Data tool rather than application language, such as Java and Scala. 
+System languages, such as C and C++, are languages that give developer total control over the hardware and de/allocation of memory without GC. 
+These features enable program written in system languages to optimized performance taking full advantage of hardware.
+
+To take example, one can build Big Data tool with C++. C++ is one of the most popular system languages which has Object-oriented features. 
+C++ has functions which provide control over memory to developers. In another word, it is responsibility for one to manage memory properly and safely. 
+The functions, malloc() and free(), take roll for memory allocation and deallocation in respectively. The manual memory de/allocation may cause several problems and require developers 
+attention to the problems with significant effort for debugging and testing. Here, we explain two of the most common problems regarding to memory management in existing system languages.
+
+Dangling pointer or reference is a pointer or reference pointing to object that no longer exists. The situation of dangling pointer happens 
+because of deallocation of memory without modification of value of the pointer. 
+If the memory region is reallocated for other object and the dangling pointer tries to access the original object, the unpredictable behavior may result.
+
+Memory leak occurs when memory is allocated and no longer referenced so that the object in the memory location cannot be reached and released.
+This is result of dereferencing object with deallocation. Memory leak consumes more memory than necessary by making unreachable location.
+
+Some solutions are established to address these problems. Actually GC is a high-level solution that guarantees memory safety. 
+C++ has a different solution called Resource Acquisition is Initialization (RAII). In RAII, objects can live within the scope where they are created. 
+The memory is released when the object goes out of scope. This solution is more predictable and deterministic than GC. 
+However, it is problematic When we need the object out of the scope, returning a value from a function. 
+There are several ways to go around this problems, such as smart pointers, copy constructors, and move semantics. 
+Nevertheless, these non-orthogonal concepts makes code in disorganize and leads to error prone implementation.
+
+\section{Region-Based Memory Management}
+\label{sec:history}

### 2020-03-10 project/playground/src/objects/aggregate.rs

@@ -8,7 +8,6 @@ const MAX_THREADS: usize = 4;
 fn tree_aggregate_sum(arr: Arc<Vec<String>>, left: usize, right: usize, depth: usize) -> i32
 {   
     let sum_current;
-    let path;
     if right - left > 1 {
         let mid = (left + right) / 2;
         let new_depth = depth + 1;
@@ -16,7 +15,7 @@ fn tree_aggregate_sum(arr: Arc<Vec<String>>, left: usize, right: usize, depth: u
         let arr_cloned2 = Arc::clone(&arr);
         let sum_left;
         let sum_right;
-        path = arr[mid];
+        let path = &arr[mid];
         if new_depth < MAX_THREADS {
             let (sender1, receiver1) = crossbeam::channel::unbounded();
             let (sender2, receiver2) = crossbeam::channel::unbounded(); 
@@ -41,7 +40,7 @@ fn tree_aggregate_sum(arr: Arc<Vec<String>>, left: usize, right: usize, depth: u
         return tree_reduce_sum(sum_current, sum_left, sum_right);
     } else {
         let mid = (right - left) / 2;
-        path = arr[mid];
+        let path = &arr[mid];
         sum_current = add_local(path);
         return sum_current;
     }    
@@ -55,13 +54,12 @@ fn tree_reduce_sum(sum_current: i32,  sum_left: i32, sum_right: i32) -> i32
 
 fn add_local<P: AsRef<Path>>(path: P) -> i32 
 {
-    let customers = deserialize_vector(path).unwrap();
+    let customers: Vec<CustomerOwned> = deserialize_vector(path).unwrap();
     let sum_current = add_customer_key(&customers[..]);
     sum_current
 }
 
-fn add_customer_key<T>(customers: &[T]) -> i32
-    where T: Clone + Customer + PartialOrd + Send + Sync + Default
+fn add_customer_key(customers: &[CustomerOwned]) -> i32
 {
     let mut sum = 0;
     for i in 0..customers.len() {

### 2020-03-10 project/playground/src/objects/customer.rs

@@ -21,7 +21,7 @@ pub trait Customer {
 // Objects whose fields are all owned.
 #[derive(Clone, Debug, Default)]
 pub struct CustomerOwned {
-    key: i32,
+    pub key: i32,
     age: i32,
     num_purchase: i32,
     total_purchase: f64,

### 2020-03-12 thesis_template/2_RelatedWork/model/spark.tex
added memory management in Rust

@@
 \label{sec:history}
+
+\section{Rust Memory Management}
+\label{sec:history}
+Rust is a system programming language which provides memory safety without runtime checking like GC and necessity of explicit memory de/allocation. 
+In addition to characteristic of memory safety, this language also enables a developer to write concurrent code , fearless concurrency. 
+Developers are able to write code with high performance given fair control of hardware and safety forced to follow restrictive pattern.
+
+Main concepts of Memory Management in Rust are ownership, move, and borrowing. In ownership feature or Rust, each value has a variable called its owner.
+This owner has information about the value, such as location in memory, length and capacity of the value. This owner can live on the scope associated with its lifetime.
+When the owner goes out of it’s scope, the value will be dropped. This feature is similar to how RAII in C++ works. 
+However, acquisition of owner out of the scope where it was constructed is available in Rust with the concept of move.
+
+With move, a value can be transferred from one owner to another, For example, a value is instantiated in a function. 
+When it is returned to a new variable , the ownership of value is moved to the new variable. In Rust, one do not have to explicitly deallocate memory, 
+because ownership of value is passed among variables across scope using move and eventually goes out of scope deallocating memory of the value.
+
+Borrowing lets code use a value temporarily without affecting its ownership so that it reduces unnecessary movement of ownership. 
+One use case is when value is used in function and needed to be passed to the argument. If the argument takes ownership and the function does not return the value, 
+the ownership of value goes out of scope and the memory is deallocated. One can pass reference of the value to the argument instead of owner. 
+The reference goes out of scope, but ownership remains the same.

### 2020-03-12 project/playground/src/main.rs

@@ -4,7 +4,7 @@ extern crate serde;
 extern crate bytes;
 use std::env;
 mod objects;
-use objects::customer::create_customer_onwed_vector;
+use objects::customer::{create_customer_onwed_vector, Customer};
 use objects::order::get_order_owned_vector;
 use objects::field::*;
 //use objects::dropping::*;
@@ -16,142 +16,122 @@ use std::collections::VecDeque;
 use std::fs::OpenOptions;
 use std::io::prelude::*;
 use objects::access::*;
+use objects::aggregate::*;
+use std::path::Path;
+use std::io::prelude::*;
 
 fn main() {
     let args: Vec<String> = env::args().collect();
     let size: usize = args[1].parse().unwrap();
-    let method: i32 = args[2].parse().unwrap(); 
-    // run(method, size);
+    let num_partition: usize = args[2].parse().unwrap();
+    let method: i32 = args[3].parse().unwrap();
+    if size < num_partition {
+        println!("Size and number of partition!");
+    } else {
+        run(method, size, num_partition);     
+    }
 }
 
-// fn run(method: i32, size: usize) {
-//     match method {
-//         1 => run_ex_shared(size),
-//         2 => run_ex_scope(size),
-//        //3 => run_ex_linkedlist(size),
-//         _ => println!("Wrong input!")
-//     }
+fn run(method: i32, size: usize, num_partition: usize) {
+    match method {
+        1 => run_ex_shared(size, num_partition),
+       // 2 => run_ex_copy(size),
+        _ => println!("Wrong input!")
+    }
+}
+
+fn run_ex_shared(size: usize, num_partition: usize) {
+    println!("running");
+    let order_ids = get_integer_vector(size);
+    let num_itemss = get_integer_vector(size);
+    let payments = get_float_vector(size);
+    let order_times = get_float_vector(size);
+    let titles = get_string_vector(size);
+    let comments_order = get_string_vector(size);
+    let orders = get_order_owned_vector(size, order_ids, num_itemss, payments, order_times, titles, comments_order);
+    
+    let keys = get_integer_vector(size);
+    let ages = get_integer_vector(size);
+    let num_purchases = get_integer_vector(size);
+    let total_purchases = get_float_vector(size);
+    let duration_spents = get_float_vector(size);
+    let duration_sinces = get_float_vector(size);
+    let zip_codes = get_string_vector(size);
+    let addresss = get_string_vector(size);
+    let countrys = get_string_vector(size);
+    let states = get_string_vector(size);
[…]

### 2020-03-12 project/playground/src/objects/access.rs

@@ -24,18 +24,31 @@ where T: Customer + Serialize,
     file.write_all(serialized.as_bytes()).expect("Fail to write file.");
 }
 
-fn serialize_vector<T, P>(customers: &[T], path: P) 
+pub fn serialize_vector<T, P>(customers: Vec<T>, partition: &String) 
     where T: Customer + Serialize,
           P: AsRef<Path> 
 {
-    let serialized = serde_json::to_string(customers).unwrap();
+    let serialized = serde_json::to_string(&customers).unwrap();
+    let path = Path::new(&partition);
     let mut file = OpenOptions::new()
-                    .append(false)
-                    .create(true)
-                    .open(path)
+                    .create_new(true)
+                    .open(&path)
                     .unwrap();
     file.write_all(serialized.as_bytes()).expect("Fail to write file.");
 }
+
+pub fn serialize_vector_arc<T>(customers: Vec<Arc<T>>, partition: &String) 
+where T: Customer + Serialize
+{
+    let serialized = serde_json::to_string(&customers).unwrap();
+    let path = Path::new(&partition);
+    println!("serialized");
+    let mut file = OpenOptions::new()
+                .create_new(true)
+                .open(&path)
+                .unwrap();
+    file.write_all(serialized.as_bytes()).expect("Fail to write file.");
+} 
 
 pub fn deserialize_vector<T, P>(path: P) -> Result<Vec<T>, Box<Error>>
     where T: Customer + Serialize + DeserializeOwned,

### 2020-03-12 project/playground/src/objects/aggregate.rs

@@ -4,8 +4,20 @@ pub use std::sync::Arc;
 use crate::objects::customer::*;
 use crate::objects::access::*;
 use std::collections::HashMap;
+use std::time::Instant;
+
+
 
 const MAX_THREADS: usize = 4;
+
+pub fn tree_aggregate_run(paths: Arc<Vec<String>>) -> (u128, HashMap<String, Vec<Arc<CustomerOwned>>>)
+{
+    let start = Instant::now();
+    let n = paths.len();
+    let res = tree_aggregate(paths, 0, n, 0);
+    let elapsed = start.elapsed().as_micros(); 
+    return (elapsed, res)
+}
 
 fn tree_aggregate(paths: Arc<Vec<String>>, left: usize, right: usize, depth: usize) -> HashMap<String, Vec<Arc<CustomerOwned>>>
 {   

### 2020-03-16 thesis_template/2_RelatedWork/model/tree_aggregate_experiment.tex
added documentation

@@
 In the traditional aggregation function in Spark, results of aggregation in all executor clusters are sent to the driver. 
-That is why this operation suffers from the CUP cost in merging partial results and the network bandwidth limit.
+That is why this operation suffers from the CPU cost in merging partial results and the network bandwidth limit.
 Tree-aggregate is a communication pattern which overcomes these problems by breaking aggregate operation in multi-level represented like tree structure.
 
-In multi-thread situation, tree-aggregate is just fork-join thread algorithm. We already implemented Merge-Sort algorithm with fork-join. 
-If we implement tree-aggregate with multi-thread, the difference is only aggregation and sorting.
+In our experiment, tree-aggregation algorithms are examined in multi-threading. This experiment is to evaluate the impact of having Arc (Atomic Reference Counting) as elements of vector. 
+In Big Data mining tool, such as Spark, it generates intermediate objects from original source vector. In tree-aggregation, aggregated HashMap like data structure is created in each step or node. 
+When this aggregated data structure is generated, two ways to acquire elements from source vector: deep copy and getting reference.
+
+Two algorithms are implemented and evaluated their runtime performance. The both algorithms perform tree-aggregation where runs seven nodes. 
+Each node load Customer vector from disk and aggregate it by Customer last name. Once a node finishes aggregation, it sends result to parent node. 
+After parent nodes receive aggregation results from all of its children nodes, it joins all aggregation results including its and sends next parent. 
+One algorithm performs aggregation by deep-copying elements from source vector loaded from disk. In the other algorithm, each element of source vector 
+is wrapped in Arc, and its reference is acquired while aggregation.
+
+Figure shows runtime performance of two tree-aggregate algorithms. The runtime of algorithm with deep-copy is slower than algorithm with Arc for every vector size. 
+This is result of overhead of deep-copy is larger than deletion of Arc. As we explained, Arc has overhead to be deleted because it has to check if the value is still referred. 
+Even though the deletion of Arc is slow, deep copy of complex objects has more impact in deterioration of runtime performance. 
+In the algorithm with deep copy, the elements of each partition in each node are deep-copied once during aggregation. 
+If total number of elements are 1000000, the all of 1000000 elements are deep-copied once during execution.
+On the other hand, acquisition and deletion of Arc occurs several time for each element object.
+First, acquisition of Arc of all elements in loaded vector happens during aggregation in each node and the loaded vector is deleted after the aggregation. 
+Second, deletion of all elements in aggregated structures from children nodes and the node is occurs after joining these aggregated structures to single one. 
+The result shows a deep-copy of Customer vector is computationally much more expensive than acquisition and deletion of Arc.
+
+This result suggests that having element objects in Arc is efficient than deep-copying element from original source vector in tree-aggregation algorithm 
+where generates intermediate data structure. The intermediate data structure is
+
+\begin{figure}[htb]
+    \includegraphics[width=15cm]{rust_tree_aggregate.eps}
+    \caption{Runtime of Tree-aggregate algorithm}
+    \label{fig:Sampling}
+\end{figure}

### 2020-03-17 thesis_template/2_RelatedWork/relatedWork.tex
added documentation
documented

@@
 
-\section{Memory Management in Rust}
-\label{sec:history}
-\input{2_RelatedWork/model/rust_memory_management}
-
-\section{State of the Art}
 \label{sec:history}
@@
 \input{2_RelatedWork/model/serialization}
-
-\section{Experiment of Memory Allocation}
-\label{sec:history}
-This experiment is to test how static and dynamic memory allocation of Java and Rust behave. For the assessment, Element addition to ArrayList in the case of Java and Vector in the case of Rust 
-is emploied here.
-These data stractures are resizable and we have control to set initial size.
-There are two parameters; initial size of ArrayList or Vector and thier final size after additions of elements.
-We are interested in the impact to memory allocation by initial allocation and expantion to runtime.
-
-First, an ArrayList and an Vector are created with specified initial size.
-Then, in a loop, a element is added for each iteration until the size of the ArrayList or Vector get the specified final size.
-Each data structure has a different resizing strategy. When an ArrayList hits current limit of its size and expands the limit, it doubles the current size.  
-While Vector does not have specific strategy for its resizing, the expantions of size of both ArrayList and Vector might affect the digradation of runtime performance.
-
-To perform benchmarks, we use Java Microbenchamrk Hardness (JMH) for Java and Criterion for Rust. The benchmark time is calculated mean from several iterarions. 
-We warm up before the execution. The parameters are set in combination of initial size, 10, 100, 1000, and 10000 and final size, 9, 99, 999, 9999. 
-The results are shown in Figure 2-4 and 2-5.
-
-Discussions here are separated to two cases: when initial size is set bigger than final size and when final size is set bigger than initial size. 
-For ArrayList in Java, it shows performance significant degradation when the initial size is bigger than final size. When we create ArrayList with intial size of 1000 and add 99 elements 
-to the ArrayList, the the average execution time is 1125 ns. However, the average excution time when we create ArrayList with intial size of 100 and add 99 elements is 623 ns. 
-This degration is caused by the cost of initializing the large array.
-On the other hand, Rust Vector does not have significant cost for the initialization of size compared to the cost of addition of elements.
-In the case of Vector with initial size of 1000 and add 99 elements to the Vector, the average excution is 320 ns. In the case of the initial size of 100 and 99 elements additions, 
-the average excution is 279 ns. This is such small degradation compared to element addition in Vector.
-
-In ArrayList when the initial size is smaller than the final size, there can be degradation in performance. When its initial size and final size are set 100 and 999 respectively, 
-the average execution time is 10884 ns. However when its initial size and final size are set 1000 and 999 respectively, the average execution time is 4250 ns. 
-This result shows the degradation of in performance caused by the copy of existing elements into newly allocated array whose size is double of the last array.
-
-This characteristic can be seen in the case of Vector in Rust. Vector with initial size 100 and final size 999 performs the average excution time 3514 ns, 
-but one with initial size 1000 and final size 999 performs 2723 ns. When the Vector reachs its capacity, it allocates a larger buffer and copies the present elements to it.
-This cost results in the degradation of the average excution time.
-
-\begin{figure}[htb]
-    \includegraphics[width=15cm]{java_arraylist.eps}
-    \caption{Memory allocation of ArrayList in Java}
-    \label{fig:Sampling}
-\end{figure}
-
-\begin{figure}[htb]
-    \includegraphics[width=15cm]{rust_vector.eps}
-    \caption{Memory allocation of Vector in Rust}
-    \label{fig:Sampling}
-\end{figure}
-
-\section{Experiment of Memory Allocation for Different Element Type.}
-\label{sec:history}
-This experiment is to test how static and dynamic memory allocation of Java and Rust behave. For the assessment, Element addition to ArrayList in the case of Java and Vector in the case of Rust 
-is emploied here.
-These data stractures are resizable and we have control to set initial size.
-There are two parameters; initial size of ArrayList or Vector and thier final size after additions of elements.
-We are interested in the impact to runtime performance by initializing memory allocation and dynamicaly allocating memory space.
-
-First, an ArrayList and an Vector are created with specified initial size.
-Then, in a loop, a element is added for each iteration until the size of the ArrayList or Vector get the specified final size.
-Each data structure has a different resizing strategy. When an ArrayList hits current limit of its size and expands the limit, it doubles the current size.  
-While Vector does not have specific strategy for its resizing, the expantions of size of both ArrayList and Vector might affect the digradation of runtime performance.
-
-Second, four types of element are used for elements addition to each data structure: integer, array of charactors, string, and Customer object. 
-Assamption is that there would be different behavior between element additions of dynamically resizable and static size objects. 
-Customer object has three fields. These fields are total order, weight of order, and zip code whose types are integer (i32 in rust), double (f32 in rust), and string respectively.
-Figure 2-6 and 2-7 are representations of customer objects in Java and Rust.
-
-Figure 2-10, 2-11, 2-12, and 2-13 represent the result of the experiments. For both data structures, integer elements addition shows the fastest runtime among all object types. 
-This is because the compilers know each integer need 4 bytes to be stored in memory so that the space for memory that should be allocated is easily inspected. 
-For the same reason, the initialization of data structures whose elements are integers alaways improves runtim performance.
-
-The elements addition of strings and array of character behave similally among each languages.
-These two types of elements addition perform the similar speed and significantly slower than integer addition.
-Customer object addition is the slowest in Java. However, in Rust the addition of Customer object is the second fastest among all element typs.
-The impacts of initialization of Java ArrayList vary among elemet types. On the other hand, the initailization Rust Vector always improves runtime performance for any of 4 types of elements addition.
-
-\begin{figure}[htb]
-    \begin{lstlisting}
-        class Customer {
-            int totalOrder;
-            double weightOrder;
-            String zipCode;
-        }
-    \end{lstlisting}
-    \caption{Representation of Customer object in Java.}
-    \label{fig:Sampling}    
-\end{figure}
-
-\begin{figure}[htb]
-    \begin{lstlisting}
-        struct Customer {
-            total_order: i32,
-            weight_order: f32,
-            zip_code: String,
-        }
-    \end{lstlisting}
-    \caption{Representation of Customer object in Rust.}
-    \label{fig:Sampling}
-\end{figure}
-
-\begin{figure}[htb]
-    \includegraphics[width=15cm]{java_arraylist_log.eps}
-    \caption{Memory allocation of Java ArrayList}
-    \label{fig:Sampling}
-\end{figure}
-
-\begin{figure}[htb]
-    \includegraphics[width=15cm]{rust_vector_log.eps}
-    \caption{Memory allocation of Rust Vector}
-    \label{fig:Sampling}
-\end{figure}
-
-\begin{figure}[htb]
-    \includegraphics[width=15cm]{java_arraylist_difference.eps}
-    \caption{Difference of Memory allocation of Java ArrayList between Non-initialization and Initialization}
-    \label{fig:Sampling}
-\end{figure}
-
-\begin{figure}[htb]
-    \includegraphics[width=15cm]{rust_arraylist_difference.eps}
-    \caption{Difference of Memory allocation of Rust Vector between Non-initialization and Initialization}
-    \label{fig:Sampling}
-\end{figure}
 
@@
 \end{itemize}
-
-\begin{figure}[htb]
-    \includegraphics[width=15cm]{rust_merge_sort.eps}
-    \caption{mergesort}
-    \label{fig:Sampling}
-\end{figure}

### 2020-03-17 thesis_template/3_Body/model/different_element.tex
documented

This experiment is to test how static and dynamic memory allocation of Java and Rust behave. For the assessment, Element addition to ArrayList in the case of Java and Vector in the case of Rust 
is emploied here. These data stractures are resizable and we have control to set initial size. There are two parameters; initial size of ArrayList or Vector and thier final size after additions of elements. 
We are interested in the impact to runtime performance by initializing memory allocation and dynamicaly allocating memory space.

First, an ArrayList and an Vector are created with specified initial size. Then, in a loop, a element is added for each iteration until the size of the ArrayList or Vector get the specified final size. 
Each data structure has a different resizing strategy. When an ArrayList hits current limit of its size and expands the limit, it doubles the current size.  
While Vector does not have specific strategy for its resizing, the expantions of size of both ArrayList and Vector might affect the digradation of runtime performance.

Second, four types of element are used for elements addition to each data structure: integer, array of charactors, string, and Customer object. 
Assamption is that there would be different behavior between element additions of dynamically resizable and static size objects. 
Customer object has three fields. These fields are total order, weight of order, and zip code whose types are integer (i32 in rust), double (f32 in rust), and string respectively.
Figure 2-6 and 2-7 are representations of customer objects in Java and Rust.

Figure 2-10, 2-11, 2-12, and 2-13 represent the result of the experiments. For both data structures, integer elements addition shows the fastest runtime among all object types. 
This is because the compilers know each integer need 4 bytes to be stored in memory so that the space for memory that should be allocated is easily inspected. 
For the same reason, the initialization of data structures whose elements are integers alaways improves runtim performance.

The elements addition of strings and array of character behave similally among each languages. These two types of elements addition perform the similar speed and significantly slower than integer addition. 
Customer object addition is the slowest in Java. However, in Rust the addition of Customer object is the second fastest among all element typs.
The impacts of initialization of Java ArrayList vary among elemet types. On the other hand, the initailization Rust Vector always improves runtime performance for any of 4 types of elements addition.

\begin{figure}[htb]
    \begin{lstlisting}
        class Customer {
            int totalOrder;
            double weightOrder;
            String zipCode;
        }
    \end{lstlisting}
    \caption{Representation of Customer object in Java.}
    \label{fig:Sampling}    
\end{figure}

\begin{figure}[htb]
    \begin{lstlisting}
        struct Customer {
            total_order: i32,
            weight_order: f32,
            zip_code: String,
        }
    \end{lstlisting}
    \caption{Representation of Customer object in Rust.}
    \label{fig:Sampling}
\end{figure}

\begin{figure}[htb]
    \includegraphics[width=15cm]{java_arraylist_log.eps}
    \caption{Memory allocation of Java ArrayList}
    \label{fig:Sampling}
\end{figure}

\begin{figure}[htb]
    \includegraphics[width=15cm]{rust_vector_log.eps}
    \caption{Memory allocation of Rust Vector}
    \label{fig:Sampling}
\end{figure}

\begin{figure}[htb]
    \includegraphics[width=15cm]{java_arraylist_difference.eps}
    \caption{Difference of Memory allocation of Java ArrayList between Non-initialization and Initialization}
    \label{fig:Sampling}
\end{figure}

\begin{figure}[htb]
    \includegraphics[width=15cm]{rust_arraylist_difference.eps}
    \caption{Difference of Memory allocation of Rust Vector between Non-initialization and Initialization}
    \label{fig:Sampling}
\end{figure}

### 2020-03-17 thesis_template/3_Body/model/memory_allocation.tex
documented

This experiment is to test how static and dynamic memory allocation of Java and Rust behave. For the assessment, Element addition to ArrayList in the case of Java and Vector in the case of Rust 
is emploied here. These data stractures are resizable and we have control to set initial size. There are two parameters; initial size of ArrayList or Vector and thier final size after additions of elements. 
We are interested in the impact to memory allocation by initial allocation and expantion to runtime.

First, an ArrayList and an Vector are created with specified initial size. Then, in a loop, a element is added for each iteration until the size of the ArrayList or Vector get the specified final size. 
Each data structure has a different resizing strategy. When an ArrayList hits current limit of its size and expands the limit, it doubles the current size.  
While Vector does not have specific strategy for its resizing, the expantions of size of both ArrayList and Vector might affect the digradation of runtime performance.

To perform benchmarks, we use Java Microbenchamrk Hardness (JMH) for Java and Criterion for Rust. The benchmark time is calculated mean from several iterarions. 
We warm up before the execution. The parameters are set in combination of initial size, 10, 100, 1000, and 10000 and final size, 9, 99, 999, 9999. 
The results are shown in Figure 2-4 and 2-5.

Discussions here are separated to two cases: when initial size is set bigger than final size and when final size is set bigger than initial size. 
For ArrayList in Java, it shows performance significant degradation when the initial size is bigger than final size. When we create ArrayList with intial size of 1000 and add 99 elements 
to the ArrayList, the the average execution time is 1125 ns. However, the average excution time when we create ArrayList with intial size of 100 and add 99 elements is 623 ns. 
This degration is caused by the cost of initializing the large array. On the other hand, Rust Vector does not have significant cost for the initialization of size compared to the cost of addition of elements. 
In the case of Vector with initial size of 1000 and add 99 elements to the Vector, the average excution is 320 ns. In the case of the initial size of 100 and 99 elements additions, 
the average excution is 279 ns. This is such small degradation compared to element addition in Vector.

In ArrayList when the initial size is smaller than the final size, there can be degradation in performance. When its initial size and final size are set 100 and 999 respectively, 
the average execution time is 10884 ns. However when its initial size and final size are set 1000 and 999 respectively, the average execution time is 4250 ns. 
This result shows the degradation of in performance caused by the copy of existing elements into newly allocated array whose size is double of the last array.

This characteristic can be seen in the case of Vector in Rust. Vector with initial size 100 and final size 999 performs the average excution time 3514 ns, 
but one with initial size 1000 and final size 999 performs 2723 ns. When the Vector reachs its capacity, it allocates a larger buffer and copies the present elements to it.
This cost results in the degradation of the average excution time.

\begin{figure}[htb]
    \includegraphics[width=15cm]{java_arraylist.eps}
    \caption{Memory allocation of ArrayList in Java}
    \label{fig:Sampling}
\end{figure}

\begin{figure}[htb]
    \includegraphics[width=15cm]{rust_vector.eps}
    \caption{Memory allocation of Vector in Rust}
    \label{fig:Sampling}
\end{figure}

### 2020-03-17 thesis_template/3_Body/model/merge_sort_experiment.tex
documented

--- 2020-03-04 thesis_template/2_RelatedWork/model/merge_sort_experiment.tex
@@
 This experiment is to assess importance of careful memory management in multithreading of Rust. 
-We implement merge-sort algorithm in three different ways. One is sharing source vector with Arc. 
-Another is passing slice of source vector to child thread. The other is LinkedList implementation other than vector.
+We implement merge-sort algorithm in two different ways. One is sharing source vector with Arc. 
+The other is passing slice of source vector to child thread.
 
@@
 For passing slice implementation, we use scope method to enable children threads to receive reference from their parent ensuring the same purpose of sending data.
+
+Experiment performed is the comparison among sharing data and passing slice implementations to see the impact of Arc, Atomic reference conuting, to runtime performance.
+These two implementations are theoritically the same operations other than using or not using Arc to share data. 
+This comparison can effectively show how important careful memory management is in multithreading computation in Rust. 
+In another word, how atomic reference counting can cost for computation in Rust programming.
+
+The figure shows the result of 
+An atomic reference count of the shareable vector is passed to every recursion steps and
+
+\begin{figure}[htb]
+    \includegraphics[width=15cm]{rust_merge_sort.eps}
+    \caption{Runtime of Sortting Elements of Customer Vector}
+    \label{fig:Sampling}
+\end{figure}
+
+The other is LinkedList implementation other than vector.
 The linkedlist implementation is different from another two. This algorithm is inplace sorting so that it does not de/allocate memory during execution. 
-
-The comparison among sharing data and passing slice implementations is to see the impact of Arc, Atomic reference conuting, to runtime performance.
-These two implementations are doing the same operations other than using or not using Arc to share data. 
-This comparison can effectively show how important careful memory management is in multithreading computation in Rust.
-
-One concern of these vector implementation is that type of elements of vector. To create merged vector in every merging phase, we need to get element value of vector at base case.
-To acquire the value of element, we need reference counting as element or copying the value of object. Both does not seem perform the best in other languages.
-
 The comparison among vector and linkedlist implementations can show trade-off between contiguous memory access and inplace non memory de/allocation. 

### 2020-03-19 thesis_template/2_RelatedWork/relatedWork.tex
Tree-aggregate documented on process

@@
 \input{2_RelatedWork/model/spark}
-
-\section{Memory Management Problems of Java}
-\label{sec:history}
-\input{2_RelatedWork/model/manual_memory_management}
+\clearpage
 
@@
 \input{2_RelatedWork/model/serialization}
+\clearpage
 
@@
 \end{figure}
+\clearpage
 
@@
 
-\section{Access time to onwned, borrowed, and sliced field of object}
+\section{Access time to owned, borrowed, and sliced field of object}
 \label{sec:history}
 In this experiment, differences of access time to among owned, borrowed, and sliced are observed. 
-Each variable has slightly different use of memomry.
+Each variable has slightly different use of memory.
 
@@
 
-\section{Accessment of different reference methods in Rust}
-\label{sec:history}
-The goal of this experiment is to assess efficiency of different reference strategies in Rust, borrowing and reference counting.
-
-By levaraging reference counting, a value can be shared like what borrowing plays the role in Rust programming. 
-The difference is that reference counting checks number of reference pointing to the actual data and makes sure the data is not deleted 
-until all the references are dereferenced. Using reference counting is sometimes preferable approach for developers, 
-we do not have care about lifetime which is usually troublesome when we use borrowing approach many times in our code. 
-However, the possible problem regarding to reference counting is the cost for tracking the number of references. 
-Having this assumption, this experiment will show difference of behavior among reference countinig and borrowing.
-
-In this experiment, CustomerBorrowed and CustomerRc in figure are used to see difference of dropping time among borrowing and reference counting. 
-In the CustomerRc and OrderRc struct, all fields take reference counting (Rc$<$T$>$). Similaly to the experiment in the last section, 
-vectors of CustomerRc and CustomerBorrowed are created and droped the elements one by one.
-
-The result shows significant difference of dropping time among the two objects; deletion of CustomerRc is much slower than CustomerBorrowed. 
-This is because reference counters which are feilds of CustomerRc have to check the number of reference pointing to the actual content and decide 
-deallocate the memory or not. However, memory management and lifetime strategy of borrowing is already determined at compile time.
-
-\section{Time to Drop Reference vs Reference Counting}
-\label{sec:history}
-In this experiment, an assessment is conducted to valify whether there is difference between behavior of borrowing and reference counting. 
-These two methods can be used in similar situation. Especially, when we want reference to an original variable and keep the original variable until all of references are dereferenced, 
-we can have reference with both storategies, borrowing and reference counting. One advantage of using reference counting is that we do not have to pay attention to lifetime.
-However, the assumption here is that use of reference counting might be computationally expenesive than borrowing, because reference counting has to track the number of reference pointing to the value.
-Considered this assumption, we assess difference of time for dropping reference using borrowing and reference counting strategies.
-
-Similally to the last section, we implement struct whose fields are borrowing reference and reference counting and measure the time to drop the struct.
-
-The result shows the time to drop borrowing reference is significatly faster than reference counting.
-This says that we should use borrwoing storategies whenever high performance computation is critical.
-
-\begin{figure}[htb]
-    \includegraphics[width=15cm]{rust_droptime_borring_rc.eps}
-    \caption{Runtime for Droping to fields of Customer Object}
-    \label{fig:Sampling}
-\end{figure}
+\clearpage
 
@@
     \item Study about LLVM
+    \item Buffer pool
 \end{itemize}

### 2020-03-19 thesis_template/3_Body/model/drop_ref_rc.tex
Tree-aggregate documented on process

The goal of this experiment is to assess efficiency of different reference strategies in Rust, borrowing and reference counting.

By levaraging reference counting, a value can be shared like what borrowing plays the role in Rust programming. 
The difference is that reference counting checks number of reference pointing to the actual data and makes sure the data is not deleted 
until all the references are dereferenced. Using reference counting is sometimes preferable approach for developers, 
we do not have care about lifetime which is usually troublesome when we use borrowing approach many times in our code. 
However, the possible problem regarding to reference counting is the cost for tracking the number of references. 
Having this assumption, this experiment will show difference of behavior among reference countinig and borrowing.

In this experiment, CustomerBorrowed and CustomerRc in figure are used to see difference of dropping time among borrowing and reference counting. 
In the CustomerRc and OrderRc struct, all fields take reference counting (Rc$<$T$>$). Similaly to the experiment in the last section, 
vectors of CustomerRc and CustomerBorrowed are created and droped the elements one by one.

The result shows significant difference of dropping time among the two objects; deletion of CustomerRc is much slower than CustomerBorrowed. 
This is because reference counters which are feilds of CustomerRc have to check the number of reference pointing to the actual content and decide 
deallocate the memory or not. However, memory management and lifetime strategy of borrowing is already determined at compile time.

In this experiment, an assessment is conducted to valify whether there is difference between behavior of borrowing and reference counting. 
These two methods can be used in similar situation. Especially, when we want reference to an original variable and keep the original variable until all of references are dereferenced, 
we can have reference with both storategies, borrowing and reference counting. One advantage of using reference counting is that we do not have to pay attention to lifetime.
However, the assumption here is that use of reference counting might be computationally expenesive than borrowing, because reference counting has to track the number of reference pointing to the value. 
Considered this assumption, we assess difference of time for dropping reference using borrowing and reference counting strategies.

Similally to the last section, we implement struct whose fields are borrowing reference and reference counting and measure the time to drop the struct.

The result shows the time to drop borrowing reference is significatly faster than reference counting. This says that we should use borrwoing storategies whenever high performance computation is critical.

\begin{figure}[htb!]
    \includegraphics[width=15cm]{rust_droptime_borring_rc.eps}
    \caption{Runtime for Droping to fields of Customer Object}
    \label{fig:Sampling}
\end{figure}

### 2020-03-19 thesis_template/3_Body/model/tree_aggregate_experiment.tex
documented
Tree-aggregate documented on process

--- 2020-03-16 thesis_template/2_RelatedWork/model/tree_aggregate_experiment.tex
@@
+\subsection{Description}
 Tree-aggregate is a communication patten heavily used for Machine Learning algorithm in Spark (MLlib). 
@@
 In Big Data mining tool, such as Spark, it generates intermediate objects from original source vector. In tree-aggregation, aggregated HashMap like data structure is created in each step or node. 
-When this aggregated data structure is generated, two ways to acquire elements from source vector: deep copy and getting reference.
+Acquisition of elements in source vector is required to perform this aggregation. There are several ways.
 
-Two algorithms are implemented and evaluated their runtime performance. The both algorithms perform tree-aggregation where runs seven nodes. 
+One way is deep-copy elements of vector. This solution allocated newly created objects by deep-copy. 
+Aggregation is performed on copied objects, stores them in the data structure and sends it to next node. 
+Deep-copy generates duplicates of objects in vector and aggregated data structure. 
+This can lead to memory intensive moment when we need memory space for the duplicated objects in addition.
+
+The other way is to get reference to the elements. Since an original source vector is deallocated after a local aggregation,
+Simple reference to elements does not live long enough and allow the aggregation result to be sent to next node. 
+Instead of simple borrowing, we need owner in the aggregation result. Reference Counting (Rc) in Rust is a way to have multiple owners to a value. 
+Since our experiment is implemented in multithreading, Atomic Reference Counting (Arc) is used instead of Rc. With Arc, multiple ownership pointer can be 
+possessed by different variables across multiple threads. Therefore a value is not deallocated until all of owners to it are dropped. 
+This does not require extra memory allocation, because only acquisition of new ownership to value is needed. 
+However, deletion of Arc type checks whether the value is still owned by other variables. 
+This checking may be a overhead in algorithms where generate a lot of intermediate data structures, because deletion of the data structures occurs in frequent.
+
+Two algorithms are implemented using the above two different methods and evaluated their runtime performance. 
+The both algorithms perform tree-aggregation where runs seven nodes. 
 Each node load Customer vector from disk and aggregate it by Customer last name. Once a node finishes aggregation, it sends result to parent node. 
@@
 
+\subsection{Result}
+
 Figure shows runtime performance of two tree-aggregate algorithms. The runtime of algorithm with deep-copy is slower than algorithm with Arc for every vector size. 
-This is result of overhead of deep-copy is larger than deletion of Arc. As we explained, Arc has overhead to be deleted because it has to check if the value is still referred. 
-Even though the deletion of Arc is slow, deep copy of complex objects has more impact in deterioration of runtime performance. 
-In the algorithm with deep copy, the elements of each partition in each node are deep-copied once during aggregation. 
-If total number of elements are 1000000, the all of 1000000 elements are deep-copied once during execution.
-On the other hand, acquisition and deletion of Arc occurs several time for each element object.
-First, acquisition of Arc of all elements in loaded vector happens during aggregation in each node and the loaded vector is deleted after the aggregation. 
-Second, deletion of all elements in aggregated structures from children nodes and the node is occurs after joining these aggregated structures to single one. 
-The result shows a deep-copy of Customer vector is computationally much more expensive than acquisition and deletion of Arc.
-
-This result suggests that having element objects in Arc is efficient than deep-copying element from original source vector in tree-aggregation algorithm 
-where generates intermediate data structure. The intermediate data structure is
+This is result of overhead of deep-copy is larger than deletion of Arc.
 
@@
 \end{figure}
+
+\subsection{Discussion}
+As we explained, Arc has overhead to be deleted because it has to check if the value is still referred. 
+Even though the deletion of Arc is slow, deep copy of complex objects has more impact in deterioration of runtime performance. 
+In the algorithm with deep copy, the elements of each partition in each node are deep-copied once during aggregation.
+
+If total number of elements are 1000000, the all of 1000000 elements are deep-copied once during execution.
+On the other hand, acquisition and deletion of Arc occurs several time for each element object.
+First, acquisition of Arc of all elements in loaded vector happens during aggregation in each node and the loaded vector is deleted after the aggregation. 
+Second, deletion of all elements in aggregated structures from children nodes and the node is occurs after joining these aggregated structures to single one.
+
+The result shows a deep-copy of Customer vector is computationally much more expensive than acquisition and deletion of Arc. 
+This result suggests that having element objects in Arc is efficient than deep-copying element from original source vector in tree-aggregation algorithm 
+where generates intermediate data structure. The intermediate data structure can be seen in traditional Big Data tool.

### 2020-03-19 project/rust_vec_memalloc_for_different_type/run.sh

@@ -11,7 +11,7 @@ do
             sizes=( 3900000 3910000 3920000 3930000 3940000 )
         ;;
         "false")
-            sizes=( 3750000 3760000 3780000 3790000 3800000 )
+            sizes=( 3760000 3770000 3780000 3790000 3800000 )
         ;;
     esac
     for size in "${sizes[@]}"

### 2020-03-22 thesis_template/3_Body/model/merge_sort_experiment.tex
redo experiment for mergesort

@@
+\subsection{Description}
 This experiment is to assess importance of careful memory management in multithreading of Rust. 
+In Rust programming, we usually need Atomic Reference Counting (Arc) to share data among threads. 
+However, 
 We implement merge-sort algorithm in two different ways. One is sharing source vector with Arc. 
@@
 
+\subsection{Result}
+
 \begin{figure}[htb]
@@
 
+\subsection{Discussion}
+
 The other is LinkedList implementation other than vector.

### 2020-03-22 thesis_template/3_Body/model/tree_aggregate_experiment.tex
document chabged
redo experiment for mergesort

@@
 However, deletion of Arc type checks whether the value is still owned by other variables. 
-This checking may be a overhead in algorithms where generate a lot of intermediate data structures, because deletion of the data structures occurs in frequent.
+This checking may be an overhead in algorithms where generate a lot of intermediate data structures, because deletion of the data structures occurs in frequent.
 
 Two algorithms are implemented using the above two different methods and evaluated their runtime performance. 
-The both algorithms perform tree-aggregation where runs seven nodes. 
-Each node load Customer vector from disk and aggregate it by Customer last name. Once a node finishes aggregation, it sends result to parent node. 
+The both algorithms perform tree-aggregation where runs on seven partitions of source vector. 
+Each steps load Customer vector from disk and aggregate it by Customer last name. Once a node finishes aggregation, it sends result to parent node. 
 After parent nodes receive aggregation results from all of its children nodes, it joins all aggregation results including its and sends next parent. 
@@
 This result suggests that having element objects in Arc is efficient than deep-copying element from original source vector in tree-aggregation algorithm 
-where generates intermediate data structure. The intermediate data structure can be seen in traditional Big Data tool.
+where generates intermediate data structure.
+
+\begin{figure}[htb]
+    \begin{lstlisting}
+        fn aggregate_local(arr :&[Arc<CustomerOwned>]) 
+        {   
+            let mut agg = HashMap::new();
+            let n = arr.len();
+            for i in 0..n {
+                let customer = Arc::clone(&arr[i]);
+                let last_name = customer.last_name.clone();
+                let vector = agg.entry(last_name).or_insert_with(Vec::new);
+                vector.push(customer);
+            }
+            return agg;
+        }
+    \end{lstlisting}
+    \caption{Aggregation function with Arc}
+    \label{fig:Sampling}
+\end{figure}
+
+\begin{figure}[htb]
+    \begin{lstlisting}
+        fn aggregate_local_copy(arr :&[CustomerOwned]) 
+        {   
+            let mut agg = HashMap::new();
+            let n = arr.len();
+            for i in 0..n {
+                let customer = arr[i].clone();
+                let last_name = customer.last_name.clone();
+                let vector = agg.entry(last_name).or_insert_with(Vec::new);
+                vector.push(customer);
+            }
+            return agg;
+        }
+    \end{lstlisting}
+    \caption{Aggregation function with deep-copy}
+    \label{fig:Sampling}
+\end{figure}

### 2020-03-22 project/rust_merge_sort/src/objects/sort.rs

@@ -1,4 +1,3 @@
-use std::thread;
 pub use std::sync::{mpsc, Arc};
 //use std::cell::RefCell;
 use crate::objects::customer::*;
@@ -11,6 +10,16 @@ use std::time::Instant;
 
 const MAX_THREADS: usize = 4;
 
+// pub fn mergesort_vecdeque<T: 'static>(arr:VecDeque<T>, left: usize, right: usize) -> (u128, VecDeque<T>) 
+//     where T: Clone + Customer + PartialOrd + Send + Sync + Default
+// {
+//     let start = Instant::now();
+//     let res = merge_helper_vecdeque(Arc::new(arr), left, right, 0);
+//     let elapsed = start.elapsed().as_micros(); 
+//     return (elapsed, res)
+// }
+
+
 pub fn mergesort_vecdeque<T: 'static>(arr:VecDeque<T>, left: usize, right: usize) -> (u128, VecDeque<T>) 
     where T: Clone + Customer + PartialOrd + Send + Sync + Default
 {
@@ -21,38 +30,77 @@ pub fn mergesort_vecdeque<T: 'static>(arr:VecDeque<T>, left: usize, right: usize
 }
 
 
+// fn merge_helper_vecdeque<T: 'static>(arr: Arc<VecDeque<T>>, left: usize, right: usize, depth: usize) -> VecDeque<T>
+//     where T: Clone + Customer + PartialOrd + Send + Sync + Default
+// {
+//     if right - left > 1 {
+//         let mid = (left + right) / 2;
+//         let new_depth = depth + 1;
+//         let arr_cloned1 = Arc::clone(&arr);
+//         let arr_cloned2 = Arc::clone(&arr);
+//         let arr_right;
+//         let arr_left;
+
+//         if new_depth < MAX_THREADS {
+//             let (sender1, receiver1) = crossbeam::channel::unbounded();
+//             let (sender2, receiver2) = crossbeam::channel::unbounded(); 
+//             let _ = thread::spawn(move || {
+//                 let sorted = merge_helper_vecdeque(arr_cloned1, left, mid, new_depth);
+//                 sender1.send(sorted).unwrap();
+//             });
+//             let _ = thread::spawn(move || {
+//                 let sorted = merge_helper_vecdeque(arr_cloned2, mid, right, new_depth);
+//                 sender2.send(sorted).unwrap();
+//             });
+//             arr_left = receiver1.recv().unwrap();
+//             arr_right = receiver2.recv().unwrap(); 
+//         } else {
[…]

### 2020-03-22 thesis_template/3_Body/chapter/concept.tex
documented mergesort

\section{Type of Reference}
\label{sec:history}
\clearpage

\section{Multithreading}
\label{sec:history}
\clearpage

\section{Data Generation}
\label{sec:history}
\clearpage

### 2020-03-22 thesis_template/3_Body/model/merge_sort_experiment.tex
documented mergesort

@@
 In Rust programming, we usually need Atomic Reference Counting (Arc) to share data among threads. 
-However, 
-We implement merge-sort algorithm in two different ways. One is sharing source vector with Arc. 
-The other is passing slice of source vector to child thread.
+Arc is a simple interface that allows threads to share data, but it may cause significant overhead in Big Data processing.
+Arc allows multiple variable to have ownerships of a particular value similarly to Rc, 
+but also supports atomic feature enabling the ownerships exist in different threads.
 
-Our merge-sort algorithm with vector is implemented with recursion. In these alogorithm, the splitting phase is merely aquiring index of split position, 
-not actually splitting the source vector. At merge phase, merge function receives two independent vector and merge these into single new vector.
+As explained in last experiment, deletion of Rc has significant overhead than normal reference. 
+By learning this result, our assumption is that deletion of Arc has also overhead when we compare to normal reference. 
+In many situation where developer write a multithreading code, Arc is used and the deletion happens multiple times. 
+To assess runtime overhead of algorithm with Arc, We implement merge-sort algorithm in two different ways. 
+One is sharing source vector with Arc. The other is passing slice of source vector to child thread.
 
-For sharing data implementaion, channel with sending data is used for multithreading method, because we want to ensure children threads return values before parent thread proceed execution. 
-For passing slice implementation, we use scope method to enable children threads to receive reference from their parent ensuring the same purpose of sending data.
+Our merge-sort algorithms are implemented with recursion. For each call of recursive function, 
+Arc or slice of the source vector needs to be passed and deleted when the function returns value. 
+These merge-sort algorithms trigger large number of Arc or reference deletion proportional to the number of call recursive function.
+Merge-sort algorithm can be separated in three phases: splitting phase, copying phase, and merging phase.
 
-Experiment performed is the comparison among sharing data and passing slice implementations to see the impact of Arc, Atomic reference conuting, to runtime performance.
-These two implementations are theoritically the same operations other than using or not using Arc to share data. 
-This comparison can effectively show how important careful memory management is in multithreading computation in Rust. 
-In another word, how atomic reference counting can cost for computation in Rust programming.
+The splitting phase is merely acquiring index of range. At this phase, multiple threads are generated and Arc or reference of source vector are passed by calling recursive function. 
+Copying phase occurs in the base case of the recursive call. The element in the source vector in a certain index is deep-copied into newly allocated vector.
+At merge phase, merge function receives two sorted independent vector and merge them into single new vector.
 
-The figure shows the result of 
-An atomic reference count of the shareable vector is passed to every recursion steps and
+We use scope method from crossbeam crate to perform multithread programming. 
+Scoped thread can have reference to value from its parent thread by ensuring children threads are joined before their parent thread returns value. 
+By using scoped thread, we can implement two merge-sort algorithms in identical way except whether the function receives Arc or reference of source vector.
+
+\begin{figure}[htb]
+    \begin{lstlisting}
+        arr: Arc<VecDeque<T>>
+        arr: &mut [T]
+    \end{lstlisting}
+    \caption{Aggregation function with Arc}
+    \label{fig:Sampling}
+\end{figure}
 
 \subsection{Result}
+The elements of source vector are CustomerOwned objects. We generates source vectors in size of 1 million, 2 million, 3 million and 4 million. 
+Finally, merge-sort is performed based on Customer key value. The figure shows the result for runtime performance of merge-sort algorithms on difference size of vectors.
 

### 2020-03-23 thesis_template/3_Body/model/merge_sort_experiment.tex
documentation for merge-sort is done except discussion

@@
 By using scoped thread, we can implement two merge-sort algorithms in identical way except whether the function receives Arc or reference of source vector.
+The representations of source vector for each algorithm are shown in figure.
 
@@
     \begin{lstlisting}
+        // Source vector for algorithm with Arc.
         arr: Arc<VecDeque<T>>
-        arr: &mut [T]
+
+        // Source vector for algorithm with reference (slice).
+        arr: &[T]
     \end{lstlisting}
-    \caption{Aggregation function with Arc}
+    \caption{Representation of Source Vector}
     \label{fig:Sampling}
@@
 \subsection{Discussion}
-
-The other is LinkedList implementation other than vector.
-The linkedlist implementation is different from another two. This algorithm is inplace sorting so that it does not de/allocate memory during execution. 
-The comparison among vector and linkedlist implementations can show trade-off between contiguous memory access and inplace non memory de/allocation. 
-Experiment with Java linkedlist implementation can be interesting, because Java GC is severe problem when number of object is large.

### 2020-03-24 thesis_template/3_Body/model/drop_ref_rc.tex
change

@@
+\subsection{Concept}
 The goal of this experiment is to assess efficiency of different reference strategies in Rust, borrowing and reference counting.
@@
 
+\subsection{Result}
 The result shows the time to drop borrowing reference is significatly faster than reference counting.
 This says that we should use borrwoing storategies whenever high performance computation is critical.
-
 \begin{figure}[htb!]
@@
 \end{figure}
+
+\subsection{Discussion}

### 2020-03-24 thesis_template/3_Body/model/drop_ref_rc.tex
knn in progress

@@
 \subsection{Concept}
-The goal of this experiment is to assess efficiency of different reference strategies in Rust, borrowing and reference counting.
+In Rust programming, a reference is a pointer to reduce unnecessary movement of ownership. 
+One use case is where we pass reference to values to arguments of function. 
+If we pass owner to function, the owner is moved and the corresponding value is deallocated when the call of function ends. 
+To avoid this, the owner should always be returned. This may be an encumbrance while complex software system development. 
+By using reference, we do not have to worry about returning it, because reference is an additional pointer to an owned value. 
+Reference can be used for operation in the same way of owner, but also be moved without deallocation of value by keeping its owner live.
 
-By levaraging reference counting, a value can be shared like what borrowing plays the role in Rust programming. 
-The difference is that reference counting checks number of reference pointing to the actual data and makes sure the data is not deleted 
-until all the references are dereferenced. Using reference counting is sometimes preferable approach for developers, 
-we do not have care about lifetime which is usually troublesome when we use borrowing approach many times in our code. 
-However, the possible problem regarding to reference counting is the cost for tracking the number of references. 
-Having this assumption, this experiment will show difference of behavior among reference countinig and borrowing.
+Reference is useful to avoid movement of ownership. However, one needs to track its lifetime and explicitly includes it in code, 
+because Rust compiler cannot infer it. This can be another encumbrance. We can instead acquire multiple owners to single value by using Reference Counting (Rc). 
+By leveraging Rc, a value can be shared like what borrowing plays the role in Rust programming. 
+The difference is that Rc checks number of owner pointing to the actual data and makes sure the data is not deleted 
+until all the owners are dereferenced. Using Rc is sometimes preferable approach for developers especially when lifetime planning is extremely difficult.
+However, the possible problem regarding to Rc is the cost for tracking the number of references. 
+Having this assumption, this experiment will show difference of behavior among Rc and simple reference.
 
+\subsection{Evaluation}
 In this experiment, CustomerBorrowed and CustomerRc in figure are used to see difference of dropping time among borrowing and reference counting. 

### 2020-03-25 thesis_template/2_RelatedWork/relatedWork.tex
documentation on Rc dropping

@@
 \clearpage
+
+\begin{figure}[htb]
+    \begin{lstlisting}
+        struct OrderOwned {
+            order_id: i32,
+            num_items: i32, 
+            payment: f64,
+            order_time: f64,
+            title: String,
+            comment: String
+        }
+
+        struct OrderBorrowed<'a> {
+            order_id: &'a i32,
+            num_items: &'a i32, 
+            payment: &'a f64,
+            order_time: &'a f64,
+            title: &'a String,
+            comment: &'a String
+        }
+
+        struct OrderRc {
+            order_id: Rc<i32>,
+            num_items: Rc<i32>, 
+            payment: Rc<f64>,
+            order_time: Rc<f64>,
+            title: Rc<String>,
+            comment: Rc<String>
+        }
+    \end{lstlisting}
+    \caption{Representation of Customer object in Rust.}
+    \label{fig:Sampling}
+\end{figure}
 

### 2020-03-25 thesis_template/3_Body/model/drop_ref_rc.tex
documentation on Rc dropping

@@
 \subsection{Evaluation}
-In this experiment, CustomerBorrowed and CustomerRc in figure are used to see difference of dropping time among borrowing and reference counting. 
-In the CustomerRc and OrderRc struct, all fields take reference counting (Rc$<$T$>$). Similaly to the experiment in the last section, 
-vectors of CustomerRc and CustomerBorrowed are created and droped the elements one by one.
-
-The result shows significant difference of dropping time among the two objects; deletion of CustomerRc is much slower than CustomerBorrowed. 
-This is because reference counters which are feilds of CustomerRc have to check the number of reference pointing to the actual content and decide 
-deallocate the memory or not. However, memory management and lifetime strategy of borrowing is already determined at compile time.
-
-In this experiment, an assessment is conducted to valify whether there is difference between behavior of borrowing and reference counting. 
-These two methods can be used in similar situation. Especially, when we want reference to an original variable and keep the original variable until all of references are dereferenced, 
-we can have reference with both storategies, borrowing and reference counting. One advantage of using reference counting is that we do not have to pay attention to lifetime.
-However, the assumption here is that use of reference counting might be computationally expenesive than borrowing, because reference counting has to track the number of reference pointing to the value.
-Considered this assumption, we assess difference of time for dropping reference using borrowing and reference counting strategies.
-
-Similally to the last section, we implement struct whose fields are borrowing reference and reference counting and measure the time to drop the struct.
+In this experiment, CustomerBorrowed and CustomerRc in figure are used to see difference of dropping time among reference and Rc. 
+In the CustomerRc and OrderRc struct, all fields take Rc (Rc$<$T$>$). Similarly to the experiment in the last section, 
+Sets of integer, float, and String vector are created and their elements are borrowed or reference counted to create CustomerBorrowed or CustomerRc objects.
+The dropping of objects deletes references or Rcs which take role in fields the objects. However, it does not deallocate values to which they are pointing. 
+Therefore, the evaluated runtime of dropping objects only consists of dropping time of reference or Rc, but deallocation time.
 
 \subsection{Result}
-The result shows the time to drop borrowing reference is significatly faster than reference counting.
-This says that we should use borrwoing storategies whenever high performance computation is critical.
+We generated 1M, 1.5M, 2M, 2.5M, 3M, 3.5M of CustomerBorrowed and CustomerRc objects and performed drop to them. 
+The result in figure shows significant difference of dropping time among the two objects; deletion of CustomerRc is much slower than CustomerBorrowed. 
+This is because reference counters which are fields of CustomerRc have to check the number of reference pointing to the actual content and decide 
+deallocate the memory or not. However, memory management and lifetime strategy of borrowing is already determined at compile time.
+The result shows the time to drop borrowing reference is significantly faster than reference counting.
+This says that we should use borrowing strategies whenever high performance computation is critical.
 \begin{figure}[htb!]
     \includegraphics[width=15cm]{rust_droptime_borring_rc.eps}
-    \caption{Runtime for Droping to fields of Customer Object}
+    \caption{Runtime for dropping Customer Object}
     \label{fig:Sampling}
@@
 \subsection{Discussion}
+In this experiment, an assessment is conducted to verify whether there is difference between behavior of borrowing and reference counting. 
+These two methods can be used in similar situation. Especially, when we want reference to an original variable and keep the original variable until all of references are dereferenced, 
+we can have reference with both strategies, borrowing and reference counting. One advantage of using reference counting is that we do not have to pay attention to lifetime.
+However, the assumption here is that use of reference counting might be computationally expensive than borrowing, because reference counting has to track the number of reference pointing to the value.
+Considered this assumption, we assess difference of time for dropping reference using borrowing and reference counting strategies.

### 2020-04-02 thesis_template/2_RelatedWork/model/spark.tex
change
updatd section of MapReduce to Spark

@@
 In several Big Data mining tools that have been developed, the most notable ones are MapReduce and Spark. MapReduce is a cluster computing framework 
-which supports locality-aware scheduling, fault tolerance, and load balancing. Spark improves operations that MapReduce does not cover well.
+which supports locality-aware scheduling, fault tolerance, and load balancing. Spark is designed to improve performance for iterative jobs keeping features of MapReduce.
 
@@
 
-Iterative job is especially common in Machine Learning Algorithm, such as Gradient Descent. In traditional MapReduce framework, each iteration can be expressed as single MapReduce job 
+Iterative job is especially common in Machine Learning Algorithm, such as learning a data model using Gradient Descent.
+In traditional MapReduce framework, each iteration can be expressed as single MapReduce job
 so that each job must reload the data from disk. This leads I/O overhead and deteriorates performance of iterative algorithms.
 
-Interactive analysis is also an inevitable task in modern data science. A data scientist want perform exploratory analysis in interactive way. 
+Interactive analysis is also an inevitable task in modern data science. A data scientist wants tp perform exploratory analysis in interactive way. 
 Nevertheless, MapReduce is designed in the way more stable for ad-hoc query, so each analysis can be single MapReduce job. 
@@
 
-\section{Resilient Distributed Datasets}
+Some of the notable improvements are shown here\cite{DBLP:journals/pvldb/ShiQMJWRO15}.
+For aggregation operation, map output selectivity, which is the ration of the map output size to the job input size,
+can be significantly reduced by using Spark. Spark uses a map side combiner, hash-based aggregation which is more efficient than sort-based aggregation used in MapReduce. 
+For iterative operation, caching the input as Resilient Distributed Datasets (RDDs) can reduce CRU and disk I/O overheads for sequence iteration. 
+This RDD caching takes a significant role to improve iterative job, because it is more efficient than other low-level caching approaches such as OS buffer caches, and HDFS caching. 
+These caching strategy reduces disk I/O overhead, but CPU overhead, such as parsing text to objects.
+
+\section{Apache Spark}
 \label{sec:history}
-The major methods in Spark are Resilient Distributed Datasets (RDDs), a data structure that abstracts distributed memory across different clusters. 
+\subsection{Resilient Distributed Datasets}
+Major methods in Spark are Resilient Distributed Datasets (RDDs), a data structure that abstracts distributed memory across different clusters. 
 The immutable coarse-grained transformation, spark-scheduler with lazy-evaluation, and memory management with cacheing achieve computation with fault-tolerance, 
@@
 
-\section{Memory Management in Spark}
-\label{sec:history}
+\subsection{Memory Management in Spark}
 Spark framework allocates multiple executors, JVMs, that run sequence of transformations and actions. As we describe the previous section, data in Spark is mainly stored as Java objects in memory, 
@@
 
-In old generation, JVM lunches multi-thread to perform GC. GC with multi-threading suffers from Stop-The-World (STW) pauses; 
+In region of old generation, JVM lunches multi-thread to perform GC. GC with multi-threading suffers from Stop-The-World (STW) pauses; 
 GC may suspend application threads while performing object marking and deallocation. 
@@
 
-\section{Garbage Collection Tuning}
-\label{sec:history}
+\subsection{Garbage Collection Tuning}
 Several solutions are suggested. Main idea is to reduce number of object and execution of GC. 
@@
 
-Main concepts of Memory Management in Rust are ownership, move, and borrowing. In ownership feature or Rust, each value has a variable called its owner.
+Main concepts of Memory Management in Rust are ownership, move, and borrowing. In ownership feature or Rust, each value has a variable called owner.
 This owner has information about the value, such as location in memory, length and capacity of the value. This owner can live on the scope associated with its lifetime.
-When the owner goes out of it’s scope, the value will be dropped. This feature is similar to how RAII in C++ works. 
+When the owner goes out of its scope, the value will be dropped. This feature is similar to how RAII in C++ works. 
 However, acquisition of owner out of the scope where it was constructed is available in Rust with the concept of move.

### 2020-04-02 project/practice/run.sh

@@ -1,1 +1,1 @@
-cargo run ~/master-thesis/data/WikipediaPagesOneDocPerLine1000LinesSmall.txt ~/master-thesis/data/TestingData.txt  20000 20
+cargo run ~/master-thesis/data/WikipediaPagesOneDocPerLine1000LinesSmall.txt ~/master-thesis/data/TestingData.txt  200 20

### 2020-04-02 project/practice/src/main.rs

@@ -88,7 +88,8 @@ fn get_n_similarity_and_index(all_similarity: &Array<f64, Ix1>, mut similarity: 
     let mut pq = BinaryHeap::with_capacity(n_neighbors);
     let n = all_similarity.shape()[0];
     for i in 0..n {
-        pq.push(Reverse(MinNonNan(i, all_similarity[i])));
+        //pq.push(Reverse(MinNonNan(i, all_similarity[i])));
+        pq.push(MinNonNan(i, all_similarity[i]));
         if pq.len() > n_neighbors {
             pq.pop();
         }
@@ -96,7 +97,8 @@ fn get_n_similarity_and_index(all_similarity: &Array<f64, Ix1>, mut similarity: 
     let mut pair;
     let mut indices = Array::zeros(n_neighbors);
     for i in 0..n_neighbors {
-        pair = pq.pop().unwrap().0;
+        //pair = pq.pop().unwrap().0;
+        pair = pq.pop().unwrap();
         similarity[i] = pair.1;
         indices[i] = pair.0;
     }

### 2020-04-03 thesis_template/1_Intro/intro.tex
revise

@@
 
-However these technologies do not come with free; we need to pay for it. Ususally, user needs to pay depending on use of computational resources. 
+However these technologies do not come for free; we need to pay for it. Ususally, user needs to pay depending on use of computational resources. 
 If your process of data analysis is too long or need to use a number of cluster with high speck specification, the cost will end up significantly hight.
@@
 
-Multiple cluster computing analysis tools have been developed, such as Hadoop MapReduce, Spark, and Flink. These tools have brought reliable and scalable ways to deal massive data. 
+Multiple cluster computing analysis tools have been developed, such as Hadoop MapReduce\footnote{\cite{ApacheHadoopHomePage}}, Apache Spark, and Apache Flink.
+These tools have brought reliable and scalable ways to deal massive data.
 These has become widely popular, in which data-parallel computations are executed on clusters of unreliable machines by systems that automatically provide locality-aware scheduling, 

### 2020-04-03 thesis_template/2_RelatedWork/model/llvm.tex
revise

--- 2020-03-19 thesis_template/2_RelatedWork/relatedWork.tex
@@
-\chapter{Related Work}
-\label{chapter:relatedwork}
-\thispagestyle{myheadings}
-
-\graphicspath{{2_RelatedWork/Figures/}}
-
-\label{sec:history}
-\input{2_RelatedWork/model/spark}
-\clearpage
-
-\section{Serialization}
-\label{sec:history}
-\input{2_RelatedWork/model/serialization}
-\clearpage
-
-\section{Elements Copy and Insertion into Size-initialized Vector in Rust.}
-\label{sec:history}
-In this experiment, four methods are used to insert elements into vector in Rust. One is clone method which performs bitwise deep copy. 
-Another is clone\_from which also performs bitwise deep copy, but copies elements of the vector to distination vector rather than 
-creating new one. We initialize the distination vector with the same size to the number of elements we insert into it. 
-Another is copy\_nonoverlapping function which copies values from source to distination memory region. 
-The other is pushing elements of source to distination vector one by one. Insertions of elements with 4 size are conducted 1000000, 1500000, 10000000, 15000000, and, 
-their runtimes for each elements type, integer and String are measured.
-
-The figure shows the result of the experiment. Among the runtime performances of integer insertion for every methods, 
-clone, clone\_from, and copy\_nonoverlapping method shows the similar performance. However, the pushing the copy of elements one by one has much slower runtime performance 
-compared to the rest. This is because integer elements are allocated contiguously in the memory, so that accessing address of memory by pointer reads some next address. 
-This boosts the copy and insertion of elements.
-
-On the other hand, all of methods show the similar runtime performance in experiment for String object insertion. 
-This is because String object is not stored in contiguous memory region. The vector stores pointer to the object and 
-process need to access around different memory region again and again to deeply copy the object.
-
-\begin{figure}[htb]
-    \includegraphics[width=15cm]{rust_various_insertion.eps}
-    \caption{Runtime of elements copy from one vector and insertion to the other vector.}
-    \label{fig:Sampling}
-\end{figure}
-\clearpage
-
-\section{Access time to elements in vector}
-\label{sec:history}
-In this experiment, whether mutability has impacts to operation on the object in terms of runtime performance. 
-According to the experiment, there is no difference on accessing to elements of mutable and immutable vector.
-
-\begin{figure}[htb]
-    \includegraphics[width=15cm]{rust_various_access.eps}
-    \caption{Runtime of elements copy from one vector and insertion to the other vector.}
-    \label{fig:Sampling}
-\end{figure}
-
-\section{Access time to owned, borrowed, and sliced field of object}
-\label{sec:history}
-In this experiment, differences of access time to among owned, borrowed, and sliced are observed. 
-Each variable has slightly different use of memory.
-
-\begin{figure}[htb]
-    \begin{lstlisting}
-        struct CustomerOwned {
-            key: i32,
-            age: i32,
-            num_purchase: i32,
-            total_purchase: f64,
-            duration_spent: f64, 
-            duration_since: f64,
-            zip_code: String,
-            address: String,
-            country: String,
-            state: String,
-            first_name: String,
-            last_name: String,
-            province: String,
-            comment: String, 
-            order: OrderOwned
-        }
-
-        struct CustomerBorrowed<'a> {
-            key: &'a i32,
-            age: &'a i32,
-            num_purchase: &'a i32,
-            total_purchase: &'a f64,
-            duration_spent: &'a f64, 
-            duration_since: &'a f64,
-            zip_code: &'a String,
-            address: &'a String,
-            country: &'a String,
-            state: &'a String,
-            first_name: &'a String,
-            last_name: &'a String,
-            province: &'a String,
-            comment: &'a String, 
-            order: &'a OrderBorrowed<'a>
-        }
-
-        struct CustomerSlice<'a> {
-            key: &'a i32,
-            age: &'a i32,
-            num_purchase: &'a i32,
-            total_purchase: &'a f64,
-            duration_spent: &'a f64, 
-            duration_since: &'a f64,
-            zip_code: &'a str,
-            address: &'a str,
-            country: &'a str, 
-            state: &'a str,
-            first_name: &'a str,
-            last_name: &'a str,
-            province: &'a str,
-            comment: &'a str,
-            order: &'a OrderSlice<'a>
-        }
-
-        struct CustomerRc {
-            key: Rc<i32>,
-            age: Rc<i32>,
-            num_purchase: Rc<i32>,
-            total_purchase: Rc<f64>,
-            duration_spent: Rc<f64>, 
-            duration_since: Rc<f64>,
-            zip_code: Rc<String>,
-            address: Rc<String>,
-            country: Rc<String>,
-            state: Rc<String>,
-            first_name: Rc<String>,
-            last_name: Rc<String>,
-            province: Rc<String>,
-            comment: Rc<String>, 
-            order: Rc<OrderRc>
-        }
-    \end{lstlisting}
-    \caption{Representation of Customer object in Rust.}
-    \label{fig:Sampling}
-\end{figure}
-
-\clearpage
-
-\section{Possible Graph Structure in Rust}
-\label{sec:history}
-In Rust, there are two essential problems to construct graph structure, lifetime and mutability.
-
-The first problem is about what kind of pointer to use to point to other nodes. 
-Since graph can be cyclic, so the ownership consept in Rust is violated if we use Box$<$Node$>$.
-
-All of graph structure are immutable at least at creation time. Because graph may have cyclic, 
-we can not create graph at one statement. Although edge of graph has to be mutable to create entire graph structure, 
-we might need multiple references to edges, which violates basic rule of Rust programming.
-
-One solution is to use raw pointers. This is the most flexible approach, but also the most dangerous. 
-By taking this way, we are ignoring all the benefits of Rust.
-
-\section{Experiment for Multithread}
-\label{sec:history}
-Experiment for multithreading in Rust is interesting, because there are many memory allocation and deallocation in each threads.
-This is because each thread offten need to form independent memory state to each other to perform computation concurrently safely.
-In addition, the multithreading strategy can be planned in different ways in Rust using different concurrent computation tools, 
-Mutex, Arc, spawn, channel, scope, and so on.
-
-Currently available plan
-\begin{itemize}
-    \item spawn, channel and sending data (currently deviding data, but we probably do not need to).
-    \item spawn, forkjoin and shared data.(shared data among child and parent).
-    \item scope, forkjoin and slice shared data.
-    \item Use linkedList instead of Vector (Each node can be sharable data structure). When we have complex object of elements in vector, we want to copy the pointer to the object.
-    \item Compare performace on LinkedList which is not contiguous allocation, but do not need additional memory allocation and Vec.
-\end{itemize}
-
-\section{Note for next}
-\label{sec:history}
-Complex object of elements copy and insertion among vector is worth to experiment. This can be compared with Java,
-because memory layouts of struct in Rust and class in Java are different. Rust stores fieds in the contiguous memory region. 
-However, Java stores field elements to different region.
-
-Complex object whose fields has reference elemenets insertion to vector can be evaluated. Operation to the fields can be little 
-more expensive because the pointer to the value of the field is not stored in contiguous memory region.
-
-Generic type and static type function can be compared.
-
-To optimise access to String elements of vector, smallstring can be improve the runtime performance. 
-This is because the smallstring optimization enables short length of string on stack as byte array. 
-This string type sets condition where it makes decition where the string is stored on heap or stack as array at certain length.
-
-Comparing operation on reference and owned variable is also interested to examine.
-
-Comparing operation on various smart pointer type. 
-Rc$<$T$>$ enables value to have multiple owners, but the value should be immutable. Rc$<$T$>$ is used in case of single thread. 
-When the situation is multi-thread, Arc$<$T$>$ is used. Arc$<$T$>$ performs atomic operation, so it is more expensive than Rc$<$T$>$. 
-When we need to mutate value of Rc$<$T$>$, RefCell$<$T$>$ can be useful. RefCell$<$T$>$ allow us to have mutiple mutable reference and immutable
-of reference mutable or immutable variable at the same time. When the mutability consistency is voilented, it terminates program during runtime. 
-That is why RefCell$<$T$>$ is expensive so that the state of mutable consistency should tracked. 
-As Cell$<$T$>$, the value is copied in and out of the Cell$<$T$>$ instead of getting refrence to it. 
-In addition, Mutex$<$T$>$ provides intetior mutability across multi-thread.
-
-Comparison between mutable and immutable tree or graph structure can be checked. 
-This is because tree structure requires Rc$<$T$>$ or Week$<$T$>$ and in addition RefCell$<$T$>$ to make it mutable.
-
-Design experiment for Trait object and Generic function. 
-We can have Trait object which is pointer to object which imprements its Trait and use the method of Trait object.
-This object has additional information other than just reference to tye original object. 
-This is because Rust needs the type information to dynamically calll the right method of Trait object depending on the type of 
-original object.
-On the other hand, we can have Generic function whose parameter types are Generic types corresponding to Trait. 
-When Rust compiles the code, it emits independent function corresponding to every types that implements the Trains specified in parameter.
-
-Vector of Trait object (need to put element into Box) vs Vector of concrete type.
-
-If we keep first created owner until the last phase, we can use borrowing to operate.
-If we delete first created owner during the operation, we should use Rc$<$T$>$.
-The question would be, we can use Rc$<$T$>$ every where?
-
-Multithread in Rust vs Java
-
-Smart pointer
-\begin{itemize}
-    \item Box$<$T$>$: Box pointer lets value allocated on heap rather than on the stack.
-    \item Rc$<$T$>$: Reference counted pointer lets variable take multiple immutable ownership.
-\end{itemize}
-
-Interier mutability
-\begin{itemize}
-    \item Cell$<$T$>$: For only Copy type, it allows us to mutate variable, even if it is immutable. Howeever, it does not support sharing the variable so that it returns always copy of the value.
-    \item RefCell$<$T$>$: This support sharing and interier immutability for all types.
-This is done by allowing to get mutable reference from immutable variable and push the error detacting time from compile time to runtime.
-\end{itemize}
-
-\section{LLVM}
-\label{sec:history}
 LLVM (Low Level Virtual Machine) is an umbrella project which contains components of compilation of programming language.
-Exsiting compilers have tightly coupled functionalities so that it is not possible to embed them into other applications.
+Existing compilers have tightly coupled functionalities so that it is not possible to embed them into other applications.
 However, the abstract framework of LLVM decouples the functionalities into peaces and the peaces of functionalities can be reused.
 
-In structure of a compiler, there are three main components; flontend, optimizer, and backend. 
-In flontend, a develper designs the interface of source programming language in way where it can be optimized by optimizer. 
+In structure of a compiler, there are three main components; frontend, optimizer, and backend. 
+In frontend, a developer designs the interface of source programming language in way where it can be optimized by optimizer. 
 Then, backend takes optimized code and produce the native machine code. LLVM has a component called LLVM Intermediate Representation (IR), 
@@
 Once source code is represented with IR, optimizer can easily find pattern and optimize it in faster time. 
-IR is useful in terms of flontend. This is because developer of language flontend need to know only how the IR works and use the framework to develop a language.
-
-\section{The existing Big Data tools}
-\label{sec:history}
-The existing Big Data tools are JVM based. JVM abstract hardware so that JVM can rarely achieve near-native speed. A garbage collector is a
-
-\section{Experiment: Tree aggregate}
-\label{sec:history}
-Three aggregate can be more memory de/allocation intensive experiment, when we load data from disk line by line to aggregate.
-This is because, we will allocate many small objects and deallocate them many times.
-We can imitate ShuffledRDDs by writing result to disk and reading it to other thread.  
-We can compare to Java implementation for ration of runtime increase.
-
-\section{Todos}
-\label{sec:history}
-\begin{itemize}
-    \item 
-    \item Redo the experiment with appropriate size
-    \item Document for Memory Management of Java with Garbage Collection and the impact for Big Data tools
-    \item The safety of Region Based Memory Management and advantage of using Rust.
-    \item Serialize problem 
-    \item Document for reference counting(measure dropt time using criterion)
-    \item Design experiment for Graph
-    \item Design experiment for Multithread
-    \item Study about LLVM
-    \item Buffer pool
-\end{itemize}
-
-\section{Done}
-\label{sec:history}
-\begin{itemize}
-    \item Study about OS memory management
-\end{itemize}
-
-\section{Time Line}
-\label{sec:history}
-\begin{itemize}
-    \item End Feb: Finish Experiment for Multithread and Graph
-    \item Mid May: ML experiment
-    \item End May: Redo experiment with bench mark dataset.
-    \item Start April: Finish Writing for first revise.
-\end{itemize}
+IR is useful in terms of frontend. This is because developer of language frontend need to know only how the IR works and use the framework to develop a language.

### 2020-04-03 thesis_template/2_RelatedWork/model/spark.tex
revise

@@
 There are three popular GCs: Parallel, CMS and G1. All of these method track generation of object based on the region of memory. 
-The Java logical heap structure is shown in Figure. It can be separated into three main parts where store objects for each corresponding generation: 
+The Java logical heap structure is shown in Figure~\ref{fig:javaheap}.
+As the figure shows, Java logical heap can be separated into three main parts where store objects for each corresponding generation:
 permanent generation, young generation, and old generation. The region for permanent generation stores metadata required by JVM to describe 
-class and method used in application which will be permanently lived on the region of memory.
+class and method used in application which will be permanently lived on the region of memory. The overview of Java GC is shown in Figure~\ref{fig:javagc}. 
+The outer box represents region for particular generation. The inner box and the number represents object and its age in GC.
 
@@
     \caption{Java Heap Structure}
-    \label{fig:Sampling}
+    \label{fig:javaheap}
 \end{figure}
@@
     \caption{Java Garbage Collection}
-    \label{fig:Sampling}
+    \label{fig:javagc}
 \end{figure}
@@
 \label{sec:history}
-Considered overhead produced by Memory Management in JVM, we suggest application of system language to Big Data tool rather than application language, such as Java and Scala. 
+Considered overhead produced by Memory Management in JVM, use of system language for development of Big Data tool can be one of solutions rather than application language, such as Java and Scala. 
 System languages, such as C and C++, are languages that give developer total control over the hardware and de/allocation of memory without GC. 
@@
 
-\section{Region-Based Memory Management}
-\label{sec:history}
-
 \section{Rust Memory Management}

### 2020-04-03 thesis_template/2_RelatedWork/relatedWork.tex
revise

--- 2020-03-19 thesis_template/2_RelatedWork/relatedWork.tex
@@
 
-\section{Elements Copy and Insertion into Size-initialized Vector in Rust.}
-\label{sec:history}
-In this experiment, four methods are used to insert elements into vector in Rust. One is clone method which performs bitwise deep copy. 
-Another is clone\_from which also performs bitwise deep copy, but copies elements of the vector to distination vector rather than 
-creating new one. We initialize the distination vector with the same size to the number of elements we insert into it. 
-Another is copy\_nonoverlapping function which copies values from source to distination memory region. 
-The other is pushing elements of source to distination vector one by one. Insertions of elements with 4 size are conducted 1000000, 1500000, 10000000, 15000000, and, 
-their runtimes for each elements type, integer and String are measured.
-
-The figure shows the result of the experiment. Among the runtime performances of integer insertion for every methods, 
-clone, clone\_from, and copy\_nonoverlapping method shows the similar performance. However, the pushing the copy of elements one by one has much slower runtime performance 
-compared to the rest. This is because integer elements are allocated contiguously in the memory, so that accessing address of memory by pointer reads some next address. 
-This boosts the copy and insertion of elements.
-
-On the other hand, all of methods show the similar runtime performance in experiment for String object insertion. 
-This is because String object is not stored in contiguous memory region. The vector stores pointer to the object and 
-process need to access around different memory region again and again to deeply copy the object.
-
-\begin{figure}[htb]
-    \includegraphics[width=15cm]{rust_various_insertion.eps}
-    \caption{Runtime of elements copy from one vector and insertion to the other vector.}
-    \label{fig:Sampling}
-\end{figure}
-\clearpage
-
-\section{Access time to elements in vector}
-\label{sec:history}
-In this experiment, whether mutability has impacts to operation on the object in terms of runtime performance. 
-According to the experiment, there is no difference on accessing to elements of mutable and immutable vector.
-
-\begin{figure}[htb]
-    \includegraphics[width=15cm]{rust_various_access.eps}
-    \caption{Runtime of elements copy from one vector and insertion to the other vector.}
-    \label{fig:Sampling}
-\end{figure}
-
-\section{Access time to owned, borrowed, and sliced field of object}
-\label{sec:history}
-In this experiment, differences of access time to among owned, borrowed, and sliced are observed. 
-Each variable has slightly different use of memory.
-
-\begin{figure}[htb]
-    \begin{lstlisting}
-        struct CustomerOwned {
-            key: i32,
-            age: i32,
-            num_purchase: i32,
-            total_purchase: f64,
-            duration_spent: f64, 
-            duration_since: f64,
-            zip_code: String,
-            address: String,
-            country: String,
-            state: String,
-            first_name: String,
-            last_name: String,
-            province: String,
-            comment: String, 
-            order: OrderOwned
-        }
-
-        struct CustomerBorrowed<'a> {
-            key: &'a i32,
-            age: &'a i32,
-            num_purchase: &'a i32,
-            total_purchase: &'a f64,
-            duration_spent: &'a f64, 
-            duration_since: &'a f64,
-            zip_code: &'a String,
-            address: &'a String,
-            country: &'a String,
-            state: &'a String,
-            first_name: &'a String,
-            last_name: &'a String,
-            province: &'a String,
-            comment: &'a String, 
-            order: &'a OrderBorrowed<'a>
-        }
-
-        struct CustomerSlice<'a> {
-            key: &'a i32,
-            age: &'a i32,
-            num_purchase: &'a i32,
-            total_purchase: &'a f64,
-            duration_spent: &'a f64, 
-            duration_since: &'a f64,
-            zip_code: &'a str,
-            address: &'a str,
-            country: &'a str, 
-            state: &'a str,
-            first_name: &'a str,
-            last_name: &'a str,
-            province: &'a str,
-            comment: &'a str,
-            order: &'a OrderSlice<'a>
-        }
-
-        struct CustomerRc {
-            key: Rc<i32>,
-            age: Rc<i32>,
-            num_purchase: Rc<i32>,
-            total_purchase: Rc<f64>,
-            duration_spent: Rc<f64>, 
-            duration_since: Rc<f64>,
-            zip_code: Rc<String>,
-            address: Rc<String>,
-            country: Rc<String>,
-            state: Rc<String>,
-            first_name: Rc<String>,
-            last_name: Rc<String>,
-            province: Rc<String>,
-            comment: Rc<String>, 
-            order: Rc<OrderRc>
-        }
-    \end{lstlisting}
-    \caption{Representation of Customer object in Rust.}
-    \label{fig:Sampling}
-\end{figure}
-
-\clearpage
-
-\section{Possible Graph Structure in Rust}
-\label{sec:history}
-In Rust, there are two essential problems to construct graph structure, lifetime and mutability.
-
-The first problem is about what kind of pointer to use to point to other nodes. 
-Since graph can be cyclic, so the ownership consept in Rust is violated if we use Box$<$Node$>$.
-
-All of graph structure are immutable at least at creation time. Because graph may have cyclic, 
-we can not create graph at one statement. Although edge of graph has to be mutable to create entire graph structure, 
-we might need multiple references to edges, which violates basic rule of Rust programming.
-
-One solution is to use raw pointers. This is the most flexible approach, but also the most dangerous. 
-By taking this way, we are ignoring all the benefits of Rust.
-
-\section{Experiment for Multithread}
-\label{sec:history}
-Experiment for multithreading in Rust is interesting, because there are many memory allocation and deallocation in each threads.
-This is because each thread offten need to form independent memory state to each other to perform computation concurrently safely.
-In addition, the multithreading strategy can be planned in different ways in Rust using different concurrent computation tools, 
-Mutex, Arc, spawn, channel, scope, and so on.
-
-Currently available plan
-\begin{itemize}
-    \item spawn, channel and sending data (currently deviding data, but we probably do not need to).
-    \item spawn, forkjoin and shared data.(shared data among child and parent).
-    \item scope, forkjoin and slice shared data.
-    \item Use linkedList instead of Vector (Each node can be sharable data structure). When we have complex object of elements in vector, we want to copy the pointer to the object.
-    \item Compare performace on LinkedList which is not contiguous allocation, but do not need additional memory allocation and Vec.
-\end{itemize}
-
-\section{Note for next}
-\label{sec:history}
-Complex object of elements copy and insertion among vector is worth to experiment. This can be compared with Java,
-because memory layouts of struct in Rust and class in Java are different. Rust stores fieds in the contiguous memory region. 
-However, Java stores field elements to different region.
-
-Complex object whose fields has reference elemenets insertion to vector can be evaluated. Operation to the fields can be little 
-more expensive because the pointer to the value of the field is not stored in contiguous memory region.
-
-Generic type and static type function can be compared.
-
-To optimise access to String elements of vector, smallstring can be improve the runtime performance. 
-This is because the smallstring optimization enables short length of string on stack as byte array. 
-This string type sets condition where it makes decition where the string is stored on heap or stack as array at certain length.
-
-Comparing operation on reference and owned variable is also interested to examine.
-
-Comparing operation on various smart pointer type. 
-Rc$<$T$>$ enables value to have multiple owners, but the value should be immutable. Rc$<$T$>$ is used in case of single thread. 
-When the situation is multi-thread, Arc$<$T$>$ is used. Arc$<$T$>$ performs atomic operation, so it is more expensive than Rc$<$T$>$. 
-When we need to mutate value of Rc$<$T$>$, RefCell$<$T$>$ can be useful. RefCell$<$T$>$ allow us to have mutiple mutable reference and immutable
-of reference mutable or immutable variable at the same time. When the mutability consistency is voilented, it terminates program during runtime. 
-That is why RefCell$<$T$>$ is expensive so that the state of mutable consistency should tracked. 
-As Cell$<$T$>$, the value is copied in and out of the Cell$<$T$>$ instead of getting refrence to it. 
-In addition, Mutex$<$T$>$ provides intetior mutability across multi-thread.
-
-Comparison between mutable and immutable tree or graph structure can be checked. 
-This is because tree structure requires Rc$<$T$>$ or Week$<$T$>$ and in addition RefCell$<$T$>$ to make it mutable.
-
-Design experiment for Trait object and Generic function. 
-We can have Trait object which is pointer to object which imprements its Trait and use the method of Trait object.
-This object has additional information other than just reference to tye original object. 
-This is because Rust needs the type information to dynamically calll the right method of Trait object depending on the type of 
-original object.
-On the other hand, we can have Generic function whose parameter types are Generic types corresponding to Trait. 
-When Rust compiles the code, it emits independent function corresponding to every types that implements the Trains specified in parameter.
-
-Vector of Trait object (need to put element into Box) vs Vector of concrete type.
-
-If we keep first created owner until the last phase, we can use borrowing to operate.
-If we delete first created owner during the operation, we should use Rc$<$T$>$.
-The question would be, we can use Rc$<$T$>$ every where?
-
-Multithread in Rust vs Java
-
-Smart pointer
-\begin{itemize}
-    \item Box$<$T$>$: Box pointer lets value allocated on heap rather than on the stack.
-    \item Rc$<$T$>$: Reference counted pointer lets variable take multiple immutable ownership.
-\end{itemize}
-
-Interier mutability
-\begin{itemize}
-    \item Cell$<$T$>$: For only Copy type, it allows us to mutate variable, even if it is immutable. Howeever, it does not support sharing the variable so that it returns always copy of the value.
-    \item RefCell$<$T$>$: This support sharing and interier immutability for all types.
-This is done by allowing to get mutable reference from immutable variable and push the error detacting time from compile time to runtime.
-\end{itemize}
-
 \section{LLVM}
 \label{sec:history}
-LLVM (Low Level Virtual Machine) is an umbrella project which contains components of compilation of programming language.
-Exsiting compilers have tightly coupled functionalities so that it is not possible to embed them into other applications.
-However, the abstract framework of LLVM decouples the functionalities into peaces and the peaces of functionalities can be reused.
-
-In structure of a compiler, there are three main components; flontend, optimizer, and backend. 
-In flontend, a develper designs the interface of source programming language in way where it can be optimized by optimizer. 
-Then, backend takes optimized code and produce the native machine code. LLVM has a component called LLVM Intermediate Representation (IR), 
-which places itself across frontend to optimizer. IR is designed to host mid-level analyses and transformations that you find in optimizer section of a compiler.
-High-level language has many common structures and functionalities, so most of all high-level program languages can be represented with IR. 
-Once source code is represented with IR, optimizer can easily find pattern and optimize it in faster time. 
-IR is useful in terms of flontend. This is because developer of language flontend need to know only how the IR works and use the framework to develop a language.
-
-\section{The existing Big Data tools}
-\label{sec:history}
-The existing Big Data tools are JVM based. JVM abstract hardware so that JVM can rarely achieve near-native speed. A garbage collector is a
-
-\section{Experiment: Tree aggregate}
-\label{sec:history}
-Three aggregate can be more memory de/allocation intensive experiment, when we load data from disk line by line to aggregate.
-This is because, we will allocate many small objects and deallocate them many times.
-We can imitate ShuffledRDDs by writing result to disk and reading it to other thread.  
-We can compare to Java implementation for ration of runtime increase.
+\input{2_RelatedWork/model/llvm}
 
@@
 \begin{itemize}
-    \item 
-    \item Redo the experiment with appropriate size
-    \item Document for Memory Management of Java with Garbage Collection and the impact for Big Data tools
-    \item The safety of Region Based Memory Management and advantage of using Rust.
-    \item Serialize problem 
-    \item Document for reference counting(measure dropt time using criterion)
-    \item Design experiment for Graph
-    \item Design experiment for Multithread
-    \item Study about LLVM
-    \item Buffer pool
+    \item Document for Serialization
+    \item Document for Region Based Memory Management
+    \item Document for LLVM in more detail.
+    \item Document for Rust in more detail.
 \end{itemize}
-
-\section{Done}
-\label{sec:history}
-\begin{itemize}
-    \item Study about OS memory management
-\end{itemize}
-
-\section{Time Line}
-\label{sec:history}
-\begin{itemize}
-    \item End Feb: Finish Experiment for Multithread and Graph
-    \item Mid May: ML experiment
-    \item End May: Redo experiment with bench mark dataset.
-    \item Start April: Finish Writing for first revise.
-\end{itemize}

### 2020-04-03 thesis_template/3_Body/model/element_copy_initialization.tex
revise

In this experiment, four methods are used to insert elements into vector in Rust. One is clone method which performs bitwise deep copy. 
Another is clone\_from which also performs bitwise deep copy, but copies elements of the vector to distination vector rather than 
creating new one. We initialize the distination vector with the same size to the number of elements we insert into it. 
Another is copy\_nonoverlapping function which copies values from source to distination memory region. 
The other is pushing elements of source to distination vector one by one. Insertions of elements with 4 size are conducted 1000000, 1500000, 10000000, 15000000, and, 
their runtimes for each elements type, integer and String are measured.

The figure shows the result of the experiment. Among the runtime performances of integer insertion for every methods, 
clone, clone\_from, and copy\_nonoverlapping method shows the similar performance. However, the pushing the copy of elements one by one has much slower runtime performance 
compared to the rest. This is because integer elements are allocated contiguously in the memory, so that accessing address of memory by pointer reads some next address. 
This boosts the copy and insertion of elements.

On the other hand, all of methods show the similar runtime performance in experiment for String object insertion. 
This is because String object is not stored in contiguous memory region. The vector stores pointer to the object and 
process need to access around different memory region again and again to deeply copy the object.

\begin{figure}[htb]
    \includegraphics[width=15cm]{rust_various_insertion.eps}
    \caption{Runtime of elements copy from one vector and insertion to the other vector.}
    \label{fig:Sampling}
\end{figure}
\clearpage

\section{Access time to elements in vector}
\label{sec:history}
In this experiment, whether mutability has impacts to operation on the object in terms of runtime performance. 
According to the experiment, there is no difference on accessing to elements of mutable and immutable vector.

\begin{figure}[htb]
    \includegraphics[width=15cm]{rust_various_access.eps}
    \caption{Runtime of elements copy from one vector and insertion to the other vector.}
    \label{fig:Sampling}
\end{figure}

\section{Access time to owned, borrowed, and sliced field of object}
\label{sec:history}
In this experiment, differences of access time to among owned, borrowed, and sliced are observed. 
Each variable has slightly different use of memory.

\begin{figure}[htb]
    \begin{lstlisting}
        struct CustomerOwned {
            key: i32,
            age: i32,
            num_purchase: i32,
            total_purchase: f64,
            duration_spent: f64, 
            duration_since: f64,
            zip_code: String,
            address: String,
            country: String,
            state: String,
            first_name: String,
            last_name: String,
            province: String,
            comment: String, 
            order: OrderOwned
        }

        struct CustomerBorrowed<'a> {
            key: &'a i32,
            age: &'a i32,
            num_purchase: &'a i32,
            total_purchase: &'a f64,
            duration_spent: &'a f64, 
            duration_since: &'a f64,
            zip_code: &'a String,
            address: &'a String,
            country: &'a String,
            state: &'a String,
            first_name: &'a String,
            last_name: &'a String,
            province: &'a String,
            comment: &'a String, 
            order: &'a OrderBorrowed<'a>
        }

        struct CustomerSlice<'a> {
            key: &'a i32,
            age: &'a i32,
            num_purchase: &'a i32,
            total_purchase: &'a f64,
            duration_spent: &'a f64, 
            duration_since: &'a f64,
            zip_code: &'a str,
            address: &'a str,
            country: &'a str, 
            state: &'a str,
            first_name: &'a str,
            last_name: &'a str,
            province: &'a str,
            comment: &'a str,
            order: &'a OrderSlice<'a>
        }

        struct CustomerRc {
            key: Rc<i32>,
            age: Rc<i32>,
            num_purchase: Rc<i32>,
            total_purchase: Rc<f64>,
            duration_spent: Rc<f64>, 
            duration_since: Rc<f64>,
            zip_code: Rc<String>,
            address: Rc<String>,
            country: Rc<String>,
            state: Rc<String>,
            first_name: Rc<String>,
            last_name: Rc<String>,
            province: Rc<String>,
            comment: Rc<String>, 
            order: Rc<OrderRc>
        }
    \end{lstlisting}
    \caption{Representation of Customer object in Rust.}
    \label{fig:Sampling}
\end{figure}

\clearpage

\begin{figure}[htb]
    \begin{lstlisting}
        struct OrderOwned {
            order_id: i32,
            num_items: i32, 
            payment: f64,
            order_time: f64,
            title: String,
            comment: String
        }

        struct OrderBorrowed<'a> {
            order_id: &'a i32,
            num_items: &'a i32, 
            payment: &'a f64,
            order_time: &'a f64,
            title: &'a String,
            comment: &'a String
        }

        struct OrderRc {
            order_id: Rc<i32>,
            num_items: Rc<i32>, 
            payment: Rc<f64>,
            order_time: Rc<f64>,
            title: Rc<String>,
            comment: Rc<String>
        }
    \end{lstlisting}
    \caption{Representation of Customer object in Rust.}
    \label{fig:Sampling}
\end{figure}

### 2020-04-03 thesis_template/Appendix/Appendix.tex
revise

@@
 When NDArray leaves the workspace scope, the memory is deallocated unless explicitly calling method to copy the NDArray out of the scope.
+
+\section{Possible Graph Structure in Rust}
+\label{sec:history}
+In Rust, there are two essential problems to construct graph structure, lifetime and mutability.
+
+The first problem is about what kind of pointer to use to point to other nodes. 
+Since graph can be cyclic, so the ownership consept in Rust is violated if we use Box$<$Node$>$.
+
+All of graph structure are immutable at least at creation time. Because graph may have cyclic, 
+we can not create graph at one statement. Although edge of graph has to be mutable to create entire graph structure, 
+we might need multiple references to edges, which violates basic rule of Rust programming.
+
+One solution is to use raw pointers. This is the most flexible approach, but also the most dangerous. 
+By taking this way, we are ignoring all the benefits of Rust.
+
+\section{Experiment for Multithread}
+\label{sec:history}
+Experiment for multithreading in Rust is interesting, because there are many memory allocation and deallocation in each threads.
+This is because each thread offten need to form independent memory state to each other to perform computation concurrently safely.
+In addition, the multithreading strategy can be planned in different ways in Rust using different concurrent computation tools, 
+Mutex, Arc, spawn, channel, scope, and so on.
+
+Currently available plan
+\begin{itemize}
+    \item spawn, channel and sending data (currently deviding data, but we probably do not need to).
+    \item spawn, forkjoin and shared data.(shared data among child and parent).
+    \item scope, forkjoin and slice shared data.
+    \item Use linkedList instead of Vector (Each node can be sharable data structure). When we have complex object of elements in vector, we want to copy the pointer to the object.
+    \item Compare performace on LinkedList which is not contiguous allocation, but do not need additional memory allocation and Vec.
+\end{itemize}
+
+\section{Note for next}
+\label{sec:history}
+Complex object of elements copy and insertion among vector is worth to experiment. This can be compared with Java,
+because memory layouts of struct in Rust and class in Java are different. Rust stores fieds in the contiguous memory region. 
+However, Java stores field elements to different region.
+
+Complex object whose fields has reference elemenets insertion to vector can be evaluated. Operation to the fields can be little 
+more expensive because the pointer to the value of the field is not stored in contiguous memory region.
+
+Generic type and static type function can be compared.
+
+To optimise access to String elements of vector, smallstring can be improve the runtime performance. 
+This is because the smallstring optimization enables short length of string on stack as byte array. 
+This string type sets condition where it makes decition where the string is stored on heap or stack as array at certain length.
+
+Comparing operation on reference and owned variable is also interested to examine.
+
+Comparing operation on various smart pointer type. 
+Rc$<$T$>$ enables value to have multiple owners, but the value should be immutable. Rc$<$T$>$ is used in case of single thread. 
+When the situation is multi-thread, Arc$<$T$>$ is used. Arc$<$T$>$ performs atomic operation, so it is more expensive than Rc$<$T$>$. 
+When we need to mutate value of Rc$<$T$>$, RefCell$<$T$>$ can be useful. RefCell$<$T$>$ allow us to have mutiple mutable reference and immutable
+of reference mutable or immutable variable at the same time. When the mutability consistency is voilented, it terminates program during runtime. 
+That is why RefCell$<$T$>$ is expensive so that the state of mutable consistency should tracked. 
+As Cell$<$T$>$, the value is copied in and out of the Cell$<$T$>$ instead of getting refrence to it. 
+In addition, Mutex$<$T$>$ provides intetior mutability across multi-thread.
+
+Comparison between mutable and immutable tree or graph structure can be checked. 
+This is because tree structure requires Rc$<$T$>$ or Week$<$T$>$ and in addition RefCell$<$T$>$ to make it mutable.
+
+Design experiment for Trait object and Generic function. 
+We can have Trait object which is pointer to object which imprements its Trait and use the method of Trait object.
+This object has additional information other than just reference to tye original object. 
+This is because Rust needs the type information to dynamically calll the right method of Trait object depending on the type of 
+original object.
+On the other hand, we can have Generic function whose parameter types are Generic types corresponding to Trait. 
+When Rust compiles the code, it emits independent function corresponding to every types that implements the Trains specified in parameter.
+
+Vector of Trait object (need to put element into Box) vs Vector of concrete type.
+
+If we keep first created owner until the last phase, we can use borrowing to operate.
+If we delete first created owner during the operation, we should use Rc$<$T$>$.
+The question would be, we can use Rc$<$T$>$ every where?
+
+Multithread in Rust vs Java
+
+Smart pointer
+\begin{itemize}
+    \item Box$<$T$>$: Box pointer lets value allocated on heap rather than on the stack.
+    \item Rc$<$T$>$: Reference counted pointer lets variable take multiple immutable ownership.
+\end{itemize}
+
+Interier mutability
+\begin{itemize}
+    \item Cell$<$T$>$: For only Copy type, it allows us to mutate variable, even if it is immutable. Howeever, it does not support sharing the variable so that it returns always copy of the value.
+    \item RefCell$<$T$>$: This support sharing and interier immutability for all types.
+This is done by allowing to get mutable reference from immutable variable and push the error detacting time from compile time to runtime.
+\end{itemize}

### 2020-04-05 thesis_template/2_RelatedWork/model/spark.tex
documented gc tuning

@@
 \subsection{Garbage Collection Tuning}
-Several solutions are suggested. Main idea is to reduce number of object and execution of GC. 
-One is avoiding pointer-based data structures, such as HashMap and LinkedList. These objects have a "wrapper" object for each entry 
-so that number of object tends to be larger than when when an array is used. Caching serialized object in memory also reduce number of object and memory usage 
-since the set of objects become a byte array. In addition, developers can allocate byte array off-heap of JVM to avoid tracking by GC. 
-Although these memory management solution for GC help developer improve performance of Spark applications, the effort to discover the best GC tuning afflicts developers.
+There are many different ways that one can improve the performance of GC in Java. One of these is for example avoiding pointer-based data structures, such as HashMap and LinkedList. 
+These objects have a "wrapper" object for each entry so that number of object tends to be larger than when when an array is used.
+
+Caching serialized object in memory also reduce number of object and memory usage since the set of objects become a byte or binary array. 
+Spark SQL applications use DataFrames\cite{DBLP:conf/sigmod/ArmbrustXLHLBMK15}, 
+whose intermediate data are managed by an optimized memory manager named Tungsten.
+Tungsten stores the intermediate data in a serialized binary form and performs aggregation functions directly on he serialized objects.
+Therefore, the number of Java objects in memory is reduced and it reduces the DC frequency and object marking/sweeping.
+
+In addition, developers can allocate data off-heap of JVM to avoid tracking by GC. 
+Facade\cite{DBLP:conf/asplos/NguyenWBFHX15} proposed a compiler and runtime system to bound the number of in-memory data objects, through storing data in an off-heap region and 
+manipulating the data with control interfaces.
+
+Although these memory management solution for GC help developer improve performance of Spark applications, 
+the effort to discover the best GC tuning afflicts developers.
 

### 2020-04-06 thesis_template/2_RelatedWork/model/spark.tex
knn debuggin

@@
 Memory leak occurs when memory is allocated and no longer referenced so that the object in the memory location cannot be reached and released.
-This is result of dereferencing object with deallocation. Memory leak consumes more memory than necessary by making unreachable location.
+This is result of dereferencing object without deallocation. Memory leak consumes more memory than necessary by making unreachable location.
 
@@
 Rust is a system programming language which provides memory safety without runtime checking like GC and necessity of explicit memory de/allocation. 
-In addition to characteristic of memory safety, this language also enables a developer to write concurrent code , fearless concurrency. 
-Developers are able to write code with high performance given fair control of hardware and safety forced to follow restrictive pattern.
+To ensure memory safety, Rust provides restrictive coding patterns and checks lifetime of value and memory safety at compile-time.
+The restrictive patterns also enables a developer to write fearless concurrent code that is free of data races.
+Main concepts of Memory Management in Rust are ownership, move, and borrowing.
 
-Main concepts of Memory Management in Rust are ownership, move, and borrowing. In ownership feature or Rust, each value has a variable called owner.
-This owner has information about the value, such as location in memory, length and capacity of the value. This owner can live on the scope associated with its lifetime.
-When the owner goes out of its scope, the value will be dropped. This feature is similar to how RAII in C++ works. 
+\subsection{Ownership}
+In ownership feature or Rust, each value has a variable called owner.
+This owner has information about the value, such as location in memory, length and capacity of the value. 
+For example, the object representation of Vec$<$i32$>$ is shown in Figure. This owner can live on the scope associated with its lifetime.
+When the owner is dropped, the value will be dropped too. This feature is similar to how RAII in C++ works. 
 However, acquisition of owner out of the scope where it was constructed is available in Rust with the concept of move.
 
-With move, a value can be transferred from one owner to another, For example, a value is instantiated in a function. 
-When it is returned to a new variable , the ownership of value is moved to the new variable. In Rust, one do not have to explicitly deallocate memory, 
+\subsection{Move}
+In Rust, for most types. operations like assigning a value to a variable, passing it to a function, or returning it from a function do not copy the value: they move it. 
+With move, a value can be transferred from one owner to another. The previous variable does not have ownership of the value; it is moved to a newly assigned variable. 
+To understand how this assignment implementation is unique from other programing languages, Python, C++, and Rust code example of assigning list or vector of strings are shown in Figure. 
+For example, a value is instantiated in a function. 
+When it is returned to a new variable, the ownership of value is moved to the new variable. In Rust, one do not have to explicitly deallocate memory, 
 because ownership of value is passed among variables across scope using move and eventually goes out of scope deallocating memory of the value.
 
+\subsection{Borrowing}
 Borrowing lets code use a value temporarily without affecting its ownership so that it reduces unnecessary movement of ownership. 

### 2020-04-06 project/practice/src/main.rs

@@ -3,71 +3,86 @@ use std::env;
 mod module;
 use module::deeptf::*;
 use module::rctf::*;
-use ndarray::{Array, ArrayView, ArrayViewMut, s, Ix1, Ix2, stack, Axis};
+use ndarray::{Array, ArrayView, ArrayViewMut, s, Ix1, Ix2};
 use std::collections::{HashMap, BinaryHeap};
 use std::cmp::{Ordering, max};
 use std::rc::Rc;
+use crossbeam;
 const MAX_THREADS: usize = 4;
 
 fn main() {
     let args: Vec<String> = env::args().collect();
     let method: i32 = args[1].parse::<i32>().unwrap();
-    let train_file = Path::new(&args[2]);
-    let test_file = Path::new(&args[3]);
+    let train_file = args[2];
+    let test_file = args[3];
     let k: usize = args[4].parse::<usize>().unwrap();
     let n_neighbors: usize = args[5].parse::<usize>().unwrap();
-    run(method, k, n_neighbors, &train_file, &test_file);
+    //run(method, k, n_neighbors, &train_file, &test_file);
 }
 
-fn run(method: i32, k: usize, n_neighbors: usize, train_file: &Path, test_file: &Path) {
+fn run(method: i32, k: usize, n_neighbors: usize, train_files: &[String], test_files: &[String]) {
     match method {
-        1 => run_ex_deepcopy(k, n_neighbors, train_file, test_file), 
-        2 => run_ex_rc(k, n_neighbors, train_file, test_file),
+        1 => run_ex_deepcopy(k, n_neighbors, train_files, test_files), 
+        //2 => run_ex_rc(k, n_neighbors, train_files, test_files),
         _ => println!("Wrong input")
     }
 }
 
-fn run_ex_deepcopy(k: usize, n_neighbors:usize, train_file: &Path, test_file: &Path) {
-    let prediction = k_nearest_neighbors(k, n_neighbors, train_file, test_file);
+fn run_ex_deepcopy(k: usize, n_neighbors:usize, train_files: &[String], test_files: &[String]) {
+    let prediction = k_nearest_neighbors_multithread(k, n_neighbors, train_files, test_files);
     println!("{:?}", prediction);
 }
 
-fn run_ex_rc(k: usize, n_neighbors:usize, train_file: &Path, test_file: &Path) {
-    let prediction = k_nearest_neighbors_with_rc(k, n_neighbors, train_file, test_file);
-    println!("{:?}", prediction);
[…]

### 2020-04-06 project/practice/src/module/deeptf.rs

@@ -8,8 +8,54 @@ use std::cmp::Reverse;
 use regex::Regex;
 use std::collections::HashSet;
 use stopwords::{Spark, Language, Stopwords};
-use ndarray::{Array, Ix1, Ix2};
+use ndarray::{Array, Ix1, Ix2, stack, Axis};
 
+pub fn vectorize_ids(ids: &[Vec<String>]) -> (Array<i32, Ix2>, HashMap<i32, String>) {
+    let n = ids.len();
+    let m = ids[0].len();
+    let mut encode_map = HashMap::new();
+    let mut decode_map = HashMap::new();
+    let mut encode = 0;
+    for i in 0..n {
+        for j in 0..m {
+            if encode_map.contains_key(&ids[i][j]) {
+                encode_map.insert(&ids[i][j].clone(), encode);
+                decode_map.insert(encode, &ids[i][j].clone());
+                encode += 1;
+            }
+        }
+    }
+    let mut vectorized = Array::zeros((n, m));
+    for i in 0..n {
+        for j in 0..m {
+            encode = *encode_map.get(&ids[i][j]).unwrap();
+            vectorized[[i, j]] = encode;
+        }
+    }
+    (vectorized, decode_map)
+}
+
+
+pub fn combine_neighbors(similarities: Vec<Array<f64, Ix2>>, mut ids: Vec<Vec<Vec<String>>>) -> (Array<f64, Ix2>, Vec<Vec<String>>){
+     let (n, m) = similarities[0].dim();
+     let l = ids.len();
+     let o = ids[0].len();
+     let mut combined_x = similarities[0]; 
+     let mut combined_y = ids[0];
+     for i in 1..l {
+        combined_x = stack![Axis(1), combined_x, similarities[i]];
+        concat_string_vectors(&combined_y[..], ids[i]);
+     }
+     (combined_x, combined_y)
+}
+
+
+pub fn concat_string_vectors(source: &mut [Vec<String>], mut other: Vec<Vec<String>>) {
+    let n = source.len();
+    for i in 0..n {
+        source[i].append(&other[i]);
+    }
+}
 
 pub fn get_id_from_label(label: &Array<i32, Ix1>, decode_map: &HashMap<i32, String>) -> Vec<String> {
     let n= label.dim();
@@ -21,6 +67,19 @@ pub fn get_id_from_label(label: &Array<i32, Ix1>, decode_map: &HashMap<i32, Stri
     res
 }
 
[…]

### 2020-04-06 project/practice/src/module/rctf.rs

@@ -19,6 +19,20 @@ pub fn get_id_from_label_with_rc(label: &Array<i32, Ix1>, decode_map: &HashMap<i
     res
 }
 
+pub fn get_ids_from_labels_with_rc(labels: &Array<i32, Ix2>, decode_map: &HashMap<i32, Rc<String>>) -> Vec<Vec<Rc<String>>> {
+    let (n, m) = labels.dim();
+    let mut res = Vec::with_capacity(n);
+    for i in 0..n {
+        let mut v = Vec::with_capacity(m);
+        for j in 0..m {
+            let id = decode_map.get(&labels[[i, j]]).unwrap();
+            v.push(Rc::clone(&id));
+        }
+        res.push(v);
+    }
+    res
+}
+
 
 
 pub fn split_x_y_with_rc(source: &[(Rc<String>, Vec<f64>)]) -> (Vec<String>, Vec<Vec<f64>>) {

### 2020-04-11 thesis_template/2_RelatedWork/model/spark.tex
complete

@@
 This owner has information about the value, such as location in memory, length and capacity of the value. 
-For example, the object representation of Vec$<$i32$>$ is shown in Figure. This owner can live on the scope associated with its lifetime.
+For example, the object representation of Vec$<$i32$>$ is shown in Figure~\ref{fig:rustvec}. The upper boxes represent owner variable in stack frame. 
+The lower boxes represent contiguous memory allocated to store i32. Its capacity is specified 10, but 7 values of i32 are stored. 
+Therefore, there are still spaces to store 3 values of i32 without reallocation of memory. This owner can live on the scope associated with its lifetime.
 When the owner is dropped, the value will be dropped too. This feature is similar to how RAII in C++ works. 
 However, acquisition of owner out of the scope where it was constructed is available in Rust with the concept of move.
+
+\begin{figure}[htb]
+    \includegraphics[width=15cm]{rust_vec.eps}
+    \caption{Representation of Rust Vec$<$i32$>$}
+    \label{fig:rustvec}
+\end{figure}
 

### 2020-04-11 project/practice/run.sh

@@ -1,1 +1,20 @@
-cargo run 1 20000 20 ~/master-thesis/data/TestingData.txt  ~/master-thesis/data/trainParition/*
+cargo clean
+cargo build
+
+for size in 100 1000 10000 100000
+do
+    rm -rf loging.log
+    echo "datastructure#k#n_neighbors#threadtime#globaltime" > loging.log
+
+    for method in 1
+    do
+        for k in 10000 20000
+        do
+            for n_neighbors in 10 20 30
+            do
+                time cargo run $method $k $n_neighbors ~/master-thesis/data/smallTest/TestingData_"$size".txt  ~/master-thesis/data/trainPartition/*
+            done
+        done
+    done
+cat loging.log > result/resultKnn_"$size".txt
+done

### 2020-04-11 project/practice/src/main.rs

@@ -2,13 +2,17 @@ use std::path::Path;
 use std::env;
 mod module;
 use module::deeptf::*;
-use module::rctf::*;
+use module::arctf::*;
 use ndarray::{Array, ArrayView, ArrayViewMut, s, Ix1, Ix2};
 use std::collections::{HashMap, BinaryHeap};
 use std::cmp::{Ordering, max};
-use std::rc::Rc;
+use std::sync::Arc;
 use crossbeam;
-const MAX_THREADS: usize = 3;
+use std::time::Instant;
+use std::fs::OpenOptions;
+use std::io::prelude::*;
+
+const MAX_THREADS: usize = 10;
 
 fn main() {
     let args: Vec<String> = env::args().collect();
@@ -20,29 +24,44 @@ fn main() {
     for i in 5..5 + MAX_THREADS {
         train_files.push(args[i].clone());
     }
-    println!("train files: {:?}", train_files);
     run(method, k, n_neighbors, &train_files, &test_file);
+}
+
+fn write_to_file(k: usize, n_neighbors:usize, elapsed_threads: u128, elapsed_global: u128) {
+    let output = format!("[RustVector]#{:?}#{:?}#{:?}#{:?}\n", 
+                         k, n_neighbors, elapsed_threads, elapsed_global);
+    println!("{}",output);
+    let mut file = OpenOptions::new()
+        .append(true)
+        .create(true)
+        .open("loging.log")
+        .unwrap();
+
+    file.write_all(output.as_bytes()).expect("Fail to write file.");
 }
 
 fn run(method: i32, k: usize, n_neighbors: usize, train_files: &[String], test_file: &String) {
     match method {
         1 => run_ex_deepcopy(k, n_neighbors, train_files, test_file), 
-        //2 => run_ex_rc(k, n_neighbors, train_files, test_files),
+        2 => run_ex_arc(k, n_neighbors, train_files, test_file),
         _ => println!("Wrong input")
     }
 }
 
 fn run_ex_deepcopy(k: usize, n_neighbors:usize, train_files: &[String], test_file: &String) {
-    let prediction = k_nearest_neighbors_multithread(k, n_neighbors, train_files, test_file);
+    let (prediction, elapsed_threads, elapsed_global)= k_nearest_neighbors_multithread(k, n_neighbors, train_files, test_file);
+    write_to_file(k, n_neighbors, elapsed_threads, elapsed_global);
     println!("{:?}", prediction);
 }
 
[…]

### 2020-04-11 project/practice/src/module/arctf.rs

@@ -6,27 +6,74 @@ use std::collections::HashMap;
 use priority_queue::PriorityQueue;
 use std::cmp::Reverse;
 use regex::Regex;
-use std::rc::Rc;
-use ndarray::{Array,Ix1, Ix2};
+use std::collections::HashSet;
+use stopwords::{Spark, Language, Stopwords};
+use ndarray::{Array, Ix1, Ix2, stack, Axis};
+use std::sync::Arc;
 
-pub fn get_id_from_label_with_rc(label: &Array<i32, Ix1>, decode_map: &HashMap<i32, Rc<String>>) -> Vec<Rc<String>> {
+pub fn vectorize_ids_with_arc(ids: &[Vec<Arc<String>>]) -> (Array<i32, Ix2>, HashMap<i32, Arc<String>>) {
+    let n = ids.len();
+    let m = ids[0].len();
+    let mut encode_map = HashMap::new();
+    let mut decode_map = HashMap::new();
+    let mut encode = 0;
+    for i in 0..n {
+        for j in 0..m {
+            if !encode_map.contains_key(&ids[i][j]) {
+                encode_map.insert(Arc::clone(&ids[i][j]), encode);
+                decode_map.insert(encode, Arc::clone(&ids[i][j]));
+                encode += 1;
+            }
+        }
+    }
+    let mut vectorized = Array::zeros((n, m));
+    for i in 0..n {
+        for j in 0..m {
+            encode = *encode_map.get(&ids[i][j]).unwrap();
+            vectorized[[i, j]] = encode;
+        }
+    }
+    (vectorized, decode_map)
+}
+
+pub fn combine_neighbors_with_arc(similarities: Vec<Array<f64, Ix2>>, mut ids: Vec<Vec<Vec<Arc<String>>>>) -> (Array<f64, Ix2>, Vec<Vec<Arc<String>>>){
+    let (n, m) = similarities[0].dim();
+    let l = ids.len();
+    let o = ids[0].len();
+    let mut combined_x = similarities[0].clone(); 
+    let mut combined_y = ids[0].clone();
+    for i in 1..l {
+       combined_x = stack![Axis(1), combined_x, similarities[i]];
+       concat_string_vectors_with_arc(&mut combined_y[..], ids[i].clone());
+    }
+    (combined_x, combined_y)
+}
+
[…]

### 2020-04-11 thesis_template/2_RelatedWork/model/spark.tex
documented rust memory management

@@
 \subsection{Move}
-In Rust, for most types. operations like assigning a value to a variable, passing it to a function, or returning it from a function do not copy the value: they move it. 
+In Rust, for most types operations like assigning a value to a variable, passing it to a function, or returning it from a function do not copy the value: they move it. 
 With move, a value can be transferred from one owner to another. The previous variable does not have ownership of the value; it is moved to a newly assigned variable. 
-To understand how this assignment implementation is unique from other programing languages, Python, C++, and Rust code example of assigning list or vector of strings are shown in Figure. 
-For example, a value is instantiated in a function. 
-When it is returned to a new variable, the ownership of value is moved to the new variable. In Rust, one do not have to explicitly deallocate memory, 
-because ownership of value is passed among variables across scope using move and eventually goes out of scope deallocating memory of the value.
+To understand how this assignment implementation is unique from other programing languages, Java, C++, and Rust code example of assigning list or vector of strings are shown.
+
+Below a few lines of code are initialization of list of string and reassigning it to other variables. 
+\begin{lstlisting}
+    List<String >s = new ArrayList<>(
+                     Arrays.asList("lemon", "orange", "apple"))
+    String t = s
+    String u = s
+ \end{lstlisting}
+Figure~\ref{fig:pythonlist} represents the memory allocated after a Java ArrayList of strings is initialized and assigned to variable called s. After assigning s to t and to u, 
+the memory representation become Figure~\ref{fig:pythonlistcopied}. The assignments are simply setting pointers to the ArrayList object and increment reference count.
+
+\begin{figure}[htb]
+    \includegraphics[width=10cm]{python_list_copied.eps}
+    \caption{Representation of Java ArrayList of String}
+    \label{fig:pythonlist}
+\end{figure}
+
+\begin{figure}[htb]
+    \includegraphics[width=10cm]{python_list.eps}
+    \caption{Representation of Java ArrayList of String after assignment to another variable}
+    \label{fig:pythonlistcopied}
+\end{figure}
+
+Now, the analogous C++ code is shown below. 
+\begin{lstlisting}
+    vector<string> s = {"lemon", "orange", "apple"};
+    vector<string> t = s;
+    vector<string> u = s;
+ \end{lstlisting}
+Figure~\ref{fig:cpluscplusvector} shows the memory allocated when the vector is initialized. Figure~\ref{fig:cpluscplusvectorcopied} is a representation of after the assignments of s to t and to u. 
+In C++, assigning value of vector to other variables involves allocating memory for new vector and copying the contents of the original vector to newly allocated one.
+
+\begin{figure}[htb]
+    \includegraphics[width=15cm]{cplusplus_vector.eps}
+    \caption{Representation of C++ vector of string}
+    \label{fig:cpluscplusvector}
+\end{figure}
+
+\begin{figure}[htb]
+    \includegraphics[width=15cm]{cplusplus_vector_copied.eps}
+    \caption{Representation of C++ vector of string after assignment to another variable}
+    \label{fig:cpluscplusvectorcopied}
+\end{figure}
+
+In Rust code, the code is like below, 
+\begin{lstlisting}
+    let s = vec!["lemon".to_string, "orange".to_string, "apple".to_string];
+    let t = s;
+    let u = s;
+ \end{lstlisting}
+
+The representation of the original Vec of String in Rust is the almost same in C++ vector of string. Figure~\ref{fig:rustvecmoved} however shows different behavior when Rust assigns s to t. 
+The value is moved to t from s so that the source variable s is uninitialized. The Rust code actually throws compile error, because we are assigning uninitialized variable at the last line.
+
+\begin{figure}[htb]
+    \includegraphics[width=15cm]{rust_vec_moved.eps}
+    \caption{Representation of Rust Vec$<$String$>$ after assignment to another variable}
+    \label{fig:rustvecmoved}
+\end{figure}
 

### 2020-04-11 project/practice/src/main.rs

@@ -56,7 +56,7 @@ fn run_ex_deepcopy( k: usize, n_neighbors:usize, train_files: &[String], test_fi
 
 fn run_ex_arc(k: usize, n_neighbors:usize, train_files: &[String], test_file: &String) {
      let (prediction, elapsed_threads, elapsed_global) = k_nearest_neighbors_multithread_with_arc(k, n_neighbors, train_files, test_file);
-     write_to_file("Arc", k, n_neighbors, elapsed_threads, elapsed_global);
+     write_to_file("arc", k, n_neighbors, elapsed_threads, elapsed_global);
      println!("{:?}", prediction);
 }
 

### 2020-04-14 project/practice/src/main.rs
done knn

@@ -2,259 +2,386 @@ use std::path::Path;
 use std::env;
 mod module;
 use module::deeptf::*;
-use module::arctf::*;
-use ndarray::{Array, ArrayView, ArrayViewMut, s, Ix1, Ix2};
-use std::collections::{HashMap, BinaryHeap};
-use std::cmp::{Ordering, max};
-use std::sync::Arc;
-use crossbeam;
 use std::time::Instant;
 use std::fs::OpenOptions;
 use std::io::prelude::*;
+use std::fs::File;
+use std::io::{self, BufRead, BufReader, Lines, Read};
+use std::iter::{Peekable, Iterator};
+use ndarray::prelude::*;
+use ndarray::{
+    Data,
+    RemoveAxis,
+    Zip,
+};
+use std::cmp::Ordering;
+use std::ptr::copy_nonoverlapping;
 
 const MAX_THREADS: usize = 4;
 
 fn main() {
-    let args: Vec<String> = env::args().collect();
-    let method: i32 = args[1].parse::<i32>().unwrap();
-    let k: usize = args[2].parse::<usize>().unwrap();
-    let n_neighbors: usize = args[3].parse::<usize>().unwrap();
-    let mut train_files = Vec::with_capacity(MAX_THREADS);
-    let mut test_file = args[4].clone();
-    for i in 5..5 + MAX_THREADS {
-        train_files.push(args[i].clone());
-    }
-    run(method, k, n_neighbors, &train_files, &test_file);
+    let a = Array::linspace(0., 63., 64).into_shape((8, 8)).unwrap();
+    let strings = a.map(|x| x.to_string());
+
+    let perm = a.sort_axis_by(Axis(1), |i, j| {
+        a[[i, 0]] > a[[j, 0]]
+    });
+    println!("{:?}", perm);
+    let b = a.permute_axis(Axis(0), &perm);
+    println!("{:?}", b);
+
+    println!("{:?}", strings);
+    let c = strings.permute_axis(Axis(1), &perm);
+    println!("{:?}", c);
+    // let args: Vec<String> = env::args().collect();
+    // let method: i32 = args[1].parse::<i32>().unwrap();
+    // let k: usize = args[2].parse::<usize>().unwrap();
+    // let n_neighbors: usize = args[3].parse::<usize>().unwrap();
+    // let mut train_files = Vec::with_capacity(MAX_THREADS);
+    // let mut test_file = args[4].clone();
[…]

### 2020-04-14 project/rust_knn_partitioned_train_fixed_test/run.sh

@@ -1,0 +1,20 @@
+cargo clean
+cargo build --release
+
+for size in 100 1000 10000 100000
+do
+    rm -rf loging.log
+    echo "datastructure#k#n_neighbors#threadtime#globaltime" > loging.log
+
+    for method in 1 2
+    do
+        for k in 10000 20000
+        do
+            for n_neighbors in 10 20 30
+            do
+                time cargo run --release  $method $k $n_neighbors ~/master-thesis/data/TestingData.txt  ~/master-thesis/data/trainPartition/*
+            done
+        done
+    done
+cat loging.log > result/resultKnn_"$size".txt
+done

### 2020-04-14 project/rust_knn_partitioned_train_fixed_test/src/main.rs

@@ -1,0 +1,260 @@
+use std::path::Path;
+use std::env;
+mod module;
+use module::deeptf::*;
+use module::arctf::*;
+use ndarray::{Array, ArrayView, ArrayViewMut, s, Ix1, Ix2};
+use std::collections::{HashMap, BinaryHeap};
+use std::cmp::{Ordering, max};
+use std::sync::Arc;
+use crossbeam;
+use std::time::Instant;
+use std::fs::OpenOptions;
+use std::io::prelude::*;
+
+const MAX_THREADS: usize = 4;
+
+fn main() {
+    let args: Vec<String> = env::args().collect();
+    let method: i32 = args[1].parse::<i32>().unwrap();
+    let k: usize = args[2].parse::<usize>().unwrap();
+    let n_neighbors: usize = args[3].parse::<usize>().unwrap();
+    let mut train_files = Vec::with_capacity(MAX_THREADS);
+    let mut test_file = args[4].clone();
+    for i in 5..5 + MAX_THREADS {
+        train_files.push(args[i].clone());
+    }
+    run(method, k, n_neighbors, &train_files, &test_file);
+}
+
+fn write_to_file(method: &str, k: usize, n_neighbors:usize, elapsed_threads: u128, elapsed_global: u128) {
+    let output = format!("[RustVector]#{:?}#{:?}#{:?}#{:?}#{:?}\n", 
+                         method, k, n_neighbors, elapsed_threads, elapsed_global);
+    println!("{}",output);
+    let mut file = OpenOptions::new()
+        .append(true)
+        .create(true)
+        .open("loging.log")
+        .unwrap();
+
+    file.write_all(output.as_bytes()).expect("Fail to write file.");
+}
+
+fn run(method: i32, k: usize, n_neighbors: usize, train_files: &[String], test_file: &String) {
+    match method {
+        1 => run_ex_deepcopy(k, n_neighbors, train_files, test_file), 
+        2 => run_ex_arc(k, n_neighbors, train_files, test_file),
+        _ => println!("Wrong input")
+    }
+}
+
+fn run_ex_deepcopy( k: usize, n_neighbors:usize, train_files: &[String], test_file: &String) {
+    let (prediction, elapsed_threads, elapsed_global)= k_nearest_neighbors_multithread(k, n_neighbors, train_files, test_file);
+    write_to_file("deepcopy", k, n_neighbors, elapsed_threads, elapsed_global);
+    println!("{:?}", prediction);
+}
+
[…]

### 2020-04-14 project/rust_knn_partitioned_train_fixed_test/src/module/arctf.rs

@@ -1,0 +1,305 @@
+use std::fs::File;
+use std::io::{self, BufReader};
+use std::io::prelude::*;
+use std::path::Path;
+use std::collections::HashMap;
+use priority_queue::PriorityQueue;
+use std::cmp::Reverse;
+use regex::Regex;
+use std::collections::HashSet;
+use stopwords::{Spark, Language, Stopwords};
+use ndarray::{Array, Ix1, Ix2, stack, Axis};
+use std::sync::Arc;
+
+pub fn vectorize_ids_with_arc(ids: &[Vec<Arc<String>>]) -> (Array<i32, Ix2>, HashMap<i32, Arc<String>>) {
+    let n = ids.len();
+    let m = ids[0].len();
+    let mut encode_map = HashMap::new();
+    let mut decode_map = HashMap::new();
+    let mut encode = 0;
+    for i in 0..n {
+        for j in 0..m {
+            if !encode_map.contains_key(&ids[i][j]) {
+                encode_map.insert(Arc::clone(&ids[i][j]), encode);
+                decode_map.insert(encode, Arc::clone(&ids[i][j]));
+                encode += 1;
+            }
+        }
+    }
+    let mut vectorized = Array::zeros((n, m));
+    for i in 0..n {
+        for j in 0..m {
+            encode = *encode_map.get(&ids[i][j]).unwrap();
+            vectorized[[i, j]] = encode;
+        }
+    }
+    (vectorized, decode_map)
+}
+
+pub fn combine_neighbors_with_arc(similarities: Vec<Array<f64, Ix2>>, mut ids: Vec<Vec<Vec<Arc<String>>>>) -> (Array<f64, Ix2>, Vec<Vec<Arc<String>>>){
+    let (n, m) = similarities[0].dim();
+    let l = ids.len();
+    let o = ids[0].len();
+    let mut combined_x = similarities[0].clone(); 
+    let mut combined_y = ids[0].clone();
+    for i in 1..l {
+       combined_x = stack![Axis(1), combined_x, similarities[i]];
+       concat_string_vectors_with_arc(&mut combined_y[..], ids[i].clone());
+    }
+    (combined_x, combined_y)
+}
+
+pub fn concat_string_vectors_with_arc(source: &mut [Vec<Arc<String>>], mut other: Vec<Vec<Arc<String>>>) {
+    let n = source.len();
+    for i in 0..n {
+        source[i].append(&mut other[i]);
+    }
+}
+
[…]

### 2020-04-14 project/rust_knn_partitioned_train_fixed_test/src/module/deeptf.rs

@@ -1,0 +1,303 @@
+use std::fs::File;
+use std::io::{self, BufReader};
+use std::io::prelude::*;
+use std::path::Path;
+use std::collections::HashMap;
+use priority_queue::PriorityQueue;
+use std::cmp::Reverse;
+use regex::Regex;
+use std::collections::HashSet;
+use stopwords::{Spark, Language, Stopwords};
+use ndarray::{Array, Ix1, Ix2, stack, Axis};
+
+pub fn vectorize_ids(ids: &[Vec<String>]) -> (Array<i32, Ix2>, HashMap<i32, String>) {
+    let n = ids.len();
+    let m = ids[0].len();
+    let mut encode_map = HashMap::new();
+    let mut decode_map = HashMap::new();
+    let mut encode = 0;
+    for i in 0..n {
+        for j in 0..m {
+            if !encode_map.contains_key(&ids[i][j]) {
+                encode_map.insert(ids[i][j].clone(), encode);
+                decode_map.insert(encode, ids[i][j].clone());
+                encode += 1;
+            }
+        }
+    }
+    let mut vectorized = Array::zeros((n, m));
+    for i in 0..n {
+        for j in 0..m {
+            encode = *encode_map.get(&ids[i][j]).unwrap();
+            vectorized[[i, j]] = encode;
+        }
+    }
+    (vectorized, decode_map)
+}
+
+
+pub fn combine_neighbors(similarities: Vec<Array<f64, Ix2>>, mut ids: Vec<Vec<Vec<String>>>) -> (Array<f64, Ix2>, Vec<Vec<String>>){
+     let (n, m) = similarities[0].dim();
+     let l = ids.len();
+     let o = ids[0].len();
+     let mut combined_x = similarities[0].clone(); 
+     let mut combined_y = ids[0].clone();
+     for i in 1..l {
+        combined_x = stack![Axis(1), combined_x, similarities[i]];
+        concat_string_vectors(&mut combined_y[..], ids[i].clone());
+     }
+     (combined_x, combined_y)
+}
+
+
+pub fn concat_string_vectors(source: &mut [Vec<String>], mut other: Vec<Vec<String>>) {
+    let n = source.len();
+    for i in 0..n {
+        source[i].append(&mut other[i]);
+    }
+}
+
+pub fn get_id_from_label(label: &Array<i32, Ix1>, decode_map: &HashMap<i32, String>) -> Vec<String> {
+    let n= label.dim();
+    let mut res = Vec::with_capacity(n);
[…]

### 2020-04-14 project/rust_knn_partitioned_train_fixed_test/src/module/mod.rs

@@ -1,0 +1,2 @@
+pub mod deeptf;
+pub mod arctf;

### 2020-04-14 project/rust_knn_streaming/run.sh

@@ -1,0 +1,8 @@
+#!/bin/sh
+cargo clean
+cargo build --release
+
+#train_file = '/Users/sinsakuokazaki/master-thesis/data/SmallTrainingData.txt'
+#train_lines = $((wc -l $train_file))
+#echo "train_line: train_file"
+cargo run --release 1 20000 20 3 /Users/sinsakuokazaki/master-thesis/data/trainPartition/* /Users/sinsakuokazaki/master-thesis/data/testPartition/* 861 861 861 859 4681 4681 4681 4681

### 2020-04-14 project/rust_knn_streaming/src/main.rs

@@ -1,0 +1,290 @@
+use std::path::Path;
+use std::env;
+mod module;
+use module::deeptf::*;
+use std::time::Instant;
+use std::fs::OpenOptions;
+use std::io::prelude::*;
+use std::fs::File;
+use std::io::{self, BufRead, BufReader, Lines, Read};
+use std::iter::{Peekable, Iterator};
+use ndarray::prelude::*;
+use std::collections::{HashMap, BinaryHeap};
+use std::cmp::{Ordering, max};
+use crossbeam;
+use std::fmt::Debug;
+
+const MAX_THREADS: usize = 4;
+
+fn main() {
+    let args: Vec<String> = env::args().collect();
+    println!("Started");
+    let mut idx = 1;
+    let method: i32 = args[idx].parse::<i32>().unwrap();
+    println!("Method: {:?}", method);
+    idx += 1;
+    let k = args[idx].parse::<usize>().unwrap();
+    println!("K: {:?}", k);
+    idx += 1;
+    let n_neighbors = args[idx].parse::<usize>().unwrap();
+    println!("N_neighbors: {:?}", n_neighbors);
+    idx +=1;
+    let n_batch = args[idx].parse::<usize>().unwrap(); 
+    println!("N_batch: {:?}", n_batch);
+    idx += 1;
+    let mut f_trains = Vec::with_capacity(MAX_THREADS);
+    for _ in 0..MAX_THREADS {
+        let f_train = args[idx].clone();
+        f_trains.push(f_train);
+        idx +=1;
+    }
+
+    let mut f_tests = Vec::with_capacity(MAX_THREADS); 
+    for _ in 0..MAX_THREADS {
+        let f_test = args[idx].clone();
+        f_tests.push(f_test);
+        idx += 1;
+    }
+
+    let mut n_line_trains = Vec::with_capacity(MAX_THREADS); 
+    for _ in 0..MAX_THREADS {
+        let n_line_train = args[idx].parse::<usize>().unwrap();
+        n_line_trains.push(n_line_train);
+        idx += 1;
+    }
+
+    let mut n_line_tests = Vec::with_capacity(MAX_THREADS);
+    for _ in 0..MAX_THREADS {
+        let n_line_test = args[idx].parse::<usize>().unwrap();
+        n_line_tests.push(n_line_test);
+        idx += 1;
+    }
+
+    run(method, k, n_neighbors, &f_trains[..], &f_tests[..], &n_line_trains[..], &n_line_tests[..], n_batch);
+}
+
[…]

### 2020-04-17 thesis_template/3_Body/body.tex
documented
Tree-aggregate documented on process
revise
documented concept

@@
-\chapter{Body of my thesis}
+\chapter{Experiment}
 \label{chapter:body}
@@
 
-\section{Some results}
-\label{sec:results}
-
-Here goes all the important stuff, likely with a lot of graphics like this:
-
-\begin{figure}[htb]
-  \begin{minipage}[t]{0.49\linewidth}\centering
-    \includegraphics[width=7cm]{figure_sampling_view1.eps}
-    \medskip
-    \centerline{(a)}
-  \end{minipage}\hfill
-  \begin{minipage}[t]{0.49\linewidth}\centering
-    \includegraphics[width=7cm]{figure_sampling_view2.eps}
-    \medskip
-    \centerline{(b)}
-  \end{minipage}
-  \caption{Assignment of single-view intensities to RGB components: (a) view
-    \#1; and (b) view \#2. }
-  \label{fig:Sampling}
-\end{figure}
-
-You will also be using a lot of citations. Here is the format required in the dissertation: \cite{lamport1985:latex},\cite{Debr01}.
-
-In all likelihood, you will need to insert tables. See one example on the next page.
+\section{Concept}
+\label{sec:history}
+\input{3_Body/chapter/concept}
 \clearpage
 
-\begin{table}[h]
-	\caption{Absolute disparity error per pixel for the test data from
-		Fig.~\ref{fig:Sampling} and different parameter values. In each experiment one
-		parameter is adjusted while other parameters are unchanged.} 
-	\centering
-	\begin{minipage}[b]{0.30\linewidth}
-		\centerline{$\eta=6000$, $\mu=2000$}\smallskip
-		\centering
-		\begin{tabular}{ccc}
-			\hline
-			$K$ & $u_1$ & $u_2$\\
-			\hline
-			3   & 0.52 &0.46\\
-			7   & 0.47 &0.43\\
-			10  & 0.35 &0.36\\
-			12  & 0.37 &0.36\\
-			\hline
-		\end{tabular}
-	\end{minipage}
-	%
-	\begin{minipage}[b]{0.34\linewidth}
-		\centerline{$K=10$, $\mu=2000$}\smallskip
-		\centering
-		\begin{tabular}{ccc}
-			\hline
-			$\eta$ & $u_1$ & $u_2$\\
-			\hline
-			1000&0.54& 0.45\\
-			3000&0.43& 0.40\\
-			6000&0.35& 0.36\\
-			9000&0.37& 0.37\\
-			\hline
-		\end{tabular}
-	\end{minipage}
-	%
-	\begin{minipage}[b]{0.32\linewidth}
-		\centerline{$K=10$, $\eta=6000$}\smallskip
-		\centering
-		\begin{tabular}{ccc}
-			\hline
-			$\mu$ & $u_1$ & $u_2$\\
-			\hline
-			100 &1.00&1.16\\
-			1000&0.53&0.47\\
-			2000&0.35&0.36\\
-			3000&0.44&0.43\\
-			\hline
-		\end{tabular}
-	\end{minipage}
-	%
-	\label{tab:Parameters}
-\end{table}
-
-Of course, there must be a Table of Contents at the beginning of the thesis.
+\section{Evaluation}
+\label{sec:history}
+\input{3_Body/chapter/evaluation}
+\clearpage

### 2020-04-17 thesis_template/3_Body/chapter/concept.tex
documented concept

@@
-\section{Type of Reference}
+\subsection{Type of Variable}
 \label{sec:history}
+In Rust, there are three variable types: owner, reference, and slice (only for sequence of values). 
+A developer is sometimes forced to use specific variable types. For example, some of methods are only implemented to specific variable types.
+However, one can select any variable types for operation in most case.
+
+These variables have different memory representation shown in Figure~\ref{fig:own_ref_slice}.
+The owner has a pointer pointing to the memory address of sequence values, length of the values, and capacity allocated to store additional values. 
+Reference and Slice are variables borrowing value owned by other variable. The reference is a pointer that points to the owner. 
+The slice is a pointer that points to memory address of sequence values. It has value such as length of sequence values stored in the memory. 
+Since they have different memory representation, an assumption is that it takes different time to access to the contents of the memory among these pointer types.
+We examine this by constructing complex objects whose fields are these variable types. The details are explained in section 3.2.
+
+\begin{figure}[htb]
+    \includegraphics[width=10cm]{own_ref_slice.eps}
+    \caption{Memory Representation of Owner, Reference, and Slice Type}
+    \label{fig:own_ref_slice}
+\end{figure}
+
+\subsection{Reference Count}
+\label{sec:history}
+Reference is useful to avoid movement of ownership. However, one needs to track its lifetime and explicitly includes it in code, 
+because Rust compiler cannot infer it. This can be another encumbrance. We can instead acquire multiple owners to single value by using Reference Counting (Rc). 
+By leveraging Rc, a value can be shared like what borrowing plays the role in Rust programming.
+
+The difference is that Rc checks number of owner pointing to the actual data and makes sure the data is not deleted 
+until all the owners are dereferenced. Using Rc is sometimes preferable approach for developers especially when lifetime planning is extremely difficult.
+However, the possible problem regarding to Rc is the cost for tracking the number of references. 
+Having this assumption, an experiment is conducted to examine difference of runtime performance of dropping reference and Rc. 
+This is explained in section 3.2.
+
+\subsection{Multithreading}
+\label{sec:history}
+In Rust programming, writing concurrent code is relatively easy. The care Rust takes with reference, mutability, and lifetimes is valuable enough in single-threaded programs, 
+but it also is in concurrent programming. Rust has tools to write concurrent code, such as threads, locks, atomic reference. 
+Therefore, one can implement various concurrent codes for the same purpose with different memory management strategies. 
+The most ubiquitous tool used in Rust concurrent code is Atomic Reference Counting (Arc).
+
+Arc is a simple interface that allows threads to share data. Arc allows multiple variable to have ownerships of a particular value similarly to Rc, 
+but also supports atomic feature enabling the ownerships exist in different threads. 
+In many situation where developer write a multithreading code, the deletion of Arc happens significant amount of times. 
+Similarly to Rc, our assumption is that deletion of Arc has also overhead when we compare to normal reference. 
+To assess runtime performances of algorithm with Arc vs normal reference, we implement merge-sort algorithm in two different ways.
+
+\subsection{Algorithm in Big Data}
+\label{sec:history}
+Finally, we implement some of algorithm common in Big Data processing: Tree-aggregate and K-Nearest-Neighbors (KNN).
+
+Tree-aggregate is a communication patten heavily used for Machine Learning algorithm in Spark (MLlib). 
+In the traditional aggregation function in Spark, results of aggregation in all executor clusters are sent to the driver. 
+That is why this operation suffers from the CPU cost in merging partial results and the network bandwidth limit.
+Tree-aggregate is a communication pattern which overcomes these problems by breaking aggregate operation in multi-level represented like tree structure.
+
+KNN is a traditional Machine Learning algorithm which classify targets into categories. 
+Through experiments with these algorithm, we aim to find algorithm with understandability and efficiency. 
 \clearpage
-
-\section{Multithreading}
-\label{sec:history}
-\clearpage
-
-\section{Data Generation}
-\label{sec:history}
-\clearpage

### 2020-04-17 thesis_template/3_Body/chapter/evaluation.tex
documented concept

\subsection{Experiment for Accessing Object with Different Variable Type}
\label{sec:history}
\input{3_Body/model/access_own_reference_slice}
\clearpage

\subsection{Assessment of different reference methods in Rust}
\label{sec:history}
\input{3_Body/model/drop_ref_rc}
\clearpage

\subsection{Experiment for Merge-sort}
\label{sec:history}
\input{3_Body/model/merge_sort_experiment}
\clearpage

\subsection{Experiment for Tree-aggregation}
\label{sec:history}
\input{3_Body/model/tree_aggregate_experiment}
\clearpage

\subsection{Elements Copy and Insertion into Size-initialized Vector in Rust.}
\label{sec:history}
\input{3_Body/model/element_copy_initialization}

### 2020-04-17 thesis_template/3_Body/model/access_own_reference_slice.tex
documented concept

\subsection{Concept}
This experiment is conducted to understand two questions. One is how different pointer types have impact to runtime performance.
The other is how initialization of Vec size has impact to runtime performance. 
In this experiment, we focus on owner, reference, and additionally slice as a pointer to sequence values. 
The memory representations of these pointer types are shown in figure.

The owner has a pointer pointing to the memory address of sequence values, length of the values, and capacity allocated to store additional values. 
The reference is a pointer that points to the owner. The slice is a pointer that points to memory address of sequence values and has value such as length of 
sequence values stored in the memory. Since they have different memory representation, an assumption is that it takes different time to access to the contents of the memory among these pointer types.

To evaluate this assumption, we use the three type of complex object.

\begin{figure}[htb]
    \includegraphics[width=15cm]{rust_access_different_poniter_init.eps}
    \caption{Runtime of Access to Different Pointer Types with Vec Size Initialization}
    \label{fig:rustaccessinit}
\end{figure}

\begin{figure}[htb]
    \includegraphics[width=15cm]{rust_access_different_poniter_noinit.eps}
    \caption{Runtime of Access to Different Pointer Types without Vec Size Initialization}
    \label{fig:rustaccessnoinit}
\end{figure}

\begin{figure}[htb]
    \includegraphics[width=15cm]{rust_access_init_vs_noint.eps}
    \caption{Runtime of Access to Fields of Complex Object with Initialization vs without Initialization}
    \label{fig:rustaccessnoinit}
\end{figure}

The representation of these objects are shown in Figure~\ref{fig:customer} and Figure~\ref{fig:order}. 
\begin{figure}[htb]
    \begin{minipage}[t]{0.2\linewidth}\centering
        \begin{lstlisting}
            struct CustomerOwned {
                key: i32,
                age: i32,
                num_purchase: i32,
                total_purchase: f64,
                duration_spent: f64, 
                duration_since: f64,
                zip_code: String,
                address: String,
                country: String,
                state: String,
                first_name: String,
                last_name: String,
                province: String,
                comment: String, 
                order: OrderOwned
            }
        \end{lstlisting}
      \medskip
      \centerline{(a)}
    \end{minipage}\hfill
    \begin{minipage}[t]{0.6\linewidth}\centering
        \begin{lstlisting}
            struct CustomerBorrowed<'a> {
                key: &'a i32,
                age: &'a i32,
                num_purchase: &'a i32,
                total_purchase: &'a f64,
                duration_spent: &'a f64, 
                duration_since: &'a f64,
                zip_code: &'a String,
                address: &'a String,
                country: &'a String,
                state: &'a String,
                first_name: &'a String,
                last_name: &'a String,
                province: &'a String,
                comment: &'a String, 
                order: &'a OrderBorrowed<'a>
            }
        \end{lstlisting}
      \medskip
      \centerline{(b)}
    \end{minipage}
    \begin{minipage}[t]{0.2\linewidth}\centering
        \begin{lstlisting}
            struct CustomerSlice<'a> {
                key: &'a i32,
                age: &'a i32,
                num_purchase: &'a i32,
                total_purchase: &'a f64,
                duration_spent: &'a f64, 
                duration_since: &'a f64,
                zip_code: &'a str,
                address: &'a str,
                country: &'a str, 
                state: &'a str,
                first_name: &'a str,
                last_name: &'a str,
                province: &'a str,
                comment: &'a str,
                order: &'a OrderSlice<'a>
            }
        \end{lstlisting}
      \medskip
      \centerline{(c)}
    \end{minipage}\hfill
    \caption{Representation of Customer objects Whose fields are different variable type: (a) CustomerOwned struct whose fields are all owned 
    (b) CustomerBorrowed struct whose fields are borrowed with reference (c) CustomerSlice struct whose fields are borrowed with slice for sequence value, otherwise reference}
    \label{fig:customer}
 \end{figure}

 \begin{figure}[htb]
    \begin{minipage}[t]{0.2\linewidth}\centering
        \begin{lstlisting}
            struct OrderOwned {
                order_id: i32,
                num_items: i32, 
                payment: f64,
                order_time: f64,
                title: String,
                comment: String
            } 
        \end{lstlisting}
      \medskip
      \centerline{(a)}
    \end{minipage}\hfill
    \begin{minipage}[t]{0.6\linewidth}\centering
        \begin{lstlisting}
            struct OrderBorrowed<'a> {
                order_id: &'a i32,
                num_items: &'a i32, 
                payment: &'a f64,
                order_time: &'a f64,
                title: &'a String,
                comment: &'a String
            }
        \end{lstlisting}
      \medskip
      \centerline{(b)}
    \end{minipage}
    \begin{minipage}[t]{0.2\linewidth}\centering
        \begin{lstlisting}
            struct OrderSlice<'a> {
                order_id: &'a i32,
                num_items: &'a i32, 
                payment: &'a f64,
                order_time: &'a f64,
                title: &'a str,
                comment: &'a str
            }
        \end{lstlisting}
      \medskip
      \centerline{(c)}
    \end{minipage}\hfill
    \caption{Representation of Order objects Whose fields are different variable type: (a) OrderOwned struct whose fields are all owned 
    (b) OrderBorrowed struct whose fields are borrowed with reference (c) OrderSlice struct whose fields are borrowed with slice for sequence value, otherwise reference}
    \label{fig:order}
 \end{figure}

### 2020-04-17 thesis_template/3_Body/model/element_copy_initialization.tex
documented concept

@@
 \end{figure}
-
-\section{Access time to owned, borrowed, and sliced field of object}
-\label{sec:history}
-In this experiment, differences of access time to among owned, borrowed, and sliced are observed. 
-Each variable has slightly different use of memory.
-
-\begin{figure}[htb]
-    \begin{lstlisting}
-        struct CustomerOwned {
-            key: i32,
-            age: i32,
-            num_purchase: i32,
-            total_purchase: f64,
-            duration_spent: f64, 
-            duration_since: f64,
-            zip_code: String,
-            address: String,
-            country: String,
-            state: String,
-            first_name: String,
-            last_name: String,
-            province: String,
-            comment: String, 
-            order: OrderOwned
-        }
-
-        struct CustomerBorrowed<'a> {
-            key: &'a i32,
-            age: &'a i32,
-            num_purchase: &'a i32,
-            total_purchase: &'a f64,
-            duration_spent: &'a f64, 
-            duration_since: &'a f64,
-            zip_code: &'a String,
-            address: &'a String,
-            country: &'a String,
-            state: &'a String,
-            first_name: &'a String,
-            last_name: &'a String,
-            province: &'a String,
-            comment: &'a String, 
-            order: &'a OrderBorrowed<'a>
-        }
-
-        struct CustomerSlice<'a> {
-            key: &'a i32,
-            age: &'a i32,
-            num_purchase: &'a i32,
-            total_purchase: &'a f64,
-            duration_spent: &'a f64, 
-            duration_since: &'a f64,
-            zip_code: &'a str,
-            address: &'a str,
-            country: &'a str, 
-            state: &'a str,
-            first_name: &'a str,
-            last_name: &'a str,
-            province: &'a str,
-            comment: &'a str,
-            order: &'a OrderSlice<'a>
-        }
-
-        struct CustomerRc {
-            key: Rc<i32>,
-            age: Rc<i32>,
-            num_purchase: Rc<i32>,
-            total_purchase: Rc<f64>,
-            duration_spent: Rc<f64>, 
-            duration_since: Rc<f64>,
-            zip_code: Rc<String>,
-            address: Rc<String>,
-            country: Rc<String>,
-            state: Rc<String>,
-            first_name: Rc<String>,
-            last_name: Rc<String>,
-            province: Rc<String>,
-            comment: Rc<String>, 
-            order: Rc<OrderRc>
-        }
-    \end{lstlisting}
-    \caption{Representation of Customer object in Rust.}
-    \label{fig:Sampling}
-\end{figure}
-
-\clearpage
-
-\begin{figure}[htb]
-    \begin{lstlisting}
-        struct OrderOwned {
-            order_id: i32,
-            num_items: i32, 
-            payment: f64,
-            order_time: f64,
-            title: String,
-            comment: String
-        }
-
-        struct OrderBorrowed<'a> {
-            order_id: &'a i32,
-            num_items: &'a i32, 
-            payment: &'a f64,
-            order_time: &'a f64,
-            title: &'a String,
-            comment: &'a String
-        }
-
-        struct OrderRc {
-            order_id: Rc<i32>,
-            num_items: Rc<i32>, 
-            payment: Rc<f64>,
-            order_time: Rc<f64>,
-            title: Rc<String>,
-            comment: Rc<String>
-        }
-    \end{lstlisting}
-    \caption{Representation of Customer object in Rust.}
-    \label{fig:Sampling}
-\end{figure}

### 2020-04-17 thesis_template/3_Body/model/merge_sort_experiment.tex
change
documented concept

@@
-\subsection{Description}
+\subsection{Concept}
 This experiment is to assess importance of careful memory management in multithreading of Rust. 
@@
 To assess runtime overhead of algorithm with Arc, We implement merge-sort algorithm in two different ways. 
-One is sharing source vector with Arc. The other is passing slice of source vector to child thread.
+One is sharing source vector with Arc. The other is passing reference of source vector to child thread.
 

### 2020-04-19 thesis_template/3_Body/chapter/concept.tex
documented concept

@@
 
-\subsection{Algorithm in Big Data}
+\subsection{Tree-aggregate}
 \label{sec:history}
-Finally, we implement some of algorithm common in Big Data processing: Tree-aggregate and K-Nearest-Neighbors (KNN).
+Finally, we implement some of algorithm common in Big Data processing. One of them is tree-aggregate.
 
 Tree-aggregate is a communication patten heavily used for Machine Learning algorithm in Spark (MLlib). 
+The topology of aggregation patterns in Apache Spark are shown in Figure~\ref{fig:aggregationk_patttern}. 
 In the traditional aggregation function in Spark, results of aggregation in all executor clusters are sent to the driver. 
@@
 
-KNN is a traditional Machine Learning algorithm which classify targets into categories. 
-Through experiments with these algorithm, we aim to find algorithm with understandability and efficiency. 
+Spark generates intermediate objects from RDDs. In Tree-aggregation, aggregated HashMap like data structure is created in each thread or node. 
+When it aggregates objects in RDD, copy of objects in source vector should be performed to construct intermediate aggregated data structure.
+In another way, one can use reference to the objects to perform aggregation instead of copying the values themselves.
+In Rust, we can clone or get Arc (Rc if in single thread) of objects to implement these operations.
+
+Since Tree-aggregation algorithm generates and deletes a lot of intermediate data structures, 
+how the data structures are constructed and how they are deallocated is important concern in memory management in this algorithm.
+In our experiment, tree-aggregation algorithms are examined in multi-threading. The detail is described in section 3.2.
+
+\begin{figure}[htb]
+    \begin{minipage}[t]{0.5\linewidth}\centering
+        \includegraphics[width=5cm]{normal_agg.eps}
+        \medskip
+        \centerline{(a)}
+        \end{minipage}\hfill
+        \begin{minipage}[t]{0.5\linewidth}\centering
+        \includegraphics[width=7cm]{tree_agg.eps} 
+        \medskip
+        \centerline{(b)}
+    \end{minipage}\hfill
+    \caption{Representation of aggregation strategies in Apache Spark: (a) Traditional Aggregation, (b) Tree Aggregation}
+    \label{fig:aggregationk_patttern}
+\end{figure}
+
+\subsection{K-Nearest-Neighbors}
+\label{sec:history}
+The other algorithm common in Big Data processing is K-nearest-neighbors (KNN). KNN is a traditional Machine Learning algorithm which classify targets into categories. 
+In training KNN, it simply stores all available training data without calculation. At prediction phase, targets are given and similarity measures are calculated. 
+Based on these similarities, the algorithm selects \(K\) (user-defined number) training observations similar to the each target. 
+Then, it checks corresponding categories of the \(K\) observations to determine predicted category.
+
+In brute force algorithm, KNN calculates similarity measures for all combinations among training and testing observations. 
+If training data has \(N\) observations and test data has \(M\) observations, KNN needs to calculate \(N \times M\) similarity measures. 
+Sort or binary heap can be used to select the \(K\) most similar training observations.
+
+In our experiment, KNN algorithms performs document classification and implemented in multithread. 
+There are three phases in our algorithm: preprocessing, query, and combine phase. 
+In preprocessing phase, the algorithm calculates Term-frequencies (Tfs) to generate numeric feature vectors and matrices. 
+In query phase, similarity measures are calculated and \(K\) nearest neighbors are selected. 
+For similarity measure, our choice is cosine similarity(~\ref{eq:cosine}). 
+In combine phase, results of query phase are gathered and combined from each threads.
+
+\begin{equation} \label{eq:cosine}
+    Cos(\vec{x}, \vec{t})
+     = \frac{\sum_{i=0}^{n} (x_i t_i)}{\sqrt{\sum_{i=0}^{n} x_i^2}\sqrt{\sum_{i=0}^{n} t_i^2}}
+\end{equation}
+
+Even though preprocessing phase is not specific process for KNN algorithm, 
+it is common in algorithms used in Natural Language Processing. Therefore, better memory management strategy should be applied in this preprocessing phase.
+This preprocessing generates many intermediate data structures and copies of String elements are used in these data structure again and again. 
+We can again either clone or get Arc of String.
+
+Our KNN algorithms are implemented with batch processing. In query phase, we control batch size to examine how size of objects allocated simultaneously in memory.
+The detail implementation is explained in section3.2.
 \clearpage

### 2020-04-21 thesis_template/3_Body/chapter/concept.tex
documented different variable and drop reference

@@
 The detail implementation is explained in section3.2.
+
+\subsection{Complex Objects}
+\label{sec:history}
+To conduct experiments for above concepts, we use the 4 types of complex object: CustomerOwned, CustomerBorrowed, CustomerSlice, and CustomerRc. 
+These object contains other type of object: OrderOwned, OrderBorrowed, OrderSlice, and OrderRc.
+The representation of these objects are shown in Figure~\ref{fig:customer} and Figure~\ref{fig:order}. 
+Three Customer objects have 15 fields: 3 fields for i32, 3 fields for f64, 8 fields for String, and 1 field for Order object.
+All of fields of CustomerOwned and OrderOwned are owned by the object. On the other hand, fields of CustomerBorrowed, CustomerSlice, OrderBorrowed, and OrderSlice are borrowed. 
+Reference of slice of values are used as the fields and owner of actual values are stored differently in source Vec. 
+CustomerRc acquires Rc of values used for its fields from the source Vec.
+
+\begin{figure}[htb]
+    \begin{minipage}[t]{0.2\linewidth}\centering
+        \begin{lstlisting}
+            struct CustomerOwned {
+                key: i32,
+                age: i32,
+                num_purchase: i32,
+                total_purchase: f64,
+                duration_spent: f64, 
+                duration_since: f64,
+                zip_code: String,
+                address: String,
+                country: String,
+                state: String,
+                first_name: String,
+                last_name: String,
+                province: String,
+                comment: String, 
+                order: OrderOwned
+            }
+        \end{lstlisting}
+      \medskip
+      \centerline{(a)}
+    \end{minipage}\hfill
+    \begin{minipage}[t]{0.6\linewidth}\centering
+        \begin{lstlisting}
+            struct CustomerBorrowed<'a> {
+                key: &'a i32,
+                age: &'a i32,
+                num_purchase: &'a i32,
+                total_purchase: &'a f64,
+                duration_spent: &'a f64, 
+                duration_since: &'a f64,
+                zip_code: &'a String,
+                address: &'a String,
+                country: &'a String,
+                state: &'a String,
+                first_name: &'a String,
+                last_name: &'a String,
+                province: &'a String,
+                comment: &'a String, 
+                order: &'a OrderBorrowed<'a>
+            }
+        \end{lstlisting}
+      \medskip
+      \centerline{(b)}
+    \end{minipage}
+    \begin{minipage}[t]{0.2\linewidth}\centering
+        \begin{lstlisting}
+            struct CustomerSlice<'a> {
+                key: &'a i32,
+                age: &'a i32,
+                num_purchase: &'a i32,
+                total_purchase: &'a f64,
+                duration_spent: &'a f64, 
+                duration_since: &'a f64,
+                zip_code: &'a str,
+                address: &'a str,
+                country: &'a str, 
+                state: &'a str,
+                first_name: &'a str,
+                last_name: &'a str,
+                province: &'a str,
+                comment: &'a str,
+                order: &'a OrderSlice<'a>
+            }
+        \end{lstlisting}
+      \medskip
+      \centerline{(c)}
+    \end{minipage}\hfill
+    \begin{minipage}[t]{0.6\linewidth}\centering
+        \begin{lstlisting}
+            struct CustomerRc {
+                key: Rc<i32>,
+                age: Rc<i32>,
+                num_purchase: Rc<i32>,
+                total_purchase: Rc<f64>,
+                duration_spent: Rc<f64>,
+                duration_since: Rc<f64>,
+                zip_code: Rc<String>,
+                address: Rc<String>,
+                country: Rc<String>,
+                state: Rc<String>,
+                first_name: Rc<String>,
+                last_name: Rc<String>,
+                province: Rc<String>,
+                comment: Rc<String>,
+                order: Rc<OrderRc>
+            }
+        \end{lstlisting}
+      \medskip
+      \centerline{(c)}
+    \end{minipage}\hfill
+    \caption{Representation of Customer objects Whose fields are different variable type: (a) CustomerOwned struct whose fields are all owned 
+    (b) CustomerBorrowed struct whose fields are borrowed with reference (c) CustomerSlice struct whose fields are borrowed with slice for sequence value, otherwise reference}
+    \label{fig:customer}
+ \end{figure}
+
+ \begin{figure}[htb]
+    \begin{minipage}[t]{0.2\linewidth}\centering
+        \begin{lstlisting}
+            struct OrderOwned {
+                order_id: i32,
+                num_items: i32, 
+                payment: f64,
+                order_time: f64,
+                title: String,
+                comment: String
+            } 
+        \end{lstlisting}
+      \medskip
+      \centerline{(a)}
+    \end{minipage}\hfill
+    \begin{minipage}[t]{0.6\linewidth}\centering
+        \begin{lstlisting}
+            struct OrderBorrowed<'a> {
+                order_id: &'a i32,
+                num_items: &'a i32, 
+                payment: &'a f64,
+                order_time: &'a f64,
+                title: &'a String,
+                comment: &'a String
+            }
+        \end{lstlisting}
+      \medskip
+      \centerline{(b)}
+    \end{minipage}
+    \begin{minipage}[t]{0.2\linewidth}\centering
+        \begin{lstlisting}
+            struct OrderSlice<'a> {
+                order_id: &'a i32,
+                num_items: &'a i32, 
+                payment: &'a f64,
+                order_time: &'a f64,
+                title: &'a str,
+                comment: &'a str
+            }
+        \end{lstlisting}
+      \medskip
+      \centerline{(c)}
+    \end{minipage}\hfill
+    \begin{minipage}[t]{0.6\linewidth}\centering
+        \begin{lstlisting}
+            struct OrderRc {
+                order_id: Rc<i32>,
+                num_items: Rc<i32>,
+                payment: Rc<f64>,
+                order_time: Rc<f64>,
+                title: Rc<String>,
+                comment: Rc<String>
+            }
+        \end{lstlisting}
+      \medskip
+      \centerline{(c)}
+    \end{minipage}\hfill
+    \caption{Representation of Order objects Whose fields are different variable type: (a) OrderOwned struct whose fields are all owned 
+    (b) OrderBorrowed struct whose fields are borrowed with reference (c) OrderSlice struct whose fields are borrowed with slice for sequence value, otherwise reference}
+    \label{fig:order}
+ \end{figure}
+
+ \subsection{Wikipedia Data Sets}
+ \label{sec:history}
+ Wikipedia page data sets are used to perform document classification with KNN. 
+ \(10^5\) pages are used for training data set, and 18724 pages are used for target.
+
+ \subsection{Experimental Details}
+ Our experiments are run on three types of VM instances on Google Cloud Platform: 
+ n1-standard-1 which has 1 vCPU, 3.75 GB RAM, and 10 GB Standard persistent disk, 
+ n1-standard-4 which has 2 vCPU, 15 GB RAM, and 10 GB Standard persistent disk, 
+ n1-standard-4 which has 2 vCPU, 15 GB RAM, and 10 GB Standard persistent disk,  
+ All of the experiments described are performed 5 times. 
+ In this thesis, we present the average of 5 separate runs for each experiment.
 \clearpage

### 2020-04-21 thesis_template/3_Body/model/access_own_reference_slice.tex
documented different variable and drop reference

@@
-\subsection{Concept}
-This experiment is conducted to understand two questions. One is how different pointer types have impact to runtime performance.
+This experiment is conducted to understand two questions. One is how different variable types have impact to runtime performance.
 The other is how initialization of Vec size has impact to runtime performance. 
-In this experiment, we focus on owner, reference, and additionally slice as a pointer to sequence values. 
-The memory representations of these pointer types are shown in figure.
+In this experiment, we focus on owner, reference, and slice as a variable of sequence values. 
+Since these variables have different memory representation, there might be differences among time for access to actual values of each variables.
 
-The owner has a pointer pointing to the memory address of sequence values, length of the values, and capacity allocated to store additional values. 
-The reference is a pointer that points to the owner. The slice is a pointer that points to memory address of sequence values and has value such as length of 
-sequence values stored in the memory. Since they have different memory representation, an assumption is that it takes different time to access to the contents of the memory among these pointer types.
+To evaluate this assumption, we use the three types of complex object: CustomerOwned, CustomerBorrowed and CustomerSlice. 
+At first, we generate source Vecs for all fields, Vecs which contain all elements used for corresponding fields of objects.
+For example, all of i32 elements used for key field in 1 million Customer object are stored in Vec$<$i32$>$ with 1 million i32 elements. 
+Later, these i32 elements are moved to be owned or borrowed by by the object's fields.
 
-To evaluate this assumption, we use the three type of complex object.
+Next, 1.5, 1.8, 2.5, 2.8, 3.5, and 3.8 million of Customer objects are created and stored in Vec. 
+When a Customer Vec is created, whether size of Vec is initialized is controlled. 
+Finally, serialization of Customer object is performed as an operation forcing program to access all of fields in the object.
+This serialization is performed each Customer objects in the Vec. We measure total runtime to serialize all of Customer objects 
+stored in Vec.
+
+\subsection{Result}
+\label{sec:history}
+The result is shown in Figure~\ref{fig:rustaccessinit} and Figure~\ref{fig:rustaccessnoinit}.
+Figure~\ref{fig:rustaccessinit} is comparison of the runtime performance among different Customer object types with Vec size initialization.
+Figure~\ref{fig:rustaccessnoinit} is comparison in the same set of experiment except Vec size is not initialized. 
+The blue, yellow, and green chats represent runtime of access to fields of CustomerOwned, CustomerBorrowed, and CustomerSlice objects respectively.
+
+No matter Vec size initialized or not, differences of runtime for accessing objects among different object types are not remarkable. 
+The percent increase in runtime of accessing to fields of from 1.5 to 3.8 million CustomerOwned objects is 121\% if the Vec is initialized, 554\% if the Vec is not initialized.
+
+Considering the differences of percent increase of runtime whether the Vec is initialized or not, 
+Figure\ref{fig:init_vs_noinit} the comparison of runtime access to fields of CustomerOwned object with and without Vec Initialization.
+For 3.8 million of objects, the difference of runtime to access to the objects is 38745 secounds; program without Vec initialization is 60\% slower than one with the initialization.
 
@@
     \caption{Runtime of Access to Fields of Complex Object with Initialization vs without Initialization}
-    \label{fig:rustaccessnoinit}
+    \label{fig:init_vs_noinit}
 \end{figure}
 
-The representation of these objects are shown in Figure~\ref{fig:customer} and Figure~\ref{fig:order}. 
-\begin{figure}[htb]
-    \begin{minipage}[t]{0.2\linewidth}\centering
-        \begin{lstlisting}
-            struct CustomerOwned {
-                key: i32,
-                age: i32,
-                num_purchase: i32,
-                total_purchase: f64,
-                duration_spent: f64, 
-                duration_since: f64,
-                zip_code: String,
-                address: String,
-                country: String,
-                state: String,
-                first_name: String,
-                last_name: String,
-                province: String,
-                comment: String, 
-                order: OrderOwned
-            }
-        \end{lstlisting}
-      \medskip
-      \centerline{(a)}
-    \end{minipage}\hfill
-    \begin{minipage}[t]{0.6\linewidth}\centering
-        \begin{lstlisting}
-            struct CustomerBorrowed<'a> {
-                key: &'a i32,
-                age: &'a i32,
-                num_purchase: &'a i32,
-                total_purchase: &'a f64,
-                duration_spent: &'a f64, 
-                duration_since: &'a f64,
-                zip_code: &'a String,
-                address: &'a String,
-                country: &'a String,
-                state: &'a String,
-                first_name: &'a String,
-                last_name: &'a String,
-                province: &'a String,
-                comment: &'a String, 
-                order: &'a OrderBorrowed<'a>
-            }
-        \end{lstlisting}
-      \medskip
-      \centerline{(b)}
-    \end{minipage}
-    \begin{minipage}[t]{0.2\linewidth}\centering
-        \begin{lstlisting}
-            struct CustomerSlice<'a> {
-                key: &'a i32,
-                age: &'a i32,
-                num_purchase: &'a i32,
-                total_purchase: &'a f64,
-                duration_spent: &'a f64, 
-                duration_since: &'a f64,
-                zip_code: &'a str,
-                address: &'a str,
-                country: &'a str, 
-                state: &'a str,
-                first_name: &'a str,
-                last_name: &'a str,
-                province: &'a str,
-                comment: &'a str,
-                order: &'a OrderSlice<'a>
-            }
-        \end{lstlisting}
-      \medskip
-      \centerline{(c)}
-    \end{minipage}\hfill
-    \caption{Representation of Customer objects Whose fields are different variable type: (a) CustomerOwned struct whose fields are all owned 
-    (b) CustomerBorrowed struct whose fields are borrowed with reference (c) CustomerSlice struct whose fields are borrowed with slice for sequence value, otherwise reference}
-    \label{fig:customer}
- \end{figure}
+\subsection{Discussion}
+\label{sec:history}
+Difference of variable types does not have huge impact to runtime of accessing to actual value.
+Even thought owner, reference , and slice have different memory representations, the access time to its value is 
+close to each other. As shown in Figure~\ref{fig:own_ref_slice}, the representations of owner and slice are almost identical except slice does not have capacity for values.
+Reference is pointer pointing to owner, so it has an additional step to access actual value. 
+However, the result shows this additional step does not have huge impact for runtime to access memory region of the value.
 
- \begin{figure}[htb]
-    \begin{minipage}[t]{0.2\linewidth}\centering
-        \begin{lstlisting}
-            struct OrderOwned {
-                order_id: i32,
-                num_items: i32, 
-                payment: f64,
-                order_time: f64,
-                title: String,
-                comment: String
-            } 
-        \end{lstlisting}
-      \medskip
-      \centerline{(a)}
-    \end{minipage}\hfill
-    \begin{minipage}[t]{0.6\linewidth}\centering
-        \begin{lstlisting}
-            struct OrderBorrowed<'a> {
-                order_id: &'a i32,
-                num_items: &'a i32, 
-                payment: &'a f64,
-                order_time: &'a f64,
-                title: &'a String,
-                comment: &'a String
-            }
-        \end{lstlisting}
-      \medskip
-      \centerline{(b)}
-    \end{minipage}
-    \begin{minipage}[t]{0.2\linewidth}\centering
-        \begin{lstlisting}
-            struct OrderSlice<'a> {
-                order_id: &'a i32,
-                num_items: &'a i32, 
-                payment: &'a f64,
-                order_time: &'a f64,
-                title: &'a str,
-                comment: &'a str
-            }
-        \end{lstlisting}
-      \medskip
-      \centerline{(c)}
-    \end{minipage}\hfill
-    \caption{Representation of Order objects Whose fields are different variable type: (a) OrderOwned struct whose fields are all owned 
-    (b) OrderBorrowed struct whose fields are borrowed with reference (c) OrderSlice struct whose fields are borrowed with slice for sequence value, otherwise reference}
-    \label{fig:order}
- \end{figure}
+Whether initializing Vec size results in disparity of runtime performance to access objects' fields. 
+This is because when Vec uninitialized, the elements of Vec are allocated across different virtual memory pages.

### 2020-04-21 thesis_template/3_Body/model/drop_ref_rc.tex
documented different variable and drop reference

--- 2020-03-24 thesis_template/3_Body/model/drop_ref_rc.tex
@@
-\subsection{Concept}
-The goal of this experiment is to assess efficiency of different reference strategies in Rust, borrowing and reference counting.
+% In Rust programming, a reference is a pointer to reduce unnecessary movement of ownership. 
+% One use case is where we pass reference to values to arguments of function. 
+% If we pass owner to function, the owner is moved and the corresponding value is deallocated when the call of function ends. 
+% To avoid this, the owner should always be returned. This may be an encumbrance while complex software system development. 
+% By using reference, we do not have to worry about returning it, because reference is an additional pointer to an owned value. 
+% Reference can be used for operation in the same way of owner, but also be moved without deallocation of value by keeping its owner live.
 
-By levaraging reference counting, a value can be shared like what borrowing plays the role in Rust programming. 
-The difference is that reference counting checks number of reference pointing to the actual data and makes sure the data is not deleted 
-until all the references are dereferenced. Using reference counting is sometimes preferable approach for developers, 
-we do not have care about lifetime which is usually troublesome when we use borrowing approach many times in our code. 
-However, the possible problem regarding to reference counting is the cost for tracking the number of references. 
-Having this assumption, this experiment will show difference of behavior among reference countinig and borrowing.
+% Reference is useful to avoid movement of ownership. However, one needs to track its lifetime and explicitly includes it in code, 
+% because Rust compiler cannot infer it. This can be another encumbrance. We can instead acquire multiple owners to single value by using Reference Counting (Rc). 
+% By leveraging Rc, a value can be shared like what borrowing plays the role in Rust programming. 
+% The difference is that Rc checks number of owner pointing to the actual data and makes sure the data is not deleted 
+% until all the owners are dereferenced. Using Rc is sometimes preferable approach for developers especially when lifetime planning is extremely difficult.
+% However, the possible problem regarding to Rc is the cost for tracking the number of references. 
+% Having this assumption, this experiment will show difference of behavior among Rc and simple reference.
 
-In this experiment, CustomerBorrowed and CustomerRc in figure are used to see difference of dropping time among borrowing and reference counting. 
-In the CustomerRc and OrderRc struct, all fields take reference counting (Rc$<$T$>$). Similaly to the experiment in the last section, 
-vectors of CustomerRc and CustomerBorrowed are created and droped the elements one by one.
-
-The result shows significant difference of dropping time among the two objects; deletion of CustomerRc is much slower than CustomerBorrowed. 
-This is because reference counters which are feilds of CustomerRc have to check the number of reference pointing to the actual content and decide 
-deallocate the memory or not. However, memory management and lifetime strategy of borrowing is already determined at compile time.
-
-In this experiment, an assessment is conducted to valify whether there is difference between behavior of borrowing and reference counting. 
-These two methods can be used in similar situation. Especially, when we want reference to an original variable and keep the original variable until all of references are dereferenced, 
-we can have reference with both storategies, borrowing and reference counting. One advantage of using reference counting is that we do not have to pay attention to lifetime.
-However, the assumption here is that use of reference counting might be computationally expenesive than borrowing, because reference counting has to track the number of reference pointing to the value.
-Considered this assumption, we assess difference of time for dropping reference using borrowing and reference counting strategies.
-
-Similally to the last section, we implement struct whose fields are borrowing reference and reference counting and measure the time to drop the struct.
+In this experiment, CustomerBorrowed and CustomerRc are used to see difference of dropping time among reference and Rc. 
+In the CustomerRc and OrderRc struct, all fields take Rc (Rc$<$T$>$). Similarly to the experiment in the last section, 
+sets of integer, float, and String vector are created and their elements are borrowed or reference counted to create CustomerBorrowed or CustomerRc objects.
+The dropping of objects deletes references or Rcs used for fields of the objects. However, it does not deallocate values to which they are pointing. 
+Therefore, the evaluated runtime of dropping objects only consists of dropping time of reference or Rc, but deallocation time.
+We generated 1, 1.5, 2, 2.5, 3, 3.5 million of CustomerBorrowed and CustomerRc objects and performed drop one by one.
 
 \subsection{Result}
-The result shows the time to drop borrowing reference is significatly faster than reference counting.
-This says that we should use borrwoing storategies whenever high performance computation is critical.
+Figure\ref{fig:rc_ref} shows comparison of runtime dropping CustomerBorrowed and CustomerRc objects. 
+The result shows significant difference of dropping time among the two objects; deletion of CustomerRc is much slower than CustomerBorrowed. 
+The runtime of dropping CustomerBorrowed is about 60 times faster than dropping CustomerRc.
+
 \begin{figure}[htb!]
     \includegraphics[width=15cm]{rust_droptime_borring_rc.eps}
-    \caption{Runtime for Droping to fields of Customer Object}
-    \label{fig:Sampling}
+    \caption{Runtime for dropping Customer Object}
+    \label{fig:rc_ref}
 \end{figure}
@@
 \subsection{Discussion}
+In this experiment, an assessment is conducted to verify whether there is difference between behavior of reference and Rc.
+The reason why dropping Rc is much slower than dropping reference it that Rc requires runtime overhead to check some states of the variable, 
+but when to drop reference is already determined at compile time. When dropping Rc, Rc has to check the number of variable pointing to the actual content and decide 
+deallocate the memory or not. However, memory management and lifetime strategy of reference is already determined at compile time.
+This determination of memory management strategy at compile increases runtime performance of dropping complex object constructed with reference type variable.
+This may say that we should use reference whenever high performance computation is critical.
+
+However, dealing with reference is sometimes cumbersome. Tracking lifetime of reference can be done easily in simple situation. 
+But, if we have complex objects constructed with fields of reference, the lifetime tracking become extremely difficult. 
+For example, constructing nested objects with reference fields require a developer to plan memory management with many lifetime symbols. 
+Using reference counting eliminates developer's responsibility to specify lifetime of variables. 
+This may ease and speed up development process, and increase understandability of codes.
+
+Even though we have stack allocated values, such as i32 and f64, in Rc in our experiment, 
+one should avoid wrapping stack allocated values in Rc. Wrapping value in Rc allocates heap memory so that allocating Rc$<$i32$>$ or Rc$<$f64$>$ unnecessarily use space of 
+heap. Additionally, stack allocated values are usually easy to be copied. Therefore, developer does not have to even use reference; one can just copy the value. 
+Copying value in Rust is to copy the original value and to assign the copy to new owner variable.

### 2020-04-22 thesis_template/2_RelatedWork/model/hadoop_to_spark.tex
documented llvm

--- 2020-04-06 thesis_template/2_RelatedWork/model/spark.tex
@@
-\section{Hadoop MapReduce to Spark}
-\label{sec:history}
 In several Big Data mining tools that have been developed, the most notable ones are MapReduce and Spark. MapReduce is a cluster computing framework 
@@
 These caching strategy reduces disk I/O overhead, but CPU overhead, such as parsing text to objects.
-
-\section{Apache Spark}
-\label{sec:history}
-\subsection{Resilient Distributed Datasets}
-Major methods in Spark are Resilient Distributed Datasets (RDDs), a data structure that abstracts distributed memory across different clusters. 
-The immutable coarse-grained transformation, spark-scheduler with lazy-evaluation, and memory management with cacheing achieve computation with fault-tolerance, 
-fast execution, and moderate control on memory efficiency \cite{DBLP:conf/nsdi/ZahariaCDDMMFSS12}.
-
-A RDD is essentially a multi-layer Java data structure. A top RDD object references Java array, which intern, references a set of tuple objects. 
-The coarse-grained transformations and immutability requires a RDD to be deep-copied to produce a new RDD, but efficiently offers fault tolerance. 
-The lost partitions of a RDD can be recomputed in parallel on different nodes rather than rolling back the whole program.
-
-Spark-pipeline consists of sequence of transformations and actions over RDDs. A transformation produces a new RDD from a set of existing RDD. 
-An action is method that computes statistics from an RDD. Due to lazy-evaluation nature, transformations do not materialize the newly created RDD. 
-Instead, RDD Lineages are created. Lineage is a graph among parent and child RDDs which represents logical execution plan. 
-This enhance fault-tolerance and improve ability to optimize execution plan.
-
-RDDs can be cached in memory for faster access by persist method. Developers can specify a storage level for a persisted RDD, in memory with serialized or deserialized, or on disk. 
-Other than persisted RDD, Spark generates a lot of intermediate RDDs during execution. Since RDD is a Java object, they are managed by Garbage Collection (GC) in the JVM. 
-However, persisted RDDs are never collected by GC. This GC might cause significant deterioration of performance of Spark, because GC shows heavy overhead when there are a number of objects.
-
-\subsection{Memory Management in Spark}
-Spark framework allocates multiple executors, JVMs, that run sequence of transformations and actions. As we describe the previous section, data in Spark is mainly stored as Java objects in memory, 
-so that they are allocated on JVM heap and managed by JVM Garbage Collection.
-The data may form three types \cite{DBLP:journals/pvldb/XuGDWW19}: Cached data, Shuffled data, and Operator-generated data.
-
-Spark can cache data in memory to reduce disk I/O. This Cached data usually long-lived Java objects and span multiple stages in Spark-pipeline. 
-Spark allocates a logical storage space to store the cached data as shown in Figure. After aggregation, Spark generates Shuffled data. Shuffled data is usually long-lived, 
-because it need to be kept in memory until the task ends. Spark allocates execution space to store Shuffled data.
-The storage space and execution space spans 60 \% of JVM heap space in default.
-Operator-generated data is data generated by user-defined operations.
-Since Operator-generated data may or may not be used,
-after the operation finish, the data object can be both short-lived or long-lived objects. These are stored in user space allocated on default 40 \% of JVM heap.
-
-All data of these types on JVM heap is managed by JVM GC. GC check references graph of objects, mark whether the objects are used and deallocate memory space occupied by unused objects. 
-There are three popular GCs: Parallel, CMS and G1. All of these method track generation of object based on the region of memory. 
-The Java logical heap structure is shown in Figure~\ref{fig:javaheap}.
-As the figure shows, Java logical heap can be separated into three main parts where store objects for each corresponding generation:
-permanent generation, young generation, and old generation. The region for permanent generation stores metadata required by JVM to describe 
-class and method used in application which will be permanently lived on the region of memory. The overview of Java GC is shown in Figure~\ref{fig:javagc}. 
-The outer box represents region for particular generation. The inner box and the number represents object and its age in GC.
-
-The region for young generation mainly consists of two parts: Eden and Survivor space. 
-First, Java objects are created in Eden space and promoted to Survivor space when survive from GC. 
-After objects survive several GCs in Survivor space, they are finally promoted to old generation.
-
-In region of old generation, JVM lunches multi-thread to perform GC. GC with multi-threading suffers from Stop-The-World (STW) pauses; 
-GC may suspend application threads while performing object marking and deallocation. 
-Different GC algorithms try to solve this problem with trade-off between GC frequency and memory utilization.
-
-Because of the problem of STW and copying objects to different physical memory pages , JVM GC cause huge overhead when number of objects is large. 
-Therefore, GC become severe issue in Big Data processing where might produce significant number of object.
-
-\begin{figure}[htb]
-    \includegraphics[width=15cm]{java_heap.eps}
-    \caption{Java Heap Structure}
-    \label{fig:javaheap}
-\end{figure}
-
-\begin{figure}[htb]
-    \includegraphics[width=15cm]{java_gc.eps}
-    \caption{Java Garbage Collection}
-    \label{fig:javagc}
-\end{figure}
-
-\subsection{Garbage Collection Tuning}
-There are many different ways that one can improve the performance of GC in Java. One of these is for example avoiding pointer-based data structures, such as HashMap and LinkedList. 
-These objects have a "wrapper" object for each entry so that number of object tends to be larger than when when an array is used.
-
-Caching serialized object in memory also reduce number of object and memory usage since the set of objects become a byte or binary array. 
-Spark SQL applications use DataFrames\cite{DBLP:conf/sigmod/ArmbrustXLHLBMK15}, 
-whose intermediate data are managed by an optimized memory manager named Tungsten.
-Tungsten stores the intermediate data in a serialized binary form and performs aggregation functions directly on he serialized objects.
-Therefore, the number of Java objects in memory is reduced and it reduces the DC frequency and object marking/sweeping.
-
-In addition, developers can allocate data off-heap of JVM to avoid tracking by GC. 
-Facade\cite{DBLP:conf/asplos/NguyenWBFHX15} proposed a compiler and runtime system to bound the number of in-memory data objects, through storing data in an off-heap region and 
-manipulating the data with control interfaces.
-
-Although these memory management solution for GC help developer improve performance of Spark applications, 
-the effort to discover the best GC tuning afflicts developers.
-
-\section{Application to System Language}
-\label{sec:history}
-Considered overhead produced by Memory Management in JVM, use of system language for development of Big Data tool can be one of solutions rather than application language, such as Java and Scala. 
-System languages, such as C and C++, are languages that give developer total control over the hardware and de/allocation of memory without GC. 
-These features enable program written in system languages to optimized performance taking full advantage of hardware.
-
-To take example, one can build Big Data tool with C++. C++ is one of the most popular system languages which has Object-oriented features. 
-C++ has functions which provide control over memory to developers. In another word, it is responsibility for one to manage memory properly and safely. 
-The functions, malloc() and free(), take roll for memory allocation and deallocation in respectively. The manual memory de/allocation may cause several problems and require developers 
-attention to the problems with significant effort for debugging and testing. Here, we explain two of the most common problems regarding to memory management in existing system languages.
-
-Dangling pointer or reference is a pointer or reference pointing to object that no longer exists. The situation of dangling pointer happens 
-because of deallocation of memory without modification of value of the pointer. 
-If the memory region is reallocated for other object and the dangling pointer tries to access the original object, the unpredictable behavior may result.
-
-Memory leak occurs when memory is allocated and no longer referenced so that the object in the memory location cannot be reached and released.
-This is result of dereferencing object without deallocation. Memory leak consumes more memory than necessary by making unreachable location.
-
-Some solutions are established to address these problems. Actually GC is a high-level solution that guarantees memory safety. 
-C++ has a different solution called Resource Acquisition is Initialization (RAII). In RAII, objects can live within the scope where they are created. 
-The memory is released when the object goes out of scope. This solution is more predictable and deterministic than GC. 
-However, it is problematic When we need the object out of the scope, returning a value from a function. 
-There are several ways to go around this problems, such as smart pointers, copy constructors, and move semantics. 
-Nevertheless, these non-orthogonal concepts makes code in disorganize and leads to error prone implementation.
-
-\section{Rust Memory Management}
-\label{sec:history}
-Rust is a system programming language which provides memory safety without runtime checking like GC and necessity of explicit memory de/allocation. 
-To ensure memory safety, Rust provides restrictive coding patterns and checks lifetime of value and memory safety at compile-time.
-The restrictive patterns also enables a developer to write fearless concurrent code that is free of data races.
-Main concepts of Memory Management in Rust are ownership, move, and borrowing.
-
-\subsection{Ownership}
-In ownership feature or Rust, each value has a variable called owner.
-This owner has information about the value, such as location in memory, length and capacity of the value. 
-For example, the object representation of Vec$<$i32$>$ is shown in Figure. This owner can live on the scope associated with its lifetime.
-When the owner is dropped, the value will be dropped too. This feature is similar to how RAII in C++ works. 
-However, acquisition of owner out of the scope where it was constructed is available in Rust with the concept of move.
-
-\subsection{Move}
-In Rust, for most types. operations like assigning a value to a variable, passing it to a function, or returning it from a function do not copy the value: they move it. 
-With move, a value can be transferred from one owner to another. The previous variable does not have ownership of the value; it is moved to a newly assigned variable. 
-To understand how this assignment implementation is unique from other programing languages, Python, C++, and Rust code example of assigning list or vector of strings are shown in Figure. 
-For example, a value is instantiated in a function. 
-When it is returned to a new variable, the ownership of value is moved to the new variable. In Rust, one do not have to explicitly deallocate memory, 
-because ownership of value is passed among variables across scope using move and eventually goes out of scope deallocating memory of the value.
-
-\subsection{Borrowing}
-Borrowing lets code use a value temporarily without affecting its ownership so that it reduces unnecessary movement of ownership. 
-One use case is when value is used in function and needed to be passed to the argument. If the argument takes ownership and the function does not return the value, 
-the ownership of value goes out of scope and the memory is deallocated. One can pass reference of the value to the argument instead of owner. 
-The reference goes out of scope, but ownership remains the same.

### 2020-04-22 thesis_template/2_RelatedWork/model/llvm.tex
documented llvm

@@
-LLVM (Low Level Virtual Machine) is an umbrella project which contains components of compilation of programming language.
+LLVM (Low Level Virtual Machine) \cite{DBLP:conf/cgo/LattnerA04} is an umbrella project which contains components of compilation of programming language.
 Existing compilers have tightly coupled functionalities so that it is not possible to embed them into other applications.
@@
 In structure of a compiler, there are three main components; frontend, optimizer, and backend. 
-In frontend, a developer designs the interface of source programming language in way where it can be optimized by optimizer. 
-Then, backend takes optimized code and produce the native machine code. LLVM has a component called LLVM Intermediate Representation (IR), 
+In frontend, a developer designs the interface of source programming language in a way where it can be optimized by optimizer. 
+Then, backend takes optimized code and produce the native machine code.
+
+This separation of functionalities gives reusability to parts of compiler. Establishing new programming language requires new front end, 
+but the existing optimizer and back end can be reused. This speeds up processes of developing new programming languages.
+
+The reusability of compiler leads to support multiple programming languages 
+so that broader set of programmers are involved in the development. 
+For open source project like Rust, This ends up larger community of potential contributors to the development.
+
+Since implementation of front end can be independent on optimizer and back end, 
+development of programming language becomes easy for person without skills required to implement optimizer and back end.
+This thrives new language developments.
+
+LLVM has a component called LLVM Intermediate Representation (IR), 
 which places itself across frontend to optimizer. IR is designed to host mid-level analyses and transformations that you find in optimizer section of a compiler.
@@
 IR is useful in terms of frontend. This is because developer of language frontend need to know only how the IR works and use the framework to develop a language.
+
+Because of emerging of LLVM, many new programming languages and compilers have been developed. Rust compiler is also developed based on LLVM.

### 2020-04-22 thesis_template/2_RelatedWork/model/application_to_system_language.tex

--- 2020-04-06 thesis_template/2_RelatedWork/model/spark.tex
@@
-\section{Hadoop MapReduce to Spark}
-\label{sec:history}
-In several Big Data mining tools that have been developed, the most notable ones are MapReduce and Spark. MapReduce is a cluster computing framework 
-which supports locality-aware scheduling, fault tolerance, and load balancing. Spark is designed to improve performance for iterative jobs keeping features of MapReduce.
-
-MapReduce provides a programming model where the user creates acyclic data flow graphs to pass input data through a set of operations. This 
-data flow programming model is useful for many of query applications. However, MapReduce framework struggles from two of main resent data mining jobs: iterative jobs and interactive analysis.
-
-Iterative job is especially common in Machine Learning Algorithm, such as learning a data model using Gradient Descent.
-In traditional MapReduce framework, each iteration can be expressed as single MapReduce job
-so that each job must reload the data from disk. This leads I/O overhead and deteriorates performance of iterative algorithms.
-
-Interactive analysis is also an inevitable task in modern data science. A data scientist wants tp perform exploratory analysis in interactive way. 
-Nevertheless, MapReduce is designed in the way more stable for ad-hoc query, so each analysis can be single MapReduce job. 
-To perform multiple analysis to explore dataset, the data needs to be written to and reload from disk many times.
-
-To overcome these limitations, Spark has been developed as a new cluster computing framework maintaining the innovative characteristics of MapReduce and improving 
-its iterative and interactive jobs with in-memory data structure.
-
-Some of the notable improvements are shown here\cite{DBLP:journals/pvldb/ShiQMJWRO15}.
-For aggregation operation, map output selectivity, which is the ration of the map output size to the job input size,
-can be significantly reduced by using Spark. Spark uses a map side combiner, hash-based aggregation which is more efficient than sort-based aggregation used in MapReduce. 
-For iterative operation, caching the input as Resilient Distributed Datasets (RDDs) can reduce CRU and disk I/O overheads for sequence iteration. 
-This RDD caching takes a significant role to improve iterative job, because it is more efficient than other low-level caching approaches such as OS buffer caches, and HDFS caching. 
-These caching strategy reduces disk I/O overhead, but CPU overhead, such as parsing text to objects.
-
-\section{Apache Spark}
-\label{sec:history}
-\subsection{Resilient Distributed Datasets}
-Major methods in Spark are Resilient Distributed Datasets (RDDs), a data structure that abstracts distributed memory across different clusters. 
-The immutable coarse-grained transformation, spark-scheduler with lazy-evaluation, and memory management with cacheing achieve computation with fault-tolerance, 
-fast execution, and moderate control on memory efficiency \cite{DBLP:conf/nsdi/ZahariaCDDMMFSS12}.
-
-A RDD is essentially a multi-layer Java data structure. A top RDD object references Java array, which intern, references a set of tuple objects. 
-The coarse-grained transformations and immutability requires a RDD to be deep-copied to produce a new RDD, but efficiently offers fault tolerance. 
-The lost partitions of a RDD can be recomputed in parallel on different nodes rather than rolling back the whole program.
-
-Spark-pipeline consists of sequence of transformations and actions over RDDs. A transformation produces a new RDD from a set of existing RDD. 
-An action is method that computes statistics from an RDD. Due to lazy-evaluation nature, transformations do not materialize the newly created RDD. 
-Instead, RDD Lineages are created. Lineage is a graph among parent and child RDDs which represents logical execution plan. 
-This enhance fault-tolerance and improve ability to optimize execution plan.
-
-RDDs can be cached in memory for faster access by persist method. Developers can specify a storage level for a persisted RDD, in memory with serialized or deserialized, or on disk. 
-Other than persisted RDD, Spark generates a lot of intermediate RDDs during execution. Since RDD is a Java object, they are managed by Garbage Collection (GC) in the JVM. 
-However, persisted RDDs are never collected by GC. This GC might cause significant deterioration of performance of Spark, because GC shows heavy overhead when there are a number of objects.
-
-\subsection{Memory Management in Spark}
-Spark framework allocates multiple executors, JVMs, that run sequence of transformations and actions. As we describe the previous section, data in Spark is mainly stored as Java objects in memory, 
-so that they are allocated on JVM heap and managed by JVM Garbage Collection.
-The data may form three types \cite{DBLP:journals/pvldb/XuGDWW19}: Cached data, Shuffled data, and Operator-generated data.
-
-Spark can cache data in memory to reduce disk I/O. This Cached data usually long-lived Java objects and span multiple stages in Spark-pipeline. 
-Spark allocates a logical storage space to store the cached data as shown in Figure. After aggregation, Spark generates Shuffled data. Shuffled data is usually long-lived, 
-because it need to be kept in memory until the task ends. Spark allocates execution space to store Shuffled data.
-The storage space and execution space spans 60 \% of JVM heap space in default.
-Operator-generated data is data generated by user-defined operations.
-Since Operator-generated data may or may not be used,
-after the operation finish, the data object can be both short-lived or long-lived objects. These are stored in user space allocated on default 40 \% of JVM heap.
-
-All data of these types on JVM heap is managed by JVM GC. GC check references graph of objects, mark whether the objects are used and deallocate memory space occupied by unused objects. 
-There are three popular GCs: Parallel, CMS and G1. All of these method track generation of object based on the region of memory. 
-The Java logical heap structure is shown in Figure~\ref{fig:javaheap}.
-As the figure shows, Java logical heap can be separated into three main parts where store objects for each corresponding generation:
-permanent generation, young generation, and old generation. The region for permanent generation stores metadata required by JVM to describe 
-class and method used in application which will be permanently lived on the region of memory. The overview of Java GC is shown in Figure~\ref{fig:javagc}. 
-The outer box represents region for particular generation. The inner box and the number represents object and its age in GC.
-
-The region for young generation mainly consists of two parts: Eden and Survivor space. 
-First, Java objects are created in Eden space and promoted to Survivor space when survive from GC. 
-After objects survive several GCs in Survivor space, they are finally promoted to old generation.
-
-In region of old generation, JVM lunches multi-thread to perform GC. GC with multi-threading suffers from Stop-The-World (STW) pauses; 
-GC may suspend application threads while performing object marking and deallocation. 
-Different GC algorithms try to solve this problem with trade-off between GC frequency and memory utilization.
-
-Because of the problem of STW and copying objects to different physical memory pages , JVM GC cause huge overhead when number of objects is large. 
-Therefore, GC become severe issue in Big Data processing where might produce significant number of object.
-
-\begin{figure}[htb]
-    \includegraphics[width=15cm]{java_heap.eps}
-    \caption{Java Heap Structure}
-    \label{fig:javaheap}
-\end{figure}
-
-\begin{figure}[htb]
-    \includegraphics[width=15cm]{java_gc.eps}
-    \caption{Java Garbage Collection}
-    \label{fig:javagc}
-\end{figure}
-
-\subsection{Garbage Collection Tuning}
-There are many different ways that one can improve the performance of GC in Java. One of these is for example avoiding pointer-based data structures, such as HashMap and LinkedList. 
-These objects have a "wrapper" object for each entry so that number of object tends to be larger than when when an array is used.
-
-Caching serialized object in memory also reduce number of object and memory usage since the set of objects become a byte or binary array. 
-Spark SQL applications use DataFrames\cite{DBLP:conf/sigmod/ArmbrustXLHLBMK15}, 
-whose intermediate data are managed by an optimized memory manager named Tungsten.
-Tungsten stores the intermediate data in a serialized binary form and performs aggregation functions directly on he serialized objects.
-Therefore, the number of Java objects in memory is reduced and it reduces the DC frequency and object marking/sweeping.
-
-In addition, developers can allocate data off-heap of JVM to avoid tracking by GC. 
-Facade\cite{DBLP:conf/asplos/NguyenWBFHX15} proposed a compiler and runtime system to bound the number of in-memory data objects, through storing data in an off-heap region and 
-manipulating the data with control interfaces.
-
-Although these memory management solution for GC help developer improve performance of Spark applications, 
-the effort to discover the best GC tuning afflicts developers.
-
-\section{Application to System Language}
-\label{sec:history}
 Considered overhead produced by Memory Management in JVM, use of system language for development of Big Data tool can be one of solutions rather than application language, such as Java and Scala. 
@@
 Nevertheless, these non-orthogonal concepts makes code in disorganize and leads to error prone implementation.
-
-\section{Rust Memory Management}
-\label{sec:history}
-Rust is a system programming language which provides memory safety without runtime checking like GC and necessity of explicit memory de/allocation. 
-To ensure memory safety, Rust provides restrictive coding patterns and checks lifetime of value and memory safety at compile-time.
-The restrictive patterns also enables a developer to write fearless concurrent code that is free of data races.
-Main concepts of Memory Management in Rust are ownership, move, and borrowing.
-
-\subsection{Ownership}
-In ownership feature or Rust, each value has a variable called owner.
-This owner has information about the value, such as location in memory, length and capacity of the value. 
-For example, the object representation of Vec$<$i32$>$ is shown in Figure. This owner can live on the scope associated with its lifetime.
-When the owner is dropped, the value will be dropped too. This feature is similar to how RAII in C++ works. 
-However, acquisition of owner out of the scope where it was constructed is available in Rust with the concept of move.
-
-\subsection{Move}
-In Rust, for most types. operations like assigning a value to a variable, passing it to a function, or returning it from a function do not copy the value: they move it. 
-With move, a value can be transferred from one owner to another. The previous variable does not have ownership of the value; it is moved to a newly assigned variable. 
-To understand how this assignment implementation is unique from other programing languages, Python, C++, and Rust code example of assigning list or vector of strings are shown in Figure. 
-For example, a value is instantiated in a function. 
-When it is returned to a new variable, the ownership of value is moved to the new variable. In Rust, one do not have to explicitly deallocate memory, 
-because ownership of value is passed among variables across scope using move and eventually goes out of scope deallocating memory of the value.
-
-\subsection{Borrowing}
-Borrowing lets code use a value temporarily without affecting its ownership so that it reduces unnecessary movement of ownership. 
-One use case is when value is used in function and needed to be passed to the argument. If the argument takes ownership and the function does not return the value, 
-the ownership of value goes out of scope and the memory is deallocated. One can pass reference of the value to the argument instead of owner. 
-The reference goes out of scope, but ownership remains the same.

### 2020-04-22 thesis_template/2_RelatedWork/model/rust_memory_management.tex
added memory management in Rust

@@
-Each value in Rust has a variable called its owner. This owner has information about the value, such as location in memory, 
-length and capacity of the value. This owner can live on the scope associated with its life time. When the owner goes out of it’s scope, 
-the value will be dropped. When a value already assigned to a variable is assigned to another variable, if the value is allocated 
-on heap its information is copied to the new owner and drop the old owner disabling old variable. Similar thing happens when we pass variable to parameter of function. 
-After passing a variable to a parameter, all the information is copied to new owner through the parameter and old owner is no longer available. 
-The new owner can only live in the function and the object will be dropped. In this case, we have no longer access to the object after the function. 
-To avoid this, Rust has a concept called borrowing. We can set reference for the parameter of function and use the reference for operation within function and drop the reference, 
-but not the ownership.
+Rust is a system programming language which provides memory safety without runtime checking like GC and necessity of explicit memory de/allocation. 
+To ensure memory safety, Rust provides restrictive coding patterns and checks lifetime of value and memory safety at compile-time.
+The restrictive patterns also enables a developer to write fearless concurrent code that is free of data races.
+Main concepts of Memory Management in Rust are ownership, move, and borrowing.
+
+\subsection{Ownership}
+In ownership feature or Rust, each value has a variable called owner.
+This owner has information about the value, such as location in memory, length and capacity of the value. 
+For example, the object representation of Vec$<$i32$>$ is shown in Figure~\ref{fig:rustvec}. The upper boxes represent owner variable in stack frame. 
+The lower boxes represent contiguous memory allocated to store i32. Its capacity is specified 10, but 7 values of i32 are stored. 
+Therefore, there are still spaces to store 3 values of i32 without reallocation of memory. This owner can live on the scope associated with its lifetime.
+When the owner is dropped, the value will be dropped too. This feature is similar to how RAII in C++ works. 
+However, acquisition of owner out of the scope where it was constructed is available in Rust with the concept of move.
+
+\begin{figure}[htb]
+    \includegraphics[width=15cm]{rust_vec.eps}
+    \caption{Representation of Rust Vec$<$i32$>$}
+    \label{fig:rustvec}
+\end{figure}
+
+\subsection{Move}
+In Rust, for most types operations like assigning a value to a variable, passing it to a function, or returning it from a function do not copy the value: they move it. 
+With move, a value can be transferred from one owner to another. The previous variable does not have ownership of the value; it is moved to a newly assigned variable. 
+To understand how this assignment implementation is unique from other programing languages, Java, C++, and Rust code example of assigning list or vector of strings are shown.
+
+Below a few lines of code are initialization of list of string and reassigning it to other variables. 
+\begin{lstlisting}
+    List<String >s = new ArrayList<>(
+                     Arrays.asList("lemon", "orange", "apple"))
+    String t = s
+    String u = s
+ \end{lstlisting}
+Figure~\ref{fig:pythonlist} represents the memory allocated after a Java ArrayList of strings is initialized and assigned to variable called s. After assigning s to t and to u, 
+the memory representation become Figure~\ref{fig:pythonlistcopied}. The assignments are simply setting pointers to the ArrayList object and increment reference count.
+
+\begin{figure}[htb]
+    \includegraphics[width=10cm]{python_list_copied.eps}
+    \caption{Representation of Java ArrayList of String}
+    \label{fig:pythonlist}
+\end{figure}
+
+\begin{figure}[htb]
+    \includegraphics[width=10cm]{python_list.eps}
+    \caption{Representation of Java ArrayList of String after assignment to another variable}
+    \label{fig:pythonlistcopied}
+\end{figure}
+
+Now, the analogous C++ code is shown below. 
+\begin{lstlisting}
+    vector<string> s = {"lemon", "orange", "apple"};
+    vector<string> t = s;
+    vector<string> u = s;
+ \end{lstlisting}
+Figure~\ref{fig:cpluscplusvector} shows the memory allocated when the vector is initialized. Figure~\ref{fig:cpluscplusvectorcopied} is a representation of after the assignments of s to t and to u. 
+In C++, assigning value of vector to other variables involves allocating memory for new vector and copying the contents of the original vector to newly allocated one.
+
+\begin{figure}[htb]
+    \includegraphics[width=15cm]{cplusplus_vector.eps}
+    \caption{Representation of C++ vector of string}
+    \label{fig:cpluscplusvector}
+\end{figure}
+
+\begin{figure}[htb]
+    \includegraphics[width=15cm]{cplusplus_vector_copied.eps}
+    \caption{Representation of C++ vector of string after assignment to another variable}
+    \label{fig:cpluscplusvectorcopied}
+\end{figure}
+
+In Rust code, the code is like below, 
+\begin{lstlisting}
+    let s = vec!["lemon".to_string, "orange".to_string, "apple".to_string];
+    let t = s;
+    let u = s;
+ \end{lstlisting}
+
+The representation of the original Vec of String in Rust is the almost same in C++ vector of string. Figure~\ref{fig:rustvecmoved} however shows different behavior when Rust assigns s to t. 
+The value is moved to t from s so that the source variable s is uninitialized. The Rust code actually throws compile error, because we are assigning uninitialized variable at the last line.
+
+\begin{figure}[htb]
+    \includegraphics[width=15cm]{rust_vec_moved.eps}
+    \caption{Representation of Rust Vec$<$String$>$ after assignment to another variable}
+    \label{fig:rustvecmoved}
+\end{figure}
+
+\subsection{Borrowing}
+Borrowing lets code use a value temporarily without affecting its ownership so that it reduces unnecessary movement of ownership. 
+One use case is when value is used in function and needed to be passed to the argument. If the argument takes ownership and the function does not return the value, 
+the ownership of value goes out of scope and the memory is deallocated. One can pass reference of the value to the argument instead of owner. 
+The reference goes out of scope, but ownership remains the same.

### 2020-04-22 thesis_template/2_RelatedWork/model/spark.tex

--- 2020-04-06 thesis_template/2_RelatedWork/model/spark.tex
@@
-\section{Hadoop MapReduce to Spark}
-\label{sec:history}
-In several Big Data mining tools that have been developed, the most notable ones are MapReduce and Spark. MapReduce is a cluster computing framework 
-which supports locality-aware scheduling, fault tolerance, and load balancing. Spark is designed to improve performance for iterative jobs keeping features of MapReduce.
-
-MapReduce provides a programming model where the user creates acyclic data flow graphs to pass input data through a set of operations. This 
-data flow programming model is useful for many of query applications. However, MapReduce framework struggles from two of main resent data mining jobs: iterative jobs and interactive analysis.
-
-Iterative job is especially common in Machine Learning Algorithm, such as learning a data model using Gradient Descent.
-In traditional MapReduce framework, each iteration can be expressed as single MapReduce job
-so that each job must reload the data from disk. This leads I/O overhead and deteriorates performance of iterative algorithms.
-
-Interactive analysis is also an inevitable task in modern data science. A data scientist wants tp perform exploratory analysis in interactive way. 
-Nevertheless, MapReduce is designed in the way more stable for ad-hoc query, so each analysis can be single MapReduce job. 
-To perform multiple analysis to explore dataset, the data needs to be written to and reload from disk many times.
-
-To overcome these limitations, Spark has been developed as a new cluster computing framework maintaining the innovative characteristics of MapReduce and improving 
-its iterative and interactive jobs with in-memory data structure.
-
-Some of the notable improvements are shown here\cite{DBLP:journals/pvldb/ShiQMJWRO15}.
-For aggregation operation, map output selectivity, which is the ration of the map output size to the job input size,
-can be significantly reduced by using Spark. Spark uses a map side combiner, hash-based aggregation which is more efficient than sort-based aggregation used in MapReduce. 
-For iterative operation, caching the input as Resilient Distributed Datasets (RDDs) can reduce CRU and disk I/O overheads for sequence iteration. 
-This RDD caching takes a significant role to improve iterative job, because it is more efficient than other low-level caching approaches such as OS buffer caches, and HDFS caching. 
-These caching strategy reduces disk I/O overhead, but CPU overhead, such as parsing text to objects.
-
-\section{Apache Spark}
-\label{sec:history}
 \subsection{Resilient Distributed Datasets}
@@
 the effort to discover the best GC tuning afflicts developers.
-
-\section{Application to System Language}
-\label{sec:history}
-Considered overhead produced by Memory Management in JVM, use of system language for development of Big Data tool can be one of solutions rather than application language, such as Java and Scala. 
-System languages, such as C and C++, are languages that give developer total control over the hardware and de/allocation of memory without GC. 
-These features enable program written in system languages to optimized performance taking full advantage of hardware.
-
-To take example, one can build Big Data tool with C++. C++ is one of the most popular system languages which has Object-oriented features. 
-C++ has functions which provide control over memory to developers. In another word, it is responsibility for one to manage memory properly and safely. 
-The functions, malloc() and free(), take roll for memory allocation and deallocation in respectively. The manual memory de/allocation may cause several problems and require developers 
-attention to the problems with significant effort for debugging and testing. Here, we explain two of the most common problems regarding to memory management in existing system languages.
-
-Dangling pointer or reference is a pointer or reference pointing to object that no longer exists. The situation of dangling pointer happens 
-because of deallocation of memory without modification of value of the pointer. 
-If the memory region is reallocated for other object and the dangling pointer tries to access the original object, the unpredictable behavior may result.
-
-Memory leak occurs when memory is allocated and no longer referenced so that the object in the memory location cannot be reached and released.
-This is result of dereferencing object without deallocation. Memory leak consumes more memory than necessary by making unreachable location.
-
-Some solutions are established to address these problems. Actually GC is a high-level solution that guarantees memory safety. 
-C++ has a different solution called Resource Acquisition is Initialization (RAII). In RAII, objects can live within the scope where they are created. 
-The memory is released when the object goes out of scope. This solution is more predictable and deterministic than GC. 
-However, it is problematic When we need the object out of the scope, returning a value from a function. 
-There are several ways to go around this problems, such as smart pointers, copy constructors, and move semantics. 
-Nevertheless, these non-orthogonal concepts makes code in disorganize and leads to error prone implementation.
-
-\section{Rust Memory Management}
-\label{sec:history}
-Rust is a system programming language which provides memory safety without runtime checking like GC and necessity of explicit memory de/allocation. 
-To ensure memory safety, Rust provides restrictive coding patterns and checks lifetime of value and memory safety at compile-time.
-The restrictive patterns also enables a developer to write fearless concurrent code that is free of data races.
-Main concepts of Memory Management in Rust are ownership, move, and borrowing.
-
-\subsection{Ownership}
-In ownership feature or Rust, each value has a variable called owner.
-This owner has information about the value, such as location in memory, length and capacity of the value. 
-For example, the object representation of Vec$<$i32$>$ is shown in Figure. This owner can live on the scope associated with its lifetime.
-When the owner is dropped, the value will be dropped too. This feature is similar to how RAII in C++ works. 
-However, acquisition of owner out of the scope where it was constructed is available in Rust with the concept of move.
-
-\subsection{Move}
-In Rust, for most types. operations like assigning a value to a variable, passing it to a function, or returning it from a function do not copy the value: they move it. 
-With move, a value can be transferred from one owner to another. The previous variable does not have ownership of the value; it is moved to a newly assigned variable. 
-To understand how this assignment implementation is unique from other programing languages, Python, C++, and Rust code example of assigning list or vector of strings are shown in Figure. 
-For example, a value is instantiated in a function. 
-When it is returned to a new variable, the ownership of value is moved to the new variable. In Rust, one do not have to explicitly deallocate memory, 
-because ownership of value is passed among variables across scope using move and eventually goes out of scope deallocating memory of the value.
-
-\subsection{Borrowing}
-Borrowing lets code use a value temporarily without affecting its ownership so that it reduces unnecessary movement of ownership. 
-One use case is when value is used in function and needed to be passed to the argument. If the argument takes ownership and the function does not return the value, 
-the ownership of value goes out of scope and the memory is deallocated. One can pass reference of the value to the argument instead of owner. 
-The reference goes out of scope, but ownership remains the same.

### 2020-04-22 thesis_template/3_Body/chapter/concept.tex

@@
  n1-standard-1 which has 1 vCPU, 3.75 GB RAM, and 10 GB Standard persistent disk, 
- n1-standard-4 which has 2 vCPU, 15 GB RAM, and 10 GB Standard persistent disk, 
- n1-standard-4 which has 2 vCPU, 15 GB RAM, and 10 GB Standard persistent disk,  
+ n1-standard-4 which has 4 vCPU, 15 GB RAM, and 10 GB Standard persistent disk, 
+ n1-standard-8 which has 8 vCPU, 30 GB RAM, and 10 GB Standard persistent disk,  
  All of the experiments described are performed 5 times. 

### 2020-04-22 thesis_template/3_Body/model/access_own_reference_slice.tex

@@
 For example, all of i32 elements used for key field in 1 million Customer object are stored in Vec$<$i32$>$ with 1 million i32 elements. 
-Later, these i32 elements are moved to be owned or borrowed by by the object's fields.
+Later, these i32 elements are moved to be owned or borrowed by the object's fields.
 
@@
 
-No matter Vec size initialized or not, differences of runtime for accessing objects among different object types are not remarkable. 
+No matter Vec size initialized or not, differences of runtime for accessing objects are not remarkable among different object types. 
 The percent increase in runtime of accessing to fields of from 1.5 to 3.8 million CustomerOwned objects is 121\% if the Vec is initialized, 554\% if the Vec is not initialized.

### 2020-04-22 thesis_template/3_Body/model/drop_ref_rc.tex

@@
 In this experiment, an assessment is conducted to verify whether there is difference between behavior of reference and Rc.
-The reason why dropping Rc is much slower than dropping reference it that Rc requires runtime overhead to check some states of the variable, 
+The reason why dropping Rc is much slower than dropping reference is that Rc requires runtime overhead to check some states of the variable, 
 but when to drop reference is already determined at compile time. When dropping Rc, Rc has to check the number of variable pointing to the actual content and decide 

### 2020-04-22 thesis_template/3_Body/model/merge_sort_experiment.tex

@@
-\subsection{Concept}
-This experiment is to assess importance of careful memory management in multithreading of Rust. 
-In Rust programming, we usually need Atomic Reference Counting (Arc) to share data among threads. 
-Arc is a simple interface that allows threads to share data, but it may cause significant overhead in Big Data processing.
-Arc allows multiple variable to have ownerships of a particular value similarly to Rc, 
-but also supports atomic feature enabling the ownerships exist in different threads.
-
 As explained in last experiment, deletion of Rc has significant overhead than normal reference. 
-By learning this result, our assumption is that deletion of Arc has also overhead when we compare to normal reference. 
-In many situation where developer write a multithreading code, Arc is used and the deletion happens multiple times. 
+By learning this result, our assumption here is that deletion of Arc has also overhead when we compare to normal reference. 
+In many situation where developer writes a multithreading code, Arc is used and the deletion happens multiple times. 
 To assess runtime overhead of algorithm with Arc, We implement merge-sort algorithm in two different ways. 
@@
 By using scoped thread, we can implement two merge-sort algorithms in identical way except whether the function receives Arc or reference of source vector.
-The representations of source vector for each algorithm are shown in figure.
+The representations of source vector for each algorithm are shown in Figure~\ref{fig:source_merge_sort}.
+The elements of source vector are CustomerOwned objects. We generates source vectors in size of 1, 2, 3 and 4 million.
+Finally, merge-sort is performed based on value of key field. The figure shows the result for runtime performance of merge-sort algorithms on difference size of vectors. 
+This experiment is run on n1-standard-4 and generates 4 threads to perform multithreading.
 
@@
     \caption{Representation of Source Vector}
-    \label{fig:Sampling}
+    \label{fig:source_merge_sort}
 \end{figure}
@@
 \subsection{Result}
-The elements of source vector are CustomerOwned objects. We generates source vectors in size of 1 million, 2 million, 3 million and 4 million. 
-Finally, merge-sort is performed based on Customer key value. The figure shows the result for runtime performance of merge-sort algorithms on difference size of vectors.
+Figure~\ref{fig:source_merge_sort} shows the runtime performance of our merge-sort algorithm with specified Vec sizes. 
+The blue and yellow bar charts represent the runtime performance of merge-sort algorithm using reference and Arc respectively. 
+The result says that algorithms with Arc is about 24\% slower than algorithms with reference.
 
@@
     \includegraphics[width=15cm]{rust_merge_sort.eps}
-    \caption{Runtime of Sortting Elements of Customer Vector}
-    \label{fig:Sampling}
+    \caption{Runtime of Sorting Elements of Customer Vector}
+    \label{fig:merge_sort}
 \end{figure}
@@
 \subsection{Discussion}
+The reason why merge-sort algorithm with Arc is much slower than one with reference is 
+the same for the reason why dropping Rc shows overhead compared to dropping reference.
+Arc has to check the number of variable pointing to the actual content and decide 
+deallocate the memory or not.
+
+In addition, Arc uses atomic operations for tis reference counting. Atomic operations bring thread-safety, but they are more expensive than ordinary memory accesses.
+Therefore, when sharing reference counting between threads is not required, using Rc is the recommended way \cite{RustArcPage}.
+
+In the situation like our experiment, normal reference can be used instead of Arc to share data between threads. 
+This solution results in better runtime performance in our experiment. Therefore, one should use reference to share data among different threads 
+whenever it is possible.

### 2020-04-22 thesis_template/3_Body/model/tree_aggregate_experiment.tex
change

@@
-\subsection{Description}
-Tree-aggregate is a communication patten heavily used for Machine Learning algorithm in Spark (MLlib). 
-In the traditional aggregation function in Spark, results of aggregation in all executor clusters are sent to the driver. 
-That is why this operation suffers from the CPU cost in merging partial results and the network bandwidth limit.
-Tree-aggregate is a communication pattern which overcomes these problems by breaking aggregate operation in multi-level represented like tree structure.
-
 In our experiment, tree-aggregation algorithms are examined in multi-threading. This experiment is to evaluate the impact of having Arc (Atomic Reference Counting) as elements of vector. 
@@
 This does not require extra memory allocation, because only acquisition of new ownership to value is needed. 
-However, deletion of Arc type checks whether the value is still owned by other variables. 
+However, as explained in the last section deletion of Arc type checks whether the value is still owned by other variables. 
 This checking may be an overhead in algorithms where generate a lot of intermediate data structures, because deletion of the data structures occurs in frequent.
@@
 Two algorithms are implemented using the above two different methods and evaluated their runtime performance. 
-The both algorithms perform tree-aggregation where runs on seven partitions of source vector. 
-Each steps load Customer vector from disk and aggregate it by Customer last name. Once a node finishes aggregation, it sends result to parent node. 
+We perform aggregation to CustomerOwned based on last\_name field. 
+Before tree-aggregation algorithms are run, partitions of Vec$<$CustomerOwned$>$ or of Vec$<$Arc$<$CustomerOwned$>>$ are created ,serialized, and stored in disk.
+A tree-aggregate algorithm has main three phases: loading, aggregating, and combining phase. 
+At loading phase the algorithm generate threads. In each node, it loads serialized CustomerOwned partition from disk and deserialize them.
+At aggregating phase, aggregation is performed on each partition by last\_name field. Once a node finishes aggregation, it sends result to parent node. 
 After parent nodes receive aggregation results from all of its children nodes, it joins all aggregation results including its and sends next parent. 
-One algorithm performs aggregation by deep-copying elements from source vector loaded from disk. In the other algorithm, each element of source vector 
-is wrapped in Arc, and its reference is acquired while aggregation.
+This joining aggregation results is considered as combining phase.
 
-\subsection{Result}
+Two kinds of algorithm are implemented. One algorithm performs aggregation by deep-copying elements from source vector loaded from disk. 
+In the other algorithm, each element of source vector is wrapped in Arc, and its reference is acquired while aggregation. 
+The difference of the both algorithm codes are represented in Figure~\ref{fig:arc_tree} and in Figure~\ref{fig:deep_tree}.
+If we glance the codes, the notable difference is only when we acquire an element from CustomerOwned Vec to construct an aggregated data structure.
+Therefore, there is few difference between two kinds of tree-aggregate algorithm in terms of code appearance.
 
-Figure shows runtime performance of two tree-aggregate algorithms. The runtime of algorithm with deep-copy is slower than algorithm with Arc for every vector size. 
-This is result of overhead of deep-copy is larger than deletion of Arc.
-
-\begin{figure}[htb]
-    \includegraphics[width=15cm]{rust_tree_aggregate.eps}
-    \caption{Runtime of Tree-aggregate algorithm}
-    \label{fig:Sampling}
-\end{figure}
-
-\subsection{Discussion}
-As we explained, Arc has overhead to be deleted because it has to check if the value is still referred. 
-Even though the deletion of Arc is slow, deep copy of complex objects has more impact in deterioration of runtime performance. 
-In the algorithm with deep copy, the elements of each partition in each node are deep-copied once during aggregation.
-
-If total number of elements are 1000000, the all of 1000000 elements are deep-copied once during execution.
-On the other hand, acquisition and deletion of Arc occurs several time for each element object.
-First, acquisition of Arc of all elements in loaded vector happens during aggregation in each node and the loaded vector is deleted after the aggregation. 
-Second, deletion of all elements in aggregated structures from children nodes and the node is occurs after joining these aggregated structures to single one.
-
-The result shows a deep-copy of Customer vector is computationally much more expensive than acquisition and deletion of Arc. 
-This result suggests that having element objects in Arc is efficient than deep-copying element from original source vector in tree-aggregation algorithm 
-where generates intermediate data structure.
+Numbers of CustomerOwned objects aggregated in our experiment are 1, 2, 3, 4 million. 
+This experiment is run on n1-standard-4.
 
@@
     \caption{Aggregation function with Arc}
-    \label{fig:Sampling}
+    \label{fig:arc_tree}
 \end{figure}
@@
     \caption{Aggregation function with deep-copy}
-    \label{fig:Sampling}
+    \label{fig:deep_tree}
 \end{figure}
+
+\subsection{Result}
+Figure~\ref{fig:ex_tree_agg} shows runtime performance of two tree-aggregate algorithms. 
+The runtime of algorithm with deep-copy is about 33\% slower than algorithm with Arc for every vector size.
+
+\begin{figure}[htb]
+    \includegraphics[width=15cm]{rust_tree_aggregate.eps}
+    \caption{Runtime of Tree-aggregate algorithm}
+    \label{fig:ex_tree_agg}
+\end{figure}
+
+\subsection{Discussion}
+As we explained, Arc has overhead to be deleted because it has to check if the value is still referred. The atomic operations are more expensive than ordinal memory access.
+Even though the use of Arc slows down runtime performance, deep copy of complex objects has more impact in deterioration of runtime performance.
+
+At the aggregating phase, each object is deep-copied or acquired with Arc once during the runtime in order to construct aggregated data structures.
+If total number of object is 1 million, the all of 1 million objets are deep-copied or cloned with Arc once during execution. 
+Deep-copy allocates new memory for copied object. On the other hand, clone with Arc is merely acquisition of additional owner. 
+Therefore, deep-copy is more expensive in terms of runtime and also use of memory than clone with Arc. 
+Deep-copy processes all the original objects to generate newly deep-copied objects. 
+This process has overhead and the existence of both original and copied objects doubles its memory usage.
+
+After construction of aggregated data structure, the dropping variables of original object occurs at the end of aggregating phase.
+In the algorithm with deep-copy, these variables are owners so that drop of variables triggers deallocation of actual values.
+In the algorithm with Arc, the variables are Arc. The aggregated data structure contains Arc pointing to the same values pointed by original Arc.
+Since the aggregated data structure continue to live after aggregating phase, drop of original Arcs does not triggers deallocation of values. 
+Therefore, drop of original variables can shows overhead of memory deallocation in algorithm with deep-copy, 
+and overhead of checking reference count of Arc in algorithm with Arc.
+
+In addition, memory access from Arc is slower than ordinal variable due to the atomic operations. This may be potential overhead of the algorithm with Arc.
+
+Considered these theoretical analysis and result of our experiment, using Arc improves runtime performance and memory usage compared to algorithm using deep-copy in tree-aggregate algorithm.

### 2020-04-23 thesis_template/Appendix/model/note.tex
documented except abstract, knn experiment, and conclusion

--- 2020-04-03 thesis_template/Appendix/Appendix.tex
@@
-\chapter{Proof of xyz}
-\label{appendix}
-\thispagestyle{myheadings}
-
-\graphicspath{{Appendix/Figures/}}
-
-\section{Memory and Process in Operation Systems}
-\label{sec:history}
-A process is a section of computation job. A process can work on a CPU core. We can divide process as well.
-Basically, each process does not share their memory. However, for multiprocessing, we could avoid this restriction.
-Processes can be represented as tree structure, because a process may create other child processes.
-Process has 4 states, new, running, waiting, and ready. 
-Process is represented in process control block (PCB) with state type, process ID, registers, and so on.
-The scheduling for process assigning to CPU core is implemented in queues containing PCB. There are two main queues in this scheduler: 
-ready queue and wait queue. The head of process in ready queue is selected for execution and once the process requested I/O request or 
-production of child process, the running process will be stored n wait queue. Once the request that the process waiting for end, 
-the waiting process will be pushed tail of ready queue.
-
-Processes executing concurrently in the operating system may be either independent processes or cooperating processes executing in the system.
-A process is independent if it does not share data with any other processes. A process cooperating if it can affect or be affected by the 
-other processed executing in the system. In cooperating process, there are two kinds, shared memory and message passing. 
-In shared memory, it removes restriction of not interfering memory region. Message passing can be useful for distribution systems as well.
-
-For a pair of processes to communicate through message, a socket is needed to be established. 
-A socket is identified by an IP address concatenated with a port number. When two process communicate, each process will have socket. 
-If another process of the same machine wants to communicate, we need new socket to be established. The protocol used in the socket connection
-can be TPC and UDP.
-
-\section{Multi-threading and Parallelism}
-\label{sec:history}
-A thread is a basic unit of CPU utilization, so that a process can have multiple thread. Threads share mainly code and data. 
-Multi-threading is increasingly popular as the multicore programming becomes in common, because we can run multiple thread on different core.
-Creating thread is much cheaper than creating process and it shares resources so that we do not need additional methods to allow threads to 
-communicate each other, such as sharing memory and message passing.
-
-\section{Memory management in Operation System}
-\label{sec:history}
-In computer storage hierarchy, the closest storage to CPU is register. It is built into each CPU core and accessible within one cycle of the CPU clock.
-However, the same cannot be said of main memory, which is accessed via a transaction on the memory bus. This takes many cycles of the CPU clock.
-The remedy is to add fast memory between the CPU and main memory, typically on the CPU chip for faster access. Such a cache plays a role for this.
-
-For the layout of main memory, it must be ensured that each process has a separate memory space, including operation system. 
-The base register and limit register, whose roles are lower bound of memory region and specific size of range respectively, can achieve that goal.
-
-Usually a program resides on a disk as binary executable file. To run, the program must be brought into memory and placed within the context of a process.
-The process is bound to corresponding parts of the physical memory. Binding program to memory address is staging process. 
-There three stages: compile time, load time execution time. The source program is compiled by compiler producing object file. 
-After the compilation, the object file is linked with other object file by linker creating executable file . 
-Finally, the executable file will be loaded to run execute. At this run time dynamic library link can be done.
-
-If where the process will reside in memory at compile time, absolute code is generated. If this is unknown at the time, 
-the binding will be done at load time. At this time, the compiler must generate relocatable code. Otherwise, the binding will be done at 
-execution time.
-
-A process does not interact with addresses of physical memory, instead virtual memory. The memory-management unit (MMU) takes roles to map 
-logical address to physical address. OS needs to ensure that any of physical memory spaces of processes do not overlap. 
-Since one process can be created and deleted and the corresponding memory space should be de/allocated, 
-optimization for use of physical memory space is important; we need to allocate memory contiguously avoiding fragmentation.
-
-There are several approaches to deal with this problems. However, we will focus on paging here, which is the most used method OS use to manage memory.
-A frame and page are a unit of Separated physical and virtual memory space in fixed size (4KB or 8KB) respectively.
-A process can use as many as pages and corresponding frames obtained by page table matching. This strategy does improve external fragmentation, but not for internal fragmentation.
-The smaller size of page has smaller fragmentation, but mapping from page to frame has overhead and also disk I/O is more efficient when the amount of data transfered is larger.
-
-\section{Demand Paging}
-\label{sec:history}
-A process can have multiple pages. However, loading entire executable code from secondary storage to memory is not necessarily needed to 
-get jobs done. A strategy used in several operating systems is loading only the portion of programs that are needed, demand page.
-
-In the storage, some pages currently used are in memory and the others are in secondary storage. 
-The page table specifies whether pages are valid or invalid, which means are in memory or not. 
-Access to a page marked invalid causes page fault and some steps to resolve the error will be required.
-
-The first part of process of demand paging would be that we check an internal table to check whether the reference is valid or invalid.
-If the reference is valid, the process reads the content from the memory. Otherwise, we terminates the process and find the free frame in 
-physical memory. Then, we schedule a secondary storage operation to read the desired page into newly allocated frame. 
-When the storage complete reading the page, we modify the internal table to indicate the page is now in memory. 
-Finally, we restart the instruction that was interrupted.
-
-However, there would be a case where the memory does not have any free frame. In this case, a victim frame that will be replaced with new coming frame should be selected. 
-To perform this selection efficiently, a modify bit is tracked for each frame or page. The modify bit represents whether the page is modified since it is loaded from secondary storage. 
-If the page or frame is modified, when we swap page we need to update the content in the secondary storage. However, it is not modified, we can simply delete the frame and replace with new frame.
-
-\section{Copy on Page}
-\label{sec:history}
-When a parent process creates child process and if these process shares contents on particular page and modify it, 
-only the page which has the contenst will be copied.
-
-\section{Threads and Concurrency}
-\label{sec:history}
-
-\section{BLAS LAPACK}
-\label{sec:history}
-
-Basic Linear Algebra Subprograms (BLAS) are standard building blocks for basic vector and matrix operations. There are 3 levels of operation. The level 1 BLAS performs scalar, 
-vector and vector-vector operations, the level 2 BLAS performs matrix-vector operation, and the level 3 BLAS performs matrix-matrix operation.
-
-LAPACK is developed on BLAS and has advanced functionalities such as LU decomposition and Singular Value Decomposition (SVD). Dense and banded matrices are handled, but not general 
-sparse matrices. The initial motivation of development of LAPACK was to make the widely used EISPACK and LINPACK libraries run efficiently on shared-memory vector and parallel processors. 
-LINPACK and EISPACK are inefficient because their memory access patterns disregard the multi-layered memory hierarchies of the machines, thereby spending too much time moving data. 
-LAPACK addresses this problem by recognizing the algorithms to use block matrix operations, such as matrix multiplication, in the innermost loops.
-These block operations can be optimized for each architecture to account for the memory hierarchy,
-and so provide a portable way to achieve high efficiency on diverse modern machines. However, LAPACK requires that highly optimized block matrix operations be already implemented on each machine.
-
-ARPACK is also a collection of linear algebra subroutines which is designed to compute a few eigenvalues and corresponding eigenvectors from large scale matrix. 
-ARPACK is based upon an algorithmic variant of the Arnoldi process called the Implicitly Restarted Arnoldi Method (IRAM). 
-When the matrix is symmetric it reduces to a variant of the Lanczos process called the Implicitly Restarted Lanczos Method(IRLM).
-The Arnoldi process only interacts with the matrix via matrix-vector multiplies.
-Therefore, this method can be applied to distributed matrix operations required in big data analysis.
-
-The original BLAS and LAPACK are written in Fortran90. Linear algebra library used for Spark is netlib-java, which is a Java wrapper library for Netlib, C API of BLAS and LAPACK. 
-The reason why the developers addressed to use this package is that the BLAS and LAPACK are already bug free and implementing linear algebra library from scratch can usually buggy.
-
-However, the main advantage of use of BLAS and LAPACK is system optimized implementation. So if we implement original Fortran linear algebra library, it cannot perform as well as BLAS and LAPACK. 
-And the performance would not be such different from one of implementation in Java or Rust.  If we want to test only memory management between Rust and Java, 
-it can be enough implementation of linear algebra operation from  pure Java and Rust sacrificing the best performance taking advantage of system optimization.
-
-\section{Netlib-Java}
-\label{sec:history}
-
-Netlib-java is a Java wrapper of BLAS, LAPACK, and ARPACK. Netlib-java choose  implementation of linear algebra depending on installation of the libraries. 
-First, if we have installed machine optimised system libraries, such as Intel MKL and OpenBLAS, netlib-java will use these as the implementation to use. 
-Next, it try to load netlib references which netlib-java use CBLAS and LAPCKE interface to perform BLAS and LAPACK native call. 
-The last option is to use f2j which is intended to translate the BLAS and LAPACK libraries from their Fortran77 reference source code to Java class files, 
-instead of calling native libraries by using Java Native Interface (JNI).
-
-We can use JNI to call native libraries from Java. The JNI is a native programming interface which allows Java code that runs inside a Java Virtual Machine (VM) 
-to interoperate with applications and libraries written in other programming languages.
-
-\section{Create Java interface of CBLAS with JNI}
-\label{sec:history}
-\begin{enumerate}
-    \item Download BLAS and build using make file. In the figure2.1, the built file is libblas.a and the header file is blas.h.
-    \item Download CBLAS and build using make file (I am not sure whether we should build archive file or shared library).
-In figure, the build file would be libcblas.a or libcblas.dylib and header file is cblas.h.
-    \item Create java file which will be the Java interface of CBLAS.
-    \item Compile java file with -h header flag to create class file (CBLASJ.class) and header file (CBLASJ.h).
-\begin{lstlisting}[language=bash]
-    $ javac -h . CBLASJ.java
-\end{lstlisting}
-    \item Create C file (CBLASJ.c) which will bind Java interface and CBLAS library. And compile it with JNI to create object file (CBLASJ.o).
-\begin{lstlisting}[language=bash]
-    $ gcc -c-fPIC -I${JAVA_HOME}/include -I${JAVA_HOME}/include/darwin CBLASJ.c
-\end{lstlisting}
-    \item Compile shared library linking library (libcblas.a or libcblas.dylib) object file (CBLASJ.o).
-\begin{lstlisting}[language=bash]
-    $ gcc -o libcblas.dylib (or libcblas.a) CBLASJ.o 
-\end{lstlisting}
-\end{enumerate}
-
-\begin{figure}[htb]
-    \includegraphics[width=15cm]{cblas_with_jni.eps}
-    \caption{Integration of Native Methods }
-    \label{fig:Sampling}
-\end{figure}
-
-\section{Matrix Computation and Optimization in Apache Spark}
-\label{sec:history}
-
-Matrix operation is a fundamental part of machine learning. Apache Spark provides implementation for distributed and local matrix operation. 
-To translate single-node algorithms to run on a distributed cluster, Spark addresses separating matrix operations from vector operations and run matrix operations on the cluster, 
-while keeping vector operations local to the driver.
-
-Spark changes its behavior for matrix operations depending on the type of operations and shape of matrices.
-For example, Singular Value Decomposition (SVD) for a square matrix is performed in distributed cluster,
-but SVD for a tall and skinny matrix is on a driver node. This is because the matrix derived among the computation of SVD for tall and skinny matrix is usually small so that it can fit to single node.
-
-Spark uses ARPACK to solve square SVD.
-ARPACK is a collection of Fortran77 designed to solve eigenvalue problems.
-ARPACK is based upon an algorithmic variant of the Arnoldi process called the Implicitly Restarted Arnoldi Method (IRAM).
-When the matrix A is symmetric it reduces to a variant of the Lanczos process called the Implicitly Restarted Lanczos Method (IRLM). 
-ARPACK calculate matrix multiplication by performing matrix-vector multiplication.
-So we can distribute matrix-vector multiplies, and exploit the computational resources available in the entire cluster.
-The other method to distribute matrix operations is Spark TFOCS. Spark TFOCS supports several optimization methods.
-
-To allow full use of hardware-specific linear algebraic operations on single node, Spark uses the BLAS (Basic Linear Algebra Systems) interface with relevant libraries for CPU and GPU acceleration. 
-Native libraries can be used in Scala are ones with C BLAS interface or wrapper and called through the Java native interface implemented in Netlib-java library and wrapped by the Scala library called Breeze.
-Following is some of the implementation of BLAS.
-
-\begin{itemize}
-    \item f2jblas -  Java implementation of Fortran BLAS
-    \item OpenBLAS - open source CPU-optimized C implementation of BLAS
-    \item MKL - CPU-optimized C and Fortran implementation of BLAS by Intel
-\end{itemize}
-
-These have different implementation and they perform differently for the type of operation and matrices shape. 
-In Sark, OpenBlas is the default method of choice. BLAS interface is made specifically for dense linear algebra. 
-Then, there are few libraries that efficiently handle sparse matrix operations.
-
-\section{Memory Management of each Linear Algebra Library}
-\label{sec:history}
-
-The pure Java linear algebra library, such as La4j, EJML, and Apache Common Math, 
-use normal GC performed by JVM to manage memory. This is because the implementation of these libraries are in purely Java.
-
-Netlib-java, Jblas or other simple Java wrapper of BLAS, LAPACK, and ARPACK with Java Native Interface (JNI) use normal GC as well. 
-This is because the native code deals with Java array by obtaining a reference to it. After the operation, 
-the native method releases the reference to the Java array with or without returning new Java array or Java primitive type object.
-
-ND4J has two types of  its own memory management methods, GC to pointer of off-heap NDArray, and MemoryWorkspaces. 
-ND4J used off-heap memory to store NDArrats, to provide better performance while working with NDArrays from vative code such as BLAS and CUDA libraries. 
-Off-heap means that the memory is allocated outside of the Java heap so that it is not managed by the JVM’s GC. NDArray itself is not tracked by JVM, 
-but its pointer is. The Java heap stores pointer to NDArray on off-heap. When a pointer is dereferenced, this pointer can be a target of JVM’s GC and when it is collected, 
-the corresponding NDArray will be deallocated. When using MemoryWorkspaces, NDArray lives only within specific workspace scope. 
-When NDArray leaves the workspace scope, the memory is deallocated unless explicitly calling method to copy the NDArray out of the scope.
-
 \section{Possible Graph Structure in Rust}

### 2020-04-23 thesis_template/2_RelatedWork/model/rust_memory_management.tex

@@
                      Arrays.asList("lemon", "orange", "apple"))
-    String t = s
-    String u = s
+    List<String> t = s
+    List<String> u = s
  \end{lstlisting}
-Figure~\ref{fig:pythonlist} represents the memory allocated after a Java ArrayList of strings is initialized and assigned to variable called s. After assigning s to t and to u, 
+Figure~\ref{fig:javalist} represents the memory allocated after a Java ArrayList of strings is initialized and assigned to variable called s. After assigning s to t and to u, 
 the memory representation become Figure~\ref{fig:pythonlistcopied}. The assignments are simply setting pointers to the ArrayList object and increment reference count.
@@
 \begin{figure}[htb]
-    \includegraphics[width=10cm]{python_list_copied.eps}
+    \includegraphics[width=10cm]{java_array.eps}
     \caption{Representation of Java ArrayList of String}
-    \label{fig:pythonlist}
+    \label{fig:javalist}
 \end{figure}

### 2020-04-23 thesis_template/Appendix/model/os.tex

--- 2020-03-09 thesis_template/Appendix/Appendix.tex
@@
-\chapter{Proof of xyz}
-\label{appendix}
-\thispagestyle{myheadings}
-
-\graphicspath{{Appendix/Figures/}}
-
-\section{Memory and Process in Operation Systems}
+\section{Memory and Process in Operating Systems}
 \label{sec:history}
@@
 
-\section{Memory management in Operation System}
+\section{Memory management in Operating System}
 \label{sec:history}
@@
 When a parent process creates child process and if these process shares contents on particular page and modify it, 
-only the page which has the contenst will be copied.
+only the page which has the context will be copied.
 
-\section{Threads and Concurrency}
-\label{sec:history}
-
-\section{BLAS LAPACK}
-\label{sec:history}
-
-Basic Linear Algebra Subprograms (BLAS) are standard building blocks for basic vector and matrix operations. There are 3 levels of operation. The level 1 BLAS performs scalar, 
-vector and vector-vector operations, the level 2 BLAS performs matrix-vector operation, and the level 3 BLAS performs matrix-matrix operation.
-
-LAPACK is developed on BLAS and has advanced functionalities such as LU decomposition and Singular Value Decomposition (SVD). Dense and banded matrices are handled, but not general 
-sparse matrices. The initial motivation of development of LAPACK was to make the widely used EISPACK and LINPACK libraries run efficiently on shared-memory vector and parallel processors. 
-LINPACK and EISPACK are inefficient because their memory access patterns disregard the multi-layered memory hierarchies of the machines, thereby spending too much time moving data. 
-LAPACK addresses this problem by recognizing the algorithms to use block matrix operations, such as matrix multiplication, in the innermost loops.
-These block operations can be optimized for each architecture to account for the memory hierarchy,
-and so provide a portable way to achieve high efficiency on diverse modern machines. However, LAPACK requires that highly optimized block matrix operations be already implemented on each machine.
-
-ARPACK is also a collection of linear algebra subroutines which is designed to compute a few eigenvalues and corresponding eigenvectors from large scale matrix. 
-ARPACK is based upon an algorithmic variant of the Arnoldi process called the Implicitly Restarted Arnoldi Method (IRAM). 
-When the matrix is symmetric it reduces to a variant of the Lanczos process called the Implicitly Restarted Lanczos Method(IRLM).
-The Arnoldi process only interacts with the matrix via matrix-vector multiplies.
-Therefore, this method can be applied to distributed matrix operations required in big data analysis.
-
-The original BLAS and LAPACK are written in Fortran90. Linear algebra library used for Spark is netlib-java, which is a Java wrapper library for Netlib, C API of BLAS and LAPACK. 
-The reason why the developers addressed to use this package is that the BLAS and LAPACK are already bug free and implementing linear algebra library from scratch can usually buggy.
-
-However, the main advantage of use of BLAS and LAPACK is system optimized implementation. So if we implement original Fortran linear algebra library, it cannot perform as well as BLAS and LAPACK. 
-And the performance would not be such different from one of implementation in Java or Rust.  If we want to test only memory management between Rust and Java, 
-it can be enough implementation of linear algebra operation from  pure Java and Rust sacrificing the best performance taking advantage of system optimization.
-
-\section{Netlib-Java}
-\label{sec:history}
-
-Netlib-java is a Java wrapper of BLAS, LAPACK, and ARPACK. Netlib-java choose  implementation of linear algebra depending on installation of the libraries. 
-First, if we have installed machine optimised system libraries, such as Intel MKL and OpenBLAS, netlib-java will use these as the implementation to use. 
-Next, it try to load netlib references which netlib-java use CBLAS and LAPCKE interface to perform BLAS and LAPACK native call. 
-The last option is to use f2j which is intended to translate the BLAS and LAPACK libraries from their Fortran77 reference source code to Java class files, 
-instead of calling native libraries by using Java Native Interface (JNI).
-
-We can use JNI to call native libraries from Java. The JNI is a native programming interface which allows Java code that runs inside a Java Virtual Machine (VM) 
-to interoperate with applications and libraries written in other programming languages.
-
-\section{Create Java interface of CBLAS with JNI}
-\label{sec:history}
-\begin{enumerate}
-    \item Download BLAS and build using make file. In the figure2.1, the built file is libblas.a and the header file is blas.h.
-    \item Download CBLAS and build using make file (I am not sure whether we should build archive file or shared library).
-In figure, the build file would be libcblas.a or libcblas.dylib and header file is cblas.h.
-    \item Create java file which will be the Java interface of CBLAS.
-    \item Compile java file with -h header flag to create class file (CBLASJ.class) and header file (CBLASJ.h).
-\begin{lstlisting}[language=bash]
-    $ javac -h . CBLASJ.java
-\end{lstlisting}
-    \item Create C file (CBLASJ.c) which will bind Java interface and CBLAS library. And compile it with JNI to create object file (CBLASJ.o).
-\begin{lstlisting}[language=bash]
-    $ gcc -c-fPIC -I${JAVA_HOME}/include -I${JAVA_HOME}/include/darwin CBLASJ.c
-\end{lstlisting}
-    \item Compile shared library linking library (libcblas.a or libcblas.dylib) object file (CBLASJ.o).
-\begin{lstlisting}[language=bash]
-    $ gcc -o libcblas.dylib (or libcblas.a) CBLASJ.o 
-\end{lstlisting}
-\end{enumerate}
-
-\begin{figure}[htb]
-    \includegraphics[width=15cm]{cblas_with_jni.eps}
-    \caption{Integration of Native Methods }
-    \label{fig:Sampling}
-\end{figure}
-
-\section{Matrix Computation and Optimization in Apache Spark}
-\label{sec:history}
-
-Matrix operation is a fundamental part of machine learning. Apache Spark provides implementation for distributed and local matrix operation. 
-To translate single-node algorithms to run on a distributed cluster, Spark addresses separating matrix operations from vector operations and run matrix operations on the cluster, 
-while keeping vector operations local to the driver.
-
-Spark changes its behavior for matrix operations depending on the type of operations and shape of matrices.
-For example, Singular Value Decomposition (SVD) for a square matrix is performed in distributed cluster,
-but SVD for a tall and skinny matrix is on a driver node. This is because the matrix derived among the computation of SVD for tall and skinny matrix is usually small so that it can fit to single node.
-
-Spark uses ARPACK to solve square SVD.
-ARPACK is a collection of Fortran77 designed to solve eigenvalue problems.
-ARPACK is based upon an algorithmic variant of the Arnoldi process called the Implicitly Restarted Arnoldi Method (IRAM).
-When the matrix A is symmetric it reduces to a variant of the Lanczos process called the Implicitly Restarted Lanczos Method (IRLM). 
-ARPACK calculate matrix multiplication by performing matrix-vector multiplication.
-So we can distribute matrix-vector multiplies, and exploit the computational resources available in the entire cluster.
-The other method to distribute matrix operations is Spark TFOCS. Spark TFOCS supports several optimization methods.
-
-To allow full use of hardware-specific linear algebraic operations on single node, Spark uses the BLAS (Basic Linear Algebra Systems) interface with relevant libraries for CPU and GPU acceleration. 
-Native libraries can be used in Scala are ones with C BLAS interface or wrapper and called through the Java native interface implemented in Netlib-java library and wrapped by the Scala library called Breeze.
-Following is some of the implementation of BLAS.
-
-\begin{itemize}
-    \item f2jblas -  Java implementation of Fortran BLAS
-    \item OpenBLAS - open source CPU-optimized C implementation of BLAS
-    \item MKL - CPU-optimized C and Fortran implementation of BLAS by Intel
-\end{itemize}
-
-These have different implementation and they perform differently for the type of operation and matrices shape. 
-In Sark, OpenBlas is the default method of choice. BLAS interface is made specifically for dense linear algebra. 
-Then, there are few libraries that efficiently handle sparse matrix operations.
-
-\section{Memory Management of each Linear Algebra Library}
-\label{sec:history}
-
-The pure Java linear algebra library, such as La4j, EJML, and Apache Common Math, 
-use normal GC performed by JVM to manage memory. This is because the implementation of these libraries are in purely Java.
-
-Netlib-java, Jblas or other simple Java wrapper of BLAS, LAPACK, and ARPACK with Java Native Interface (JNI) use normal GC as well. 
-This is because the native code deals with Java array by obtaining a reference to it. After the operation, 
-the native method releases the reference to the Java array with or without returning new Java array or Java primitive type object.
-
-ND4J has two types of  its own memory management methods, GC to pointer of off-heap NDArray, and MemoryWorkspaces. 
-ND4J used off-heap memory to store NDArrats, to provide better performance while working with NDArrays from vative code such as BLAS and CUDA libraries. 
-Off-heap means that the memory is allocated outside of the Java heap so that it is not managed by the JVM’s GC. NDArray itself is not tracked by JVM, 
-but its pointer is. The Java heap stores pointer to NDArray on off-heap. When a pointer is dereferenced, this pointer can be a target of JVM’s GC and when it is collected, 
-the corresponding NDArray will be deallocated. When using MemoryWorkspaces, NDArray lives only within specific workspace scope. 
-When NDArray leaves the workspace scope, the memory is deallocated unless explicitly calling method to copy the NDArray out of the scope.
+% \section{Threads and Concurrency}
+% \label{sec:history}

### 2020-04-23 thesis_template/1_Intro/intro.tex

--- 2020-02-29 thesis_template/1_Intro/intro.tex
@@
 
-\section{Motivataion}
+\section{Motivation}
 \label{sec:history}
@@
 Recently, almost all businesses stand on data, from web marketing analysis to factory automations and leverage of data is ubiquitous, because 
-there are many open source tools to analyze data and cloud computer infractrustures which can support computation for massive amount of data. 
-The improvement of accessability to these technologies to deal with big data democratized data driven businesses by 
+there are many open source tools to analyze data and cloud computer infrastructure which can support computation for massive amount of data. 
+The improvement of accessibility to these technologies democratized data driven businesses by 
 eliminating significant amount of initial investment.
 
-However these technologies do not come with free; we need to pay for it. Ususally, user needs to pay depending on use of computational resources. 
-If your process of data analysis is too long or need to use a number of cluster with high speck specification, the cost will end up significantly hight.
+However these technologies do not come for free; we need to pay money for use of these resources. Usually, user needs to pay depending on use of computational resources. 
+If your process of data analysis is too long or need to use a number of cluster with high speck specification, the cost may end up significantly hight.
 To address these problems, the quality of analysis tool is critical. If the tool can optimize the runtime performance and usage of computational resources, 
-the cost for runing the businesses can be efficient.
+the cost for running the businesses can become efficient.
 
-Multiple cluster computing analysis tools have been developed, such as Hadoop MapReduce, Spark, and Flink. These tools have brought reliable and scalable ways to deal massive data. 
+Multiple cluster computing analysis tools have been developed, such as Hadoop MapReduce \cite{ApacheHadoopHomePage}, 
+Apache Spark \cite{ApacheSparkHomePage}, and Apache Flink \cite{ApacheFlinkHomePage}. 
+These tools have brought reliable and scalable ways to deal massive data. 
 These has become widely popular, in which data-parallel computations are executed on clusters of unreliable machines by systems that automatically provide locality-aware scheduling, 
@@
 
-These tools are constructed on top of Java Virtual Machine (JVM). JVM abstracts hardware and memory management from the developper so that the development is fairly easy. 
+These tools are constructed on top of Java Virtual Machine (JVM). JVM abstracts hardware and memory management from the developer so that the development is fairly easy. 
 In addition, Java or Scala compiled code is platform-independent, which can run on any machine with JVM. However, these advantages may be really critical weakness when it comes to 
-processing big data. JVM abstract away most detail regarding memeory management from the system designer, including memory deallocation, reuse, and movement, as well as pointers, 
-object serialization and deserialization. Since managing and utilizing memory is one of the most important factors determining Big Data systems performance, 
-reliance on a managed environment can mean an ordeer-of-magnitude increase in CPU cost for some computations. This cost may be unacceptable for high-perfomance tool development by an expert.
+processing big data. JVM abstract away most detail regarding memory management from the system designer, including memory deallocation, reuse, and movement, as well as pointers, 
+object serialization and deserialization. Since managing and utilizing memory is one of the most important factors determining Big Data systems' performance, 
+reliance on a managed environment can mean an order-of-magnitude increase in CPU cost for some computations. This cost may be unacceptable for high-performance tool development by an expert.
 
-To overcome these problems, one can use programming languages with more contoral on hardware, system languages, for development of Big Data tools.
+To overcome these problems, one can use programming languages with more control on hardware, system languages, for development of Big Data tools.
 For example, C++ is a general-purpose, statically typed,
-compiled programming language which supports multiple programming paradcigm.
-It is also a system language which gives full control over hardware.
-There are several researches or projects where developers and
+compiled programming language which supports multiple programming paradigm. It is also a system language which gives full control over hardware. 
+There are several researches or projects \cite{DBLP:conf/sigmod/0001BLLMSTYJ18} where developers and 
 researchers implement Big Data tools with this language. These tools shows significantly better performances than those developed with application languages. 
-Although the evidence of the advantage of building high speed computational tools with C++ has been discovered, the steep learning curve and difficulty of writing memory safe codes are bariiers to technology diffusion.
+Although the evidence of the advantage of building high speed computational tools with C++ has been discovered, the steep learning curve and difficulty of writing memory safe codes are barrier to technology diffusion.
 
-Rust is a system language which gives the similar performance and control of hardware to C++ or C and safety of runtime.
-Unique memory management strategy of Rust, ownership and borrowing, and fearless concurrenry
-make the language one of the ideal candidate for development of Big Data tools. There are several existing Big Data tools developed with Rust. Inspired by these activity
-
-Write about some development and research for Big Data tools with system language.
-
-Platform depenedance is no longer disadvantage, because of docker and kubernets.
-
-Rust safe language advantage
+Rust is a system language which gives the similar performance and control of hardware to C++ or C and safety of runtime. The memory-safety, and fearless concurrently in Rust programming 
+make the language one of the ideal candidate for development of Big Data tools. 
+Since the design of the language is different from any other programming languages, implementations that can be selected for algorithms can differ from existing ones.
+In this dissertation, we focus on memory management strategy for Big Data processing algorithms in development with Rust.
 
@@
 
-Memory management in Java and Scala is performed by garbage collection. 
+One of the memory management tool on JVM is garbage collection. 
 The garbage collection brings a significant advantage for programmers by removing responsibility
-for planning memory management by themselves. Instead, JVM monitors the state of memory and performs garbage
+for planning memory management by themselves manually. Instead, JVM monitors the state of memory and performs garbage
 collection at certain points. However, these monitoring and auto-execution of garbage collection cost additional 
@@
 
-Considering the issue of memory management, we introduce solution based on unique memory management methods implemented in Rust, ownership and borrowing.
-This unique concepts in Rust secure codes and perform memory management without monitoring memory or calling functions. We introduce implementations of
-machine learning algorithms in both Java and Rust to assess performances of each memory management system for iterative big data processing tasks.
+Considering the issue of memory management, we introduces solution based on unique memory management methods implemented in Rust, ownership , move and borrowing.
+This unique concepts in Rust secure codes and perform memory management without monitoring memory. 
+Since developer can select variety of memory management strategies to implement Big Data processing algorithms in Rust.
+We develop such algorithms with different strategies and compare their runtime performance to study the best algorithm implementation.

### 2020-04-23 thesis_template/Appendix/Appendix.tex

--- 2020-03-09 thesis_template/Appendix/Appendix.tex
@@
-\chapter{Proof of xyz}
+\graphicspath{{Appendix/Figures/}}
+
+\chapter{Operating Systems}
 \label{appendix}
 \thispagestyle{myheadings}
+\input{Appendix/model/os}
 
-\graphicspath{{Appendix/Figures/}}
-
-\section{Memory and Process in Operation Systems}
-\label{sec:history}
-A process is a section of computation job. A process can work on a CPU core. We can divide process as well.
-Basically, each process does not share their memory. However, for multiprocessing, we could avoid this restriction.
-Processes can be represented as tree structure, because a process may create other child processes.
-Process has 4 states, new, running, waiting, and ready. 
-Process is represented in process control block (PCB) with state type, process ID, registers, and so on.
-The scheduling for process assigning to CPU core is implemented in queues containing PCB. There are two main queues in this scheduler: 
-ready queue and wait queue. The head of process in ready queue is selected for execution and once the process requested I/O request or 
-production of child process, the running process will be stored n wait queue. Once the request that the process waiting for end, 
-the waiting process will be pushed tail of ready queue.
-
-Processes executing concurrently in the operating system may be either independent processes or cooperating processes executing in the system.
-A process is independent if it does not share data with any other processes. A process cooperating if it can affect or be affected by the 
-other processed executing in the system. In cooperating process, there are two kinds, shared memory and message passing. 
-In shared memory, it removes restriction of not interfering memory region. Message passing can be useful for distribution systems as well.
-
-For a pair of processes to communicate through message, a socket is needed to be established. 
-A socket is identified by an IP address concatenated with a port number. When two process communicate, each process will have socket. 
-If another process of the same machine wants to communicate, we need new socket to be established. The protocol used in the socket connection
-can be TPC and UDP.
-
-\section{Multi-threading and Parallelism}
-\label{sec:history}
-A thread is a basic unit of CPU utilization, so that a process can have multiple thread. Threads share mainly code and data. 
-Multi-threading is increasingly popular as the multicore programming becomes in common, because we can run multiple thread on different core.
-Creating thread is much cheaper than creating process and it shares resources so that we do not need additional methods to allow threads to 
-communicate each other, such as sharing memory and message passing.
-
-\section{Memory management in Operation System}
-\label{sec:history}
-In computer storage hierarchy, the closest storage to CPU is register. It is built into each CPU core and accessible within one cycle of the CPU clock.
-However, the same cannot be said of main memory, which is accessed via a transaction on the memory bus. This takes many cycles of the CPU clock.
-The remedy is to add fast memory between the CPU and main memory, typically on the CPU chip for faster access. Such a cache plays a role for this.
-
-For the layout of main memory, it must be ensured that each process has a separate memory space, including operation system. 
-The base register and limit register, whose roles are lower bound of memory region and specific size of range respectively, can achieve that goal.
-
-Usually a program resides on a disk as binary executable file. To run, the program must be brought into memory and placed within the context of a process.
-The process is bound to corresponding parts of the physical memory. Binding program to memory address is staging process. 
-There three stages: compile time, load time execution time. The source program is compiled by compiler producing object file. 
-After the compilation, the object file is linked with other object file by linker creating executable file . 
-Finally, the executable file will be loaded to run execute. At this run time dynamic library link can be done.
-
-If where the process will reside in memory at compile time, absolute code is generated. If this is unknown at the time, 
-the binding will be done at load time. At this time, the compiler must generate relocatable code. Otherwise, the binding will be done at 
-execution time.
-
-A process does not interact with addresses of physical memory, instead virtual memory. The memory-management unit (MMU) takes roles to map 
-logical address to physical address. OS needs to ensure that any of physical memory spaces of processes do not overlap. 
-Since one process can be created and deleted and the corresponding memory space should be de/allocated, 
-optimization for use of physical memory space is important; we need to allocate memory contiguously avoiding fragmentation.
-
-There are several approaches to deal with this problems. However, we will focus on paging here, which is the most used method OS use to manage memory.
-A frame and page are a unit of Separated physical and virtual memory space in fixed size (4KB or 8KB) respectively.
-A process can use as many as pages and corresponding frames obtained by page table matching. This strategy does improve external fragmentation, but not for internal fragmentation.
-The smaller size of page has smaller fragmentation, but mapping from page to frame has overhead and also disk I/O is more efficient when the amount of data transfered is larger.
-
-\section{Demand Paging}
-\label{sec:history}
-A process can have multiple pages. However, loading entire executable code from secondary storage to memory is not necessarily needed to 
-get jobs done. A strategy used in several operating systems is loading only the portion of programs that are needed, demand page.
-
-In the storage, some pages currently used are in memory and the others are in secondary storage. 
-The page table specifies whether pages are valid or invalid, which means are in memory or not. 
-Access to a page marked invalid causes page fault and some steps to resolve the error will be required.
-
-The first part of process of demand paging would be that we check an internal table to check whether the reference is valid or invalid.
-If the reference is valid, the process reads the content from the memory. Otherwise, we terminates the process and find the free frame in 
-physical memory. Then, we schedule a secondary storage operation to read the desired page into newly allocated frame. 
-When the storage complete reading the page, we modify the internal table to indicate the page is now in memory. 
-Finally, we restart the instruction that was interrupted.
-
-However, there would be a case where the memory does not have any free frame. In this case, a victim frame that will be replaced with new coming frame should be selected. 
-To perform this selection efficiently, a modify bit is tracked for each frame or page. The modify bit represents whether the page is modified since it is loaded from secondary storage. 
-If the page or frame is modified, when we swap page we need to update the content in the secondary storage. However, it is not modified, we can simply delete the frame and replace with new frame.
-
-\section{Copy on Page}
-\label{sec:history}
-When a parent process creates child process and if these process shares contents on particular page and modify it, 
-only the page which has the contenst will be copied.
-
-\section{Threads and Concurrency}
-\label{sec:history}
-
-\section{BLAS LAPACK}
-\label{sec:history}
-
-Basic Linear Algebra Subprograms (BLAS) are standard building blocks for basic vector and matrix operations. There are 3 levels of operation. The level 1 BLAS performs scalar, 
-vector and vector-vector operations, the level 2 BLAS performs matrix-vector operation, and the level 3 BLAS performs matrix-matrix operation.
-
-LAPACK is developed on BLAS and has advanced functionalities such as LU decomposition and Singular Value Decomposition (SVD). Dense and banded matrices are handled, but not general 
-sparse matrices. The initial motivation of development of LAPACK was to make the widely used EISPACK and LINPACK libraries run efficiently on shared-memory vector and parallel processors. 
-LINPACK and EISPACK are inefficient because their memory access patterns disregard the multi-layered memory hierarchies of the machines, thereby spending too much time moving data. 
-LAPACK addresses this problem by recognizing the algorithms to use block matrix operations, such as matrix multiplication, in the innermost loops.
-These block operations can be optimized for each architecture to account for the memory hierarchy,
-and so provide a portable way to achieve high efficiency on diverse modern machines. However, LAPACK requires that highly optimized block matrix operations be already implemented on each machine.
-
-ARPACK is also a collection of linear algebra subroutines which is designed to compute a few eigenvalues and corresponding eigenvectors from large scale matrix. 
-ARPACK is based upon an algorithmic variant of the Arnoldi process called the Implicitly Restarted Arnoldi Method (IRAM). 
-When the matrix is symmetric it reduces to a variant of the Lanczos process called the Implicitly Restarted Lanczos Method(IRLM).
-The Arnoldi process only interacts with the matrix via matrix-vector multiplies.
-Therefore, this method can be applied to distributed matrix operations required in big data analysis.
-
-The original BLAS and LAPACK are written in Fortran90. Linear algebra library used for Spark is netlib-java, which is a Java wrapper library for Netlib, C API of BLAS and LAPACK. 
-The reason why the developers addressed to use this package is that the BLAS and LAPACK are already bug free and implementing linear algebra library from scratch can usually buggy.
-
-However, the main advantage of use of BLAS and LAPACK is system optimized implementation. So if we implement original Fortran linear algebra library, it cannot perform as well as BLAS and LAPACK. 
-And the performance would not be such different from one of implementation in Java or Rust.  If we want to test only memory management between Rust and Java, 
-it can be enough implementation of linear algebra operation from  pure Java and Rust sacrificing the best performance taking advantage of system optimization.
-
-\section{Netlib-Java}
-\label{sec:history}
-
-Netlib-java is a Java wrapper of BLAS, LAPACK, and ARPACK. Netlib-java choose  implementation of linear algebra depending on installation of the libraries. 
-First, if we have installed machine optimised system libraries, such as Intel MKL and OpenBLAS, netlib-java will use these as the implementation to use. 
-Next, it try to load netlib references which netlib-java use CBLAS and LAPCKE interface to perform BLAS and LAPACK native call. 
-The last option is to use f2j which is intended to translate the BLAS and LAPACK libraries from their Fortran77 reference source code to Java class files, 
-instead of calling native libraries by using Java Native Interface (JNI).
-
-We can use JNI to call native libraries from Java. The JNI is a native programming interface which allows Java code that runs inside a Java Virtual Machine (VM) 
-to interoperate with applications and libraries written in other programming languages.
-
-\section{Create Java interface of CBLAS with JNI}
-\label{sec:history}
-\begin{enumerate}
-    \item Download BLAS and build using make file. In the figure2.1, the built file is libblas.a and the header file is blas.h.
-    \item Download CBLAS and build using make file (I am not sure whether we should build archive file or shared library).
-In figure, the build file would be libcblas.a or libcblas.dylib and header file is cblas.h.
-    \item Create java file which will be the Java interface of CBLAS.
-    \item Compile java file with -h header flag to create class file (CBLASJ.class) and header file (CBLASJ.h).
-\begin{lstlisting}[language=bash]
-    $ javac -h . CBLASJ.java
-\end{lstlisting}
-    \item Create C file (CBLASJ.c) which will bind Java interface and CBLAS library. And compile it with JNI to create object file (CBLASJ.o).
-\begin{lstlisting}[language=bash]
-    $ gcc -c-fPIC -I${JAVA_HOME}/include -I${JAVA_HOME}/include/darwin CBLASJ.c
-\end{lstlisting}
-    \item Compile shared library linking library (libcblas.a or libcblas.dylib) object file (CBLASJ.o).
-\begin{lstlisting}[language=bash]
-    $ gcc -o libcblas.dylib (or libcblas.a) CBLASJ.o 
-\end{lstlisting}
-\end{enumerate}
-
-\begin{figure}[htb]
-    \includegraphics[width=15cm]{cblas_with_jni.eps}
-    \caption{Integration of Native Methods }
-    \label{fig:Sampling}
-\end{figure}
-
-\section{Matrix Computation and Optimization in Apache Spark}
-\label{sec:history}
-
-Matrix operation is a fundamental part of machine learning. Apache Spark provides implementation for distributed and local matrix operation. 
-To translate single-node algorithms to run on a distributed cluster, Spark addresses separating matrix operations from vector operations and run matrix operations on the cluster, 
-while keeping vector operations local to the driver.
-
-Spark changes its behavior for matrix operations depending on the type of operations and shape of matrices.
-For example, Singular Value Decomposition (SVD) for a square matrix is performed in distributed cluster,
-but SVD for a tall and skinny matrix is on a driver node. This is because the matrix derived among the computation of SVD for tall and skinny matrix is usually small so that it can fit to single node.
-
-Spark uses ARPACK to solve square SVD.
-ARPACK is a collection of Fortran77 designed to solve eigenvalue problems.
-ARPACK is based upon an algorithmic variant of the Arnoldi process called the Implicitly Restarted Arnoldi Method (IRAM).
-When the matrix A is symmetric it reduces to a variant of the Lanczos process called the Implicitly Restarted Lanczos Method (IRLM). 
-ARPACK calculate matrix multiplication by performing matrix-vector multiplication.
-So we can distribute matrix-vector multiplies, and exploit the computational resources available in the entire cluster.
-The other method to distribute matrix operations is Spark TFOCS. Spark TFOCS supports several optimization methods.
-
-To allow full use of hardware-specific linear algebraic operations on single node, Spark uses the BLAS (Basic Linear Algebra Systems) interface with relevant libraries for CPU and GPU acceleration. 
-Native libraries can be used in Scala are ones with C BLAS interface or wrapper and called through the Java native interface implemented in Netlib-java library and wrapped by the Scala library called Breeze.
-Following is some of the implementation of BLAS.
-
-\begin{itemize}
-    \item f2jblas -  Java implementation of Fortran BLAS
-    \item OpenBLAS - open source CPU-optimized C implementation of BLAS
-    \item MKL - CPU-optimized C and Fortran implementation of BLAS by Intel
-\end{itemize}
-
-These have different implementation and they perform differently for the type of operation and matrices shape. 
-In Sark, OpenBlas is the default method of choice. BLAS interface is made specifically for dense linear algebra. 
-Then, there are few libraries that efficiently handle sparse matrix operations.
-
-\section{Memory Management of each Linear Algebra Library}
-\label{sec:history}
-
-The pure Java linear algebra library, such as La4j, EJML, and Apache Common Math, 
-use normal GC performed by JVM to manage memory. This is because the implementation of these libraries are in purely Java.
-
-Netlib-java, Jblas or other simple Java wrapper of BLAS, LAPACK, and ARPACK with Java Native Interface (JNI) use normal GC as well. 
-This is because the native code deals with Java array by obtaining a reference to it. After the operation, 
-the native method releases the reference to the Java array with or without returning new Java array or Java primitive type object.
-
-ND4J has two types of  its own memory management methods, GC to pointer of off-heap NDArray, and MemoryWorkspaces. 
-ND4J used off-heap memory to store NDArrats, to provide better performance while working with NDArrays from vative code such as BLAS and CUDA libraries. 
-Off-heap means that the memory is allocated outside of the Java heap so that it is not managed by the JVM’s GC. NDArray itself is not tracked by JVM, 
-but its pointer is. The Java heap stores pointer to NDArray on off-heap. When a pointer is dereferenced, this pointer can be a target of JVM’s GC and when it is collected, 
-the corresponding NDArray will be deallocated. When using MemoryWorkspaces, NDArray lives only within specific workspace scope. 
-When NDArray leaves the workspace scope, the memory is deallocated unless explicitly calling method to copy the NDArray out of the scope.
+\chapter{Linear Algebra Computation}
+\label{appendix}
+\thispagestyle{myheadings}
+\input{Appendix/model/linalg}

### 2020-04-23 thesis_template/Appendix/model/linalg.tex

\section{BLAS LAPACK}
\label{sec:history}

Basic Linear Algebra Subprograms (BLAS) are standard building blocks for basic vector and matrix operations. There are 3 levels of operation. The level 1 BLAS performs scalar, 
vector and vector-vector operations, the level 2 BLAS performs matrix-vector operation, and the level 3 BLAS performs matrix-matrix operation.

LAPACK is developed on BLAS and has advanced functionalities such as LU decomposition and Singular Value Decomposition (SVD). Dense and banded matrices are handled, but not general 
sparse matrices. The initial motivation of development of LAPACK was to make the widely used EISPACK and LINPACK libraries run efficiently on shared-memory vector and parallel processors. 
LINPACK and EISPACK are inefficient because their memory access patterns disregard the multi-layered memory hierarchies of the machines, thereby spending too much time moving data. 
LAPACK addresses this problem by recognizing the algorithms to use block matrix operations, such as matrix multiplication, in the innermost loops. These block operations can be optimized for each architecture to account for the memory hierarchy, 
and so provide a portable way to achieve high efficiency on diverse modern machines. However, LAPACK requires that highly optimized block matrix operations be already implemented on each machine.

ARPACK is also a collection of linear algebra subroutines which is designed to compute a few eigenvalues and corresponding eigenvectors from large scale matrix. 
ARPACK is based upon an algorithmic variant of the Arnoldi process called the Implicitly Restarted Arnoldi Method (IRAM). 
When the matrix is symmetric it reduces to a variant of the Lanczos process called the Implicitly Restarted Lanczos Method(IRLM). The Arnoldi process only interacts with the matrix via matrix-vector multiplies. 
Therefore, this method can be applied to distributed matrix operations required in big data analysis.

The original BLAS and LAPACK are written in Fortran90. Linear algebra library used for Spark is netlib-java, which is a Java wrapper library for Netlib, C API of BLAS and LAPACK. 
The reason why the developers addressed to use this package is that the BLAS and LAPACK are already bug free and implementing linear algebra library from scratch can usually buggy.

However, the main advantage of use of BLAS and LAPACK is system optimized implementation. So if we implement original Fortran linear algebra library, it cannot perform as well as BLAS and LAPACK. 
And the performance would not be such different from one of implementation in Java or Rust.  If we want to test only memory management between Rust and Java, 
it can be enough implementation of linear algebra operation from  pure Java and Rust sacrificing the best performance taking advantage of system optimization.

\section{Netlib-Java}
\label{sec:history}

Netlib-java is a Java wrapper of BLAS, LAPACK, and ARPACK. Netlib-java choose  implementation of linear algebra depending on installation of the libraries. 
First, if we have installed machine optimised system libraries, such as Intel MKL and OpenBLAS, netlib-java will use these as the implementation to use. 
Next, it try to load netlib references which netlib-java use CBLAS and LAPCKE interface to perform BLAS and LAPACK native call. 
The last option is to use f2j which is intended to translate the BLAS and LAPACK libraries from their Fortran77 reference source code to Java class files, 
instead of calling native libraries by using Java Native Interface (JNI).

We can use JNI to call native libraries from Java. The JNI is a native programming interface which allows Java code that runs inside a Java Virtual Machine (VM) 
to interoperate with applications and libraries written in other programming languages.

\section{Create Java interface of CBLAS with JNI}
\label{sec:history}
\begin{enumerate}
    \item Download BLAS and build using make file. In the figure2.1, the built file is libblas.a and the header file is blas.h.
    \item Download CBLAS and build using make file (I am not sure whether we should build archive file or shared library). In figure, the build file would be libcblas.a or libcblas.dylib and header file is cblas.h.
    \item Create java file which will be the Java interface of CBLAS.
    \item Compile java file with -h header flag to create class file (CBLASJ.class) and header file (CBLASJ.h).
\begin{lstlisting}[language=bash]
    $ javac -h . CBLASJ.java
\end{lstlisting}
    \item Create C file (CBLASJ.c) which will bind Java interface and CBLAS library. And compile it with JNI to create object file (CBLASJ.o).
\begin{lstlisting}[language=bash]
    $ gcc -c-fPIC -I${JAVA_HOME}/include -I${JAVA_HOME}/include/darwin CBLASJ.c
\end{lstlisting}
    \item Compile shared library linking library (libcblas.a or libcblas.dylib) object file (CBLASJ.o).
\begin{lstlisting}[language=bash]
    $ gcc -o libcblas.dylib (or libcblas.a) CBLASJ.o 
\end{lstlisting}
\end{enumerate}

\begin{figure}[htb]
    \includegraphics[width=15cm]{cblas_with_jni.eps}
    \caption{Integration of Native Methods }
    \label{fig:Sampling}
\end{figure}

\section{Matrix Computation and Optimization in Apache Spark}
\label{sec:history}

Matrix operation is a fundamental part of machine learning. Apache Spark provides implementation for distributed and local matrix operation. 
To translate single-node algorithms to run on a distributed cluster, Spark addresses separating matrix operations from vector operations and run matrix operations on the cluster, 
while keeping vector operations local to the driver.

Spark changes its behavior for matrix operations depending on the type of operations and shape of matrices. For example, Singular Value Decomposition (SVD) for a square matrix is performed in distributed cluster, 
but SVD for a tall and skinny matrix is on a driver node. This is because the matrix derived among the computation of SVD for tall and skinny matrix is usually small so that it can fit to single node.

Spark uses ARPACK to solve square SVD. ARPACK is a collection of Fortran77 designed to solve eigenvalue problems. ARPACK is based upon an algorithmic variant of the Arnoldi process called the Implicitly Restarted Arnoldi Method (IRAM). 
When the matrix A is symmetric it reduces to a variant of the Lanczos process called the Implicitly Restarted Lanczos Method (IRLM). 
ARPACK calculate matrix multiplication by performing matrix-vector multiplication. So we can distribute matrix-vector multiplies, and exploit the computational resources available in the entire cluster. 
The other method to distribute matrix operations is Spark TFOCS. Spark TFOCS supports several optimization methods.

To allow full use of hardware-specific linear algebraic operations on single node, Spark uses the BLAS (Basic Linear Algebra Systems) interface with relevant libraries for CPU and GPU acceleration. 
Native libraries can be used in Scala are ones with C BLAS interface or wrapper and called through the Java native interface implemented in Netlib-java library and wrapped by the Scala library called Breeze. 
Following is some of the implementation of BLAS.

\begin{itemize}
    \item f2jblas -  Java implementation of Fortran BLAS
    \item OpenBLAS - open source CPU-optimized C implementation of BLAS
    \item MKL - CPU-optimized C and Fortran implementation of BLAS by Intel
\end{itemize}

These have different implementation and they perform differently for the type of operation and matrices shape. 
In Sark, OpenBlas is the default method of choice. BLAS interface is made specifically for dense linear algebra. 
Then, there are few libraries that efficiently handle sparse matrix operations.

\section{Memory Management of each Linear Algebra Library}
\label{sec:history}

The pure Java linear algebra library, such as La4j, EJML, and Apache Common Math, 
use normal GC performed by JVM to manage memory. This is because the implementation of these libraries are in purely Java.

Netlib-java, Jblas or other simple Java wrapper of BLAS, LAPACK, and ARPACK with Java Native Interface (JNI) use normal GC as well. 
This is because the native code deals with Java array by obtaining a reference to it. After the operation, 
the native method releases the reference to the Java array with or without returning new Java array or Java primitive type object.

ND4J has two types of  its own memory management methods, GC to pointer of off-heap NDArray, and MemoryWorkspaces. 
ND4J used off-heap memory to store NDArrats, to provide better performance while working with NDArrays from vative code such as BLAS and CUDA libraries. 
Off-heap means that the memory is allocated outside of the Java heap so that it is not managed by the JVM’s GC. NDArray itself is not tracked by JVM, 
but its pointer is. The Java heap stores pointer to NDArray on off-heap. When a pointer is dereferenced, this pointer can be a target of JVM’s GC and when it is collected, 
the corresponding NDArray will be deallocated. When using MemoryWorkspaces, NDArray lives only within specific workspace scope. 
When NDArray leaves the workspace scope, the memory is deallocated unless explicitly calling method to copy the NDArray out of the scope.

### 2020-04-24 thesis_template/0_Prelim/abs.tex
abstract done

@@
 
-Existing big data processing tools are developed on A
+Many existing big data processing tools are developed with application languages. 
+Dataflow platform such as Hadoop MapReduce,  Apache Spark, and Apache Flink 
+developed on Java Virtual Machine (JVM). JVM abstracts hardware and memory management from the developer. 
+This eases development processes and distribution of these tools and gives by eliminating manual memory management and 
+platform dependency.
+
+However, the automated memory strategy, such as Garbage Collection (GC), may lead significant overhead in Big Data processing. 
+Apache Spark and Apache Flink use complex objects to manipulate and transfer data. 
+Generating many of these complex objects in memory forces GC to rearrange states of memory frequently waisting computation. 
+Keeping these objects in memory for long period of time may trigger stop-the-world where the JVM stops application from running to
+execute a GC.
+
+Considered these problems in memory management in JVM, developing Big Data processing tools with system language can be the solution.
+By using system language, a developer has control on memory management, so that one can implement systems with better optimized memory management strategies.
+We selects Rust as good candidate for development of Big Data processing tools, due to its ability to write memory-safe and fearless concurrent codes.
+
+To implement optimal memory management in Rust for such tools, there may be variety of strategies and tools. 
+In this dissertation, we conduct experiments to examine the best memory management strategies in Rust for Big Data processing.

### 2020-04-24 project/rust_knn_streaming/run.sh

@@ -25,7 +25,7 @@ rm -f serialized/*
 n_lines_train=$(< $train_file wc -l)
 n_lines_test=$(< $test_file wc -l) 
 
-header="datastructure#method#k#n_neighbors#n_batch"
+header="datastructure#method#strategy#k#n_neighbors#n_batch"
 for ((i=0; i<$n_thread; i++))
 do
     header="$header#n_line_train$i"

### 2020-04-26 thesis_template/0_Prelim/abs.tex
labled documentation

@@
 
-Many existing big data processing tools are developed with application languages. 
+Many existing Big Data processing tools are developed with application languages. 
 Dataflow platform such as Hadoop MapReduce,  Apache Spark, and Apache Flink 
 developed on Java Virtual Machine (JVM). JVM abstracts hardware and memory management from the developer. 
-This eases development processes and distribution of these tools and gives by eliminating manual memory management and 
+This eases development processes and distribution of these tools by eliminating manual memory management and 
 platform dependency.
@@
 However, the automated memory strategy, such as Garbage Collection (GC), may lead significant overhead in Big Data processing. 
-Apache Spark and Apache Flink use complex objects to manipulate and transfer data. 
-Generating many of these complex objects in memory forces GC to rearrange states of memory frequently waisting computation. 
+Apache Spark and Apache Flink use complex objects to manipulate and transfer tremendous amount of data. 
+Generating many of these complex objects in memory forces GC to rearrange the objects in memory frequently waisting computation. 
 Keeping these objects in memory for long period of time may trigger stop-the-world where the JVM stops application from running to

### 2020-04-26 thesis_template/1_Intro/intro.tex
labled documentation

@@
 \section{Motivation}
-\label{sec:history}
+\label{sec:motivation}
 Importance of cluster computing tool for Big Data Analysis has been increasing as amount, value, use of data has increased. 
-Recently, almost all businesses stand on data, from web marketing analysis to factory automations and leverage of data is ubiquitous, because 
+Recently, almost all businesses stand on data, from web marketing analysis to factory automations. The leverage of data is ubiquitous, because 
 there are many open source tools to analyze data and cloud computer infrastructure which can support computation for massive amount of data. 
-The improvement of accessibility to these technologies democratized data driven businesses by 
+The improvement of accessibility to these technologies have democratized data driven businesses by 
 eliminating significant amount of initial investment.
@@
 However these technologies do not come for free; we need to pay money for use of these resources. Usually, user needs to pay depending on use of computational resources. 
-If your process of data analysis is too long or need to use a number of cluster with high speck specification, the cost may end up significantly hight.
+If your process of data analysis is too long or need to use number of clusters with high speck specification, the cost may end up significantly hight.
 To address these problems, the quality of analysis tool is critical. If the tool can optimize the runtime performance and usage of computational resources, 
@@
 \section{Problem Description}
-\label{sec:history}
+\label{sec:probdesc}
 

### 2020-04-26 thesis_template/3_Body/chapter/concept.tex
labled documentation

@@
 \subsection{Type of Variable}
-\label{sec:history}
+\label{sec:concept_diffval}
 In Rust, there are three variable types: owner, reference, and slice (only for sequence of values). 
@@
 \subsection{Reference Count}
-\label{sec:history}
+\label{sec:concept_refcount}
 Reference is useful to avoid movement of ownership. However, one needs to track its lifetime and explicitly includes it in code, 
@@
 until all the owners are dereferenced. Using Rc is sometimes preferable approach for developers especially when lifetime planning is extremely difficult.
-However, the possible problem regarding to Rc is the cost for tracking the number of references. 
-Having this assumption, an experiment is conducted to examine difference of runtime performance of dropping reference and Rc. 
+However, the possible problems regarding to Rc are the cost for tracking the number of references and allocating memory on heap instead of stack.
+Having these assumption, an experiment is conducted to examine difference of runtime performance of dropping reference and Rc. 
 This is explained in section 3.2.
 
-\subsection{Multithreading}
-\label{sec:history}
+\subsection{Multithread}
+\label{sec:concenpt_multithreading}
 In Rust programming, writing concurrent code is relatively easy. The care Rust takes with reference, mutability, and lifetimes is valuable enough in single-threaded programs, 
 but it also is in concurrent programming. Rust has tools to write concurrent code, such as threads, locks, atomic reference. 
-Therefore, one can implement various concurrent codes for the same purpose with different memory management strategies. 
+One can implement various concurrent codes for the same purpose with different memory management strategies. 
 The most ubiquitous tool used in Rust concurrent code is Atomic Reference Counting (Arc).
@@
 \subsection{Tree-aggregate}
-\label{sec:history}
+\label{sec:concept_treeagg}
 Finally, we implement some of algorithm common in Big Data processing. One of them is tree-aggregate.
 
-Tree-aggregate is a communication patten heavily used for Machine Learning algorithm in Spark (MLlib). 
+Tree-aggregate is a communication patten heavily used for Machine Learning algorithm in Spark (MLlib \cite{DBLP:journals/jmlr/MengBYSVLFTAOXX16}). 
 The topology of aggregation patterns in Apache Spark are shown in Figure~\ref{fig:aggregationk_patttern}. 
@@
 Spark generates intermediate objects from RDDs. In Tree-aggregation, aggregated HashMap like data structure is created in each thread or node. 
-When it aggregates objects in RDD, copy of objects in source vector should be performed to construct intermediate aggregated data structure.
-In another way, one can use reference to the objects to perform aggregation instead of copying the values themselves.
+When it aggregates objects in RDD, copy of objects should be performed to construct intermediate aggregated data structure.
+In another possible way that might be implemented, one can use reference to the objects to perform aggregation instead of copying the values themselves.
 In Rust, we can clone or get Arc (Rc if in single thread) of objects to implement these operations.
@@
 \subsection{K-Nearest-Neighbors}
-\label{sec:history}
+\label{sec:concept_history}
 The other algorithm common in Big Data processing is K-nearest-neighbors (KNN). KNN is a traditional Machine Learning algorithm which classify targets into categories. 
@@
 
-Our KNN algorithms are implemented with batch processing. In query phase, we control batch size to examine how size of objects allocated simultaneously in memory.
+Our KNN algorithms are implemented with batch processing.
+In query phase, we control batch size to examine how size of objects allocated simultaneously in memory has impact to algorithm's runtime performance.
 The detail implementation is explained in section3.2.
@@
 \subsection{Complex Objects}
-\label{sec:history}
+\label{sec:concept_history}
 To conduct experiments for above concepts, we use the 4 types of complex object: CustomerOwned, CustomerBorrowed, CustomerSlice, and CustomerRc. 
@@
  \subsection{Wikipedia Data Sets}
- \label{sec:history}
+ \label{sec:concept_dataset}
  Wikipedia page data sets are used to perform document classification with KNN. 
@@
  \subsection{Experimental Details}
+ \label{sec:concept_expdetail}
  Our experiments are run on three types of VM instances on Google Cloud Platform: 

### 2020-04-26 thesis_template/1_Intro/intro.tex
document updated

@@
 there are many open source tools to analyze data and cloud computer infrastructure which can support computation for massive amount of data. 
-The improvement of accessibility to these technologies have democratized data driven businesses by 
+The improvement of accessibility to these technologies has democratized data driven businesses by 
 eliminating significant amount of initial investment.

### 2020-04-26 thesis_template/2_RelatedWork/model/linalg.tex
document updated

--- 2020-04-23 thesis_template/Appendix/model/linalg.tex
@@
-\section{BLAS LAPACK}
-\label{sec:history}
+\subsection{BLAS LAPACK}
+\label{sec:linalg_blas_lapack}
 
@@
 
-\section{Netlib-Java}
-\label{sec:history}
+\subsection{Netlib-Java}
+\label{sec:linalg_netlib}
 
@@
 
-\section{Create Java interface of CBLAS with JNI}
-\label{sec:history}
-\begin{enumerate}
-    \item Download BLAS and build using make file. In the figure2.1, the built file is libblas.a and the header file is blas.h.
-    \item Download CBLAS and build using make file (I am not sure whether we should build archive file or shared library).
-In figure, the build file would be libcblas.a or libcblas.dylib and header file is cblas.h.
-    \item Create java file which will be the Java interface of CBLAS.
-    \item Compile java file with -h header flag to create class file (CBLASJ.class) and header file (CBLASJ.h).
-\begin{lstlisting}[language=bash]
-    $ javac -h . CBLASJ.java
-\end{lstlisting}
-    \item Create C file (CBLASJ.c) which will bind Java interface and CBLAS library. And compile it with JNI to create object file (CBLASJ.o).
-\begin{lstlisting}[language=bash]
-    $ gcc -c-fPIC -I${JAVA_HOME}/include -I${JAVA_HOME}/include/darwin CBLASJ.c
-\end{lstlisting}
-    \item Compile shared library linking library (libcblas.a or libcblas.dylib) object file (CBLASJ.o).
-\begin{lstlisting}[language=bash]
-    $ gcc -o libcblas.dylib (or libcblas.a) CBLASJ.o 
-\end{lstlisting}
-\end{enumerate}
-
-\begin{figure}[htb]
-    \includegraphics[width=15cm]{cblas_with_jni.eps}
-    \caption{Integration of Native Methods }
-    \label{fig:Sampling}
-\end{figure}
-
-\section{Matrix Computation and Optimization in Apache Spark}
-\label{sec:history}
+\subsection{Matrix Computation and Optimization in Apache Spark}
+\label{sec:linalg_spark_marix}
 
@@
 
-\section{Memory Management of each Linear Algebra Library}
-\label{sec:history}
+\subsection{Memory Management of each Linear Algebra Library}
+\label{sec:linalg_memmanage}
 

### 2020-04-26 thesis_template/2_RelatedWork/model/os.tex
document updated

--- 2020-04-23 thesis_template/Appendix/model/os.tex
@@
-\section{Memory and Process in Operating Systems}
-\label{sec:history}
-A process is a section of computation job. A process can work on a CPU core. We can divide process as well.
+\subsection{Memory and Process in Operating Systems}
+\label{sec:os_mem_process}
+A process is a subsection of computation job. A process can work on a CPU core. We can divide process as well.
 Basically, each process does not share their memory. However, for multiprocessing, we could avoid this restriction.
@@
 
-\section{Multi-threading and Parallelism}
-\label{sec:history}
+\subsection{Multi-threading and Parallelism}
+\label{sec:os_thread}
 A thread is a basic unit of CPU utilization, so that a process can have multiple thread. Threads share mainly code and data. 
@@
 
-\section{Memory management in Operating System}
-\label{sec:history}
+\subsection{Memory management in Operating System}
+\label{sec:os_memmanage}
 In computer storage hierarchy, the closest storage to CPU is register. It is built into each CPU core and accessible within one cycle of the CPU clock.
@@
 
-\section{Demand Paging}
-\label{sec:history}
+\subsection{Demand Paging}
+\label{sec:os_paging}
 A process can have multiple pages. However, loading entire executable code from secondary storage to memory is not necessarily needed to 
@@
 
-\section{Copy on Page}
-\label{sec:history}
+\subsection{Copy on Page}
+\label{sec:os_copypage}
 When a parent process creates child process and if these process shares contents on particular page and modify it, 
@@
 
-% \section{Threads and Concurrency}
+% \subsection{Threads and Concurrency}
 % \label{sec:history}

### 2020-04-26 thesis_template/3_Body/chapter/concept.tex
document updated

@@
-\subsection{Type of Variable}
+\section{Type of Variable}
 \label{sec:concept_diffval}
@@
 
-\subsection{Reference Count}
+\section{Reference Count}
 \label{sec:concept_refcount}
@@
 
-\subsection{Multithread}
+\section{Multithread}
 \label{sec:concenpt_multithreading}
@@
 
-\subsection{Tree-aggregate}
+\section{Tree-aggregate}
 \label{sec:concept_treeagg}
@@
 
-\subsection{K-Nearest-Neighbors}
+\section{K-Nearest-Neighbors}
 \label{sec:concept_history}
@@
 
-\subsection{Complex Objects}
+\section{Complex Objects}
 \label{sec:concept_history}
@@
 
- \subsection{Wikipedia Data Sets}
- \label{sec:concept_dataset}
- Wikipedia page data sets are used to perform document classification with KNN. 
- \(10^5\) pages are used for training data set, and 18724 pages are used for target.
-
- \subsection{Experimental Details}
- \label{sec:concept_expdetail}
- Our experiments are run on three types of VM instances on Google Cloud Platform: 
- n1-standard-1 which has 1 vCPU, 3.75 GB RAM, and 10 GB Standard persistent disk, 
- n1-standard-4 which has 4 vCPU, 15 GB RAM, and 10 GB Standard persistent disk, 
- n1-standard-8 which has 8 vCPU, 30 GB RAM, and 10 GB Standard persistent disk,  
- All of the experiments described are performed 5 times. 
- In this thesis, we present the average of 5 separate runs for each experiment.
 \clearpage

### 2020-04-26 thesis_template/3_Body/chapter/evaluation.tex
documented llvm
labled documentation
document updated

@@
-\subsection{Experiment for Accessing Object with Different Variable Type}
-\label{sec:history}
+\section{Experimental Set and Detail}
+\label{sec:eval_setdetail}
+\input{3_Body/model/experimental_set_detail}
+\clearpage
+
+\section{Experiment 1: Accessing Object with Different Variable Type}
+\label{sec:eval_diffval}
 \input{3_Body/model/access_own_reference_slice}
@@
 
-\subsection{Assessment of different reference methods in Rust}
-\label{sec:history}
+\section{Experiment 2: Assessment of different reference methods in Rust}
+\label{sec:eval_refcount}
 \input{3_Body/model/drop_ref_rc}
@@
 
-\subsection{Experiment for Merge-sort}
-\label{sec:history}
+\section{Experiment 2: Merge-sort}
+\label{sec:eval_sort}
 \input{3_Body/model/merge_sort_experiment}
@@
 
-\subsection{Experiment for Tree-aggregation}
-\label{sec:history}
+\section{Experiment 4: Tree-aggregation}
+\label{sec:eval_treeagg}
 \input{3_Body/model/tree_aggregate_experiment}
@@
 
-\subsection{Elements Copy and Insertion into Size-initialized Vector in Rust.}
-\label{sec:history}
-\input{3_Body/model/element_copy_initialization}
+% \section{Elements Copy and Insertion into Size-initialized Vector in Rust.}
+% \label{sec:history}
+% \input{3_Body/model/element_copy_initialization}

### 2020-04-26 thesis_template/3_Body/model/experimental_set_detail.tex
document updated

\subsection{Wikipedia Data Sets}
 \label{sec:concept_dataset}
 Wikipedia page data sets are used to perform document classification with KNN. 
 \(10^5\) pages are used for training data set, and 18724 pages are used for target.

 \subsection{Experimental Details}
 \label{sec:concept_expdetail}
 Our experiments are run on three types of VM instances on Google Cloud Platform: 
 n1-standard-1 which has 1 vCPU, 3.75 GB RAM, and 10 GB Standard persistent disk, 
 n1-standard-4 which has 4 vCPU, 15 GB RAM, and 10 GB Standard persistent disk, 
 n1-standard-8 which has 8 vCPU, 30 GB RAM, and 10 GB Standard persistent disk,  
 All of the experiments described are performed 5 times. 
 In this thesis, we present the average of 5 separate runs for each experiment.

### 2020-04-26 thesis_template/Appendix/model/linalg.tex
document updated

@@
-\section{BLAS LAPACK}
-\label{sec:history}
-
-Basic Linear Algebra Subprograms (BLAS) are standard building blocks for basic vector and matrix operations. There are 3 levels of operation. The level 1 BLAS performs scalar, 
-vector and vector-vector operations, the level 2 BLAS performs matrix-vector operation, and the level 3 BLAS performs matrix-matrix operation.
-
-LAPACK is developed on BLAS and has advanced functionalities such as LU decomposition and Singular Value Decomposition (SVD). Dense and banded matrices are handled, but not general 
-sparse matrices. The initial motivation of development of LAPACK was to make the widely used EISPACK and LINPACK libraries run efficiently on shared-memory vector and parallel processors. 
-LINPACK and EISPACK are inefficient because their memory access patterns disregard the multi-layered memory hierarchies of the machines, thereby spending too much time moving data. 
-LAPACK addresses this problem by recognizing the algorithms to use block matrix operations, such as matrix multiplication, in the innermost loops.
-These block operations can be optimized for each architecture to account for the memory hierarchy,
-and so provide a portable way to achieve high efficiency on diverse modern machines. However, LAPACK requires that highly optimized block matrix operations be already implemented on each machine.
-
-ARPACK is also a collection of linear algebra subroutines which is designed to compute a few eigenvalues and corresponding eigenvectors from large scale matrix. 
-ARPACK is based upon an algorithmic variant of the Arnoldi process called the Implicitly Restarted Arnoldi Method (IRAM). 
-When the matrix is symmetric it reduces to a variant of the Lanczos process called the Implicitly Restarted Lanczos Method(IRLM).
-The Arnoldi process only interacts with the matrix via matrix-vector multiplies.
-Therefore, this method can be applied to distributed matrix operations required in big data analysis.
-
-The original BLAS and LAPACK are written in Fortran90. Linear algebra library used for Spark is netlib-java, which is a Java wrapper library for Netlib, C API of BLAS and LAPACK. 
-The reason why the developers addressed to use this package is that the BLAS and LAPACK are already bug free and implementing linear algebra library from scratch can usually buggy.
-
-However, the main advantage of use of BLAS and LAPACK is system optimized implementation. So if we implement original Fortran linear algebra library, it cannot perform as well as BLAS and LAPACK. 
-And the performance would not be such different from one of implementation in Java or Rust.  If we want to test only memory management between Rust and Java, 
-it can be enough implementation of linear algebra operation from  pure Java and Rust sacrificing the best performance taking advantage of system optimization.
-
-\section{Netlib-Java}
-\label{sec:history}
-
-Netlib-java is a Java wrapper of BLAS, LAPACK, and ARPACK. Netlib-java choose  implementation of linear algebra depending on installation of the libraries. 
-First, if we have installed machine optimised system libraries, such as Intel MKL and OpenBLAS, netlib-java will use these as the implementation to use. 
-Next, it try to load netlib references which netlib-java use CBLAS and LAPCKE interface to perform BLAS and LAPACK native call. 
-The last option is to use f2j which is intended to translate the BLAS and LAPACK libraries from their Fortran77 reference source code to Java class files, 
-instead of calling native libraries by using Java Native Interface (JNI).
-
-We can use JNI to call native libraries from Java. The JNI is a native programming interface which allows Java code that runs inside a Java Virtual Machine (VM) 
-to interoperate with applications and libraries written in other programming languages.
-
 \section{Create Java interface of CBLAS with JNI}
@@
 \end{figure}
-
-\section{Matrix Computation and Optimization in Apache Spark}
-\label{sec:history}
-
-Matrix operation is a fundamental part of machine learning. Apache Spark provides implementation for distributed and local matrix operation. 
-To translate single-node algorithms to run on a distributed cluster, Spark addresses separating matrix operations from vector operations and run matrix operations on the cluster, 
-while keeping vector operations local to the driver.
-
-Spark changes its behavior for matrix operations depending on the type of operations and shape of matrices.
-For example, Singular Value Decomposition (SVD) for a square matrix is performed in distributed cluster,
-but SVD for a tall and skinny matrix is on a driver node. This is because the matrix derived among the computation of SVD for tall and skinny matrix is usually small so that it can fit to single node.
-
-Spark uses ARPACK to solve square SVD.
-ARPACK is a collection of Fortran77 designed to solve eigenvalue problems.
-ARPACK is based upon an algorithmic variant of the Arnoldi process called the Implicitly Restarted Arnoldi Method (IRAM).
-When the matrix A is symmetric it reduces to a variant of the Lanczos process called the Implicitly Restarted Lanczos Method (IRLM). 
-ARPACK calculate matrix multiplication by performing matrix-vector multiplication.
-So we can distribute matrix-vector multiplies, and exploit the computational resources available in the entire cluster.
-The other method to distribute matrix operations is Spark TFOCS. Spark TFOCS supports several optimization methods.
-
-To allow full use of hardware-specific linear algebraic operations on single node, Spark uses the BLAS (Basic Linear Algebra Systems) interface with relevant libraries for CPU and GPU acceleration. 
-Native libraries can be used in Scala are ones with C BLAS interface or wrapper and called through the Java native interface implemented in Netlib-java library and wrapped by the Scala library called Breeze.
-Following is some of the implementation of BLAS.
-
-\begin{itemize}
-    \item f2jblas -  Java implementation of Fortran BLAS
-    \item OpenBLAS - open source CPU-optimized C implementation of BLAS
-    \item MKL - CPU-optimized C and Fortran implementation of BLAS by Intel
-\end{itemize}
-
-These have different implementation and they perform differently for the type of operation and matrices shape. 
-In Sark, OpenBlas is the default method of choice. BLAS interface is made specifically for dense linear algebra. 
-Then, there are few libraries that efficiently handle sparse matrix operations.
-
-\section{Memory Management of each Linear Algebra Library}
-\label{sec:history}
-
-The pure Java linear algebra library, such as La4j, EJML, and Apache Common Math, 
-use normal GC performed by JVM to manage memory. This is because the implementation of these libraries are in purely Java.
-
-Netlib-java, Jblas or other simple Java wrapper of BLAS, LAPACK, and ARPACK with Java Native Interface (JNI) use normal GC as well. 
-This is because the native code deals with Java array by obtaining a reference to it. After the operation, 
-the native method releases the reference to the Java array with or without returning new Java array or Java primitive type object.
-
-ND4J has two types of  its own memory management methods, GC to pointer of off-heap NDArray, and MemoryWorkspaces. 
-ND4J used off-heap memory to store NDArrats, to provide better performance while working with NDArrays from vative code such as BLAS and CUDA libraries. 
-Off-heap means that the memory is allocated outside of the Java heap so that it is not managed by the JVM’s GC. NDArray itself is not tracked by JVM, 
-but its pointer is. The Java heap stores pointer to NDArray on off-heap. When a pointer is dereferenced, this pointer can be a target of JVM’s GC and when it is collected, 
-the corresponding NDArray will be deallocated. When using MemoryWorkspaces, NDArray lives only within specific workspace scope. 
-When NDArray leaves the workspace scope, the memory is deallocated unless explicitly calling method to copy the NDArray out of the scope.

### 2020-04-27 thesis_template/2_RelatedWork/model/intro.tex
related intro

This chapter describes background knowledge that we have studied for our research.
In Section~\ref{sec:os}, some of topics in Operating Systems are described focusing on memory management in operating systems.
Knowledge of operating systems helps us to understand how operating systems handle memory management and 
how other technologies takes advantage of them. Even though this dissertation does not focus technologies used for Linear Algebra Computation, 
there are some active researches in technologies in Linear Algebra Computation for Big Data processing. 
It worths to study these concepts explained in Section~\ref{sec:linalg}. 
In Section~\ref{sec:hadoopspark}, major Big Data processing tools and improvement of these tools are introduced. 
Then, Section~\ref{sec:spark} details technologies used for Apache Spark, which is one of the most popular tools for Big Data processing.
In Section~\ref{sec:appsys} and Section~\ref{sec:rustmem}, the advantages of using System Language and Rust for such tools are discussed respectively.
Finally, Section~\ref{sec:llvm} describes how LLVM thrives computer language development.

### 2020-04-27 thesis_template/2_RelatedWork/model/summary.tex
added intro and summary for each chapter

In this chapter, we cover some of main concepts to understand our research. 
The topics of Operating Systems and Linear Algebra Computation are not directly relevant to our research, 
but it is worth to cover these topics for deep analysis of experimental result. 
The advantage and disadvantage of modern Big Data processing tools are discussed and 
some of solutions are introduced. Finally, how Rust can be a good candidate for development of Big Data processing tools and 
details of its technologies are described. In next chapter, we discuss main concepts needed to understand theoretical assumption of our experiments.

### 2020-04-27 thesis_template/3_Body/chapter/concept.tex
added intro and summary for each chapter

@@
+\section{Introduction}
+\label{sec::concept_intro}
+This chapter discusses the concepts studied in our experiments. 
+Section~\ref{sec:concept_diffval} explains different variable type we can use in Rust programming.
+In Section~\ref{sec:concept_refcount}, we explain the advantage and disadvantage of Reference Count in Rust. 
+Multithread programming in Rust is studied in Section~\ref{sec:concenpt_multithreading}. 
+Two algorithms are discussed used in Big Data processing and examined in our experiments: 
+Tree-aggregate in Section~\ref{sec:concept_treeagg} and K-Nearest-Neighbors in Section~\ref{sec:concept_knn}.
+Finally, Section~\ref{sec:concept_compobj} shows complex object representations used in our experiments.
+
 \section{Type of Variable}
@@
 Since they have different memory representation, an assumption is that it takes different time to access to the contents of the memory among these pointer types.
-We examine this by constructing complex objects whose fields are these variable types. The details are explained in section 3.2.
+We examine this by constructing complex objects whose fields are these variable types. The details are explained in Section~\ref{sec:eval_diffval}.
 
@@
 \section{K-Nearest-Neighbors}
-\label{sec:concept_history}
+\label{sec:concept_knn}
 The other algorithm common in Big Data processing is K-nearest-neighbors (KNN). KNN is a traditional Machine Learning algorithm which classify targets into categories. 
@@
 \section{Complex Objects}
-\label{sec:concept_history}
+\label{sec:concept_compobj}
 To conduct experiments for above concepts, we use the 4 types of complex object: CustomerOwned, CustomerBorrowed, CustomerSlice, and CustomerRc. 
@@
 
+\section{Summary}
+\label{sec:concept_summary}
+We discussed some of concepts to understand goals of our experiments. 
+Theoretical discussions are noted in this chapter, such as assumptions where behavior of different variable types differ from each other, the impact of use of Reference Counting and Atomic Reference Counting,
+and the best practice to implement algorithms used in Big Data processing. In Chapter\ref{chapter:evaluation}, it discusses details setting of our experiments, their results and analysis.
+
 \clearpage

### 2020-04-27 thesis_template/3_Body/chapter/evaluation.tex
added intro and summary for each chapter

@@
+\section{Introduction}
+\label{sec:eval_intro}
+In this chapter, detail setting, result, and analysis of our experiments are discussed.
+Section~\ref{sec:eval_setdetail} details hardware configurations and data set we use. 
+There are 5 experiments conducted. In Section~\ref{sec:eval_diffval}, we discuss the experiment 
+where we assess runtime to access object's field with different variable types. 
+Section~\ref{sec:eval_refcount} shows details to examine how behaviors of normal reference and Reference Count are different. 
+Section~\ref{sec:eval_sort} describes our Merge-sort experiment to examine behavior of Atomic Reference Counting.
+Two algorithms are discussed used in Big Data processing and examined in our experiments: 
+Tree-aggregate in Section~\ref{sec:concept_treeagg} and K-Nearest-Neighbors in Section~\ref{sec:concept_knn}.
+
 \section{Experimental Set and Detail}
@@
 \input{3_Body/model/experimental_set_detail}
-\clearpage
 
@@
 \input{3_Body/model/access_own_reference_slice}
-\clearpage
 
@@
 \input{3_Body/model/drop_ref_rc}
-\clearpage
 
@@
 \input{3_Body/model/merge_sort_experiment}
-\clearpage
+\
 
@@
 \input{3_Body/model/tree_aggregate_experiment}
-\clearpage
+
+\section{Summary}
+\label{sec:eval_summary}
 

### 2020-04-30 thesis_template/3_Body/model/knn.tex

Finally, we examine performance of a Machine Learning (ML) algorithms. 
The goal of this experiment is to evaluate better memory management strategies in ML algorithms developed with Rust.
We employ K-Nearest-Neighbors (KNN) for ML algorithm to be studied in our experiments.
Our KNN algorithms perform document classification on Wikipedia page data set described in Section~\ref{sec:eval_setdetail}.

The algorithms have 4 phase; load, preprocess, query, and combine phase. 
The algorithms spawn threads at the beginning ,and in the load phase partition of files are loaded in each threads. 
In preprocessing phase, the algorithm process document strings to generate Term-frequencies (Tfs) matrices and other data structures. 
In query phase, it calculates cosine similarities between all combination of train and test observations and select to top \(K\) nearest neighbors. 
In combine phase, the results from each batch and from each are combined. 
Based on our experiments result, the runtime in preprocess and query phase are significantly larger than other two phases.
Therefore, we focus discussion in these two phases considering them bottlenecks in our KNN algorithms.

KNN algorithms are implemented with different memory management strategies. 
We parametrize these memory management and some other values. These parameters are listed in Table~\ref{tab:parameter}.

\begin{table}
    \renewcommand{\arraystretch}{1.2}
    \begin{tabular}{|l|l|l|l|l|}
    \hline
    Parameter Name  & \multicolumn{4}{l|}{Values and Description}                                                                                                                                                                                \\ \hline
    Method          & \multicolumn{4}{l|}{\begin{tabular}[c]{@{}l@{}}deep-copy:  use deep-copy to generate intermediate objects\\ arc: use atomic reference count to generate intermediate objects\end{tabular}}                                 \\ \hline
    Strategy        & \multicolumn{4}{l|}{\begin{tabular}[c]{@{}l@{}}1: keep intermediate objects in memory until owner is changed\\ 2: remove intermediate objects as soon as it is not needed\end{tabular}}                                    \\ \hline
    Number of batch & \multicolumn{4}{l|}{\begin{tabular}[c]{@{}l@{}}2: generate 2 batch from each partition\\ 3: generate 3 batch from each partition\end{tabular}}                                                                             \\ \hline
    k               & \multicolumn{4}{l|}{\begin{tabular}[c]{@{}l@{}}15K: dimension of feature matrices is 15 thousands \\ 20K: dimension of feature matrices is 20 thousands\\ 25K: dimension of feature matrices is 25 thousands\end{tabular}} \\ \hline
    \end{tabular}
    \caption{Parameter of KNN algorithms}
    \label{tab:parameter}
 \end{table}

Method parameter is specified to select memory management strategy used in preprocess phase. 
In preprocess phase, the algorithm generates many intermediate data structures using same String elements.
Deep-copy method deeply copies String to generate intermediate data structures. Arc method use Atomic Reference Count (Arc) to wrap String elements in the original data structure and 
clone Arc when the elements are used in other data structures. As Experiment 4 had shown in in Section~\ref{sec:eval_treeagg}, deep-copy of complex objects is more expensive than cloning Arc. 
String is a sort of objects allocated in heap and copied many times in preprocess phase. Therefore, it is worth to assess which method can be better memory management strategy in our experiments.

Strategy parameter controls memory management strategy used in both preprocess and query phase.
Strategy 1 keeps all intermediate data structures and numeric matrix objects from preprocess to query phase. 
Strategy 2 removes these data structures and objects as soon as they are not needed. 
These strategies differ from each other in terms of memory usage and frequency of memory deallocations.
These may cause significant runtime difference of the algorithms.

Number of batch controls number and size of batch for each partition. This parameter varies size of intermediate data structures and numeric matrices, and 
frequency of memory deallocations. Parameter k specifies dimension of feature matrices. This determines size of intermediate data structures and numeric matrices.

By controlling these parameter, we compare runtime and memory usage of KNN algorithms.

\subsection{Result}
\label{sec:history}

\begin{figure}[htb]
    \includegraphics[width=15cm]{total.eps}
    \caption{Total runtime whole KNN algorithm (seconds)}
    \label{fig:total}
\end{figure}

\begin{figure}[htb]
    \includegraphics[width=15cm]{preprocessing.eps}
    \caption{Total runtime of preprocessing phase in KNN (seconds)}
    \label{fig:preprocess}
\end{figure}

\begin{figure}[htb]
    \includegraphics[width=15cm]{query.eps}
    \caption{Total runtime of query phase in KNN (seconds)}
    \label{fig:query}
\end{figure}

### 2020-05-01 thesis_template/3_Body/model/knn.tex
knn result

@@
 \label{sec:history}
+Figure~\ref{fig:total}, ~\ref{fig:preprocess}, and ~\ref{fig:query} show the runtime performance of our KNN algorithms in total, preprocess, and query phase respectively. 
+The algorithms whose runtime is showing 0 seconds are algorithms that are terminated during execution due to fail of memory allocation.
+The algorithm with 2 batches, strategy 1, Arc method, and 20K and 25K dimension, 
+and the algorithm with 2 batches, strategy 1, deep-copy method, 25K dimension are such algorithms whose memory capacity get over during execution time.
+
+As shown in Figure~\ref{fig:preprocess}, the algorithms using Arc is much slower than using deep-copy in preprocessing phase. 
+If we set algorithm's parameter in 3 batches , strategy 2, and 25K dimension, the algorithm with Arc is about 38\% slower than the one with deep-copy. 
+In addition, the algorithms with strategy 2 are slower than with strategy 1. When the parameters are set in 3 batches, deep-copy method, and 25K dimension, 
+runtime performance of the algorithm with strategy 2 is about 85\% slower than one with strategy 1. 
+Furthermore, as we increase the number of dimension, the number of batch becomes more and more critical to runtime performance of the algorithms with deep-copy.
+The runtime differences among different number of batch are about 44\%, 28\%, and 39\% for the algorithms whose parameters are set in strategy 2 and Arc method. 
+However, those for the algorithms with strategy 2 and deep-copy method are about 11\%, 28\%, and 54\%. The ratios of difference increase proportionally to the number of dimension.
 
@@
 \end{figure}
+
+\subsection{Discussion}
+\label{sec:history}

### 2020-05-02 thesis_template/3_Body/model/knn.tex
proceded discussion

--- 2020-04-30 thesis_template/3_Body/model/knn.tex
@@
 Number of batch controls number and size of batch for each partition. This parameter varies size of intermediate data structures and numeric matrices, and 
-frequency of memory deallocations. Parameter k specifies dimension of feature matrices. This determines size of intermediate data structures and numeric matrices.
+frequency of memory deallocations. 
+The parameter k specifies number of dimension of feature matrices created out of preprocess phase. 
+By controlling this, it determines size of intermediate data structures and numeric matrices.
 
@@
 \label{sec:history}
+Figure~\ref{fig:total}, ~\ref{fig:preprocess}, and ~\ref{fig:query} show the runtime performance of our KNN algorithms in total, preprocess, and query phase respectively. 
+The algorithms used in our experiments are indexed in Table~\ref{tab:algorithm}. We call each algorithm in algorithm number for easy understanding.
+The Algorithm 3 with 20K and 25K dimension, and the Algorithm 1 with 25K dimension whose runtime is showing 0 seconds are algorithms that are terminated during execution due to fail of memory allocation.
+
+Figure~\ref{fig:total} shows Algorithm 8 shows much slower performance compare to the other algorithms.
+Algorithm 7 also starts to slow down as we increase the number of dimension.
+
+As shown in Figure~\ref{fig:preprocess}, the algorithms using Arc is much slower than using deep-copy in preprocessing phase. 
+Algorithm 6 is 38\%  slower than Algorithm 6 in dimension of 25K. 
+In addition, the algorithms with strategy 2 are slower than with strategy 1. 
+For example, Algorithm 6 is about 85\% slower than one Algorithm 2 in dimension of 25K.
+The algorithms with 3 batches are slower that ones with 2 batches.
+Furthermore, as we increase the number of dimension, the number of batch becomes more and more critical to runtime performance of the algorithms with deep-copy.
+The runtime ratios of difference from Algorithm 7 to Algorithm 8 are about 44\%, 28\%, and 39\% for dimension of 15K, 20K, and 25K respectively. 
+However, those from Algorithm 5 to Algorithm 6 are about 11\%, 28\%, and 54\%. The ratios of difference increase proportionally to the number of dimension.
+
+In query phase, Algorithm 8 is much slower than the others in different parameter settings.
+Algorithm 7 starts to slow down as number of dimension is increased.
+
+\begin{table}
+    \renewcommand{\arraystretch}{1.2}
+    \begin{tabular}{|l|l|l|l|}
+    \hline
+    Algorithm number & Method    & Strategy & Number of batch \\ \hline
+    1                & deep-copy & 1        & 2               \\ \hline
+    2                & deep-copy & 1        & 3               \\ \hline
+    3                & arc       & 1        & 2               \\ \hline
+    4                & arc       & 1        & 3               \\ \hline
+    5                & deep-copy & 2        & 2               \\ \hline
+    6                & deep-copy & 2        & 3               \\ \hline
+    7                & arc       & 2        & 2               \\ \hline
+    8                & arc       & 2        & 3               \\ \hline
+    \end{tabular}
+    \caption{Index of Algorithm}
+    \label{tab:algorithm}
+ \end{table}
 
@@
 \end{figure}
+
+\subsection{Discussion}
+\label{sec:history}
+In preprocess phase, the algorithms using Arc method performs worse that one with deep-copy method. 
+This result may seem to contradict to the result of Experiment 4 in Section~\ref{sec:eval_treeagg}.
+In Experiment 4, complex objects, CustomerOwned, are cloned with Arc or deep-copied. 
+In this Experiment 5, we however get Arc or deep-copy of String instead of complex object.
+The result explains deep-copying String is much inexpensive than deep-copying the complex object and 
+actually efficient than using Arc to share String. 
+Therefore, we need to make decision which method to use depending on size and complexity of objects.
+
+In addition, use of different strategies in preprocess phase explains how deallocations of intermediate data structures and drops of their variables impact algorithm's runtime performance.
+The result shows deallocations of intermediate data costs a lot; Algorithm 6 is 85\% slower than Algorithm 2.
+This may be more severe bottleneck for algorithms using Arc; Algorithm 8 is 102\% slower than Algorithm 4.
+This is the same reason explained in Experiment 4. 
+Arc has to check reference count and its atomic operation is expensive.
+
+The impact of number of batch can explain how frequency of memory de/allocation affects runtime performance. 
+Dealing with more number of batch has negative impacts to runtime performance, because it triggers more frequent memory de/allocation.
+In addition, as we increase the number of dimension, the ration of runtime difference among different numbers of batch for the algorithms with deep-copy, but not for ones with Arc.
+This is because algorithm with Arc does not de/allocate memory as much frequent as ones with deep-copy.
+The intermediate datas mealy get reference to String values without actually allocating memory for copied Strings.

### 2020-05-03 thesis_template/3_Body/chapter/evaluation.tex
done evaluation section

@@
 \input{3_Body/model/merge_sort_experiment}
-\
 
@@
 
+\section{Experiment 5: K-Nearest-Neighbors}
+\label{sec:eval_knn}
+\input{3_Body/model/knn}
+
 \section{Summary}
 \label{sec:eval_summary}
+In this chapter, we examines various memory management strategies for different algorithms in Rust programming.
+There are many factors that might differ performance of algorithms: different variable type, Reference Counting, Atomic Reference Counting, and frequency of memory de/allocation.
+We should select the best memory management strategies when developing Big Data processing tools. 
+Some of tips for the development are proved in our experiments. We conclude this dissertation in Chapter~\ref{chapter:Conclusions}.
 

### 2020-05-03 thesis_template/3_Body/model/knn.tex
done evaluation section

@@
 \label{sec:history}
-In preprocess phase, the algorithms using Arc method performs worse that one with deep-copy method. 
+In preprocess phase, the algorithms using Arc method performs worse than ones with deep-copy method. 
 This result may seem to contradict to the result of Experiment 4 in Section~\ref{sec:eval_treeagg}.
@@
 The result explains deep-copying String is much inexpensive than deep-copying the complex object and 
-actually efficient than using Arc to share String. 
+using deep-copy method is actually efficient than using Arc to share String. 
 Therefore, we need to make decision which method to use depending on size and complexity of objects.
@@
 This is because algorithm with Arc does not de/allocate memory as much frequent as ones with deep-copy.
-The intermediate datas mealy get reference to String values without actually allocating memory for copied Strings.
+The intermediate data structures mealy get reference to String values without actually allocating memory for copied Strings.
+
+In query phase, most of our algorithms shows similar runtime performance among the same number of dimension. 
+Why such differences seen in preprocess phase are not shown in query phase? This is because the data structures processed in this phase are numeric matrices and vectors. 
+These data structures do not contain String so that the selection of method parameter does not have direct impact to algorithm's runtime performance.
+
+Furthermore, numeric matrices and vectors are contiguously allocated initializing their size, so they are easy to be de/allocated. 
+The computation needed for these de/allocations is fairly fast. Therefore, setting parameters, such as number of batch and strategy, does not impacts runtime performance.
+
+However, we can see significant degradation in Algorithm 7 with 20K and 25K dimension and Algorithm 8 with 15K, 20K, and 25K dimension. 
+By using strategy 2, we deallocate the numeric matrices and vectors in query phase. However, it is difficult to think that these contiguous memory deallocations cause the degradation. 
+If that is so, Algorithm 5 and 6 should also show some overheads. No page-swapping does not happen during the execution. 
+One possible reason is that these algorithms suffer from the allocation of numeric matrices and vectors due to previous deallocation of intermediate data structures in preprocess phase. 
+The frequent deallocations and low locality of Arc may lead long free-space-list making difficult to search enough spaces to allocate numeric matrices and vectors.
+The other possibility is that the frequent deallocations and low locality of Arc cause cache of numeric matrices and vectors. 
+The computation on these numeric objects may slow down due to their caching levels. 
+To conclude these discussion, we need to conduct more experiments and deeper analysis. 
+However, we push those discussion in next paper.
+
+In a part of conclusion, using Arc to String may be overhead. Considered the result from Experiment 4, we need careful consideration which object to use which strategy, deep-copy and Arc.
+In addition, frequent memory deallocation can lead to slower runtime performance. 
+Therefore, we need to decide when to deallocate unused values taking account of memory capacity.

### 2020-05-03 thesis_template/3_Body/model/access_own_reference_slice.tex
docu
conclusion done

@@
-This experiment is conducted to understand two questions. One is how different variable types have impact to runtime performance.
+This experiment is conducted to provide answers to the following two questions. One is how different variable types have impact to runtime performance.
 The other is how initialization of Vec size has impact to runtime performance. 
@@
 
-Next, 1.5, 1.8, 2.5, 2.8, 3.5, and 3.8 million of Customer objects are created and stored in Vec. 
+Next, 3, 13, 23, 33 million of Customer objects are created and stored in Vec. 
 When a Customer Vec is created, whether size of Vec is initialized is controlled. 
@@
 No matter Vec size initialized or not, differences of runtime for accessing objects are not remarkable among different object types.
-The percent increase in runtime of accessing to fields of from 1.5 to 3.8 million CustomerOwned objects is 121\% if the Vec is initialized, 554\% if the Vec is not initialized.
-
-Considering the differences of percent increase of runtime whether the Vec is initialized or not, 
-Figure\ref{fig:init_vs_noinit} the comparison of runtime access to fields of CustomerOwned object with and without Vec Initialization.
-For 3.8 million of objects, the difference of runtime to access to the objects is 38745 secounds; program without Vec initialization is 60\% slower than one with the initialization.
 
@@
 
-\begin{figure}[htb]
-    \includegraphics[width=15cm]{rust_access_init_vs_noint.eps}
-    \caption{Runtime of Access to Fields of Complex Object with Initialization vs without Initialization}
-    \label{fig:init_vs_noinit}
-\end{figure}
+% \begin{figure}[htb]
+%     \includegraphics[width=15cm]{rust_access_init_vs_noint.eps}
+%     \caption{Runtime of Access to Fields of Complex Object with Initialization vs without Initialization}
+%     \label{fig:init_vs_noinit}
+% \end{figure}
 
@@
 
-Whether initializing Vec size results in disparity of runtime performance to access objects' fields. 
-This is because when Vec uninitialized, the elements of Vec are allocated across different virtual memory pages.
+% Whether initializing Vec size results in disparity of runtime performance to access objects' fields. 
+% This is because when Vec uninitialized, the elements of Vec are allocated across different virtual memory pages.

### 2020-05-03 thesis_template/3_Body/model/experimental_set_detail.tex
conclusion done

@@
  \label{sec:concept_expdetail}
- Our experiments are run on three types of VM instances on Google Cloud Platform: 
- n1-standard-1 which has 1 vCPU, 3.75 GB RAM, and 10 GB Standard persistent disk, 
- n1-standard-4 which has 4 vCPU, 15 GB RAM, and 10 GB Standard persistent disk, 
- n1-standard-8 which has 8 vCPU, 30 GB RAM, and 10 GB Standard persistent disk,  
- All of the experiments described are performed 5 times. 
+ Our experiments are run on VM instances on Google Cloud Platform, 
+ n1-standard-8 which has 8 vCPU, 30 GB RAM, and 10 GB Standard persistent disk.
  In this thesis, we present the average of 5 separate runs for each experiment.

### 2020-05-03 thesis_template/3_Body/model/merge_sort_experiment.tex
conclusion done

@@
 The representations of source vector for each algorithm are shown in Figure~\ref{fig:source_merge_sort}.
-The elements of source vector are CustomerOwned objects. We generates source vectors in size of 1, 2, 3 and 4 million.
+The elements of source vector are CustomerOwned objects. We generates source vectors in size of 4, 8, 12 and 16 million.
 Finally, merge-sort is performed based on value of key field. The figure shows the result for runtime performance of merge-sort algorithms on difference size of vectors.
-This experiment is run on n1-standard-4 and generates 4 threads to perform multithreading.
 
@@
 The blue and yellow bar charts represent the runtime performance of merge-sort algorithm using reference and Arc respectively. 
-The result says that algorithms with Arc is about 24\% slower than algorithms with reference.
+The result says that algorithms with Arc is about 21\% slower than algorithms with reference.
 

### 2020-05-03 thesis_template/3_Body/model/tree_aggregate_experiment.tex
conclusion done

@@
 
-Numbers of CustomerOwned objects aggregated in our experiment are 1, 2, 3, 4 million. 
-This experiment is run on n1-standard-4.
+Numbers of CustomerOwned objects aggregated in our experiment are 2, 4, 6, 8 million.
 
@@
 Figure~\ref{fig:ex_tree_agg} shows runtime performance of two tree-aggregate algorithms. 
-The runtime of algorithm with deep-copy is about 33\% slower than algorithm with Arc for every vector size.
+The runtime of algorithm with deep-copy is about 40 to 50\% slower than algorithm with Arc for every vector size.
 

### 2020-05-03 thesis_template/4_Conclusion/conclusion.tex
conclusion done

@@
 
-\section{Summary of the thesis}
+% Quick recap of what we did 
+% - The purpose of this research
+% - Experiment that we conducted
+In this thesis, we have presented a number of experiments to assess better implementation of algorithms 
+when one develops Big Data analysis tools with Rust programming. 
+Those experiments examine how different variable types, Reference Count (Rc), and different memory management strategies in Rust affect performance of algorithms.
 
-Time to get philosophical and wordy.
+% What we find 
+% - The result of our experiments
+The results show useful benchmark when one implements Big Data analysis tools.
+The different variable types in Rust have similar access time to the memory address of their value. 
+Therefore, we do not need to consider such access overheads. 
+The drop on Rc or Arc is more expensive than ordinal variables, 
+because these shared variables need to check count of reference to its actual value. 
+The atomic operation used by Arc may be a cause of overhead in multithread programming in Rust.
 
-IMPORTANT: In the references at the end of thesis, all journal names must be
-spelled out in full, except for standard abbreviations like IEEE, ACM, SPIE,
-INFOCOM, ...
+% What is the most significant
+% - Use of Reference is depending on Complex object type
+% - When we have complex object, we should use Reference count
+% - Frequency of memory de/allocation has impact
+One of the most notable discussion is selection of whether developers should use sharing (Rc or Arc) or deep-copy. 
+In algorithms used to process Big Data, the same elements are used over and over agin. 
+In Experiment 4 and 5, we implement the algorithms in different strategies and assess which implementations performs better in runtime.
+The result is that the algorithms sharing elements using Arc is more efficient strategy when the shared elements are very complex objects. 
+On the other hand, when the elements have light complexity, such as String, the algorithms deep-copying the elements is more faster.
+Therefore, the decision of which strategy to use is dependent on how complex element objects are.
+
+% Conclusion acquired from that
+% - the design of algorithm is depend on implemetation of complex objects
+% - Rust ownership memory management seem to work well
+% - We can manually de/allocate memory and compiler can still ensure memory safety.
+The other important discussion is how Rust ownership memory management can impact performance of algorithm.
+Even though the main concept of ownership is safety of memory, programming patterns using this ownership may determine the frequency and timing of de/allocation. 
+Experiment 5 shows the ownership memory management works well; the frequency and timing of de/allocation is fairly reasonable for algorithms to result good runtime performance and memory usage. 
+However, when the situation is memory intensive and needs more fast runtime performance, developers need to perform more careful memory managements,such as manually specifying when to deallocate memory.
+Rust can check memory-safety of these manual operation at compile time, so such optimizations can be done fairly easy.
+
+% How our conclusion can be applied in real world 
+% - Decide data structure implementation that used in Big Data Systems then
+% conduct experiment that fits for the best runtime performance.
+As we can see in the results of experiment, different memory strategy varies the performance of algorithms in Rust programming.
+Which memory management strategy to take depends on what objects to deal with. 
+Therefore, development of Big Data analysis tools in Rust programming should be started with objects implementation used in the systems.
+Next, one can select suitable memory management strategies. 
+Finally, algorithms can be optimized with more dedicated strategies to application setting, such as capacity of memory.

### 2020-05-04 thesis_template/0_Prelim/ack.tex
ready to review

Foremost, I would like to show my appreciation to my advisor Prof. Kia Teymourian for his guidance, encouragement and support.
His expertise and insights were essential for this research work. His passion for research and education motivates me and push this thesis to be a precious work for me.

I am especially thankful to Prof. Eugene Pinsky for accepting reviewing of this thesis. 
I also thank Prof. Reza Rawassizadeh for review and advice on this thesis.

Finally, I would like to express special thanks to my parents to support this excellent educational opportunity.

\vskip 1in

\noindent
Janusz Konrad\\
Professor\\
ECE Department

### 2020-05-04 thesis_template/1_Intro/intro.tex
ready to review

@@
 Multiple cluster computing analysis tools have been developed, such as Hadoop MapReduce \cite{ApacheHadoopHomePage}, 
-Apache Spark \cite{ApacheSparkHomePage}, and Apache Flink \cite{ApacheFlinkHomePage}. 
+Apache Spark \cite{ApacheSparkHomePage}, and Apache Flink \cite{ApacheFlinkHomePage} \cite{DBLP:journals/debu/CarboneKEMHT15}. 
 These tools have brought reliable and scalable ways to deal massive data. 

### 2020-05-04 thesis_template/2_RelatedWork/model/linalg.tex
ready to review

@@
 
-The original BLAS and LAPACK are written in Fortran90. Linear algebra library used for Spark is netlib-java, which is a Java wrapper library for Netlib, C API of BLAS and LAPACK. 
-The reason why the developers addressed to use this package is that the BLAS and LAPACK are already bug free and implementing linear algebra library from scratch can usually buggy.
-
-However, the main advantage of use of BLAS and LAPACK is system optimized implementation. So if we implement original Fortran linear algebra library, it cannot perform as well as BLAS and LAPACK. 
-And the performance would not be such different from one of implementation in Java or Rust.  If we want to test only memory management between Rust and Java, 
-it can be enough implementation of linear algebra operation from  pure Java and Rust sacrificing the best performance taking advantage of system optimization.
-
 \subsection{Netlib-Java}
@@
 Netlib-java is a Java wrapper of BLAS, LAPACK, and ARPACK. Netlib-java choose  implementation of linear algebra depending on installation of the libraries. 
-First, if we have installed machine optimised system libraries, such as Intel MKL and OpenBLAS, netlib-java will use these as the implementation to use. 
+First, if we have installed machine optimized system libraries, such as Intel MKL and OpenBLAS, netlib-java will use these as the implementation to use. 
 Next, it try to load netlib references which netlib-java use CBLAS and LAPCKE interface to perform BLAS and LAPACK native call. 
@@
 
-Matrix operation is a fundamental part of machine learning. Apache Spark provides implementation for distributed and local matrix operation. 
+Matrix operation is a fundamental part of machine learning. Apache Spark provides implementation for distributed and local matrix operation \cite{DBLP:conf/kdd/ZadehMUYPVSSZ16}. 
 To translate single-node algorithms to run on a distributed cluster, Spark addresses separating matrix operations from vector operations and run matrix operations on the cluster, 
@@
 
-ND4J has two types of  its own memory management methods, GC to pointer of off-heap NDArray, and MemoryWorkspaces. 
+ND4J \cite{nd4j} has two types of  its own memory management methods, GC to pointer of off-heap NDArray, and MemoryWorkspaces. 
 ND4J used off-heap memory to store NDArrats, to provide better performance while working with NDArrays from vative code such as BLAS and CUDA libraries. 

### 2020-05-04 thesis_template/2_RelatedWork/model/os.tex
ready to review

@@
 \label{sec:os_mem_process}
-A process is a subsection of computation job. A process can work on a CPU core. We can divide process as well.
+A process is a subsection of computation job. A process can work on a CPU core, we can divide process as well.
 Basically, each process does not share their memory. However, for multiprocessing, we could avoid this restriction.
@@
 
-\subsection{Copy on Page}
-\label{sec:os_copypage}
-When a parent process creates child process and if these process shares contents on particular page and modify it, 
-only the page which has the context will be copied.
+% \subsection{Copy on Page}
+% \label{sec:os_copypage}
+% When a parent process creates child process and if these process shares contents on particular page and modify it, 
+% only the page which has the context will be copied.
 

### 2020-05-05 thesis_template/0_Prelim/abs.tex
revise untill intro

--- 2020-02-28 thesis_template/0_Prelim/abs.tex
@@
 
-Existing big data processing tools are developed on A
+% Motivation 
+% - Faster computation and  saving computer resource is important 
+% - introduce Big Data tool can be improve
+% Problem description
+% - introduce Spark, MapReduce is implemented in Application Language.
+% - some problems
+% Concept 
+% - use of rust 
+% - what is core concept of experiment
+% Evaluation
+% - how to evaluate that
+% - some notable result
+
+Planning optimized memory management is critical for Big Data analysis tools to perform faster runtime and efficient use of computation resources.
+Modern Big Data analysis tools are developed with application languages that abstract their memory management, so that developers do not have to pay extreme attention to memory management strategies.
+
+Many existing Big Data processing tools are developed on Java Virtual Machine (JVM). 
+Memory strategies in JVM, such as Garbage Collection (GC), may lead significant overhead in Big Data processing. 
+Apache Spark and Apache Flink use complex objects to manipulate and transfer tremendous amount of data. 
+Generating many of these complex objects in memory forces GC to rearrange the objects in memory frequently waisting computation.
+
+Considered the problems in memory management in JVM, developing Big Data processing tools with system languages can be the solution.
+By using a system language, a developer has control on memory management, so that one can implement systems with better optimized memory management strategies.
+We selects Rust as good candidate for development of Big Data processing tools, due to its ability to write memory-safe and fearless concurrent codes with its concept of ownership.
+
+There may be many possible strategies to optimize memory management for Big Data processing in Rust programming: 
+selection of different variable types, use of Reference Counting, and multithreading with Atomic Reference Counting.
+We conduct several experiments to assess how much these different memory management strategies differ runtime performance of algorithms.
+
+Our experiments focus complex object manipulation and common algorithms for Big Data processing with various memory management.
+The results show significant difference among the algorithms using these different memory strategies.

### 2020-05-05 thesis_template/1_Intro/intro.tex
revise untill intro

@@
 \label{sec:motivation}
-Importance of cluster computing tool for Big Data Analysis has been increasing as amount, value, use of data has increased. 
+Cluster computing tool for Big Data Analysis has been more important as magnitude and quality of data that we can obtain increases. 
 Recently, almost all businesses stand on data, from web marketing analysis to factory automations. The leverage of data is ubiquitous, because 
@@
 
-However these technologies do not come for free; we need to pay money for use of these resources. Usually, user needs to pay depending on use of computational resources. 
+However these computation resources do not come for free; we need to pay money to use these resources. Usually, user needs to pay depending on usage of computational resources. 
 If your process of data analysis is too long or need to use number of clusters with high speck specification, the cost may end up significantly hight.
@@
 Since the design of the language is different from any other programming languages, implementations that can be selected for algorithms can differ from existing ones.
-In this dissertation, we focus on memory management strategy for Big Data processing algorithms in development with Rust.
+In this thesis, we focus on memory management strategy for Big Data processing algorithms in development with Rust.
 
@@
 
-Many of popular open source cluster computing frameworks for large scale data analysis, 
-such as Hadoop and Spark, allow programmers to define objects in a host languages, such as Java.
-The objects are then managed in RAM by the language and its runtime, Java Virtual Machine 
-in the case of Java and Scala. Storing objects in memory enables machine to process iterative computation. 
-One of the fundamental tasks for recent big data analysis is analysis using Machine Learning Algorithms, 
-which require iterative process. As the amount of data increases, memory is required to keep many objects. 
-Therefore, memory management plays a critical role in this task.
+% Many of popular open source cluster computing frameworks for large scale data analysis, 
+% such as Hadoop and Spark, allow programmers to define objects in a host languages, such as Java.
+% The objects are then managed in RAM by the language and its runtime, Java Virtual Machine 
+% in the case of Java and Scala. Storing objects in memory enables machine to process iterative computation. 
+% One of the fundamental tasks for recent big data analysis is analysis using Machine Learning Algorithms, 
+% which require iterative process. As the amount of data increases, memory is required to keep many objects. 
+% Therefore, memory management plays a critical role in this task.
 
-One of the memory management tool on JVM is garbage collection. 
-The garbage collection brings a significant advantage for programmers by removing responsibility
-for planning memory management by themselves manually. Instead, JVM monitors the state of memory and performs garbage
-collection at certain points. However, these monitoring and auto-execution of garbage collection cost additional 
-computation and might consume computation resources which should be used for data processing. This can significantly decrease performance of the computation.
+% One of the memory management tool on JVM is garbage collection. 
+% The garbage collection brings a significant advantage for programmers by removing responsibility
+% for planning memory management by themselves manually. Instead, JVM monitors the state of memory and performs garbage
+% collection at certain points. However, these monitoring and auto-execution of garbage collection cost additional 
+% computation and might consume computation resources which should be used for data processing. This can significantly decrease performance of the computation.
 
-In contrast, memory management in system language, such as C++, relies on programmers’ decision for when to allocate and deallocate memory. 
-The functions, malloc/free consume most of the memory management. Proper implementation of system language for big data processing can be overperform the implementation in host language.
-Nevertheless, implementing C++ performing proper memory management and guaranteeing security can be unproductive and complicated.
+% In contrast, memory management in system language, such as C++, relies on programmers’ decision for when to allocate and deallocate memory. 
+% The functions, malloc/free consume most of the memory management. Proper implementation of system language for big data processing can be overperform the implementation in host language.
+% Nevertheless, implementing C++ performing proper memory management and guaranteeing security can be unproductive and complicated.
 
-Considering the issue of memory management, we introduces solution based on unique memory management methods implemented in Rust, ownership , move and borrowing.
-This unique concepts in Rust secure codes and perform memory management without monitoring memory. 
-Since developer can select variety of memory management strategies to implement Big Data processing algorithms in Rust.
-We develop such algorithms with different strategies and compare their runtime performance to study the best algorithm implementation.
+Even though Rust can be a great candidate to develop Big Data processing tools, there are few study for development on such tools with Rust programming.
+
+Rust has various ways to manage memory. Rust has different variable types for values allocated in sequence of memory region. 
+Each variables take different memory representation that can produce variation of operation time on the variable types.
+
+In addition, Reference Counting takes important role in Rust ownership concept. By using Reference Counting, a value is able to have multiple owners.
+This situation may happen quite often, when we want to acquire complex values from contiguous memory regions. 
+Reference Counting has both advantage and disadvantage. 
+Reference count can share data which might decrease unnecessary copy of data, but checking reference count might be a overhead.
+
+Atomic Reference Counting is ubiquitous in Rust multithreading program. Atomic Reference Count also has similar features to Reference Counting. 
+In addition, it is allowed to use among different threads. This may lead additional overhead from atomic operation.
+
+As we can see, we can choose various memory management strategies in Rust programming.
+Therefore, we assess following research question in this thesis.
+\begin{itemize}
+    \item What are better memory management strategies for complex object processing to perform faster runtime performance.
+    \item How much impact do different variable types in Rust have in order to algorithms' runtime performance?
+    \item How much can algorithms runtime be improved or degraded, if we use Reference Count?
+    \item What are better memory management strategies for faster Big Data processing in Rust multithreading?
+    \item How can we improve runtime performance of common Big Data algorithms by Rust memory management?
+\end{itemize}
+
+To answer these question, we conduct 5 experiments.

### 2020-05-05 thesis_template/2_RelatedWork/model/intro.tex
revise untill intro

@@
-This chapter describes background knowledge that we have studied for our research.
+This chapter describes the related work and concepts to our research in this thesis. 
 In Section~\ref{sec:os}, some of topics in Operating Systems are described focusing on memory management in operating systems.
 Knowledge of operating systems helps us to understand how operating systems handle memory management and 
-how other technologies takes advantage of them. Even though this dissertation does not focus technologies used for Linear Algebra Computation, 
+how other technologies takes advantage of them. Even though this thesis does not focus technologies used for Linear Algebra Computation, 
 there are some active researches in technologies in Linear Algebra Computation for Big Data processing. 

### 2020-05-06 thesis_template/2_RelatedWork/model/gctuning.tex
need object size and conclusion documentation

--- 2020-04-22 thesis_template/2_RelatedWork/model/spark.tex
@@
-\subsection{Resilient Distributed Datasets}
-Major methods in Spark are Resilient Distributed Datasets (RDDs), a data structure that abstracts distributed memory across different clusters. 
-The immutable coarse-grained transformation, spark-scheduler with lazy-evaluation, and memory management with cacheing achieve computation with fault-tolerance, 
-fast execution, and moderate control on memory efficiency \cite{DBLP:conf/nsdi/ZahariaCDDMMFSS12}.
-
-A RDD is essentially a multi-layer Java data structure. A top RDD object references Java array, which intern, references a set of tuple objects. 
-The coarse-grained transformations and immutability requires a RDD to be deep-copied to produce a new RDD, but efficiently offers fault tolerance. 
-The lost partitions of a RDD can be recomputed in parallel on different nodes rather than rolling back the whole program.
-
-Spark-pipeline consists of sequence of transformations and actions over RDDs. A transformation produces a new RDD from a set of existing RDD. 
-An action is method that computes statistics from an RDD. Due to lazy-evaluation nature, transformations do not materialize the newly created RDD. 
-Instead, RDD Lineages are created. Lineage is a graph among parent and child RDDs which represents logical execution plan. 
-This enhance fault-tolerance and improve ability to optimize execution plan.
-
-RDDs can be cached in memory for faster access by persist method. Developers can specify a storage level for a persisted RDD, in memory with serialized or deserialized, or on disk. 
-Other than persisted RDD, Spark generates a lot of intermediate RDDs during execution. Since RDD is a Java object, they are managed by Garbage Collection (GC) in the JVM. 
-However, persisted RDDs are never collected by GC. This GC might cause significant deterioration of performance of Spark, because GC shows heavy overhead when there are a number of objects.
-
-\subsection{Memory Management in Spark}
-Spark framework allocates multiple executors, JVMs, that run sequence of transformations and actions. As we describe the previous section, data in Spark is mainly stored as Java objects in memory, 
-so that they are allocated on JVM heap and managed by JVM Garbage Collection.
-The data may form three types \cite{DBLP:journals/pvldb/XuGDWW19}: Cached data, Shuffled data, and Operator-generated data.
-
-Spark can cache data in memory to reduce disk I/O. This Cached data usually long-lived Java objects and span multiple stages in Spark-pipeline. 
-Spark allocates a logical storage space to store the cached data as shown in Figure. After aggregation, Spark generates Shuffled data. Shuffled data is usually long-lived, 
-because it need to be kept in memory until the task ends. Spark allocates execution space to store Shuffled data.
-The storage space and execution space spans 60 \% of JVM heap space in default.
-Operator-generated data is data generated by user-defined operations.
-Since Operator-generated data may or may not be used,
-after the operation finish, the data object can be both short-lived or long-lived objects. These are stored in user space allocated on default 40 \% of JVM heap.
-
-All data of these types on JVM heap is managed by JVM GC. GC check references graph of objects, mark whether the objects are used and deallocate memory space occupied by unused objects. 
-There are three popular GCs: Parallel, CMS and G1. All of these method track generation of object based on the region of memory. 
-The Java logical heap structure is shown in Figure~\ref{fig:javaheap}.
-As the figure shows, Java logical heap can be separated into three main parts where store objects for each corresponding generation:
-permanent generation, young generation, and old generation. The region for permanent generation stores metadata required by JVM to describe 
-class and method used in application which will be permanently lived on the region of memory. The overview of Java GC is shown in Figure~\ref{fig:javagc}. 
-The outer box represents region for particular generation. The inner box and the number represents object and its age in GC.
-
-The region for young generation mainly consists of two parts: Eden and Survivor space. 
-First, Java objects are created in Eden space and promoted to Survivor space when survive from GC. 
-After objects survive several GCs in Survivor space, they are finally promoted to old generation.
-
-In region of old generation, JVM lunches multi-thread to perform GC. GC with multi-threading suffers from Stop-The-World (STW) pauses; 
-GC may suspend application threads while performing object marking and deallocation. 
-Different GC algorithms try to solve this problem with trade-off between GC frequency and memory utilization.
-
-Because of the problem of STW and copying objects to different physical memory pages , JVM GC cause huge overhead when number of objects is large. 
-Therefore, GC become severe issue in Big Data processing where might produce significant number of object.
-
-\begin{figure}[htb]
-    \includegraphics[width=15cm]{java_heap.eps}
-    \caption{Java Heap Structure}
-    \label{fig:javaheap}
-\end{figure}
-
-\begin{figure}[htb]
-    \includegraphics[width=15cm]{java_gc.eps}
-    \caption{Java Garbage Collection}
-    \label{fig:javagc}
-\end{figure}
-
-\subsection{Garbage Collection Tuning}
 There are many different ways that one can improve the performance of GC in Java. One of these is for example avoiding pointer-based data structures, such as HashMap and LinkedList. 

### 2020-05-06 thesis_template/2_RelatedWork/model/linalg.tex
need object size and conclusion documentation

@@
 
-Basic Linear Algebra Subprograms (BLAS) are standard building blocks for basic vector and matrix operations. There are 3 levels of operation. The level 1 BLAS performs scalar, 
+Basic Linear Algebra Subprograms (BLAS) \cite{DBLP:journals/toms/LawsonHKK79} are standard building blocks for basic vector and matrix operations.
+There are 3 levels of operation.
+The level 1 BLAS performs scalar,
 vector and vector-vector operations, the level 2 BLAS performs matrix-vector operation, and the level 3 BLAS performs matrix-matrix operation.
 
-LAPACK is developed on BLAS and has advanced functionalities such as LU decomposition and Singular Value Decomposition (SVD). Dense and banded matrices are handled, but not general 
-sparse matrices. The initial motivation of development of LAPACK was to make the widely used EISPACK and LINPACK libraries run efficiently on shared-memory vector and parallel processors. 
+LAPACK \cite{laug} is developed on BLAS and has advanced functionalities such as LU decomposition and Singular Value Decomposition (SVD). Dense and banded matrices are handled, but not general 
+sparse matrices.
+The initial motivation of development of LAPACK was to make the widely used EISPACK \cite{DBLP:books/sp/SmithB76} and LINPACK \cite{DBLP:journals/sigarch/Dongarra92} libraries run efficiently on shared-memory vector and parallel processors.
 LINPACK and EISPACK are inefficient because their memory access patterns disregard the multi-layered memory hierarchies of the machines, thereby spending too much time moving data. 
@@
 
-ARPACK is also a collection of linear algebra subroutines which is designed to compute a few eigenvalues and corresponding eigenvectors from large scale matrix. 
+ARPACK \cite{DBLP:books/daglib/0000896} is also a collection of linear algebra subroutines which is designed to compute a few eigenvalues and corresponding eigenvectors from large scale matrix. 
 ARPACK is based upon an algorithmic variant of the Arnoldi process called the Implicitly Restarted Arnoldi Method (IRAM). 
@@
 \label{sec:linalg_netlib}
-
-Netlib-java is a Java wrapper of BLAS, LAPACK, and ARPACK. Netlib-java choose  implementation of linear algebra depending on installation of the libraries. 
+Netlib-java \cite{netlib} is a Java wrapper of BLAS, LAPACK, and ARPACK. Netlib-java choose  implementation of linear algebra depending on installation of the libraries. 
 First, if we have installed machine optimized system libraries, such as Intel MKL and OpenBLAS, netlib-java will use these as the implementation to use. 

### 2020-05-06 thesis_template/2_RelatedWork/model/spark.tex
ready to review
need object size and conclusion documentation

@@
 so that they are allocated on JVM heap and managed by JVM Garbage Collection.
-The data may form three types \cite{DBLP:journals/pvldb/XuGDWW19}: Cached data, Shuffled data, and Operator-generated data.
+The data may form three types \cite{DBLP:journals/pvldb/XuGDWW19} \cite{DBLP:conf/pldi/WangCCZVML0X19}: Cached data, Shuffled data, and Operator-generated data.
 
@@
 \end{figure}
-
-\subsection{Garbage Collection Tuning}
-There are many different ways that one can improve the performance of GC in Java. One of these is for example avoiding pointer-based data structures, such as HashMap and LinkedList. 
-These objects have a "wrapper" object for each entry so that number of object tends to be larger than when when an array is used.
-
-Caching serialized object in memory also reduce number of object and memory usage since the set of objects become a byte or binary array. 
-Spark SQL applications use DataFrames\cite{DBLP:conf/sigmod/ArmbrustXLHLBMK15}, 
-whose intermediate data are managed by an optimized memory manager named Tungsten.
-Tungsten stores the intermediate data in a serialized binary form and performs aggregation functions directly on he serialized objects.
-Therefore, the number of Java objects in memory is reduced and it reduces the DC frequency and object marking/sweeping.
-
-In addition, developers can allocate data off-heap of JVM to avoid tracking by GC. 
-Facade\cite{DBLP:conf/asplos/NguyenWBFHX15} proposed a compiler and runtime system to bound the number of in-memory data objects, through storing data in an off-heap region and 
-manipulating the data with control interfaces.
-
-Although these memory management solution for GC help developer improve performance of Spark applications, 
-the effort to discover the best GC tuning afflicts developers.

### 2020-05-06 thesis_template/3_Body/chapter/evaluation.tex
done
revise untill intro
need object size and conclusion documentation

@@
 \label{sec:eval_intro}
-In this chapter, detail setting, result, and analysis of our experiments are discussed.
+In this chapter, detail experiment settings, executions and results are discussed.
 Section~\ref{sec:eval_setdetail} details hardware configurations and data set we use. 
@@
 
-\section{Experiment 2: Merge-sort}
+\section{Experiment 3: Merge-sort}
 \label{sec:eval_sort}
@@
 We should select the best memory management strategies when developing Big Data processing tools. 
-Some of tips for the development are proved in our experiments. We conclude this dissertation in Chapter~\ref{chapter:Conclusions}.
+Some of tips for the development are proved in our experiments. We conclude this thesis in Chapter~\ref{chapter:Conclusions}.
 

### 2020-05-06 thesis_template/3_Body/model/experimental_set_detail.tex
need object size and conclusion documentation

@@
+We have used two different data sets. One is a real-world data set, Wikipedia page data set,
+and another is a syntactic randomized generated data set based on Complex object described in Section~\ref{sec:concept_compobj}. 
+We use one machine with particular specification.
 \subsection{Wikipedia Data Sets}
@@
  Wikipedia page data sets are used to perform document classification with KNN. 
+ We have separated the data set into training and test data set, 
  \(10^5\) pages are used for training data set, and 18724 pages are used for target.
@@
  \label{sec:concept_expdetail}
- Our experiments are run on VM instances on Google Cloud Platform, 
+ All experiments are run on VM instances on Google Cloud Platform, 
  n1-standard-8 which has 8 vCPU, 30 GB RAM, and 10 GB Standard persistent disk.
- In this thesis, we present the average of 5 separate runs for each experiment.
+ In this thesis, we present the result of runtime as the average of 5 separate runs for each experiment.

### 2020-05-06 thesis_template/3_Body/model/knn.tex
need object size and conclusion documentation

@@
 The algorithms have 4 phase; load, preprocess, query, and combine phase. 
+Before these phase, we separate data sets into 8 partitions to run these in different threads. 
 The algorithms spawn threads at the beginning ,and in the load phase partition of files are loaded in each threads. 
@@
     Strategy        & \multicolumn{4}{l|}{\begin{tabular}[c]{@{}l@{}}1: keep intermediate objects in memory until owner is changed\\ 2: remove intermediate objects as soon as it is not needed\end{tabular}}                                    \\ \hline
-    Number of batch & \multicolumn{4}{l|}{\begin{tabular}[c]{@{}l@{}}2: generate 2 batch from each partition\\ 3: generate 3 batch from each partition\end{tabular}}                                                                             \\ \hline
+    Number of batch & \multicolumn{4}{l|}{\begin{tabular}[c]{@{}l@{}}2: generate 2 batches from each partition\\ 3: generate 3 batches from each partition\end{tabular}}                                                                             \\ \hline
     k               & \multicolumn{4}{l|}{\begin{tabular}[c]{@{}l@{}}15K: dimension of feature matrices is 15 thousands \\ 20K: dimension of feature matrices is 20 thousands\\ 25K: dimension of feature matrices is 25 thousands\end{tabular}} \\ \hline
@@
 frequency of memory deallocations. 
+The size of each batch is defined in 6250 pages when we have 2 batches, and 4166 or 4167 when we have 3 batches. 
 The parameter k specifies number of dimension of feature matrices created out of preprocess phase. 
@@
 
-The impact of number of batch can explain how frequency of memory de/allocation affects runtime performance. 
-Dealing with more number of batch has negative impacts to runtime performance, because it triggers more frequent memory de/allocation.
+The impact of batch number can explain how frequency of memory de/allocation affects runtime performance. 
+Dealing with more number of batch has negative impacts on runtime performance because it triggers more frequent memory de/allocation.
 In addition, as we increase the number of dimension, the ration of runtime difference among different numbers of batch for the algorithms with deep-copy, but not for ones with Arc.

### 2020-05-06 thesis_template/3_Body/model/merge_sort_experiment.tex
need object size and conclusion documentation

@@
-As explained in last experiment, deletion of Rc has significant overhead than normal reference. 
+Sorting algorithm like merge-sort is a very ubiquitous algorithm in any computation. 
+Especially in Big Data processing, merge-sort algorithm de/allocates contiguous memory for partitions of sorted vector multiple times.
+We are interested in memory de/allocation pattern in merge-sort algorithm, because it generates many intermediate data structures and delete them many times.
+
+As explained in Experiment 2 in Section~\ref{sec:eval_refcount}, deletion of Rc has significant overhead than normal reference. 
 By learning this result, our assumption here is that deletion of Arc has also overhead when we compare to normal reference. 

### 2020-05-08 thesis_template/4_Conclusion/conclusion.tex
conclusion done

--- 2019-10-17 thesis_template/4_Conclusion/conclusion.tex
@@
 
-\section{Summary of the thesis}
+% Quick recap of what we did 
+% - The purpose of this research
+% - Experiment that we conducted
+In this thesis, we have presented a number of experiments to assess better implementation of algorithms 
+when one develops Big Data analysis tools with Rust programming.
 
-Time to get philosophical and wordy.
+Difference of variable types does not have impact on operation to access memory address where a value is located. 
+This result gives us freedom of choices for variable types to construct complex objects in terms of runtime performance. 
+When we however use borrowed types, such as references and slices, their lifetime should be explicitly defined. 
+Therefore, we may use owner type variables to construct construct complex objects in order to facilitate lifetime tracking.
 
-IMPORTANT: In the references at the end of thesis, all journal names must be
-spelled out in full, except for standard abbreviations like IEEE, ACM, SPIE,
-INFOCOM, ...
+Runtime to drop Rc is much 60 times slower than normal reference. This is because Rc needs to check reference count to determine whether to deallocate its value. 
+This result may say that we should use normal reference whenever it is possible. 
+Again, tracking lifetime of references used in complex objects can be cumbersome. 
+Choice of Rc and reference is dependent on complexity of object implemented.
+
+In Rust, we can implement multithread programming with sharing data using Arc. In simple multithread algorithms, 
+one can write code where shares data with Arc and simple reference among different threads.
+Merge-sort algorithms sharing data with Arc is 21\% slower than normal reference. 
+In this situation, sharing data with normal reference require relatively easy lifetime tracking, 
+so we should use normal reference to share data among different thread whenever it is possible.
+
+For more complex algorithms, like tree-aggregate and preprocess phase in KNN, one can implement algorithms sharing data with Arc or simply deep-copy the values.
+The algorithms with deep-copy is about 40 to 50\% slower than the algorithm with Arc for complex objects.
+When we however deal with String, the algorithms with deep-copy is faster than Arc. 
+Therefore, the decision which to use deep-copy or Arc method should be determined based on complexity of objects.
+
+Decreasing frequency of memory de/allocation may be an effective solution to improve runtime performance of Big Data processing algorithms. 
+There is a trade-off between memory usage and frequency of memory de/allocation. 
+That is why developers should conduct careful analysis of algorithms' memory usage pattern and timing of memory de/allocation.
+
+As we can see in the results of experiment, different memory strategy varies the performance of algorithms in Rust programming.
+Which memory management strategy to take depends on what objects to deal with. 
+Therefore, development of Big Data analysis tools in Rust programming should be started with objects implementation used in the systems.
+Next, one can select suitable memory management strategies. 
+Finally, algorithms can be optimized with more dedicated strategies to application setting, such as capacity of memory.

### 2020-05-10 thesis_template/3_Body/model/drop_ref_rc.tex
conclusion done
done

@@
 Therefore, the evaluated runtime of dropping objects only consists of dropping time of reference or Rc, but deallocation time.
-We generated 1, 1.5, 2, 2.5, 3, 3.5 million of CustomerBorrowed and CustomerRc objects and performed drop one by one.
+We generated 10, 20, 30, and 40 million of CustomerBorrowed and CustomerRc objects and performed drop one by one.
 
@@
 The runtime of dropping CustomerBorrowed is about 60 times faster than dropping CustomerRc. 
+The memory usage for algorithms with 40 million of Customer objects are about 26G bytes for both CustomerRc and CustomerBorrowed.
 

### 2020-05-10 thesis_template/0_Prelim/abs.tex
abstract done

@@
 Planning optimized memory management is critical for Big Data analysis tools to perform faster runtime and efficient use of computation resources.
-Modern Big Data analysis tools are developed with application languages that abstract their memory management, so that developers do not have to pay extreme attention to memory management strategies.
+Modern Big Data analysis tools use application languages that abstract their memory management so that developers do not have to pay extreme attention to memory management strategies.
 
-Many existing Big Data processing tools are developed on Java Virtual Machine (JVM). 
-Memory strategies in JVM, such as Garbage Collection (GC), may lead significant overhead in Big Data processing. 
-Apache Spark and Apache Flink use complex objects to manipulate and transfer tremendous amount of data. 
+Many existing Big Data processing tools use Java Virtual Machine (JVM). 
+Memory strategies in JVM, such as Garbage Collection (GC), may lead to significant overhead in Big Data processing. 
+Apache Spark and Apache Flink use complex objects to manipulate and transfer a tremendous amount of data. 
 Generating many of these complex objects in memory forces GC to rearrange the objects in memory frequently waisting computation.
 
-Considered the problems in memory management in JVM, developing Big Data processing tools with system languages can be the solution.
-By using a system language, a developer has control on memory management, so that one can implement systems with better optimized memory management strategies.
-We selects Rust as good candidate for development of Big Data processing tools, due to its ability to write memory-safe and fearless concurrent codes with its concept of ownership.
+Considered problems in memory management in JVM, developing Big Data processing tools with system languages can be the solution.
+By using a system language, a developer has control on the memory management. Therefore, one can implement systems with more optimized memory management strategies.
+We selectRust as a good candidate for the development of Big Data processing tools, due to its ability to write memory-safe and fearless concurrent codes with its concept of ownership.
 
@@
 
-Our experiments focus complex object manipulation and common algorithms for Big Data processing with various memory management.
-The results show significant difference among the algorithms using these different memory strategies.
+Our experiments focus complex object manipulation and common Big Data processing with various memory management.
+The results show significant different runtime hits among these different memory strategies.

### 2020-05-10 thesis_template/0_Prelim/abs.tex
abstract done

@@
 
-Many existing Big Data processing tools use Java Virtual Machine (JVM). 
+Many existing dataflow tools use Java Virtual Machine (JVM). 
 Memory strategies in JVM, such as Garbage Collection (GC), may lead to significant overhead in Big Data processing. 
@@
 By using a system language, a developer has control on the memory management. Therefore, one can implement systems with more optimized memory management strategies.
-We selectRust as a good candidate for the development of Big Data processing tools, due to its ability to write memory-safe and fearless concurrent codes with its concept of ownership.
+We select Rust as a good candidate for the development of Big Data processing tools, due to its ability to write memory-safe and fearless concurrent codes with its concept of ownership.
 
@@
 selection of different variable types, use of Reference Counting, and multithreading with Atomic Reference Counting.
-We conduct several experiments to assess how much these different memory management strategies differ runtime performance of algorithms.
+We conduct several experiments to assess how much these different memory management strategies differ runtime performance.
 

### 2020-05-11 thesis_template/0_Prelim/abs.tex
updated Abstract

@@
 
-Planning optimized memory management is critical for Big Data analysis tools to perform faster runtime and efficient use of computation resources.
-Modern Big Data analysis tools use application languages that abstract their memory management so that developers do not have to pay extreme attention to memory management strategies.
+Planning optimized memory management is critical for Big Data analysis tools to
+perform faster runtime and efficient use of computation resources.
+Modern Big Data analysis tools use application languages that abstract their
+memory management so that developers do not have to pay extreme attention
+to memory management strategies.
 
-Many existing dataflow tools use Java Virtual Machine (JVM). 
-Memory strategies in JVM, such as Garbage Collection (GC), may lead to significant overhead in Big Data processing. 
-Apache Spark and Apache Flink use complex objects to manipulate and transfer a tremendous amount of data. 
-Generating many of these complex objects in memory forces GC to rearrange the objects in memory frequently waisting computation.
+Many existing modern cloud-based data processing systems such as Hadoop, Spark or Flink use
+Java Virtual Machine (JVM) and taking full advantage of features such as automated memory management in JVM
+including Garbage Collection (GC) which may lead to a significant overhead.
+Dataflow-based systems like Spark allow programmers to define complex objects in a
+host language like Java to manipulate and transfer tremendous amount of data.
 
-Considered problems in memory management in JVM, developing Big Data processing tools with system languages can be the solution.
-By using a system language, a developer has control on the memory management. Therefore, one can implement systems with more optimized memory management strategies.
-We select Rust as a good candidate for the development of Big Data processing tools, due to its ability to write memory-safe and fearless concurrent codes with its concept of ownership.
+% Generating many of these complex objects in memory forces GC to rearrange the objects in memory frequently waisting computation.
+% Considered performance overhead in memory management in JVM makes system languages to be a better choice to
+% develop systems for Big Data processing.
 
-There may be many possible strategies to optimize memory management for Big Data processing in Rust programming: 
+System languages like C++ or Rust seems to be a better choice to
+develop systems for Big Data processing becasuse they do not relay on JVM.
+By using a system language, a developer has full control on the memory management.
+% Therefore, one can implement systems with more optimized memory management strategies.
+We found Rust programming language to be a good candidate due to its ability to write memory-safe and
+fearless concurrent codes with its concept of memory ownership and borrowing.
+Rust programming language includes many possible strategies to optimize memory management for Big Data processing including
 selection of different variable types, use of Reference Counting, and multithreading with Atomic Reference Counting.
-We conduct several experiments to assess how much these different memory management strategies differ runtime performance.
 
-Our experiments focus complex object manipulation and common Big Data processing with various memory management.
-The results show significant different runtime hits among these different memory strategies.
+In this thesis, we conducted an experimental study to assess how much these different memory management
+strategies differ regarding overall runtime performance.
+Our experiments focusses on complex object manipulation and common Big Data processing patterns
+with various memory management. Our experimental results indicate a significant
+difference among these different memory strategies regarding data processing performance.

### 2020-05-11 thesis_template/0_Prelim/abs.tex
updated Abstract

@@
 System languages like C++ or Rust seems to be a better choice to
-develop systems for Big Data processing becasuse they do not relay on JVM.
+develop systems for Big Data processing because they do not relay on JVM.
 By using a system language, a developer has full control on the memory management.
@@
 strategies differ regarding overall runtime performance.
-Our experiments focusses on complex object manipulation and common Big Data processing patterns
+Our experiments focus on complex object manipulation and common Big Data processing patterns
 with various memory management. Our experimental results indicate a significant

### 2020-05-28 paper/Association for Computing Machinery (ACM) - SIG Proceedings Template/sample-authordraft.tex
problem description

%%
%% This is file `sample-authordraft.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `authordraft')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-authordraft.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigconf,authordraft]{acmart}
% NOTE that a single column version is required for submission and peer review. This can be done by changing the \doucmentclass[...]{acmart} in this template to 
% \documentclass[manuscript,screen]{acmart}

%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{acmcopyright}
\copyrightyear{2018}
\acmYear{2018}
\acmDOI{10.1145/1122445.1122456}

%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[Woodstock '18]{Woodstock '18: ACM Symposium on Neural
  Gaze Detection}{June 03--05, 2018}{Woodstock, NY}
\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
  June 03--05, 2018, Woodstock, NY}
\acmPrice{15.00}
\acmISBN{978-1-4503-XXXX-X/18/06}

%%
%% Submission ID.
%% Use this when submitting an article to a sponsored event. You'll
%% receive a unique submission ID from the organizers
%% of the event, and this ID should be used as the parameter to this command.
%%\acmSubmissionID{123-A56-BU3}

%%
%% The majority of ACM publications use numbered citations and
%% references.  The command \citestyle{authoryear} switches to the
%% "author year" style.
%%
%% If you are preparing content for an event
%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
%% citations and references.
%% Uncommenting
%% the next command will enable that style.
%%\citestyle{acmauthoryear}

%%
%% end of the preamble, start of the body of the document source.
\begin{document}

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{The Name of the Title is Hope}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Ben Trovato}
\authornote{Both authors contributed equally to this research.}
\email{trovato@corporation.com}
\orcid{1234-5678-9012}
\author{G.K.M. Tobin}
\authornotemark[1]
\email{webmaster@marysville-ohio.com}
\affiliation{%
  \institution{Institute for Clarity in Documentation}
  \streetaddress{P.O. Box 1212}
  \city{Dublin}
  \state{Ohio}
  \postcode{43017-6221}
}

\author{Lars Th{\o}rv{\"a}ld}
\affiliation{%
  \institution{The Th{\o}rv{\"a}ld Group}
  \streetaddress{1 Th{\o}rv{\"a}ld Circle}
  \city{Hekla}
  \country{Iceland}}
\email{larst@affiliation.org}

\author{Valerie B\'eranger}
\affiliation{%
  \institution{Inria Paris-Rocquencourt}
  \city{Rocquencourt}
  \country{France}
}

\author{Aparna Patel}
\affiliation{%
 \institution{Rajiv Gandhi University}
 \streetaddress{Rono-Hills}
 \city{Doimukh}
 \state{Arunachal Pradesh}
 \country{India}}

\author{Huifen Chan}
\affiliation{%
  \institution{Tsinghua University}
  \streetaddress{30 Shuangqing Rd}
  \city{Haidian Qu}
  \state{Beijing Shi}
  \country{China}}

\author{Charles Palmer}
\affiliation{%
  \institution{Palmer Research Laboratories}
  \streetaddress{8600 Datapoint Drive}
  \city{San Antonio}
  \state{Texas}
  \postcode{78229}}
\email{cpalmer@prl.com}

\author{John Smith}
\affiliation{\institution{The Th{\o}rv{\"a}ld Group}}
\email{jsmith@affiliation.org}

\author{Julius P. Kumquat}
\affiliation{\institution{The Kumquat Consortium}}
\email{jpkumquat@consortium.net}

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
\renewcommand{\shortauthors}{Trovato and Tobin, et al.}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  A clear and well-documented \LaTeX\ document is presented as an
  article formatted for publication by ACM in a conference proceedings
  or journal publication. Based on the ``acmart'' document class, this
  article presents and explains many of the common variations, as well
  as many of the formatting elements an author may use in the
  preparation of the documentation of their work.
\end{abstract}

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Computer systems organization~Redundancy}
\ccsdesc{Computer systems organization~Robotics}
\ccsdesc[100]{Networks~Network reliability}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{datasets, neural networks, gaze detection, text tagging}

%% A "teaser" image appears between the author and affiliation
%% information and the body of the document, and typically spans the
%% page.
\begin{teaserfigure}
  \includegraphics[width=\textwidth]{sampleteaser}
  \caption{Seattle Mariners at Spring Training, 2010.}
  \Description{Enjoying the baseball game from the third-base
  seats. Ichiro Suzuki preparing to bat.}
  \label{fig:teaser}
\end{teaserfigure}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle

\section{Introduction}
ACM's consolidated article template, introduced in 2017, provides a
consistent \LaTeX\ style for use across ACM publications, and
incorporates accessibility and metadata-extraction functionality
necessary for future Digital Library endeavors. Numerous ACM and
SIG-specific \LaTeX\ templates have been examined, and their unique
features incorporated into this single new template.

If you are new to publishing with ACM, this document is a valuable
guide to the process of preparing your work for publication. If you
have published with ACM before, this document provides insight and
instruction into more recent changes to the article template.

The ``\verb|acmart|'' document class can be used to prepare articles
for any ACM publication --- conference or journal, and for any stage
of publication, from review to final ``camera-ready'' copy, to the
author's own version, with {\itshape very} few changes to the source.

\section{Template Overview}
As noted in the introduction, the ``\verb|acmart|'' document class can
be used to prepare many different kinds of documentation --- a
double-blind initial submission of a full-length technical paper, a
two-page SIGGRAPH Emerging Technologies abstract, a ``camera-ready''
journal article, a SIGCHI Extended Abstract, and more --- all by
selecting the appropriate {\itshape template style} and {\itshape
  template parameters}.

This document will explain the major features of the document
class. For further information, the {\itshape \LaTeX\ User's Guide} is
available from
\url{https://www.acm.org/publications/proceedings-template}.

\subsection{Template Styles}

The primary parameter given to the ``\verb|acmart|'' document class is
the {\itshape template style} which corresponds to the kind of publication
or SIG publishing the work. This parameter is enclosed in square
brackets and is a part of the {\verb|documentclass|} command:
\begin{verbatim}
  \documentclass[STYLE]{acmart}
\end{verbatim}

Journals use one of three template styles. All but three ACM journals
use the {\verb|acmsmall|} template style:
\begin{itemize}
\item {\verb|acmsmall|}: The default journal template style.
\item {\verb|acmlarge|}: Used by JOCCH and TAP.
\item {\verb|acmtog|}: Used by TOG.
\end{itemize}

The majority of conference proceedings documentation will use the {\verb|acmconf|} template style.
\begin{itemize}
\item {\verb|acmconf|}: The default proceedings template style.
\item{\verb|sigchi|}: Used for SIGCHI conference articles.
\item{\verb|sigchi-a|}: Used for SIGCHI ``Extended Abstract'' articles.
\item{\verb|sigplan|}: Used for SIGPLAN conference articles.
\end{itemize}

\subsection{Template Parameters}

In addition to specifying the {\itshape template style} to be used in
formatting your work, there are a number of {\itshape template parameters}
which modify some part of the applied template style. A complete list
of these parameters can be found in the {\itshape \LaTeX\ User's Guide.}

Frequently-used parameters, or combinations of parameters, include:
\begin{itemize}
\item {\verb|anonymous,review|}: Suitable for a ``double-blind''
  conference submission. Anonymizes the work and includes line
  numbers. Use with the \verb|\acmSubmissionID| command to print the
  submission's unique ID on each page of the work.
\item{\verb|authorversion|}: Produces a version of the work suitable
  for posting by the author.
\item{\verb|screen|}: Produces colored hyperlinks.
\end{itemize}

This document uses the following string as the first command in the
source file:
\begin{verbatim}
\documentclass[sigconf,authordraft]{acmart}
\end{verbatim}

\section{Modifications}

Modifying the template --- including but not limited to: adjusting
margins, typeface sizes, line spacing, paragraph and list definitions,
and the use of the \verb|\vspace| command to manually adjust the
vertical spacing between elements of your work --- is not allowed.

{\bfseries Your document will be returned to you for revision if
  modifications are discovered.}

\section{Typefaces}

The ``\verb|acmart|'' document class requires the use of the
``Libertine'' typeface family. Your \TeX\ installation should include
this set of packages. Please do not substitute other typefaces. The
``\verb|lmodern|'' and ``\verb|ltimes|'' packages should not be used,
as they will override the built-in typeface families.

\section{Title Information}

The title of your work should use capital letters appropriately -
\url{https://capitalizemytitle.com/} has useful rules for
capitalization. Use the {\verb|title|} command to define the title of
your work. If your work has a subtitle, define it with the
{\verb|subtitle|} command.  Do not insert line breaks in your title.

If your title is lengthy, you must define a short version to be used
in the page headers, to prevent overlapping text. The \verb|title|
command has a ``short title'' parameter:
\begin{verbatim}
  \title[short title]{full title}
\end{verbatim}

\section{Authors and Affiliations}

Each author must be defined separately for accurate metadata
identification. Multiple authors may share one affiliation. Authors'
names should not be abbreviated; use full first names wherever
possible. Include authors' e-mail addresses whenever possible.

Grouping authors' names or e-mail addresses, or providing an ``e-mail
alias,'' as shown below, is not acceptable:
\begin{verbatim}
  \author{Brooke Aster, David Mehldau}
  \email{dave,judy,steve@university.edu}
  \email{firstname.lastname@phillips.org}
\end{verbatim}

The \verb|authornote| and \verb|authornotemark| commands allow a note
to apply to multiple authors --- for example, if the first two authors
of an article contributed equally to the work.

If your author list is lengthy, you must define a shortened version of
the list of authors to be used in the page headers, to prevent
overlapping text. The following command should be placed just after
the last \verb|\author{}| definition:
\begin{verbatim}
  \renewcommand{\shortauthors}{McCartney, et al.}
\end{verbatim}
Omitting this command will force the use of a concatenated list of all
of the authors' names, which may result in overlapping text in the
page headers.

The article template's documentation, available at
\url{https://www.acm.org/publications/proceedings-template}, has a
complete explanation of these commands and tips for their effective
use.

Note that authors' addresses are mandatory for journal articles.

\section{Rights Information}

Authors of any work published by ACM will need to complete a rights
form. Depending on the kind of work, and the rights management choice
made by the author, this may be copyright transfer, permission,
license, or an OA (open access) agreement.

Regardless of the rights management choice, the author will receive a
copy of the completed rights form once it has been submitted. This
form contains \LaTeX\ commands that must be copied into the source
document. When the document source is compiled, these commands and
their parameters add formatted text to several areas of the final
document:
\begin{itemize}
\item the ``ACM Reference Format'' text on the first page.
\item the ``rights management'' text on the first page.
\item the conference information in the page header(s).
\end{itemize}

Rights information is unique to the work; if you are preparing several
works for an event, make sure to use the correct set of commands with
each of the works.

The ACM Reference Format text is required for all articles over one
page in length, and is optional for one-page articles (abstracts).

\section{CCS Concepts and User-Defined Keywords}

Two elements of the ``acmart'' document class provide powerful
taxonomic tools for you to help readers find your work in an online
search.

The ACM Computing Classification System ---
\url{https://www.acm.org/publications/class-2012} --- is a set of
classifiers and concepts that describe the computing
discipline. Authors can select entries from this classification
system, via \url{https://dl.acm.org/ccs/ccs.cfm}, and generate the
commands to be included in the \LaTeX\ source.

User-defined keywords are a comma-separated list of words and phrases
of the authors' choosing, providing a more flexible way of describing
the research being presented.

CCS concepts and user-defined keywords are required for for all
articles over two pages in length, and are optional for one- and
two-page articles (or abstracts).

\section{Sectioning Commands}

Your work should use standard \LaTeX\ sectioning commands:
\verb|section|, \verb|subsection|, \verb|subsubsection|, and
\verb|paragraph|. They should be numbered; do not remove the numbering
from the commands.

Simulating a sectioning command by setting the first word or words of
a paragraph in boldface or italicized text is {\bfseries not allowed.}

\section{Tables}

The ``\verb|acmart|'' document class includes the ``\verb|booktabs|''
package --- \url{https://ctan.org/pkg/booktabs} --- for preparing
high-quality tables.

Table captions are placed {\itshape above} the table.

Because tables cannot be split across pages, the best placement for
them is typically the top of the page nearest their initial cite.  To
ensure this proper ``floating'' placement of tables, use the
environment \textbf{table} to enclose the table's contents and the
table caption.  The contents of the table itself must go in the
\textbf{tabular} environment, to be aligned properly in rows and
columns, with the desired horizontal and vertical rules.  Again,
detailed instructions on \textbf{tabular} material are found in the
\textit{\LaTeX\ User's Guide}.

Immediately following this sentence is the point at which
Table~\ref{tab:freq} is included in the input file; compare the
placement of the table here with the table in the printed output of
this document.

\begin{table}
  \caption{Frequency of Special Characters}
  \label{tab:freq}
  \begin{tabular}{ccl}
    \toprule
    Non-English or Math&Frequency&Comments\\
    \midrule
    \O & 1 in 1,000& For Swedish names\\
    $\pi$ & 1 in 5& Common in math\\
    \$ & 4 in 5 & Used in business\\
    $\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
  \bottomrule
\end{tabular}
\end{table}

To set a wider table, which takes up the whole width of the page's
live area, use the environment \textbf{table*} to enclose the table's
contents and the table caption.  As with a single-column table, this
wide table will ``float'' to a location deemed more
desirable. Immediately following this sentence is the point at which
Table~\ref{tab:commands} is included in the input file; again, it is
instructive to compare the placement of the table here with the table
in the printed output of this document.

\begin{table*}
  \caption{Some Typical Commands}
  \label{tab:commands}
  \begin{tabular}{ccl}
    \toprule
    Command &A Number & Comments\\
    \midrule
    \texttt{{\char'134}author} & 100& Author \\
    \texttt{{\char'134}table}& 300 & For tables\\
    \texttt{{\char'134}table*}& 400& For wider tables\\
    \bottomrule
  \end{tabular}
\end{table*}

\section{Math Equations}
You may want to display math equations in three distinct styles:
inline, numbered or non-numbered display.  Each of the three are
discussed in the next sections.

\subsection{Inline (In-text) Equations}
A formula that appears in the running text is called an inline or
in-text formula.  It is produced by the \textbf{math} environment,
which can be invoked with the usual
\texttt{{\char'134}begin\,\ldots{\char'134}end} construction or with
the short form \texttt{\$\,\ldots\$}. You can use any of the symbols
and structures, from $\alpha$ to $\omega$, available in
\LaTeX~\cite{Lamport:LaTeX}; this section will simply show a few
examples of in-text equations in context. Notice how this equation:
\begin{math}
  \lim_{n\rightarrow \infty}x=0
\end{math},
set here in in-line math style, looks slightly different when
set in display style.  (See next section).

\subsection{Display Equations}
A numbered display equation---one set off by vertical space from the
text and centered horizontally---is produced by the \textbf{equation}
environment. An unnumbered display equation is produced by the
\textbf{displaymath} environment.

Again, in either environment, you can use any of the symbols and
structures available in \LaTeX\@; this section will just give a couple
of examples of display equations in context.  First, consider the
equation, shown as an inline equation above:
\begin{equation}
  \lim_{n\rightarrow \infty}x=0
\end{equation}
Notice how it is formatted somewhat differently in
the \textbf{displaymath}
environment.  Now, we'll enter an unnumbered equation:
\begin{displaymath}
  \sum_{i=0}^{\infty} x + 1
\end{displaymath}
and follow it with another numbered equation:
\begin{equation}
  \sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f
\end{equation}
just to demonstrate \LaTeX's able handling of numbering.

\section{Figures}

The ``\verb|figure|'' environment should be used for figures. One or
more images can be placed within a figure. If your figure contains
third-party material, you must clearly identify it as such, as shown
in the example below.
\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{sample-franklin}
  \caption{1907 Franklin Model D roadster. Photograph by Harris \&
    Ewing, Inc. [Public domain], via Wikimedia
    Commons. (\url{https://goo.gl/VLCRBB}).}
  \Description{The 1907 Franklin Model D roadster.}
\end{figure}

Your figures should contain a caption which describes the figure to
the reader. Figure captions go below the figure. Your figures should
{\bfseries also} include a description suitable for screen readers, to
assist the visually-challenged to better understand your work.

Figure captions are placed {\itshape below} the figure.

\subsection{The ``Teaser Figure''}

A ``teaser figure'' is an image, or set of images in one figure, that
are placed after all author and affiliation information, and before
the body of the article, spanning the page. If you wish to have such a
figure in your article, place the command immediately before the
\verb|\maketitle| command:
\begin{verbatim}
  \begin{teaserfigure}
    \includegraphics[width=\textwidth]{sampleteaser}
    \caption{figure caption}
    \Description{figure description}
  \end{teaserfigure}
\end{verbatim}

\section{Citations and Bibliographies}

The use of \BibTeX\ for the preparation and formatting of one's
references is strongly recommended. Authors' names should be complete
--- use full first names (``Donald E. Knuth'') not initials
(``D. E. Knuth'') --- and the salient identifying features of a
reference should be included: title, year, volume, number, pages,
article DOI, etc.

The bibliography is included in your source document with these two
commands, placed just before the \verb|\end{document}| command:
\begin{verbatim}
  \bibliographystyle{ACM-Reference-Format}
  \bibliography{bibfile}
\end{verbatim}
where ``\verb|bibfile|'' is the name, without the ``\verb|.bib|''
suffix, of the \BibTeX\ file.

Citations and references are numbered by default. A small number of
ACM publications have citations and references formatted in the
``author year'' style; for these exceptions, please include this
command in the {\bfseries preamble} (before
``\verb|\begin{document}|'') of your \LaTeX\ source:
\begin{verbatim}
  \citestyle{acmauthoryear}
\end{verbatim}

  Some examples.  A paginated journal article \cite{Abril07}, an
  enumerated journal article \cite{Cohen07}, a reference to an entire
  issue \cite{JCohen96}, a monograph (whole book) \cite{Kosiur01}, a
  monograph/whole book in a series (see 2a in spec. document)
  \cite{Harel79}, a divisible-book such as an anthology or compilation
  \cite{Editor00} followed by the same example, however we only output
  the series if the volume number is given \cite{Editor00a} (so
  Editor00a's series should NOT be present since it has no vol. no.),
  a chapter in a divisible book \cite{Spector90}, a chapter in a
  divisible book in a series \cite{Douglass98}, a multi-volume work as
  book \cite{Knuth97}, an article in a proceedings (of a conference,
  symposium, workshop for example) (paginated proceedings article)
  \cite{Andler79}, a proceedings article with all possible elements
  \cite{Smith10}, an example of an enumerated proceedings article
  \cite{VanGundy07}, an informally published work \cite{Harel78}, a
  doctoral dissertation \cite{Clarkson85}, a master's thesis:
  \cite{anisi03}, an online document / world wide web resource
  \cite{Thornburg01, Ablamowicz07, Poker06}, a video game (Case 1)
  \cite{Obama08} and (Case 2) \cite{Novak03} and \cite{Lee05} and
  (Case 3) a patent \cite{JoeScientist001}, work accepted for
  publication \cite{rous08}, 'YYYYb'-test for prolific author
  \cite{SaeediMEJ10} and \cite{SaeediJETC10}. Other cites might
  contain 'duplicate' DOI and URLs (some SIAM articles)
  \cite{Kirschmer:2010:AEI:1958016.1958018}. Boris / Barbara Beeton:
  multi-volume works as books \cite{MR781536} and \cite{MR781537}. A
  couple of citations with DOIs:
  \cite{2004:ITE:1009386.1010128,Kirschmer:2010:AEI:1958016.1958018}. Online
  citations: \cite{TUGInstmem, Thornburg01, CTANacmart}. Artifacts:
  \cite{R} and \cite{UMassCitations}.

\section{Acknowledgments}

Identification of funding sources and other support, and thanks to
individuals and groups that assisted in the research and the
preparation of the work should be included in an acknowledgment
section, which is placed just before the reference section in your
document.

This section has a special environment:
\begin{verbatim}
  \begin{acks}
  ...
  \end{acks}
\end{verbatim}
so that the information contained therein can be more easily collected
during the article metadata extraction phase, and to ensure
consistency in the spelling of the section heading.

Authors should not prepare this section as a numbered or unnumbered {\verb|\section|}; please use the ``{\verb|acks|}'' environment.

\section{Appendices}

If your work needs an appendix, add it before the
``\verb|\end{document}|'' command at the conclusion of your source
document.

Start the appendix with the ``\verb|appendix|'' command:
\begin{verbatim}
  \appendix
\end{verbatim}
and note that in the appendix, sections are lettered, not
numbered. This document has two appendices, demonstrating the section
and subsection identification method.

\section{SIGCHI Extended Abstracts}

The ``\verb|sigchi-a|'' template style (available only in \LaTeX\ and
not in Word) produces a landscape-orientation formatted article, with
a wide left margin. Three environments are available for use with the
``\verb|sigchi-a|'' template style, and produce formatted output in
the margin:
\begin{itemize}
\item {\verb|sidebar|}:  Place formatted text in the margin.
\item {\verb|marginfigure|}: Place a figure in the margin.
\item {\verb|margintable|}: Place a table in the margin.
\end{itemize}

%%
%% The acknowledgments section is defined using the "acks" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.
\begin{acks}
To Robert, for the bagels and explaining CMYK and color spaces.
\end{acks}

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{sample-base}

%%
%% If your work has an appendix, this is the place to put it.
\appendix

\section{Research Methods}

\subsection{Part One}

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi
malesuada, quam in pulvinar varius, metus nunc fermentum urna, id
sollicitudin purus odio sit amet enim. Aliquam ullamcorper eu ipsum
vel mollis. Curabitur quis dictum nisl. Phasellus vel semper risus, et
lacinia dolor. Integer ultricies commodo sem nec semper.

\subsection{Part Two}

Etiam commodo feugiat nisl pulvinar pellentesque. Etiam auctor sodales
ligula, non varius nibh pulvinar semper. Suspendisse nec lectus non
ipsum convallis congue hendrerit vitae sapien. Donec at laoreet
eros. Vivamus non purus placerat, scelerisque diam eu, cursus
ante. Etiam aliquam tortor auctor efficitur mattis.

\section{Online Resources}

Nam id fermentum dui. Suspendisse sagittis tortor a nulla mollis, in
pulvinar ex pretium. Sed interdum orci quis metus euismod, et sagittis
enim maximus. Vestibulum gravida massa ut felis suscipit
congue. Quisque mattis elit a risus ultrices commodo venenatis eget
dui. Etiam sagittis eleifend elementum.

Nam interdum magna at lectus dignissim, ac dignissim lorem
rhoncus. Maecenas eu arcu ac neque placerat aliquam. Nunc pulvinar
massa et mattis lacinia.

\end{document}
\endinput
%%
%% End of file `sample-authordraft.tex'.

### 2020-05-28 paper/Association for Computing Machinery (ACM) - SIG Proceedings Template/sample-lualatex.tex
problem description

--- 2020-05-28 paper/Association for Computing Machinery (ACM) - SIG Proceedings Template/sample-authordraft.tex
@@
 %%
-%% This is file `sample-authordraft.tex',
+%% This is file `sample-lualatex.tex',
 %% generated with the docstrip utility.
@@
 %%
-%% samples.dtx  (with options: `authordraft')
+%% samples.dtx  (with options: `sigconf')
 %% 
@@
 %% Any modified versions of this file must be renamed
-%% with new filenames distinct from sample-authordraft.tex.
+%% with new filenames distinct from sample-lualatex.tex.
 %% 
@@
 %% The first command in your LaTeX source must be the \documentclass command.
-\documentclass[sigconf,authordraft]{acmart}
-% NOTE that a single column version is required for submission and peer review. This can be done by changing the \doucmentclass[...]{acmart} in this template to 
-% \documentclass[manuscript,screen]{acmart}
+\documentclass[sigconf]{acmart}
 
@@
 %% allowing the author to define a "short title" to be used in page headers.
-\title{The Name of the Title is Hope}
+\title{An Experimental Study of Memory Management in Rust Programming for Big Data Processing}
 
@@
 %% used to denote shared contribution to the research.
-\author{Ben Trovato}
+\author{Shinsaku Okazaki}
 \authornote{Both authors contributed equally to this research.}
-\email{trovato@corporation.com}
-\orcid{1234-5678-9012}
-\author{G.K.M. Tobin}
+\email{so4639@bu.edu}
+\orcid{631-415-6888}
 \authornotemark[1]
-\email{webmaster@marysville-ohio.com}
 \affiliation{%
-  \institution{Institute for Clarity in Documentation}
-  \streetaddress{P.O. Box 1212}
-  \city{Dublin}
-  \state{Ohio}
-  \postcode{43017-6221}
+  \institution{Boston University}
+  \streetaddress{1010 Commonwealth Avenue}
+  \city{Boston}
+  \state{Massachusetts}
+  \postcode{02215}
 }
 
-\author{Lars Th{\o}rv{\"a}ld}
+\author{Kia Teymourian}
 \affiliation{%
-  \institution{The Th{\o}rv{\"a}ld Group}
-  \streetaddress{1 Th{\o}rv{\"a}ld Circle}
-  \city{Hekla}
-  \country{Iceland}}
-\email{larst@affiliation.org}
-
-\author{Valerie B\'eranger}
-\affiliation{%
-  \institution{Inria Paris-Rocquencourt}
-  \city{Rocquencourt}
-  \country{France}
-}
-
-\author{Aparna Patel}
-\affiliation{%
- \institution{Rajiv Gandhi University}
- \streetaddress{Rono-Hills}
- \city{Doimukh}
- \state{Arunachal Pradesh}
- \country{India}}
-
-\author{Huifen Chan}
-\affiliation{%
-  \institution{Tsinghua University}
-  \streetaddress{30 Shuangqing Rd}
-  \city{Haidian Qu}
-  \state{Beijing Shi}
-  \country{China}}
-
-\author{Charles Palmer}
-\affiliation{%
-  \institution{Palmer Research Laboratories}
-  \streetaddress{8600 Datapoint Drive}
-  \city{San Antonio}
-  \state{Texas}
-  \postcode{78229}}
-\email{cpalmer@prl.com}
-
-\author{John Smith}
-\affiliation{\institution{The Th{\o}rv{\"a}ld Group}}
-\email{jsmith@affiliation.org}
-
-\author{Julius P. Kumquat}
-\affiliation{\institution{The Kumquat Consortium}}
-\email{jpkumquat@consortium.net}
+  \institution{Boston University}
+  \streetaddress{1010 Commonwealth Avenue}
+  \city{Boston}
+  \country{Massachusetts}}
+\email{kiat@bu.edu}
 
@@
 \begin{abstract}
-  A clear and well-documented \LaTeX\ document is presented as an
-  article formatted for publication by ACM in a conference proceedings
-  or journal publication. Based on the ``acmart'' document class, this
-  article presents and explains many of the common variations, as well
-  as many of the formatting elements an author may use in the
-  preparation of the documentation of their work.
+  Planning optimized memory management is critical for Big Data analysis tools to
+perform faster runtime and efficient use of computation resources.
+Modern Big Data analysis tools use application languages that abstract their
+memory management so that developers do not have to pay extreme attention
+to memory management strategies.
+
+Many existing modern cloud-based data processing systems such as Hadoop, Spark or Flink use
+Java Virtual Machine (JVM) and taking full advantage of features such as automated memory management in JVM
+including Garbage Collection (GC) which may lead to a significant overhead.
+Dataflow-based systems like Spark allow programmers to define complex objects in a
+host language like Java to manipulate and transfer tremendous amount of data.
+
+% Generating many of these complex objects in memory forces GC to rearrange the objects in memory frequently waisting computation.
+% Considered performance overhead in memory management in JVM makes system languages to be a better choice to
+% develop systems for Big Data processing.
+
+System languages like C++ or Rust seems to be a better choice to
+develop systems for Big Data processing because they do not relay on JVM.
+By using a system language, a developer has full control on the memory management.
+% Therefore, one can implement systems with more optimized memory management strategies.
+We found Rust programming language to be a good candidate due to its ability to write memory-safe and
+fearless concurrent codes with its concept of memory ownership and borrowing.
+Rust programming language includes many possible strategies to optimize memory management for Big Data processing including
+selection of different variable types, use of Reference Counting, and multithreading with Atomic Reference Counting.
+
+In this thesis, we conducted an experimental study to assess how much these different memory management
+strategies differ regarding overall runtime performance.
+Our experiments focus on complex object manipulation and common Big Data processing patterns
+with various memory management. Our experimental results indicate a significant
+difference among these different memory strategies regarding data processing performance.
 \end{abstract}
@@
 \section{Introduction}
-ACM's consolidated article template, introduced in 2017, provides a
-consistent \LaTeX\ style for use across ACM publications, and
-incorporates accessibility and metadata-extraction functionality
-necessary for future Digital Library endeavors. Numerous ACM and
-SIG-specific \LaTeX\ templates have been examined, and their unique
-features incorporated into this single new template.
+\subsection{Motivation}
+\label{sec:motivation}
+Cluster computing tool for Big Data Analysis has been more important as magnitude and quality of data that we can obtain increases. 
+Recently, almost all businesses stand on data, from web marketing analysis to factory automations. The leverage of data is ubiquitous, because 
+there are many open source tools to analyze data and cloud computer infrastructure which can support computation for massive amount of data. 
+The improvement of accessibility to these technologies has democratized data driven businesses by 
+eliminating significant amount of initial investment.
 
-If you are new to publishing with ACM, this document is a valuable
-guide to the process of preparing your work for publication. If you
-have published with ACM before, this document provides insight and
-instruction into more recent changes to the article template.
+However these computation resources do not come for free; we need to pay money to use these resources. Usually, user needs to pay depending on usage of computational resources. 
+If your process of data analysis is too long or need to use number of clusters with high speck specification, the cost may end up significantly hight.
+To address these problems, the quality of analysis tool is critical. If the tool can optimize the runtime performance and usage of computational resources, 
+the cost for running the businesses can become efficient.
 
-The ``\verb|acmart|'' document class can be used to prepare articles
-for any ACM publication --- conference or journal, and for any stage
-of publication, from review to final ``camera-ready'' copy, to the
-author's own version, with {\itshape very} few changes to the source.
+Multiple cluster computing analysis tools have been developed, such as Hadoop MapReduce \cite{ApacheHadoopHomePage}, 
+Apache Spark \cite{ApacheSparkHomePage}, and Apache Flink \cite{ApacheFlinkHomePage} \cite{DBLP:journals/debu/CarboneKEMHT15}. 
+These tools have brought reliable and scalable ways to deal massive data. 
+These has become widely popular, in which data-parallel computations are executed on clusters of unreliable machines by systems that automatically provide locality-aware scheduling, 
+fault tolerance, and load balancing.
 
+These tools are constructed on top of Java Virtual Machine (JVM). JVM abstracts hardware and memory management from the developer so that the development is fairly easy. 
+In addition, Java or Scala compiled code is platform-independent, which can run on any machine with JVM. However, these advantages may be really critical weakness when it comes to 
+processing big data. JVM abstract away most detail regarding memory management from the system designer, including memory deallocation, reuse, and movement, as well as pointers, 
+object serialization and deserialization. Since managing and utilizing memory is one of the most important factors determining Big Data systems' performance, 
+reliance on a managed environment can mean an order-of-magnitude increase in CPU cost for some computations. This cost may be unacceptable for high-performance tool development by an expert.
+
+To overcome these problems, one can use programming languages with more control on hardware, system languages, for development of Big Data tools.
+For example, C++ is a general-purpose, statically typed,
+compiled programming language which supports multiple programming paradigm. It is also a system language which gives full control over hardware. 
+There are several researches or projects \cite{DBLP:conf/sigmod/0001BLLMSTYJ18} where developers and 
+researchers implement Big Data tools with this language. These tools shows significantly better performances than those developed with application languages. 
+Although the evidence of the advantage of building high speed computational tools with C++ has been discovered, the steep learning curve and difficulty of writing memory safe codes are barrier to technology diffusion.
+
+Rust is a system language which gives the similar performance and control of hardware to C++ or C and safety of runtime. The memory-safety, and fearless concurrently in Rust programming 
+make the language one of the ideal candidate for development of Big Data tools. 
+Since the design of the language is different from any other programming languages, implementations that can be selected for algorithms can differ from existing ones.
+In this thesis, we focus on memory management strategy for Big Data processing algorithms in development with Rust.
+
+\subsection{Problem Description}
+\label{sec:probdesc}
+
+% Many of popular open source cluster computing frameworks for large scale data analysis, 
+% such as Hadoop and Spark, allow programmers to define objects in a host languages, such as Java.
+% The objects are then managed in RAM by the language and its runtime, Java Virtual Machine 
+% in the case of Java and Scala. Storing objects in memory enables machine to process iterative computation. 
+% One of the fundamental tasks for recent big data analysis is analysis using Machine Learning Algorithms, 
+% which require iterative process. As the amount of data increases, memory is required to keep many objects. 
+% Therefore, memory management plays a critical role in this task.
+
+% One of the memory management tool on JVM is garbage collection. 
+% The garbage collection brings a significant advantage for programmers by removing responsibility
+% for planning memory management by themselves manually. Instead, JVM monitors the state of memory and performs garbage
+% collection at certain points. However, these monitoring and auto-execution of garbage collection cost additional 
+% computation and might consume computation resources which should be used for data processing. This can significantly decrease performance of the computation.
+
+% In contrast, memory management in system language, such as C++, relies on programmers’ decision for when to allocate and deallocate memory. 
+% The functions, malloc/free consume most of the memory management. Proper implementation of system language for big data processing can be overperform the implementation in host language.
+% Nevertheless, implementing C++ performing proper memory management and guaranteeing security can be unproductive and complicated.
+
+Even though Rust can be a great candidate to develop Big Data processing tools, there are few study for development on such tools with Rust programming.
+
+Rust has various ways to manage memory. Rust has different variable types for values allocated in sequence of memory region. 
+Each variables take different memory representation that can produce variation of operation time on the variable types.
+
+In addition, Reference Counting takes important role in Rust ownership concept. By using Reference Counting, a value is able to have multiple owners.
+This situation may happen quite often, when we want to acquire complex values from contiguous memory regions. 
+Reference Counting has both advantage and disadvantage. 
+Reference count can share data which might decrease unnecessary copy of data, but checking reference count might be a overhead.
+
+Atomic Reference Counting is ubiquitous in Rust multithreading program. Atomic Reference Count also has similar features to Reference Counting. 
+In addition, it is allowed to use among different threads. This may lead additional overhead from atomic operation.
+
+As we can see, we can choose various memory management strategies in Rust programming.
+Therefore, we assess following research question in this thesis.
+\begin{itemize}
+    \item What are better memory management strategies for complex object processing to perform faster runtime performance.
+    \item How much impact do different variable types in Rust have in order to algorithms' runtime performance?
+    \item How much can algorithms runtime be improved or degraded, if we use Reference Count?
+    \item What are better memory management strategies for faster Big Data processing in Rust multithreading?
+    \item How can we improve runtime performance of common Big Data algorithms by Rust memory management?
+\end{itemize}
+
+To answer these question, we conduct 5 experiments. 
 \section{Template Overview}
@@
 \begin{verbatim}
-\documentclass[sigconf,authordraft]{acmart}
+\documentclass[sigconf]{acmart}
 \end{verbatim}
@@
 
+Always use midrule to separate table header rows from data rows, and
+use it only for this purpose. This enables assistive technologies to
+recognise table headers and support their users in navigating tables
+more easily.
+
 \section{Math Equations}
@@
     Commons. (\url{https://goo.gl/VLCRBB}).}
-  \Description{The 1907 Franklin Model D roadster.}
+  \Description{A woman and a girl in white dresses sit in an open car.}
 \end{figure}
@@
 Your figures should contain a caption which describes the figure to
-the reader. Figure captions go below the figure. Your figures should
-{\bfseries also} include a description suitable for screen readers, to
-assist the visually-challenged to better understand your work.
+the reader.
 
 Figure captions are placed {\itshape below} the figure.
+
+Every figure should also have a figure description unless it is purely
+decorative. These descriptions convey what’s in the image to someone
+who cannot see it. They are also used by search engine crawlers for
+indexing images, and when images cannot be loaded.
+
+A figure description must be unformatted plain text less than 2000
+characters long (including spaces).  {\bfseries Figure descriptions
+  should not repeat the figure caption – their purpose is to capture
+  important information that is not already provided in the caption or
+  the main text of the paper.} For figures that convey important and
+complex new information, a short text description may not be
+adequate. More complex alternative descriptions can be placed in an
+appendix and referenced in a short figure description. For example,
+provide a data table capturing the information in a bar chart, or a
+structured list representing a graph.  For additional information
+regarding how best to write figure descriptions and why doing this is
+so important, please see
+\url{https://www.acm.org/publications/taps/describing-figures/}.
 
@@
 ``author year'' style; for these exceptions, please include this
-command in the {\bfseries preamble} (before
+command in the {\bfseries preamble} (before the command
 ``\verb|\begin{document}|'') of your \LaTeX\ source:
@@
   divisible book in a series \cite{Douglass98}, a multi-volume work as
-  book \cite{Knuth97}, an article in a proceedings (of a conference,
-  symposium, workshop for example) (paginated proceedings article)
-  \cite{Andler79}, a proceedings article with all possible elements
-  \cite{Smith10}, an example of an enumerated proceedings article
-  \cite{VanGundy07}, an informally published work \cite{Harel78}, a
-  doctoral dissertation \cite{Clarkson85}, a master's thesis:
-  \cite{anisi03}, an online document / world wide web resource
-  \cite{Thornburg01, Ablamowicz07, Poker06}, a video game (Case 1)
-  \cite{Obama08} and (Case 2) \cite{Novak03} and \cite{Lee05} and
-  (Case 3) a patent \cite{JoeScientist001}, work accepted for
+  book \cite{Knuth97}, a couple of articles in a proceedings (of a
+  conference, symposium, workshop for example) (paginated proceedings
+  article) \cite{Andler79, Hagerup1993}, a proceedings article with
+  all possible elements \cite{Smith10}, an example of an enumerated
+  proceedings article \cite{VanGundy07}, an informally published work
+  \cite{Harel78}, a couple of preprints \cite{Bornmann2019,
+    AnzarootPBM14}, a doctoral dissertation \cite{Clarkson85}, a
+  master's thesis: \cite{anisi03}, an online document / world wide web
+  resource \cite{Thornburg01, Ablamowicz07, Poker06}, a video game
+  (Case 1) \cite{Obama08} and (Case 2) \cite{Novak03} and \cite{Lee05}
+  and (Case 3) a patent \cite{JoeScientist001}, work accepted for
   publication \cite{rous08}, 'YYYYb'-test for prolific author
@@
 %%
-%% End of file `sample-authordraft.tex'.
+%% End of file `sample-lualatex.tex'.

### 2020-05-28 paper/paper-main.tex
update

--- 2020-05-28 paper/Association for Computing Machinery (ACM) - SIG Proceedings Template/sample-authordraft.tex
@@
-%%
-%% This is file `sample-authordraft.tex',
-%% generated with the docstrip utility.
-%%
-%% The original source files were:
-%%
-%% samples.dtx  (with options: `authordraft')
-%% 
-%% IMPORTANT NOTICE:
-%% 
-%% For the copyright see the source file.
-%% 
-%% Any modified versions of this file must be renamed
-%% with new filenames distinct from sample-authordraft.tex.
-%% 
-%% For distribution of the original source see the terms
-%% for copying and modification in the file samples.dtx.
-%% 
-%% This generated file may be distributed as long as the
-%% original source files, as listed above, are part of the
-%% same distribution. (The sources need not necessarily be
-%% in the same archive or directory.)
-%%
-%% The first command in your LaTeX source must be the \documentclass command.
-\documentclass[sigconf,authordraft]{acmart}
-% NOTE that a single column version is required for submission and peer review. This can be done by changing the \doucmentclass[...]{acmart} in this template to 
-% \documentclass[manuscript,screen]{acmart}
+\documentclass[sigconf]{acmart}
 
@@
 %% complete the rights form.
-\setcopyright{acmcopyright}
-\copyrightyear{2018}
-\acmYear{2018}
-\acmDOI{10.1145/1122445.1122456}
+%\setcopyright{acmcopyright}
+%\copyrightyear{2018}
+%\acmYear{2018}
+%\acmDOI{10.1145/1122445.1122456}
 
@@
 \acmPrice{15.00}
-\acmISBN{978-1-4503-XXXX-X/18/06}
+\acmISBN{978-1-4503-9999-9/18/06}
 
@@
 %% end of the preamble, start of the body of the document source.
+
 \begin{document}
@@
 %% allowing the author to define a "short title" to be used in page headers.
-\title{The Name of the Title is Hope}
+%% \title{Smart Assignment System for Data Science Education}
 
-%%
-%% The "author" command and its associated commands are used to define
-%% the authors and their affiliations.
-%% Of note is the shared affiliation of the first two authors, and the
-%% "authornote" and "authornotemark" commands
-%% used to denote shared contribution to the research.
-\author{Ben Trovato}
-\authornote{Both authors contributed equally to this research.}
-\email{trovato@corporation.com}
-\orcid{1234-5678-9012}
-\author{G.K.M. Tobin}
-\authornotemark[1]
-\email{webmaster@marysville-ohio.com}
+\title{An Experimental Study of Memory Management in Rust Programming for Big Data Processing}
+
+% \author{Lars Th{\o}rv{\"a}ld}
+% \affiliation{%
+%  \institution{The Th{\o}rv{\"a}ld Group}
+%  \streetaddress{1 Th{\o}rv{\"a}ld Circle}
+%  \city{Hekla}
+%  \country{Iceland}}
+% \email{larst@affiliation.org}
+
+\author{Shinsaku Okazaki}
 \affiliation{%
-  \institution{Institute for Clarity in Documentation}
-  \streetaddress{P.O. Box 1212}
-  \city{Dublin}
-  \state{Ohio}
-  \postcode{43017-6221}
+  \institution{Boston University}
 }
+\email{so4639@bu.edu}
 
-\author{Lars Th{\o}rv{\"a}ld}
+\author{Kia Teymourian}
 \affiliation{%
-  \institution{The Th{\o}rv{\"a}ld Group}
-  \streetaddress{1 Th{\o}rv{\"a}ld Circle}
-  \city{Hekla}
-  \country{Iceland}}
-\email{larst@affiliation.org}
+  \institution{Boston University}
+}
+\email{kiat@bu.edu}
 
-\author{Valerie B\'eranger}
-\affiliation{%
-  \institution{Inria Paris-Rocquencourt}
-  \city{Rocquencourt}
-  \country{France}
-}
+% Other good conference for publising this idea
 
-\author{Aparna Patel}
-\affiliation{%
- \institution{Rajiv Gandhi University}
- \streetaddress{Rono-Hills}
- \city{Doimukh}
- \state{Arunachal Pradesh}
- \country{India}}
-
-\author{Huifen Chan}
-\affiliation{%
-  \institution{Tsinghua University}
-  \streetaddress{30 Shuangqing Rd}
-  \city{Haidian Qu}
-  \state{Beijing Shi}
-  \country{China}}
-
-\author{Charles Palmer}
-\affiliation{%
-  \institution{Palmer Research Laboratories}
-  \streetaddress{8600 Datapoint Drive}
-  \city{San Antonio}
-  \state{Texas}
-  \postcode{78229}}
-\email{cpalmer@prl.com}
-
-\author{John Smith}
-\affiliation{\institution{The Th{\o}rv{\"a}ld Group}}
-\email{jsmith@affiliation.org}
-
-\author{Julius P. Kumquat}
-\affiliation{\institution{The Kumquat Consortium}}
-\email{jpkumquat@consortium.net}
-
-%%
-%% By default, the full list of authors will be used in the page
-%% headers. Often, this list is too long, and will overlap
-%% other information printed in the page headers. This command allows
-%% the author to define a more concise list
-%% of authors' names for this purpose.
-\renewcommand{\shortauthors}{Trovato and Tobin, et al.}
+% https://iticse.acm.org/2020/
 
@@
 \begin{abstract}
-  A clear and well-documented \LaTeX\ document is presented as an
-  article formatted for publication by ACM in a conference proceedings
-  or journal publication. Based on the ``acmart'' document class, this
-  article presents and explains many of the common variations, as well
-  as many of the formatting elements an author may use in the
-  preparation of the documentation of their work.
+
+Planning optimized memory management is critical for Big Data analysis tools to
+perform faster runtime and efficient use of computation resources.
+Modern Big Data analysis tools use application languages that abstract their
+memory management so that developers do not have to pay extreme attention
+to memory management strategies.
+
+Many existing modern cloud-based data processing systems such as Hadoop, Spark or Flink use
+Java Virtual Machine (JVM) and taking full advantage of features such as automated memory management in JVM
+including Garbage Collection (GC) which may lead to a significant overhead.
+Dataflow-based systems like Spark allow programmers to define complex objects in a
+host language like Java to manipulate and transfer tremendous amount of data.
+
+Planning optimized memory management is critical for Big Data analysis tools to
+perform faster runtime and efficient use of computation resources.
+Modern Big Data analysis tools use application languages that abstract their
+memory management so that developers do not have to pay extreme attention
+to memory management strategies.
+
+Many existing modern cloud-based data processing systems such as Hadoop, Spark or Flink use
+Java Virtual Machine (JVM) and taking full advantage of features such as automated memory management in JVM
+including Garbage Collection (GC) which may lead to a significant overhead.
+Dataflow-based systems like Spark allow programmers to define complex objects in a
+host language like Java to manipulate and transfer tremendous amount of data.
 \end{abstract}
-
 %%
@@
 %%
-\begin{CCSXML}
-<ccs2012>
- <concept>
-  <concept_id>10010520.10010553.10010562</concept_id>
-  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
-  <concept_significance>500</concept_significance>
- </concept>
- <concept>
-  <concept_id>10010520.10010575.10010755</concept_id>
-  <concept_desc>Computer systems organization~Redundancy</concept_desc>
-  <concept_significance>300</concept_significance>
- </concept>
- <concept>
-  <concept_id>10010520.10010553.10010554</concept_id>
-  <concept_desc>Computer systems organization~Robotics</concept_desc>
-  <concept_significance>100</concept_significance>
- </concept>
- <concept>
-  <concept_id>10003033.10003083.10003095</concept_id>
-  <concept_desc>Networks~Network reliability</concept_desc>
-  <concept_significance>100</concept_significance>
- </concept>
-</ccs2012>
-\end{CCSXML}
+%\begin{CCSXML}
+%<ccs2012>
+% <concept>
+%  <concept_id>10010520.10010553.10010562</concept_id>
+%  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
+%  <concept_significance>500</concept_significance>
+% </concept>
+% <concept>
+%  <concept_id>10010520.10010575.10010755</concept_id>
+%  <concept_desc>Computer systems organization~Redundancy</concept_desc>
+%  <concept_significance>300</concept_significance>
+% </concept>
+% <concept>
+%  <concept_id>10010520.10010553.10010554</concept_id>
+%  <concept_desc>Computer systems organization~Robotics</concept_desc>
+%  <concept_significance>100</concept_significance>
+% </concept>
+% <concept>
+%  <concept_id>10003033.10003083.10003095</concept_id>
+%  <concept_desc>Networks~Network reliability</concept_desc>
+%  <concept_significance>100</concept_significance>
+% </concept>
+%</ccs2012>
+%\end{CCSXML}
 
-\ccsdesc[500]{Computer systems organization~Embedded systems}
-\ccsdesc[300]{Computer systems organization~Redundancy}
-\ccsdesc{Computer systems organization~Robotics}
-\ccsdesc[100]{Networks~Network reliability}
+%\ccsdesc[500]{Computer systems organization~Embedded systems}
+%\ccsdesc[300]{Computer systems organization~Redundancy}
+%\ccsdesc{Computer systems organization~Robotics}
+%\ccsdesc[100]{Networks~Network reliability}
 
@@
 %% the work being presented. Separate the keywords with commas.
-\keywords{datasets, neural networks, gaze detection, text tagging}
-
-%% A "teaser" image appears between the author and affiliation
-%% information and the body of the document, and typically spans the
-%% page.
-\begin{teaserfigure}
-  \includegraphics[width=\textwidth]{sampleteaser}
-  \caption{Seattle Mariners at Spring Training, 2010.}
-  \Description{Enjoying the baseball game from the third-base
-  seats. Ichiro Suzuki preparing to bat.}
-  \label{fig:teaser}
-\end{teaserfigure}
+% \keywords{datasets, neural networks, gaze detection, text tagging}
 
@@
 \section{Introduction}
-ACM's consolidated article template, introduced in 2017, provides a
-consistent \LaTeX\ style for use across ACM publications, and
-incorporates accessibility and metadata-extraction functionality
-necessary for future Digital Library endeavors. Numerous ACM and
-SIG-specific \LaTeX\ templates have been examined, and their unique
-features incorporated into this single new template.
 
-If you are new to publishing with ACM, this document is a valuable
-guide to the process of preparing your work for publication. If you
-have published with ACM before, this document provides insight and
-instruction into more recent changes to the article template.
+Our contribution includes:
 
-The ``\verb|acmart|'' document class can be used to prepare articles
-for any ACM publication --- conference or journal, and for any stage
-of publication, from review to final ``camera-ready'' copy, to the
-author's own version, with {\itshape very} few changes to the source.
-
-\section{Template Overview}
-As noted in the introduction, the ``\verb|acmart|'' document class can
-be used to prepare many different kinds of documentation --- a
-double-blind initial submission of a full-length technical paper, a
-two-page SIGGRAPH Emerging Technologies abstract, a ``camera-ready''
-journal article, a SIGCHI Extended Abstract, and more --- all by
-selecting the appropriate {\itshape template style} and {\itshape
-  template parameters}.
-
-This document will explain the major features of the document
-class. For further information, the {\itshape \LaTeX\ User's Guide} is
-available from
-\url{https://www.acm.org/publications/proceedings-template}.
-
-\subsection{Template Styles}
-
-The primary parameter given to the ``\verb|acmart|'' document class is
-the {\itshape template style} which corresponds to the kind of publication
-or SIG publishing the work. This parameter is enclosed in square
-brackets and is a part of the {\verb|documentclass|} command:
-\begin{verbatim}
-  \documentclass[STYLE]{acmart}
-\end{verbatim}
-
-Journals use one of three template styles. All but three ACM journals
-use the {\verb|acmsmall|} template style:
 \begin{itemize}
-\item {\verb|acmsmall|}: The default journal template style.
-\item {\verb|acmlarge|}: Used by JOCCH and TAP.
-\item {\verb|acmtog|}: Used by TOG.
+  \item 
+  \item 
 \end{itemize}
 
-The majority of conference proceedings documentation will use the {\verb|acmconf|} template style.
-\begin{itemize}
-\item {\verb|acmconf|}: The default proceedings template style.
-\item{\verb|sigchi|}: Used for SIGCHI conference articles.
-\item{\verb|sigchi-a|}: Used for SIGCHI ``Extended Abstract'' articles.
-\item{\verb|sigplan|}: Used for SIGPLAN conference articles.
-\end{itemize}
+\section{Related Work}
 
-\subsection{Template Parameters}
+\cite{Ahoniemi:2006:AGT:1315803.1315830}
 
-In addition to specifying the {\itshape template style} to be used in
-formatting your work, there are a number of {\itshape template parameters}
-which modify some part of the applied template style. A complete list
-of these parameters can be found in the {\itshape \LaTeX\ User's Guide.}
+\section{Evaluation}
 
-Frequently-used parameters, or combinations of parameters, include:
-\begin{itemize}
-\item {\verb|anonymous,review|}: Suitable for a ``double-blind''
-  conference submission. Anonymizes the work and includes line
-  numbers. Use with the \verb|\acmSubmissionID| command to print the
-  submission's unique ID on each page of the work.
-\item{\verb|authorversion|}: Produces a version of the work suitable
-  for posting by the author.
-\item{\verb|screen|}: Produces colored hyperlinks.
-\end{itemize}
+\section{Conclusion}
 
-This document uses the following string as the first command in the
-source file:
-\begin{verbatim}
-\documentclass[sigconf,authordraft]{acmart}
-\end{verbatim}
-
-\section{Modifications}
-
-Modifying the template --- including but not limited to: adjusting
-margins, typeface sizes, line spacing, paragraph and list definitions,
-and the use of the \verb|\vspace| command to manually adjust the
-vertical spacing between elements of your work --- is not allowed.
-
-{\bfseries Your document will be returned to you for revision if
-  modifications are discovered.}
-
-\section{Typefaces}
-
-The ``\verb|acmart|'' document class requires the use of the
-``Libertine'' typeface family. Your \TeX\ installation should include
-this set of packages. Please do not substitute other typefaces. The
-``\verb|lmodern|'' and ``\verb|ltimes|'' packages should not be used,
-as they will override the built-in typeface families.
-
-\section{Title Information}
-
-The title of your work should use capital letters appropriately -
-\url{https://capitalizemytitle.com/} has useful rules for
-capitalization. Use the {\verb|title|} command to define the title of
-your work. If your work has a subtitle, define it with the
-{\verb|subtitle|} command.  Do not insert line breaks in your title.
-
-If your title is lengthy, you must define a short version to be used
-in the page headers, to prevent overlapping text. The \verb|title|
-command has a ``short title'' parameter:
-\begin{verbatim}
-  \title[short title]{full title}
-\end{verbatim}
-
-\section{Authors and Affiliations}
-
-Each author must be defined separately for accurate metadata
-identification. Multiple authors may share one affiliation. Authors'
-names should not be abbreviated; use full first names wherever
-possible. Include authors' e-mail addresses whenever possible.
-
-Grouping authors' names or e-mail addresses, or providing an ``e-mail
-alias,'' as shown below, is not acceptable:
-\begin{verbatim}
-  \author{Brooke Aster, David Mehldau}
-  \email{dave,judy,steve@university.edu}
-  \email{firstname.lastname@phillips.org}
-\end{verbatim}
-
-The \verb|authornote| and \verb|authornotemark| commands allow a note
-to apply to multiple authors --- for example, if the first two authors
-of an article contributed equally to the work.
-
-If your author list is lengthy, you must define a shortened version of
-the list of authors to be used in the page headers, to prevent
-overlapping text. The following command should be placed just after
-the last \verb|\author{}| definition:
-\begin{verbatim}
-  \renewcommand{\shortauthors}{McCartney, et al.}
-\end{verbatim}
-Omitting this command will force the use of a concatenated list of all
-of the authors' names, which may result in overlapping text in the
-page headers.
-
-The article template's documentation, available at
-\url{https://www.acm.org/publications/proceedings-template}, has a
-complete explanation of these commands and tips for their effective
-use.
-
-Note that authors' addresses are mandatory for journal articles.
-
-\section{Rights Information}
-
-Authors of any work published by ACM will need to complete a rights
-form. Depending on the kind of work, and the rights management choice
-made by the author, this may be copyright transfer, permission,
-license, or an OA (open access) agreement.
-
-Regardless of the rights management choice, the author will receive a
-copy of the completed rights form once it has been submitted. This
-form contains \LaTeX\ commands that must be copied into the source
-document. When the document source is compiled, these commands and
-their parameters add formatted text to several areas of the final
-document:
-\begin{itemize}
-\item the ``ACM Reference Format'' text on the first page.
-\item the ``rights management'' text on the first page.
-\item the conference information in the page header(s).
-\end{itemize}
-
-Rights information is unique to the work; if you are preparing several
-works for an event, make sure to use the correct set of commands with
-each of the works.
-
-The ACM Reference Format text is required for all articles over one
-page in length, and is optional for one-page articles (abstracts).
-
-\section{CCS Concepts and User-Defined Keywords}
-
-Two elements of the ``acmart'' document class provide powerful
-taxonomic tools for you to help readers find your work in an online
-search.
-
-The ACM Computing Classification System ---
-\url{https://www.acm.org/publications/class-2012} --- is a set of
-classifiers and concepts that describe the computing
-discipline. Authors can select entries from this classification
-system, via \url{https://dl.acm.org/ccs/ccs.cfm}, and generate the
-commands to be included in the \LaTeX\ source.
-
-User-defined keywords are a comma-separated list of words and phrases
-of the authors' choosing, providing a more flexible way of describing
-the research being presented.
-
-CCS concepts and user-defined keywords are required for for all
-articles over two pages in length, and are optional for one- and
-two-page articles (or abstracts).
-
-\section{Sectioning Commands}
-
-Your work should use standard \LaTeX\ sectioning commands:
-\verb|section|, \verb|subsection|, \verb|subsubsection|, and
-\verb|paragraph|. They should be numbered; do not remove the numbering
-from the commands.
-
-Simulating a sectioning command by setting the first word or words of
-a paragraph in boldface or italicized text is {\bfseries not allowed.}
-
-\section{Tables}
-
-The ``\verb|acmart|'' document class includes the ``\verb|booktabs|''
-package --- \url{https://ctan.org/pkg/booktabs} --- for preparing
-high-quality tables.
-
-Table captions are placed {\itshape above} the table.
-
-Because tables cannot be split across pages, the best placement for
-them is typically the top of the page nearest their initial cite.  To
-ensure this proper ``floating'' placement of tables, use the
-environment \textbf{table} to enclose the table's contents and the
-table caption.  The contents of the table itself must go in the
-\textbf{tabular} environment, to be aligned properly in rows and
-columns, with the desired horizontal and vertical rules.  Again,
-detailed instructions on \textbf{tabular} material are found in the
-\textit{\LaTeX\ User's Guide}.
-
-Immediately following this sentence is the point at which
-Table~\ref{tab:freq} is included in the input file; compare the
-placement of the table here with the table in the printed output of
-this document.
-
-\begin{table}
-  \caption{Frequency of Special Characters}
-  \label{tab:freq}
-  \begin{tabular}{ccl}
-    \toprule
-    Non-English or Math&Frequency&Comments\\
-    \midrule
-    \O & 1 in 1,000& For Swedish names\\
-    $\pi$ & 1 in 5& Common in math\\
-    \$ & 4 in 5 & Used in business\\
-    $\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
-  \bottomrule
-\end{tabular}
-\end{table}
-
-To set a wider table, which takes up the whole width of the page's
-live area, use the environment \textbf{table*} to enclose the table's
-contents and the table caption.  As with a single-column table, this
-wide table will ``float'' to a location deemed more
-desirable. Immediately following this sentence is the point at which
-Table~\ref{tab:commands} is included in the input file; again, it is
-instructive to compare the placement of the table here with the table
-in the printed output of this document.
-
-\begin{table*}
-  \caption{Some Typical Commands}
-  \label{tab:commands}
-  \begin{tabular}{ccl}
-    \toprule
-    Command &A Number & Comments\\
-    \midrule
-    \texttt{{\char'134}author} & 100& Author \\
-    \texttt{{\char'134}table}& 300 & For tables\\
-    \texttt{{\char'134}table*}& 400& For wider tables\\
-    \bottomrule
-  \end{tabular}
-\end{table*}
-
-\section{Math Equations}
-You may want to display math equations in three distinct styles:
-inline, numbered or non-numbered display.  Each of the three are
-discussed in the next sections.
-
-\subsection{Inline (In-text) Equations}
-A formula that appears in the running text is called an inline or
-in-text formula.  It is produced by the \textbf{math} environment,
-which can be invoked with the usual
-\texttt{{\char'134}begin\,\ldots{\char'134}end} construction or with
-the short form \texttt{\$\,\ldots\$}. You can use any of the symbols
-and structures, from $\alpha$ to $\omega$, available in
-\LaTeX~\cite{Lamport:LaTeX}; this section will simply show a few
-examples of in-text equations in context. Notice how this equation:
-\begin{math}
-  \lim_{n\rightarrow \infty}x=0
-\end{math},
-set here in in-line math style, looks slightly different when
-set in display style.  (See next section).
-
-\subsection{Display Equations}
-A numbered display equation---one set off by vertical space from the
-text and centered horizontally---is produced by the \textbf{equation}
-environment. An unnumbered display equation is produced by the
-\textbf{displaymath} environment.
-
-Again, in either environment, you can use any of the symbols and
-structures available in \LaTeX\@; this section will just give a couple
-of examples of display equations in context.  First, consider the
-equation, shown as an inline equation above:
-\begin{equation}
-  \lim_{n\rightarrow \infty}x=0
-\end{equation}
-Notice how it is formatted somewhat differently in
-the \textbf{displaymath}
-environment.  Now, we'll enter an unnumbered equation:
-\begin{displaymath}
-  \sum_{i=0}^{\infty} x + 1
-\end{displaymath}
-and follow it with another numbered equation:
-\begin{equation}
-  \sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f
-\end{equation}
-just to demonstrate \LaTeX's able handling of numbering.
-
-\section{Figures}
-
-The ``\verb|figure|'' environment should be used for figures. One or
-more images can be placed within a figure. If your figure contains
-third-party material, you must clearly identify it as such, as shown
-in the example below.
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=\linewidth]{sample-franklin}
-  \caption{1907 Franklin Model D roadster. Photograph by Harris \&
-    Ewing, Inc. [Public domain], via Wikimedia
-    Commons. (\url{https://goo.gl/VLCRBB}).}
-  \Description{The 1907 Franklin Model D roadster.}
-\end{figure}
-
-Your figures should contain a caption which describes the figure to
-the reader. Figure captions go below the figure. Your figures should
-{\bfseries also} include a description suitable for screen readers, to
-assist the visually-challenged to better understand your work.
-
-Figure captions are placed {\itshape below} the figure.
-
-\subsection{The ``Teaser Figure''}
-
-A ``teaser figure'' is an image, or set of images in one figure, that
-are placed after all author and affiliation information, and before
-the body of the article, spanning the page. If you wish to have such a
-figure in your article, place the command immediately before the
-\verb|\maketitle| command:
-\begin{verbatim}
-  \begin{teaserfigure}
-    \includegraphics[width=\textwidth]{sampleteaser}
-    \caption{figure caption}
-    \Description{figure description}
-  \end{teaserfigure}
-\end{verbatim}
-
-\section{Citations and Bibliographies}
-
-The use of \BibTeX\ for the preparation and formatting of one's
-references is strongly recommended. Authors' names should be complete
---- use full first names (``Donald E. Knuth'') not initials
-(``D. E. Knuth'') --- and the salient identifying features of a
-reference should be included: title, year, volume, number, pages,
-article DOI, etc.
-
-The bibliography is included in your source document with these two
-commands, placed just before the \verb|\end{document}| command:
-\begin{verbatim}
 \bibliographystyle{ACM-Reference-Format}
-  \bibliography{bibfile}
-\end{verbatim}
-where ``\verb|bibfile|'' is the name, without the ``\verb|.bib|''
-suffix, of the \BibTeX\ file.
-
-Citations and references are numbered by default. A small number of
-ACM publications have citations and references formatted in the
-``author year'' style; for these exceptions, please include this
-command in the {\bfseries preamble} (before
-``\verb|\begin{document}|'') of your \LaTeX\ source:
-\begin{verbatim}
-  \citestyle{acmauthoryear}
-\end{verbatim}
-
-  Some examples.  A paginated journal article \cite{Abril07}, an
-  enumerated journal article \cite{Cohen07}, a reference to an entire
-  issue \cite{JCohen96}, a monograph (whole book) \cite{Kosiur01}, a
-  monograph/whole book in a series (see 2a in spec. document)
-  \cite{Harel79}, a divisible-book such as an anthology or compilation
-  \cite{Editor00} followed by the same example, however we only output
-  the series if the volume number is given \cite{Editor00a} (so
-  Editor00a's series should NOT be present since it has no vol. no.),
-  a chapter in a divisible book \cite{Spector90}, a chapter in a
-  divisible book in a series \cite{Douglass98}, a multi-volume work as
-  book \cite{Knuth97}, an article in a proceedings (of a conference,
-  symposium, workshop for example) (paginated proceedings article)
-  \cite{Andler79}, a proceedings article with all possible elements
-  \cite{Smith10}, an example of an enumerated proceedings article
-  \cite{VanGundy07}, an informally published work \cite{Harel78}, a
-  doctoral dissertation \cite{Clarkson85}, a master's thesis:
-  \cite{anisi03}, an online document / world wide web resource
-  \cite{Thornburg01, Ablamowicz07, Poker06}, a video game (Case 1)
-  \cite{Obama08} and (Case 2) \cite{Novak03} and \cite{Lee05} and
-  (Case 3) a patent \cite{JoeScientist001}, work accepted for
-  publication \cite{rous08}, 'YYYYb'-test for prolific author
-  \cite{SaeediMEJ10} and \cite{SaeediJETC10}. Other cites might
-  contain 'duplicate' DOI and URLs (some SIAM articles)
-  \cite{Kirschmer:2010:AEI:1958016.1958018}. Boris / Barbara Beeton:
-  multi-volume works as books \cite{MR781536} and \cite{MR781537}. A
-  couple of citations with DOIs:
-  \cite{2004:ITE:1009386.1010128,Kirschmer:2010:AEI:1958016.1958018}. Online
-  citations: \cite{TUGInstmem, Thornburg01, CTANacmart}. Artifacts:
-  \cite{R} and \cite{UMassCitations}.
-
-\section{Acknowledgments}
-
-Identification of funding sources and other support, and thanks to
-individuals and groups that assisted in the research and the
-preparation of the work should be included in an acknowledgment
-section, which is placed just before the reference section in your
-document.
-
-This section has a special environment:
-\begin{verbatim}
-  \begin{acks}
-  ...
-  \end{acks}
-\end{verbatim}
-so that the information contained therein can be more easily collected
-during the article metadata extraction phase, and to ensure
-consistency in the spelling of the section heading.
-
-Authors should not prepare this section as a numbered or unnumbered {\verb|\section|}; please use the ``{\verb|acks|}'' environment.
-
-\section{Appendices}
-
-If your work needs an appendix, add it before the
-``\verb|\end{document}|'' command at the conclusion of your source
-document.
-
-Start the appendix with the ``\verb|appendix|'' command:
-\begin{verbatim}
-  \appendix
-\end{verbatim}
-and note that in the appendix, sections are lettered, not
-numbered. This document has two appendices, demonstrating the section
-and subsection identification method.
-
-\section{SIGCHI Extended Abstracts}
-
-The ``\verb|sigchi-a|'' template style (available only in \LaTeX\ and
-not in Word) produces a landscape-orientation formatted article, with
-a wide left margin. Three environments are available for use with the
-``\verb|sigchi-a|'' template style, and produce formatted output in
-the margin:
-\begin{itemize}
-\item {\verb|sidebar|}:  Place formatted text in the margin.
-\item {\verb|marginfigure|}: Place a figure in the margin.
-\item {\verb|margintable|}: Place a table in the margin.
-\end{itemize}
-
-%%
-%% The acknowledgments section is defined using the "acks" environment
-%% (and NOT an unnumbered section). This ensures the proper
-%% identification of the section in the article metadata, and the
-%% consistent spelling of the heading.
-\begin{acks}
-To Robert, for the bagels and explaining CMYK and color spaces.
-\end{acks}
-
-%%
-%% The next two lines define the bibliography style to be used, and
-%% the bibliography file.
-\bibliographystyle{ACM-Reference-Format}
-\bibliography{sample-base}
-
-%%
-%% If your work has an appendix, this is the place to put it.
-\appendix
-
-\section{Research Methods}
-
-\subsection{Part One}
-
-Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi
-malesuada, quam in pulvinar varius, metus nunc fermentum urna, id
-sollicitudin purus odio sit amet enim. Aliquam ullamcorper eu ipsum
-vel mollis. Curabitur quis dictum nisl. Phasellus vel semper risus, et
-lacinia dolor. Integer ultricies commodo sem nec semper.
-
-\subsection{Part Two}
-
-Etiam commodo feugiat nisl pulvinar pellentesque. Etiam auctor sodales
-ligula, non varius nibh pulvinar semper. Suspendisse nec lectus non
-ipsum convallis congue hendrerit vitae sapien. Donec at laoreet
-eros. Vivamus non purus placerat, scelerisque diam eu, cursus
-ante. Etiam aliquam tortor auctor efficitur mattis.
-
-\section{Online Resources}
-
-Nam id fermentum dui. Suspendisse sagittis tortor a nulla mollis, in
-pulvinar ex pretium. Sed interdum orci quis metus euismod, et sagittis
-enim maximus. Vestibulum gravida massa ut felis suscipit
-congue. Quisque mattis elit a risus ultrices commodo venenatis eget
-dui. Etiam sagittis eleifend elementum.
-
-Nam interdum magna at lectus dignissim, ac dignissim lorem
-rhoncus. Maecenas eu arcu ac neque placerat aliquam. Nunc pulvinar
-massa et mattis lacinia.
+\bibliography{mybiblio.bib}
 
@@
 \endinput
-%%
-%% End of file `sample-authordraft.tex'.

### 2020-05-29 paper/paper-main.tex
updated
need to be improved more

@@
 \acmISBN{978-1-4503-9999-9/18/06}
+
+\usepackage{listings}
 
@@
 \end{abstract}
+
 %%
@@
 
-Our contribution includes:
+Multiple cluster computing analysis tools have been developed, such as Hadoop MapReduce \cite{ApacheHadoopHomePage}, 
+Apache Spark \cite{ApacheSparkHomePage}, and Apache Flink \cite{ApacheFlinkHomePage} \cite{DBLP:journals/debu/CarboneKEMHT15}. 
+These tools have brought reliable and scalable ways to deal massive data. 
+These has become widely popular, in which data-parallel computations are executed on clusters of unreliable machines by systems that automatically provide locality-aware scheduling, 
+fault tolerance, and load balancing.
 
+These tools are constructed on top of Java Virtual Machine (JVM). JVM abstracts hardware and memory management from the developer so that the development is fairly easy. 
+In addition, Java or Scala compiled code is platform-independent, which can run on any machine with JVM. However, these advantages may be really critical weakness when it comes to 
+processing big data. JVM abstract away most detail regarding memory management from the system designer, including memory deallocation, reuse, and movement, as well as pointers, 
+object serialization and deserialization. Since managing and utilizing memory is one of the most important factors determining Big Data systems' performance, 
+reliance on a managed environment can mean an order-of-magnitude increase in CPU cost for some computations. This cost may be unacceptable for high-performance tool development by an expert.
+
+To overcome these problems, one can use programming languages with more control on hardware, system languages, for development of Big Data tools.
+For example, C++ is a general-purpose, statically typed,
+compiled programming language which supports multiple programming paradigm. It is also a system language which gives full control over hardware. 
+There are several researches or projects \cite{DBLP:conf/sigmod/0001BLLMSTYJ18} where developers and 
+researchers implement Big Data tools with this language. These tools shows significantly better performances than those developed with application languages. 
+Although the evidence of the advantage of building high speed computational tools with C++ has been discovered, the steep learning curve and difficulty of writing memory safe codes are barrier to technology diffusion.
+
+Rust is a system language which gives the similar performance and control of hardware to C++ or C and safety of runtime. The memory-safety, and fearless concurrently in Rust programming 
+make the language one of the ideal candidate for development of Big Data tools. 
+Since the design of the language is different from any other programming languages, implementations that can be selected for algorithms can differ from existing ones.
+In this paper, we focus on memory management strategy for Big Data processing algorithms in development with Rust.
+
+Even though Rust can be a great candidate to develop Big Data processing tools, there are few study for development on such tools with Rust programming.
+
+Rust has various ways to manage memory. Rust has different variable types for values allocated in sequence of memory region. 
+Each variables take different memory representation that can produce variation of operation time on the variable types.
+
+In addition, Reference Counting takes important role in Rust ownership concept. By using Reference Counting, a value is able to have multiple owners.
+This situation may happen quite often, when we want to acquire complex values from contiguous memory regions. 
+Reference Counting has both advantage and disadvantage. 
+Reference count can share data which might decrease unnecessary copy of data, but checking reference count might be a overhead.
+
+Atomic Reference Counting is ubiquitous in Rust multithreading program. Atomic Reference Count also has similar features to Reference Counting. 
+In addition, it is allowed to use among different threads. This may lead additional overhead from atomic operation.
+
+As we can see, we can choose various memory management strategies in Rust programming.
+Therefore, we assess following research question in this thesis.
 \begin{itemize}
-  \item 
-  \item 
+    \item What are better memory management strategies for complex object processing to perform faster runtime performance.
+    \item How much impact do different variable types in Rust have in order to algorithms' runtime performance?
+    \item How much can algorithms runtime be improved or degraded, if we use Reference Count?
+    \item What are better memory management strategies for faster Big Data processing in Rust multithreading?
+    \item How can we improve runtime performance of common Big Data algorithms by Rust memory management?
 \end{itemize}
@@
 
-\cite{Ahoniemi:2006:AGT:1315803.1315830}
+Rust is a system programming language which provides memory safety without runtime checking like GC and necessity of explicit memory de/allocation. 
+To ensure memory safety, Rust provides restrictive coding patterns and checks lifetime of value and memory safety at compile-time.
+The restrictive patterns also enables a developer to write fearless concurrent code that is free of data races.
+Main concepts of Memory Management in Rust are ownership, move, and borrowing.
 
-\section{Evaluation}
+\subsection{Ownership}
+In ownership feature or Rust, each value has a variable called owner.
+This owner has information about the value, such as location in memory, length and capacity of the value. 
+For example, the object representation of Vec$<$i32$>$ is shown in Figure~\ref{fig:rustvec}. The upper boxes represent owner variable in stack frame. 
+The lower boxes represent contiguous memory allocated to store i32. Its capacity is specified 10, but 7 values of i32 are stored. 
+Therefore, there are still spaces to store 3 values of i32 without reallocation of memory. This owner can live on the scope associated with its lifetime.
+When the owner is dropped, the value will be dropped too. This feature is similar to how RAII in C++ works. 
+However, acquisition of owner out of the scope where it was constructed is available in Rust with the concept of move.
+
+\begin{figure}[htb]
+    \includegraphics[width=5cm]{images/rust_vec.eps}
+    \caption{Representation of Rust Vec$<$i32$>$}
+    \label{fig:rustvec}
+\end{figure}
+
+\subsection{Move}
+In Rust, for most types operations like assigning a value to a variable, passing it to a function, or returning it from a function do not copy the value: they move it. 
+With move, a value can be transferred from one owner to another. The previous variable does not have ownership of the value; it is moved to a newly assigned variable. 
+To understand how this assignment implementation is unique from other programing languages, Rust code example for Vec of strings are shown.
+
+\begin{lstlisting}
+    let s = vec!["lemon".to_string, 
+                 "orange".to_string, 
+                 "apple".to_string];
+    let t = s;
+    let u = s;
+ \end{lstlisting}
+
+The representation of the original Vec of String in Rust is the almost same in C++ vector of string. Figure~\ref{fig:rustvecmoved} however shows different behavior when Rust assigns s to t. 
+The value is moved to t from s so that the source variable s is uninitialized. The Rust code actually throws compile error, because we are assigning uninitialized variable at the last line.
+
+\begin{figure}[htb]
+    \includegraphics[width=5cm]{images/rust_vec_moved.eps}
+    \caption{Representation of Rust Vec$<$String$>$ after assignment to another variable}
+    \label{fig:rustvecmoved}
+\end{figure}
+
+\subsection{Borrowing}
+Borrowing lets code use a value temporarily without affecting its ownership so that it reduces unnecessary movement of ownership. 
+One use case is when value is used in function and needed to be passed to the argument. If the argument takes ownership and the function does not return the value, 
+the ownership of value goes out of scope and the memory is deallocated. One can pass reference of the value to the argument instead of owner. 
+The reference goes out of scope, but ownership remains the same.
 

### 2020-05-31 paper/paper-main.tex
related work

@@
 
+\subsection{Type of Variable}
+\label{sec:concept_diffval}
+In Rust, there are three variable types: owner, reference, and slice (only for sequence of values). 
+A developer is sometimes forced to use specific variable types. For example, some of methods are only implemented to specific variable types.
+However, one can select any variable types for operation in most case.
+
+These variables have different memory representation shown in Figure~\ref{fig:own_ref_slice}.
+The owner has a pointer pointing to the memory address of sequence values, length of the values, and capacity allocated to store additional values. 
+Reference and Slice are variables borrowing value owned by other variable. The reference is a pointer that points to the owner. 
+The slice is a pointer that points to memory address of sequence values. It has value such as length of sequence values stored in the memory. 
+Since they have different memory representation, an assumption is that it takes different time to access to the contents of the memory among these pointer types.
+We examine this by constructing complex objects whose fields are these variable types. The details are explained in Section~\ref{sec:eval_diffval}.
+
+\begin{figure}[htb]
+    \includegraphics[width=5cm]{images/own_ref_slice.eps}
+    \caption{Memory Representation of Owner, Reference, and Slice Type}
+    \label{fig:own_ref_slice}
+\end{figure}
+
+\subsection{Reference Count}
+\label{sec:concept_refcount}
+Reference is useful to avoid movement of ownership. However, one needs to track its lifetime and explicitly includes it in code, 
+because Rust compiler cannot infer it. This can be another encumbrance. We can instead acquire multiple owners to single value by using Reference Counting (Rc). 
+By leveraging Rc, a value can be shared like what borrowing plays the role in Rust programming.
+
+The difference is that Rc checks number of owner pointing to the actual data and makes sure the data is not deleted 
+until all the owners are dereferenced. Using Rc is sometimes preferable approach for developers especially when lifetime planning is extremely difficult.
+However, the possible problems regarding to Rc are the cost for tracking the number of references and allocating memory on heap instead of stack.
+Having these assumption, an experiment is conducted to examine difference of runtime performance of dropping reference and Rc.
+
+\subsection{Multithread}
+\label{sec:concenpt_multithreading}
+In Rust programming, writing concurrent code is relatively easy. The care Rust takes with reference, mutability, and lifetimes is valuable enough in single-threaded programs, 
+but it also is in concurrent programming. Rust has tools to write concurrent code, such as threads, locks, atomic reference. 
+One can implement various concurrent codes for the same purpose with different memory management strategies. 
+The most ubiquitous tool used in Rust concurrent code is Atomic Reference Counting (Arc).
+
+Arc is a simple interface that allows threads to share data. Arc allows multiple variable to have ownerships of a particular value similarly to Rc, 
+but also supports atomic feature enabling the ownerships exist in different threads. 
+In many situation where developer write a multithreading code, the deletion of Arc happens significant amount of times. 
+Similarly to Rc, our assumption is that deletion of Arc has also overhead when we compare to normal reference. 
+To assess runtime performances of algorithm with Arc vs normal reference, we implement merge-sort algorithm in two different ways.
+
 \section{Conclusion}

### 2020-06-28 thesis_template/0_Prelim/abs.tex
corrected

@@
 Many existing modern cloud-based data processing systems such as Hadoop, Spark or Flink use
-Java Virtual Machine (JVM) and taking full advantage of features such as automated memory management in JVM
+Java Virtual Machine (JVM) and take full advantage of features such as automated memory management in JVM
 including Garbage Collection (GC) which may lead to a significant overhead.
@@
 
-System languages like C++ or Rust seems to be a better choice to
+System languages like C++ or Rust seem to be a better choice to
 develop systems for Big Data processing because they do not relay on JVM.
@@
 Rust programming language includes many possible strategies to optimize memory management for Big Data processing including
-selection of different variable types, use of Reference Counting, and multithreading with Atomic Reference Counting.
+a selection of different variable types, use of Reference Counting, and multithreading with Atomic Reference Counting.
 

### 2020-06-28 thesis_template/0_Prelim/ack.tex
corrected

@@
 Foremost, I would like to show my appreciation to my advisor Prof. Kia Teymourian for his guidance, encouragement and support.
-His expertise and insights were essential for this research work. His passion for research and education motivates me and push this thesis to be a precious work for me.
+His expertise and insights were essential for this research work. His passion for research and education motivates me and his experience is instrumental to the completion of the thesis.
 
@@
 
-Finally, I would like to express special thanks to my parents to support this excellent educational opportunity.
+Finally, I would like to express special thanks to my parents for supporting this excellent educational opportunity.
 

### 2020-06-28 thesis_template/1_Intro/intro.tex
corrected

@@
 \label{sec:motivation}
-Cluster computing tool for Big Data Analysis has been more important as magnitude and quality of data that we can obtain increases. 
+Cluster computing tools for Big Data Analysis have been more important as magnitude and quality of data that we can obtain increases. 
 Recently, almost all businesses stand on data, from web marketing analysis to factory automations. The leverage of data is ubiquitous, because 
@@
 
-However these computation resources do not come for free; we need to pay money to use these resources. Usually, user needs to pay depending on usage of computational resources. 
-If your process of data analysis is too long or need to use number of clusters with high speck specification, the cost may end up significantly hight.
+However these computation resources do not come for free; we need to pay money to use these resources. Usually, users need to pay depending on usage of computational resources. 
+If your process of data analysis is too long or needs to use number of clusters with high speck specification, the cost may end up significantly hight.
 To address these problems, the quality of analysis tool is critical. If the tool can optimize the runtime performance and usage of computational resources, 
@@
 These tools are constructed on top of Java Virtual Machine (JVM). JVM abstracts hardware and memory management from the developer so that the development is fairly easy. 
-In addition, Java or Scala compiled code is platform-independent, which can run on any machine with JVM. However, these advantages may be really critical weakness when it comes to 
+In addition, Java or Scala compiled code is platform-independent, which can run on any machine with JVM. However, these advantages may be really critical weaknesses when it comes to 
 processing big data. JVM abstract away most detail regarding memory management from the system designer, including memory deallocation, reuse, and movement, as well as pointers, 
 object serialization and deserialization. Since managing and utilizing memory is one of the most important factors determining Big Data systems' performance, 
-reliance on a managed environment can mean an order-of-magnitude increase in CPU cost for some computations. This cost may be unacceptable for high-performance tool development by an expert.
+reliance on a managed environment can mean an order-of-magnitude increase in CPU cost for some computations. This cost may be unacceptable for a high-performance tool development by an expert.
 
@@
 researchers implement Big Data tools with this language. These tools shows significantly better performances than those developed with application languages. 
-Although the evidence of the advantage of building high speed computational tools with C++ has been discovered, the steep learning curve and difficulty of writing memory safe codes are barrier to technology diffusion.
+Although the evidence of the advantage of building high speed computational tools with C++ has been discovered, the steep learning curve and difficulty of writing memory safe codes are barriers to technology diffusion.
 
@@
 
-Even though Rust can be a great candidate to develop Big Data processing tools, there are few study for development on such tools with Rust programming.
+Even though Rust can be a great candidate to develop Big Data processing tools, there are few studies for development on such tools with Rust programming.
 
@@
 
-In addition, Reference Counting takes important role in Rust ownership concept. By using Reference Counting, a value is able to have multiple owners.
+In addition, Reference Counting takes an important role in Rust ownership concept. By using Reference Counting, a value is able to have multiple owners.
 This situation may happen quite often, when we want to acquire complex values from contiguous memory regions. 
@@
 Atomic Reference Counting is ubiquitous in Rust multithreading program. Atomic Reference Count also has similar features to Reference Counting. 
-In addition, it is allowed to use among different threads. This may lead additional overhead from atomic operation.
+In addition, it can be used among different threads. This may lead additional overhead from atomic operation.
 

### 2020-06-28 thesis_template/2_RelatedWork/model/application_to_system_language.tex
need object size and conclusion documentation
corrected

@@
-Considered overhead produced by Memory Management in JVM, use of system language for development of Big Data tool can be one of solutions rather than application language, such as Java and Scala. 
-System languages, such as C and C++, are languages that give developer total control over the hardware and de/allocation of memory without GC. 
-These features enable program written in system languages to optimized performance taking full advantage of hardware.
+Considering the overhead produced by Memory Management in JVM, use of system language for development of Big Data tools can be a better solution rather than application languages, such as Java and Scala.
+System languages, such as C and C++, are languages that give developers total control over the hardware and de/allocation of memory without GC. 
+These features enable programs written in system languages to optimize performance taking full advantage of hardware.
 
-To take example, one can build Big Data tool with C++. C++ is one of the most popular system languages which has Object-oriented features. 
-C++ has functions which provide control over memory to developers. In another word, it is responsibility for one to manage memory properly and safely. 
+For example, one can build Big Data tools with C++. C++ is one of the most popular system languages which has Object-oriented features. 
+C++ has functions which provide control over memory to developers. In another words, it is responsible for managing memory properly and safely. 
 The functions, malloc() and free(), take roll for memory allocation and deallocation in respectively. The manual memory de/allocation may cause several problems and require developers 
-attention to the problems with significant effort for debugging and testing. Here, we explain two of the most common problems regarding to memory management in existing system languages.
+attention to the problems with significant effort for debugging and testing. Here, we explain two of the most common problems regarding memory management in existing system languages.
 
@@
 because of deallocation of memory without modification of value of the pointer. 
-If the memory region is reallocated for other object and the dangling pointer tries to access the original object, the unpredictable behavior may result.
+If the memory region is reallocated for other objects and the dangling pointer tries to access the original object, the unpredictable behavior may result.
 
-Memory leak occurs when memory is allocated and no longer referenced so that the object in the memory location cannot be reached and released.
-This is result of dereferencing object without deallocation. Memory leak consumes more memory than necessary by making unreachable location.
+Memory leaks occur when memory is allocated and no longer referenced so that the object in the memory location cannot be reached and released.
+This is result of dereferencing object without deallocation. Memory leaks consume more memory than necessary by making unreachable location.
 
-Some solutions are established to address these problems. Actually GC is a high-level solution that guarantees memory safety. 
+Some solutions are established to address these problems. Actually, GC is a high-level solution that guarantees memory safety. 
 C++ has a different solution called Resource Acquisition is Initialization (RAII). In RAII, objects can live within the scope where they are created. 
 The memory is released when the object goes out of scope. This solution is more predictable and deterministic than GC. 
-However, it is problematic When we need the object out of the scope, returning a value from a function. 
+However, it is problematic when we need the object out of the scope, returning a value from a function. 
 There are several ways to go around this problems, such as smart pointers, copy constructors, and move semantics. 
-Nevertheless, these non-orthogonal concepts makes code in disorganize and leads to error prone implementation.
+Nevertheless, these non-orthogonal concepts may disorganize code and lead to error prone implementation.

### 2020-06-28 thesis_template/2_RelatedWork/model/gctuning.tex
corrected

@@
 There are many different ways that one can improve the performance of GC in Java. One of these is for example avoiding pointer-based data structures, such as HashMap and LinkedList. 
-These objects have a "wrapper" object for each entry so that number of object tends to be larger than when when an array is used.
+These objects have a "wrapper" object for each entry so that number of objects tends to be larger than when when an array is used.
 
-Caching serialized object in memory also reduce number of object and memory usage since the set of objects become a byte or binary array. 
+Caching serialized objects in memory also reduces the number of objects and memory usage since the set of objects become a byte or binary array. 
 Spark SQL applications use DataFrames\cite{DBLP:conf/sigmod/ArmbrustXLHLBMK15}, 

### 2020-06-28 thesis_template/2_RelatedWork/model/hadoop_to_spark.tex
corrected

@@
-In several Big Data mining tools that have been developed, the most notable ones are MapReduce and Spark. MapReduce is a cluster computing framework 
+Among Big Data mining tools that have been developed, the most notable ones are MapReduce and Spark. MapReduce is a cluster computing framework 
 which supports locality-aware scheduling, fault tolerance, and load balancing. Spark is designed to improve performance for iterative jobs keeping features of MapReduce.
@@
 
-Iterative job is especially common in Machine Learning Algorithm, such as learning a data model using Gradient Descent.
+Iterative job is especially common in Machine Learning algorithms, such as learning a data model using Gradient Descent.
 In traditional MapReduce framework, each iteration can be expressed as single MapReduce job
@@
 
-Interactive analysis is also an inevitable task in modern data science. A data scientist wants tp perform exploratory analysis in interactive way. 
-Nevertheless, MapReduce is designed in the way more stable for ad-hoc query, so each analysis can be single MapReduce job. 
-To perform multiple analysis to explore dataset, the data needs to be written to and reload from disk many times.
+Interactive analysis is also an inevitable task in modern data science. A data scientist wants to perform exploratory analysis in interactive way. 
+Nevertheless, MapReduce is designed in a way more stable for ad-hoc queries, so each analysis can be single MapReduce job. 
+To perform multiple analyses to explore dataset, the data needs to be written to and reloaded from disk many times.
 
@@
 Some of the notable improvements are shown here\cite{DBLP:journals/pvldb/ShiQMJWRO15}.
-For aggregation operation, map output selectivity, which is the ration of the map output size to the job input size,
+For aggregation operations, map output selectivity, which is the ration of the map output size to the job input size,
 can be significantly reduced by using Spark. Spark uses a map side combiner, hash-based aggregation which is more efficient than sort-based aggregation used in MapReduce. 
-For iterative operation, caching the input as Resilient Distributed Datasets (RDDs) can reduce CRU and disk I/O overheads for sequence iteration. 
+For iterative operations, caching the input as Resilient Distributed Datasets (RDDs) can reduce CRU and disk I/O overheads for sequence iteration. 
 This RDD caching takes a significant role to improve iterative job, because it is more efficient than other low-level caching approaches such as OS buffer caches, and HDFS caching. 

### 2020-06-28 thesis_template/2_RelatedWork/model/intro.tex
corrected

@@
 This chapter describes the related work and concepts to our research in this thesis. 
-In Section~\ref{sec:os}, some of topics in Operating Systems are described focusing on memory management in operating systems.
+In Section~\ref{sec:os}, some topics in Operating Systems are described focusing on memory management in operating systems.
 Knowledge of operating systems helps us to understand how operating systems handle memory management and 
-how other technologies takes advantage of them. Even though this thesis does not focus technologies used for Linear Algebra Computation, 
+how other technologies takes advantage of them. Even though this thesis does not focus on technologies used for Linear Algebra Computation, 
 there are some active researches in technologies in Linear Algebra Computation for Big Data processing. 
-It worths to study these concepts explained in Section~\ref{sec:linalg}. 
+It is worth studying these concepts explained in Section~\ref{sec:linalg}. 
 In Section~\ref{sec:hadoopspark}, major Big Data processing tools and improvement of these tools are introduced. 

### 2020-06-28 thesis_template/2_RelatedWork/model/llvm.tex
corrected

--- 2020-04-03 thesis_template/2_RelatedWork/model/llvm.tex
@@
-LLVM (Low Level Virtual Machine) is an umbrella project which contains components of compilation of programming language.
+LLVM (Low Level Virtual Machine) \cite{DBLP:conf/cgo/LattnerA04} is an umbrella project which contains components of compilation of programming languages.
 Existing compilers have tightly coupled functionalities so that it is not possible to embed them into other applications.
-However, the abstract framework of LLVM decouples the functionalities into peaces and the peaces of functionalities can be reused.
+However, the abstract framework of LLVM decouples the functionalities into pieces and the pieces of functionalities can be reused.
 
 In structure of a compiler, there are three main components; frontend, optimizer, and backend. 
-In frontend, a developer designs the interface of source programming language in way where it can be optimized by optimizer. 
-Then, backend takes optimized code and produce the native machine code. LLVM has a component called LLVM Intermediate Representation (IR), 
+In frontend, a developer designs the interface of source programming language in a way where it can be optimized by an optimizer. 
+Then, backend takes optimized code and produce the native machine code.
+
+This separation of functionalities gives reusability to parts of the compiler. Establishing new programming language requires new frontend, 
+but the existing optimizer and back end can be reused. This speeds up processes of developing new programming languages.
+
+The reusability of compiler leads to support multiple programming languages 
+so that broader set of programmers are involved in the development. 
+For open source projects like Rust, This ends up larger community of potential contributors to the development.
+
+Since implementation of frontend can be independent on optimizer and backend, 
+development of programming languages becomes easy for people without skills required to implement optimizer and backFend.
+This thrives new language development.
+
+LLVM has a component called LLVM Intermediate Representation (IR), 
 which places itself across frontend to optimizer. IR is designed to host mid-level analyses and transformations that you find in optimizer section of a compiler.
@@
 IR is useful in terms of frontend. This is because developer of language frontend need to know only how the IR works and use the framework to develop a language.
+
+Thanks to emerging of LLVM, many new programming languages and compilers have been developed. Rust compiler is also developed based on LLVM.

### 2020-06-28 thesis_template/2_RelatedWork/model/os.tex
corrected

@@
 Basically, each process does not share their memory. However, for multiprocessing, we could avoid this restriction.
-Processes can be represented as tree structure, because a process may create other child processes.
-Process has 4 states, new, running, waiting, and ready. 
-Process is represented in process control block (PCB) with state type, process ID, registers, and so on.
-The scheduling for process assigning to CPU core is implemented in queues containing PCB. There are two main queues in this scheduler: 
+Processes can be represented as tree structures, because a process may create other child processes.
+Processes have 4 states, new, running, waiting, and ready. 
+Processes are represented in process control block (PCB) with state type, process ID, registers, and so on.
+The scheduling for processes assigning to CPU core is implemented in queues containing PCB. There are two main queues in this scheduler: 
 ready queue and wait queue. The head of process in ready queue is selected for execution and once the process requested I/O request or 
-production of child process, the running process will be stored n wait queue. Once the request that the process waiting for end, 
+production of child process, the running process will be stored n wait queue. Once the request that the process is waiting for its end, 
 the waiting process will be pushed tail of ready queue.
@@
 Processes executing concurrently in the operating system may be either independent processes or cooperating processes executing in the system.
-A process is independent if it does not share data with any other processes. A process cooperating if it can affect or be affected by the 
-other processed executing in the system. In cooperating process, there are two kinds, shared memory and message passing. 
+A process is independent if it does not share data with any other processes. A process is cooperating if it can affect or be affected by the 
+other processed executing in the system. In cooperating processes, there are two kinds, shared memory and message passing. 
 In shared memory, it removes restriction of not interfering memory region. Message passing can be useful for distribution systems as well.
@@
 A socket is identified by an IP address concatenated with a port number. When two process communicate, each process will have socket. 
-If another process of the same machine wants to communicate, we need new socket to be established. The protocol used in the socket connection
+If another process of the same machine wants to communicate, we need a new socket to be established. The protocol used in the socket connection
 can be TPC and UDP.
@@
 Multi-threading is increasingly popular as the multicore programming becomes in common, because we can run multiple thread on different core.
-Creating thread is much cheaper than creating process and it shares resources so that we do not need additional methods to allow threads to 
+Creating threads is much cheaper than creating processes and it shares resources so that we do not need additional methods to allow threads to 
 communicate each other, such as sharing memory and message passing.
@@
 
-Usually a program resides on a disk as binary executable file. To run, the program must be brought into memory and placed within the context of a process.
-The process is bound to corresponding parts of the physical memory. Binding program to memory address is staging process. 
+Usually, a program resides on a disk as binary executable file. To run, the program must be brought into memory and placed within the context of a process.
+The process is bound to corresponding parts of the physical memory. Starting processes binds programs to the memory address. 
 There three stages: compile time, load time execution time. The source program is compiled by compiler producing object file. 
@@
 
-If where the process will reside in memory at compile time, absolute code is generated. If this is unknown at the time, 
+If the process will reside in memory at compile time, absolute code is generated. If this is unknown at the time, 
 the binding will be done at load time. At this time, the compiler must generate relocatable code. Otherwise, the binding will be done at 
@@
 The first part of process of demand paging would be that we check an internal table to check whether the reference is valid or invalid.
-If the reference is valid, the process reads the content from the memory. Otherwise, we terminates the process and find the free frame in 
+If the reference is valid, the process reads the content from the memory. Otherwise, we terminate the process and find the free frame in 
 physical memory. Then, we schedule a secondary storage operation to read the desired page into newly allocated frame. 
-When the storage complete reading the page, we modify the internal table to indicate the page is now in memory. 
+When the storage finished reading the page, we modify the internal table to indicate that the page is now in memory. 
 Finally, we restart the instruction that was interrupted.
 
-However, there would be a case where the memory does not have any free frame. In this case, a victim frame that will be replaced with new coming frame should be selected. 
+However, there could be a case where the memory does not have any free frame. In this case, a victim frame that will be replaced with new coming frame should be selected. 
 To perform this selection efficiently, a modify bit is tracked for each frame or page. The modify bit represents whether the page is modified since it is loaded from secondary storage. 
-If the page or frame is modified, when we swap page we need to update the content in the secondary storage. However, it is not modified, we can simply delete the frame and replace with new frame.
+If the page or frame is modified, when we swap page we need to update the content in the secondary storage.
+However, if it is not modified, we can simply delete the frame and replace it with new frame.
 

### 2020-06-28 thesis_template/2_RelatedWork/model/rust_memory_management.tex
need object size and conclusion documentation
corrected

@@
 \subsection{Move}
-In Rust, for most types operations like assigning a value to a variable, passing it to a function, or returning it from a function do not copy the value: they move it. 
-With move, a value can be transferred from one owner to another. The previous variable does not have ownership of the value; it is moved to a newly assigned variable. 
+In Rust, for most types of operations like assigning a value to a variable, passing it to a function, or returning it from a function does not copy the value: it moves it. 
+With each move, a value can be transferred from one owner to another. The previous variable does not have ownership of the value; it is moved to a newly assigned variable. 
 To understand how this assignment implementation is unique from other programing languages, Java, C++, and Rust code example of assigning list or vector of strings are shown.

### 2020-06-28 thesis_template/2_RelatedWork/model/spark.tex
corrected

@@
 
-A RDD is essentially a multi-layer Java data structure. A top RDD object references Java array, which intern, references a set of tuple objects. 
+A RDD is essentially a multi-layer Java data structure. A top RDD object references Java array, which in tern, references a set of tuple objects. 
 The coarse-grained transformations and immutability requires a RDD to be deep-copied to produce a new RDD, but efficiently offers fault tolerance. 
@@
 Spark-pipeline consists of sequence of transformations and actions over RDDs. A transformation produces a new RDD from a set of existing RDD. 
-An action is method that computes statistics from an RDD. Due to lazy-evaluation nature, transformations do not materialize the newly created RDD. 
+An action is a method that computes statistics from an RDD. Due to lazy-evaluation nature, transformations do not materialize the newly created RDD. 
 Instead, RDD Lineages are created. Lineage is a graph among parent and child RDDs which represents logical execution plan. 
@@
 
-All data of these types on JVM heap is managed by JVM GC. GC check references graph of objects, mark whether the objects are used and deallocate memory space occupied by unused objects. 
-There are three popular GCs: Parallel, CMS and G1. All of these method track generation of object based on the region of memory. 
+All data of these types on JVM heap is managed by JVM GC. GC check reference graphs of objects, mark whether the objects are used and deallocate memory space occupied by unused objects. 
+There are three popular GCs: Parallel, CMS and G1. All of these methods track generation of objects based on the region of memory. 
 The Java logical heap structure is shown in Figure~\ref{fig:javaheap}.
@@
 Because of the problem of STW and copying objects to different physical memory pages , JVM GC cause huge overhead when number of objects is large. 
-Therefore, GC become severe issue in Big Data processing where might produce significant number of object.
+Therefore, GC becomes a severe issue in Big Data processing where it might produce significant number of object.
 

### 2020-06-28 thesis_template/2_RelatedWork/model/summary.tex
corrected

@@
 The topics of Operating Systems and Linear Algebra Computation are not directly relevant to our research, 
-but it is worth to cover these topics for deep analysis of experimental result. 
+but it is worth covering these topics for deep analysis of experimental result. 
 The advantage and disadvantage of modern Big Data processing tools are discussed and 
-some of solutions are introduced. Finally, how Rust can be a good candidate for development of Big Data processing tools and 
-details of its technologies are described. In next chapter, we discuss main concepts needed to understand theoretical assumption of our experiments.
+some solutions are introduced. Finally, how Rust can be a good candidate for development of Big Data processing tools and 
+details of its technologies are described. In the next chapter, we discuss main concepts needed to understand theoretical assumptions of our experiments.

### 2020-06-28 thesis_template/3_Body/chapter/concept.tex
corrected

@@
 This chapter discusses the concepts studied in our experiments. 
-Section~\ref{sec:concept_diffval} explains different variable type we can use in Rust programming.
-In Section~\ref{sec:concept_refcount}, we explain the advantage and disadvantage of Reference Count in Rust. 
+Section~\ref{sec:concept_diffval} explains different variable types we can use in Rust programming.
+In Section~\ref{sec:concept_refcount}, we explain the advantages and disadvantages of Reference Count in Rust. 
 Multithread programming in Rust is studied in Section~\ref{sec:concenpt_multithreading}. 
@@
 
-\section{Type of Variable}
+\section{Types of Variables}
 \label{sec:concept_diffval}
@@
 A developer is sometimes forced to use specific variable types. For example, some of methods are only implemented to specific variable types.
-However, one can select any variable types for operation in most case.
+However, one can select any variable type for operation in most cases.
 
@@
 Reference and Slice are variables borrowing value owned by other variable. The reference is a pointer that points to the owner. 
-The slice is a pointer that points to memory address of sequence values. It has value such as length of sequence values stored in the memory. 
-Since they have different memory representation, an assumption is that it takes different time to access to the contents of the memory among these pointer types.
+The slice is a pointer that points to memory addresses of sequence values. It has values such as length of sequence values stored in the memory. 
+Since they have different memory representations, an assumption is that it takes different time to access the contents of the memory among these pointer types.
 We examine this by constructing complex objects whose fields are these variable types. The details are explained in Section~\ref{sec:eval_diffval}.
@@
 \label{sec:concept_refcount}
-Reference is useful to avoid movement of ownership. However, one needs to track its lifetime and explicitly includes it in code, 
+References are useful to avoid movement of ownership. However, one needs to track its lifetime and explicitly includes it in code, 
 because Rust compiler cannot infer it. This can be another encumbrance. We can instead acquire multiple owners to single value by using Reference Counting (Rc). 
@@
 
-The difference is that Rc checks number of owner pointing to the actual data and makes sure the data is not deleted 
-until all the owners are dereferenced. Using Rc is sometimes preferable approach for developers especially when lifetime planning is extremely difficult.
-However, the possible problems regarding to Rc are the cost for tracking the number of references and allocating memory on heap instead of stack.
+The difference is that Rc checks the number of owners pointing to the actual data and makes sure the data is not deleted 
+until all the owners are dereferenced. Using Rc is sometimes the preferred approach for developers especially when lifetime planning is extremely difficult.
+However, the possible problems regarding Rc are the cost for tracking the number of references and allocating memory on heaps instead of stacks.
 Having these assumption, an experiment is conducted to examine difference of runtime performance of dropping reference and Rc. 
@@
 but also supports atomic feature enabling the ownerships exist in different threads. 
-In many situation where developer write a multithreading code, the deletion of Arc happens significant amount of times. 
-Similarly to Rc, our assumption is that deletion of Arc has also overhead when we compare to normal reference. 
-To assess runtime performances of algorithm with Arc vs normal reference, we implement merge-sort algorithm in two different ways.
+In many situation where developers write a multithreading code, the deletion of Arc happens a significant amount of times. 
+Similarly to Rc, our assumption is that deletion of Arc also has overhead when we compare to normal references. 
+To assess runtime performances of algorithm with Arc vs normal references, we implement merge-sort algorithm in two different ways.
 
@@
 \label{sec:concept_treeagg}
-Finally, we implement some of algorithm common in Big Data processing. One of them is tree-aggregate.
+Finally, we implement some of common algorithms in Big Data processing. One of them is tree-aggregate.
 
-Tree-aggregate is a communication patten heavily used for Machine Learning algorithm in Spark (MLlib \cite{DBLP:journals/jmlr/MengBYSVLFTAOXX16}). 
+Tree-aggregate is a communication patten heavily used for Machine Learning algorithms in Spark (MLlib \cite{DBLP:journals/jmlr/MengBYSVLFTAOXX16}). 
 The topology of aggregation patterns in Apache Spark are shown in Figure~\ref{fig:aggregationk_patttern}. 
-In the traditional aggregation function in Spark, results of aggregation in all executor clusters are sent to the driver. 
+In the traditional aggregation functions in Spark, results of aggregation in all executor clusters are sent to the driver. 
 That is why this operation suffers from the CPU cost in merging partial results and the network bandwidth limit.
@@
 Spark generates intermediate objects from RDDs. In Tree-aggregation, aggregated HashMap like data structure is created in each thread or node. 
-When it aggregates objects in RDD, copy of objects should be performed to construct intermediate aggregated data structure.
-In another possible way that might be implemented, one can use reference to the objects to perform aggregation instead of copying the values themselves.
+When it aggregates objects in RDD, copies of objects should be performed to construct intermediate aggregated data structure.
+In another possible way that might be implemented, one can use references to the objects to perform aggregation instead of copying the values themselves.
 In Rust, we can clone or get Arc (Rc if in single thread) of objects to implement these operations.
 
-Since Tree-aggregation algorithm generates and deletes a lot of intermediate data structures, 
-how the data structures are constructed and how they are deallocated is important concern in memory management in this algorithm.
+Since Tree-aggregation algorithms generate and delete a lot of intermediate data structures, 
+how the data structures are constructed and how they are deallocated is an important concern in memory management in this algorithm.
 In our experiment, tree-aggregation algorithms are examined in multi-threading. The detail is described in section 3.2.
@@
 \label{sec:concept_knn}
-The other algorithm common in Big Data processing is K-nearest-neighbors (KNN). KNN is a traditional Machine Learning algorithm which classify targets into categories. 
+The other algorithm common in Big Data processing is K-nearest-neighbors (KNN). KNN is a traditional Machine Learning algorithm which classifies targets into categories. 
 In training KNN, it simply stores all available training data without calculation. At prediction phase, targets are given and similarity measures are calculated. 
-Based on these similarities, the algorithm selects \(K\) (user-defined number) training observations similar to the each target. 
-Then, it checks corresponding categories of the \(K\) observations to determine predicted category.
+Based on these similarities, the algorithm selects \(K\) (user-defined number) training observations similar to each target. 
+Then, it checks corresponding categories of the \(K\) observations to determine predicted categories.
 
@@
 If training data has \(N\) observations and test data has \(M\) observations, KNN needs to calculate \(N \times M\) similarity measures. 
-Sort or binary heap can be used to select the \(K\) most similar training observations.
+Sort or binary heaps can be used to select the \(K\) most similar training observations.
 
@@
 There are three phases in our algorithm: preprocessing, query, and combine phase. 
-In preprocessing phase, the algorithm calculates Term-frequencies (Tfs) to generate numeric feature vectors and matrices. 
-In query phase, similarity measures are calculated and \(K\) nearest neighbors are selected. 
+The preprocessing phase, the algorithm calculates Term-frequencies (Tfs) to generate numeric feature vectors and matrices. 
+In the query phase, similarity measures are calculated and \(K\) nearest neighbors are selected. 
 For similarity measure, our choice is cosine similarity(~\ref{eq:cosine}). 
-In combine phase, results of query phase are gathered and combined from each threads.
+In the combine phase, results of query phase are gathered and combined from each threads.
 
@@
 
-Even though preprocessing phase is not specific process for KNN algorithm, 
+Even though the preprocessing phase is not specific process for KNN algorithm, 
 it is common in algorithms used in Natural Language Processing. Therefore, better memory management strategy should be applied in this preprocessing phase.
@@
 In query phase, we control batch size to examine how size of objects allocated simultaneously in memory has impact to algorithm's runtime performance.
-The detail implementation is explained in section3.2.
+The detailed implementation is explained in section 3.2.
 
@@
 \label{sec:concept_compobj}
-To conduct experiments for above concepts, we use the 4 types of complex object: CustomerOwned, CustomerBorrowed, CustomerSlice, and CustomerRc. 
-These object contains other type of object: OrderOwned, OrderBorrowed, OrderSlice, and OrderRc.
+To conduct experiments for the above concepts, we use 4 types of complex objects: CustomerOwned, CustomerBorrowed, CustomerSlice, and CustomerRc. 
+These objects contain other type of objects: OrderOwned, OrderBorrowed, OrderSlice, and OrderRc.
 The representation of these objects are shown in Figure~\ref{fig:customer} and Figure~\ref{fig:order}. 
 Three Customer objects have 15 fields: 3 fields for i32, 3 fields for f64, 8 fields for String, and 1 field for Order object.
-All of fields of CustomerOwned and OrderOwned are owned by the object. On the other hand, fields of CustomerBorrowed, CustomerSlice, OrderBorrowed, and OrderSlice are borrowed. 
-Reference of slice of values are used as the fields and owner of actual values are stored differently in source Vec. 
+All fields of CustomerOwned and OrderOwned are owned by the object. On the other hand, fields of CustomerBorrowed, CustomerSlice, OrderBorrowed, and OrderSlice are borrowed. 
+References of slices of values are used as the fields and owners of actual values are stored differently in source Vec. 
 CustomerRc acquires Rc of values used for its fields from the source Vec.
@@
 \label{sec:concept_summary}
-We discussed some of concepts to understand goals of our experiments. 
+We discussed some concepts to understand goals of our experiments. 
 Theoretical discussions are noted in this chapter, such as assumptions where behavior of different variable types differ from each other, the impact of use of Reference Counting and Atomic Reference Counting,
-and the best practice to implement algorithms used in Big Data processing. In Chapter\ref{chapter:evaluation}, it discusses details setting of our experiments, their results and analysis.
+and the best practice to implement algorithms used in Big Data processing. In Chapter\ref{chapter:evaluation}, we discuss detailed settings of our experiments, their results and analysis.
 

### 2020-06-28 thesis_template/3_Body/chapter/evaluation.tex
corrected

@@
 \label{sec:eval_intro}
-In this chapter, detail experiment settings, executions and results are discussed.
-Section~\ref{sec:eval_setdetail} details hardware configurations and data set we use. 
+In this chapter, detailed experiment settings, executions and results are discussed.
+Section~\ref{sec:eval_setdetail} details hardware configurations and datasets we use. 
 There are 5 experiments conducted. In Section~\ref{sec:eval_diffval}, we discuss the experiment 
-where we assess runtime to access object's field with different variable types. 
+where we assess runtime to access object's fields with different variable types. 
 Section~\ref{sec:eval_refcount} shows details to examine how behaviors of normal reference and Reference Count are different. 
 Section~\ref{sec:eval_sort} describes our Merge-sort experiment to examine behavior of Atomic Reference Counting.
-Two algorithms are discussed used in Big Data processing and examined in our experiments: 
+Two algorithms are used in Big Data processing and examined in our experiments: 
 Tree-aggregate in Section~\ref{sec:concept_treeagg} and K-Nearest-Neighbors in Section~\ref{sec:concept_knn}.
@@
 
-\section{Experiment 1: Accessing Object with Different Variable Type}
+\section{Experiment 1: Accessing Objects with Different Variable Types}
 \label{sec:eval_diffval}
@@
 \label{sec:eval_summary}
-In this chapter, we examines various memory management strategies for different algorithms in Rust programming.
+In this chapter, we examine various memory management strategies for different algorithms in Rust programming.
 There are many factors that might differ performance of algorithms: different variable type, Reference Counting, Atomic Reference Counting, and frequency of memory de/allocation.
 We should select the best memory management strategies when developing Big Data processing tools. 
-Some of tips for the development are proved in our experiments. We conclude this thesis in Chapter~\ref{chapter:Conclusions}.
+Some tips for the development are proven in our experiments. We conclude this thesis in Chapter~\ref{chapter:Conclusions}.
 

### 2020-06-28 thesis_template/3_Body/model/access_own_reference_slice.tex
corrected

@@
-This experiment is conducted to provide answers to the following two questions. One is how different variable types have impact to runtime performance.
-The other is how initialization of Vec size has impact to runtime performance. 
-In this experiment, we focus on owner, reference, and slice as a variable of sequence values. 
+This experiment is conducted to provide answers to the following two questions. One is how different variable types impact runtime performance.
+The other is how initialization of Vec size impacts runtime performance. 
+In this experiment, we focus on owner, reference, and slice as variables of sequence values. 
 Since these variables have different memory representation, there might be differences among time for access to actual values of each variables.
 
-To evaluate this assumption, we use the three types of complex object: CustomerOwned, CustomerBorrowed and CustomerSlice. 
+To evaluate this assumption, we use the three types of complex objects: CustomerOwned, CustomerBorrowed and CustomerSlice. 
 At first, we generate source Vecs for all fields, Vecs which contain all elements used for corresponding fields of objects.
 For example, all of i32 elements used for key field in 1 million Customer object are stored in Vec$<$i32$>$ with 1 million i32 elements. 
-Later, these i32 elements are moved to be owned or borrowed by the object's fields.
+Later, these i32 elements are moved to be owned or borrowed by the objects' fields.
 
-Next, 3, 13, 23, 33 million of Customer objects are created and stored in Vec. 
+Next, 3, 13, 23, 33 million Customer objects are created and stored in Vec. 
 When a Customer Vec is created, whether size of Vec is initialized is controlled. 
-Finally, serialization of Customer object is performed as an operation forcing program to access all of fields in the object.
-This serialization is performed each Customer objects in the Vec. We measure total runtime to serialize all of Customer objects 
+Finally, serialization of Customer object is performed as an operation forcing the program to access all of fields in the object.
+This serialization is performed for each Customer objects in the Vec. We measure total runtime to serialize all of Customer objects 
 stored in Vec.
@@
 The result is shown in Figure~\ref{fig:rustaccessinit} and Figure~\ref{fig:rustaccessnoinit}.
-Figure~\ref{fig:rustaccessinit} is comparison of the runtime performance among different Customer object types with Vec size initialization.
-Figure~\ref{fig:rustaccessnoinit} is comparison in the same set of experiment except Vec size is not initialized. 
-The blue, yellow, and green chats represent runtime of access to fields of CustomerOwned, CustomerBorrowed, and CustomerSlice objects respectively.
+Figure~\ref{fig:rustaccessinit} is a comparison of the runtime performance among different Customer object types with Vec size initialization.
+Figure~\ref{fig:rustaccessnoinit} is a comparison in the same set of experiment except Vec size is not initialized. 
+The blue, yellow, and green bars represent runtime of access to fields of CustomerOwned, CustomerBorrowed, and CustomerSlice objects respectively.
 
-No matter Vec size initialized or not, differences of runtime for accessing objects are not remarkable among different object types.
+Whether Vec size is initialized or not, differences of runtime for accessing objects are not remarkable among different object types. 
+The memory usage for algorithms with 33 million of Customer objects are about 26G bytes for any type of variable.
 
@@
 Difference of variable types does not have huge impact to runtime of accessing to actual value.
-Even thought owner, reference , and slice have different memory representations, the access time to its value is 
+Even though owner, reference , and slice have different memory representations, the access time to its value is 
 close to each other. As shown in Figure~\ref{fig:own_ref_slice}, the representations of owner and slice are almost identical except slice does not have capacity for values.

### 2020-06-28 thesis_template/3_Body/model/drop_ref_rc.tex
corrected

@@
 Therefore, the evaluated runtime of dropping objects only consists of dropping time of reference or Rc, but deallocation time.
-We generated 10, 20, 30, and 40 million of CustomerBorrowed and CustomerRc objects and performed drop one by one.
+We generated 10, 20, 30, and 40 million CustomerBorrowed and CustomerRc objects and performed drop one by one.
 
@@
 The reason why dropping Rc is much slower than dropping reference is that Rc requires runtime overhead to check some states of the variable, 
-but when to drop reference is already determined at compile time. When dropping Rc, Rc has to check the number of variable pointing to the actual content and decide 
-deallocate the memory or not. However, memory management and lifetime strategy of reference is already determined at compile time.
+but when to drop reference is already determined at compile time. When dropping Rc, Rc has to check the number of variables pointing to the actual content and decide 
+whether to deallocate the memory or not. However, memory management and lifetime strategy of reference is already determined at compile time.
 This determination of memory management strategy at compile increases runtime performance of dropping complex object constructed with reference type variable.
@@
 However, dealing with reference is sometimes cumbersome. Tracking lifetime of reference can be done easily in simple situation. 
-But, if we have complex objects constructed with fields of reference, the lifetime tracking become extremely difficult. 
-For example, constructing nested objects with reference fields require a developer to plan memory management with many lifetime symbols. 
-Using reference counting eliminates developer's responsibility to specify lifetime of variables. 
+But, if we have complex objects constructed with fields of reference, the lifetime tracking becomes extremely difficult. 
+For example, constructing nested objects with reference fields requires a developer to plan memory management with many lifetime symbols. 
+Using reference counting eliminates the developer's responsibility to specify lifetime of variables. 
 This may ease and speed up development process, and increase understandability of codes.
@@
 Even though we have stack allocated values, such as i32 and f64, in Rc in our experiment, 
-one should avoid wrapping stack allocated values in Rc. Wrapping value in Rc allocates heap memory so that allocating Rc$<$i32$>$ or Rc$<$f64$>$ unnecessarily use space of 
+one should avoid wrapping stack allocated values in Rc. Wrapping value in Rc allocates heap memory so that allocating Rc$<$i32$>$ or Rc$<$f64$>$ unnecessarily uses space of 
 heap. Additionally, stack allocated values are usually easy to be copied. Therefore, developer does not have to even use reference; one can just copy the value. 

### 2020-06-28 thesis_template/3_Body/model/experimental_set_detail.tex
corrected

@@
-We have used two different data sets. One is a real-world data set, Wikipedia page data set,
-and another is a syntactic randomized generated data set based on Complex object described in Section~\ref{sec:concept_compobj}. 
-We use one machine with particular specification.
+We have used two different datasets. One is a real-world data set, Wikipedia page data set,
+and another is a syntactic randomized generated data set based on Complex objects described in Section~\ref{sec:concept_compobj}. 
+We use one machine with particular specifications.
 \subsection{Wikipedia Data Sets}

### 2020-06-28 thesis_template/3_Body/model/knn.tex
presentation
corrected

@@
-Finally, we examine performance of a Machine Learning (ML) algorithms. 
+Finally, we examine the performance of Machine Learning (ML) algorithms. 
 The goal of this experiment is to evaluate better memory management strategies in ML algorithms developed with Rust.
-We employ K-Nearest-Neighbors (KNN) for ML algorithm to be studied in our experiments.
+We employ K-Nearest-Neighbors (KNN) for ML algorithms to be studied in our experiments.
 Our KNN algorithms perform document classification on Wikipedia page data set described in Section~\ref{sec:eval_setdetail}.
 
-The algorithms have 4 phase; load, preprocess, query, and combine phase. 
-Before these phase, we separate data sets into 8 partitions to run these in different threads. 
-The algorithms spawn threads at the beginning ,and in the load phase partition of files are loaded in each threads. 
-In preprocessing phase, the algorithm process document strings to generate Term-frequencies (Tfs) matrices and other data structures. 
-In query phase, it calculates cosine similarities between all combination of train and test observations and select to top \(K\) nearest neighbors. 
-In combine phase, the results from each batch and from each are combined. 
-Based on our experiments result, the runtime in preprocess and query phase are significantly larger than other two phases.
-Therefore, we focus discussion in these two phases considering them bottlenecks in our KNN algorithms.
+The algorithms have 4 phases; load, preprocess, query, and combine phase. 
+Before these phases, we separate data sets into 8 partitions to run these in different threads. 
+The algorithms spawn threads at the beginning, and in the load phase partition of files are loaded in each threads. 
+In the preprocessing phase, the algorithm process document strings to generate Term-frequencies (Tfs) matrices and other data structures. 
+In the query phase, it calculates cosine similarities between all combination of train and test observations and select to top \(K\) nearest neighbors. 
+In combine the phase, the results from each batch and from each thread are combined. 
+Based on our experiment's result, the runtime in preprocess and query phase are significantly larger than other two phases.
+Therefore, we focus our discussion in these two phases considering them bottlenecks in our KNN algorithms.
 
@@
 
-Method parameter is specified to select memory management strategy used in preprocess phase. 
-In preprocess phase, the algorithm generates many intermediate data structures using same String elements.
+Method parameters are specified to select memory management strategy used in preprocess phase. 
+In preprocess the phase, the algorithm generates many intermediate data structures using same String elements.
 Deep-copy method deeply copies String to generate intermediate data structures. Arc method use Atomic Reference Count (Arc) to wrap String elements in the original data structure and 
 clone Arc when the elements are used in other data structures. As Experiment 4 had shown in in Section~\ref{sec:eval_treeagg}, deep-copy of complex objects is more expensive than cloning Arc. 
-String is a sort of objects allocated in heap and copied many times in preprocess phase. Therefore, it is worth to assess which method can be better memory management strategy in our experiments.
+String is a sort of object allocated in heap and copied many times in preprocess phase. Therefore, it is worth assessing which method can be a better memory management strategy in our experiments.
 
-Strategy parameter controls memory management strategy used in both preprocess and query phase.
+Strategy parameter control memory management strategy used in both preprocess and query phase.
 Strategy 1 keeps all intermediate data structures and numeric matrix objects from preprocess to query phase. 
@@
 frequency of memory deallocations. 
-The size of each batch is defined in 6250 pages when we have 2 batches, and 4166 or 4167 when we have 3 batches. 
-The parameter k specifies number of dimension of feature matrices created out of preprocess phase. 
+The size of each batch is defined in 6,250 pages when we have 2 batches, and 4166 or 4167 when we have 3 batches. 
+The parameter k specifies the number of dimensions of feature matrices created out of the preprocess phase. 
 By controlling this, it determines size of intermediate data structures and numeric matrices.
@@
 \label{sec:history}
-Figure~\ref{fig:total}, ~\ref{fig:preprocess}, and ~\ref{fig:query} show the runtime performance of our KNN algorithms in total, preprocess, and query phase respectively. 
+Figures~\ref{fig:total}, ~\ref{fig:preprocess}, and ~\ref{fig:query} show the runtime performance of our KNN algorithms in total, preprocess, and query phase respectively. 
 The algorithms used in our experiments are indexed in Table~\ref{tab:algorithm}. We call each algorithm in algorithm number for easy understanding.
@@
 Figure~\ref{fig:total} shows Algorithm 8 shows much slower performance compare to the other algorithms.
-Algorithm 7 also starts to slow down as we increase the number of dimension.
+Algorithm 7 also starts to slow down as we increase the number of dimensions.
 
 As shown in Figure~\ref{fig:preprocess}, the algorithms using Arc is much slower than using deep-copy in preprocessing phase. 
-Algorithm 6 is 38\%  slower than Algorithm 6 in dimension of 25K. 
+Algorithm 8 is 38\%  slower than Algorithm 6 in dimension of 25K. 
 In addition, the algorithms with strategy 2 are slower than with strategy 1. 
@@
 The algorithms with 3 batches are slower that ones with 2 batches.
-Furthermore, as we increase the number of dimension, the number of batch becomes more and more critical to runtime performance of the algorithms with deep-copy.
+Furthermore, as we increase the numbers of dimension, the number of batches becomes more and more critical to runtime performance of the algorithms with deep-copy.
 The runtime ratios of difference from Algorithm 7 to Algorithm 8 are about 44\%, 28\%, and 39\% for dimension of 15K, 20K, and 25K respectively. 
-However, those from Algorithm 5 to Algorithm 6 are about 11\%, 28\%, and 54\%. The ratios of difference increase proportionally to the number of dimension.
+However, those from Algorithm 5 to Algorithm 6 are about 11\%, 28\%, and 54\%. The ratios of difference increase proportionally to the number of dimensions.
 
@@
 \label{sec:history}
-In preprocess phase, the algorithms using Arc method performs worse than ones with deep-copy method. 
+In the preprocess phase, the algorithms using Arc method perform worse than ones with deep-copy method. 
 This result may seem to contradict to the result of Experiment 4 in Section~\ref{sec:eval_treeagg}.
@@
 In this Experiment 5, we however get Arc or deep-copy of String instead of complex object.
-The result explains deep-copying String is much inexpensive than deep-copying the complex object and 
-using deep-copy method is actually efficient than using Arc to share String. 
+The result explains deep-copying String is more inexpensive than deep-copying the complex object and 
+using deep-copy method is actually more efficient than using Arc to share String. 
 Therefore, we need to make decision which method to use depending on size and complexity of objects.
 
-In addition, use of different strategies in preprocess phase explains how deallocations of intermediate data structures and drops of their variables impact algorithm's runtime performance.
+In addition, the use of different strategies in the preprocess phase explains how deallocations of intermediate data structures and drops of their variables impact algorithm's runtime performance.
 The result shows deallocations of intermediate data costs a lot; Algorithm 6 is 85\% slower than Algorithm 2.
-This may be more severe bottleneck for algorithms using Arc; Algorithm 8 is 102\% slower than Algorithm 4.
+This may be a more severe bottleneck for algorithms using Arc; Algorithm 8 is 102\% slower than Algorithm 4.
 This is the same reason explained in Experiment 4. 
@@
 In addition, as we increase the number of dimension, the ration of runtime difference among different numbers of batch for the algorithms with deep-copy, but not for ones with Arc.
-This is because algorithm with Arc does not de/allocate memory as much frequent as ones with deep-copy.
-The intermediate data structures mealy get reference to String values without actually allocating memory for copied Strings.
+This is because algorithm with Arc does not de/allocate memory as much frequently as ones with deep-copy.
+The intermediate data structures merely get reference to String values without actually allocating memory for copied Strings.
 
@@
 
-However, we can see significant degradation in Algorithm 7 with 20K and 25K dimension and Algorithm 8 with 15K, 20K, and 25K dimension. 
+However, we can see significant degradation in Algorithm 7 with 20K and 25K dimensions and Algorithm 8 with 15K, 20K, and 25K dimensions. 
 By using strategy 2, we deallocate the numeric matrices and vectors in query phase. However, it is difficult to think that these contiguous memory deallocations cause the degradation. 
-If that is so, Algorithm 5 and 6 should also show some overheads. No page-swapping does not happen during the execution. 
+If that is so, Algorithm 5 and 6 should also show some overheads. No page-swapping happens during the execution. 
 One possible reason is that these algorithms suffer from the allocation of numeric matrices and vectors due to previous deallocation of intermediate data structures in preprocess phase. 
@@
 The computation on these numeric objects may slow down due to their caching levels. 
-To conclude these discussion, we need to conduct more experiments and deeper analysis. 
-However, we push those discussion in next paper.
+To conclude this discussion, we need to conduct more experiments and deeper analysis. 
+However, we push those discussion to next paper.
 
-In a part of conclusion, using Arc to String may be overhead. Considered the result from Experiment 4, we need careful consideration which object to use which strategy, deep-copy and Arc.
+As a part of the conclusion, using Arc to String may be overhead. Considering the result from Experiment 4, we need careful consideration which object to use which strategy, deep-copy and Arc.
 In addition, frequent memory deallocation can lead to slower runtime performance. 

### 2020-06-28 thesis_template/3_Body/model/merge_sort_experiment.tex
done
corrected

@@
 Sorting algorithm like merge-sort is a very ubiquitous algorithm in any computation. 
-Especially in Big Data processing, merge-sort algorithm de/allocates contiguous memory for partitions of sorted vector multiple times.
-We are interested in memory de/allocation pattern in merge-sort algorithm, because it generates many intermediate data structures and delete them many times.
+Especially in Big Data processing, merge-sort algorithms de/allocate contiguous memory for partitions of sorted vector multiple times.
+We are interested in memory de/allocation patterns in merge-sort algorithm, because it generates many intermediate data structures and deletes them many times.
 
 As explained in Experiment 2 in Section~\ref{sec:eval_refcount}, deletion of Rc has significant overhead than normal reference. 
-By learning this result, our assumption here is that deletion of Arc has also overhead when we compare to normal reference. 
-In many situation where developer writes a multithreading code, Arc is used and the deletion happens multiple times. 
-To assess runtime overhead of algorithm with Arc, We implement merge-sort algorithm in two different ways. 
+By learning this result, our assumption here is that deletion of Arc also has overhead when we compare to normal reference. 
+In many situations where a developer writes a multithreading code, Arc is used and the deletion happens multiple times. 
+To assess runtime overhead of algorithms with Arc, we implement merge-sort algorithm in two different ways. 
 One is sharing source vector with Arc. The other is passing reference of source vector to child thread.
@@
 Copying phase occurs in the base case of the recursive call. The element in the source vector in a certain index is deep-copied into newly allocated vector.
-At merge phase, merge function receives two sorted independent vector and merge them into single new vector.
+At merge phase, merge function receives two sorted independent vectors and merges them into a single new vector.
 
@@
 Scoped thread can have reference to value from its parent thread by ensuring children threads are joined before their parent thread returns value. 
-By using scoped thread, we can implement two merge-sort algorithms in identical way except whether the function receives Arc or reference of source vector.
-The representations of source vector for each algorithm are shown in Figure~\ref{fig:source_merge_sort}.
-The elements of source vector are CustomerOwned objects. We generates source vectors in size of 4, 8, 12 and 16 million.
-Finally, merge-sort is performed based on value of key field. The figure shows the result for runtime performance of merge-sort algorithms on difference size of vectors.
+By using scoped thread, we can implement two merge-sort algorithms in an identical way except whether the function receives Arc or reference of source vector.
+The representations of source vectors for each algorithm are shown in Figure~\ref{fig:source_merge_sort}.
+The elements of source vector are CustomerOwned objects. We generate source vectors in sizes 4, 8, 12 and 16 million.
+Finally, merge-sort is performed based on value of key field. The figure shows the result for runtime performance of merge-sort algorithms on difference sizes of vectors.
 
@@
 The result says that algorithms with Arc is about 21\% slower than algorithms with reference.
+The memory usage for algorithms with 16 million Customer objects are about 26G bytes.
 
@@
 \subsection{Discussion}
-The reason why merge-sort algorithm with Arc is much slower than one with reference is 
+The reason why merge-sort algorithms with Arc is much slower than one with reference is 
 the same for the reason why dropping Rc shows overhead compared to dropping reference.
@@
 
-In addition, Arc uses atomic operations for tis reference counting. Atomic operations bring thread-safety, but they are more expensive than ordinary memory accesses.
+In addition, Arc uses atomic operations for reference counting. Atomic operations bring thread-safety, but they are more expensive than ordinary memory accesses.
 Therefore, when sharing reference counting between threads is not required, using Rc is the recommended way \cite{RustArcPage}.
 
-In the situation like our experiment, normal reference can be used instead of Arc to share data between threads. 
+In situations like our experiment, normal reference can be used instead of Arc to share data between threads. 
 This solution results in better runtime performance in our experiment. Therefore, one should use reference to share data among different threads 

### 2020-06-28 thesis_template/3_Body/model/tree_aggregate_experiment.tex
corrected

@@
-In our experiment, tree-aggregation algorithms are examined in multi-threading. This experiment is to evaluate the impact of having Arc (Atomic Reference Counting) as elements of vector. 
-In Big Data mining tool, such as Spark, it generates intermediate objects from original source vector. In tree-aggregation, aggregated HashMap like data structure is created in each step or node. 
-Acquisition of elements in source vector is required to perform this aggregation. There are several ways.
+In our experiment, tree-aggregation algorithms are examined in multi-threading. This experiment is to evaluate the impact of having Arc (Atomic Reference Counting) as elements of vectors. 
+In Big Data mining tools, such as Spark, it generates intermediate objects from the original source vector.
+In tree-aggregation, aggregated HashMap like data structures is created in each step or node.
+Acquisition of elements in the source vector is required to perform this aggregation. There are several ways.
 
-One way is deep-copy elements of vector. This solution allocated newly created objects by deep-copy. 
-Aggregation is performed on copied objects, stores them in the data structure and sends it to next node. 
-Deep-copy generates duplicates of objects in vector and aggregated data structure. 
-This can lead to memory intensive moment when we need memory space for the duplicated objects in addition.
+One way is to deep-copy elements of the vector. This solution allocates newly created objects by deep-copy. 
+Aggregation is performed on copied objects, they are stored in the data structure and sent to next node. 
+Deep-copying generates duplicates of objects in vectors and aggregated data structure. 
+This can lead to memory intensive moments when we need memory space for the additional duplicated objects.
 
 The other way is to get reference to the elements. Since an original source vector is deallocated after a local aggregation,
-Simple reference to elements does not live long enough and allow the aggregation result to be sent to next node. 
-Instead of simple borrowing, we need owner in the aggregation result. Reference Counting (Rc) in Rust is a way to have multiple owners to a value. 
-Since our experiment is implemented in multithreading, Atomic Reference Counting (Arc) is used instead of Rc. With Arc, multiple ownership pointer can be 
-possessed by different variables across multiple threads. Therefore a value is not deallocated until all of owners to it are dropped. 
-This does not require extra memory allocation, because only acquisition of new ownership to value is needed. 
+simple references to elements do not live long enough and allow the aggregation result to be sent to next node. 
+Instead of simple borrowing, we need owners in the aggregation result. Reference Counting (Rc) in Rust is a way to have multiple owners to a value. 
+Since our experiment is implemented in multithreading, Arc (Arc) is used instead of Rc. With Arc, multiple ownership pointers can be 
+possessed by different variables across multiple threads. Therefore, a value is not deallocated until all owners to it are dropped. 
+This does not require extra memory allocation, because only acquisition of new ownership to the value is needed. 
 However, as explained in the last section deletion of Arc type checks whether the value is still owned by other variables. 
-This checking may be an overhead in algorithms where generate a lot of intermediate data structures, because deletion of the data structures occurs in frequent.
+This checking may be an overhead in algorithms that generate a lot of intermediate data structures, because deletion of the data structures occurs frequently.
 
-Two algorithms are implemented using the above two different methods and evaluated their runtime performance. 
+Two algorithms are implemented using the above two methods and their runtime performance is evaluated . 
 We perform aggregation to CustomerOwned based on last\_name field. 
-Before tree-aggregation algorithms are run, partitions of Vec$<$CustomerOwned$>$ or of Vec$<$Arc$<$CustomerOwned$>>$ are created ,serialized, and stored in disk.
+Before tree-aggregation algorithms are run, partitions of Vec$<$CustomerOwned$>$ or of Vec$<$Arc$<$CustomerOwned$>>$ are created, serialized, and stored in disk.
 A tree-aggregate algorithm has main three phases: loading, aggregating, and combining phase. 
-At loading phase the algorithm generate threads. In each node, it loads serialized CustomerOwned partition from disk and deserialize them.
+At loading phase the algorithm generates threads. In each node, it loads serialized CustomerOwned partition from disk and deserialize them.
 At aggregating phase, aggregation is performed on each partition by last\_name field. Once a node finishes aggregation, it sends result to parent node. 
-After parent nodes receive aggregation results from all of its children nodes, it joins all aggregation results including its and sends next parent. 
+After parent nodes receive aggregation results from all of its children nodes, it joins all aggregation results including its and sends to the next parent. 
 This joining aggregation results is considered as combining phase.
 
-Two kinds of algorithm are implemented. One algorithm performs aggregation by deep-copying elements from source vector loaded from disk. 
-In the other algorithm, each element of source vector is wrapped in Arc, and its reference is acquired while aggregation. 
-The difference of the both algorithm codes are represented in Figure~\ref{fig:arc_tree} and in Figure~\ref{fig:deep_tree}.
-If we glance the codes, the notable difference is only when we acquire an element from CustomerOwned Vec to construct an aggregated data structure.
-Therefore, there is few difference between two kinds of tree-aggregate algorithm in terms of code appearance.
+Two kinds of algorithms are implemented. One algorithm performs aggregation by deep-copying elements from a source vector loaded from a disk. 
+In the other algorithm, each element of the source vector is wrapped in Arc, and its reference is acquired while aggregation. 
+The difference between the both algorithm codes are represented in Figure~\ref{fig:arc_tree} and in Figure~\ref{fig:deep_tree}.
+If we glance at the codes, the notable difference is only when we acquire an element from CustomerOwned Vec to construct an aggregated data structure.
+Therefore, there are few difference between the two kinds of tree-aggregate algorithm in terms of code appearance.
 
@@
 The runtime of algorithm with deep-copy is about 40 to 50\% slower than algorithm with Arc for every vector size. 
+The memory usage of algorithm with Arc and size of 8 million is about 15G bytes. On the other hand, 
+the memory usage of algorithm with deep-copy and size of 8 million is about 26G bytes.
 
@@
 At the aggregating phase, each object is deep-copied or acquired with Arc once during the runtime in order to construct aggregated data structures.
-If total number of object is 1 million, the all of 1 million objets are deep-copied or cloned with Arc once during execution. 
+If total number of objects is 1 million, the all of 1 million objects are deep-copied or cloned with Arc once during execution. 
 Deep-copy allocates new memory for copied object. On the other hand, clone with Arc is merely acquisition of additional owner. 
@@
 
-After construction of aggregated data structure, the dropping variables of original object occurs at the end of aggregating phase.
+After construction of aggregated data structure, the dropping variables of original objects occurs at the end of the aggregating phase.
 In the algorithm with deep-copy, these variables are owners so that drop of variables triggers deallocation of actual values.
 In the algorithm with Arc, the variables are Arc. The aggregated data structure contains Arc pointing to the same values pointed by original Arc.
-Since the aggregated data structure continue to live after aggregating phase, drop of original Arcs does not triggers deallocation of values. 
+Since the aggregated data structures continue to live after aggregating phase, drop of original Arcs does not triggers deallocation of values. 
 Therefore, drop of original variables can shows overhead of memory deallocation in algorithm with deep-copy, 
@@
 
-In addition, memory access from Arc is slower than ordinal variable due to the atomic operations. This may be potential overhead of the algorithm with Arc.
+In addition, memory access from Arc is slower than ordinal variables due to the atomic operations. This may be potential overhead of the algorithm with Arc.
 
-Considered these theoretical analysis and result of our experiment, using Arc improves runtime performance and memory usage compared to algorithm using deep-copy in tree-aggregate algorithm.
+Considered these theoretical analysis and result of our experiment, using Arc improves runtime performance and memory usage compared to algorithms using deep-copy in tree-aggregate algorithms.

### 2020-06-28 thesis_template/4_Conclusion/conclusion.tex
corrected

@@
 
-Difference of variable types does not have impact on operation to access memory address where a value is located. 
-This result gives us freedom of choices for variable types to construct complex objects in terms of runtime performance. 
-When we however use borrowed types, such as references and slices, their lifetime should be explicitly defined. 
-Therefore, we may use owner type variables to construct construct complex objects in order to facilitate lifetime tracking.
+Differences between variable types do not have an impact on operations to access memory address where a value is located. 
+This result gives us freedom of choice for variable types to construct complex objects in terms of runtime performance. 
+However when we use borrowed types, such as references and slices, their lifetime should be explicitly defined. 
+Therefore, we may use owner type variables to construct complex objects in order to facilitate lifetime tracking.
 
-Runtime to drop Rc is much 60 times slower than normal reference. This is because Rc needs to check reference count to determine whether to deallocate its value. 
+Runtime to drop Rc is 60 times slower than normal reference. This is because Rc needs to check reference count to determine whether to deallocate its value. 
 This result may say that we should use normal reference whenever it is possible. 
 Again, tracking lifetime of references used in complex objects can be cumbersome. 
-Choice of Rc and reference is dependent on complexity of object implemented.
+Choice of Rc and reference is dependent on complexity of objects implemented.
 
-In Rust, we can implement multithread programming with sharing data using Arc. In simple multithread algorithms, 
-one can write code where shares data with Arc and simple reference among different threads.
+In Rust, we can implement multithread programming by sharing data using Arc. In simple multithread algorithms, 
+one can write code that shares data with Arc and simple reference among different threads.
 Merge-sort algorithms sharing data with Arc is 21\% slower than normal reference. 
@@
 For more complex algorithms, like tree-aggregate and preprocess phase in KNN, one can implement algorithms sharing data with Arc or simply deep-copy the values.
-The algorithms with deep-copy is about 40 to 50\% slower than the algorithm with Arc for complex objects.
-When we however deal with String, the algorithms with deep-copy is faster than Arc. 
-Therefore, the decision which to use deep-copy or Arc method should be determined based on complexity of objects.
+The algorithms with deep-copy are about 40 to 50\% slower than the algorithms with Arc for complex objects.
+However when we deal with String, the algorithms with deep-copy are faster than Arc. 
+Therefore, the decision on whether to use deep-copy or Arc method should be determined based on the complexity of objects.
 
@@
 
-As we can see in the results of experiment, different memory strategy varies the performance of algorithms in Rust programming.
+As we can see in the results of our experiments, different memory strategies vary the performance of algorithms in Rust programming.
 Which memory management strategy to take depends on what objects to deal with. 

### 2020-07-03 thesis_template/3_Body/chapter/concept.tex
resolved

@@
       \medskip
-      \centerline{(c)}
+      \centerline{(d)}
     \end{minipage}\hfill
     \caption{Representation of Customer objects Whose fields are different variable type: (a) CustomerOwned struct whose fields are all owned 
-    (b) CustomerBorrowed struct whose fields are borrowed with reference (c) CustomerSlice struct whose fields are borrowed with slice for sequence value, otherwise reference}
+    (b) CustomerBorrowed struct whose fields are borrowed with reference (c) CustomerSlice struct whose fields are borrowed with slice for sequence value, otherwise reference 
+    (d) CustomerRc struct whose fields are reference counting}
     \label{fig:customer}
@@
       \medskip
-      \centerline{(c)}
+      \centerline{(d)}
     \end{minipage}\hfill
     \caption{Representation of Order objects Whose fields are different variable type: (a) OrderOwned struct whose fields are all owned 
-    (b) OrderBorrowed struct whose fields are borrowed with reference (c) OrderSlice struct whose fields are borrowed with slice for sequence value, otherwise reference}
+    (b) OrderBorrowed struct whose fields are borrowed with reference (c) OrderSlice struct whose fields are borrowed with slice for sequence value, otherwise reference 
+    (d) OrderRc struct whose fields are reference counting}
     \label{fig:order}

### 2020-10-11 thesis_template/0_Prelim/cv.tex
completed correction

\addcontentsline{toc}{chapter}{Curriculum Vitae}
\thispagestyle{empty}

\begin{center}
{\LARGE {\bf CURRICULUM VITAE}}\\
\vspace{0.5in}
\end{center}

\setcounter{section}{0}
\renewcommand*{\theHsection}{chX.\the\value{section}}

\section*{Contact}
\begin{itemize}
    \item Phone: +81-90-4148-4639 \textbullet{} City: Tokyo \textbullet{} Email: \href{golisaku4639@gmail.com}{golisaku4639@gmail.com} 
    \item GitHub: \href{https://github.com/ShinsakuOkazaki}{\textbf{github}.com/ShinsakuOkazaki} 
    \item LinkedIn\href{https://www.linkedin.com/in/shinsaku-okazaki-7b786b13b}{ \textbf{linkedin}.com/in/shinsaku-okazaki-7b786b13b}
\end{itemize}

\section*{Education}
\subsection*{Boston University, Boston, MA}
\begin{itemize}
    \item Program: Master of Science in Computer Information Systems (September 2018 - May 2020)
    \item Course Work: Software Design Pattern, Database, Big Data Analysis, Data Analysis
    \item Master Thesis: An Experimental Study of Memory Management with Rust Programming for Big Data Processing
\end{itemize}

\subsection*{Seikei University, Tokyo}
\begin{itemize}
    \item Program: Bachelor of Science in System Design (April 2013 - March 2018)
    \item Course Work: Image Processing, Control Engineering, Digital Signal Processing, Engineering Economics
\end{itemize}

\section*{Experience} 
\subsection*{Research Assistant, Boston University, September 2019 - May 2020}
\begin{itemize}
    \item  Improved run-time performance of Large Scale Sort Algorithm 30\% by implementing algorithm with careful Memory Management strategies in Rust.
    \item  Developed Merge-sort Algorithm and Tree-aggregate Algorithm with Multithreading using Rust on Cloud Instances using GCP.
    \item Implemented \textbf{Machine Learning} Algorithm with different memory management strategy to assess best workflow on \textbf{Natural Language Processing} with Rust.
\end{itemize}

\subsection*{Teaching Assistant, Boston University, September 2019 - May 2020}
\begin{itemize}
    \item  Developed a R package where student can take R programming exercises to improve student's learning experience.
    \item  Designed data collection feature by adding REST APIs using Flask and MongoDB.
    \item  Facilitated customization of software by reducing building process 60\% with automation using Bash script.
    \item  Collaborated with a team of 4 members to design flexible and robust software architecture.
\end{itemize}

\subsection*{Software Engineer Intern, Brigham and Women's Hospital, June 2019 - August 2019}
\begin{itemize}
    \item  Automated data inputs with attribute suggestion feature using React.js and AJAX
    \item  Designed data collection feature by adding REST APIs using Flask and MongoDB.
    \item  Wrote about 100 unit test cases in Mocha and Chai and increased test coverage by 5\%.
\end{itemize}

### 2020-10-11 thesis_template/3_Body/chapter/concept.tex
completed correction

@@
 \begin{figure}[htb]
-    \begin{minipage}[t]{0.2\linewidth}\centering
-        \begin{lstlisting}
+    \begin{subfigure}{.5\textwidth}\centering
+        \begin{lstlisting}[
+            basicstyle=\tiny, %or \small or \footnotesize etc.
+        ]
             struct CustomerOwned {
@@
       \centerline{(a)}
-    \end{minipage}\hfill
-    \begin{minipage}[t]{0.6\linewidth}\centering
-        \begin{lstlisting}
+    \end{subfigure}\hfill
+    \begin{subfigure}{.5\textwidth}\centering
+        \begin{lstlisting}[
+            basicstyle=\tiny, %or \small or \footnotesize etc.
+        ]
             struct CustomerBorrowed<'a> {
@@
       \centerline{(b)}
-    \end{minipage}
-    \begin{minipage}[t]{0.2\linewidth}\centering
-        \begin{lstlisting}
+    \end{subfigure}\hfill
+
+    \medskip
+
+    \begin{subfigure}{.5\textwidth}\centering
+        \begin{lstlisting}[
+            basicstyle=\tiny, %or \small or \footnotesize etc.
+        ]
             struct CustomerSlice<'a> {
@@
       \centerline{(c)}
-    \end{minipage}\hfill
-    \begin{minipage}[t]{0.6\linewidth}\centering
-        \begin{lstlisting}
+    \end{subfigure}\hfill
+    \begin{subfigure}{.5\linewidth}\centering
+        \begin{lstlisting}[
+            basicstyle=\tiny, %or \small or \footnotesize etc.
+        ]
             struct CustomerRc {
@@
       \centerline{(d)}
-    \end{minipage}\hfill
+    \end{subfigure}\hfill
     \caption{Representation of Customer objects Whose fields are different variable type: (a) CustomerOwned struct whose fields are all owned 
@@
  \begin{figure}[htb]
-    \begin{minipage}[t]{0.2\linewidth}\centering
-        \begin{lstlisting}
+    \begin{minipage}[t]{0.5\linewidth}\centering
+        \begin{lstlisting}[
+            basicstyle=\tiny, %or \small or \footnotesize etc.
+        ]
             struct OrderOwned {
@@
     \end{minipage}\hfill
-    \begin{minipage}[t]{0.6\linewidth}\centering
-        \begin{lstlisting}
+    \begin{minipage}[t]{0.5\linewidth}\centering
+        \begin{lstlisting}[
+            basicstyle=\tiny, %or \small or \footnotesize etc.
+        ]
             struct OrderBorrowed<'a> {
@@
     \end{minipage}
-    \begin{minipage}[t]{0.2\linewidth}\centering
-        \begin{lstlisting}
+    \begin{minipage}[t]{0.5\linewidth}\centering
+        \begin{lstlisting}[
+            basicstyle=\tiny, %or \small or \footnotesize etc.
+        ]
             struct OrderSlice<'a> {
@@
     \end{minipage}\hfill
-    \begin{minipage}[t]{0.6\linewidth}\centering
-        \begin{lstlisting}
+    \begin{minipage}[t]{0.5\linewidth}\centering
+        \begin{lstlisting}[
+            basicstyle=\tiny, %or \small or \footnotesize etc.
+        ]
             struct OrderRc {

### 2020-10-11 thesis_template/3_Body/model/different_element.tex
completed correction

@@
 \begin{figure}[htb]
-    \begin{lstlisting}
+    \begin{lstlisting}[
+            basicstyle=\tiny, %or \small or \footnotesize etc.
+        ]
         class Customer {
@@
 \begin{figure}[htb]
-    \begin{lstlisting}
+    \begin{lstlisting}[
+            basicstyle=\tiny, %or \small or \footnotesize etc.
+        ]
         struct Customer {

### 2020-10-11 thesis_template/3_Body/model/tree_aggregate_experiment.tex
completed correction

@@
 \begin{figure}[htb]
-    \begin{lstlisting}
+    \begin{lstlisting}[
+            basicstyle=\tiny, %or \small or \footnotesize etc.
+        ]
         fn aggregate_local(arr :&[Arc<CustomerOwned>]) 
@@
 \begin{figure}[htb]
-    \begin{lstlisting}
+    \begin{lstlisting}[
+            basicstyle=\tiny, %or \small or \footnotesize etc.
+        ]
         fn aggregate_local_copy(arr :&[CustomerOwned]) 

### 2020-10-11 thesis_template/Appendix/model/linalg.tex
completed correction

@@
     \item Compile java file with -h header flag to create class file (CBLASJ.class) and header file (CBLASJ.h).
-\begin{lstlisting}[language=bash]
+\begin{lstlisting}[
+    language=bash, 
+    basicstyle=\tiny, %or \small or \footnotesize etc.
+    ]
     $ javac -h . CBLASJ.java
@@
     \item Create C file (CBLASJ.c) which will bind Java interface and CBLAS library. And compile it with JNI to create object file (CBLASJ.o).
-\begin{lstlisting}[language=bash]
+\begin{lstlisting}[
+    language=bash, 
+    basicstyle=\tiny, %or \small or \footnotesize etc.
+    ]
     $ gcc -c-fPIC -I${JAVA_HOME}/include -I${JAVA_HOME}/include/darwin CBLASJ.c
 \end{lstlisting}
-    \item Compile shared library linking library (libcblas.a or libcblas.dylib) object file (CBLASJ.o).
-\begin{lstlisting}[language=bash]
+    \item Compile shared library linking library (libcblas.a or libcblas.dylib) to object file (CBLASJ.o).
+\begin{lstlisting}[
+    language=bash, 
+    basicstyle=\tiny, %or \small or \footnotesize etc.
+    ]
     $ gcc -o libcblas.dylib (or libcblas.a) CBLASJ.o 
